### 2018-09-07 phil_paper/jmp_wjv_v2.tex
tons of good work here

\documentclass[12pt]{article}
\usepackage[margin=1in] {geometry}                
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
\pagestyle{plain}                           % Eliminates both the header and footer
\usepackage[parfill]{parskip}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{array}
%\usepackage{pgfplots}
\usepackage{tikz}
\usepackage{tkz-euclide}
\usepackage{longtable}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{verbatim}  %so that you can comment blocks of code
\usepackage{setspace}  %change the spacing
\usepackage[authoryear]{natbib}
\usepackage{bbm}
\usetikzlibrary{calc}
%\usepackage{csvsimple}
\usepackage[toc,page]{appendix}
\usepackage{hyperref}
\usepackage{cleveref}
\usepackage{rotating}
\usepackage{booktabs}
\usepackage{authblk}
\usepackage[bottom]{footmisc}
\usepackage{titling}
%% \newcommand{\KEYtitle}{Even Weights}
%\usepackage[nomarkers]{endfloat}
%\bibliography{library} 
%\renewcommand{\efloatseparator}{\mbox{}}
\usepackage{rotating}
\usepackage{pdflscape}
\usepackage[export]{adjustbox}
\usetikzlibrary{positioning}

%\usepackage{datetime}
%\newdateformat{monthyeardate}{\monthname[\THEMONTH]}

%\usepackage[dvipsnames]{xcolor}
%\usepackage{cite}
\onehalfspacing
\usepackage{natbib}  
\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
\author{William Violette}
\affil{Brown University\thanks{ I am grateful to Andrew Foster, Matthew Turner, Jesse Shapiro, Daniel Bj\"{o}rkegren, and Bryce Steinberg for guidance and encouragement.  For helpful conversations, I am also grateful to John Friedman, Edward Glaeser, Emily Oster, Brian Knight, and Lint Barrage.  In Manila, thank you to the staff of my water company partner, government regulators at MWSS, as well as the USAID Be-Secure project for access to data and excellent conversations.  This work was supported through the Watson Institute for International and Public Affairs. } \\ [Job Market Paper: \href{https://drive.google.com/file/d/1dM41qZLZY3EPtUqHbca6MIS-nT77hv_-/view?usp=sharing}{\textcolor{blue}{Link to Current Version}}]}

\date{November, 2017}
\begin{document}

\maketitle
\begin{abstract}

%How should public utilities set fixed fees and marginal prices to provide access while covering costs?
%Why are there fixed vs. marginal?
%Public utilities recover fixed and marginal costs through a combination of fixed and marginal %prices.
%WHY CARE?! THE POOR!

	Public utilities subsidize fixed connection fees with high marginal prices to provide access especially for the poor, but this policy can have the opposite effect when many households share connections.  Using data on 1.5 million water connections in Manila, I establish that informal sharing networks provide \input{tables/shr_use_from_neighbor}\unskip\% 
	of total access.  I structurally estimate household water demand across three sources: purchasing directly from the provider, sharing with a neighbor's tap, or buying from a small-scale vendor.  The model predicts that low fixed fees and high marginal prices decrease access by weakening incentives to share water.  In contrast, the optimal pricing policy features high fixed fees and low marginal prices, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.  This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.

%	When households frequently share connections, this strategy may reduce access by weakening incentives to share.
%weaken incentives for households to extend water access to their neighbors through sharing 
%this strategy may have the opposite effect when connections are frequently shared between households.  
%	I analyze the welfare impacts of pricing for piped water in a context where households may choose to share their water connections with their neighbors.  
%	based on first-world experience

	%This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.

\end{abstract} 
{\bf JEL-Classification:} H23, L95, L98, O13, O17, O18 \\
\vspace{.1cm}
{\bf Keywords:} Water demand, non-linear pricing, informal sector, developing countries.

\section{Introduction}

Despite large investments in piped water throughout the developing world, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries for at least the past decade (World Bank [2015]).  Given health, time-savings, and other benefits from piped water, how can water utilities set prices in order to close gaps in access while still covering costs?\footnote{\cite{gamper2010impact,cutler2005role}, and \cite{galiani2005water} find health improvements in both developed and developing settings while \cite{devoto2012happiness} find time savings and other utility benefits.}  A popular approach particularly in developing cities is to subsidize upfront connection fees with high marginal prices to extend access especially for the poor.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.  Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  In a similar spirit, over 70\% of developing cities increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}). \cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.}  Recent empirical papers in South Africa and C{\^o}te d'Ivoire support this intuition, predicting gains in both access to piped water and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).

\begin{comment}

Conventional pricing policies often rely on the assumption that each water connection serves a single household; however, many households in developing cities share with neighbors instead of purchasing their own connections.  For example, 70\% of African cities report frequent water sharing (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).  While previous studies have focused on particular suburbs, this paper is the first to my knowledge to measure the role of water sharing in extending access across an urban population.

Water sharing has important implications for the welfare impacts of common pricing policies.  Increasing marginal prices weaken incentives for households to extend water access to their neighbors through sharing (\cite{whittington1992possible}).  Fixed fee subsidies may have limited impacts on water access when sharing households split connection fees with their neighbors.  Since low-income households are more likely to use water from their neighbors, increasing marginal prices and low fixed fees may combine to act as regressive taxes in the presence of sharing.

%  Shared connections record high levels of monthly consumption, which can expose them to high prices when marginal prices increase with usage . 
This paper analyzes the welfare impacts of pricing policies in the presence of informal water sharing.  Welfare impacts depend not only on heterogeneity in demand for water across the population, but also on costs associated with forming and maintaining water sharing relationships.  To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2008 to 2015 with detailed survey data on the number of households and people using each water connection.  With comprehensive geographic coverage of half of Manila and a variety of price variation, these data allow for a rich characterization of water demand.  Additional variation in water source choices identify the relative fixed and marginal costs associated with sharing water with a neighbor.  I find that despite relatively high marginal costs of sharing, shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.  At the same time, informal sharing networks act as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.

To evaluate the impacts of different pricing policies, I build a model of household water demand that includes both initial source choices as well as monthly consumption choices.  This model expands on the demand estimation literature for public utilities that focuses almost exclusively on quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).  I specify a sequential game where households choose whether to connect individually, share with their neighbors, or purchase from a water vendor.  For sharing households, I develop a simple model of the water sharing contract that captures two key features of these relationships: (1) households face challenges in observing each other's demand and (2) households often split the monthly water bill evenly.  The model characterizes monthly consumption choices when households face non-linear budget constraints and imperfect control over their exact consumption levels.  This approach extends previous models of optimization over non-linear budget constraints by allowing households to anticipate unobserved shocks to their demand (\cite{moffitt1986econometrics,burtless1978effect}).

The estimation combines water source and consumption decisions to structurally recover preferences and unobserved costs of water sharing.  To include reduced-form approaches to identification within the context of a structural model, I divide the estimation into three steps.  The first step uses variation in the non-linear price schedule (both across and within households) to identify water demand for each household using monthly consumption data.  To measure the shadow costs of fetching water from a shared connection, the second step analyzes a quasi-experiment where households face leaks in their service pipes, forcing them to substitute to a neighbor's connection.  The model maps the extent to which these households are able to offset their consumption to a neighbor's connection into an estimate of the marginal costs of fetching water.  This exercise recovers sizable sharing costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.  This quasi-experimental approach builds on a descriptive literature pointing to potential costs of sharing water (\cite{whittington1992possible,nauges2006water}).  On top of an initial connection fee and monthly service fee, households may face unobserved fixed costs in owning a connection, which may include application costs, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.  The third step estimates these fixed costs by simulating the sequential game to match cross-sectional variation in water source choices.  This strategy provides a structural, revealed-preference approach to recovering unobserved fixed costs, complementing previous reduced-form evidence in \cite{devoto2012happiness}.

Combining the model and estimates, I simulate a series of counterfactual policies.  First, I consider a connection fee subsidy policy consistent with recommendations from the World Bank, NGOs, and other researchers to improve water access for the poor (\cite{komives2005water,wsup,jimenez2014factors,mcintosh2003asian}).  I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.  This policy reduces access by incentivizing households to substitute away from sharing arrangements toward both individual connections and water vendors (which mainly include deepwells and water refilling stations).

Next, I compute an optimal tariff schedule to maximize consumer surplus while exactly covering production costs.  Compared to the current tariff, I find that a simple, two-part tariff characterized by a fixed fee and low, flat marginal price can produce gains on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.  These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections to install and maintain.  Yet, since sharing involves costly redistribution of water, the optimal tariff subsidizes individual connections on the margin by pricing above marginal cost and setting the fixed fee below the cost of installing and maintaining each connection.

Finally, I compare the optimal tariff with a social tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.  The social tariff features a much higher fixed fee and lower marginal price, does not improve access to piped water, and reallocates little consumer surplus to low-demand households at a large cost to average welfare.  By contrast, in a counterfactual world without sharing, the social tariff features a fixed fee subsidy and increasing marginal prices; it also increases access and efficiently redistributes consumer surplus to low users as compared the optimal tariff.  These results provide evidence that the presence of informal sharing networks constrains pricing policy as an effective tool for redistribution.

In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal pricing policy.  First, I do not directly model environmental, health, or other externalities associated with piped water use.  From a policy perspective, water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.  Finally, the counterfactual exercises borrow the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.  Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of public funding for water (\cite{laffont2005regulation}).

% Despite the relevance of water sharing arrangements to pricing policy, previous studies have provided either a descriptive analysis of water sharing (\cite{whittington1992possible}) or 
% in fixed fee incentivizes households to substitute away from water sharing arrangements toward individual connections as well as  , it also increases the share of households using from a local 
%among low-demand households by as much as \input{tables/discount_low_welfare_change}\unskip\% of monthly income.  
%%%% WHAT IS ACCESS DUDE!!!!!!!

The next section describes the context of water provision in Manila.  Section~\ref{section:data} describes the data.  Section~\ref{section:patternsofwateruse} presents stylized facts about water usage in Manila.  Section~\ref{section:modelofhouseholdwateruse} introduces a model of household water usage and source choices.  The estimation is divided into three steps in Section~\ref{section:specificationandestimation}.  Section~\ref{section:preferenceestimation} uses monthly quantity choices and price variation to estimate preferences.  Section~\ref{section:hasslecostestimation} analyzes a quasi-experiment to recover an estimate of the marginal costs of sharing with a neighbor.  Given these estimates, Section~\ref{section:fixedcostestimation} recovers the relative fixed costs of owning a connection or using from a vendor.  Section~\ref{section:counterfactualexercises} uses these estimates to examine counterfactual pricing policies.  Section~\ref{section:conclusion} concludes.

%%  This strategy has counterintuitive effects in a context with widespread sharing by subsidizing costs for high

%%  Served by a large, government-regulated water monopoly, Manila provides an ideal setting since over \input{tables/shr_1or2hh}\unskip\% of households share water connections.  Given many positive health exernalities from access to safe, reliable water (\cite{galiani2005water,gamper2010impact,kremer2011spring}), redesigning pricing regimes to boost access and usage especially among the poor can have significant welfare consequences.

%%  Over 70\% of developing cities have water pricing regimes characterized by high fixed connection fees and marginal prices that increase with monthly usage to cross-subsidize low-income users (\cite{hoque2013state}).  From a theoretical perspective, the optimal pricing strategy to maximize surplus especially for low-income households while covering costs of production depends on the frictions associated with sharing water.  These sharing frictions may include time costs fetching water from a neighbor as well as difficulties dividing the monthly water bill among sharing households.  If sharing frictions are large, policymakers may want to disincentivize sharing by implementing a low fixed fee and increasing the marginal price schedule.  On the other hand if sharing frictions are small, policymakers may instead use a high fixed fee and alongside a decreasing marginal price schedule in order to encourage sharing networks, set marginal prices closer to marginal costs, and minimize the number of connections that would need to be installed.  This paper provides empirical estimates of these sharing frictions in an effort to guide these pricing decisions.

%%  From a theoretical perspective, the impacts of this pricing regime depend on the frictions associated both with sharing water as well as connecting to the network.  These sharing frictions may include time costs fetching water from a neighbor as well as difficulties dividing the monthly water bill among sharing households.  If sharing frictions are high, policymakers may want to disincentivize sharing by implementing a low fixed fee and increasing marginal price schedule.  COME BACK TO THIS ISSUE: DO I WANT TO GET INTO OPTIMAL SO SOON!? NOT SURE....

%%  While low-cost sharing networks constrain the set of efficient pricing strategies available to the regulator, these networks ultimately improve welfare for low-income households by providing an additional mechanism for these households to access low-cost piped water.

%%  This paper contributes most directly to an expanding literature on estimating demand for public utilities in developing countries, including water in South Africa (\cite{szabo2015value}) and C{\^o}te d'Ivoire (\cite{diakite2009proposal}) and electricity in Colombia (\cite{mcrae2014infrastructure}).  Previous work has focused on how pricing affects monthly consumption decisions.  This paper extends these models by allowing households to also choose their initial water source.  By structurally modeling source choice, this paper also connects to a small reduced-form literature that emphasizes the importance of fixed costs associated with connecting to a piped water network (\cite{devoto2012happiness,jimenez2014factors,kayaga2007costs}).

\section{Water Provision in Manila}

In 1997, citing poor service quality and low coverage of the public water provider, the Philippines conducted the largest water privatization in the developing world.  Two private companies evenly divided the city into east and west zones as part of a public-private partnership.  Both companies invested heavily in infrastructure, which has resulted in near universal availability of piped water services for Manila.  A government regulator oversees these companies and implements rate-of-return regulation: water tariffs are revised periodically in order to ensure that providers recover all operating costs as well as earn a percentage return on any capital investments.  Rate-of-return regulation is common in developing countries since high costs of public funds as well as high risks of regulatory capture limit funding of utilities through government revenue (\cite{laffont2005regulation}).

This paper focuses on one of the providers which serves 1.5 million connections and around 5 million people.  Figure~\ref{figure:tariff} shows the regulated tariff in Manila.  The increasing marginal price is thought to cross-subsidize consumption among low-demand, poorer households through higher bills from large users.  The regulator assigns zero marginal price to the first 10 cubic meters of monthly usage, which is called the ``lifeline'' rate.  This policy is intended to provide a minimum level of consumption for all households.  This tariff may also perform efficient price discrimination if low-usage households are more price-sensitive.
\begin{figure}
\centering
\caption{Water Tariff in Manila}\label{figure:tariff}
\begin{center}
\includegraphics[scale=.7]{tables/tariff_structure.pdf}\\
\footnotesize{1 USD = 50 PhP}
\end{center}
\end{figure}
% detail more about how to get water, with the fixed fee and conne{}ction fee?!
On top of this tariff schedule, the regulator also charges a fixed fee independent of usage totaling 225 PhP/month.  This fee includes both the monthly service charge and the initial connection fee that I have put into monthly terms for the duration of the water connection.\footnote{Appendix~\ref{appendix:connectionfeeamortization} provides more details about how this monthly fee is calculated and amortized.}  The fixed fee allows the provider to recover any operating costs associated with serving the connection.  This form of increasing tariff and fixed fee combination is implemented in over 70\% of developing cities as well as over 50\% of developed cities (\cite{hoque2013state}).

Faced with this fixed fee as well as other costs associated with getting and maintaining a connection such as additional application costs or land tenure insecurity, I find that over 23\unskip\% of households use a neighbor's tap in Manila.  Sharing a connection with a neighbor mechanically increases the total monthly consumption recorded per connection, often doubling the marginal prices faced by these households compared to using a connection alone.  Although most households use piped water either through their own or neighboring connections, \input{tables/vendor_total}\unskip\% of households remain unconnected to the network and instead fetch water primarily from nearby deepwells while some use water refilling stations or other vendors.

\section{Data}\label{section:data}

%Monthly quantity choices across different households and at different prices reveal information about household demand.  Observing multiple quantities choices for the same household allows for a rich characterization of demand heterogeneity at the household-level.  
Evaluating different pricing policies requires measuring demand at the household level as well as costs associated with providing piped water.  For information about these attributes, I developed a partnership with one of the regulated, private providers in Manila who provided both billing records as well as information about the regulatory structure, pricing, and production costs.  Complete billing records for each water connection including the monthly meter reading, the total bill charged, and the precise location for each meter serve as the primary measure of quantity choices.  These data span 2008 to 2015, during which connections grew from 800,000 to 1.5 million water connections, generating nearly 100 million transaction records.  Connections are divided into residential (90\%), semi-business (4\%), commercial (5\%), and industrial (1\%).  This paper focuses on residential and semi-business connections.\footnote{Semi-business connections are largely composed of households that own small roadside stands.  These connections provide a useful source of price variation which is described in Appendix~\ref{appendix:ratechangeelasticity}.}  The monthly meter reading is used as the measure of consumption for each connection.  Meter readings are rounded to the nearest cubic meter, and I limit consideration to meter readings below 120 $\text{m}^{3}$ in order to exclude pipe leaks as well as meter reading errors (readings above 120 $\text{m}^{3}$ compose less than 0.5\% of the sample).

Since the object of interest for welfare is household-level demand, I merge the billing records to unique survey data recording information on households using each connection.  To evaluate the performance of the water provider, the regulator contracted with a local university to conduct the Public Assessment of Water Services (PAWS) in three waves from 2008 to 2012, surveying around 50,000 water connections.\footnote{Appendix~\ref{appendix:pawssampling} describes the sampling design and tests the extent to which it may be correlated with demographic characteristics.  This exercise finds relatively weak correlations in economic terms with key characteristics.}  I have collected unique identifiers for this survey, which allows responses to be linked to water connections.  The connection survey records the total number of households and people using each connection, providing the primary measure of sharing behavior.  The connection survey also includes basic demographics for the owner of the connection.  The demographics used in this paper are household size, dwelling type (whether apartment, duplex, or single house), number of employed household members, and whether the head of household is employed in a low-skill profession.
%consumption and water source choices at the household-level.  
%To examine both consumption decisions and water source choices at the household-level, I construct a dataset that merges (1) monthly water usage for around 50,000 connections, (2) demographics and water sharing measures for households using these connections, and (3) a cross-section of all households and their water source choices.  Put together, these data form a representative sample of households in half of Metro Manila.

A full analysis of water usage in Manila also requires describing households that choose to use water from local vendors.  For information on households that are using water from alternative sources, I turn to the 2010 Census of Population and Housing.  Households are defined as connected to the piped network if they report using a ``faucet community water system'' for their cooking, laundry, or bathing needs.\footnote{The census was designed largely for rural populations so it does not directly ask whether households are connected to a piped water network.}  Alternatively, I define households as using from a water vendor if they report any other category, which includes deep wells, peddlers, or other sources.  I then construct similar demographic measures to the connection survey using questions in the census and compare these measures across these data sources in Table~\ref{table:pawstocensus} of Appendix~\ref{appendix:pawstocensus}.  Households that own a connection in the connection survey are similar to households connected to the piped water network in the Census data.  To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 8 regions of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.\footnote{Regions are chosen to overlap with village administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}

For additional information on water sharing relationships between households, I fielded a small, non-representative survey of 600 households via mobile phone app.  This survey asks about issues associated with using different water sources, basic demographics, as well as how the bill and connection fee are paid for sharing households.  Appendix~\ref{appendix:pollfish} includes additional details on this survey and finds roughly similar measures between the connection survey and the mobile survey, suggesting that the mobile survey may provide a reasonable descriptive picture of sharing in Manila.

The water provider also maintains call records of all service complaints, which can be linked to individual connections.  This data is used to measure instances where households face unanticipated shocks to their water source as part of the identification strategy to estimate the hassle costs of sharing water.  Finally, the water provider tracks data on the marginal cost of pumping an additional cubic meter of water as well as the costs associated with installing new connections.  These data provide inputs into the provider's budget constraint, which are necessary for computing counterfactual pricing regimes.  Supplemental survey data from a subset of Manila include income measures that are used to impute income for the remainder of the sample across a variety of demographic variables and their interactions.

\section{Patterns of Water Use}\label{section:patternsofwateruse}

The welfare consequences of informal sharing networks depend on both the types of households that choose to share with neighbors as well as the costs of these networks.  To provide some descriptive evidence, Table~\ref{descriptives} merges the connection survey of water connections with billing records associated with each connection.  The columns group connections by the number of households they serve: one, two, or at least three.

The first rows provide demographic information from the connection survey for households who own connections.  Smaller and younger households are more likely to share water with neighbors.  Because household size is a strong proxy for water demand, this finding suggests that sharing a connection is negatively correlated with household water demand.  Households with lower imputed income more commonly share water connections.  Sharing households are over twice as likely to reside in duplexes possibly because transporting water between neighbors requires less effort for duplex residents.

\begin{table}
\centering
\captionsetup{justification=centering}
\caption{ Water Connections  by Number of Households Served}\label{descriptives}
\input{tables/new_descriptives} \\
\footnotesize{The data include billing records merged with the connection survey. \\ Income is imputed using location, demographic variables, and their interactions.}
\end{table}

Table~\ref{descriptives} also summarizes water use and sharing behavior for these connections, merging information from the connection survey with the billing records.  Larger numbers of households sharing a water connection are correlated with higher total water usage, but less water per person.\footnote{Total People Served by a connection includes both the owning household and any other households using a connection.}  This decline in usage per person may have many possible drivers: (1) sharing households face higher prices by locating at a higher point on the tariff schedule (Figure~\ref{figure:tariff}), (2) sharing households may face hassle costs in fetching water from neighboring taps, (3) these price effects may incentivize low-demand households to select into sharing relationships, consistent with the demographic patterns, and (4) low-demand households may have idiosyncratic preferences for sharing relationships.  On average, monthly water bills (inclusive of service fees) take up around \input{tables/incshr}\unskip\% of household income, which does not include other unobserved costs in accessing water.  These findings suggest that policies which affect sharing choices can have significant welfare consequences.

%Also, the mobile survey indicates that only around 30\% of sharing households would substitute to toward a neighbor's connection if they no longer had access to their primary water source.  For this reason, I treat connections reported to serve more than three households as only serving three households.  
Table~\ref{descriptives} also computes the total number of households using from each source.  I assume that households sharing with one or two other households are uniquely linked to one connection so that the population of households connected to the network can be computed by summing the number of households served by each connection.  This assumption is consistent with the presence of fixed costs in setting up a connection or a sharing relationship.  To the extent that households are drawing water from multiple connections, this assumption may lead to an overestimation of the population engaged in sharing relationships.  Under this assumption, I find that \input{tables/shr_individual}\unskip\% of connected households receive their water from an individual connection, \input{tables/shr_1hh}\unskip\% are involved in a sharing relationship with a single neighbor, and \input{tables/shr_2hh}\unskip\% are in a sharing relationship with 2 or more other households.  These proportions do not take into consideration households that are using from water vendors, which are discussed in more detail below.  Each water connection contributes over six years of billing records on average.

Since the connection survey only includes households connected to piped water, I use census data to learn about households using from water vendors.  \input{tables/vendor_total}\unskip\% of the population report using vendors, which is composed of \input{tables/vendor_well}\unskip\% of households using from a ``deep well'' and \input{tables/vendor_peddler}\unskip\% using from a ``peddler'' while the remaining fall into an ``other'' category.  Anecdotal evidence suggests that groundwater from wells often has very low quality.  Appendix Table~\ref{table:pawstocensus} compares means of demographic variables between connection owners from the connection survey and all households from the census.  Demographic variables are similar between connection owners in the connection survey and the census data.  Households using from vendors have lower imputed incomes, greater probability of low-skill employment, and slightly fewer members than own-use households.  Across most dimensions, households using from vendors more closely resemble households that share with their neighbors as opposed to households that use their connections individually.

%  While demographics are broadly similar between the first and second columns, any differences are likely driven by two factors.  First, connection owners may have different demographic characteristics than households using from a neighbor's tap.  This explanation is consistent with larger household sizes and lower rates of low skilled employment among connection owners in the first column relative to connection owners and other users captured in the second column.  Second, demographic measures may not be exactly comparable across these surveys.  Consistent with this theory, easily measured demographics like age of household head, household size, and total household members employed are very similar across the first and second columns; however, more subjective measures such as level of skill in employment and type of dwelling exhibit greater variation across data sources.  For this reason, the imputation strategy used in Section~\ref{section:fixedcostestimation} also relies on local geographic measures alongside these demographic measures.

\section{A Model of Household Water Use}\label{section:modelofhouseholdwateruse}
% Given that households derive utility from a water source through a stream of water use, 
% Taking these observed choices as inputs, this model is designed to recover both preference parameters for water as well as the shadow costs of using different water sources.

This section presents a stylized model of water source choice and monthly quantity decisions at the household level.  This model allows for an analysis of the impacts of pricing policies on both source and quantity margins, which are often equally relevant to policymakers (\cite{mcintosh2003asian,komives2005water}).  Using both margins also enables the estimation to include cross-sectional variation in sources alongside time-series variation in quantities to recover a broad set of demand and cost parameters.

Let the city of Manila be partitioned into neighborhoods, where each neighborhood is defined by a set of households that are physically close enough to share water connections with each other.  In the context of Manila, these neighborhoods are often characterized by dense clusters of houses or duplexes.  This partition embeds the assumption that neighborhoods are mutually exclusive so that a household located in one neighborhood cannot share water with households in a nearby neighborhood.  Restricting the choice set in this way may tend to overestimate the costs that households face in finding a sharing partner.\footnote{This limitation is discussed in more detail in Section~\ref{section:fixedcostestimation}}

In the first period, each household makes a one-time decision about their water source between purchasing a connection, using a neighbor's connection, or buying from a local water vendor.  These decisions result in a set of water connections for each neighborhood ranging from an empty set if all households use from a vendor to equaling the size of the neighborhood if each household uses an individual connection.  If households choose to connect to the network, each connection, $C$, serves a set of households given by $S$, which depends on which households have decided to share the water connection.  Also, let the index $C$ indicate connection-level attributes, summing over all households using connection $C$.  This model does not allow for households to choose different water sources over time, which is consistent with large fixed costs involved in initially purchasing a connection or establishing a sharing relationship.  At the same time, some households may exogenously lose access to their water source, forcing these households to substitute toward other sources as detailed in Section~\ref{section:hasslemodel}.

Conditional on their water source choice, households then choose how much water to use each month.  Since water sources provide utility through monthly consumption, this section describes the decision process in reverse order, first characterizing monthly water consumption choices (taking the initial source choice as given) and second, describing the water source choice (according to the expected utilities from using each source).

\subsection{Consumption Choices for Households Using Piped Water}\label{section:consumptionchoice}
% The goal is to take water consumption data and map it into preferences...
% Water consumption data for each connection aggregates the monthly consumption for all households as well as individuals within these households. 
% Modeling this behavior is not only useful for accurately characterizing demand, but may also play an important role in measuring the potential welfare losses from these non-linear pricing schedules.  
%(CITE JAYACHANDRAN AND JACK)

This section details how households choose their monthly quantities of consumption holding their water source fixed.  For households using piped water, this consumption choice is complicated by four features:  (1) households may have difficulty targeting their exact monthly consumption levels; (2) increasing marginal prices in the water tariff result in non-linear budget constraints; (3) households that share a connection need to determine how to divide the monthly water bill; and (4) households fetching from a neighbor may face additional hassle costs in transporting water.  Since the data record monthly consumption for each connection, this model first introduces individual household demand before aggregating household demand at the connection-level for estimation.

Households that use piped water face the difficult task of coordinating water consumption among all household members.  For example, consider a household head trying to manage water consumption across all of their household members each month.  This task would involve monitoring the meter located outside of their dwelling and observing water use among all members.\footnote{Given that many developing countries feature steeply increasing prices with monthly usage, these coordination challenges may magnify any distortions caused by non-linear pricing.}  Mobile survey data indicate that \input{tables/no_info}\unskip\% of surveyed household members do not recall how much they paid for water in the last month while \input{tables/no_use}\unskip\% do not recall the amount that their household consumed in the previous month.

As a simple way to capture this coordination task, the model assumes that each household $i$ sets a goal for water use each month, $w_i$, knowing that idiosyncratic factors, $\epsilon_i$, may increase or decrease the realized amount of usage.  Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.  Household utility over water, $W_i$ and a numeraire good, $x_i$ is assumed to take the following shape:
\begin{align}\label{equation:umaxfirst}
\begin{split}
U(x_i,W_i) &=  x_i + W_i - \frac{1}{2\alpha_i } ( W_i - \Gamma_i + \alpha_i )^2  \\
W_i &= w_i + \epsilon_i \\
\epsilon_i &\sim \mathcal{N}(0,\Sigma_{\epsilon})
\end{split}
\end{align}
Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as in Figure~\ref{figure:consumptionhistogram}.  Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are price sensitive.  These terms have clearer interpretations in the demand function below.  The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean, variance terms, $\sigma_{\epsilon}^2$, and allowing for correlation with neighboring households, ${\rho}^{\epsilon}_{i,j}$.  Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible shocks, allowing them to maximize expected utility.
\subsubsection{Determining the Budget Constraint}
The household problem is additionally complicated by the presence of non-linear price schedules for water.  Figure~\ref{figure:tariff} provides the increasing tariff in Manila.  The non-linear price schedule produces kinks in household budget constraints leading to non-linear demand functions.  Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.  The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
\begin{align*}
P(W_C)=&  
\begin{cases}
      p^{1} &\text{ if } W_C \in [\overline{W}^{0}(=0),\overline{W}^{1}], \\
      p^{2} &\text{ if } W_C \in [\overline{W}^{1},\overline{W}^{2}], \\
      ...   &\text{ ...}, \\
      p^{K} &\text{ if } W_C \in[\overline{W}^{K-1},\overline{W}^{K}(=\infty)]
    \end{cases}
\end{align*}
Given prices and household utility, the final ingredient for characterizing consumption choices is the budget constraint.  The budget constraint includes monthly household income, $Y_i$, and monthly fixed costs of using the water connection, $F_i$, which are assumed to capture three components: (1) monthly service fees, (2) initial connection fees amortized in monthly terms for the duration of the connection, and (3) unobserved, fixed hassle costs associated with setting up a connection, which are also amortized into monthly terms.  Data does not track household water source choices over time in a comprehensive way, which limits the extent to which the model can distinguish between one-time connection costs and monthly service/maintenance costs.  This limitation means that the model cannot address the optimal timing of fixed payments or capture any potential heterogeneity in monthly fixed costs.

Water sharing relationships impact monthly consumption choices through the budget constraint in three ways.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.

First, this model assumes that the monthly water bill is split evenly between all sharing households.  Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.  Among owners of the water connection responding to the mobile survey, \input{tables/bill_split}\unskip\% report splitting the water bill evenly or alternating payment each month, \input{tables/bill_fixed}\unskip\% charge sharing households a fixed amount each month regardless of their consumption, and \input{tables/bill_usage}\unskip\% charge other users a price according to their usage.\footnote{The remaining households report ``I don't know'' or ``other.''}  Evenly splitting the bill, alternating payment, or charging a fixed amount provide easy ways to extract compensation without requiring specific information on the monthly consumption of each sharing household.  Yet, these methods also introduce free-rider incentives since households do not have to fully pay for their contributions to the total water bill.  Since data limitations prevent identifying the specific type of contract associated with each shared connection, the model assumes that all households evenly split the bill and explores the theoretical and empirical implications of alternate models in Appendix~\ref{appendix:fixedprice}.  The model captures bill splitting by dividing the total monthly payment for a water connection across the $S$ sharing households.

%\footnote{Under the additional assumption that households never directly observe the $\epsilon$ shocks, splitting the bill provides an intuitive way to ensure all households account for at least some of their usage.  }
Second, sharing households may face a hassle cost, $p_h$, per unit of water, which captures any inconvenience associated with using water from a neighbor's tap.  The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.  These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.  Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households, normalized as $i>1$, face a homogeneous hassle cost, $p_h$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.}  The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.  Hassle costs for household $i$ are given by the following function:
\begin{align*}
H_{i} =& 
\begin{cases}
0     &  \text{ if } i=1 \text{ (connection owner) }\\
p_h   &  \text{ if } i \neq 1
\end{cases}
\end{align*}
Third, sharing households must negotiate over how to pay the monthly fixed fees.  The model assumes that households commit to dividing any fixed fees at the start of the sharing arrangement.  Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions.  For ease of exposition, this section assigns a fixed fee, $F_i$ to each household and postpones discussion of how the total fixed fee may be divided between households to Section~\ref{section:watersourcechoice}.

Normalizing the price of the numeraire good, $x$, to one, the budget constraint for household, $i$, using a connection with households, $S$, takes the following form:
\begin{align*}
Y_i - F_i &=  
\begin{cases}
      x_i + H_{i} W_i + \frac{1}{S} p^{1} W_C   &\text{ if }   W_C \in [0,\overline{W}^{1}], \\
      x_i +  H_{i} W_i +  \frac{1}{S} \big [p^{k} W_C -  E_{k} \big]     &\text{ if } W_C \in [\overline{W}^{k-1},\overline{W}^{k}], \\
      ...   &\text{ ... }      
\end{cases} \\
E_{k} &= \big  [\sum_{j=1}^{k-1}  (p^{k} - p^{j})(\overline{W}^{j}-\overline{W}^{j-1})  \big ]
\end{align*}

$E_{k}$ represents the discount that the household earns on all previous price thresholds below the current level of consumption.  This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.  In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.  In this scenario, the household does not face any hassle costs, $p_h$, and pays the total bill from its corresponding consumption.

\subsubsection{Maximizing Expected Utility}

When households share a water connection, the consumption choice for each household becomes a strategic decision.  Since prices are non-linear, the total consumption level for each connection, $W_C$, determines the marginal price faced by all households.  For example, with an increasing block tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.   Rewriting the utility function in equation (\ref{equation:umaxfirst}) by substituting the numeraire good, $x$, with the budget constraint, expected utility for household $i$ over the consumption shocks takes the following form:
%\begin{comment}
\scalebox{.88}{\parbox{1\linewidth}{
\begin{align*}
E[U(x_i,w_i)] = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C -  E_{k} \big] d \epsilon_C + \int_{-\infty}^{\infty} W_i - H_{i} W_i - \frac{1}{2\alpha_i} ( W_i - \Gamma_i + \alpha_i )^2 d \epsilon_i  \\  
          = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C d -  E_{k} \big] d \epsilon_C+ w_i - H_{i} w_i - \frac{1}{2\alpha_i} ( w_i - \Gamma_i + \alpha_i )^2 + \sigma_{\epsilon}^{2}  
\end{align*}
}} \\
Where $\epsilon_C$ is the convolution of consumption shocks across sharing households distributed as follows:
\begin{align*}
          \epsilon_C &\sim \mathcal{N}(0,\sigma_{\epsilon_C}^2 = \sum_{i=1}^{S} \sigma_{\epsilon}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \sigma_{\epsilon}^2 \rho^{\epsilon}_{i,j} )
\end{align*}
To solve this system, the model assumes that households follow a perfect information, pure-strategy Nash-Equilibrium in choosing consumption.  Using this structure, households compute their best response consumption functions to arrive at a symmetric equilibrium taking consumption for their sharing partners as given.  
% % % % % % % % % % % % % % % % \footnote{  APPENDIX PROVES THIS;  NEED TO GO DEEPER PLEASE!!! SHOW EXPLICITLY }  % % % % % % % % % % % % % % % % % % %
%Because of the quadratic shape of the utility function, the exogenous shock to consumption, $\epsilon_s$, only affects the optimal consumption choice to the extent that it pushes the household across price thresholds.  Therefore, the solution to equation (\ref{equation:umaxfirst}) is isomorphic to removing the $\epsilon_s$ terms from the utility function and only allowing these shocks to enter through the budget constraint.  This simplification ensures that the $\epsilon_s$ terms enter linearly into the optimization problem through the budget constraint.

Taking the derivative of expected utility with respect to $w_i$ while letting $\Phi(.)$ equal the standard normal cumulative distribution function produces the following first-order condition:
\begin{align}
\label{equation:firstordercondition}
\begin{split}
 0 =  w_i - \Gamma_i - \alpha_i H_{i} -  \frac{1}{S}  \sum_{j=1}^{K} \alpha_i  p^{j} \Big [ \Phi \Big( \frac{W_C - \overline{W}^{j}}{\sigma_{\epsilon_C}} \Big) - \Phi \Big( \frac{ W_C - \overline{W}^{j-1}}{\sigma_{\epsilon_C}} \Big)   \Big ]
\end{split}
\end{align}
The sum of the cumulative distribution functions in equation (\ref{equation:firstordercondition}) calculate the expected marginal price faced by the connection, which is scaled by the number of households sharing the connection, $S$.  This expression intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the household to higher prices.  Higher total consumption, $W_C$, raises the probability that the exogenous shock, $\epsilon_C$, places the households in a higher price range.  This first-order condition characterizes the best-response functions for each household.

The model deviates from the direct solution to this program in two ways.

First, I use an approximation for the normal cumulative distribution function taking the following form:
\begin{align*}
g(z)=& 
\begin{cases}
       0  							  & \text{ if } z    < -\sqrt{2}                       \\
     \frac{1}{2} + \frac{z}{2\sqrt2}  & \text{ if } z \geq -\sqrt{2} \text{ and } z \leq \sqrt{2}  \\
       1 						      & \text{ if } z    >  \sqrt{2}
    \end{cases}
\end{align*}
This function can be interpreted in two ways.  On one hand, this function provides a useful approximation, allowing for an analytical solution to the demand function while the empirical exercise can rely on the properties of the normal distribution.  This approach recovers rich heterogeneity in preferences through a tractable likelihood function.  Appendix~\ref{appendix:linearapprox} graphs this approximation against a standard normal c.d.f. and conducts a simulation exercise, finding negligible evidence that this approximation significantly biases the estimates or affects welfare calculations.  On the other hand, this function implies the additional economic assumption that household decision-makers approximate normally distributed shocks with a simple uniform distribution.  In this case, households are assumed to give zero likelihood to extremely high or low shocks and even likelihood to moderate shocks.

Second, I impose an ex-ante assumption on the size of consumption shocks, $\sigma_{\epsilon_C}$.  Given this linear approximation, the variance of the consumption shocks determine which prices enter the optimal demand function at each level of demand.  For example, in the limiting case where $\sigma_{\epsilon_C}$ is very large, demand becomes a function of all prices at every point because the consumption shocks are large enough to produce a positive probability of reaching every price segment regardless of where the households choose to consume.  In the opposite scenario where $\sigma_{\epsilon_C}$ is close to zero, then households can perfectly target their consumption and therefore, only need to consider the single price local to any desired consumption level.  I identify a demand function that best fits the observed consumption data by reestimating demand according to different ex-ante assumptions on $\sigma_{\epsilon_C}$.   Appendix~\ref{appendix:sigmanuassumptions} provides the results from this exercise finding that the results are robust to this ex-ante assumption.  This section proceeds by describing the demand function that is most consistent with the data.

The model also allows for idiosyncratic preference shocks for each household by decomposing the fixed preference of water demand for each household given by $\Gamma_{i}$, into a static, household-specific component, $\gamma_i$, and a normally distributed idiosyncratic component, $\eta_{i}$, which is assumed to follow a multivariate normal distribution among sharing partners:
\begin{align*}
\Gamma_{i} &= \gamma_i + \eta_{i} \\
\eta_{i} &\sim \mathcal{N} (\textbf{0},\Sigma_{\eta}) 
\end{align*}
This component helps to capture unexplained fluctuations in consumption for households over time.  This preference shock is also assumed to be independent of the consumption shocks, $\epsilon_C$.  Aggregating these preferences shocks over all sharing households using connection, $C$, produces a joint shock, $\eta_C$, according to the convolution of these random normal variables with a variance equal to $\sum_{i=1}^{S} \sigma_{\eta}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \rho^{\eta}_{i,j} \sigma_{\eta}^2$.

\subsubsection{Characterizing the Optimal Demand Function}

The best-response functions for each household can be solved and summed across all sharing households $S$ to form demand at the level of each connection, $C$.  The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs since in this case, the budget constraint is convex.  Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments.  I take this calculation into account when allowing for decreasing marginal prices in the counterfactual exercises.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):\footnote{For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.}
\begin{align}\label{equation:generaldemand}
\begin{split}
w^{*}_C &=
\begin{cases}
D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
\end{cases}\\
\text{Where: } & \\
D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{H,L} }   \\
d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \sqrt{2} \sigma_{\epsilon_C} \\
\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \sqrt{2} \sigma_{\epsilon_C} \\
\end{split}
\end{align}

In this expression, $d^{L,M,H}_C$ captures the deterministic component of demand while $D^{L,M,H}_C$ adds the stochastic component of fixed preferences.  Connection-level fixed preferences $\gamma_C$, price sensitivities $\alpha_C$, and  hassle costs $H_C$ sum across their respective values for all households using a connection.  A series of thresholds in the level of unobserved fixed preference, $\eta_C$, given by $\overline{\eta}^{j}_{l,L}$ and $\overline{\eta}^{j}_{l,U}$ work to determine which prices influence demand at each point in the schedule.  Crossing a threshold means that the consumption shock now exposes the connection to a different set of prices.  Figure~\ref{figure:intuitivedemand} graphs an example demand curve where the slope is determined by the functions $D^{L,M,H}_C$ and the changes in slope are given by the preference thresholds.

%Also, the model assumes ex-ante that the parameter $\sigma_{\epsilon_C}$ satisfies two boundary conditions that is developed in more detail below as well as in Section~\ref{section:preferenceestimation}.

\begin{figure}
\caption{Example Demand Curve}\label{figure:intuitivedemand}
\centering
\begin{tikzpicture}[      
        every node/.style={anchor=south west,inner sep=0pt},
        x=1cm, y=1cm,
      ]   
     \node (fig1) at (0,0)
       {\includegraphics[width=.66\textwidth,height=1\textheight,keepaspectratio]{tables/tariff_structure_1_no_label.pdf}};

\draw [line width=0.2mm,color=red,dashed] (2.8,1.8) -- (2.8,7.6);
\draw [line width=0.2mm,color=red,dashed] (3.8,1.8) -- (3.8,7.6);
\draw [line width=0.2mm,color=red,dashed] (4.6,1.8) -- (4.6,7.6);
\draw [line width=0.2mm,color=red,dashed] (5.5,1.8) -- (5.5,7.6);
\draw [line width=0.2mm,color=red,dashed] (8.2,1.8) -- (8.2,7.6);
\draw [line width=0.2mm,color=red,dashed] (9.1,1.8) -- (9.1,7.6);

\node[align=center] at (2.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{1}_{1,L} $}};
\node[align=center] at (3.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{2,L} $}};
\node[align=center] at (4.5,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{1,U} $}};
\node[align=center] at (5.4,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{2,U} $}};
\node[align=center] at (8.1,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{3,L}  $}};
\node[align=center] at (9,7.6)  { \text{\footnotesize  $\overline{\eta}^{4}_{3,U}  $}};

\draw [line width=0.5mm] (1.2,7.6) -- (2.8,7) -- (3.8,6) -- (4.6,4.5) -- (5.2,2); %% curve

\node[align=center] at (1.8,1)  { \text{\footnotesize  $D^{1}_C$}};
\node[align=center] at (2.8,1) { \text{\footnotesize  $D^{1,2}_C$}};
\node[align=center] at (3.8,1)  { \text{\footnotesize  $D^{1,2,3}_C $}};
\node[align=center] at (4.8,1) { \text{\footnotesize  $D^{2,3}_C $}};
\node[align=center] at (6.8,1)  { \text{\footnotesize  $D^{3}_C $}};
\node[align=center] at (8.3,1)    { \text{\footnotesize  $D^{3,4}_C $}};
\node[align=center] at (9.6,1)  { \text{\footnotesize  $D^{4}_C $}};

\node[align=center] at (2.3,2.3) { \text{$p^1$} };
\node[align=center] at (4,4.5)   { \text{$p^2$} };
\node[align=center] at (6.6,6.4) { \text{$p^3$} };
\node[align=center] at (10,7.6) { \text{$p^4$} };

\end{tikzpicture}
\end{figure}

This section now discusses the separate parts of the demand function in more detail.

\textbf{  Demand over a Single Price:  }  The first, third, and fourth price segments of the tariff schedule in Manila given in Figure~\ref{figure:intuitivedemand} exhibit large gaps of 20 $\text{m}^{3}$ between price changes.  Within these segments, the consumption shocks are not large enough to ever bounce the households across a kink point in these regions.  Therefore, households are exposed only to the current price for that segment.  Setting the low, medium, and high prices all equal to $k$ in expression $D^{L,M,H}_C$, demand arrives at the following expression:
\begin{align*}
  D_C  =& \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{S} p^k + \eta_C 
\end{align*}
This case produces a linear demand function where $\alpha_C$ can be readily interpreted as the price sensitivity parameter while $\gamma_C$ captures the portion of demand that is invariant to prices.  This demand function captures moral hazard from bill-splitting by dividing the price sensitivity, $\alpha_C$, by the total number of households using the connection, $S$.  Comparing demand among shared connections to individual connections, the extent of over-consumption at an average price of $p$ can be roughly summarized as $\frac{S-1}{S} \alpha_C p $.

\textbf{ Demand over Many Prices: }  When households choose to consume close to price thresholds points, they become exposed to price segments both above and below the thresholds.  Demand becomes a weighted average of these two price segments.  In this case, demand takes the following form, setting low and medium prices equal to $k$, and the high price equal to $k+1$:
\begin{align*}
D_C &= \frac{ 1}{ V^{k,k+1} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{k} + p^{k+1} - \overline{W}^{k+1} (\frac{p^{k+1} - p^{k}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big ) + \frac{ \eta_C }{ V_{k+1,k} } 
\end{align*}
Setting $L=M=k$ simplifies the demand expression so that only the single nearby kink point, $\overline{W}^{k+1}$, is considered.  Under increasing mprices, a decrease in the kink point, $\overline{W}^{k+1}$, lowers demand by increasing the probability that the household faces a higher price.

When the distance between price segments is relatively small compared to the size of the consumption shocks, then households are exposed to three prices when consuming on a particular segment.  Despite locating far from the neighboring kink points, households still face some probability of crossing into another price segment either above or below their current price.  This demand function applies to households locating between the second and third tariff blocks because this gap only spans 10 $\text{m}^{3}$ (as shown in Figure~\ref{figure:intuitivedemand}).  The demand function corresponds to the full expression for demand, setting indices for the low price equal to $1$, the middle price equal to $2$, and the high price equal to $3$.

\subsubsection{Deriving the Likelihood Function}

Given the optimal consumption choice, $w^{*}_C$, for each connection, observed consumption for a particular connection, $Q_C$, becomes the sum of optimal consumption and the total consumption shock for that connection, $\epsilon_C$:
\begin{align}\label{equation:observeddemand}
Q_C &= w^{*}_C + \epsilon_C
\end{align}
The probability of observing any consumption outcome, $Q_C$, can be expressed as the sum of the probability that the preference shock, $\eta_C$, locates the households within a particular price segment multiplied by the joint probability that the consumption shock, $\epsilon_C$, and the preference shock are equal to $Q_C$ conditional on being in this price segment.

These probabilities allow for the derivation the likelihood function for each consumption realization, using some additional notation.\footnote{By allowing households to anticipate exogenous shocks to their consumption, this approach builds on the standard framework of \cite{burtless1978effect} and \cite{moffitt1986econometrics} to estimate demand over non-linear budget constraints, which has been recently implemented by \cite{szabo2015value} and \cite{mcrae2014infrastructure}.}  Let demand within each segment in equation (\ref{equation:generaldemand}) simplify to $D_k = D^{l_k,m_k,h_k}_C$.  Similarly, denote the variance term for each segment as $V_k = V^{l_k,h_k}$.  Given by the conditions on $\eta_C$ defining each segment in equation (\ref{equation:generaldemand}), denote the bottom threshold for the preference shock as, $\overline{\eta}_{B,k} = \overline{\eta}^{B_p,k}_{B_{\overline{W},k},B_{\sigma}}$ and the top threshold as $\overline{\eta}_{T,k} = \overline{\eta}^{T_p,k}_{T_{\overline{W},k},T_{\sigma}}$.  Define the variance-adjusted preference shock as $\Psi = \frac{\eta_C}{V_k}$.  Let the sum of the two stochastic terms equal $\zeta = \Psi + \epsilon_C$.  For any random variable, $x$, denote the cumulative distribution function as $F_x$ and the corresponding probability distribution function as $f_x$.  Also, let $\phi$ and $\Phi$ denote the standard normal p.d.f. and c.d.f. respectively.  Given equation (\ref{equation:generaldemand}), the contribution to the likelihood function for consumption observation for each connection can be written as:
\begin{align}\label{equation:llcontributionlinear}
\sum_{k} f_{\zeta}( Q - D_k ) \Big [ F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{T,k}) - F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{B,k})  \Big ]
\end{align}
This expression takes the sum of the densities of $\zeta$ for each consumption level weighted by the probability that the preference shock $\Psi$ locates the desired consumption level for that household between the two thresholds, $\overline{\eta}_{T,k}$ and $\overline{\eta}_{B,k}$ over all thresholds.  Given that $\eta_C$ and $\epsilon_C$ are assumed to be independent and normally distributed, the terms in equation (\ref{equation:llcontributionlinear}) can be rewritten using both the convolution and conditional distributions of multivariate normals:
\begin{align*}
f_{\zeta}( Q - D_k ) &= \frac{1}{\sigma_{\zeta,k}} \phi(\frac{Q - D_k}{\sigma_{\zeta,k}} ) \\
F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{k}) &= \int_{-\infty}^{\overline{\eta}_{k}} f_{\Psi | \zeta = Q - D_k} (x) dx \\
&= \int_{-\infty}^{\overline{\eta}_{k}} \frac{1}{\sigma_{\zeta,k} \sqrt{1-\rho_k^2}}\phi \Big ( \big ( \frac{ x V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) dx \\
&= \Phi \Big ( \big ( \frac{\overline{\eta}_{k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) \\
\text{Where:} &\\
q_k &= \frac{(Q - D_k)}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta,k} = \sqrt{ \frac{\sigma_{\eta}^2}{V_k^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho_{k} = \frac{ \sigma_{\eta}}{  \sigma_{\zeta,k} V_k  } 
\end{align*}
Given these terms, equation (\ref{equation:llcontributionlinear}) can be rewritten in the following way:
\begin{align}\label{equation:LLikelihood}
\begin{split}
LL &= \sum_{k=1}^{K}  \frac{1}{\sigma_{\zeta,k}} \phi (q_{k}) \Big[ \Phi \Big ( \big ( \frac{\overline{\eta}_{T,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) -  \Phi \Big( \big ( \frac{\overline{\eta}_{B,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big)\Big] 
\end{split}
\end{align}
Summing each part of the demand function in equation (\ref{equation:generaldemand}) in the likelihood expression in equation (\ref{equation:LLikelihood}) computes the probability of observing consumption outcomes for each connection.  In order to include multiple time periods, the model captures variation in consumption over time by assuming that each household receives independent draws of preference shocks, $\eta_{i,t}$, and consumption shocks, $\epsilon_{i,t}$, which aggregate at the connection-level to $\eta_{C,t}$ and $\epsilon_{C,t}$ respectively for each month, $t$.  All other parameters are assumed to remain stable over time.  The full log-likelihood is computed by summing the log of the likelihood in equation  (\ref{equation:LLikelihood}) over all connections and time periods.

\subsubsection{Households using from Water Small-Scale Providers}

6\unskip\% of households source their water from small-scale water vendors.  These sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed fee, $F_v$, and a marginal price, $p_v$.  The monthly fixed fee, $F_v$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.  Similarly, the marginal price, $p_v$, includes both the price per unit as well as any differences in water quality or ease of use relative to piped water.  Demand for this source becomes a simple linear function of prices given by equation (\ref{equation:vendordemand}).
\begin{align}\label{equation:vendordemand}
w^{*} = \Gamma_i - \alpha_i p_v
\end{align}
Since the data do not record monthly consumption information for households using from vendors, these households do not contribute to the likelihood function above.

\subsection{Water Source Choice}\label{section:watersourcechoice}

This section describes a sequential game where households choose their water sources.  This game results in a unique equilibrium of source choices given the preferences parameters for each household as well as the costs of using each water source.  This game also allows for a mapping between the fixed costs of setting up and maintaining each water source and cross-sectional variation in source choices, which informs the third step of the estimation strategy.  The fundamental assumption of this model is that the decision to share a water connection balances splitting the fixed costs among many households against facing higher marginal costs --- hassle costs in fetching water and free-rider costs splitting the water bill.

With demand for water for each household, I am able to calculate the expected utility that each household receives from each water source, guiding their source choices.  This choice becomes a strategic decision since each household's water connection can also serve as a water source for other households in a neighborhood.  The model assumes that each set of neighboring households plays a full-information, sequential game, deciding whether to purchase their own tap, share with a previously connected household, or purchase from a vendor.  Assuming a sequential order of moves acts a refinement to rule out situations with multiple equilibria.  Eliminated equilibria mainly include cases that are both strictly dominated and unrealistic such as having all households use from vendors when they would prefer to share a connection.

Let superscripts index households by the order in which they move.  Let $a^{i}$ denote the water source choice for each household $i$.  The choices consist of (1) using from a vendor, $v$, (2) purchasing a connection, $c$, or (3) sharing with neighbor, $j$, given by $s^{j}$.  The first mover faces a simple choice set defined by $A^{1} = \{  v, c  \}$.

For all other households, define the following function that maps a household's choice to connect into a sharing opportunity for the following households:
\begin{align*}
g( a^{j} ) &=
\begin{cases}
s^j        &  \text{ if } a^{j} = c \\
\emptyset  &  \text{ else } 
\end{cases}
\end{align*}
Given this function, the choice sets for households $i>1$ consist of $A^{i} = \{ v,c,g(a^{1}),...,g(a^{i-1}) \} $ where households only have the option to share with neighbors that have previously connected.

The payoffs equal the expected utilities from each source over the duration of usage.  Since the data do not measure the exact duration for which households reside in a location using a water source, the model includes two additional assumptions: (1) households do not discount their future utilities and (2) all households demand water for an equal number of months.  These assumptions limit the extent to which this model can examine the timing of any one-time connection fees or other upfront costs of water connections.  Instead, the model collapses one-time fees into a single monthly fixed fee.  Any heterogeneity in either the duration of demand or discount factors is captured by estimates of this monthly fixed fee.  
%This section now describes the payoffs in more detail.
%% Potential limitations of this approach are discussed in more detail in the estimation section.

To compute the payoffs from using vended water, households simply compute their expected utility given by equation (\ref{equation:umaxfirst}) according to their demand in equation (\ref{equation:vendordemand}).  Let $u^{i}(v)$ capture this payoff.

The payoff from owning a connection depends on whether other households choose to use the connection as well.  Households are assumed to have perfect information about each other's preferences including distributions of preference and consumption shocks.  In order to calculate surplus from sharing, let the set $S^{i}$ contain all households that have chosen to use household $i$'s connection (including the owner).  In this model, sharing affects the utility of the owner in three ways.  First, increasing the number of sharing households splits the total water bill over more households, exacerbating any moral hazard distortions as illustrated in equation (\ref{equation:generaldemand}).  Second, under non-linear tariffs, including more consumption on the same connection may alter the marginal prices faced by all sharing households.

Third, in this model, owning households ($i=1$) are assumed to pay the full fixed cost, $F$, and sharing households commit ex-ante to providing a fixed transfer to the owner each month to compensate the owner.  This transfer allows sharing households to help contribute to the fixed costs of owning and maintaining the connection.  \input{tables/fee_even_some}\unskip\% of sharing households in the mobile survey report splitting some or all of the initial connection fee with their neighbors; for the remaining share, the owner pays the full connection fee.

To capture this behavior, the model assumes that sharing households offer transfers to the owner which equally split their surpluses from using the connection.  This setup is analogous to a Nash-Bargaining framework with equal bargaining weights.  While the division of surplus does not affect the efficiency of sharing relationships, it has normative implications for the types of households that are able to benefit from these arrangements.  Three features of the context in Manila support this assumption of a roughly equal division of surplus.  First, these sharing arrangements feature long-term relationships between close neighbors who are also often family members.  Second, neighborhoods often feature multiple sharing opportunities for each household, creating some competitive pressure on sharing arrangements.  Third, in the mobile survey, sharing households appeal to an ethic of fairness as the primary reason for dividing monthly payments instead of other reasons such as matching tariff prices or conserving environmental resources.

Expected utility from using a connection alone is defined as $u^{i} (c|1)$.  This expression can be computed by inputting demand from equation (\ref{equation:generaldemand}) with $S=1$ into utility given by equation (\ref{equation:umaxfirst}).  Expected utility from owning and sharing a connection is defined as $u^{i}(c | S^i ) $ and expected utility for household $j$ from using a connection owned by neighbor $i$ as $u^{j} ( s^{i} | S^i )$.  
%Sharing utilities can be calculated with the same method, substituting for $S$.

Sharing surplus for the owner of the connection can be represented as $ O^{i} = u^{i} ( c | S^{i} ) - max \{ u^{i} (c | 1), u^{i}(v) \} $ while surplus for each other sharing household $j$ takes the form $ G^{j} = u^{j} ( s^{i} | S^{i} ) - max \{ u^{j}(c | 1), u^{j}(v) \} $.  Let $t_{j}(S^{i})$ denote the transfer from sharing household $j$ to the owning household $i$.  Following the outcome of a Nash-Bargain with equal weights, define $  t_{j}(S^{i}) = \frac{S^{i}-1}{S^{i}} G^{j}  - \frac{1}{S^i} O^{i} - \sum_{k \in  S^{i} \setminus \{ 1,j \} } \frac{1}{S^i} G^{k}  $.  The total transfer that the owner receives from all sharing partners equals $T (S^{i}) = \sum_{j \in S^{i} \setminus \{ 1 \} } t_{j} (S^{i})$.  For example, when only two households use the connection, then $T(\{1,2\}) = t_{2}(\{1,2\}) = \frac{1}{2} (G^2 - G^{1})$, which simply divides the surplus in two.  While these transfers are usually positive since the owner is assumed to shoulder all of the fixed costs of maintaining a connection, there may be cases where the owner will offer payment to other households to use their connection: for example, if the owner has a much larger demand for water than other users, the owner may benefit substantially from splitting the bill evenly with these other households.  This case would be captured through a negative transfer.

From a welfare perspective, these transfers help to ensure that households form efficient sharing relationships.  For example, transfers allow neighbors to incentivize others to purchase a connection in cases when owners would not otherwise be willing to own and share a water connection.  Transfers also serve to reconcile a tension introduced by the sequential structure of the game where a first mover may be compelled into a sharing relationship by a second mover although the first mover would rather use the connection alone.  Transfers eliminate this possibility by calculating surplus from sharing relative to the maximum expected utility from using a vendor or using a water connection alone.

Given these transfers, the payoff for household $i$ choosing to connect takes the form $u^{i} (c|S^{i}) + T(S^{i})$.  Meanwhile, the payoff for household $j$ sharing a connection with household $i$ is $u^{j} (s^{i}|S^{i}) + t_{j}(S^{i})$.  Both the past and future decisions of all other households enter these payoffs by determining the resulting set of sharing households, $S^{i}$, which affects expected utilities directly as well as through transfers.

The last step in the specification of this game is determining the order in which households choose water sources.  The model sequences households according to their expected net utility from owning a connection alone relative to using from a vendor, $u^{i}(c|1) - u^{i}(v)$.  This arrangement matches the intuition that households with the greatest incentives to own and maintain a water connection would likely be the first to purchase a connection.  Table~\ref{descriptives} shows that for connections serving two households, the owner's household size is 8\% larger than the buyer's household size on average.  To the extent that household size serves as a proxy for demand, this finding provides suggestive evidence that larger demand households with greater utility from purchasing a water connection are also more likely to be owners.  Given that transfers allow households to efficiently share surplus, the sequence is unlikely to have large impact on the overall efficiency of the resulting arrangements.  However, moving earlier may affect the welfare of particular households.  On one hand, early movers can select to join high-value sharing relationships, crowding out these opportunities for later movers.  On the other hand, later movers have a broader choice set of already-connected households to establish a sharing relationship.

The sequential game is solved using backward induction and considering only pure-strategy equilibria.  First, the last mover, household $I$, identifies the choices that maximize its payoffs at each possible choice set reached by the game.\footnote{In rare cases where payoffs are equal, the tie-breaking rule prioritizes vendors, then individual connections, and finally shared connections ranked by the sequence of owners.}  Given these choices, the next-to-last mover, household $(I-1)$, can calculate its payoffs for each corresponding choice set.  Iterating backwards, this process characterizes a unique equilibrium set of source choices for all households.  Appendix Figure~\ref{figure:fullgametree} provides an extensive form for the game that is simulated in this paper.

\subsubsection{Exogenous Interruptions to a Water Source}\label{section:hasslemodel}

This section describes an extension of the model to allow for exogenous interruptions in a water source that induce households to substitute toward another water source.  Exogenous interruptions produce useful variation in the types of water sources used by each household, serving an important role in estimating the hassle costs of transporting water from a neighbor.  Due to shifts in the geology, road construction, or aging infrastructure, households sometimes experience underground breaks in the service pipe between the main line and the water meter.  These leaks result in repair costs and water bills borne by households that can be large enough to force affected households to switch to an alternative water source.

Descriptive evidence suggests that the decision process to choose an alternative water source in response to a leak is much different from the initial choice households face in deciding on a long-term water source.  The mobile survey asks households which source they would substitute towards if they were to be disconnected for at least three months.  \input{tables/neighbor}\unskip\% report that they would ``use a neighbor's tap'' while the remaining responses are roughly evenly split between using a public or private deep well, fetching from a water truck, or filling bottles at a water refilling shop.  Although shared connections vastly outnumber households using from vendors in the population as shown in Table~\ref{descriptives}, using a neighbor's tap is less common in response to a sudden disconnection.  Since sharing relationships often take the form of long-term contracts, households may often face high costs in reaching a temporary sharing agreement with a neighbor.  Additional descriptive findings discussed in Section~\ref{section:hasslecostestimation} suggest that the decision to share with a neighbor is uncorrelated with the features of water demand among both the household experiencing a leak as well as their neighbors.  These patterns indicate that substitution may be driven less by minimizing the long-term costs of using each source and more by convenience such as immediate access or relationships between neighbors.

From the perspective of the sequential game, households experiencing leaks are assumed to be last-movers, which implies that other households cannot update their water source choices in response to a neighbor's leak.  Additionally, the model assumes that households do not anticipate any risks of leaks in making their initial connection decisions.  Since leaks are relatively rare events as discussed in Section~\ref{section:hasslecostestimation}, this assumption is unlikely to significantly affect predicted water source choices.

Let $l$ index households experiencing a leak while $j$ indexes connections in the same neighborhood (reaching a total of $J$ connections).  This model deviates from the initial water source choice by assigning an idiosyncratic preference term, $\xi_{A,l}$, to each alternative water source $A$ --- either using from a vendor, $v$, or sharing with a neighbor, $s^{j}$.  $\xi_{A,l}$ captures the convenience of temporarily using each source following a sudden loss of water access.  For example, the first term, $\xi_{A,l}$, may capture idiosyncratic, easy access to a neighbor's private deep well or a water refilling station.  Similarly, the second term, $\xi_{A,l}$, might measure the relative social capital among potential sharing partners: nearby family members may be more willing to quickly share their connection.  The model also includes the term $F^{S}$ to capture any fixed costs associated with setting up a temporary sharing relationship relative to simply fetching from a vendor.  Given these preference shocks, total utility for household $l$ for using alternative $A$ can be parameterized with the following:
\begin{align}\label{equation:hassleutilities} 
\begin{split}
U_{l}(A) &= \omega u_{l}(A) - \mathbbm{1}\{ A \neq v \} F^{S}  + \xi_{A,l} \\
A & \in \{v,s^{1},...,s^{J}\}
\end{split}
\end{align}
$F^{S}$ captures the relative substitution to sharing relationships and to water vendors.  This model includes the additional assumption that $\xi_{A,l}$ is distributed Type I Extreme Value and is independent of preferences for water usage.  Under the distributional assumptions, the model predicts that conditional on choosing a sharing relationship, households evenly distribute between sharing partners as $\omega$ approaches zero.  When $\omega$ equals zero, the probabilities of households choosing each alternative source simplify to the following:
\begin{align*}
Pr[A=v] &= \frac{e^{-F^{S}}}{e^{-F^{S}}+e J} = G \\
Pr[A=s^{j}] &= \frac{e}{e^{-F^{S}}+eJ} = \frac{(1-G)}{J}  \\
\text{ for } j &= 1..J
\end{align*}
Let $L$ represent the total households affected by a leak.  $L$ is greater than one in cases where connections serving multiple households experience a leak.  All $L$ households are assumed to receive the same preference shock $\xi_{leak,A}$ so that they follow identical substitution patterns.  This assumption may lead to a slight underestimation of the hassle costs since these households may actually distribute across different sharing relationships, exposing them to lower points on the tariff schedule than if all households were clustered on the same connection.

These assumptions allow for the specification of a likelihood function that expresses neighbor's consumption following a leak as a function of household preferences and the hassle cost, $p_h$.  Define $LL(\gamma,\alpha,S)$ as the likelihood function in equation (\ref{equation:LLikelihood}) in terms of the preference parameters--- $\gamma$ and $\alpha$ --- as well as the number of households using the connection, $S$.  Given the probabilities above, the likelihood for consumption from connection $j$ after a nearby leak can be expressed as follows:
\begin{align}\label{equation:hasslelikelihood}
\begin{split}
LL_{j,Post l} = & \frac{J-(1-G)}{J} \overbrace{LL(\gamma_j,\alpha_j,S_j)}^{\text{$L$ do not share with $j$}} + \\
	    & \frac{(1-G)}{J}  \underbrace{LL(\gamma_j + \gamma_{L},\alpha_j+\alpha_{L},S_j+S_L)}_{\text{$L$ share with $j$}}
\end{split}
\end{align}
The first term multiplies the standard likelihood for this connection by the probability that households $L$ do not share with connection $j$.  The second term adds the probability that $L$ households choose to share with connection $j$ following the leak.  This probability is multiplied by the likelihood corresponding to joint consumption, which includes both preference terms from connection $j$ as well from $L$ households.  This approach recovers the hassle cost, $p_h$, by comparing the fixed preferences for households experiencing the leak before and after they start using from a neighbor.  Let $pre$ take a value of one for months before a leak.  Fixed preferences for $L$ households take the following form:
\begin{align*}
\gamma_{L} = &  \sum_{l=1}^{\overline{L}} ( \gamma_{l} - \alpha_{l} P_{h,l} ) \\
P_{h,l} = & 
	\begin{cases}
	0     &  \text{ if } l=1 \text{ and } pre=1 \\
	p_h   &  \text{ else }
	\end{cases}
\end{align*}
Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $p_h$ while other households $s \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.  Therefore, this method identifies hassle costs from variation in exposure for owners of the connection.  Section~\ref{section:hasslecostestimation} details potential limitations of this assumption.

\section{Specification and Estimation}\label{section:specificationandestimation}

The estimation strategy takes place in three steps.  In the first step, preference parameters --- fixed preferences $\gamma$, price sensitivities $\alpha$, as well as variances for the consumption and preference shocks, $\sigma_{\epsilon}$ and $\sigma_{\eta}$ respectively --- are recovered by combining monthly consumption patterns with price variation.  The second step analyzes a quasi-experiment where households are exogenously switched from individual connections to shared connections to estimate the hassle cost, $p_h$, associated with sharing.  In the third step, monthly fixed costs associated with an individual connection, $F$, and using a water vendor, $F_{V}$, as well as the marginal price from vendors, $p_V$, are chosen to best match cross-sectional moments in the data, including the shares of households choosing each source.

\subsection{Preference Estimation}\label{section:preferenceestimation}

Household preferences for water are estimated by maximizing the likelihood function in equation (\ref{equation:LLikelihood}) for consumption recorded at each connection and month.  This section first details how each set of parameters are parameterized in the estimation:

\textbf{Fixed Preferences} $\hat{\gamma_C} = (\gamma_C - \alpha_C H_C)$  :  Since consumption data is recorded for connections rather than for households, this approach estimates a separate $\hat{\gamma_C}$ for each connection from the mean observed usage for each connection.  $\hat{\gamma_C}$ includes not only the total fixed preference parameters for households sharing a connection $\gamma_C$, but also any hassle costs faced by shared households weighted by the price sensitivity, $\alpha_C H_C$.  Since hassle costs do not vary over time or with prices, they are indistinguishable from fixed preferences for consumption in this step of the estimation.  I later decompose these estimates into household-level preferences as detailed in Section~\ref{section:fixedcostestimation}.

\textbf{Price Sensitivity} $\alpha_C$  :  The estimation parameterizes household price-sensitivity terms $\alpha_i$ as a linear function of a vector of observable characteristics $Z_i$ that may affect price sensitivity so that $\alpha_i = \alpha Z_i$.  $Z_i$ includes dummy variables for household size, type of dwelling, whether a household member is employed in a low-skilled industry, number of employed household members, and age of the head of household as shown in Table~\ref{table:demandestimates}.\footnote{For shared connections, the data include information on household size separately for owners and sharing households; however, the other observables are recorded only for owners.  For these owner-specific measures, the estimation simply assigns the owner's characteristics to sharing households.  While this imputation may be reasonable for spatially correlated characteristics like type of dwelling, this approach may introduce bias if sharing households have systematically different levels of employed individuals or ages.  Estimates of $\alpha$ in Table~\ref{table:demandestimates} exhibit little heterogeneity across many of these dimensions, which suggests that any bias from mismeasurement may have small effects on the counterfactual exercises.}  Since household-specific price sensitivities $\alpha_i$ enter linearly into the connection-level demand function in equation (\ref{equation:generaldemand}), connection-level price sensitivity can be written simply as $\alpha_C = \alpha \sum_{i=1}^{S} Z_i$.\footnote{The model does not control for seasonality or calendar time since the raw data exhibit negligible trends in water usage over time.}

The empirical setting in Manila provides a broad range of price variation to identify these price sensitivity terms separately from the fixed preferences.  First, the non-linear pricing structure given by Figure~\ref{figure:tariff} forces households to decide whether to consume above or below tariff kink points as they face monthly shocks to their demand.  Second, regulated tariff changes over time affecting all households generate time-series variation in the tariff, which can be seen in Appendix \ref{appendix:tariffvariation}.  Third, I use rate-changes which affect individual connections differently over time described in more detail in Appendix~\ref{appendix:ratechangeelasticity}.  The structural model combines all of these sources of price variation in the estimation.  The identification assumption is that the consumption and preference shocks, $\epsilon,\eta$ are uncorrelated with these price changes.

\textbf{Preference and Consumption Shocks} $\sigma_{\eta},\rho_{\eta},\sigma_{\epsilon},\rho_{\epsilon}$  :  This strategy also estimates parameters governing the distribution of preference and consumption shocks.

%Household-level preference shocks $\eta_i$ can be aggregated to a connection-level preference shock $\eta_C$ which is composed of both the standard deviation of the $\eta_i$ terms as well as the extent to which these terms are correlated between sharing households.  
The estimation strategy recovers connection-level variance terms $\sigma_{\eta}$ for different types of connections, which are later decomposed into household variance and covariances between neighboring households below.  Heterogeneity in $\sigma_{\eta}$ is estimated with respect to connections serving one, two, or three plus households.  The estimation also allows $\sigma_{\eta}$ to vary non-parametrically according to quintiles of mean consumption at the connection-level.  Since larger users naturally have higher variance in their consumption, estimating a single $\sigma_{\eta}$ across all connections produces a large bias in the price sensitivity coefficients, $\alpha$.  This bias results from constraining large and small users to receive similarly scaled shocks and therefore enforcing that these users respond to the non-linear tariff schedule in similar ways.  While using quintiles of observed consumption may be problematic since consumption choices are themselves endogenous, this approach approximates connection-specific, $\sigma_{\eta}$ terms, which would be infeasible given limited months of data available for each connection.  The results are robust to different non-parametric specifications for $\sigma_{\eta}$.

Following a similar strategy, the estimation recovers separate standard deviation terms at the connection-level for consumption shocks $\sigma_{\epsilon}$ according to the number of households using each connection.  Since consumption shocks exhibit little heterogeneity with respect to observed consumption quintiles, I exclude these terms from the estimation to preserve parsimony.

The $\sigma_{\eta}$ and $\sigma_{\epsilon}$ parameters are separately identified from the extent of clustering around price thresholds relative to the overall variance of consumption.  Greater clustering near price thresholds implies that households face small consumption shocks, allowing them to accurately target price thresholds and lowering estimates of $\sigma_{\epsilon}$.  Similarly, wide variance in overall consumption is attributed to large consumption shocks, increasing estimates of $\sigma_{\eta}$.  Identification for these parameters as well as the preference parameters also relies heavily on the distributional assumptions of normality.

To recover the correlations of preference and consumption shocks between neighboring households given by $\rho_{\eta}, \rho_{\epsilon}$, this method compares the estimates of $\sigma_{\epsilon}$ and $\sigma_{\eta}$ according to the number of households using each connection.  This approach assumes that household-level shocks are drawn from distributions with the same standard deviations --- $\sigma_{\eta}$ and $\sigma_{\epsilon}$.  Under this assumption, any differences in estimated standard deviations for connections serving different numbers of households can be attributed to correlations in shocks between households in the same neighborhood.  Ordering households according to the sequential game in Section~\ref{section:watersourcechoice}, let the correlation terms between the first-mover and any other households in the neighborhood, $\rho_{l,1}$, be determined in terms of the following expression where the second subscripts on the $\sigma$ terms index the number of households using a connection:
\begin{align*}
\rho_{l,1} &= \frac{\sigma_{l,2}^2 - 2\sigma_{l,1}^2}{2\sigma_{l,1}^2} \text{ for } l =  \eta, \epsilon 
\end{align*}
The next expression extends this framework to identify the correlation between the second mover and all other households in a neighborhood:
\begin{align*}
\rho_{l,2} &= \frac{\sigma_{l,3}^2 - 3\sigma_{l,1}^2- 4 \rho_{l,1} \sigma_{l,1}^2 }{2\sigma_{l,1}^2 } \text{ for } l =  \eta, \epsilon
\end{align*}
Although sharing relationships and neighborhoods are limited to a maximum of three households in this paper, this approach can be used to identify correlations between an arbitrary number of sharing partners.

\textbf{Sample} : The estimation uses a 10\% sample of connections from the connection survey (5,000 connections), which serves as the primary sample for the counterfactual exercises.  This sample is combined with 5,239 connections from the leak quasi-experiment used in Section~\ref{section:hasslecostestimation}, which takes preference estimates from this step as an input.  Together these connections produce 473,114 months of consumption observations used in the preference estimation.  All standard errors throughout this paper are bootstrapped using \input{tables/boot_max}repetitions.  This sample does not include households using water from vendors since the data do not include information on consumption for these households.  Section~\ref{section:fixedcostestimation} details the imputation procedure used to infer preferences for these households.  Appendix~\ref{appendix:sigmanuassumptions} determines the ex-ante assumptions on $\sigma_{\epsilon}$ needed to identify the particular demand function.
%The estimates are robust to varying the total and relative sample sizes of these groups.

\textbf{Estimates} : Table~\ref{table:demandestimates} provides estimates for the different parameters as well as bootstrapped standard errors.  The price sensitivity parameter, $\alpha$, exhibits some statistically significant heterogeneity across demographic measures although the magnitudes of these estimates are relatively small compared to the intercept.  Moderately sized households have larger price sensitivities while employment among household members tends to lower price sensitivity estimates.  Relative to living in a duplex, households in apartments and single houses exhibit greater price sensitivities with large standard errors.  These estimates can be difficult to interpret economically since the elasticity of demand depends not only on these $\alpha$ terms, but also on variation in the fixed preferences for water across households.

Estimates of the variance of consumption shocks, $\sigma_{\epsilon}$ increase slowly as the number of households using a connection increases.  This finding provides suggestive evidence that shocks to sharing households may be negatively correlated.  The standard deviation of preference shocks, $\sigma_{\eta}$, increases dramatically with quintile of water usage.  After controlling for quintile of water usage, increasing the number of households per connection has a very small effect on the term, $\sigma_{\eta}$.

\begin{table}
\centering
\caption{Demand Estimates}\label{table:demandestimates}
\input{tables/step_1_estimates_paper} \\
\vspace{.1cm}
{\footnotesize{Total Observations:  473,114   Total Connections:  10,239} }
\end{table}
To interpret these estimates in economic terms, I compute the elasticity of demand with respect to price at the connection-level.  Given a linear demand structure, the elasticity of demand depends on both the price sensitivity and fixed preferences for water.  As a simplified example, consider the calculation for elasticity under a single marginal price and linear demand specification:
\begin{align*}
\frac{\delta Q}{\delta P} \frac{P}{Q} = \alpha_{C} \frac{P}{\gamma_{C}-\alpha_{C} P}
\end{align*}
According to this expression, increasing the fixed preference for water consumption, $\gamma_C$, while holding constant the price sensitivity, $\alpha_C$, mechanically reduces the elasticity.  Many previous studies estimate heterogeneity in $\gamma_C$ alongside a single $\alpha_C$ parameter for the population (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).  This paper builds on these previous studies by estimating heterogeneity in both terms to allow to for a broader range of possibilities, including that larger users may be relatively more sensitive to prices than smaller users.  To compare estimates in this paper with previous papers under non-linear pricing schedules, this approach follows the same formula for computing elasticities by (1) taking draws of $\epsilon$ and $\eta$, (2) computing predicted demand under prices that are 1\% greater than current prices, and (3) comparing the average percentage change in demand before and after the price change.  For tariff blocks equal to zero, prices are increased from 0 to 1 PhP following \cite{szabo2015value}.

Table~\ref{table:elasticity} presents demand elasticity estimates across terciles of (1) imputed income for the connection owner and (2) average monthly usage for the connection.  Elasticities exhibit little heterogeneity across imputed income levels, but substantial variation across usage levels with larger users appearing much less sensitive to prices than smaller users.  Since many low-income households share connections with neighbors, there is a weak correlation between income and usage-levels, which helps account for these patterns of heterogeneity.\footnote{Noise in the income imputation process may also weaken any correlation between elasticity and income.}  Heterogeneity in elasticities according to monthly usage is consistent with moral hazard when households share a connection:  increasing the number of households per connection increases the water use for those connections while also exacerbating free-riding behavior.  Different water using activities across the water demand profile may also produce this heterogeneity in elasticities.  This heterogeneity provides a potential motivation for usage-based price discrimination.  For example, matching larger, less price-sensitive users with higher prices may allow for a more efficient allocation of water while covering costs of production.

\begin{table}
\centering
\caption{Elasticity Estimates}\label{table:elasticity}
\input{tables/elasticity_estimates} \\
\vspace{.5cm}
{\footnotesize Total Observations:  473,114   Total Connections:  10,239 \\
Standard errors are bootstrapped at the connection level.}
\end{table}

The demand estimation yields an average elasticity of -\input{tables/mean_elasticity}\unskip, which can be interpreted as the percentage change in quantity due to a one percentage change in price.  This estimate also closely matches reduced-form elasticity estimates from price-change quasi-experiment detailed in Appendix~\ref{appendix:ratechangeelasticity}.  This estimate is well below the -0.98 estimate of \cite{szabo2015value} but in the range of other similar studies in developing world that find elasticities between -0.01 and -0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).

\begin{figure}
\caption{Comparing Predicted and Observed Water Use}\label{figure:predictedwateruse}
\begin{center}
\includegraphics[scale=.77]{tables/hist_both.pdf}
\end{center}
\end{figure}

Figure~\ref{figure:predictedwateruse} compares the predicted histogram of consumption with observed values.  Vertical red lines indicate the price thresholds in the tariff schedule.  By roughly matching the smoothness of the distributions especially across price thresholds, this model improves on standard models in the literature, which often predict excessive bunching at thresholds (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).  The model has difficultly rationalizing low levels of consumption likely because households face zero prices below this threshold.\footnote{Since preference and consumption shocks are assumed to be normally distributed, the model predicts a handful of negative consumption values.  In the counterfactual exercises, I round these negative realizations to zero consumption.}  Likewise, the model also cannot account for bunching at zero (likely capturing households that go on vacation).  The model also predicts greater bunching around the upper price threshold despite little observed bunching in the data as large users tend to ignore this smaller jump in price.

Table~\ref{table:correstimates} presents correlation estimates decomposed from the standard deviation terms.  Both $\epsilon$ and $\eta$ shocks demonstrate negative correlations between neighbors for both first-movers and second-movers.  This finding suggests that neighboring households may intentionally form sharing relationships with whom their shocks are negatively correlated.  This behavior may provide an insurance benefit in the presence of non-linear prices, reducing the risk that joint consumption exceeds price thresholds each month.  Alternatively, these negative consumption findings may stem from households that frequently travel ensuring that at least one user is home to take care of the connection.  For example, given the high rate of overseas workers from the Philippines, it may be common for households to match with other households with different work schedules.  
%Since I have no information on the overseas work status of individuals, I am not able to test this hypothesis empirically.

\begin{table}
\centering
\caption{Correlation Estimates}\label{table:correstimates}
\input{tables/corr_table_group}\\
\vspace{.3cm}
\footnotesize{1 indexes correlations with first movers \\ while 2 indexes correlations with second movers}
\end{table}

\subsection{Hassle Cost Estimation}\label{section:hasslecostestimation}

This section details how exogenous interruptions in water connections caused by leaks combine with billing records to provide a measure of hassle costs of sharing water.  The estimation strategy compares a connection's demand before disconnection to the change in demand among neighboring connections after disconnection (as a result of sharing), attributing the extent to which neighbors may not fully offset their consumption to the hassle cost, $p_h$.  Baseline preference parameters for both disconnecting connections and their neighbors are estimated in the procedure from Section~\ref{section:preferenceestimation}.  Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $p_h$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).

I now describe how the estimation sample is constructed.  In 36 months, the water provider received 106,171 complaints of excessive billing --- 34,927 of which can be precisely identified as underground pipe leaks along the service pipe through a text analysis of call transcripts.  These complaints do not appear to be spatially correlated with only a handful of leaks occurring among neighbors in the 36 months.  I consider any call identified as an excessive billing complaint as a leak.  While some calls may not explicitly refer to leaks, in all cases these calls refer to billing errors, meter malfunctions, or other surprise events that may drive disconnection.  Instances where leaks in main water pipes reduce access for entire neighborhoods at a time are coded separately and excluded from the sample.  Leaks are limited to cases with at least 3 observations before the leak in order to calculate baseline water demand for these connections.  Disconnection is defined as having 0 or missing consumption values for at least 90\% of the year following the leak date.  Neighboring connections that connect after the leak has taken place are dropped, since these connections lack a pre-period to estimate their fixed preference for water.  The estimation includes observations within a year and a half of the leak event to avoid bias from possible reconnection of these households as well as changes in the composition of neighboring households.  Since many of these households are not included in the connection survey, demographic characteristics as well as sharing behavior are imputed using averages from small areas surrounding these connections; this process introduces additional noise into the estimation.

To determine which neighbors to include, Appendix~\ref{appendix:sharingneighbor} ranks nearby households according to their distance from the leak and examine how the responsiveness of neighbors' consumption levels after a leak dissipates with distance.  Results indicate substitution is concentrated among the nearest four neighbors.  Given these findings, the empirical exercise defines neighbors as the four closest connections.

%\footnote{Neighbors ranked 6 through 8 are grouped together since there are very few of them in the radius.}

Given the set of leaking households, $J=4$, as well as their preferences, the final input to the likelihood function in equation (\ref{equation:hasslelikelihood}) is the probability that leaking households choose to use from vendors.  This probability is calibrated directly from the hypothetical question in the mobile survey, which finds that 70\% of households would use a vendor in response to a sudden disconnection for over three months.  Directly including this parameter in the estimation requires the assumption that this hypothetical response provides an accurate measure of true behavior.

This analysis requires the assumption that the hassle cost, $p_h$, is homogenous across all households.  This assumption ensures that the hassle cost identified from the subset of leaking households can be extended to the population of households.  One concern may be that heterogenous hassle costs induce households to select into sharing relationships conditional on these costs.  Since households included in this quasi-experiment have selected into purchasing connections at baseline, they may face higher hassle costs compared to households that select into sharing.  Therefore, this exercise provides an upper-bound on hassle costs for the population.  The mobile survey finds a range of sharing access from fetching with containers to using the same plumbing, which suggests that households face different hassle costs.
The following additional assumptions are required to ensure that this empirical setting accurately captures the model described in Section~\ref{section:hasslemodel}.  These assumptions are discussed in more detail and tested empirically in Appendix~\ref{appendix:sharingcostassumptions}.
\begin{enumerate}
	\item \textit{ Connections that experience a leak are representative of the population of connections. } 
	\item \textit{ The decision to disconnect conditional on experiencing a leak is uncorrelated with water demand. } 
	\item \textit{ The timing of a leak is uncorrelated with any underlying changes in demand. } 
	\item \textit{  The leaking household's choice of a sharing partner is uncorrelated with that partner's water demand.  }	
	\item \textit{ Leaks are uncorrelated with changes in neighborhood demand. }
	\item \textit{  A leak for one household is uncorrelated with probability of a neighboring household experiencing a leak. }
\end{enumerate}

%%% ELABORATE ON ALL THE CAPTIONS TO MAKE THE FIGURES RELATIVELY SELF-CONTAINED!

Table~\ref{table:step2estimates} shows the estimation results for the hassle cost estimation.  The hassle cost is estimated to be \input{tables/mean_hassle}PhP per cubic meter of usage, which is approximately \input{tables/hassle_percentage}\unskip\% of the average tariff.  With only 1,247 connections that experience leaks, the estimation recovers wide standard errors for this estimate, rejecting a hassle cost of zero with 10\% confidence.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  These results suggest that the time-costs or other physical challenges transporting water to share with a neighbor may play an important role in the extent to which households choose to use water from a neighbor's tap.

%One possibility may be that estimating a single average hassle cost for the population of connections masks significant heterogeneity across household density and dwelling type among other factors.\footnote{Future versions will estimate this heterogeneity directly.}

\begin{table}
\centering
\caption{Hassle Cost Estimates}\label{table:step2estimates}
\input{tables/step_2_estimates} 
\vspace{.2cm} 
\footnotesize{Leaking Connections:  1,247,   Neighboring Connections:  5,239,  Total Obs:  36,662  \\ Standard errors are bootstrapped at the leaking connection-neighborhood level.  \\
Appendix~\ref{appendix:hasslecostbootstrap} includes more details on the bootstrapping procedure.}
\end{table}

\subsection{Fixed Cost Estimation}\label{section:fixedcostestimation}

This section details how unobserved fixed costs of owning a connection are recovered from cross-sectional variation in water source choices.  The third step of the estimation uses the preference parameters recovered in Section~\ref{section:preferenceestimation} and hassle cost estimates from Section~\ref{section:hasslecostestimation} to simulate the initial water source choices for households.  By matching observed with predicted source choices, the estimation recovers the fixed costs of using a connection as well as prices associated with fetching from a vendor.  The fixed costs capture both one-time costs put into monthly terms --- connection fees, permitting with local governments, etc. --- as well as monthly costs --- service fees, plumbing maintenance, etc.

The fixed cost estimation sample includes the random sample of 5,000 connections from the preference estimation.\footnote{This sample excludes connections used to estimate hassle costs since the majority of these connections use imputed demographics.}  I merge the estimation sample with the subsample of households using water from small-scale vendors drawn from the Census of Population and Housing 2010 as described in Section~\ref{section:data}.  Neighborhoods of potential sharing partners are limited to groups of three households, which is consistent with the vast majority of households forming sharing relationships of three households or less.  Within a three person neighborhood, households can share with a maximum of two other households. Assuming a limited neighborhood size and restricting households to only share within their neighborhoods both work to reduce sharing opportunities for households.  Since high fixed costs for new connections incentivize sharing, this approach may underestimate the true fixed costs faced by households.

\subsubsection{Disaggregating Connection-Level Preferences to Household-Level Preferences}

In order to simulate these choices, I first need to recover household-level preferences from the connection-level preferences estimated in Section~\ref{section:preferenceestimation}.  Household price sensitivity, $\alpha_i$, can be inferred as a linear function of the vector of demographics specific to each household, $Z_i$, and estimates of $\alpha_C$.  Since fixed preferences $\hat{\gamma_C}$ are estimated non-parametrically at the connection-level, I specify a parametric method of splitting $\hat{\gamma_C}$ into $\gamma_i$ for all households using demographics, $Z_i$:
\begin{align*}
\hat{\gamma_C}  		   		& =  \sum_{i=1}^{S} ( \gamma_i - \alpha_i H_{i} ) \\
\big [ \hat{\gamma_C} - \sum_{i=1}^{S}  \alpha_i H_{i} \big ]		& =  \sum_{i=1}^{S}  (\lambda_{S} Z_i + \mu_{i})  
\end{align*}
$Z_i$ captures demographic characteristics specific to each household.  $\lambda_{S}$ are coefficients measuring the effect of these demographics on fixed preferences $\gamma_C$.  These coefficients are allowed to differ across connections serving different numbers of households, $S$ as well as whether household $i$ is an owner of the connection.  $\mu_{i}$ captures any residual variation that is unexplained by demographics.  In this case, $Z_i$ consists of household size since it is the only demographic measure reported separately for connection owners and other users.  I estimate a simple regression to recover estimates of $\lambda_{S}$, which provides predicted levels of $\gamma_i$ for each household.  Finally, this method needs to allocate any residual variation in preferences $\mu_{i}$ across the households.  Instead of either allocating $\mu_i$ entirely to the connection owner or splitting $\mu_{i}$ evenly across households, I allocate $M \mu_{i}$ to the owner and $\frac{(1-M)}{S-1} \mu_{i}$ to neighboring users where $M$ is the ratio of average connection-level preferences for single users, $\gamma_{S=1}$ to average connection-level preferences for shared connections $\gamma_{S>1}$.  This approach nests the assumption that connection owners are more likely than their sharing partners to resemble the water demand of single-users.  Another limitation is that the data only provide the total number of people using a connection for shared connections.  Therefore, in cases where three households use a connection, I assume that sharing people are allocated evenly between the two sharing households.
%%% , which is consistent with the discussion in Section~\ref{section:watersourcechoice}

\subsubsection{Imputing Preferences for Households using from Water Vendors}

Given the full set of household-level demand parameters for connected households, I then impute preferences for households using from vendors.  $\alpha_i$ can be computed simply from demographic measures, $Z_i$, for these households.  Since $\gamma_i$ is estimated non-parametrically for connected households, I use a regression with location, demographic variables, and their full set of interactions to impute preferences for households using from vendors:
\begin{align*}
\gamma_i = \beta_0 Z_i + \beta_1 L_i + \beta_2 Z_i L_i + \zeta_i
\end{align*}
$Z_i$ contains demographics while $L_i$ includes dummy variables for small census areas.  After recovering coefficients for the sample of connected households, I then compute predicted $\gamma_i$ for households using water from vendors.  This method requires the assumption that unobserved variation in preferences $\zeta_i$ is uncorrelated between connected households and households using from vendors.  This assumption may not hold if unobservable aspects of preferences drive some households to use from vendors.  Since vendors offer high marginal prices, this form of selection would likely lead the method to overestimate demand among households using from vendors.

Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from 5,000 connections to 6,984 households.

\subsubsection{Simulation and Estimation}

With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors with each of the 8 geographic regions.  The routine then orders households in the sequential game according to their utilities from using an individual connection.  This assumption captures the intuition that households who would have connected in the absence of any sharing are likely to be the first to take-up a new connection.  Random draws of the preference shocks, $\eta$ and $\epsilon$, are assigned to each household so that households can compute expected utilities over \input{tables/sim_time_periods}months for all possible water source choices.  These shocks are sampled from a multivariate normal distribution taking into account the estimated correlation between sharing partners from Table~\ref{table:correstimates}.  
%\footnote{ Future versions will not condition on observed choices in this way, and instead sample households across sharing relationships. }

Households calculate payoffs following Section~\ref{section:watersourcechoice} given all potential choice sets.  Appendix~\ref{appendix:gametreefull} maps the full game tree with three players that is simulated in the estimation.  This sequential game is repeated \input{tables/sim_repetitions}times to construct a set of draws to compute simulated moments.  The moments used in the estimation include the shares of households choosing different sources --- using an individual connection, using water from a neighbor, and using from a vendor --- as well as the covariance between each of these source choices and the fixed preference parameters for each household, $\gamma_i$.\footnote{I ensure that the estimation places heavier weight on matching the source-choice moments over the correlation moments because these correlations rely on possibly noisy measures of the preference parameters both due to incidental parameter issues in estimation as well as imputation for households using vended water. }  % Future versions will re-weight these moments given the boot-strapped variance-covariance matrix.

\begin{table}
\centering
\caption{Simulated Method of Moments Estimates}\label{table:smmestimates}
\input{tables/step_3_estimates_group}\\
\vspace{.05cm}
\footnotesize{ Standard errors are bootstrapped at the connection level.  Total Households:  6,984  }
\end{table}

Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee}PhP monthly fixed fee paid the provider.  This finding suggests that households face sizable barriers to connecting to the water network such as maintenance land tenure insecurity, or administrative costs.  This total fixed fee is also comparable to the total variable price paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.

The estimates also reveal a fixed cost for vendors equivalent to \input{tables/vendorfixedfee_group}PhP per month.  This likely captures fixed quality differences between vended water and other water sources.  The mean price for vended water of \input{tables/vendorprice_group}PhP per cubic meter is close to the highest tariff price in Figure~\ref{figure:tariff}.  These estimates include a sizable variance term for the vendor price, which is consistent with the large variety of small-scale water sources that are collapsed into this measure, including primarily deep wells as well as tanker trucks and water refilling stations.  These sources may also be unevenly distributed throughout the city.

Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option, particularly the marginal price, $p_v$.  As a simple out-of-sample test, I compare this estimate of $p_v$ to the implied $p_v$ from data on total water expenditures for vendor households using additional census data from a section of Manila.\footnote{The 2011 Community Based Monitoring System data covers over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown Manila --- and includes information on income (used to compute imputed income) as well as water source and monthly expenditures.}  In this data, households using from vendors report expenditures of 365 PhP/month while households using individual connections report expenditures of 470 PhP/month and households sharing connections report expenditures of 370 PhP/month.  Assuming that the vendor expenditures only reflect the marginal prices paid for water (excluding the fixed cost), I can express average expenditures, $E_v$, by multiplying average vendor demand by the vendor price, $E_v = (\gamma - \alpha p_v) p_v$.  Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=33$, and price sensitivity, $\alpha=.62$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 15.7 PhP/$\text{m}^{3}$ or 37.53 PhP/$\text{m}^{3}$.  The latter price matches closely to the estimated price of 37.16 PhP/$\text{m}^3$, providing additional support to the structural estimates.

\subsection{Out-of-Sample Test}\label{section:oostest}

To evaluate how well the model is able to match observed substitution patterns between water sources, I investigate reduced-form evidence from a connection-fee discount program since this variation is not used explicitly in any part of the estimation.  The fundamental assumption of the model is that the decision to share a water connection balances splitting the fixed fee among many households against facing marginal hassle costs in fetching water as well as free-rider costs in splitting the water bill.  Under this assumption, reducing the fixed fee would lead to substitution away from shared connections toward individual connections.  This section uses quasi-experimental variation in the connection-fee to test this assumption.

In 2009, the government regulator issued new regulations reducing the connection fee from 6,000 to 2,400 PhP for low-income areas partially in an effort to extend access and affordability to low-income households.  Under the assumption that households reside in Manila for 80 months and face negligible credit constraints, this discount lowered the monthly fixed fee faced by households by 45 PhP on average.  In the presence of credit constraints, this estimate can be interpreted as a lower bound on the policy's impact on the monthly fixed price faced by households.  Figure~\ref{figure:discountfirststage} indicates the share of new connections receiving discounted fees.  The sudden rise by \input{tables/first_stage}percentage points coincides with the change in regulations and will be used to identify the timing of the discount policy.  A small fraction of households are observed to receive connection fee discounts prior to the program as part of other, smaller pro-poor strategies implemented by the water provider.

\begin{figure}
\centering
\caption{Share of New Connections Receiving a Discount}\label{figure:discountfirststage}
\includegraphics[scale=.7]{tables/diff_595_first_stage.pdf}
\end{figure}

Since the data do not identify precisely which local areas or specific households were eligible for the discount, additional assumptions are necessary to measure eligibility.  First, I define treated areas as any meter reading unit that receives at least one discounted connection over the full duration while control areas include any meter reading units that never receive discounts.  Meter reading units (MRUs) are common geographical designations used by the water provider and include between 100 and 500 meters.  There are 3,757 MRUs in the service area.  I include only MRUs that were established long prior to the discount fee program to ensure that these areas are likely to be at saturation in terms of water connections prior to the program.  Second, to identify the share of households in treated areas that were eligible, I conceptually divide new connections into two groups --- (1) households substituting away from shared connections or water vendors in response to the program and (2) new households migrating to the city.  I then measure eligibility as the share of new migrants receiving discounted connections fees after the policy.

This approach requires the following assumptions:
\begin{enumerate}
	\item Before the discount program, households that have already moved to the city have reached an equilibrium at the current prices; therefore, all new full-price connections in the pre-period are driven by migration to the city.  This assumption is consistent with the large fixed costs incurred in setting up a new connection.
	\item The rate of migration is unaffected by the policy, which is supported by the stable rate of new connections for untreated areas in Figure~\ref{figure:discountreducedform} below.  
	\item After the discount policy is implemented, all new migrant households that are eligible take up the discounted connections.
	\item Rates of eligibility are similar across migrant and non-migrant groups.
\end{enumerate}
Under these assumptions, I compute the impact of the policy on new full-price connections in the treated areas and interpret any reduction in the rate of new full-price connections as driven by new migrants receiving discounted connections.  I estimate the following simple difference-in-differences equation across all treated and untreated Meter Reading Units, $m$, and months, $t$, pre and post policy implementation:
\begin{align*}
\text{New Full-Price Connections}_{t,m} &= \beta_1 \text{Post X Treated}_{t,m} + \beta_2 \text{Post}_{t,m} + \beta_3 \text{Treated}_{t,m} + \epsilon_{t,m}
\end{align*}
Table~\ref{table:difffullpriced} presents the results from this estimation.\footnote{These results do not exactly match reduced-form results from Table~\ref{table:diffdiscountreducedform} because the data only have information on the price per connection for about 80\% of new connections.}  Adding the coefficients in Table~\ref{table:difffullpriced} shows that in the absence of the policy, treated areas were expected to have added 0\input{tables/would_have_added}new full-price connections each month; yet, as a result of the policy, these areas actually experienced 0\input{tables/actually_added}new full-price connections with the remaining households receiving discounted connections.  This discrepancy implies that \input{tables/substitution}\unskip\% of households were eligible for the program.

\begin{table}
\centering
\caption{Difference-in-Differences Estimate for Full Priced Connections}\label{table:difffullpriced}
\input{tables/diff_595_reg_secondary}
\end{table}

I next examine the reduced-form impacts of the policy using the following event-study regression equation, which computes the average number of new connections in bi-monthly intervals relative to the discount fee program for both treated and untreated areas:
\begin{align*}
\text{New Connections}_{t,m} &= \sum_{r=0}^{T} \beta^{\text{Treated}}_{r} \mathbbm{1} \{t=r\} + \sum_{r=0}^{T} \beta^{\text{Untreated}}_{r} \mathbbm{1} \{t=r\}  +  \theta_{m} + \epsilon_{t,m} \\
t &= \text{2 Month Intervals}\\
m &= \text{Meter Reading Unit}
\end{align*}
Figure~\ref{figure:discountreducedform} provides the graphical estimates from this equation.  The untreated group on the left-hand side exhibits a very stable trend in new connections with no changes relative to the discount program.  This finding is consistent with steady population growth generating a constant rise in the total number of connections.

The treated group on the right-hand side shows a relatively stable pre-trend interrupted by a substantial increase in the number of connections just following the discount program implementation.  This increase lasts for a couple years before returning to pre-program levels.  These trends provide evidence that households who are sharing water or purchasing from vendors are gradually learning about the price change and choosing to purchase their own connections.  After a couple years, this additional demand for connections has been satisfied, letting migration take over as the sole driver of new connections.
\begin{figure}
\centering
\caption{Reduced Form: Connection Fee Discount}\label{figure:discountreducedform}
\includegraphics[scale=.57]{tables/diff_595_untreated.pdf}
\includegraphics[scale=.57]{tables/diff_595_treated.pdf}
\end{figure}

\begin{table}
\centering
\caption{Difference-in-Differences Estimate}\label{table:diffdiscountreducedform}
\input{tables/diff_595_reg_primary}
\end{table}

A simple difference-in-differences estimate provided by Table~\ref{table:diffdiscountreducedform} calculates an increase of 0\input{tables/red_form_est}new connections per month for the treated areas on a base average of 0\input{tables/red_form_base}new connections per month.  Aggregated over the full \input{tables/treated_months}months of the program, this program led to a total of \input{tables/total_effect}new connections per Meter Reading Unit.  Given that the average Meter Reading Unit has \input{tables/mru_size}connections over the full time period, this program generated about a \input{tables/percent_increase_discount}\unskip\% increase in the number of new connections.

To compare results from this policy to counterfactual estimates from the model, I now convert the change in number of connections induced by the policy to a shift from shared and vendor connections to individual connections.  Given that \input{tables/share_2_hhs}\unskip\% of connections serve two households and \input{tables/share_3_hhs}\unskip\% of connections serve three or more households, and 5\% of households access water from vendors, then \input{tables/mru_size}connections per Meter Reading Unit are calculated to serve an average population of around \input{tables/population_served}households.  This policy results in a \input{tables/increase_in_individual_connections}percentage point increase in the share of households owning a connection, which can be directly compared to predictions from the counterfactual exercise.

In order to relate the quasi-experimental results from the policy to the model outputs, I simulate the impacts of the connection-fee discount policy by (1) randomly selecting \input{tables/substitution}\unskip\% of households, (2) lowering the fixed fee by 45 PhP for these households, and (3) recomputing their water source choices.  As a result of this policy, the share of households owning a water connection is calculated to rise by \input{tables/out_of_sample_inc_ind_conn_group}percentage points.  This finding is smaller, but comparable to the reduced form results indicating a \input{tables/increase_in_individual_connections}percentage point increase.  There may be many reasons that the counterfactual results lag behind the reduced-form estimates.  First, the assumptions used to amortize the connection fee discount into monthly terms  may work to understate the impact of the discount, especially in cases where households face credit-constraints in funding large, lump-sum connection fees.  Second, in practice, the discount policy targeted a low-income segment of the population, which may have different substitution patterns across water sources.

Despite these caveats, the fact that the reduced-form and model-based estimates are similar in magnitude lends support to the counterfactual exercises in Section~\ref{section:counterfactualexercises}.  Table~\ref{table:oosestimates} calculates the impacts of this connection fee discount on water source choices as well as consumer welfare.  Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended water.  Since utility is assumed to be quasi-linear, consumer welfare is reported in PhP/month.  Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile}\unskip\% of users.

\begin{table}
\centering
\caption{Connection Fee Discount: Out-of-Sample Test Results}\label{table:oosestimates}
\input{tables/oos_discount_estimates_group} \\ 
Consumer surplus is measured in PhP/month.
\end{table}

\section{Counterfactual Exercises}\label{section:counterfactualexercises}

This section reconstructs the economic problem faced by the regulator in order to investigate how alternative pricing policies might impact welfare.  I consider the government regulator's maximization problem given by equation (\ref{equation:regulator}) where the regulator chooses a fixed fee, $Fee$ and a price schedule, $P$, to maximize consumer surplus while covering the costs of production (holding profits equal to zero).  Consumer welfare is defined as the expected sum of all households' utilities subject to welfare weights, $\delta_i$, for different subpopulations, which capture any preferences the regulator may have towards redistribution.  The counterfactual exercises consider two sets of these preferences: (1) the regulator weights all utilities equally and (2) the regulator only considers utility for the bottom 50th percentile of water demand, summarized by the fixed water preferences $\gamma$ for each household.  Giving preference to low-demand households intends to capture dual policy goals of ensuring access as well as minimum monthly usage for all households.  Since low-demand households are also often low-income households, this preference also provides a proxy for standard preferences toward redistribution.\footnote{Using income directly is less informative due to noise in the imputation process, especially for households that are sharing with their neighbors.}  Similarly, this approach may capture efficiency gains if connecting low-users produces positive health externalities (\cite{galiani2005water,gamper2010impact}).  For ease of exposition, the utility function below nests the water source choices of each household.
\begin{align}
\begin{split}
max_{Fee,p_{L},p_{H}} &\hspace{.4cm} E\text{\LARGE [} \sum_{i=1}^{N} \delta_i U_{i}(Fee,p_{L},p_{H}) \text{\LARGE ]} \\
s.t. \hspace{.5cm} & \text{Total Connections} \times \big[ Fee - \text{Installation/Service Costs} \big] + \\
              & \text{Total Water} \times \big[ \text{Revenue per Unit}(p_{L},p_{H})  - \text{Marginal Cost}  \big] \\
      & \hspace{5.5cm} \geq \text{Capital Costs}
\end{split}
\label{equation:regulator}
\end{align}
The budget constraint ensures that the fixed monthly fee, $Fee$, paid to the company for each connection as well as the revenue earned for each unit of water consumption (given the non-linear pricing scheme) outweighs the costs of servicing each connection, the marginal costs of providing a cubic meter of water, as well as any capital costs associated with the pipe-network, pumping stations, and dam maintenance.  The water provider calculates that their marginal costs are equal to 5 PhP per $\text{m}^{3}$ and that the fixed fee exactly covers any installation/service costs.  To determine the capital costs, I subtract the total marginal and services costs from the total revenue earned by the company, assigning the remainder to capital costs.  Capital costs include maintaining the pipes, pumping stations, and billing infrastructure.  This calculation provides a close approximation to the Capital Expenditures regulatory structure implemented in this context, which exactly compensates the water provider for its costs through increases in the tariff.\footnote{This paper abstracts away from any principal agent problems between the company and the regulator by assuming that the regulator has perfect information over the firm's capital investments and operating costs (\cite{laffont1993theory}).}  This regulatory problem forms the basis for evaluating the following counterfactual policies.  All counterfactual policies evaluated below hold firm profits equal to zero.

\subsection{Compensated Fixed Fee Discount}

I first examine a counterfactual policy where the regulator discounts the upfront fee while increasing the tariff to remain revenue neutral.  By discounting the fixed fee by \input{tables/c_fee_discount_group}PhP, this policy mimics the policy implemented by the water provider; however, while the provider's discount decreased overall revenue, this policy imposes the necessary tariff increase to fund the lower fixed fee.  This counterfactual also echoes recent recommendations from policymakers and researchers including the World Bank who have strongly advocated for lower connection fees as a way of extending access to piped water among the poor (\cite{wsup,komives2005water,jimenez2014factors,kayaga2007costs,mcintosh2003asian}).  Figure~\ref{figure:discounttariff} indicates the current tariff and the compensated tariff, which is shifted upwards by \input{tables/discount_tariff_rise_group}PhP/$\text{m}^{3}$ to maintain revenue neutrality.

\begin{figure}
\centering
\caption{Tariff Shift from Connection Fee Discount}\label{figure:discounttariff}
\includegraphics[scale=.7]{tables/discount_tariff_groups.pdf}
\end{figure}

Table~\ref{table:fixedfeediscount} summarizes the impacts of this change on source choices and consumer welfare measured in terms of the difference between current utility and utility from using the outside vendor option as in Section~\ref{section:oostest}.  The decrease in the fixed fee and increase in the tariff both act to decrease the incentives for sharing a connection and leading to a drop of \input{tables/discount_sharing_change_group}percentage points in households using water from their neighbors.  The third row indicates even greater substitution toward water vendors of around \input{tables/discount_vendor_change_group}percentage points in response to the higher tariff.  These effects combine to reduce average consumer surplus by \input{tables/discount_avg_surplus_change_group}PhP per month, which is over half of the initial fixed fee discount of \input{tables/c_fee_discount_group}PhP.  This decline translates into a \input{tables/discount_avg_welfare_change_group}percent loss of monthly household income.  Households in the bottom \input{tables/group_percentile_group}\unskip th percentile of water users also experience lower consumer surplus although the magnitude is much less, amounting to \input{tables/discount_low_welfare_change_group}percent of monthly household income.  Taken together, these results suggest that connection fee discount policies in this context can have unintended distributional consequences by reducing both access to piped water and welfare for the intended beneficiaries. %\footnote{Consumer surplus is measured relative to utility from using vended water.}  
\begin{table}
	\centering
	\caption{Fixed Fee Discount Counterfactual}\label{table:fixedfeediscount}
	\input{tables/discount_estimates_group} \\
	\footnotesize{Low Users include the bottom 50\% of water users. \\
	Surplus is measured in terms of PhPd/month.}
\end{table}

\subsection{Characterizing Optimal Tariff Schedules}

This section considers the welfare impacts of six tariff structures in order to inform water regulators who face a variety of institutional settings and redistributional priorities: while some regulators may be restricted to simple two-part tariffs, others can allow for complex, non-linear price schedules as in Manila (\cite{hoque2013state}).  Similarly, while encouraging efficient use, many developing countries also include distributional motivations for their tariff structures such as ensuring all households reach a certain minimum level of usage (\cite{szabo2015value}).

As a benchmark, this exercise first examines a First-Best tariff informed by the industrial organization literature where (1) the marginal price per unit of water equals the marginal cost of production, (2) every household pays a fixed fee just equal to costs of installing and maintaining a connection, and (3) the regulator is able to perfectly price discriminate according to household demand, extracting additional transfers from households to exactly fund the fixed capital costs (\cite{auerbach1978two,oi1971disneyland}).  Without sharing, this tariff follows economic theory to maximize efficiency.  I then compare how the current tariff in Manila performs relative to this First-Best tariff structure.
%Additionally in this case, I assume that the regulator can use these costless transfers to reallocate surplus from high users to low users in order to achieve distributional goals as well.

The next tariff imposes restrictions on the regulator by only allowing for a simple two-part tariff with a monthly fixed component and a single variable component.  First, I look for the two-part tariff that maximizes overall consumer surplus.  Second, I define a social two-part tariff, which maximizes surplus for low users and provides a means of summarizing regulator preferences toward redistribution or ensuring basic levels of access.  Low users are classified as households with fixed preferences for water usage, $\gamma$, below the average level.  Since households exhibit little heterogeneity in their price sensitivities, $\alpha$, this approach provides a simple method to summarize water demand across the population.  
%An alternative approach may be to examine welfare impacts by household incomes; however, the data only allow for noisy imputations of income, which may mask larger distributional effects.  Additionally, placing extra welfare weight on smaller users captures the spirit of recent goals by policymakers to ensure a basic right to water.

Finally, I calculate optimal three-part tariffs, which include a fixed fee and separate marginal prices for consumption below and above a 20 cubic meter threshold.  This structure more closely mirrors the current tariff implemented in Manila.\footnote{I calculate optimal tariffs for a 5\% subset of the sample since non-linear budget constraints make this process computationally expensive.  Preliminary tests suggest that the results are robust to this sampling technique.}

\subsubsection{Optimal Tariffs Without Sharing}\label{section:optimaltariffswithoutsharing}

This section computes optimal tariffs when sharing is prohibitively expensive.  This counterfactual setting without sharing allows me to (1) verify optimal tariff designs from the economics literature without sharing and (2) examine the extent to which these tariff designs resemble current pricing policies in Manila.  When households are unable to share, the provider raises less revenue at the current tariff.  Therefore, I recalculate a lower level of capital costs according to revenue generated by imposing the current tariff without sharing.  This procedure allows for direct welfare comparisons between the current tariff and counterfactual tariffs; however, because of this procedure, the magnitudes of the results in this section are not directly comparable to counterfactuals with sharing in Section~\ref{section:optimaltariffswithsharing}.

Figure~\ref{figure:optimaltariffnosharing} provides the optimal tariffs without sharing, and Table~\ref{table:optimaltariffnosharing} includes the corresponding monthly fixed fees as well as the impacts of these tariff structures on the share of households using vendors and using neighboring connections.  The last two rows include consumer surplus measures for the average household as well as the bottom 50\% of users.  Since producer surplus is always held to be zero in these exercises, these consumer surplus measures fully capture welfare.  For ease of comparison, Table~\ref{table:optimaltariffnosharing} also includes the average tariff level in the second row.

\begin{figure}
\centering
\caption{Optimal Tariffs Without Sharing}\label{figure:optimaltariffnosharing}
\includegraphics{tables/no_shr_tariff_groups.pdf}  
\end{figure}

The First-Best tariff schedule produces the highest level of consumer surplus reaching \input{tables/first_best_surplus_group}PhP/month or \input{tables/first_best_surplus_percent_income_group}\unskip\% of household income.  This tariff also produces the minimum share of households using vended water at \input{tables/first_best_percent_vendor_group}\unskip\%.  With costless transfers, the regulator could theoretically reallocate all surplus to the lowest users providing an upper bound on redistribution through pricing at almost double the average surplus.

Relative to the First-Best, implementing the current tariff in this context without sharing reduces average surplus dramatically and increases the share of households using vended water by raising the average marginal price.  The optimal two-part tariff in column three features a higher fixed fee affording a lower marginal price at all consumption levels.  Compared to the current tariff, the optimal two-part tariff brings consumer surplus up to \input{tables/tpt_surplus_improvement_group}\unskip\% of the First-Best surplus.  These welfare gains are primarily driven by increased consumption for large users since surplus for low-users is cut in half and the share of households connected to the network declines substantially.

\begin{table}
\centering
\caption{Optimal Tariffs Without Sharing}\label{table:optimaltariffnosharing}
\resizebox{\textwidth}{!}{%
\input{tables/welfare_no_sharing_groups}
}	\\
\footnotesize{$\text{ }^{*}$ The First-Best fee does not include individual transfers imposed by the regulator. \\  Social tariffs place all welfare weight on the bottom 50\% of water users. \\ Surplus is measured in terms of PhP/month.}

\end{table}

The optimal social tariff in column four attempts to offset these welfare losses for low users by reducing the fixed fee just below zero and doubling the marginal price.  The low fees incentivize small users to connect to the network, reducing the share using from vendors to the First-Best levels.  Average surplus declines since high marginal prices reduce consumption for large users; however, surplus for low users more than doubles.  This result points to the attractiveness of using non-linear pricing to achieve normative goals of redistribution when shared connections are infeasible.

By adding an extra segment to the tariff schedule, the fifth column tests the extent to which more complex linear tariffs can improve efficiency.  Figure~\ref{figure:optimaltariffnosharing} graphs this three-part tariff relative to the current tariff.  The shape of the optimal three-part tariff resembles the current tariff with a low first segment followed by a higher second segment (although the optimal three-part tariff maximizes total surplus while the current tariff is motivated by distributional concerns).  The intuition for this finding is that a low first price segment combined with a high fixed fee provides an additional mechanism for the regulator to price discriminate on the extensive margin; under this pricing regime, only relatively large users connect and their high usage allows the regulator to further lower prices (since the marginal price well exceeds marginal cost).  Despite this attempt to improve welfare, surplus changes are negligible.

The social three-part tariff in column six has slightly more success in redistributing surplus by using an additional tariff block extract greater revenue from large users and improve reallocation to low users.  Relative to the social two-part tariff, the social three-part tariff achieves this goal by offsetting a lower first price segment with a higher second price segment.

\subsubsection{Optimal Tariffs With Sharing}\label{section:optimaltariffswithsharing}

This section calculates the optimal tariff structure in the current environment in Manila (when sharing is possible subject to the estimated hassle costs).  Figure~\ref{figure:optimaltariffsharing} plots the marginal prices associated with each counterfactual tariff.  Table~\ref{table:optimaltariffsharing} computes the impacts of these tariffs on source choices as well as welfare.  Comparing columns two and three of Table~\ref{table:optimaltariffsharing}, I find large welfare improvements on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income from shifting from the current tariff schedule to an optimal two-part tariff schedule.  These gains are mainly enjoyed by large users benefiting from a lower marginal price relative to the current tariff.  At the same time, flattening the tariff greatly reduces the implicit ``tax'' on shared connections, allowing small demand households to also benefit from lower marginal prices through their neighbors' connections.  These lower marginal prices almost compensate for the higher hassle and free-rider costs facing low-demand households, leaving surplus for these households unchanged.
%zooming in on tariffs below 20 PhP/$\text{m}^{3}$ in order to highlight distinctions between the two-part and three-part tariffs.  
\begin{figure}
\centering
\caption{Optimal Tariffs With Sharing}\label{figure:optimaltariffsharing}
\includegraphics{tables/shr_tariff_groups.pdf}
\end{figure}

The optimal fixed fee lies below the current fixed fee, which is priced at the cost of installing and maintaining a connection.  Since households incur hassle costs and free-rider distortions from splitting the bill in sharing connections, pricing below cost allows the regulator to encourage households to substitute away from shared connections toward individual connections and avoid these hassle costs at the margin.  By subsidizing individual connections, the two-part tariff in column three performs very close to the First-Best tariff in terms of average consumer surplus.

\begin{table}
\centering
\caption{Optimal Tariffs With Sharing}\label{table:optimaltariffsharing}
\resizebox{\textwidth}{!}{%
\input{tables/welfare_sharing_groups}
}
\footnotesize{$\text{ }^{*}$ The First-Best fee does not include individual transfers imposed by the regulator. \\  Social tariffs place all welfare weight on the bottom 50\% of water users. \\ Surplus is measured in terms of PhP/month.}
\end{table}

Moving to a social two-part tariff in column four, I find that maximizing welfare for low users counterintuitively involves increasing the fixed fee in order to subsidize a very low marginal price.  This tariff maximizes the share of households using from neighbors while also driving a significant share of households toward water vendors.  Since low-users are able to split the fixed fee with their sharing partner, they can enjoy greater consumption at the low marginal price.  Despite this relatively extreme pricing schedule, surplus for low users only increases by \input{tables/tpt_social_surplus_change_low_sharing_group}PhP/month while average surplus declines by \input{tables/tpt_social_surplus_change_avg_sharing_group}PhP/month.  While manipulating the two-part tariff proved to be an effective redistributive strategy without sharing in Section~\ref{section:optimaltariffswithoutsharing}, this finding suggests that informal sharing networks act to constrain the effectiveness of non-linear pricing in redistributing surplus.

An optimal three-part tariff with sharing in column five follows the same pattern as in the case without sharing: moving to an increasing tariff structure selects for high-usage connections, which provide greater revenue to cover the fixed costs.  As before, this tariff produces negligible changes in welfare.  Figure~\ref{figure:optimaltariffsharing} indicates an optimal three-part tariff with an almost zero first price segment followed by a much higher second price segment, which again broadly aligns with the current tariff structure.  This tariff structure supports the ``life-line'' tariff as a way of efficiently maximizing surplus (rather than achieving distributional goals).  Column six (along with Figure~\ref{figure:optimaltariffsharing}) finds no difference in the optimal social two and three part tariffs.  This result points to the extent to which sharing networks constrain the ability of cities to achieve redistribution through complex, non-linear pricing strategies.

\subsubsection{Optimal Two-Part Tariffs and Sharing Hassle Costs}

To investigate mechanisms driving these optimal pricing schedules, this section considers how the optimal two-part tariff varies continuously with counterfactual levels of the hassle cost, $p_h$.  I follow the same routine as in Sections~\ref{section:optimaltariffswithoutsharing} and \ref{section:optimaltariffswithsharing} by (1) calculating total revenue raised under the current tariff (in Figure~\ref{figure:tariff}) given the counterfactual hassle cost, (2) recalculating the implied capital costs from total revenue under this hassle cost, and (3) determining the optimal two-part tariff maximizing total consumer surplus while just covering costs.\footnote{As the hassle cost rises, the current tariff raises less revenue, lowering the capital costs.  The patterns below are robust to instead holding the capital costs fixed while increasing the hassle costs.}

Figure~\ref{figure:tptshrcosts} plots the optimal marginal price, fixed fee, and share of the population choosing each water source as a function of the hassle cost.  The vertical gray lines show the estimated hassle cost of 15.14 from Section~\ref{section:hasslecostestimation}.  When hassle costs are very low, the regulator chooses a relatively high marginal price and low fixed fee.  This equilibrium maximizes sharing so that one third of households purchase connections and each share their connection with two neighbors.  The high marginal price serves as an way to mitigate overconsumption from free-riding on these shared connections: when three households share a tap, they respond to one third of the marginal price through spitting the bill.  Therefore, setting a price around 13 PhP/$\text{m}^3$ ensures that households actually respond close to the marginal cost of 5 PhP/$\text{m}^3$.  This high marginal price also raises greater revenue allowing the regulator to lower the fixed fee.  As the hassle cost increases to 5 PhP/$\text{m}^3$, the optimal marginal price decreases as more households substitute away from sharing arrangements.  This substitution reduces the extent of free-rider distortions, driving the marginal price closer to the marginal cost.

As the hassle cost increases from 5 PhP/$\text{m}^3$ to around 17 PhP/$\text{m}^3$, it becomes optimal for the regulator to increase the marginal price as a way of taxing shared connections and subsidizing individual connections.  In this range, households are not able to internalize the extent to which costly sharing relationships reduce their own contributions to the capital costs.  Therefore, a high marginal price serves as an additional disincentive for sharing.

Above 17 PhP/$\text{m}^3$, the hassle cost becomes large enough to disincentivize sharing on the margin, allowing the regulator to begin lowering the marginal price again.  Yet, at these high levels of hassle cost, some households begin substituting toward vended water, providing a new incentive for subsidizing access by keeping prices above the marginal cost (consistent with theoretical work by \cite{auerbach1978two}).  The slow decline in marginal price over this range helps to offset the increasing hassle cost, reducing the rate of substitution away from shared connections.  From a distributional perspective, I find that a hassle cost of around 18 PhP/$\text{m}^3$ represents a threshold where the bottom 50\% of users transition from preferring a very high fixed fee as in Section~\ref{section:optimaltariffswithsharing} to preferring fixed fee subsidies as in Section~\ref{section:optimaltariffswithoutsharing}.

This exercise demonstrates how the presence of water sharing can have additional implications for optimal water pricing.  Free-rider behavior among sharing households creates an incentive for the regulator to maintain high marginal prices, and large hassle costs similarly motivate high marginal prices as an efficient tax on shared connections.

\begin{figure}
\caption{Two-Part Tariffs and Sharing Hassle Costs}\label{figure:tptshrcosts}
\begin{center}
\includegraphics[scale=.55,valign=t]{tables/tpt_full_graph_prices.pdf}
\includegraphics[scale=.58,valign=t]{tables/tpt_full_graph_shares.pdf}\\
{\footnotesize The vertical gray lines show the estimated hassle cost of 15.14 PhP/$\text{m}^3$ from Section~\ref{section:hasslecostestimation}.}
% \\ Marginal prices and fixed fees are smoothed with a moving average.}
\end{center}
\end{figure}

\section{Conclusion}\label{section:conclusion}

% didnt show this yet.... This paper finds that incorporating a model of informal sharing networks into a standard regulatory problem produces substantively different policy recommendations with potentially large welfare implications.

This paper demonstrates that pricing policies intended to increase water access especially among the poor can have unintended consequences when low-income households can simply access the piped water network through their neighbors.  The counterfactual exercise finds that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water and total welfare while leaving welfare among low-users unchanged.  In this counterfactual, high fixed costs of accessing an individual connection allow for sharing networks to play an important role in extending water access despite sizable hassle costs.  I also find that complex non-linear price schedules are largely ineffective in terms of achieving both efficiency and equity goals when sharing networks are readily available.

Taken together, these results suggest that households may act as efficient subcontractors in redistributing water to their neighbors.  Instead of sending trained engineers to install and maintain connections in dense neighborhoods, providers can instead rely on informal networks to extend water distribution.  From this perspective, cities may benefit from considering how prices not only might encourage access and redistribute consumer surplus, but also may affect the endogenous formation of water sharing networks.  For example, price discriminating according to neighborhood income instead of by level of monthly usage may achieve similar goals of redistribution without distorting sharing networks.  While this policy may not be appropriate in Manila since neighborhoods are often very heterogeneous in income, this approach may work well in other contexts where neighborhoods are more segregated, such as in Colombia where electricity rates vary according to the social category of each neighborhood (\cite{mcrae2014infrastructure}).

Since sharing networks constrain the menu of pricing policies available to policymakers, cities may benefit from considering a broader range of policies to improve welfare from water use.  For example, cities may be able to lower the frictions associated with these sharing networks by providing technical resources for managing plumbing networks or distributing extra water meters to assist households in accurately splitting the bill.  The empirical results also confirm previous findings that substantial barriers exist for households to connect to the network (\cite{devoto2012happiness}).  Cities may be able to similarly achieve substantial welfare gains by streamlining administrative requirements for new connections and by allowing households to pay connection fees in smaller increments.

\pagebreak

%Taken together, these findings suggest that rather than serve as evidence of underdevelopment, shared water taps, which are common across the developing world, may instead act as an efficient solution to the ``last-mile'' problem of connecting the poor to bulk water infrastructure.

\begin{appendices}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Connection Fee}\label{appendix:connectionfeeamortization}

This section constructs a total fee paid to the water provider each month as the sum of the monthly service fee, 150 PhP/month on average, and the connection fee of 6,000 PhP, amortized over the duration of the water connection.  To amortize the connection fee without information on full durations of residence for all households, I assume that households move to Manila, use a water connection for 80 months, then leave the city.  This assumption is roughly consistent with the hazard rate of disconnection for water connections.  Dividing the connection fee by 80 months and adding it to the monthly service fee results in a total monthly fee of 225 PhP.  Any credit constraints, discount rates, or other barriers to accessing a water connection are captured in monthly terms in the fixed cost estimates in Section~\ref{section:fixedcostestimation}.

\section{Assessing the Sampling of the Connection Survey}\label{appendix:pawssampling}

This section assesses the extent to which the connection survey constitutes a random sample of connected households.  The documentation for the connection survey indicates that sampling was stratified based on geographic areas, assigning a target number of households owning connection to be survey according to the Census population for each area.  Households owning connections were randomly interviewed until these targets were reached.  While ensuring a random sample of connections with areas, this method may oversample areas with few connections per population.  To test this hypothesis, the following equation predicts the share of connections surveyed in each Meter Reading Unit (MRU) --- the smallest geographical unit used by the water provider including a couple hundred water connections on average --- according to demographics of households owning connections, $Z_{MRU,i}$, in each of these MRUs:
\begin{align*}
ShareSurveyed_{MRU} = \beta Z_{MRU,i} + \epsilon_{MRU,i}
\end{align*}
Table~\ref{table:pawssampling} provides the results for this regression.  Although many coefficients are statistically significant consistent with large sample sizes for this estimation, the magnitudes of the effects are small in economic terms across most measures.  For example, increasing the average number of households per connection by a standard deviation (0.65) results in a 0.0021 percentage point decrease in the probability of being surveyed; given a mean survey probability of 6\%, this change represents only a 3.3\% decrease.  Dwelling types are the strongest predictor of coverage, indicating that surveyors may have oversampled apartments possibly due to easier availability.  Taken together, these results suggest that to the extent that non-random sampling may affect results, it will lead to an underestimation of the importance of sharing networks in Manila.

\begin{table}
\centering
\caption{ Predicting Share of Connections Surveyed with \\ Connection Owner Demographics }\label{table:pawssampling}
\input{tables/paws_sampling}
\end{table}

\section{Comparing Demographics in the Census to the Connection Survey}\label{appendix:pawstocensus}

Census households are divided into three groups according to their water source for cooking, laundry, or bathing needs: the first group includes households that select ``own use, faucet community water system'' defined as own use, the second group includes ``shared use, faucet community water system'' defined as shared use, and the third group includes all other categories defined as vendor.  I find a lower percentage of households sharing connections in Table~\ref{descriptives} than in Table~\ref{table:pawstocensus}.  One reason is that all households sharing a connection may identify as owning the connection while the water provider only registers one household as the owner.  Since the empirical strategy combines data from the connection survey with the census, I examine the first two columns for comparability across samples and find that demographics appear broadly similar.

Comparing columns two and three, I find that shared-use households have lower imputed incomes, greater probability of low-skill employment, and slightly smaller households than own-use households.  These trends mirror the findings from connection owners in Table~\ref{descriptives}.  Vendor households captured in the final column of Table~\ref{table:pawstocensus} closely resemble shared-use households across age, employment, and income measures.  These households are especially likely to reside in a single house, which may lead to easier access to vendors as well as more difficult access to neighboring connections.

\begin{table}
\centering
\caption{Household Demographics across \\ Survey and Census Data by Water Source}\label{table:pawstocensus}
\input{tables/descriptives_census_to_paws} \\
\footnotesize{The data include connection survey data on households owning water connections \\ as well as 2010 Census data on households.  This sample includes overlapping villages between surveys (67\%)}
\end{table}

\section{Details on Mobile Survey}\label{appendix:pollfish}

The mobile survey was conducted using Pollfish--- an organization that advertises the opportunity to complete a survey for the chance to win an Amazon gift certificate.  Pollfish reaches potential respondents through ads on mobile apps and Facebook.  The survey was fielded in 6 batches of 100 respondents in July, 2017, which allowed for the addition and modification of questions across survey rounds.

\begin{table}
\centering
\caption{Mobile and PAWS Water Source Choices}\label{table:pollfishpawsmeans}
\input{tables/pollfish_paws_means_1} 
\vspace{.3cm}
\footnotesize{The PAWS data have been adjusted to reflect that \\ shared connections serve multiple households.}
\end{table}

Since this survey is not designed to be representative of the population of households in Manila, the following tables compare descriptive statistics between the mobile survey and the Public Assessment of Water Services (PAWS) survey.  Table~\ref{table:pollfishpawsmeans} compares the shares of households choosing each water source --- individual, sharing with 1 other household, or sharing with 2 other households --- across the two datasets, adjusting for the fact that the connection survey was conducted at the water connection-level.  I find similar shares of households choosing these three water sources across these datasets with more households choosing to connect as single users in the Mobile survey data.  Since the mobile survey was conducted over 8 years after the connection survey, this increase in single connections is consistent with a general substitution toward purchasing own connections (with increasing income and declining vendor opportunities).

Table~\ref{table:pollfishpawssharing} compares demographics within each of these categories of water source.  The first row indicates that Pollfish respondents tend to be much younger than connection survey respondents, which is consistent with higher mobile phone use among younger people as well as the fact that the connection survey largely targeted heads of household while any member could respond to Pollfish.  Dwelling types and household size appear largely similar for single users with differences increasing as the number of households using each water connection increases.  Since the connection survey only captures demographics for water connection owners while the mobile survey covers all users, this trend may capture differences between these groups.  Taken together, these findings suggest that the mobile and connection surveys are broadly consistent in capturing the population of water users despite differences in survey methods and timing.

%Finally, while the number of users increases with the number of households drawing from each connection, this increase is greater for the mobile survey than for the connection survey.

\begin{table}
\centering
\caption{Mobile and PAWS Descriptives by Water Sharing Status}\label{table:pollfishpawssharing}
\input{tables/pollfish_paws_diff_1}
\end{table}

\section{Linear Approximation}\label{appendix:linearapprox}

This section now investigates the extent to which this linear approximation might impact coefficient estimates as well as welfare calculations.  The following figure compares the linear approximation to the standard normal CDF function over the range $(-3,3)$:
\begin{center}
\includegraphics[scale=.5]{tables/cdf_approx.png}
\end{center}
To ballpark the effects of this approximation, I simulate a dataset with two prices and one kink point as well as simulated parameters that are close to estimated values.  Using this dataset, demand can be calculated in two ways: (1) according to the approximated function in equation (\ref{equation:generaldemand}) and (2) according to the exact demand function given by the numerical solution to the first order condition in equation (\ref{equation:firstordercondition}).  Table~\ref{table:linapproxsim} provides the parameters used for simulation as well as the simulation results.  The second and third columns provide estimates from the likelihood function in equation (\ref{equation:LLikelihood}).  The second column shows estimates when consumption is generated through the exact numerical solution to the first order conditions.  In this case, the likelihood function would be misspecified since the likelihood relies on the linear approximation.  The third column shows estimates for when consumption is generated using the linear approximation, ensuring that the likelihood function is properly specified in this case.  The estimates rely on a small sample of households in order to speed performance.  Sampling error can help explain why the estimates in column three do not exactly match the true parameters.  The last column finds small differences between estimates in columns two and three, providing some evidence that the linear approximation does not introduce substantial bias in the estimation.  Welfare differences between following  approximated versus actual versus are negligible, totaling \input{tables/approx_welfare}PhP per month.

\begin{table}
\caption{Simulation Estimates for Linear Approximation}\label{table:linapproxsim}
\centering
\input{tables/approx_simulation} \\
\footnotesize{The prices as well as the $\gamma$ terms are sampled from a uniform distribution on the given interval.  Approx. DGP stands for approximated data generating process, which generates consumption values using the linear approximation.  Exact DGP calculates consumption using the true demand function.   }
\end{table}

\section{Alternative Sharing Contracts}\label{appendix:fixedprice}

Two alternative sharing contracts include (1) alternating bill payment each month and (2) charging a fixed price to sharing households.  Alternating bill payments can be thought of as a fixed price contract where each household faces a payment of zero each month.  To model fixed price contract, consider a simple setting with two households and a linear budget constraint.  Let household $1$ pay the full bill while household $2$ pays a fixed amount $Z$ each month regardless of their consumption:.

The household optimization problems and solutions are as follows:
\begin{align*}
max_{x_1,w_1} \hspace{.2cm} & E\big[ U(x_1,w_1) \big] \\
\text{s.t.  }\hspace{.3cm} Y_1 &=   x_1  + p (W_1 + W_{2})  \\
w_1 &= \Gamma_1 - \alpha_1  p \\
max_{x_2,w_2} \hspace{.2cm} & E\big[ U(x_2,w_2) \big] \\
\text{s.t.  }\hspace{.3cm} Y_2 &=   x_1  + Z \\
w_2 &= \Gamma_2
\end{align*}
Joint consumption takes the following form:
\begin{align*}
(w_1+w_2) = (\Gamma_1 + \Gamma_2) - \alpha_1 p
\end{align*}
In the case where price sensitivities are equal between households, $\alpha_1=\alpha_2=\alpha$, joint consumption under a fixed price contract is empirically identical to joint consumption under even bill-splitting.  Therefore, assuming bill-splitting when households use fixed price contracts may bias price sensitivity estimates when these price sensitivities are very different from each other.  This bias becomes less of a concern if households alternate paying the bill because the joint estimate of $\alpha$ will capture some weighted average of $\alpha_1$ and $\alpha_2$.  Fixed price contracts may lead to a different allocation of surplus from sharing contracts depending on the size of the fixed price $Z$.  Yet, since the model assumes that households are able to split expected surplus from the sharing relationship through fixed monthly transfers in Section~\ref{section:watersourcechoice}, the type of contract likely has little effect on empirical or welfare estimates.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Price Variation}\label{appendix:pricevariation}

\subsection{Targeting the Non-linear Tariff}

Figure~\ref{figure:consumptionhistogram} shows a histogram of monthly consumption choices across all water connections and months in the data alongside the tariff schedule (censored below 50).  Usage hovers around 20 cubic meters per month; by comparison, households in the United States use closer to 50 cubic meters per month.  Intuitively, households may be less willing to consume an additional cubic meter on the margin if the price for that unit is much higher.  The histogram provides some evidence of bunching at 10 and 20 cubic meters, although the magnitudes are quite small.  Many households are also observed to consume below 10 units where the marginal price is actually zero.  Taken together, this evidence suggests households may be unresponsive to price.

\begin{figure}
\caption{Consumption Histogram}\label{figure:consumptionhistogram}
\begin{center}
\includegraphics[scale=.7]{tables/tariff_structure_2.pdf}\\
\footnotesize{Consumption values are truncated at 60 to highlight bunching at kink points.}
\end{center}
\end{figure}

\subsection{Time Series Variation in Tariffs}\label{appendix:tariffvariation}
This figure indicates time series variation in prices as a result of the government regulator raising prices incrementally to ensure production costs are covered.

\begin{center}
\includegraphics[scale=.65]{tables/tariff_time_series.pdf}
\end{center}

\subsection{Within Connection Price Variation}\label{appendix:ratechangeelasticity}

This setting also provides quasi-experimental variation in the tariff over time at the connection-level, which serves as a useful setting to examine household demand response to price changes over time.  Previous work estimating demand for public utilities has relied on time-series variation from regulated changes in the tariff (\cite{szabo2015value,mcrae2014infrastructure}).  While the estimation strategy in this paper also includes this variation, regulated tariff changes are often relatively small, affect all households equally during the same month, and are anticipated well in advance.  Through a quirk in the regulatory agreement, the water provider is able to upgrade households that are discovered engaging small businesses to a higher tariff class called the semi-business rate.  The vast majority of these businesses are roadside stands, locally known as Sari-Sari stores.  The connection survey covers \input{tables/semi_sample_size}connections that are upgraded from residential to semi-business status used in the analysis.

Figure~\ref{figure:ressemi} compares the tariff structure between residential and semi-business rates.  The tariffs mainly deviate between 10 and 20 cubic meters where the semi-business rate is about 30\% higher.

\begin{figure}
\caption{Residential and Semi-Business Tariffs}\label{figure:ressemi}
\begin{center}
\includegraphics[scale=.65]{tables/res_semi_tariff.pdf}
\end{center}
\end{figure}

Table~\ref{table:semittests} provides summary statistics and t-tests comparing residential connections to semi-business connections, and semi-business connections to connections that are upgraded from semi-business to residential.  Semi-business connections use more water, while having smaller households sizes, greater low-skilled employment, and higher likelihoods of living in a single house.  Despite using more water, those upgraded to semi-business rates are broadly similar to the population of semi-business connections.  
%While many differences are statistically significant, the economic magnitudes of these differences are relatively small suggesting that demand responsiveness for this sub-population may be informative about the full population.

\begin{table}
\centering
\caption{Summary Statistics and Comparison of Means for Residential, Semi-Business, and Upgraded Connections}\label{table:semittests}
\input{tables/sem_compare_means1}\\
\footnotesize{Data are from the connection survey.}
\end{table}

The following equations estimate both event study and differences-in-differences strategies used to determine consumption response to changes in the rate class.  For connections $i$ in month $t$, these equations predict consumption as a function of individual, $\theta_i$, and time, $\delta_t$ fixed effects.  The event study in the first equation includes $\beta_r$ dummy variables for months to the rate change while the differences-in-differences approach in the second equation captures the $\beta$ effect on consumption of being after the rate-change, $Post_{i,t}$.
\begin{align*}
w_{i,t} &= \sum_{r=-12}^{12} \beta_{r} \mathbbm{1} \{t=r\}  +  \theta_{i} +\delta_t + \epsilon_{t,i} \\
w_{i,t} &= \beta Post_{i,t} +  \lambda_{1} r_{i,t} + \lambda_{2} Post_{i,t} \times r_{i,t} + \theta_{i} +\delta_t  + \epsilon_{t,i}\\
&r \text{ : month to upgrade to semi-business rate}
\end{align*}

Figure~\ref{figure:semieventstudy} plots average consumption for these connections relative to the month that they are upgraded to the semi-business tariff level.  Before the upgrade consumption trends slightly upward, before dropping immediately following the tariff increase.  A simple differences-in-differences estimate calculates a sizable price elasticity of 0.5 from this change, indicating significant demand responsiveness to time-series variation in the tariff.  This elasticity is very similar to the structural estimates in Section~\ref{section:preferenceestimation}.

\begin{figure}
\caption{Demand Response to Time Series Price Variation}\label{figure:semieventstudy}
\begin{center}
\includegraphics[scale=.7]{tables/sem_event.pdf}
\end{center}
\end{figure}

\section{Determining the Demand Function with Respect to Variance of Consumption Shocks}\label{appendix:sigmanuassumptions}

The specification of the demand function is sensitive to ex-ante assumptions on the standard deviation of the consumption shocks, $\sigma_{\epsilon}$.  To identify the appropriate demand function in this empirical setting, I maximize the likelihood function in equation (\ref{equation:LLikelihood}) over three demand specifications with different assumptions on $\sigma_{\epsilon}$ before selecting equation (\ref{equation:generaldemand}) as the primary specification.

I first construct and estimate demand under the limiting assumption that $\sigma_{\epsilon}$ falls below the minimum threshold, $min_{\forall k}\hspace{.2cm} \{ \frac{\overline{W}_{k+1} - \overline{W}_k}{2\sqrt{2}} \} = \frac{10}{2\sqrt{2}} = 3.53$.  Under this assumption, households only consider one price at all segments and two prices near thresholds.  This assumption produces the following demand function:
\begin{align}\label{equation:demandalt1}
\begin{split}
w^{*}_C &=
\begin{cases}
D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{1,U}  \\
D^{2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }   
\end{cases}\\
\text{Assuming:}\\
 \sigma_{\epsilon_C} \leq &\frac{  \overline{W}^{2} - \overline{W}^{1} }{ 2\sqrt{2} } = \frac{ 10 }{ 2 \sqrt{2} } = 3.53 
\end{split}
\end{align}
Estimates according to this demand function in the first column of Table~\ref{table:sigguess} find that the standard deviation for consumption shocks for connections serving single households through connections serving three or more households exceeds the 3.53 threshold in all cases.
\begin{table}
\centering
\caption{Alternative Demand Specification Estimates}\label{table:sigguess}
\input{tables/sig_guess_estimates}
\end{table}
Next, I estimate the primary specification in equation (\ref{equation:generaldemand}), which holds under the hypothesis that $\sigma_{\epsilon}$ falls between $3.53$ and $\frac{\overline{W}_{2} - \overline{W}_1}{2\sqrt{2}} = \frac{20}{2\sqrt{2}} = 7.06$.  Estimates from the second column of Table~\ref{table:sigguess} fail to reject the hypothesis.

Finally, I allow for greater variance of $\sigma_{\epsilon}$ exceeding $7.06$ and ensuring that the household responds to three prices at both interior price segments in the tariff schedule.  This specification takes the following functional form:
\begin{align}\label{equation:demandalt2}
\begin{split}
w^{*}_C &=
\begin{cases}
D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
D^{2,3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{2,4} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
\end{cases}\\
\text{Assuming:}\\
 \sigma_{\epsilon_C} \geq &\frac{  \overline{W}^{2} - \overline{W}^{1} }{ \sqrt{2} } = \frac{ 10 }{  \sqrt{2} } = 7.06 \\
 \sigma_{\epsilon_C} \leq &\frac{  \overline{W}^{3} - \overline{W}^{2} }{ \sqrt{2} } = \frac{ 20 }{  \sqrt{2} } = 14.12
\end{split}
\end{align}
The final column in Table~\ref{table:sigguess} again rejects this hypothesis finding estimates of $\sigma_{\epsilon}$ that fall below the 7.06 threshold.  Comparing all of the parameter estimates across specifications, I find very minor differences according to the different demand functions, providing suggestive evidence that the estimation strategy is robust to ex-ante assumptions on $\sigma_{\epsilon}$.

\section{Hassle Cost: Neighbor Radius}\label{appendix:sharingneighbor}

The following equation predicts usage for neighboring households, $i$, relative to a nearby leak according to their distance rank, $DR$, relative to the leaking household with rank $1$ being closest and rank $D$ being furthest from the leaking household.  To capture any spatial changes in consumption over time, the regression also allows for differential time trends before and after the leak according to distance rank, $DR$, captured by $\lambda^{d}_{1}$ and $\lambda^{d}_{2}$:
\begin{align*}
	w_{t,i} &= \sum_{d=1}^{D} \mathbbm{1}\{DR_{i}=d\} \Big [ \beta^{d} Post_{i,t} +  \lambda^{d}_{1} r_{i,t} + \lambda^{d}_{2} Post_{i,t} \times r_{i,t} \Big ] + \theta_{i}  + \epsilon_{t,i}\\
r_{i,t} &\text{ : Months to leak} \\
DR_{i} &\text{ : Distance Rank Relative to Leaking Connection} \\
Post_{i,t} &\text{ : After leak}
\end{align*}
The coefficients of interest, $\beta^{d}$, are presented in Table~\ref{table:neighbordistance}.  I find that the closest neighbor receives the most consumption from the leaking household, closely followed by the second and fourth neighbors.  Substitution drops off quickly past the fourth neighbor, reaching statistically insignificant and economically smaller magnitudes for the fifth through eighth neighbors.  
\begin{table}
\caption{Sharing and Distance to Leaking Connection}\label{table:neighbordistance}
\centering
\input{tables/neighbor_distance}
\end{table}

\section{Hassle Cost Assumptions}\label{appendix:sharingcostassumptions}

The following additional assumptions are required to ensure that this empirical setting accurately captures the model described in Section~\ref{section:hasslemodel}:
\begin{enumerate}

	\item \textit{ Connections that experience a leak are representative of the population of connections. }  This assumption is supported by minimal economic differences in means of observables between connections with leaks and without in Table~\ref{table:leakbalance} (although some differences are statistically significant).  
\begin{table}
\centering
\caption{Descriptives and Balance Test for Non-Leaking and Leaking Connections}\label{table:leakbalance}
\input{tables/mean_diff_leak1} \\
\footnotesize{Drink is a dummy for drinking tap water.  Water flow is a dummy for low water pressure. \\ Water storage is a dummy for owning a water storage container.  Std. errors result from a T-test of differences in means.}
\end{table}

	\item  \textit{ The decision to disconnect conditional on experiencing a leak is uncorrelated with water demand. }  Table~\ref{table:leakbalancedc} provides partial support by showing few large differences in characteristics between those that disconnect and those that remain connected other than the size of leak.  This evidence suggests that the disconnection decision is driven primarily by variation in the magnitude of the leak.
\begin{table}
\centering
\caption{Balance Test for Disconnection among Leaking Connections}\label{table:leakbalancedc}
\input{tables/mean_diff_DC1.tex} \\
\footnotesize{Drink is a dummy for drinking tap water.  Water flow is a dummy for low water pressure. \\ Water storage is a dummy for owning a water storage container. Std. errors result from a T-test of differences in means.}
\end{table}

	\item \textit{ The timing of a leak is uncorrelated with any underlying changes in demand. }  I test this assumption with a regression predicting a connection $i$'s consumption in the 30 months before the leak event controlling for a connection fixed effect, $\theta_{i}$:  
\begin{align*}
w_{t,i} &=  \sum_{r=-30}^{0} \beta_{r} \mathbbm{1} \{t=r\}  +  \theta_{i} + \epsilon_{t,i} \\
r 		 &\text{ : Month to leak}\\
\theta_i &\text{ : Connection-level fixed effect}
\end{align*}
	I include a dummy variable for each month before the leak.  Figure~\ref{figure:leakpretrend} plots demeaned monthly consumption relative to the month of the leak.  This figure shows stable a consumption pattern interrupted by a large jump at the exact time of the leak.
\begin{figure}
\centering
\caption{Pre-Trend in Leaker's Consumption}\label{figure:leakpretrend}
\begin{center}
\includegraphics[scale=.7]{tables/leakers_pre_2.pdf}
\end{center}
\end{figure}

	\item \textit{ Leaks are uncorrelated with changes in neighborhood demand. }  A simple regression tests this assumption by predicting total consumption among four closest neighbors in neighborhood $N$, before and after a nearby leak, controlling for a neighborhood fixed effect, $\theta_{N}$.  I include a dummy variable for each month relative to the month that the neighbor leaks:
	\begin{align*}
	w_{N,t} &= \sum_{r=-14}^{14} \beta_{r} \mathbbm{1} \{t=r\}  +  \theta_{N} + \epsilon_{N,t} \\
	r &\text{ : Month to leak} \\
	N &\text{ : Neighborhood }
	\end{align*}
	Figure~\ref{figure:leakeventstudy} plots the results of this regression indicating average total neighborhood consumption in the months just preceding and following the date that the leakis reported.  I find a stable trend in neighbors' consumption before the leak followed by a quick leap as the leaking household starts to share with their neighbors.  This sharing behavior remains persistent for at least a year after the initial pipe leak, providing a useful window of time to estimate the hassle cost.
	\begin{figure}
	\centering
	\caption{Neighbors' Water Usage following a Leak Disconnection}\label{figure:leakeventstudy}
	\begin{center}
	\includegraphics[scale=.7]{tables/leakers_full_2.pdf}
	\end{center}
	\end{figure}

	\item \textit{  The leaking household's choice of a sharing partner is uncorrelated with that partner's water demand.  }  This assumption holds when the $\omega$ term in equation (\ref{equation:hassleutilities}) is equal to zero.  If $\omega$ is nonzero allowing leaking households to weigh the utility from using each source in this decision, households may choose to share with low demand neighbors to enjoy lower points on the tariff in Figure~\ref{figure:tariff}.  To test this hypothesis, I predict the heterogeneous increase in neighbor's consumption following a leak according to that neighbor's water demand, which is proxied by average consumption prior to the leak.  The following regression equation tests this relationship by predicting changes in usage according to the rank of average consumption at baseline among all neighbors: 
\begin{align*}
	w_{t,i} &= \sum_{d=1}^{4} \mathbbm{1}\{Rank_{i}=d\}  \beta^{q} Post_{i,t}  + \theta_{i}  + \epsilon_{t,i}\\
r &\text{ : Month to leak} \\
Rank &\text{ : Rank of avg. usage in the neighborhood at baseline} \\
\theta_i &\text{ : Connection-level fixed effect}
\end{align*}
	One issue with this analysis is that predicting the usage response of a neighbor as a function of their previous consumption is likely to produce mean reversion bias: connections with low usage at baseline demonstrate larger increases in consumption than connections with high usage at baseline due to natural variation in preference shocks.  To test for mean reversion, I create a random treatment date using only data before the leak has occurred.  Table~\ref{table:neighborselection} presents the $\beta^{d}$ estimates of the true leak-date specification in the first column and the mean randomized leak-date estimates in the second column.  The third column takes the difference of the first and second columns, which provides a coarse method of netting out any mean reversion bias.  The first column predicts strong increases in consumption for smaller users (ranks 1 and 2) while large users (ranks 3 and 4) exhibit small and even negative demand responses.  These differential responses are only exaggerated in the second column, suggesting that mean reversion may play a large role in biasing estimates.  The third columns shows that after adjusting for mean reversion bias, the demand response of neighboring connections is roughly equal as the relative demand increases for these connections.  This finding provides suggestive evidence that households are not selecting sharing partners conditional on their neighbors' water demands.
\begin{table}
\centering
\caption{Leak Demand Response and Rank of Baseline Usage in Neighborhood}
\input{tables/neighbor_selection}\label{table:neighborselection}
\end{table}
	\item \textit{ In response to a leak, the choice to share with a neighbor or use a vendor is uncorrelated with water demand. }  This assumption also holds when the $\omega$ term in equation (\ref{equation:hassleutilities}) is equal to zero.  If water demand were correlated with substitution across these sources, then I would expect to find that the water demand of the leaking household predicts a differential rise in usage among neighbors following the leak.  Since vended water is characterized by high prices and low fees, a simple model would predict that households with low water demand would substitute toward vendors at a higher rate and would therefore offset less consumption to neighboring households following a leak.  To test this assumption, I use average consumption for a leaking household prior to the leak as a proxy for their water demand.\footnote{Using the same test as before, I detect no evidence of mean reversion given this demand proxy.}  The following equation predicts total usage in neighborhood, $N$, before and after a household in that neighborhood experiences a leak.  The regression allows for separate impacts of a neighbor's leak, $\beta^d$ depending on that neighbor's quintile of average consumption (measured before the leak).
\begin{align*}
	w_{t,N} &= \sum_{d=1}^{5} \mathbbm{1}\{Quintile_{N}=d\}  \beta^{d} Post_{N,t}  + \theta_{N}  + \epsilon_{N,t}\\
r &\text{ : Month to leak} \\
Quintile &\text{ : Quintile of avg. usage for leaking connections at baseline} \\
\theta_N &\text{ : Neighborhood-level fixed effect}
\end{align*}
	Table~\ref{table:leakerselection} presents the results from this regression in the first column.  The size of the coefficients increase as the quintile of leaker demand increases, which is consistent with larger users at baseline using greater amounts of water from their neighbors.  To compare the relative demand response for large and small users, column three divides this coefficient estimate by the average usage for each quintile at baseline to arrive at the percentage of water consumption that is offset among neighbors after a leak occurs.  Column three finds no strong trends in the share of consumption that is offset to neighbors across water demand quintiles.  This finding provides suggestive evidence that household's are left to use whichever source is most immediately available (neighbor or vendor) following a leak.
\begin{table}
\centering
\caption{Neighborhood Usage Response and Quintile of Usage for Leaking Connection}\label{table:leakerselection}
\input{tables/leaker_selection}
\end{table}

	\item \textit{  A leak for one household is uncorrelated with probability of a neighboring household experiencing a leak. }  While the data show little evidence that leaks  are spatially correlated, I cannot rule out unreported leaks affecting nearby households.  The presence of unobserved spatial correlation in leaks would lead this method to overestimate the hassle costs associated with sharing a connection.
\end{enumerate}

\section{Bootstrapping Procedure for Hassle Cost}\label{appendix:hasslecostbootstrap}

The bootstrapping procedure resamples at the level of full neighborhoods including both leaking connection and the neighboring connections, which treats each ``leak'' as its own cluster.  In a small number of bootstrapped samples ($<5\%$), the estimation procedure for this step converges to extreme outliers; this is because these samples have a relatively high share of households choosing zero monthly consumption, which are difficult values for the model to fit.  In these cases, I adjust the routine to drop zero consumption values ($<2\%$ of all values), which allows the procedure to converge to plausible parameter values.

%\begin{align*}
%w_{i}^{pre} &= \Gamma_{i} - \alpha_{i} p \\
%w_{i}^{post} &= \Gamma_{i} - \alpha_{i} ( p + p_{h}) \\
%\frac{w_{i}^{pre} - w_{i}^{post}}{\alpha_{i}} &= p_{h}
%\end{align*}

\section{Game Tree with Three Players}\label{appendix:gametreefull}

This section maps the game tree for three players, $1$, $2$, and $3$ in Figure~\ref{figure:fullgametree}.

%\begin{landscape}
%\setcounter{figure}{10}

\begin{figure}
\caption{Sequential Game Choosing Water Sources}\label{figure:fullgametree}
\centering
\begin{turn}{90}
\resizebox{1.1\textwidth}{!}{%
\begin{tikzpicture}
\node(0){ \textbf{HH  1}}
child[level distance=8mm,sibling distance=150mm]{node{\textbf{HH2}} %%% HERE IS NODE 1 %%%
child[level distance=20mm,sibling distance=25mm]{node{\textbf{HH3}}
child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
}  
child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
}
edge from parent node[left]{ \scriptsize{Vendor}}
}
child[level distance=50mm,sibling distance=25mm]{node{\textbf{HH3}}
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
}  
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$U_{2}(P_S,F-T_{3,2})$} \\ \scriptsize{$u^{3}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH2}}
}
child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]280: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
}
edge from parent node[right]{ \scriptsize{Connect}}
}
edge from parent node[below]{ \footnotesize{Vendor} }
}
child[level distance=8mm,sibling distance=80mm]{node{\textbf{HH2}} %%% HERE IS NODE 2 %%%
child[level distance=10mm,sibling distance=50mm]{node{\textbf{HH3}}
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
}  
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$U_{1}(P_S,F-T_{3,1})$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(s^{1}|\{ 1,3 \}) + T(\{ 1,3 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH1}}
}
child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]280: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
}
edge from parent node[right]{ \scriptsize{Vendor}}
}
child[level distance=40mm,sibling distance=50mm]{node{\textbf{HH3}}
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
}
child[level distance=15mm,sibling distance=35mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$U_{1}(P,F-T_{3,1})$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(s^{1}|\{ 1,3 \}) + T(\{ 1,3 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH1}}
}  
child[level distance=15mm,sibling distance=35mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$U_{2}(P_S,F-T_{3,2})$} \\ \scriptsize{$u^{3}(s^{2}|\{ 2,3 \}) + T(\{ 2,3 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH2}}
}
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]280: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
}
edge from parent node[right]{ \scriptsize{Connect}}
}
child[level distance=10mm,sibling distance=60mm]{node{\textbf{HH3}}
child[level distance=15mm,sibling distance=20mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(c|\{ 1,2 \}) + T(\{ 2 \})$} \\ \scriptsize{$u^{2}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
}
child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(c|\{ 1,2,3 \}) + T(\{ 1,2,3 \})$} \\ \scriptsize{$u^{2}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$} \\ \scriptsize{$u^{3}(s^{1}|\{ 1,2,3 \}) + T(\{ 1,2,3 \})$}  }]{} edge from parent node[right]{\scriptsize{Shr HH1}}
}  
child[level distance=30mm,sibling distance=30mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(c|\{ 1,2 \}) + T(\{ 2 \})$} \\ \scriptsize{$u^{2}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Vendor}}
}
edge from parent node[right]{ \scriptsize{Shr HH1}}
}
edge from parent node[below]{ \footnotesize{Connect} }
}
;
%\node at($(0-1)!.7!(0-2)$){ \textbf{HH 2} };
%\node at($(2-1)!.5!(2-2)$){ \textbf{HH 3} };
\end{tikzpicture}
}
\end{turn}
%\begin{itemize}
%\item $p_v$: Vendor Price
%\item $F_v$: Vendor Fee/Disutility
%\item $T_{i,j}$: Transfer from household $i$ to household $j$
%\item $P, P_S$: Tariff schedules for single and joint users
%\item $p_{h}$: Hassle Cost
%\end{itemize}
\end{figure}

%\end{landscape}

\section{Test for Incidental Parameter Bias}\label{appendix:incidentalparametertest}

The estimation strategy relies heavily on connection-specific fixed preference terms estimated in the Section~\ref{section:preferenceestimation} to recover parameters in Section~\ref{section:hasslecostestimation} and Section~\ref{section:fixedcostestimation}.  Since the data contain a limited number of months of consumption for each connection (averaging around 77 months), noise in the estimation of these preference terms may produce bias in latter estimates.  I test for this type of bias by simulating data given true parameters close to the estimates and reestimating the model on this simulated data.  Table~\ref{table:incidentalparameters} provides results for this test.

The first column presents the true assumed parameter values, the second column provides the estimations results for the simulated data using the full sample, and the third column includes estimates for a subsample of the data where I have dropped half of the observations for each connection.  Examining the second column and percent deviations in the third column, I find that the incidental parameters do not seem to lead to a large degree of bias in any of the coefficients with the maximum occurring for the variance estimate for the vendor price.  Dropping half of the time periods, the fourth and fifth columns indicate that the hassle cost and connection fee parameters would be the most sensitive to any possible bias from incidental parameters.

\begin{table}
\centering
\caption{Simulation Test for Incidental Parameter Bias}\label{table:incidentalparameters}
\input{tables/incidental_parameters}\\
\footnotesize{T refers to months observed for each connections.  The first sample includes half of the time periods per connection (around 35 months), while the second sample includes all months.  Both samples include 5,000 accounts.}
\end{table}

\end{appendices}

\end{comment}

{
\small
\nocite{*}
\bibliographystyle{abbrvnat}
\setcitestyle{authoryear,open={((},close={))}}
\bibliography{library}
}

%\begin{center}
%  \input{mean_diff_leak1}
%\end{center}

%\begin{center}
%    \input{mean_diff_DC1}
%\end{center}

% \begin{table}[]
% \centering
% \caption{Source Choices}
% \label{my-label}
% \begin{tabular}{|l|c|c|c|}
% \hline
%                 & Fixed Price                  & Marginal Price                 & Tariff Kink Points      \\ \hline
% Individual (I)  & $F$                          & $P_k$                         & $\overline{w}_{k}$                         \\ \hline
% Shared   (S)    & $\frac{F}{2}$                & $P_k + P_{h}$                 & $\frac{\overline{w}_{k}}{2}$                            \\ \hline
% Vendor   (V)    & $0$                          & $P_{v}$                        & $0$                          \\ \hline
% \end{tabular}
% \end{table}
%\bibliography{lib}

\end{document}

### 2018-09-07 notes.py

@@ -1,61 +1,0 @@
-
-
-
-# CREATE TABLE query right here !!
-#	qry = '''
-#    	CREATE TABLE paw_density AS
-#    	SELECT 
-#                    FROM bblu_{} as A, rdp_conhulls AS G
-#                    WHERE A.ROWID IN (SELECT ROWID FROM SpatialIndex 
-#                        WHERE f_table_name='bblu_{}' AND search_frame=G.GEOMETRY)
-#                        AND st_intersects(A.GEOMETRY,G.GEOMETRY)
-#                    GROUP BY A.conacct;
-#    	'''
-
-
-
-# ADD python path for QGIS
-# open bash in text editor through terminal with:
-#   touch ~/.bash_profile; open ~/.bash_profile
-
-
-# on OSX: export PYTHONPATH=/Applications/QGIS.app/Contents/Resources/python
-#         export PATH="/Applications/QGIS.app/Contents/MacOS/bin:$PATH"
-
-## RUN QGIS REMOTELY
-
-#from qgis.core import *
-
-#	QgsApplication.setPrefixPath("/Applications/QGIS.app/Contents/MacOS/", True)
-#	qgs = QgsApplication([], True)
-#	qgs.initQgis()
-
-#	uri = QgsDataSourceURI()
-#	uri.setDatabase(db)
-#	schema = ''
-#	table = 'meter'
-#	geom_column = 'GEOMETRY'
-#	uri.setDataSource(schema, table, geom_column)
-
-#	display_name = 'METER'
-#	vlayer = QgsVectorLayer(uri.uri(), display_name, 'spatialite')
-
-#	QgsMapLayerRegistry.instance().addMapLayer(vlayer)
-#	qgs.exitQgis()
-
-
-
-## TEST ENTRY OF NEIGHBORS TABLE
-
-#	for i in range(0,3):
-#		for j in range(1,5):
-#			print 'line'
-#			print i
-#			print j
-#			print mat[i][2]
-#			print mat[res[1][i][j]][2]
-#			print res[0][i][j]
-
-
-
-

### 2018-09-07 phil_matlab/data_prep.m

@@ -28,20 +28,20 @@ if sample(1)==1
         X = X(i_B,:);
         %{
                     if BOOT(1)>1
-                        i_pre=csvread(strcat('BOOT\iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
+                        i_pre=csvread(strcat('BOOT/iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
                         i_post=[i_pre i_B];
-                        csvwrite(strcat('BOOT\iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),i_post);
-                        t_pre=csvread(strcat('BOOT\tBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
+                        csvwrite(strcat('BOOT/iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),i_post);
+                        t_pre=csvread(strcat('BOOT/tBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
                         t_post=[t_pre t];
-                        csvwrite(strcat('BOOT\tBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),t_post);
+                        csvwrite(strcat('BOOT/tBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),t_post);
                     else
 
-                        csvwrite(strcat('BOOT\iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),i_B);    
+                        csvwrite(strcat('BOOT/iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),i_B);    
                         csvwrite(strcat('tBOOT',num2str(est_version),'.csv'),t); 
                     end
        %}
-                        dlmwrite(strcat(cd_dir,'BOOT\iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),i_B,'precision',20);    
-                        csvwrite(strcat(cd_dir,'BOOT\tBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),t);       
+                        dlmwrite(strcat(cd_dir,'BOOT/iBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'),i_B,'precision',20);    
[…]

### 2018-09-07 phil_matlab/data_prep_bg.m

@@ -31,7 +31,7 @@ function [t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,gamma,x,CONTROL,CONTROL_PH,beta_O,
             gindex=csvread(strcat(cd_dir,'BOOT',slash,'gBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
             %gindex=gindex(:,BOOT(1));
             [~,~,iB,t] = boot_testing_2(g-1,t,gindex);
-            X          = csvread(strcat(cd_dir,'post_',tag_v1,'.csv'),1,0, [ 1 0 max(iB) (6+control_size) ]);
+            X          = csvread(strcat(cd_dir,'post_',tag_g,'.csv'),1,0, [ 1 0 max(iB) (6+control_size) ]);
             X = X(iB,:);
             %x_pre=csvread(strcat('xBOOT',num2str(est_version),'.csv'));
             x=csvread(strcat(cd_dir,'BOOT',slash,'xBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));

### 2018-09-07 phil_matlab/error_sample.m

@@ -1,0 +1,10 @@
+function nu = error_sample(sn1,sn2,sn3,corr_2,corr_3)
+
+rng(1);
+nu = zeros(length(sn1),3);
+
+for i = 1:length(sn1)
+    nu(i,:) = mvnrnd( [0;0;0] ,[sn1(i)     (corr_2.*sqrt(sn1(i)).*sqrt(sn2(i)))  (corr_2.*sqrt(sn1(i)).*sqrt(sn3(i))) ; ...
+                            (corr_2.*sqrt(sn1(i)).*sqrt(sn2(i)))  sn2(i)     (corr_3.*sqrt(sn2(i)).*sqrt(sn3(i))) ; ...
+                            (corr_2.*sqrt(sn1(i)).*sqrt(sn3(i)))  (corr_3.*sqrt(sn2(i)).*sqrt(sn3(i)))   sn3(i)    ])   ;
+end

### 2018-09-07 phil_matlab/generate_controls.m

@@ -19,10 +19,21 @@ controls_gen = controls(1:3);
     
     CC = zeros(size(CONTROL,1),1);    %%%%%%%%%%%%% SE %%%%%%%%%%%%%
     for i = 1:controls_gen(2)
-       pct = ( i./controls_gen(2) ).*100;
+       pct = ( i./controls_gen(2) ).*100 ; %%%%% KEY!!! 
        CC = CC +  ( PRC(pct,Q_obs,t)==1 ) ;
     end
     SE = dummyvar(CC);
+    
+    %SE = [ones(size(CONTROL,1),1) (ones(size(CONTROL,1),1) - PRC(60,Q_obs,t)==1 )];
+    
+    %UB = 10;
+    %SE = [ones(size(CONTROL,1),1)  (PRC(UB,Q_obs,t)==1)  (ones(size(CONTROL,1),1) - PRC(100-UB,Q_obs,t)==1 ) ];
+    %SE = ones(size(CONTROL,1),1);
+    %SE = [ones(size(CONTROL,1),1)  (PRC(10,Q_obs,t)==1)  (ones(size(CONTROL,1),1) - PRC(40,Q_obs,t)==1 ) ];
+    %SE = [ones(size(CONTROL,1),1)  (PRC(10,Q_obs,t)==1) ((PRC(20,Q_obs,t)==1) - (PRC(10,Q_obs,t)==1)) ((PRC(30,Q_obs,t)==1) - (PRC(20,Q_obs,t)==1))  (ones(size(CONTROL,1),1) - PRC(50,Q_obs,t)==1 ) ];
+    
+    SE = [ones(size(CONTROL,1),1)  (PRC(10,Q_obs,t)==1)  (ones(size(CONTROL,1),1) - PRC(60,Q_obs,t)==1 ) ];
+
     
     if SHH_control>0
        SE = [SE (round(CONTROL(:,2))==2) (round(CONTROL(:,2))==3)];
@@ -32,7 +43,7 @@ controls_gen = controls(1:3);
         D = ones(size(CONTROL,1),1); %%%%%%%%%%%%%%%%%%%%%% D %%%%%%%%%%%
     if controls_gen(3)>=3
         D =[ones(size(CONTROL,1),1) ...
-            (CONTROL(:,1)>prctile(CONTROL(:,1),33) & CONTROL(:,1)<prctile(CONTROL(:,1),67))...
[…]

### 2018-09-07 phil_matlab/graph_main.m

@@ -1,0 +1,171 @@
+%{
+function h = graph_main(print,tag,mac,size_smp,...
+                    fileID,est_version,controls,control_size,ph_controls,given,...
+                    a_start,sto,reps,...
+                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                    real_data,TUNE,boot_max,boot_estimates,alt_sample,...
+                    PH_COUNTER,group_percentile,COST_INPUTS,c_dir)
+%}
+
+%%% OLD NAME: graph_time_v4_groups.m
+
+
+%%%%%% KEY : SET PH_COUNTER = ?
+
+
+h =1;
+
+est_opt=0;
+BOOT=[];
+
+[x1,given,moments,smm_est_option,...
+                input1s,input2s,input3s,...
+                errors1s,errors2s,errors3s,...
+                SIG_EP_INPUTS,reps,sto,alt_error,...
+                sort_condition,split_F_option,transfer_option,TUNE]=...
+est3(print,tag,mac,size_smp,...
+                    fileID,est_version,controls,control_size,ph_controls,given,...
+                    a_start,sto,reps,...
+                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,cd_dir);
+
+if mac==1
+    table_pre= 'tables/';
+else
+    table_pre= 'tables\';  
+end
+
+%%%%%%%%%%%%%%% SETTINGS FROM SIM PRINT ! %%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%% SETTINGS FROM SIM PRINT ! %%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%% SETTINGS FROM SIM PRINT ! %%%%%%%%%%%%%%%
+
+%%% TEMP SET !!
+group_percentile = 50;
+
+                sub_sample = .05   ;
+
+                groups     = [  group_percentile  group_percentile  ];
+                sort_condition=0;
+                split_F_condition=0;
+                transfer_option=1;
+            
+    capital_real = 0;
+    PH_COUNTER   = []  ;   
+    income_opt   = 0   ;
+
+    
+        TRIALS = 50  + 1;            
+if isempty(PH_COUNTER)~=1
+    if income_opt==0
+        F_MIN = -50;
+        F_MAX = 400;
+        start_value = [  5 15  ] ;
+    else
[…]

### 2018-09-07 phil_matlab/graph_maker_full_V3.m

@@ -1,0 +1,167 @@
+function [solutions1, choices1, mean_utility1, F_MAX1, SOL_MAX1, sharing1, US_TOTAL] = graph_maker_full_V3(F_GRID,TRIALS,groups,...
+                    alternative_parameters,...
+                                    input1sub,input2sub,input3sub,...
+                                    errors1sub,errors2sub,errors3sub,...
+                                    SIG_EP_INPUTS,reps,sto,...
+                                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                                    COST_PARAMETERS,PH_COUNTER,TUNE,alt_errorsub,start_value,income_opt)
+
+          %     F_GRID=500;
+            %    TRIALS=1;
+            
+    SL=3;
+
+solutions1=zeros(TRIALS,1);
+choices1=zeros(TRIALS,SL); 
+mean_utility1=zeros(TRIALS,SL);
+sharing1=zeros(TRIALS,SL);
+US_TOTAL=zeros(TRIALS,1);
+
+for r=1:TRIALS
+ 
+%{
+    r=1
+    F_GRID = -100
+%}
+    
+    given_p = F_GRID(r);
+    obj=@ (a_start)  smm_shell_counterfactual_v3(  a_start, given_p, alternative_parameters,...
+                                    input1sub,input2sub,input3sub,...
+                                    errors1sub,errors2sub,errors3sub,...
+                                    SIG_EP_INPUTS,reps,sto,...
+                                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                                    COST_PARAMETERS,PH_COUNTER,TUNE,alt_errorsub);
+
+
+ %{
+                                                    
+psol_temp = fminsearch(obj,40)
+obj(psol_temp)
+a_low=0;
+a_high=50;
+V=10;
+av=((1:V)'./V).*(a_high-a_low) + a_low;
+OBJ=ones(V,1);
+for vv = 1:V
+     ot=obj(av(vv,1));
+     OBJ(vv,1)=ot;
+end
+plot(av,OBJ)
+          
+%}                               
+                                
+                                
+%tic
+%threshold=.0001;
+%start_value = [-30 -20 -10 0 5 10 20 30 ];
+%start_value = [ 5 15 ];
[…]

### 2018-09-07 phil_matlab/graph_time_v4_group_comparison_graph.m

@@ -4,7 +4,7 @@ function h = graph_time_v4_group_comparison_graph(print,tag,mac,size_smp,...
                     a_start,sto,reps,...
                     sort_condition,split_F_option,transfer_option,smm_est_option,...
                     real_data,TUNE,boot_max,boot_estimates,alt_sample,...
-                    PH_COUNTER,group_percentile,COST_INPUTS,c_dir)
+                    PH_COUNTER,group_percentile,COST_INPUTS,cd_dir)
 %}
 
 
@@ -179,7 +179,7 @@ plot( PH_SET , PEQ./max(PEQ), ...
 
 
 
-%dlmwrite(strcat(cd_dir,table_pre,'tpt_graph_full.csv'),[PH_SET' PEQ FEQ CON SHR],'delimiter',',','precision',15);
+dlmwrite(strcat(cd_dir,table_pre,'tpt_graph_full.csv'),[PH_SET' PEQ FEQ CON SHR],'delimiter',',','precision',15);
 
 
 %plot(F_GRID(:,1),mean_utility1(:,2))

### 2018-09-07 phil_matlab/main.m

@@ -4,23 +4,24 @@
 
     %{a
     
-
+%%%% FOR ESTIMATION OPTION IS OFF !!!   [ just in case, to save time.. ]
     
 clear;
 rng(1);
     
 print                   = 1;  %%% $$$ DEFAULT OPTIONS
-est_version             = 10;
+est_version             = 11;
 tag                     = 'v1';
 tag_g                   = 'v1';
 only_alpha              = 0;
 mac                     = 1 ;
 moffitt                 = 1 ;    % 0: standard % 1: norm added
 control_size             = 10;
-est_title               = ' try 2000 '; 
+est_title               = ' now run it '; 
 
 cd '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_code/phil_matlab/';
 cd_dir  = '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_generated/';
+cd_out  = '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_code/phil_paper/'; % most add tables anyways..
 %%% $$$  PERFECT VARIATION OPTIONS
 perf_var                = 0;
         Q_obs_range     = [10 80];
@@ -28,11 +29,14 @@ perf_var                = 0;
         i               = 200;
         reps            = 100;
 
-controls        = [3  5  9    9   2]; % [sig_ep sig_nu alpha other_controls(1 is hhsize, 2 is SHH)  SHH_control(0:off 2:on!)]
+%controls        = [3  5  9    9   2]; % [sig_ep sig_nu alpha other_controls(1 is hhsize, 2 is SHH)  SHH_control(0:off 2:on!)]
+
+controls        = [3  3  9    9   2  ]; % [sig_ep sig_nu alpha other_controls(1 is hhsize, 2 is SHH)  SHH_control(0:off 2:on!)]
+
 
 %%% $$$  REAL DATA OPTIONS
 real_data               = 1; % first: controls data, second: controls random subsample
-        sample   = [   1    0    0   1  ]; % standard rts rtc  GROUP
+        sample   = [   1    0    0   0  ]; % standard rts rtc  GROUP
         size_smp = [   5000    0   0    ];
 %%% $$$ STARTING VALUES
         TUNE = 1; %% set linear tuning parameter
[…]

### 2018-09-07 phil_matlab/tp3_stepwise_groups.m

@@ -1,0 +1,153 @@
+function h = tp3_stepwise_groups(a, stepsize, iterations, alternative_parameters,...
+                                    input1sub,input2sub,input3sub,...
+                                    errors1sub,errors2sub,errors3sub,...
+                                    SIG_EP_INPUTS,reps,sto,...
+                                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                                    COST_PARAMETERS,PH_COUNTER,TUNE,alt_errorsub, groups,mac,tagline, LOW,cd_dir)
+
+                                
+                                
+                       
+%{
+LOW      = 1; 
+a        = tpt1;
+LOW      = 0;
+a       =  tpt0;
+%a = [1050 2];                                    
+stepsize = [2 .5];
+iterations   =  3;
+%}
+
+                                    
+compression  = .95;
+
+%%% OUTPUTS : TU and PRICES
+Z   = iterations ;
+NR  = zeros(Z,4);
+US  = zeros(Z,4);
+FEE = zeros(Z,4);
+P1  = zeros(Z,4);
+P2  = zeros(Z,4);
+GAP = zeros(Z,1);
+U_MAX = zeros(Z,1);
+NEW_STORE    = zeros(Z,3);
+MAX_ID_STORE = zeros(Z,1);
+
+    for z=1:Z
+        if z==1
+                GIVEN_P_START = [ a + stepsize.*[1 1]; ...
+                       a + stepsize.*[1 -1]; ...
+                       a + stepsize.*[-1 1]; ...
+                       a + stepsize.*[-1 -1] ];      
+        else
+                GIVEN_P_START = [ NEW + stepsize_NEW.*[1 1]; ...
+                       NEW + stepsize_NEW.*[1 -1]; ...
+                       NEW + stepsize_NEW.*[-1 1]; ...
+                       NEW + stepsize_NEW.*[-1 -1] ];  
+        end
+
+        for r = 1:size(GIVEN_P_START,1)
+
+                   GIVEN_P1 = GIVEN_P_START(r,:);
+
+                           obj =@(a1)  smm_shell_counterfactual_v3(  a1, GIVEN_P1, alternative_parameters,...
+                                        input1sub,input2sub,input3sub,...
+                                        errors1sub,errors2sub,errors3sub,...
[…]

### 2018-09-16 phil_paper/jmp_wjv_v2.tex
lots of good stuff

@@
 
-\begin{comment}
-
 Conventional pricing policies often rely on the assumption that each water connection serves a single household; however, many households in developing cities share with neighbors instead of purchasing their own connections.
@@
 Welfare impacts depend not only on heterogeneity in demand for water across the population, but also on costs associated with forming and maintaining water sharing relationships.
-To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2008 to 2015 with detailed survey data on the number of households and people using each water connection.
+To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2010 to 2015 with detailed survey data on the number of households and people using each water connection.
 With comprehensive geographic coverage of half of Manila and a variety of price variation, these data allow for a rich characterization of water demand.
@@
 Complete billing records for each water connection including the monthly meter reading, the total bill charged, and the precise location for each meter serve as the primary measure of quantity choices.
-These data span 2008 to 2015, during which connections grew from 800,000 to 1.5 million water connections, generating nearly 100 million transaction records.
+These data span 2010 to 2015, during which connections grew from 800,000 to 1.5 million water connections, generating nearly 100 million transaction records.
 Connections are divided into residential (90\%), semi-business (4\%), commercial (5\%), and industrial (1\%).
@@
 \caption{Demand Estimates}\label{table:demandestimates}
-\input{tables/step_1_estimates_paper} \\
+\input{tables/step_1_estimates_group} \\
 \vspace{.1cm}
-{\footnotesize{Total Observations:  473,114   Total Connections:  10,239} }
+{\footnotesize{Total Observations:  349,265   Total Connections:  7,151} }
 \end{table}
@@
 \vspace{.5cm}
-{\footnotesize Total Observations:  473,114   Total Connections:  10,239 \\
+{\footnotesize Total Observations:  349,265   Total Connections:  7,151 \\
 Standard errors are bootstrapped at the connection level.}
@@
 \input{tables/corr_table_group}\\
-\vspace{.3cm}
-\footnotesize{1 indexes correlations with first movers \\ while 2 indexes correlations with second movers}
+%\vspace{.3cm}
+%\footnotesize{1 indexes correlations with first movers \\ while 2 indexes correlations with second movers}
 \end{table}
@@
 The hassle cost is estimated to be \input{tables/mean_hassle}PhP per cubic meter of usage, which is approximately \input{tables/hassle_percentage}\unskip\% of the average tariff.
-With only 1,247 connections that experience leaks, the estimation recovers wide standard errors for this estimate, rejecting a hassle cost of zero with 10\% confidence.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  These results suggest that the time-costs or other physical challenges transporting water to share with a neighbor may play an important role in the extent to which households choose to use water from a neighbor's tap.
+With only 548 connections that experience leaks, the estimation recovers wide standard errors for this estimate.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  These results suggest that the time-costs or other physical challenges transporting water to share with a neighbor may play an important role in the extent to which households choose to use water from a neighbor's tap.
+
+%, rejecting a hassle cost of zero with 10\% confidence
 
@@
 \caption{Hassle Cost Estimates}\label{table:step2estimates}
-\input{tables/step_2_estimates} 
+\input{tables/step_2_estimates} \\
 \vspace{.2cm} 
-\footnotesize{Leaking Connections:  1,247,   Neighboring Connections:  5,239,  Total Obs:  36,662  \\ Standard errors are bootstrapped at the leaking connection-neighborhood level.  \\
-Appendix~\ref{appendix:hasslecostbootstrap} includes more details on the bootstrapping procedure.}
-\end{table}
+\footnotesize{Leaking Connections:  548,   Neighboring Connections:  2,151,   Total Obs:  20,299  \\ Standard errors are bootstrapped at the leaking connection-neighborhood level. }
+\end{table}
+
+\begin{table}
+\centering
+\caption{Predicted Hassle Cost Distribution}\label{table:step2histogram}
+\includegraphics[scale=.7]{tables/hassle_cost_distribution.pdf} \\
+%\vspace{cm}
+\footnotesize{Excludes top and bottom 1\% outliers}
+\end{table}
+
+%Appendix~\ref{appendix:hasslecostbootstrap} includes more details on the bootstrapping procedure.
 
@@
 
-Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from 5,000 connections to 6,984 households.
+Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from \input{tables/totalhhsmm_group} connections to  households.
 
@@
 \vspace{.05cm}
-\footnotesize{ Standard errors are bootstrapped at the connection level.  Total Households:  6,984  }
-\end{table}
-
-Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee}PhP monthly fixed fee paid the provider.
+\footnotesize{ Standard errors are bootstrapped at the connection level.  Total Households:  \input{tables/totalhhsmm_group}  }
+\end{table}
+
+Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee_group}PhP monthly fixed fee paid the provider.
 This finding suggests that households face sizable barriers to connecting to the water network such as maintenance land tenure insecurity, or administrative costs.
@@
 \caption{Reduced Form: Connection Fee Discount}\label{figure:discountreducedform}
-\includegraphics[scale=.57]{tables/diff_595_untreated.pdf}
-\includegraphics[scale=.57]{tables/diff_595_treated.pdf}
+\includegraphics[scale=.8]{tables/diff_595.pdf}
+%\includegraphics[scale=.57]{tables/diff_595_treated.pdf}
 \end{figure}
@@
 Since utility is assumed to be quasi-linear, consumer welfare is reported in PhP/month.
-Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile}\unskip\% of users.
+Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile_group}\unskip\% of users.
 
@@
 \caption{Mobile and PAWS Water Source Choices}\label{table:pollfishpawsmeans}
-\input{tables/pollfish_paws_means_1} 
+\input{tables/pollfish_paws_means} 
 \vspace{.3cm}
@@
 \caption{Mobile and PAWS Descriptives by Water Sharing Status}\label{table:pollfishpawssharing}
-\input{tables/pollfish_paws_diff_1}
+\input{tables/pollfish_paws_diff}
 \end{table}
@@
 
+\section{Descriptive for Estimation Sample}\label{appendix:descriptivesest}
+
+\begin{table}
+\caption{Descriptives for Estimation Sample}
+\begin{center}
+\input{tables/new_descriptives_est_sample}
+\end{center}
+\end{table}
+
 \section{Price Variation}\label{appendix:pricevariation}
@@
 \begin{center}
-\includegraphics[scale=.7]{tables/tariff_structure_2.pdf}\\
+\includegraphics[scale=.7]{tables/consumption_histogram.pdf}\\
 \footnotesize{Consumption values are truncated at 60 to highlight bunching at kink points.}
@@
 This figure indicates time series variation in prices as a result of the government regulator raising prices incrementally to ensure production costs are covered.
-
+\begin{figure}
+\caption{Regulated Tariff Changes}\label{figure:regulatedtariffchanges}
 \begin{center}
-\includegraphics[scale=.65]{tables/tariff_time_series.pdf}
+\includegraphics[scale=.7]{tables/tariff_time_series.pdf}
 \end{center}
+\end{figure}
 
@@
 \caption{Summary Statistics and Comparison of Means for Residential, Semi-Business, and Upgraded Connections}\label{table:semittests}
-\input{tables/sem_compare_means1}\\
+\resizebox{\textwidth}{!}{  
+\input{tables/sem_compare_means}
+}\\
 \footnotesize{Data are from the connection survey.}
@@
 \caption{Descriptives and Balance Test for Non-Leaking and Leaking Connections}\label{table:leakbalance}
-\input{tables/mean_diff_leak1} \\
+\input{tables/mean_diff_leak} \\
 \footnotesize{Drink is a dummy for drinking tap water.
@@
 \caption{Balance Test for Disconnection among Leaking Connections}\label{table:leakbalancedc}
-\input{tables/mean_diff_DC1.tex} \\
+\input{tables/mean_diff_DC.tex} \\
 \footnotesize{Drink is a dummy for drinking tap water.
@@
 
-\section{Bootstrapping Procedure for Hassle Cost}\label{appendix:hasslecostbootstrap}
-
-The bootstrapping procedure resamples at the level of full neighborhoods including both leaking connection and the neighboring connections, which treats each ``leak'' as its own cluster.
+%\section{Bootstrapping Procedure for Hassle Cost}\label{appendix:hasslecostbootstrap}
+
+%The bootstrapping procedure resamples at the level of full neighborhoods including both leaking connection and the neighboring connections, which treats each ``leak'' as its own cluster.
 In a small number of bootstrapped samples ($<5\%$), the estimation procedure for this step converges to extreme outliers; this is because these samples have a relatively high share of households choosing zero monthly consumption, which are difficult values for the model to fit.
@@
 \begin{table}
+
 \centering
@@
 \end{appendices}
-
-\end{comment}
 

### 2018-09-16 phil_matlab/data_prep_bg.m

@@ -31,7 +31,7 @@ function [t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,gamma,x,CONTROL,CONTROL_PH,beta_O,
             gindex=csvread(strcat(cd_dir,'BOOT',slash,'gBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
             %gindex=gindex(:,BOOT(1));
             [~,~,iB,t] = boot_testing_2(g-1,t,gindex);
-            X          = csvread(strcat(cd_dir,'post_',tag_g,'.csv'),1,0, [ 1 0 max(iB) (6+control_size) ]);
+            X          = csvread(strcat(cd_dir,'post_',tag_g,'.csv'),1,0, [ 1 0 max(iB) (6+control_size+4) ]);
             X = X(iB,:);
             %x_pre=csvread(strcat('xBOOT',num2str(est_version),'.csv'));
             x=csvread(strcat(cd_dir,'BOOT',slash,'xBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));

### 2018-09-16 phil_matlab/data_prep_smm_grouping_v2.m

@@ -38,9 +38,7 @@ end
     end
     
     
-    %X          = csvread(strcat(cd_dir,'standard_',tag,'.csv'),1,0, [ 1 0 sum(t) (4+control_size+3) ]);
-    %%% ADD PH CONTROLS
-    X          = csvread(strcat(cd_dir,'standard_',tag,'.csv'),1,0, [ 1 0 sum(t) (4+control_size+3+2) ]);
+    %X          = csvread(strcat(cd_dir,'standard_',tag,'.csv'),1,0, [ 1 0 sum(t) (4+control_size+3+2) ]);
     
     
     if isempty(BOOT)~=1
@@ -54,6 +52,8 @@ end
         %t=csvread(strcat('tBOOT',num2str(est_version),'.csv'));        
         %t=csvread(strcat('BOOT\tBOOT',num2str(est_version),'_',num2str(BOOT(1)),'.csv'));
         %t=t(:,BOOT(1));
+    else
+        X          = csvread(strcat(cd_dir,'standard_',tag,'.csv'),1,0, [ 1 0 sum(t) (4+control_size+3+2) ]);
     end
     
  %   xa =grpstats(X,repelem((1:length(t))',t,1));

### 2018-09-16 phil_matlab/est1.m

@@ -22,6 +22,12 @@ else
     SHH_control=0;
 end
 
+SIG_GUESS = 0;
+if length(TUNE)>1
+   SIG_GUESS = TUNE(2);
+   TUNE = TUNE(1);
+end
+
 %%% REAL DATA OPTION
 if length(real_data)>1
     RLENGTH=real_data(2);
@@ -66,7 +72,15 @@ if real_data~=1
     Q_obs=moffitt_prep_norm_med_VAR_tune(t,k_1,k_2,k_3,p_1,p_2,p_3,p_4,...
                 gamma,SIG_NU,SIG_EP,ALPHA_1,TUNE);
 end
-    obj = @(a)est_nmid_general_tune(a,t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,D,SE,CA,control_id,TUNE);
+	if SIG_GUESS==1
+                obj = @(a)est_no_mid_general_tune(a,t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,D,SE,CA,control_id,TUNE);    
+	elseif SIG_GUESS==2
+                obj = @(a)est_full_mid_general_tune(a,t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,D,SE,CA,control_id,TUNE);   
+	else
+                obj = @(a)est_nmid_general_tune(a,t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,D,SE,CA,control_id,TUNE);                
+	end
+    %obj = @(a)est_nmid_general_tune(a,t,Q_obs,k_1,k_2,k_3,p_1,p_2,p_3,p_4,D,SE,CA,control_id,TUNE);
+
 
 
     TRUTH = [ sig_ep sigma_1 alpha_1 gamma1 ];

### 2018-09-16 phil_matlab/first_best_graph.m

@@ -21,7 +21,7 @@ est3(print,tag,mac,size_smp,...
                     fileID,est_version,controls,control_size,ph_controls,given,...
                     a_start,sto,reps,...
                     sort_condition,split_F_option,transfer_option,smm_est_option,...
-                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,cd_dir);
+                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,many_sv_smm,cd_dir);
 
                 
                 

### 2018-09-16 phil_matlab/fixed_cost_discount_groupings_v1.m

@@ -28,9 +28,9 @@ est3(print,tag,mac,size_smp,...
                     fileID,est_version,controls,control_size,ph_controls,given,...
                     a_start,sto,reps,...
                     sort_condition,split_F_option,transfer_option,smm_est_option,...
-                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,cd_dir);
+                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,many_sv_smm,cd_dir);
 
- PH_COUNTER = [];
+ PH_COUNTER = [1200];
     MARGINAL_COST   = COST_INPUTS(1);
     CONNECTION_COST = COST_INPUTS(2);
     

### 2018-09-16 phil_matlab/graph_time_v4_group_comparison_graph.m

@@ -31,7 +31,7 @@ est3(print,tag,mac,size_smp,...
                     fileID,est_version,controls,control_size,ph_controls,given,...
                     a_start,sto,reps,...
                     sort_condition,split_F_option,transfer_option,smm_est_option,...
-                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,cd_dir);
+                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,many_sv_smm,cd_dir);
 
 
                             

### 2018-09-16 phil_matlab/incidental_print.m

@@ -1,0 +1,10 @@
+function h = incidental_print(var_name,r,Tstep1_v1,Estep1_v1,Estep1_v2,fileID)
+
+fprintf(fileID,'%s\n',strcat(var_name,'&', ...
+                            num2str(Tstep1_v1(r),'%5.2f'),'&',...
+                            num2str(Estep1_v1(r),'%5.2f'),'&',...
+                            num2str((Estep1_v1(r)-Tstep1_v1(r))./Tstep1_v1(r),'%5.2f'),'&',...
+                            num2str(Estep1_v2(r),'%5.2f'),'&',...
+                            num2str((Estep1_v2(r)-Tstep1_v1(r))./Tstep1_v1(r),'%5.2f'),'\\'));
+                        
+                        h=1;

### 2018-09-16 phil_matlab/num2bankScalar.m

@@ -1,0 +1,26 @@
+function [str]=num2bankScalar(num)
+
+     num=floor(num*100)/100;
+
+     str = num2str(num);
+
+     k=find(str == '.', 1);
+
+     if(isempty(k))
+
+         str=[str,'.00'];
+
+     end
+
+     FIN = min(length(str),find(str == '.')-1);
+
+     for i = FIN-2:-3:2
+
+     str(i+1:end+1) = str(i:end);
+
+     str(i) = ',';
+
+     end
+
+     str = str(1:end-3);
+end

### 2018-09-16 phil_matlab/sim_build_counterfactual_out_of_sample_groupings_v1.m

@@ -1,0 +1,223 @@
+function [h] = sim_build_counterfactual_out_of_sample_groupings_v1(print,tag,mac,size_smp,...
+                    fileID,est_version,controls,control_max,ph_controls,given,...
+                    a_start,sto,reps,...
+                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                    real_data,TUNE,boot_max,boot_estimates,alt_sample,income_opt,group_percentile,COST_INPUTS,cd_dir,cd_out)
+
+                
+                
+                income_opt=0;
+                
+est_opt=0;
+BOOT=[];
+
+[x1,given,moments,smm_est_option,...
+                input1s,input2s,input3s,...
+                errors1s,errors2s,errors3s,...
+                SIG_EP_INPUTS,reps,sto,alt_error,...
+                sort_condition,split_F_option,transfer_option,TUNE]=...
+est3(print,tag,mac,size_smp,...
+                    fileID,est_version,controls,control_size,ph_controls,given,...
+                    a_start,sto,reps,...
+                    sort_condition,split_F_option,transfer_option,smm_est_option,...
+                    real_data,TUNE,BOOT,boot_max,boot_estimates,est_opt,many_sv_smm,cd_dir);
+
+                
+                        
+ PH_COUNTER = [];
+    MARGINAL_COST   = COST_INPUTS(1);
+    CONNECTION_COST = COST_INPUTS(2);
+    
+    
+    %{
+        MARGINAL_COST = 5;
+        CONNECTION_COST=150;
+        PH_COUNTER=[];  
+    %}
+        % COST_PARAMETERS:    MARGINAL_COST                CONNECTION_COST  F_ADDITIONAL             CAPITAL  
+        
+  %  p_3/p_4
+  %  a = 0 ;
+                % F_PAY  p_1/p_2
+    GIVEN_P = [  CONNECTION_COST 0  ]; % payment is equal to cost!
+                              % FA    PA etc.
+    alternative_parameters =  x1(2:end)' ;
+    
+                  [~,~,~,~,CAPITAL]   = smm_shell_counterfactual_v3(  0 ,GIVEN_P, alternative_parameters,...
+                                    input1s,input2s,input3s,...
+                                    errors1s,errors2s,errors3s,...
[…]

### 2018-09-16 phil_matlab/table_appendix_incidental_parameters.m

@@ -1,0 +1,64 @@
+function h = table_appendix_incidental_parameters(mac,est_version1,est_version2)
+
+
+mac=1;
+est_version1=388;
+est_version2=389;
+
+
+
+if mac==1
+    slash = '/';
+else
+    slash = '\';
+end
+
+% obs : 5000 hhs
+% time periods : 38 months, around half!
+
+Tstep1_v1=csvread(strcat('tables',slash,'TRUTHp_step1_',num2str(est_version1),'.csv'))
+Estep1_v1=csvread(strcat('tables',slash,'ESTp_step1_',num2str(est_version1),'.csv'))
+Estep1_v2=csvread(strcat('tables',slash,'ESTp_step1_',num2str(est_version2),'.csv'))
+
+Tstep2_v1=csvread(strcat('tables',slash,'TRUTH_step2_',num2str(est_version1),'.csv'))
+Estep2_v1=csvread(strcat('tables',slash,'ESTp_step2_',num2str(est_version1),'.csv'))
+Estep2_v2=csvread(strcat('tables',slash,'ESTp_step2_',num2str(est_version2),'.csv'))
+
+Tstep3_v1=csvread(strcat('tables',slash,'TRUTH_step3_',num2str(est_version1),'.csv'))
+Estep3_v1=csvread(strcat('tables',slash,'ESTp_step3_',num2str(est_version1),'.csv'))
+Estep3_v2=csvread(strcat('tables',slash,'ESTp_step3_',num2str(est_version2),'.csv'))
+
+
+
+
+HLINE=0;
+
+fileID = fopen(strcat('tables',slash,'incidental_parameters.tex'),'w');
+
+fprintf(fileID,'%s\n','\begin{tabular}{|lccccc|}');
+fprintf(fileID,'%s\n','\hline');
+fprintf(fileID,'%s\n','Parameter & True Value & Est: Full T & (\% Diff)  & Est: 50\% T & (\% Diff) \\');
+fprintf(fileID,'%s\n','\hline');
+fprintf(fileID,'%s\n','\hline');
+
+
+%%%%%%% ALPHA! (PUT MORE IN AND DESCRIBE THEM)
+
+[~] = incidental_print('$\sigma_{\epsilon}$',1,Tstep1_v1,Estep1_v1,Estep1_v2,fileID);
[…]

### 2018-09-16 phil_matlab/table_step_1_estimates.m

@@ -1,0 +1,149 @@
+function h=table_step_1_estimates...
+    (est_version,tag,tag_g,controls,sample,size_smp,boot_max,mac,cd_out,cd_dir)
+
+% generate step 1 estimates
+
+if length(controls)>=4
+    control_size=controls(4);
+else
+    control_size=1;
+end
+if length(controls)>=5
+    SHH_control=controls(5);
+else
+    SHH_control=0;
+end
+
+%t = data_prepc_v4(est_version,sample,size_smp,mac,tag,control_size,0,[]);
+t = data_prep(est_version,sample,size_smp,tag,tag_g,control_size,0,[],cd_dir);
+
+OBS=sum(t);
+HH=length(t);
+
+%R_to_S=size_smp(2);
+
+if mac==1
+    slash='/';
+else
+    slash='\';
+end
+
+X_ORIGINAL = csvread(strcat(cd_dir,slash,'results',slash,'x',num2str(est_version),'.csv'));
+X_ORIGINAL = X_ORIGINAL(1:sum(controls(1:3)+SHH_control));
+
+X = csvread(strcat(cd_dir,'BOOT',slash,'xBOOT',num2str(est_version),'_',num2str(1),'.csv'));
+X = X(1:sum(controls(1:3)+SHH_control));
+for i = 2:boot_max
+       x_r = csvread(strcat(cd_dir,'BOOT',slash,'xBOOT',num2str(est_version),'_',num2str(i),'.csv'))  ;
+   X   = [X(1:sum(controls(1:3))+SHH_control,:) x_r(1:sum(controls(1:3))+SHH_control)]            ;
+end
+
+Xmean=mean(X_ORIGINAL,2);
+Xstd=std(X,0,2);
+
+as = 2; %%% Deals with fewer controls since the sig nu reduction
+
+fileID = fopen(strcat(cd_out,'tables/step_1_estimates_group.tex'),'w');
+
+
+fprintf(fileID,'%s\n','\begin{tabular}{lcc}');
+fprintf(fileID,'%s\n','& Estimate & Standard Error \\');
+fprintf(fileID,'%s\n','Price Sensitivity : $\alpha$ & \multicolumn{2}{c}{}\\');
+fprintf(fileID,'%s\n','\hline');
+%fprintf(fileID,'%s\n','\hline');
+
+
[…]

### 2018-09-17 phil_paper/jmp_wjv_v2.tex
lots of good updates

@@
 Households that own a connection in the connection survey are similar to households connected to the piped water network in the Census data.
-To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 8 regions of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.\footnote{Regions are chosen to overlap with village administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}
+To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 8 regions of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.\footnote{Regions are chosen to overlap with ward administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}
 
@@
 
-With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors with each of the 8 geographic regions.
+With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors with each of the 599 geographic regions.
 The routine then orders households in the sequential game according to their utilities from using an individual connection.
@@
 \input{tables/oos_discount_estimates_group} \\ 
-Consumer surplus is measured in PhP/month.
+\footnotesize{Consumer surplus is measured in PhP/month.}
 \end{table}
@@
 	\footnotesize{Low Users include the bottom 50\% of water users. \\
-	Surplus is measured in terms of PhPd/month.}
+	Surplus is measured in terms of PhP/month.}
 \end{table}
@@
 \footnotesize{The data include connection survey data on households owning water connections \\ as well as 2010 Census data on households.
-This sample includes overlapping villages between surveys (67\%)}
+This sample includes \\ overlapping wards between  surveys (67\%)}
 \end{table}
@@
 \caption{Mobile and PAWS Water Source Choices}\label{table:pollfishpawsmeans}
-\input{tables/pollfish_paws_means} 
+\input{tables/pollfish_paws_means} \\
 \vspace{.3cm}
@@
 
-\begin{table}
-\caption{Descriptives for Estimation Sample}
+Table~\ref{table:descriptivesestsample} provides descriptive statistics for the connection-level sample used in the simulated method of moments estimation.
+Demographic variables are expressed in terms of dummy variables capturing various features that might drive demand for water.
+Ward-level attributes include features that determine hassle-costs of sharing with a neighbor.
+The sample includes a random sample of 5,000 connections combined with a sample of unconnected households in order to ensure a representative sample of the population of households.
+
+\begin{table}
+\caption{Descriptives for Estimation Sample}\label{table:descriptivesestsample}
 \begin{center}
@@
 
+\section{Simulated Method of Moments Model Fit}\label{appendix:modelfit}
+
+By weighting the first three moments highly, the model almost exactly matches moments shown in Table~\ref{table:modelfit}.
+The model is also able to match the direction but predicts stronger correlations with fixed preferences for water $\beta_i$ and percent owning connections and percent using from a neighbor.
+One interpretation is that there may be other factors besides simply water preferences and heterogeneity in hassle costs that are driving source decisions.
+The model has difficulty matching correlation between fixed preferences and share using from vendors, which may be partially due to noise generated in the process of projecting fixed preferences.
+
+\begin{table}
+\centering
+\caption{Simulated Method of Moments Model Fit}\label{table:modelfit}
+\input{tables/smm_moments}
+\end{table}
+
 \end{appendices}

### 2018-09-17 phil_matlab/main.m

@@ -107,9 +107,9 @@ end
 
 
 
-for i = 26:60
+%for i = 51:60
 
-   BOOT = [i]
+%   BOOT = [i]
 
                 %{
 [~]=est1(print,tag,tag_g,mac,sample,size_smp,...
@@ -130,7 +130,7 @@ for i = 26:60
                     sort_condition,split_F_option,transfer_option,smm_est_option,...
                     real_data,TUNE,BOOT,boot_max,boot_estimates,ESTIMATION_OPTION,many_sv_smm,cd_dir);
                 %} 
-end
+%end
 
 
 %%%% DO THE COUNTERFACTUALS HERE PLEASE !
@@ -174,10 +174,12 @@ end
 
 % 4. full ph counterfactuals: graph_time_v4_group_comparison_graph.m
 
+
 %%% print welfare outputs: tables_print_welfare_facts_groupings.m
 
-
 %%% print counterfactual parameters: sim_build_counterfactual_out_of_sample_groupings_v1.m
+
+
 
 %%% ROBUSTNESS
 

### 2018-09-19 phil_paper/jmp_wjv_v2.tex
lots of good little fixes here

@@
 By roughly matching the smoothness of the distributions especially across price thresholds, this model improves on standard models in the literature, which often predict excessive bunching at thresholds (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).
-The model has difficultly rationalizing low levels of consumption likely because households face zero prices below this threshold.\footnote{Since preference and consumption shocks are assumed to be normally distributed, the model predicts a handful of negative consumption values.
-In the counterfactual exercises, I round these negative realizations to zero consumption.}  Likewise, the model also cannot account for bunching at zero (likely capturing households that go on vacation).
+The model has difficultly rationalizing low levels of consumption likely because households face zero prices below this threshold.
+Since preference and consumption shocks are assumed to be normally distributed, the model predicts some negative consumption values.
+In the counterfactual exercises, I round these negative realizations to zero consumption.
+Likewise, the model also cannot account for bunching at zero (likely capturing households that go on vacation).
 The model also predicts greater bunching around the upper price threshold despite little observed bunching in the data as large users tend to ignore this smaller jump in price.
 
-Table~\ref{table:correstimates} presents correlation estimates decomposed from the standard deviation terms.
-Both $\epsilon$ and $\eta$ shocks demonstrate negative correlations between neighbors for both first-movers and second-movers.
+Table~\ref{table:correstimates} presents correlation estimates decomposed from the consumption and preference shocks.
+Both the consumptions shocks, $\epsilon$ and preference shocks, $\eta$ demonstrate negative correlations between neighbors for owners and buyers.
 This finding suggests that neighboring households may intentionally form sharing relationships with whom their shocks are negatively correlated.
@@
 \caption{Correlation Estimates}\label{table:correstimates}
-\input{tables/corr_table_group}\\
+\input{tables/corr_table_group}
 %\vspace{.3cm}
@@
 This section details how exogenous interruptions in water connections caused by leaks combine with billing records to provide a measure of hassle costs of sharing water.
-The estimation strategy compares a connection's demand before disconnection to the change in demand among neighboring connections after disconnection (as a result of sharing), attributing the extent to which neighbors may not fully offset their consumption to the hassle cost, $p_h$.
+The estimation strategy compares a connection's demand before disconnection to the change in demand among neighboring connections after disconnection (as a result of sharing), attributing the extent to which neighbors may not fully offset their consumption to the hassle cost, $H_C$.
 Baseline preference parameters for both disconnecting connections and their neighbors are estimated in the procedure from Section~\ref{section:preferenceestimation}.
-Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $p_h$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).
-
-I now describe how the estimation sample is constructed.
-In 36 months, the water provider received 106,171 complaints of excessive billing --- 34,927 of which can be precisely identified as underground pipe leaks along the service pipe through a text analysis of call transcripts.
-These complaints do not appear to be spatially correlated with only a handful of leaks occurring among neighbors in the 36 months.
+Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $H_C$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).
+
+Leveraging this variation requires identifying a sample of leaking connections, the timing of leaks/disconnection, and usage for neighboring connections.
+In 36 months, the water provider received 106,171 consumer complaints of excessive billing --- 34,927 of which can be precisely identified as underground pipe leaks along the service pipe through a text analysis of call transcripts.
+These complaints do not appear to be spatially correlated with only a handful of leaks occurring among direct neighbors.
 I consider any call identified as an excessive billing complaint as a leak.
@@
 
-This analysis requires the assumption that the hassle cost, $p_h$, is homogenous across all households.
-This assumption ensures that the hassle cost identified from the subset of leaking households can be extended to the population of households.
+To capture heterogeneity in the hassle cost, $H_C$ is parameterized as a linear function of two summary characteristics of local neighborhoods defined as wards.
+First, the share of single houses or apartment buildings in a neighborhood may increase the per-unit cost of sharing since the buildings often require longer informal pipe networks with possibly more maintenance costs as compared with duplexes.
+Second, the average distance between water meters in a neighborhood provides another useful proxy for the average distance that informal pipe networks may need to extend between households.
+Importantly, this distance measure does not account measure the physical distances between sharing partners or unconnected households.
+These omissions are likely to overestimate the average distance between all neighbors.
+Furthermore, areas with smaller physical distances are likely to increase observed sharing as well as the observed distance between meters, which would bias the estimates against finding heterogeneity in the hassle costs.
+Table~\ref{table:descriptivesestsample} in Appendix~\ref{appendix:descriptivesest} includes descriptive statistics for these two measures.
+
+One additional concern would be that households select into sharing relationships conditional on unobserved heterogeneity in sharing costs (not modeled here).
+Since households included in this quasi-experiment have selected into purchasing connections at baseline, they may face higher hassle costs compared to households that select into sharing.
+Therefore, this exercise may provide an upper-bound on hassle costs for the population.
+
+%his assumption ensures that the hassle cost identified from the subset of leaking households can be extended to the population of households.
 One concern may be that heterogenous hassle costs induce households to select into sharing relationships conditional on these costs.
@@
 Therefore, this exercise provides an upper-bound on hassle costs for the population.
-The mobile survey finds a range of sharing access from fetching with containers to using the same plumbing, which suggests that households face different hassle costs.
+
+%The mobile survey finds a range of sharing access from fetching with containers to using the same plumbing, which suggests that households face different hassle costs.
+
 The following additional assumptions are required to ensure that this empirical setting accurately captures the model described in Section~\ref{section:hasslemodel}.
@@
 
-Table~\ref{table:step2estimates} shows the estimation results for the hassle cost estimation.
-The hassle cost is estimated to be \input{tables/mean_hassle}PhP per cubic meter of usage, which is approximately \input{tables/hassle_percentage}\unskip\% of the average tariff.
-With only 548 connections that experience leaks, the estimation recovers wide standard errors for this estimate.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  These results suggest that the time-costs or other physical challenges transporting water to share with a neighbor may play an important role in the extent to which households choose to use water from a neighbor's tap.
-
-%, rejecting a hassle cost of zero with 10\% confidence
-
-%One possibility may be that estimating a single average hassle cost for the population of connections masks significant heterogeneity across household density and dwelling type among other factors.\footnote{Future versions will estimate this heterogeneity directly.}
-
 \begin{table}
@@
 
-\begin{table}
-\centering
-\caption{Predicted Hassle Cost Distribution}\label{table:step2histogram}
+Table~\ref{table:step2estimates} shows the coefficient estimates for the hassle cost estimation.
+Consistent with the theory, the hassle cost rises with the share of households living in single homes or apartment buildings (instead of duplexes).
+Similarly, increasing the average distance between households by one meter raises the predicted hassle cost by 17.59 PhP/m3.
+For the average household, the hassle cost is estimated to be \input{tables/mean_hassle}PhP per cubic meter of usage, which is approximately \input{tables/hassle_percentage}\unskip\% of the average tariff.
+
+Figure~\ref{figure:step2histogram} plots the histogram of predicted hassle costs across the population of households, finding substantial heterogeneity with a long tail of prohibitively expensive hassle costs.
+Predicted hassle costs also have a correlation of \input{tables/correlation_hassle} with household fixed water preferences.\footnote{Section~\ref{section:disaggregation} discusses how connection-level fixed preferences $\gamma_C$ are disaggregated into household components, $\gamma_i$.}  This correlation has substantive implications for the impacts of counterfactual pricing policies; for example, high hassle costs may drive large users to sort away from sharing while small users can happily share water at little additional cost.
+
+With only 548 connections that experience leaks, the estimation recovers wide standard errors for all three parameters.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  Taken together, these results suggest that the time-costs or other physical challenges transporting water to share with a neighbor may play an important role in the extent to which households choose to use water from a neighbor's tap.
+
+%, rejecting a hassle cost of zero with 10\% confidence
+%One possibility may be that estimating a single average hassle cost for the population of connections masks significant heterogeneity across household density and dwelling type among other factors.\footnote{Future versions will estimate this heterogeneity directly.}
+
+\begin{figure}
+\centering
+\caption{Predicted Hassle Cost Distribution}\label{figure:step2histogram}
 \includegraphics[scale=.7]{tables/hassle_cost_distribution.pdf} \\
@@
 \footnotesize{Excludes top and bottom 1\% outliers}
-\end{table}
+\end{figure}
 
@@
 
-\subsubsection{Disaggregating Connection-Level Preferences to Household-Level Preferences}
+\subsubsection{Disaggregating Connection-Level Preferences to Household-Level Preferences}\label{section:disaggregation}
 
@@
 
-With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors with each of the 599 geographic regions.
+%Grouping households into sets of three produces some remainder households that I remove from the sample bringing the total number of households to \input{tables/totalhhsmm_group}.
+
+With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors within each of the 599 wards.
 The routine then orders households in the sequential game according to their utilities from using an individual connection.
 This assumption captures the intuition that households who would have connected in the absence of any sharing are likely to be the first to take-up a new connection.
-Random draws of the preference shocks, $\eta$ and $\epsilon$, are assigned to each household so that households can compute expected utilities over \input{tables/sim_time_periods}months for all possible water source choices.
-These shocks are sampled from a multivariate normal distribution taking into account the estimated correlation between sharing partners from Table~\ref{table:correstimates}.
+Random draws of the preference and consumption shocks, $\eta$ and $\epsilon$, are assigned to each household so that households can compute expected utilities over \input{tables/sim_time_periods}months for all possible water source choices.
+These shocks are sampled from a multivariate normal distribution taking into account the estimated correlation between sharing partners presented in Table~\ref{table:correstimates}.
 %\footnote{ Future versions will not condition on observed choices in this way, and instead sample households across sharing relationships. }
@@
 \vspace{.05cm}
-\footnotesize{ Standard errors are bootstrapped at the connection level.  Total Households:  \input{tables/totalhhsmm_group}  }
-\end{table}
-
-Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee_group}PhP monthly fixed fee paid the provider.
+\footnotesize{ Total Households:  \input{tables/totalhhsmm_group}   Total Wards:  599 \\ Standard errors are bootstrapped at the connection level.   }
+\end{table}
+
+Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee_group}PhP monthly fixed fee paid to the provider.
 This finding suggests that households face sizable barriers to connecting to the water network such as maintenance land tenure insecurity, or administrative costs.
-This total fixed fee is also comparable to the total variable price paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.
+This total fixed fee is also comparable to the total variable price (tariff $\times$ volume) paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.
 
@@
 This likely captures fixed quality differences between vended water and other water sources.
-The mean price for vended water of \input{tables/vendorprice_group}PhP per cubic meter is close to the highest tariff price in Figure~\ref{figure:tariff}.
-These estimates include a sizable variance term for the vendor price, which is consistent with the large variety of small-scale water sources that are collapsed into this measure, including primarily deep wells as well as tanker trucks and water refilling stations.
+The mean price for vended water of \input{tables/vendorprice_group}PhP per cubic meter is close to the highest tariff prices in Figure~\ref{figure:tariff}.
+These estimates include a modest variance term for the vendor price, which is consistent with a competitive market for alternative water sources through deep wells, tanker trucks, and water refilling stations.
+
+%These sources may also be unevenly distributed throughout the city.
+%These estimates include a sizable variance term for the vendor price, which is consistent with the large variety of small-scale water sources that are collapsed into this measure, including primarily deep wells as well as tanker trucks and water refilling stations.
 These sources may also be unevenly distributed throughout the city.
@@
 Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option, particularly the marginal price, $p_v$.
-As a simple out-of-sample test, I compare this estimate of $p_v$ to the implied $p_v$ from data on total water expenditures for vendor households using additional census data from a section of Manila.\footnote{The 2011 Community Based Monitoring System data covers over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown Manila --- and includes information on income (used to compute imputed income) as well as water source and monthly expenditures.}  In this data, households using from vendors report expenditures of 365 PhP/month while households using individual connections report expenditures of 470 PhP/month and households sharing connections report expenditures of 370 PhP/month.
-Assuming that the vendor expenditures only reflect the marginal prices paid for water (excluding the fixed cost), I can express average expenditures, $E_v$, by multiplying average vendor demand by the vendor price, $E_v = (\gamma - \alpha p_v) p_v$.
-Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=33$, and price sensitivity, $\alpha=.62$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 15.7 PhP/$\text{m}^{3}$ or 37.53 PhP/$\text{m}^{3}$.
+As a simple out-of-sample test, Appendix~\ref{appendix:vendorpriceestimates} finds that the estimate of $p_v$ in Table~\ref{table:smmestimates} matches closely with the implied $p_v$ from data on total water expenditures for vendor households using additional census data from part of Manila.
+This exercise provides additional confidence that the vendor price estimates are within a reasonable range.
+
+%Assuming that the vendor expenditures only reflect the marginal prices paid for water (excluding the fixed cost), I can express average expenditures, $E_v$, by multiplying average vendor demand by the vendor price, $E_v = (\gamma - \alpha p_v) p_v$.
+Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=37$, and price sensitivity, $\alpha=.91$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 15.7 PhP/$\text{m}^{3}$ or 37.53 PhP/$\text{m}^{3}$.
 The latter price matches closely to the estimated price of 37.16 PhP/$\text{m}^3$, providing additional support to the structural estimates.
 
-\subsection{Out-of-Sample Test}\label{section:oostest}
-
-To evaluate how well the model is able to match observed substitution patterns between water sources, I investigate reduced-form evidence from a connection-fee discount program since this variation is not used explicitly in any part of the estimation.
-The fundamental assumption of the model is that the decision to share a water connection balances splitting the fixed fee among many households against facing marginal hassle costs in fetching water as well as free-rider costs in splitting the water bill.
+\subsection{Out-of-Sample Test: A Connection Fee Discount Program}\label{section:oostest}
+
+A connection fee discount program implemented by the water company provides a useful setting to test the out-of-sample predictions of the economic model: do predicted water source choices match observed choices in response to a discount in the fixed fee?
+According to the model, reducing the fixed fee would make individual connections more attractive relative to shared connections or water vendors.
+This section compares the predicted and observed increase in connections in response to the program.
+
+%To evaluate how well the model is able to match observed substitution patterns between water sources, I investigate reduced-form evidence from a connection-fee discount program since this variation is not used explicitly in any part of the estimation.
+%[chk] The fundamental assumption of the model is that the decision to share a water connection balances splitting the fixed fee among many households against facing marginal hassle costs in fetching water as well as free-rider costs in splitting the water bill.
 Under this assumption, reducing the fixed fee would lead to substitution away from shared connections toward individual connections.
@@
 A small fraction of households are observed to receive connection fee discounts prior to the program as part of other, smaller pro-poor strategies implemented by the water provider.
+% and these households are excluded from the main analysis
 
@@
 Table~\ref{table:oosestimates} calculates the impacts of this connection fee discount on water source choices as well as consumer welfare.
-Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended water.
-Since utility is assumed to be quasi-linear, consumer welfare is reported in PhP/month.
+Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended.
+Since utility is assumed to be quasi-linear, consumer welfare is measured in PhP/month.
 Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile_group}\unskip\% of users.
@@
 Table~\ref{table:fixedfeediscount} summarizes the impacts of this change on source choices and consumer welfare measured in terms of the difference between current utility and utility from using the outside vendor option as in Section~\ref{section:oostest}.
-The decrease in the fixed fee and increase in the tariff both act to decrease the incentives for sharing a connection and leading to a drop of \input{tables/discount_sharing_change_group}percentage points in households using water from their neighbors.
+While the increase in the tariff drives large users to substitute toward vendor options, the decrease in the fixed price allows some small users to join together and purchase shared connections, resulting in no change in the share of households using from a neighbor.
 The third row indicates even greater substitution toward water vendors of around \input{tables/discount_vendor_change_group}percentage points in response to the higher tariff.
@@
 %\footnote{Consumer surplus is measured relative to utility from using vended water.}
+% a drop of \input{tables/discount_sharing_change_group}percentage points in households using water from their neighbors The decrease in the fixed fee and increase in the tariff both act to decrease the incentives for sharing a connection and leading to no change in households using water from their neighbors.
 \begin{table}
@@
 
-\begin{figure}
+\begin{figure}[!htp]
 \centering
@@
 
-Relative to the First-Best, implementing the current tariff in this context without sharing reduces average surplus dramatically and increases the share of households using vended water by raising the average marginal price.
-The optimal two-part tariff in column three features a higher fixed fee affording a lower marginal price at all consumption levels.
-Compared to the current tariff, the optimal two-part tariff brings consumer surplus up to \input{tables/tpt_surplus_improvement_group}\unskip\% of the First-Best surplus.
-These welfare gains are primarily driven by increased consumption for large users since surplus for low-users is cut in half and the share of households connected to the network declines substantially.
-
-\begin{table}
+\begin{table}[!hbp]
 \centering
@@
 \\ Surplus is measured in terms of PhP/month.}
-
-\end{table}
+\end{table}
+
+Relative to the First-Best, implementing the current tariff in this context without sharing reduces average surplus dramatically and increases the share of households using vended water by raising the average marginal price.
+The optimal two-part tariff in column three features a higher fixed fee affording a lower marginal price at all consumption levels.
+Compared to the current tariff, the optimal two-part tariff brings consumer surplus up to \input{tables/tpt_surplus_improvement_group}\unskip\% of the First-Best surplus.
+These welfare gains are primarily driven by increased consumption for large users since surplus for low-users is cut in half and the share of households connected to the network declines substantially.
 
@@
 %zooming in on tariffs below 20 PhP/$\text{m}^{3}$ in order to highlight distinctions between the two-part and three-part tariffs.
-\begin{figure}
-\centering
-\caption{Optimal Tariffs With Sharing}\label{figure:optimaltariffsharing}
-\includegraphics{tables/shr_tariff_groups.pdf}
-\end{figure}
 
@@
 By subsidizing individual connections, the two-part tariff in column three performs very close to the First-Best tariff in terms of average consumer surplus.
-
-\begin{table}
-\centering
-\caption{Optimal Tariffs With Sharing}\label{table:optimaltariffsharing}
-\resizebox{\textwidth}{!}{%
-\input{tables/welfare_sharing_groups}
-}
-\footnotesize{$\text{ }^{*}$ The First-Best fee does not include individual transfers imposed by the regulator.
-\\  Social tariffs place all welfare weight on the bottom 50\% of water users.
-\\ Surplus is measured in terms of PhP/month.}
-\end{table}
 
@@
 While manipulating the two-part tariff proved to be an effective redistributive strategy without sharing in Section~\ref{section:optimaltariffswithoutsharing}, this finding suggests that informal sharing networks act to constrain the effectiveness of non-linear pricing in redistributing surplus.
+
+\begin{figure}[!htp]
+\centering
+\caption{Optimal Tariffs With Sharing}\label{figure:optimaltariffsharing}
+\includegraphics{tables/shr_tariff_groups.pdf}
+\end{figure}
 
@@
 This result points to the extent to which sharing networks constrain the ability of cities to achieve redistribution through complex, non-linear pricing strategies.
+
+\begin{table}[!hbp]
+\centering
+\caption{Optimal Tariffs With Sharing}\label{table:optimaltariffsharing}
+\resizebox{\textwidth}{!}{%
+\input{tables/welfare_sharing_groups}
+}
+\footnotesize{$\text{ }^{*}$ The First-Best fee does not include individual transfers imposed by the regulator.
+\\  Social tariffs place all welfare weight on the bottom 50\% of water users.
+\\ Surplus is measured in terms of PhP/month.}
+\end{table}
 
@@
 
+\section{Out of Sample Test for Vendor Price Estimates}\label{appendix:vendorpriceestimates}
+
+%Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option, particularly the marginal price, $p_v$.
+As a simple out-of-sample test, I compare this estimate of $p_v$ to the implied $p_v$ from data on total water expenditures for vendor households using additional census data from a section of Manila.
+
+As a simple out-of-sample test, I compare the estimate of $p_v$ in Table~\ref{table:smmestimates} to the implied $p_v$ from data on total water expenditures for vendor households using additional census data from a section of Manila.
+The 2011 Community Based Monitoring System data covers over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown Manila --- and includes information on income (used to compute imputed income) as well as water source and monthly expenditures.
+In this data, households using from vendors report expenditures of 365 PhP/month while households using individual connections report expenditures of 470 PhP/month and households sharing connections report expenditures of 365 PhP/month.
+I can express average marginal expenditures, $E_v$, by multiplying average vendor demand by the vendor price and adding the vendor fixed cost, $E_v = (\gamma - \alpha p_v) p_v + F_v$.
+Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=37$, and price sensitivity, $\alpha=.91$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 7.9 PhP/$\text{m}^{3}$ or 32.8 PhP/$\text{m}^{3}$.
+The latter price almost perfectly matches the estimated price of 32.85 PhP/$\text{m}^3$, providing additional support for the structural estimates.
+
 \section{Simulated Method of Moments Model Fit}\label{appendix:modelfit}

### 2018-09-19 phil_matlab/fixed_cost_discount_groupings_v1.m

@@ -203,10 +203,10 @@ fileID = fopen(strcat(cd_out,table_pre,'discount_estimates_group.tex'),'w');
 
 %fprintf(fileID,'%s\n','\caption{Welfare Impacts of a Fixed Fee Discount Policy}'); 
 fprintf(fileID,'%s\n','\begin{tabular}{lcc}');
-fprintf(fileID,'%s\n','\hline');
+%fprintf(fileID,'%s\n','\hline');
 fprintf(fileID,'%s\n','& Current & Discount \\');
-fprintf(fileID,'%s\n','\hline');
-fprintf(fileID,'%s\n','\hline');
+%fprintf(fileID,'%s\n','\hline');
+%fprintf(fileID,'%s\n','\hline');
 
 
     
@@ -248,11 +248,11 @@ end
 if income_opt==0
 fprintf(fileID,'%s\n',strcat(' Surplus: Low Users  &',num2str(surplus_current_low,'%5.1f') ,'&', ...
                     num2str(surplus_discount_low,'%5.1f'),' \\'));
-    fprintf(fileID,'%s\n','\hline');    
+%    fprintf(fileID,'%s\n','\hline');    
 else
     fprintf(fileID,'%s\n',strcat('Gain HH Inc: Low Inc & &', ...
                         num2str(TU_change_low_income,'%5.1f'),' \\'));
-    fprintf(fileID,'%s\n','\hline');
+%    fprintf(fileID,'%s\n','\hline');
 end
 
 fprintf(fileID,'%s\n','\end{tabular}'); 

### 2018-09-19 phil_matlab/sim_build_counterfactual_out_of_sample_groupings_v1.m

@@ -139,7 +139,7 @@ fileID = fopen(strcat(cd_out,table_pre,'oos_discount_estimates_group.tex'),'w');
 fprintf(fileID,'%s\n','\begin{tabular}{lcc}');
 %fprintf(fileID,'%s\n','\hline');
 fprintf(fileID,'%s\n','& Current &  Discount \\');
-fprintf(fileID,'%s\n','\hline');
+%fprintf(fileID,'%s\n','\hline');
 %fprintf(fileID,'%s\n','\hline');
 
 
@@ -171,11 +171,11 @@ end
 if income_opt==0
 fprintf(fileID,'%s\n',strcat(' Surplus: Low Users  &',num2str(surplus_current_low,'%5.1f') ,'&', ...
                     num2str(surplus_discount_low,'%5.1f'),' \\'));
-    fprintf(fileID,'%s\n','\hline');    
+%    fprintf(fileID,'%s\n','\hline');    
 else
     fprintf(fileID,'%s\n',strcat('Gain HH Inc: Low Inc & &', ...
                         num2str(TU_change_low_income,'%5.1f'),' \\'));
-    fprintf(fileID,'%s\n','\hline');
+%    fprintf(fileID,'%s\n','\hline');
 end
 
 fprintf(fileID,'%s\n','\end{tabular}'); 

### 2018-09-19 phil_matlab/table_step_2_estimates.m

@@ -102,10 +102,10 @@ fprintf(fileID,'%s\n','\hline');
 
 fprintf(fileID,'%s\n',strcat('Intercept & 1 &', ...
                     num2str(Xmean(1),'%5.2f'),' & ', num2str(Xstd(1),'%5.2f'),'\\'));
-fprintf(fileID,'%s\n',strcat('\% HHs in Single Homes  &', ...
+fprintf(fileID,'%s\n',strcat('\% HHs in Single Home/Apt.  &', ...
                     num2str(mean(PH_CONTROL(:,1)),'%5.2f'),'&',num2str(Xmean(2),'%5.2f'),'&', ...
                     num2str(Xstd(2),'%5.2f'),'\\'));
-fprintf(fileID,'%s\n',strcat('Avg. Distance Between HHs &', ...
+fprintf(fileID,'%s\n',strcat('Avg. Dist. Between HHs (meters) &', ...
                     num2str(mean(PH_CONTROL(:,2)),'%5.2f'), '&', num2str(Xmean(3),'%5.2f'),'&', ...
                     num2str(Xstd(3),'%5.2f'),'\\'));
                 

### 2018-09-20 phil_paper/jmp_wjv_v2.tex
lots of fixes to jmp paper

@@
 
-This section details how households choose their monthly quantities of consumption holding their water source fixed.
-For households using piped water, this consumption choice is complicated by four features:  (1) households may have difficulty targeting their exact monthly consumption levels; (2) increasing marginal prices in the water tariff result in non-linear budget constraints; (3) households that share a connection need to determine how to divide the monthly water bill; and (4) households fetching from a neighbor may face additional hassle costs in transporting water.
-Since the data record monthly consumption for each connection, this model first introduces individual household demand before aggregating household demand at the connection-level for estimation.
-
-Households that use piped water face the difficult task of coordinating water consumption among all household members.
+%This section details how households choose their monthly quantities of consumption holding their water source fixed.
+
+%For households using piped water, they have to consider four aspects when choosing how much to use each month:  (1) households may have difficulty targeting their exact monthly consumption levels since meters can be hard to observe and many family members use the same tap; (2) increasing marginal prices in the water tariff mean that households face non-linear budget constraints; (3) households that share a connection need to determine how to divide the monthly water bill; and (4) households fetching from a neighbor may face additional hassle costs in transporting water.
+
+%Since the data record monthly consumption for each connection, this model first introduces individual household demand before aggregating household demand at the connection-level for estimation.
+
+In choosing how much water to use each month, households using piped water face the difficult task of coordinating water consumption among all household members.
 For example, consider a household head trying to manage water consumption across all of their household members each month.
@@
 
-As a simple way to capture this coordination task, the model assumes that each household $i$ sets a goal for water use each month, $w_i$, knowing that idiosyncratic factors, $\epsilon_i$, may increase or decrease the realized amount of usage.
+As a simple way to capture this coordination task, let each household $i$ set a goal for water use each month, $w_i$, knowing that consumption shocks, $\epsilon_i$, may increase or decrease the realized amount of usage.
 Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.
@@
 \begin{split}
-U(x_i,W_i) &=  x_i + W_i - \frac{1}{2\alpha_i } ( W_i - \Gamma_i + \alpha_i )^2  \\
+U(x_i,W_i) &=  x_i + (1-H_i) W_i - \frac{1}{2\alpha_i } ( W_i - \Gamma_i + \alpha_i )^2  \\
 W_i &= w_i + \epsilon_i \\
@@
 Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible shocks, allowing them to maximize expected utility.
+
+Households that are using water from a neighbor's tap may face an additional utility cost per gallon of water $H_i$.
+This hassle cost captures any inconvenience associated with using water from a neighbor's tap.
+The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.
+These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.
+Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households face a homogeneous hassle cost, $H_i$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.
+The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.}
+
+% , normalized as $i>1$,
+
 \subsubsection{Determining the Budget Constraint}
+
 The household problem is additionally complicated by the presence of non-linear price schedules for water.
@@
 
-Water sharing relationships impact monthly consumption choices through the budget constraint in three ways.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.
-
-First, this model assumes that the monthly water bill is split evenly between all sharing households.
+Water sharing relationships impact monthly consumption choices through the budget constraint.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.
+Therefore, all households, $i\neq1$, using from a neighbor's tap have a positive hassle cost, $H$, while the connection owner, $i=1$, has zero hassle cost.
+
+This model assumes that the monthly water bill is split evenly between all sharing households.
 Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.
@@
 }
-Second, sharing households may face a hassle cost, $p_h$, per unit of water, which captures any inconvenience associated with using water from a neighbor's tap.
-The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.
-These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.
-Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households, normalized as $i>1$, face a homogeneous hassle cost, $p_h$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.}  The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.
-Hassle costs for household $i$ are given by the following function:
-\begin{align*}
-H_{i} =& 
-\begin{cases}
-0     &  \text{ if } i=1 \text{ (connection owner) }\\
-p_h   &  \text{ if } i \neq 1
-\end{cases}
-\end{align*}
-Third, sharing households must negotiate over how to pay the monthly fixed fees.
+
+Sharing households must negotiate over how to pay the monthly fixed fees.
 The model assumes that households commit to dividing any fixed fees at the start of the sharing arrangement.
@@
 
-Normalizing the price of the numeraire good, $x$, to one, the budget constraint for household, $i$, using a connection with households, $S$, takes the following form:
-\begin{align*}
-Y_i - F_i &=  
-\begin{cases}
-      x_i + H_{i} W_i + \frac{1}{S} p^{1} W_C   &\text{ if }   W_C \in [0,\overline{W}^{1}], \\
-      x_i +  H_{i} W_i +  \frac{1}{S} \big [p^{k} W_C -  E_{k} \big]     &\text{ if } W_C \in [\overline{W}^{k-1},\overline{W}^{k}], \\
-      ...   &\text{ ... }      
-\end{cases} \\
-E_{k} &= \big  [\sum_{j=1}^{k-1}  (p^{k} - p^{j})(\overline{W}^{j}-\overline{W}^{j-1})  \big ]
-\end{align*}
-
-$E_{k}$ represents the discount that the household earns on all previous price thresholds below the current level of consumption.
-This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.
-In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.
-In this scenario, the household does not face any hassle costs, $p_h$, and pays the total bill from its corresponding consumption.
+Normalizing the price of the numeraire good, $x$, to one, the budget constraint for household, $i$, using a connection with households, $S$, takes the following form given that total consumption for their connection, $W_C$, falls between thresholds, $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
+%\begin{align*}
+%Y_i - F_i &=  
+%\begin{cases}
+%      x_i + H_{i} W_i + \frac{1}{S} p^{1} W_C   &\text{ if }   W_C \in [0,\overline{W}^{1}], \\
+%      x_i +  H_{i} W_i +  \frac{1}{S} \big [p^{k} W_C -  E_{k} \big]     &\text{ if } W_C \in [\overline{W}^{k-1},\overline{W}^{k}], \\
+%      ...   &\text{ ... }      
+%\end{cases} \\
+%E_{k} &= \big  [\sum_{j=1}^{k-1}  (p^{k} - p^{j})(\overline{W}^{j}-\overline{W}^{j-1})  \big ]
+%\end{align*}
+\begin{align}
+\label{equation:budgetconstraint}
+\begin{split}
+(Y_i - F_i) &= x_i +   \dfrac{  B_{C,k}  }{S_C}    \hspace{.3cm} \text{ if } \hspace{.1cm} W_C \in [\overline{W}^{k-1},\overline{W}^{k}] \\
+\text{Where: }& \\
+B_{C,k}  &= p^{k} (W_{C}^{*} - \overline{W}^{k-1}) +\sum_{j=1}^{k-1}  p^{j}(\overline{W}^{j}-\overline{W}^{j-1}) 
+\end{split}
+\end{align}
+
+The full budget constraint is a piece-wise expression of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.
+$B_{C,k}$represents the total water bill for connection $C$ given the tariff schedule.
+This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.\footnote{In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.
+In this scenario, the household does not face any hassle costs, $H_i$, and pays the total bill from its corresponding consumption.}
 
@@
 Rewriting the utility function in equation (\ref{equation:umaxfirst}) by substituting the numeraire good, $x$, with the budget constraint, expected utility for household $i$ over the consumption shocks takes the following form:
-%\begin{comment}
-\scalebox{.88}{\parbox{1\linewidth}{
-\begin{align*}
-E[U(x_i,w_i)] = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C -  E_{k} \big] d \epsilon_C + \int_{-\infty}^{\infty} W_i - H_{i} W_i - \frac{1}{2\alpha_i} ( W_i - \Gamma_i + \alpha_i )^2 d \epsilon_i  \\
-          = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C d -  E_{k} \big] d \epsilon_C+ w_i - H_{i} w_i - \frac{1}{2\alpha_i} ( w_i - \Gamma_i + \alpha_i )^2 + \sigma_{\epsilon}^{2}
-\end{align*}
-}} \\
+
+%\scalebox{.88}{\parbox{1\linewidth}{
+%\begin{align*}
+%E[U(x_i,w_i)] = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C -  E_{k} \big] d \epsilon_C + \int_{-\infty}^{\infty} W_i - H_{i} W_i - \frac{1}{2\alpha_i} ( W_i - \Gamma_i + \alpha_i )^2 d \epsilon_i  \\
+ %         = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C d -  E_{k} \big] d \epsilon_C+ w_i - H_{i} w_i - \frac{1}{2\alpha_i} ( w_i - \Gamma_i + \alpha_i )^2 + \sigma_{\epsilon}^{2}
+%\end{align*}
+%}} \\
+
+% E[U(w_i)] = 
+\begin{align*}
+max_{w_i} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-{w_C}}^{\overline{W}^{k}-{w_C}} (Y_i - F_i) -  \dfrac{ B_{C,k} }{S_C}     + (1-p_s) W_i   - \frac{1}{2\alpha } ( W_i - \Gamma_i + \alpha_i )^2  d \epsilon_C
+\end{align*}
+
 Where $\epsilon_C$ is the convolution of consumption shocks across sharing households distributed as follows:
@@
 Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments.
-I take this calculation into account when allowing for decreasing marginal prices in the counterfactual exercises.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):\footnote{For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.}
+I take this calculation into account when allowing for decreasing marginal prices in the counterfactual exercises.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
 \begin{align}\label{equation:generaldemand}
@@
 \text{Where: } & \\
-D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{H,L} }   \\
+D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{L,H} }   \\
 d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
@@
 \end{align}
+
+%\begin{align}\label{equation:generaldemand}
+%\begin{split}
+%w^{*}_C &=
+%\begin{cases}
+%D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+%D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
+%D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
+%D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
+%D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
+%D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
+%D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
+%\end{cases}\\
+%\text{Where: } & \\
+%D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{H,L} }   \\
+%d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} (\tfrac{\lambda_C - \overline{W}^{H}}{\lambda_C}) + p^{M} (\tfrac{\overline{W}^{H} - \overline{W}^{H}}{\lambda_C} ) -    p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\lambda_C})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\lambda_C})  ]  \Big )    \\
+%V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\lambda_C})  ,  \lambda_C = \sqrt{2}{\sigma_{\epsilon_C}} \\
+%\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \lambda_C \\
+%\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \lambda_C \\
+%\end{split}
+%\end{align}
+
+For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.
 
@@
 \begin{split}
-LL_{j,Post l} = & \frac{J-(1-G)}{J} \overbrace{LL(\gamma_j,\alpha_j,S_j)}^{\text{$L$ do not share with $j$}} + \\
+LL_{j,PostLeak} = & \frac{J-(1-G)}{J} \overbrace{LL(\gamma_j,\alpha_j,S_j)}^{\text{$L$ do not share with $j$}} + \\
 	    & \frac{(1-G)}{J}  \underbrace{LL(\gamma_j + \gamma_{L},\alpha_j+\alpha_{L},S_j+S_L)}_{\text{$L$ share with $j$}}
@@
 \begin{align*}
-\gamma_{L} = &  \sum_{l=1}^{\overline{L}} ( \gamma_{l} - \alpha_{l} P_{h,l} ) \\
-P_{h,l} = & 
+\gamma_{L} = &  \sum_{l=1}^{\overline{L}} ( \gamma_{l} - \alpha_{l} H_l ) \\
+H_{l} = & 
 	\begin{cases}
 	0     &  \text{ if } l=1 \text{ and } pre=1 \\
-	p_h   &  \text{ else }
+	H   &  \text{ else }
 	\end{cases}
 \end{align*}
-Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $p_h$ while other households $s \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.
+Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $H_i$ while other households $s \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.
 Therefore, this method identifies hassle costs from variation in exposure for owners of the connection.
@@
 \textbf{Sample} : The estimation uses a 10\% sample of connections from the connection survey (5,000 connections), which serves as the primary sample for the counterfactual exercises.
-This sample is combined with 5,239 connections from the leak quasi-experiment used in Section~\ref{section:hasslecostestimation}, which takes preference estimates from this step as an input.
-Together these connections produce 473,114 months of consumption observations used in the preference estimation.
+This sample is combined with 2,151 connections from the leak quasi-experiment used in Section~\ref{section:hasslecostestimation}, which takes preference estimates from this step as an input.
+Together these connections produce 349,265 months of consumption observations used in the preference estimation.
 All standard errors throughout this paper are bootstrapped using \input{tables/boot_max}repetitions.

### 2018-09-23 phil_paper/jmp_wjv_v2.tex
fixing some graph stuff

@@
 \usepackage{array}
+\usepackage{threeparttable}
 %\usepackage{pgfplots}
@@
 For example, 70\% of African cities report frequent water sharing (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
-While previous studies have focused on particular suburbs, this paper is the first to my knowledge to measure the role of water sharing in extending access across an urban population.
+While previous studies have focused on specific suburbs, this paper is the first to my knowledge to measure the role of water sharing in extending access across an urban population.
 
@@
 I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.
-This policy reduces access by incentivizing households to substitute away from sharing arrangements toward both individual connections and water vendors (which mainly include deepwells and water refilling stations).
+This policy reduces access by incentivizing households to substitute toward water vendors (which mainly include deepwells and water refilling stations).
+
+%substitute away from sharing arrangements toward both individual connections and
+%This policy reduces access by incentivizing households to substitute away from sharing arrangements toward both individual connections and water vendors (which mainly include deepwells and water refilling stations).
 
@@
 Finally, I compare the optimal tariff with a social tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.
-The social tariff features a much higher fixed fee and lower marginal price, does not improve access to piped water, and reallocates little consumer surplus to low-demand households at a large cost to average welfare.
+With sharing, social tariffs are ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, social tariffs achieve substantial redistribution, over doubling consumer surplus for small users.
+This evidence suggests that the presence of informal sharing networks constrains non-linear pricing as an effective tool for redistribution.
+
+%features a much lower fixed fee and higher marginal price and redistributes substantial surplus to low users as compared to the optimal tariff.
+
+%features a slightly lower fixed fee and higher marginal price, produces universal access to piped water and reduces sharing, but reallocates little consumer surplus to low-demand households.
+
+%and increasing marginal prices; it also increases access and efficiently redistributes consumer surplus to low users as compared the optimal tariff.
+These results provide evidence that the presence of informal sharing networks constrains pricing policy as an effective tool for redistribution.
+
+%The social tariff features a much higher fixed fee and lower marginal price, does not improve access to piped water, and reallocates little consumer surplus to low-demand households at a large cost to average welfare.
 By contrast, in a counterfactual world without sharing, the social tariff features a fixed fee subsidy and increasing marginal prices; it also increases access and efficiently redistributes consumer surplus to low users as compared the optimal tariff.
@@
 Complete billing records for each water connection including the monthly meter reading, the total bill charged, and the precise location for each meter serve as the primary measure of quantity choices.
-These data span 2010 to 2015, during which connections grew from 800,000 to 1.5 million water connections, generating nearly 100 million transaction records.
+These data span 2010 to 2015, during which connections grew from 900,000 to 1.5 million water connections, generating nearly 100 million transaction records.
 Connections are divided into residential (90\%), semi-business (4\%), commercial (5\%), and industrial (1\%).
@@
 These connections provide a useful source of price variation which is described in Appendix~\ref{appendix:ratechangeelasticity}.}  The monthly meter reading is used as the measure of consumption for each connection.
-Meter readings are rounded to the nearest cubic meter, and I limit consideration to meter readings below 120 $\text{m}^{3}$ in order to exclude pipe leaks as well as meter reading errors (readings above 120 $\text{m}^{3}$ compose less than 0.5\% of the sample).
+Meter readings are rounded to the nearest cubic meter, and I limit consideration to meter readings below 100 $\text{m}^{3}$ in order to exclude pipe leaks as well as meter reading errors (readings above 100 $\text{m}^{3}$ compose less than 0.7\% of the sample).
 
@@
 Households that own a connection in the connection survey are similar to households connected to the piped water network in the Census data.
-To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 8 regions of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.\footnote{Regions are chosen to overlap with ward administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}
+To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 599 wards of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.
+%\footnote{Regions are chosen to overlap with ward administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}
 
@@
 The water provider also maintains call records of all service complaints, which can be linked to individual connections.
-This data is used to measure instances where households face unanticipated shocks to their water source as part of the identification strategy to estimate the hassle costs of sharing water.
+This data is used to measure instances where households face unanticipated shocks to their water source as part of the identification strategy to estimate the marginal costs of sharing water.
 Finally, the water provider tracks data on the marginal cost of pumping an additional cubic meter of water as well as the costs associated with installing new connections.
@@
 \centering
-\captionsetup{justification=centering}
+%\captionsetup{justification=centering}
+\begin{threeparttable}
 \caption{ Water Connections  by Number of Households Served}\label{descriptives}
-\input{tables/new_descriptives} \\
-\footnotesize{The data include billing records merged with the connection survey. \\ Income is imputed using location, demographic variables, and their interactions.}
-\end{table}
-
-Table~\ref{descriptives} also summarizes water use and sharing behavior for these connections, merging information from the connection survey with the billing records.
+\input{tables/new_descriptives}
+\begin{tablenotes}
+\item \footnotesize{The data include billing records merged with the connection survey.  Income is imputed using location, demographic variables, and their interactions.}
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+Table~\ref{descriptives} summarizes water use and sharing behavior for these connections, merging information from the connection survey with the billing records.
 Larger numbers of households sharing a water connection are correlated with higher total water usage, but less water per person.\footnote{Total People Served by a connection includes both the owning household and any other households using a connection.}  This decline in usage per person may have many possible drivers: (1) sharing households face higher prices by locating at a higher point on the tariff schedule (Figure~\ref{figure:tariff}), (2) sharing households may face hassle costs in fetching water from neighboring taps, (3) these price effects may incentivize low-demand households to select into sharing relationships, consistent with the demographic patterns, and (4) low-demand households may have idiosyncratic preferences for sharing relationships.
@@
 
-Sharing households must negotiate over how to pay the monthly fixed fees.
-The model assumes that households commit to dividing any fixed fees at the start of the sharing arrangement.
+Sharing households must negotiate over how to pay the monthly fixed costs (including the fixed fee paid to the firm and any unobserved costs of using a connection).
+The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement.
 Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions.
-For ease of exposition, this section assigns a fixed fee, $F_i$ to each household and postpones discussion of how the total fixed fee may be divided between households to Section~\ref{section:watersourcechoice}.
+For ease of exposition, this section assigns a fixed cost, $F_i$ to each household and postpones discussion of how the total fixed cost may be divided between households to Section~\ref{section:watersourcechoice}.
 
@@
 6\unskip\% of households source their water from small-scale water vendors.
-These sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed fee, $F_v$, and a marginal price, $p_v$.
-The monthly fixed fee, $F_v$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.
+These sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed cost, $F_v$, and a marginal price, $p_v$.
+The monthly fixed cost, $F_v$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.
 Similarly, the marginal price, $p_v$, includes both the price per unit as well as any differences in water quality or ease of use relative to piped water.
@@
 \input{tables/step_1_estimates_group} \\
-\vspace{.1cm}
-{\footnotesize{Total Observations:  349,265   Total Connections:  7,151} }
+\vspace{.2cm}
+{\footnotesize{Sample includes 349,265 billing months for 7,151 connections. } }
 \end{table}
@@
 \centering
+\begin{threeparttable}
 \caption{Elasticity Estimates}\label{table:elasticity}
-\input{tables/elasticity_estimates} \\
-\vspace{.5cm}
-{\footnotesize Total Observations:  349,265   Total Connections:  7,151 \\
+\input{tables/elasticity_estimates} 
+\begin{tablenotes}
+\item {\footnotesize Elasticities are calculated from 7,151 connections making 349,265 connection-months.
+Income is imputed based on demographics, locations, and their interactions.
 Standard errors are bootstrapped at the connection level.}
-\end{table}
-
-The demand estimation yields an average elasticity of -\input{tables/mean_elasticity}\unskip, which can be interpreted as the percentage change in quantity due to a one percentage change in price.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+The demand estimation yields an average elasticity of \input{tables/mean_elasticity}\unskip, which can be interpreted as the percentage decrease in quantity due to a one percentage increase in price.
 This estimate also closely matches reduced-form elasticity estimates from price-change quasi-experiment detailed in Appendix~\ref{appendix:ratechangeelasticity}.
-This estimate is well below the -0.98 estimate of \cite{szabo2015value} but in the range of other similar studies in developing world that find elasticities between -0.01 and -0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).
+This estimate is in range of the 0.98 estimate from \cite{szabo2015value} as well as similar studies in the developing world that find elasticities between 0.01 and 0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).
 
@@
 Since preference and consumption shocks are assumed to be normally distributed, the model predicts some negative consumption values.
-In the counterfactual exercises, I round these negative realizations to zero consumption.
+In the counterfactual exercises, I treat these negative realizations as zero consumption choices.
 Likewise, the model also cannot account for bunching at zero (likely capturing households that go on vacation).
@@
 \centering
+\begin{threeparttable}
 \caption{Correlation Estimates}\label{table:correstimates}
 \input{tables/corr_table_group}
+\begin{tablenotes}
+\item { \footnotesize Errors are bootstrapped at the connection level. }
+\end{tablenotes}
+\end{threeparttable}
 %\vspace{.3cm}
@@
 \centering
+\begin{threeparttable}
 \caption{Hassle Cost Estimates}\label{table:step2estimates}
-\input{tables/step_2_estimates} \\
-\vspace{.2cm} 
-\footnotesize{Leaking Connections:  548,   Neighboring Connections:  2,151,   Total Obs:  20,299  \\ Standard errors are bootstrapped at the leaking connection-neighborhood level. }
+\input{tables/step_2_estimates}
+\begin{tablenotes}
+\item \footnotesize{Estimates include 548 leaking connections and 2,151 neighboring connections, making 20,299 connection-months.
+\% single/home and neighbor distance are averages within wards.
+Neighbor distance is in meters.
+Standard errors are bootstrapped at the level of the leaking connection (and neighbors).
+}
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 \centering
-\caption{Simulated Method of Moments Estimates}\label{table:smmestimates}
-\input{tables/step_3_estimates_group}\\
-\vspace{.05cm}
-\footnotesize{ Total Households:  \input{tables/totalhhsmm_group}   Total Wards:  599 \\ Standard errors are bootstrapped at the connection level.   }
+\begin{threeparttable}
+\caption{Fixed Cost Estimates}\label{table:smmestimates}
+\input{tables/step_3_estimates_group}
+\begin{tablenotes}
+\item \footnotesize{  Fixed costs are in PhP/month and prices are in PhP/m3.
+\input{tables/totalhhsmm_group} households across 599 wards are included in simulated method of moment estimation using source choices.
+Standard errors are bootstrapped at the connection level }
+\end{tablenotes}
+\end{threeparttable}
 \end{table}
@@
 \input{tables/oos_discount_estimates_group} \\ 
-\footnotesize{Consumer surplus is measured in PhP/month.}
+\vspace{.2cm}
+\footnotesize{Fixed fee and consumer surplus are in PhP/month.}
 \end{table}
@@
 	\input{tables/discount_estimates_group} \\
+	\vspace{.2cm}
 	\footnotesize{Low Users include the bottom 50\% of water users. \\
-	Surplus is measured in terms of PhP/month.}
+	Surplus and fixed fee are in PhP/month.}
 \end{table}
@@
 \\  Social tariffs place all welfare weight on the bottom 50\% of water users.
-\\ Surplus is measured in terms of PhP/month.}
+All terms are monthly.}
 \end{table}

### 2018-09-23 phil_matlab/main.m

@@ -123,7 +123,7 @@ end
                     fileID,est_version,controls,ph_controls,pollfish,real_data,BOOT,TUNE,cd_dir);
                 %}  
                 
-                %{a
+                %{
 [~]=est3(print,tag,mac,size_smp,...
                     fileID,est_version,controls,control_size,ph_controls,given,...
                     a_start,sto,reps,...

### 2018-09-23 phil_matlab/table_step_1_estimates.m

@@ -48,8 +48,8 @@ fileID = fopen(strcat(cd_out,'tables/step_1_estimates_group.tex'),'w');
 
 fprintf(fileID,'%s\n','\begin{tabular}{lcc}');
 fprintf(fileID,'%s\n','& Estimate & Standard Error \\');
-fprintf(fileID,'%s\n','Price Sensitivity : $\alpha$ & \multicolumn{2}{c}{}\\');
-fprintf(fileID,'%s\n','\hline');
+fprintf(fileID,'%s\n','\textbf{Price Sensitivity} : $\alpha$ & \multicolumn{2}{c}{}\\');
+%fprintf(fileID,'%s\n','\hline');
 %fprintf(fileID,'%s\n','\hline');
 
 
@@ -86,8 +86,8 @@ fprintf(fileID,'%s\n',strcat('Over 2 Empl. Members &', ...
 
 fprintf(fileID,'%s\n','\multicolumn{3}{c}{} \\');
 
-fprintf(fileID,'%s\n','Consumption Shock : $\sigma_{\epsilon}$ & \multicolumn{2}{c}{}\\');
-fprintf(fileID,'%s\n','\hline');
+fprintf(fileID,'%s\n','\textbf{Consumption Shocks} : $\sigma_{\epsilon}$ & \multicolumn{2}{c}{}\\');
+%fprintf(fileID,'%s\n','\hline');
 %fprintf(fileID,'%s\n','\hline');
 
 %%%%% SIG EP
@@ -102,7 +102,7 @@ fprintf(fileID,'%s\n',strcat('Three HHs &', ...
 
 fprintf(fileID,'%s\n','\multicolumn{3}{c}{} \\');
 
-fprintf(fileID,'%s\n','Preference Shock : $\sigma_{\psi}$ & \multicolumn{2}{c}{}\\');
+fprintf(fileID,'%s\n','\textbf{Preference Shocks} : $\sigma_{\psi}$ & \multicolumn{2}{c}{}\\');
 fprintf(fileID,'%s\n','\hline');
 
 %%%%%%% QUINTILE OF CONSUMPTION %%%%%%%%
@@ -128,7 +128,7 @@ fprintf(fileID,'%s\n',strcat('Two HHs &', ...
 
 fprintf(fileID,'%s\n',strcat('Three HHs &', ...
[…]

### 2018-09-25 phil_paper/jmp_wjv_v2.tex
add out of sample prediction

@@
 
-\begin{figure}
-\caption{Comparing Predicted and Observed Water Use}\label{figure:predictedwateruse}
-\begin{center}
-\includegraphics[scale=.77]{tables/hist_both.pdf}
-\end{center}
-\end{figure}
-
-Figure~\ref{figure:predictedwateruse} compares the predicted histogram of consumption with observed values.
+%is its inability to match zero consumption values observed in the data.
+
+\begin{table}
+\caption{Model Performance}\label{table:modelperformance}
+\input{tables/sample_prediction}
+\end{table}
+
+Table~\ref{table:modelperformance} compares predicted consumption from the model to observed consumption in the data.
+This exercise finds negligible differences across average consumption and the variance of consumption for connections according to sharing status.
+Closely matching observed patterns, this model improves on previous approaches to demand estimation likely by recovering a separate fixed preference term for each connection as well as rich heterogeneity in the variance terms (\cite{szabo2015value}).
+
+%\begin{figure}
+%\caption{Comparing Predicted and Observed Water Use}\label{figure:predictedwateruse}
+%\begin{center}
+%\includegraphics[scale=.77]{tables/hist_both.pdf}
+%\end{center}
+%\end{figure}
+
+%Figure~\ref{figure:predictedwateruse} compares the predicted histogram of consumption with observed values.
 Vertical red lines indicate the price thresholds in the tariff schedule.
@@
 These shocks are sampled from a multivariate normal distribution taking into account the estimated correlation between sharing partners presented in Table~\ref{table:correstimates}.
+One limitation of the model is that the linear demand structure with normal error terms also predicts occasional negative consumption values.
+Those values are rounded to zero for calculating household utility.
+
 %\footnote{ Future versions will not condition on observed choices in this way, and instead sample households across sharing relationships. }

### 2018-09-25 phil_matlab/table_step_1_elasticities.m

@@ -33,11 +33,8 @@ end
 
         [CA,SE,D,~]=...
                    generate_controls( controls , SHH_control, CONTROL ,Q_obs,t );
-        if mac==1
-           x_r = csvread(strcat(cd_dir,'BOOT/xBOOT',num2str(est_version),'_',num2str(i),'.csv'))  ;
-        else
-           x_r = csvread(strcat(cd_dir,'BOOT\xBOOT',num2str(est_version),'_',num2str(i),'.csv'))  ;
-        end
+
+       x_r = csvread(strcat(cd_dir,'results/x',num2str(est_version),'.csv'))  ;
         
        sig_ep = x_r(1:controls(1));
        sigma_1 = x_r(controls(1)+1:controls(1)+controls(2)+SHH_control);
@@ -65,11 +62,17 @@ HH=length(t);
 
 %R_to_S=size_smp(2);
 
-
+shr = CONTROL(:,2);
+true = [mean(Q_obs) mean(Q_obs(shr==1)) mean(Q_obs(shr==2)) mean(Q_obs(shr==3))];
+tstd = [std(Q_obs) std(Q_obs(shr==1)) std(Q_obs(shr==2)) std(Q_obs(shr==3))];
 
 %%%% ELASTICITY!!! %%%%%%
 elasticity = zeros(boot_max,7);
-    
+   
+pred = zeros(boot_max,4);
+pstd = zeros(boot_max,4);
+
+
     for i = 1:boot_max
 
         t=csvread(strcat(cd_dir,'BOOT/tBOOT',num2str(est_version),'_',num2str(i),'.csv'));
@@ -94,7 +97,8 @@ elasticity = zeros(boot_max,7);
             Q_obs  = X(:,1) ; 
 
             CONTROL = X(:,6:5+control_size);
-
+    
+        shr = CONTROL(:,2);
 
         [CA,SE,D,~]=...
                    generate_controls( controls , SHH_control, CONTROL ,Q_obs,t );
@@ -125,6 +129,10 @@ elasticity = zeros(boot_max,7);
         elasticity(i,1) = 100.*(mean(Q_obs_pred)-mean(Q_obs_pred1))./mean(Q_obs_pred);
         
         
+        Q_obsp = Q_obs_pred.*(Q_obs_pred>0);
+        
+        pred(i,:)=[mean(Q_obsp) mean(Q_obsp(shr==1)) mean(Q_obsp(shr==2)) mean(Q_obsp(shr==3))];
[…]

### 2018-09-28 phil_paper/jmp_wjv_v2.tex
try splitting best-response

@@
 I find that despite relatively high marginal costs of sharing, shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.
-At the same time, informal sharing networks act as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
+At the same time, informal sharing networks serve as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
 
@@
 I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.
-This policy reduces access by incentivizing households to substitute toward water vendors (which mainly include deepwells and water refilling stations).
+This policy reduces access by incentivizing households to substitute toward water vendors, which mainly include deepwells and water refilling stations.
 
@@
 
-In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal pricing policy.
+In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal water pricing.
 First, I do not directly model environmental, health, or other externalities associated with piped water use.
-From a policy perspective, water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
+Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
 Finally, the counterfactual exercises borrow the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
@@
 Evaluating different pricing policies requires measuring demand at the household level as well as costs associated with providing piped water.
-For information about these attributes, I developed a partnership with one of the regulated, private providers in Manila who provided both billing records as well as information about the regulatory structure, pricing, and production costs.
+Data was gathered through a partnership with one of the two regulated, private providers in Manila who provided both billing records as well as information about the regulatory structure, pricing, and production costs.
 Complete billing records for each water connection including the monthly meter reading, the total bill charged, and the precise location for each meter serve as the primary measure of quantity choices.
@@
 These connections provide a useful source of price variation which is described in Appendix~\ref{appendix:ratechangeelasticity}.}  The monthly meter reading is used as the measure of consumption for each connection.
-Meter readings are rounded to the nearest cubic meter, and I limit consideration to meter readings below 100 $\text{m}^{3}$ in order to exclude pipe leaks as well as meter reading errors (readings above 100 $\text{m}^{3}$ compose less than 0.7\% of the sample).
-
-Since the object of interest for welfare is household-level demand, I merge the billing records to unique survey data recording information on households using each connection.
-To evaluate the performance of the water provider, the regulator contracted with a local university to conduct the Public Assessment of Water Services (PAWS) in three waves from 2008 to 2012, surveying around 50,000 water connections.\footnote{Appendix~\ref{appendix:pawssampling} describes the sampling design and tests the extent to which it may be correlated with demographic characteristics.
-This exercise finds relatively weak correlations in economic terms with key characteristics.}  I have collected unique identifiers for this survey, which allows responses to be linked to water connections.
-The connection survey records the total number of households and people using each connection, providing the primary measure of sharing behavior.
+Meter readings are rounded to the nearest cubic meter limited to monthly readings below 100 $\text{m}^{3}$ in order to exclude pipe leaks as well as meter reading errors (readings above 100 $\text{m}^{3}$ compose less than 0.7\% of the sample).
+
+Since the object of interest for welfare is household-level demand, the billing records are merged to survey data recording information on households using each connection as well as demographics for the owners of each connection.
+To evaluate the performance of the water provider, the regulator contracted with a local university to conduct the Public Assessment of Water Services survey in three waves from 2008 to 2012, surveying around 50,000 water connections.\footnote{Appendix~\ref{appendix:pawssampling} describes the sampling design and tests the extent to which it may be correlated with demographic characteristics.
+This exercise finds relatively weak correlations in economic terms with key characteristics.}  The connection survey records the total number of households and people using each connection, providing the primary measure of sharing behavior.
 The connection survey also includes basic demographics for the owner of the connection.
-The demographics used in this paper are household size, dwelling type (whether apartment, duplex, or single house), number of employed household members, and whether the head of household is employed in a low-skill profession.
+The demographics used in the analysis include household size, dwelling type (whether apartment, duplex, or single house), number of employed household members, and whether the head of household is employed in a low-skill profession.
 %consumption and water source choices at the household-level.  
@@
 
-A full analysis of water usage in Manila also requires describing households that choose to use water from local vendors.
-For information on households that are using water from alternative sources, I turn to the 2010 Census of Population and Housing.
-Households are defined as connected to the piped network if they report using a ``faucet community water system'' for their cooking, laundry, or bathing needs.\footnote{The census was designed largely for rural populations so it does not directly ask whether households are connected to a piped water network.}  Alternatively, I define households as using from a water vendor if they report any other category, which includes deep wells, peddlers, or other sources.
-I then construct similar demographic measures to the connection survey using questions in the census and compare these measures across these data sources in Table~\ref{table:pawstocensus} of Appendix~\ref{appendix:pawstocensus}.
-Households that own a connection in the connection survey are similar to households connected to the piped water network in the Census data.
-To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 599 wards of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.
+A full analysis of water usage in Manila also requires measuring households that are unconnected to the bulk water system and instead use water from local vendors.
+The 2010 Census of Population and Housing records demographics for households that are using water from alternative sources.
+Households are defined as connected to the piped network if they report using a ``faucet community water system'' for their cooking, laundry, or bathing needs.\footnote{The census was designed largely for rural populations so it does not directly ask whether households are connected to a piped water network.}  Alternatively, households are considered to be using from a water vendor if they report any other category, which includes deep wells, peddlers, or other sources.\footnote{Since demographic questions in the census and connection surveys are worded differently, Table~\ref{table:pawstocensus} of Appendix~\ref{appendix:pawstocensus} compares measures across the two data sources for households that own connections finding broadly similar patterns.}  Census data is merged geographically with the connection survey for 599 wards in Manila.
+
+%To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 599 wards of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.
 %\footnote{Regions are chosen to overlap with ward administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}
 
-For additional information on water sharing relationships between households, I fielded a small, non-representative survey of 600 households via mobile phone app.
+For additional information on water sharing relationships between households, I fielded a small, non-representative survey of 600 households via mobile phone application.
 This survey asks about issues associated with using different water sources, basic demographics, as well as how the bill and connection fee are paid for sharing households.
-Appendix~\ref{appendix:pollfish} includes additional details on this survey and finds roughly similar measures between the connection survey and the mobile survey, suggesting that the mobile survey may provide a reasonable descriptive picture of sharing in Manila.
+Appendix~\ref{appendix:pollfish} compares this survey to the connection survey finding roughly similar rates of sharing and demographic characteristics.
+
+%includes additional details on this survey and finds roughly similar measures between the connection survey and the mobile survey, suggesting that the mobile survey may provide a reasonable descriptive picture of sharing in Manila.
 
 The water provider also maintains call records of all service complaints, which can be linked to individual connections.
-This data is used to measure instances where households face unanticipated shocks to their water source as part of the identification strategy to estimate the marginal costs of sharing water.
+This data is used to measure instances where households face unanticipated shocks to their water source, which are used to identify the marginal costs of using water from a neighbor.
 Finally, the water provider tracks data on the marginal cost of pumping an additional cubic meter of water as well as the costs associated with installing new connections.
 These data provide inputs into the provider's budget constraint, which are necessary for computing counterfactual pricing regimes.
-Supplemental survey data from a subset of Manila include income measures that are used to impute income for the remainder of the sample across a variety of demographic variables and their interactions.
+
+Supplemental survey data from a subset of Manila include income measures that are used to approximate household income using the full set of demographic measures and their interactions.
 
@@
 The columns group connections by the number of households they serve: one, two, or at least three.
-
-The first rows provide demographic information from the connection survey for households who own connections.
-Smaller and younger households are more likely to share water with neighbors.
+Demographics for connection owners indicate that smaller, slightly younger, and poorer households are more likely to share water with neighbors.
+Sharing households are over twice as likely to reside in duplexes possibly because transporting water between neighbors requires less effort for duplex residents.
+
+Larger numbers of households sharing a water connection are correlated with more total water usage, but less water per person.\footnote{Total People Served by a connection includes both the owning household and any other households using a connection.}  This decline may have many possible drivers: (1) sharing households face higher prices by locating at a higher point on the tariff schedule (Figure~\ref{figure:tariff}), (2) sharing households may face hassle costs in fetching water from neighboring taps, (3) these price effects may incentivize low-demand households to select into sharing relationships, consistent with the demographic patterns, and (4) low-demand households may have idiosyncratic preferences for sharing relationships.
+On average, monthly water bills (inclusive of service fees) take up around \input{tables/incshr}\unskip\% of household income, which does not include other unobserved costs in accessing water.
+These findings suggest that policies which affect sharing choices can have significant impacts on water consumption as well as monthly expenditures.
+
+%Demographics for connection owners indicate that smaller and younger households are more likely to share water with neighbors.
 Because household size is a strong proxy for water demand, this finding suggests that sharing a connection is negatively correlated with household water demand.
@@
 
-Table~\ref{descriptives} summarizes water use and sharing behavior for these connections, merging information from the connection survey with the billing records.
-Larger numbers of households sharing a water connection are correlated with higher total water usage, but less water per person.\footnote{Total People Served by a connection includes both the owning household and any other households using a connection.}  This decline in usage per person may have many possible drivers: (1) sharing households face higher prices by locating at a higher point on the tariff schedule (Figure~\ref{figure:tariff}), (2) sharing households may face hassle costs in fetching water from neighboring taps, (3) these price effects may incentivize low-demand households to select into sharing relationships, consistent with the demographic patterns, and (4) low-demand households may have idiosyncratic preferences for sharing relationships.
-On average, monthly water bills (inclusive of service fees) take up around \input{tables/incshr}\unskip\% of household income, which does not include other unobserved costs in accessing water.
-These findings suggest that policies which affect sharing choices can have significant welfare consequences.
+%Table~\ref{descriptives} summarizes water use and sharing behavior for these connections, merging information from the connection survey with the billing records.
 
@@
 Table~\ref{descriptives} also computes the total number of households using from each source.
-I assume that households sharing with one or two other households are uniquely linked to one connection so that the population of households connected to the network can be computed by summing the number of households served by each connection.
-This assumption is consistent with the presence of fixed costs in setting up a connection or a sharing relationship.
+This calculation requires the additional assumption that households sharing with one or two other households are uniquely linked to one connection.
+This way, the population of households connected to the network can be computed by summing the number of households across all connections.
+This assumption is consistent with the presence of fixed costs in setting up a connection or a sharing relationship so that households stay committed to one water source.
 To the extent that households are drawing water from multiple connections, this assumption may lead to an overestimation of the population engaged in sharing relationships.
-Under this assumption, I find that \input{tables/shr_individual}\unskip\% of connected households receive their water from an individual connection, \input{tables/shr_1hh}\unskip\% are involved in a sharing relationship with a single neighbor, and \input{tables/shr_2hh}\unskip\% are in a sharing relationship with 2 or more other households.
+With this assumption, \input{tables/shr_individual}\unskip\% of connected households receive their water from an individual connection, \input{tables/shr_1hh}\unskip\% are involved in a sharing relationship with a single neighbor, and \input{tables/shr_2hh}\unskip\% are in a sharing relationship with 2 or more other households.
 These proportions do not take into consideration households that are using from water vendors, which are discussed in more detail below.
-Each water connection contributes over six years of billing records on average.
-
-Since the connection survey only includes households connected to piped water, I use census data to learn about households using from water vendors.
-\input{tables/vendor_total}\unskip\% of the population report using vendors, which is composed of \input{tables/vendor_well}\unskip\% of households using from a ``deep well'' and \input{tables/vendor_peddler}\unskip\% using from a ``peddler'' while the remaining fall into an ``other'' category.
+Each water connection contributes over four years of billing records on average.
+
+Since the connection survey only includes households connected to piped water, census of population and housing data is required to learn about households using from water vendors.
+In this data, \input{tables/vendor_total}\unskip\% of the population report using vendors, which is composed of \input{tables/vendor_well}\unskip\% of households using from a ``deep well'' and \input{tables/vendor_peddler}\unskip\% using from a ``peddler'' while the remaining fall into an ``other'' category.
 Anecdotal evidence suggests that groundwater from wells often has very low quality.
@@
 This partition embeds the assumption that neighborhoods are mutually exclusive so that a household located in one neighborhood cannot share water with households in a nearby neighborhood.
-Restricting the choice set in this way may tend to overestimate the costs that households face in finding a sharing partner.\footnote{This limitation is discussed in more detail in Section~\ref{section:fixedcostestimation}}
-
-In the first period, each household makes a one-time decision about their water source between purchasing a connection, using a neighbor's connection, or buying from a local water vendor.
-These decisions result in a set of water connections for each neighborhood ranging from an empty set if all households use from a vendor to equaling the size of the neighborhood if each household uses an individual connection.
-If households choose to connect to the network, each connection, $C$, serves a set of households given by $S$, which depends on which households have decided to share the water connection.
-Also, let the index $C$ indicate connection-level attributes, summing over all households using connection $C$.
+Restricting the choice set in this way is necessary for computation but may in some cases overestimate the costs that households face in finding a sharing partner.\footnote{This limitation is discussed in more detail in Section~\ref{section:fixedcostestimation}}
+
+In the first step, each household makes a one-time decision about their water source between 1) purchasing a connection, 2) using a neighbor's connection, or 3) buying from a local water vendor.
+These decisions result in a set of water connections for each neighborhood ranging from an empty set (if all households use from a vendor) to the whole neighborhood (if each household uses an individual connection).
+Let each connection, $C$, serve $S$ households that have decided to share the connection.
+For ease of notation, let the subscript $C$ indicate connection-level attributes, summing over all households using from connection $C$.
+
 This model does not allow for households to choose different water sources over time, which is consistent with large fixed costs involved in initially purchasing a connection or establishing a sharing relationship.
-At the same time, some households may exogenously lose access to their water source, forcing these households to substitute toward other sources as detailed in Section~\ref{section:hasslemodel}.
-
-Conditional on their water source choice, households then choose how much water to use each month.
-Since water sources provide utility through monthly consumption, this section describes the decision process in reverse order, first characterizing monthly water consumption choices (taking the initial source choice as given) and second, describing the water source choice (according to the expected utilities from using each source).
+Section~\ref{section:hasslemodel} extends the model to allow for cases where households exogenously lose access to their current water source and must substitute toward another nearby source.
+
+In the second step, each household then chooses how much water to use each month from their source.
+Since water sources provide utility through monthly consumption, the following section describes the decision process in reverse order, first characterizing monthly water consumption choices (taking the initial source choice as given) and second, describing the initial water source choices.
 
@@
 In choosing how much water to use each month, households using piped water face the difficult task of coordinating water consumption among all household members.
-For example, consider a household head trying to manage water consumption across all of their household members each month.
-This task would involve monitoring the meter located outside of their dwelling and observing water use among all members.\footnote{Given that many developing countries feature steeply increasing prices with monthly usage, these coordination challenges may magnify any distortions caused by non-linear pricing.}  Mobile survey data indicate that \input{tables/no_info}\unskip\% of surveyed household members do not recall how much they paid for water in the last month while \input{tables/no_use}\unskip\% do not recall the amount that their household consumed in the previous month.
-
-As a simple way to capture this coordination task, let each household $i$ set a goal for water use each month, $w_i$, knowing that consumption shocks, $\epsilon_i$, may increase or decrease the realized amount of usage.
+For example, consider the head of a household trying to manage water consumption across all of their household members each month.
+This task would involve monitoring the meter located outside of their dwelling and coordinating water use among all members.\footnote{Given that many developing countries feature steeply increasing prices with monthly usage, these coordination challenges may magnify any distortions caused by non-linear pricing.}  Consistent with these challenges, mobile survey data indicate that \input{tables/no_info}\unskip\% of surveyed household members do not recall how much they paid for water in the last month while \input{tables/no_use}\unskip\% do not recall the amount that their household consumed in the previous month.
+
+As a simple way to capture this coordination task, let each household $i$ set a goal for water use each month, $w_i$, knowing that unobserved consumption shocks, $\epsilon_i$, may increase or decrease their realized amount of usage.
 Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.
-Household utility over water, $W_i$ and a numeraire good, $x_i$ is assumed to take the following shape:
+Household utility over total water, $W_i$ and a numeraire good, $x_i$ is assumed to take the following shape:
 \begin{align}\label{equation:umaxfirst}
@@
 \end{align}
-Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as in Figure~\ref{figure:consumptionhistogram}.
-Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are price sensitive.
-These terms have clearer interpretations in the demand function below.
-The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean, variance terms, $\sigma_{\epsilon}^2$, and allowing for correlation with neighboring households, ${\rho}^{\epsilon}_{i,j}$.
-Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible shocks, allowing them to maximize expected utility.
+Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as in Figure~\ref{figure:consumptionhistogram}.\footnote{This utility form builds on \cite{einav2013selection} who use a similar form to characterize extensive and intensive choices of health insurance.}   Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are price sensitive.
+The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean and variance terms, $\sigma_{\epsilon}^2$, allowing for correlation with neighboring households $i$ and $j$ through term ${\rho}^{\epsilon}_{i,j}$.
+Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible consumption shocks, allowing them to maximize expected utility.
 
 Households that are using water from a neighbor's tap may face an additional utility cost per gallon of water $H_i$.
-This hassle cost captures any inconvenience associated with using water from a neighbor's tap.
-The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.
+This hassle cost captures any inconvenience associated with using an additional unit of water from a neighbor's tap.\footnote{Accordingly, the connection owner is assumed to face zero hassle cost.}  The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.
 These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.
-Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households face a homogeneous hassle cost, $H_i$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.
+
+%To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.
+Therefore, all households, $i\neq1$, using from a neighbor's tap have a positive hassle cost, $H$, while the connection owner, $i=1$, has zero hassle cost.
+
+%FIX HERE!
+
+%Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households face a homogeneous hassle cost, $H_i$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.
 The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.}
@@
 Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.
-The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
+The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:\footnote{In this case in Manila, $\overline{W}^{0}$ is zero while $\overline{W}^{K}$ is infinity.}
 \begin{align*}
@@
 \begin{cases}
-      p^{1} &\text{ if } W_C \in [\overline{W}^{0}(=0),\overline{W}^{1}], \\
+      p^{1} &\text{ if } W_C \in [\overline{W}^{0},\overline{W}^{1}], \\
       p^{2} &\text{ if } W_C \in [\overline{W}^{1},\overline{W}^{2}], \\
       ...   &\text{ ...}, \\
-      p^{K} &\text{ if } W_C \in[\overline{W}^{K-1},\overline{W}^{K}(=\infty)]
+      p^{K} &\text{ if } W_C \in[\overline{W}^{K-1},\overline{W}^{K}]
     \end{cases}
@@
 Data does not track household water source choices over time in a comprehensive way, which limits the extent to which the model can distinguish between one-time connection costs and monthly service/maintenance costs.
-This limitation means that the model cannot address the optimal timing of fixed payments or capture any potential heterogeneity in monthly fixed costs.
-
-Water sharing relationships impact monthly consumption choices through the budget constraint.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.
-Therefore, all households, $i\neq1$, using from a neighbor's tap have a positive hassle cost, $H$, while the connection owner, $i=1$, has zero hassle cost.
-
-This model assumes that the monthly water bill is split evenly between all sharing households.
-Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.
+This limitation means that the model cannot address the optimal timing of fixed payments or capture potential heterogeneity in monthly fixed costs.
+
+Water sharing relationships impact monthly consumption choices through the budget constraint.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  The model assumes that the monthly water bill is split evenly between all sharing households.
+Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also exend across households.
 Among owners of the water connection responding to the mobile survey, \input{tables/bill_split}\unskip\% report splitting the water bill evenly or alternating payment each month, \input{tables/bill_fixed}\unskip\% charge sharing households a fixed amount each month regardless of their consumption, and \input{tables/bill_usage}\unskip\% charge other users a price according to their usage.\footnote{The remaining households report ``I don't know'' or ``other.''}  Evenly splitting the bill, alternating payment, or charging a fixed amount provide easy ways to extract compensation without requiring specific information on the monthly consumption of each sharing household.
@@
 Sharing households must negotiate over how to pay the monthly fixed costs (including the fixed fee paid to the firm and any unobserved costs of using a connection).
-The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement.
-Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions.
-For ease of exposition, this section assigns a fixed cost, $F_i$ to each household and postpones discussion of how the total fixed cost may be divided between households to Section~\ref{section:watersourcechoice}.
+The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement, allocating $F_i$ to each household.
+Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions and Section~\ref{section:watersourcechoice} later discusses how fixed costs are divided.
 
@@
 The full budget constraint is a piece-wise expression of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.
-$B_{C,k}$represents the total water bill for connection $C$ given the tariff schedule.
-This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.\footnote{In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.
+$B_{C,k}$ represents the total water bill for connection $C$ given the tariff schedule.
+This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.
+%\footnote{In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.
 In this scenario, the household does not face any hassle costs, $H_i$, and pays the total bill from its corresponding consumption.}
@@
 For example, with an increasing block tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.
-Rewriting the utility function in equation (\ref{equation:umaxfirst}) by substituting the numeraire good, $x$, with the budget constraint, expected utility for household $i$ over the consumption shocks takes the following form:
+
+Substituting the numeraire good, $x_i$ for the budget constraint in household utility from equation (\ref{equation:umaxfirst}) simplifies the household's problem to a single choice variable --- targeted consumption, $w_i$.
+The household's expected utility problem over consumption shocks $\epsilon_C$ then takes the following form:
 
@@
 
-Taking the derivative of expected utility with respect to $w_i$ while letting $\Phi(.)$ equal the standard normal cumulative distribution function produces the following first-order condition:
+Taking the derivative of expected utility with respect to $w_i$ (holding sharing partners' choices $w_{-i}$ fixed) while letting $\Phi(.)$ equal the standard normal cumulative distribution function produces the following first-order condition:
 \begin{align}
@@
 \end{align}
-The sum of the cumulative distribution functions in equation (\ref{equation:firstordercondition}) calculate the expected marginal price faced by the connection, which is scaled by the number of households sharing the connection, $S$.
-This expression intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the household to higher prices.
-Higher total consumption, $W_C$, raises the probability that the exogenous shock, $\epsilon_C$, places the households in a higher price range.
+The summation in equation (\ref{equation:firstordercondition}) calculates the expected marginal price faced by the connection, which is scaled by the number of households sharing the connection, $S$.
+This expression intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the household to higher prices in expectation.
 This first-order condition characterizes the best-response functions for each household.
-
-The model deviates from the direct solution to this program in two ways.
-
-First, I use an approximation for the normal cumulative distribution function taking the following form:
-\begin{align*}
+%Higher total consumption, $W_C$, raises the probability that the exogenous shock, $\epsilon_C$, places the households in a higher price range.
+
+To arrive at a tractable expression for water demand, I simplify the best-response function by assuming that households approximate the normal distribution with a simple uniform distribution.
+This assumption implies that households give zero likelihood to extremely high or low consumption shocks and even likelihood to moderate consumption shocks.
+From an empirical perspective, this function allows for an analytical solution to the demand function while ensuring that the estimation can rely on normally distributed errors to estimate rich preference heterogeneity.
+
+I use the following piece-wise function form to approximate the normal cumulative distribution:
+
+\begin{align*}
+%\label{equation:approximation}
+\begin{split}
 g(z)=& 
@@
     \end{cases}
-\end{align*}
-This function can be interpreted in two ways.
-On one hand, this function provides a useful approximation, allowing for an analytical solution to the demand function while the empirical exercise can rely on the properties of the normal distribution.
-This approach recovers rich heterogeneity in preferences through a tractable likelihood function.
-Appendix~\ref{appendix:linearapprox} graphs this approximation against a standard normal c.d.f.
-and conducts a simulation exercise, finding negligible evidence that this approximation significantly biases the estimates or affects welfare calculations.
-On the other hand, this function implies the additional economic assumption that household decision-makers approximate normally distributed shocks with a simple uniform distribution.
-In this case, households are assumed to give zero likelihood to extremely high or low shocks and even likelihood to moderate shocks.
-
-Second, I impose an ex-ante assumption on the size of consumption shocks, $\sigma_{\epsilon_C}$.
-Given this linear approximation, the variance of the consumption shocks determine which prices enter the optimal demand function at each level of demand.
-For example, in the limiting case where $\sigma_{\epsilon_C}$ is very large, demand becomes a function of all prices at every point because the consumption shocks are large enough to produce a positive probability of reaching every price segment regardless of where the households choose to consume.
-In the opposite scenario where $\sigma_{\epsilon_C}$ is close to zero, then households can perfectly target their consumption and therefore, only need to consider the single price local to any desired consumption level.
-I identify a demand function that best fits the observed consumption data by reestimating demand according to different ex-ante assumptions on $\sigma_{\epsilon_C}$.
+\end{split}
+\end{align*}
+
+% This  implies the additional economic assumption that household decision-makers approximate normally distributed shocks with .  
+% This approach recovers rich heterogeneity in preferences through a tractable likelihood function.  
+% I impose an ex-ante assumption on the size of consumption shocks, $\sigma_{\epsilon_C}$. 
+%are partially determined by the variance of the consumption shocks, $\sigma_{\epsilon_C}$.
+For example, when $\sigma_{\epsilon_C}$ is very large, demand becomes a function of all prices at every point because the consumption shocks are large enough to produce a positive probability of reaching every price segment regardless of where the households choose to consume.
+
+Appendix~\ref{appendix:linearapprox} graphs this approximation against a standard normal cumulative distribution function and simulates optimal demand under both distributions, finding negligible evidence that this approximation would substantially bias the estimates or affect welfare measures.
+
+After replacing the normal cdf $\Phi(.)$ for $g(.)$, the best-response function in equation (\ref{equation:firstordercondition}) now includes the weighted sum of piece-wise functions, $g(.)$, which may also overlap with each other.
+This weighted sum determines the marginal prices that each household must consider in choosing their optimal consumption-level.
+The degree of overlap depends on the variance in consumption shocks, $\sigma_{\epsilon_C}$.
+For example, when $\sigma_{\epsilon_C}$ is very large, the consumption shocks produce a positive probability reaching any price segment, ensuring full overlap in piece-wise functions.
+
+there is full overlap meaning that households consider all prices at every consumption level.
+
+In the opposite case, having zero consumption shocks produces zero overlap so that households only consider the single price local to their consumption level.
+
+Identifying a particular piece-wise best-response function requires imposing bounds on $\sigma_{\epsilon_C}$ ex-ante, ensuring a certain level of overlap.
+I take the approach of 1) assuming bounds on $\sigma_{\epsilon_C}$, 2) constructing the corresponding demand function, and 3) estimating the model to see if the estimated $\sigma_{\epsilon_C}$ lies within the bounds.
 Appendix~\ref{appendix:sigmanuassumptions} provides the results from this exercise finding that the results are robust to this ex-ante assumption.
+
  This section proceeds by describing the demand function that is most consistent with the data.
+
+% determine which prices enter the optimal demand function at each level of demand.
 
@@
 This game results in a unique equilibrium of source choices given the preferences parameters for each household as well as the costs of using each water source.
-This game also allows for a mapping between the fixed costs of setting up and maintaining each water source and cross-sectional variation in source choices, which informs the third step of the estimation strategy.
+
+%This game also allows for a mapping between the fixed costs of setting up and maintaining each water source and cross-sectional variation in source choices, which informs the third step of the estimation strategy.
 The fundamental assumption of this model is that the decision to share a water connection balances splitting the fixed costs among many households against facing higher marginal costs --- hassle costs in fetching water and free-rider costs splitting the water bill.
@@
 The latter price matches closely to the estimated price of 37.16 PhP/$\text{m}^3$, providing additional support to the structural estimates.
-
-\subsection{Out-of-Sample Test: A Connection Fee Discount Program}\label{section:oostest}
-
-A connection fee discount program implemented by the water company provides a useful setting to test the out-of-sample predictions of the economic model: do predicted water source choices match observed choices in response to a discount in the fixed fee?
-According to the model, reducing the fixed fee would make individual connections more attractive relative to shared connections or water vendors.
-This section compares the predicted and observed increase in connections in response to the program.
-
-%To evaluate how well the model is able to match observed substitution patterns between water sources, I investigate reduced-form evidence from a connection-fee discount program since this variation is not used explicitly in any part of the estimation.
-%[chk] The fundamental assumption of the model is that the decision to share a water connection balances splitting the fixed fee among many households against facing marginal hassle costs in fetching water as well as free-rider costs in splitting the water bill.
-Under this assumption, reducing the fixed fee would lead to substitution away from shared connections toward individual connections.
-This section uses quasi-experimental variation in the connection-fee to test this assumption.
-
-In 2009, the government regulator issued new regulations reducing the connection fee from 6,000 to 2,400 PhP for low-income areas partially in an effort to extend access and affordability to low-income households.
-Under the assumption that households reside in Manila for 80 months and face negligible credit constraints, this discount lowered the monthly fixed fee faced by households by 45 PhP on average.
-In the presence of credit constraints, this estimate can be interpreted as a lower bound on the policy's impact on the monthly fixed price faced by households.
-Figure~\ref{figure:discountfirststage} indicates the share of new connections receiving discounted fees.
-The sudden rise by \input{tables/first_stage}percentage points coincides with the change in regulations and will be used to identify the timing of the discount policy.
-A small fraction of households are observed to receive connection fee discounts prior to the program as part of other, smaller pro-poor strategies implemented by the water provider.
-% and these households are excluded from the main analysis
-
-\begin{figure}
-\centering
-\caption{Share of New Connections Receiving a Discount}\label{figure:discountfirststage}
-\includegraphics[scale=.7]{tables/diff_595_first_stage.pdf}
-\end{figure}
-
-Since the data do not identify precisely which local areas or specific households were eligible for the discount, additional assumptions are necessary to measure eligibility.
-First, I define treated areas as any meter reading unit that receives at least one discounted connection over the full duration while control areas include any meter reading units that never receive discounts.
-Meter reading units (MRUs) are common geographical designations used by the water provider and include between 100 and 500 meters.
-There are 3,757 MRUs in the service area.
-I include only MRUs that were established long prior to the discount fee program to ensure that these areas are likely to be at saturation in terms of water connections prior to the program.
-Second, to identify the share of households in treated areas that were eligible, I conceptually divide new connections into two groups --- (1) households substituting away from shared connections or water vendors in response to the program and (2) new households migrating to the city.
-I then measure eligibility as the share of new migrants receiving discounted connections fees after the policy.
-
-This approach requires the following assumptions:
-\begin{enumerate}
-	\item Before the discount program, households that have already moved to the city have reached an equilibrium at the current prices; therefore, all new full-price connections in the pre-period are driven by migration to the city.
-This assumption is consistent with the large fixed costs incurred in setting up a new connection.
-	\item The rate of migration is unaffected by the policy, which is supported by the stable rate of new connections for untreated areas in Figure~\ref{figure:discountreducedform} below.  
-	\item After the discount policy is implemented, all new migrant households that are eligible take up the discounted connections.
-	\item Rates of eligibility are similar across migrant and non-migrant groups.
-\end{enumerate}
-Under these assumptions, I compute the impact of the policy on new full-price connections in the treated areas and interpret any reduction in the rate of new full-price connections as driven by new migrants receiving discounted connections.
-I estimate the following simple difference-in-differences equation across all treated and untreated Meter Reading Units, $m$, and months, $t$, pre and post policy implementation:
-\begin{align*}
-\text{New Full-Price Connections}_{t,m} &= \beta_1 \text{Post X Treated}_{t,m} + \beta_2 \text{Post}_{t,m} + \beta_3 \text{Treated}_{t,m} + \epsilon_{t,m}
-\end{align*}
-Table~\ref{table:difffullpriced} presents the results from this estimation.\footnote{These results do not exactly match reduced-form results from Table~\ref{table:diffdiscountreducedform} because the data only have information on the price per connection for about 80\% of new connections.}  Adding the coefficients in Table~\ref{table:difffullpriced} shows that in the absence of the policy, treated areas were expected to have added 0\input{tables/would_have_added}new full-price connections each month; yet, as a result of the policy, these areas actually experienced 0\input{tables/actually_added}new full-price connections with the remaining households receiving discounted connections.
-This discrepancy implies that \input{tables/substitution}\unskip\% of households were eligible for the program.
-
-\begin{table}
-\centering
-\caption{Difference-in-Differences Estimate for Full Priced Connections}\label{table:difffullpriced}
-\input{tables/diff_595_reg_secondary}
-\end{table}
-
-I next examine the reduced-form impacts of the policy using the following event-study regression equation, which computes the average number of new connections in bi-monthly intervals relative to the discount fee program for both treated and untreated areas:
-\begin{align*}
-\text{New Connections}_{t,m} &= \sum_{r=0}^{T} \beta^{\text{Treated}}_{r} \mathbbm{1} \{t=r\} + \sum_{r=0}^{T} \beta^{\text{Untreated}}_{r} \mathbbm{1} \{t=r\}  +  \theta_{m} + \epsilon_{t,m} \\
-t &= \text{2 Month Intervals}\\
-m &= \text{Meter Reading Unit}
-\end{align*}
-Figure~\ref{figure:discountreducedform} provides the graphical estimates from this equation.
-The untreated group on the left-hand side exhibits a very stable trend in new connections with no changes relative to the discount program.
-This finding is consistent with steady population growth generating a constant rise in the total number of connections.
-
-The treated group on the right-hand side shows a relatively stable pre-trend interrupted by a substantial increase in the number of connections just following the discount program implementation.
-This increase lasts for a couple years before returning to pre-program levels.
-These trends provide evidence that households who are sharing water or purchasing from vendors are gradually learning about the price change and choosing to purchase their own connections.
-After a couple years, this additional demand for connections has been satisfied, letting migration take over as the sole driver of new connections.
-\begin{figure}
-\centering
-\caption{Reduced Form: Connection Fee Discount}\label{figure:discountreducedform}
-\includegraphics[scale=.8]{tables/diff_595.pdf}
-%\includegraphics[scale=.57]{tables/diff_595_treated.pdf}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Difference-in-Differences Estimate}\label{table:diffdiscountreducedform}
-\input{tables/diff_595_reg_primary}
-\end{table}
-
-A simple difference-in-differences estimate provided by Table~\ref{table:diffdiscountreducedform} calculates an increase of 0\input{tables/red_form_est}new connections per month for the treated areas on a base average of 0\input{tables/red_form_base}new connections per month.
-Aggregated over the full \input{tables/treated_months}months of the program, this program led to a total of \input{tables/total_effect}new connections per Meter Reading Unit.
-Given that the average Meter Reading Unit has \input{tables/mru_size}connections over the full time period, this program generated about a \input{tables/percent_increase_discount}\unskip\% increase in the number of new connections.
-
-To compare results from this policy to counterfactual estimates from the model, I now convert the change in number of connections induced by the policy to a shift from shared and vendor connections to individual connections.
-Given that \input{tables/share_2_hhs}\unskip\% of connections serve two households and \input{tables/share_3_hhs}\unskip\% of connections serve three or more households, and 5\% of households access water from vendors, then \input{tables/mru_size}connections per Meter Reading Unit are calculated to serve an average population of around \input{tables/population_served}households.
-This policy results in a \input{tables/increase_in_individual_connections}percentage point increase in the share of households owning a connection, which can be directly compared to predictions from the counterfactual exercise.
-
-In order to relate the quasi-experimental results from the policy to the model outputs, I simulate the impacts of the connection-fee discount policy by (1) randomly selecting \input{tables/substitution}\unskip\% of households, (2) lowering the fixed fee by 45 PhP for these households, and (3) recomputing their water source choices.
-As a result of this policy, the share of households owning a water connection is calculated to rise by \input{tables/out_of_sample_inc_ind_conn_group}percentage points.
-This finding is smaller, but comparable to the reduced form results indicating a \input{tables/increase_in_individual_connections}percentage point increase.
-There may be many reasons that the counterfactual results lag behind the reduced-form estimates.
-First, the assumptions used to amortize the connection fee discount into monthly terms  may work to understate the impact of the discount, especially in cases where households face credit-constraints in funding large, lump-sum connection fees.
-Second, in practice, the discount policy targeted a low-income segment of the population, which may have different substitution patterns across water sources.
-
-Despite these caveats, the fact that the reduced-form and model-based estimates are similar in magnitude lends support to the counterfactual exercises in Section~\ref{section:counterfactualexercises}.
-Table~\ref{table:oosestimates} calculates the impacts of this connection fee discount on water source choices as well as consumer welfare.
-Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended.
-Since utility is assumed to be quasi-linear, consumer welfare is measured in PhP/month.
-Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile_group}\unskip\% of users.
-
-\begin{table}
-\centering
-\caption{Connection Fee Discount: Out-of-Sample Test Results}\label{table:oosestimates}
-\input{tables/oos_discount_estimates_group} \\ 
-\vspace{.2cm}
-\footnotesize{Fixed fee and consumer surplus are in PhP/month.}
-\end{table}
 
@@
 
+\subsection{Out-of-Sample Test: A Connection Fee Discount Program}\label{section:oostest}
+
+A connection fee discount program implemented by the water company provides a useful setting to test the out-of-sample predictions of the economic model: do predicted water source choices match observed choices in response to a discount in the fixed fee?
+According to the model, reducing the fixed fee would make individual connections more attractive relative to shared connections or water vendors.
+This section compares the predicted and observed increase in connections in response to the program.
+
+%To evaluate how well the model is able to match observed substitution patterns between water sources, I investigate reduced-form evidence from a connection-fee discount program since this variation is not used explicitly in any part of the estimation.
+%[chk] The fundamental assumption of the model is that the decision to share a water connection balances splitting the fixed fee among many households against facing marginal hassle costs in fetching water as well as free-rider costs in splitting the water bill.
+Under this assumption, reducing the fixed fee would lead to substitution away from shared connections toward individual connections.
+This section uses quasi-experimental variation in the connection-fee to test this assumption.
+
+In 2009, the government regulator issued new regulations reducing the connection fee from 6,000 to 2,400 PhP for low-income areas partially in an effort to extend access and affordability to low-income households.
+Under the assumption that households reside in Manila for 80 months and face negligible credit constraints, this discount lowered the monthly fixed fee faced by households by 45 PhP on average.
+In the presence of credit constraints, this estimate can be interpreted as a lower bound on the policy's impact on the monthly fixed price faced by households.
+Figure~\ref{figure:discountfirststage} indicates the share of new connections receiving discounted fees.
+The sudden rise by \input{tables/first_stage}percentage points coincides with the change in regulations and will be used to identify the timing of the discount policy.
+A small fraction of households are observed to receive connection fee discounts prior to the program as part of other, smaller pro-poor strategies implemented by the water provider.
+% and these households are excluded from the main analysis
+
+\begin{figure}
+\centering
+\caption{Share of New Connections Receiving a Discount}\label{figure:discountfirststage}
+\includegraphics[scale=.7]{tables/diff_595_first_stage.pdf}
+\end{figure}
+
+Since the data do not identify precisely which local areas or specific households were eligible for the discount, additional assumptions are necessary to measure eligibility.
+First, I define treated areas as any meter reading unit that receives at least one discounted connection over the full duration while control areas include any meter reading units that never receive discounts.
+Meter reading units (MRUs) are common geographical designations used by the water provider and include between 100 and 500 meters.
+There are 3,757 MRUs in the service area.
+I include only MRUs that were established long prior to the discount fee program to ensure that these areas are likely to be at saturation in terms of water connections prior to the program.
+Second, to identify the share of households in treated areas that were eligible, I conceptually divide new connections into two groups --- (1) households substituting away from shared connections or water vendors in response to the program and (2) new households migrating to the city.
+I then measure eligibility as the share of new migrants receiving discounted connections fees after the policy.
+
+This approach requires the following assumptions:
+\begin{enumerate}
+	\item Before the discount program, households that have already moved to the city have reached an equilibrium at the current prices; therefore, all new full-price connections in the pre-period are driven by migration to the city.
+This assumption is consistent with the large fixed costs incurred in setting up a new connection.
+	\item The rate of migration is unaffected by the policy, which is supported by the stable rate of new connections for untreated areas in Figure~\ref{figure:discountreducedform} below.  
+	\item After the discount policy is implemented, all new migrant households that are eligible take up the discounted connections.
+	\item Rates of eligibility are similar across migrant and non-migrant groups.
+\end{enumerate}
+Under these assumptions, I compute the impact of the policy on new full-price connections in the treated areas and interpret any reduction in the rate of new full-price connections as driven by new migrants receiving discounted connections.
+I estimate the following simple difference-in-differences equation across all treated and untreated Meter Reading Units, $m$, and months, $t$, pre and post policy implementation:
+\begin{align*}
+\text{New Full-Price Connections}_{t,m} &= \beta_1 \text{Post X Treated}_{t,m} + \beta_2 \text{Post}_{t,m} + \beta_3 \text{Treated}_{t,m} + \epsilon_{t,m}
+\end{align*}
+Table~\ref{table:difffullpriced} presents the results from this estimation.\footnote{These results do not exactly match reduced-form results from Table~\ref{table:diffdiscountreducedform} because the data only have information on the price per connection for about 80\% of new connections.}  Adding the coefficients in Table~\ref{table:difffullpriced} shows that in the absence of the policy, treated areas were expected to have added 0\input{tables/would_have_added}new full-price connections each month; yet, as a result of the policy, these areas actually experienced 0\input{tables/actually_added}new full-price connections with the remaining households receiving discounted connections.
+This discrepancy implies that \input{tables/substitution}\unskip\% of households were eligible for the program.
+
+\begin{table}
+\centering
+\caption{Difference-in-Differences Estimate for Full Priced Connections}\label{table:difffullpriced}
+\input{tables/diff_595_reg_secondary}
+\end{table}
+
+I next examine the reduced-form impacts of the policy using the following event-study regression equation, which computes the average number of new connections in bi-monthly intervals relative to the discount fee program for both treated and untreated areas:
+\begin{align*}
+\text{New Connections}_{t,m} &= \sum_{r=0}^{T} \beta^{\text{Treated}}_{r} \mathbbm{1} \{t=r\} + \sum_{r=0}^{T} \beta^{\text{Untreated}}_{r} \mathbbm{1} \{t=r\}  +  \theta_{m} + \epsilon_{t,m} \\
+t &= \text{2 Month Intervals}\\
+m &= \text{Meter Reading Unit}
+\end{align*}
+Figure~\ref{figure:discountreducedform} provides the graphical estimates from this equation.
+The untreated group on the left-hand side exhibits a very stable trend in new connections with no changes relative to the discount program.
+This finding is consistent with steady population growth generating a constant rise in the total number of connections.
+
+The treated group on the right-hand side shows a relatively stable pre-trend interrupted by a substantial increase in the number of connections just following the discount program implementation.
+This increase lasts for a couple years before returning to pre-program levels.
+These trends provide evidence that households who are sharing water or purchasing from vendors are gradually learning about the price change and choosing to purchase their own connections.
+After a couple years, this additional demand for connections has been satisfied, letting migration take over as the sole driver of new connections.
+\begin{figure}
+\centering
+\caption{Reduced Form: Connection Fee Discount}\label{figure:discountreducedform}
+\includegraphics[scale=.8]{tables/diff_595.pdf}
+%\includegraphics[scale=.57]{tables/diff_595_treated.pdf}
+\end{figure}
+
+\begin{table}
+\centering
+\caption{Difference-in-Differences Estimate}\label{table:diffdiscountreducedform}
+\input{tables/diff_595_reg_primary}
+\end{table}
+
+A simple difference-in-differences estimate provided by Table~\ref{table:diffdiscountreducedform} calculates an increase of 0\input{tables/red_form_est}new connections per month for the treated areas on a base average of 0\input{tables/red_form_base}new connections per month.
+Aggregated over the full \input{tables/treated_months}months of the program, this program led to a total of \input{tables/total_effect}new connections per Meter Reading Unit.
+Given that the average Meter Reading Unit has \input{tables/mru_size}connections over the full time period, this program generated about a \input{tables/percent_increase_discount}\unskip\% increase in the number of new connections.
+
+To compare results from this policy to counterfactual estimates from the model, I now convert the change in number of connections induced by the policy to a shift from shared and vendor connections to individual connections.
+Given that \input{tables/share_2_hhs}\unskip\% of connections serve two households and \input{tables/share_3_hhs}\unskip\% of connections serve three or more households, and 5\% of households access water from vendors, then \input{tables/mru_size}connections per Meter Reading Unit are calculated to serve an average population of around \input{tables/population_served}households.
+This policy results in a \input{tables/increase_in_individual_connections}percentage point increase in the share of households owning a connection, which can be directly compared to predictions from the counterfactual exercise.
+
+In order to relate the quasi-experimental results from the policy to the model outputs, I simulate the impacts of the connection-fee discount policy by (1) randomly selecting \input{tables/substitution}\unskip\% of households, (2) lowering the fixed fee by 45 PhP for these households, and (3) recomputing their water source choices.
+As a result of this policy, the share of households owning a water connection is calculated to rise by \input{tables/out_of_sample_inc_ind_conn_group}percentage points.
+This finding is smaller, but comparable to the reduced form results indicating a \input{tables/increase_in_individual_connections}percentage point increase.
+There may be many reasons that the counterfactual results lag behind the reduced-form estimates.
+First, the assumptions used to amortize the connection fee discount into monthly terms  may work to understate the impact of the discount, especially in cases where households face credit-constraints in funding large, lump-sum connection fees.
+Second, in practice, the discount policy targeted a low-income segment of the population, which may have different substitution patterns across water sources.
+
+Despite these caveats, the fact that the reduced-form and model-based estimates are similar in magnitude lends support to the counterfactual exercises in Section~\ref{section:counterfactualexercises}.
+Table~\ref{table:oosestimates} calculates the impacts of this connection fee discount on water source choices as well as consumer welfare.
+Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended.
+Since utility is assumed to be quasi-linear, consumer welfare is measured in PhP/month.
+Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile_group}\unskip\% of users.
+
+\begin{table}
+\centering
+\caption{Connection Fee Discount: Out-of-Sample Test Results}\label{table:oosestimates}
+\input{tables/oos_discount_estimates_group} \\ 
+\vspace{.2cm}
+\footnotesize{Fixed fee and consumer surplus are in PhP/month.}
+\end{table}
+
 \section{Test for Incidental Parameter Bias}\label{appendix:incidentalparametertest}

### 2018-10-29 phil_paper/jmp_wjv_v2.tex
some new stuff happening

@@
 Despite large investments in piped water throughout the developing world, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries for at least the past decade (World Bank [2015]).
-Given health, time-savings, and other benefits from piped water, how can water utilities set prices in order to close gaps in access while still covering costs?\footnote{\cite{gamper2010impact,cutler2005role}, and \cite{galiani2005water} find health improvements in both developed and developing settings while \cite{devoto2012happiness} find time savings and other utility benefits.}  A popular approach particularly in developing cities is to subsidize upfront connection fees with high marginal prices to extend access especially for the poor.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
-Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  In a similar spirit, over 70\% of developing cities increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}).
-\cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.}  Recent empirical papers in South Africa and C{\^o}te d'Ivoire support this intuition, predicting gains in both access to piped water and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).
+Given health, time-savings, and other benefits from piped water, how can water utilities set prices to ensure access while covering costs?\footnote{\cite{gamper2010impact,cutler2005role}, and \cite{galiani2005water} find health improvements in both developed and developing settings while \cite{devoto2012happiness} find time savings and other utility benefits.}  A popular approach particularly in developing cities is to subsidize upfront connection fees with high marginal prices.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
+Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  Over 70\% of developing cities also increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}).
+\cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.}  Recent empirical papers in South Africa and C{\^o}te d'Ivoire predict gains in both access and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).
 
@@
 This partition embeds the assumption that neighborhoods are mutually exclusive so that a household located in one neighborhood cannot share water with households in a nearby neighborhood.
-Restricting the choice set in this way is necessary for computation but may in some cases overestimate the costs that households face in finding a sharing partner.\footnote{This limitation is discussed in more detail in Section~\ref{section:fixedcostestimation}}
+Restricting the choice set in this way is necessary for computation but may in some cases overestimate the costs that households face in finding a sharing partner.\footnote{This limitation is discussed in more detail in Section~\ref{section:fixedcostestimation}.}
 
@@
 
-In choosing how much water to use each month, households using piped water face the difficult task of coordinating water consumption among all household members.
+In choosing how much water to consume each month, households using piped water face the difficult task of coordinating water consumption among all household members.
 For example, consider the head of a household trying to manage water consumption across all of their household members each month.
@@
 
+To account for idiosyncratic preference shocks for water each month, let household's fixed preference, $\Gamma_{i}$, be decomposed into a static, household-specific component, $\gamma_i$, and a normally distributed, idiosyncratic component, $\eta_{i}$, which is assumed to follow a multivariate normal distribution among sharing partners:
+\begin{align*}
+\Gamma_{i} &= \gamma_i + \eta_{i} \\
+\eta_{i} &\sim \mathcal{N} (\textbf{0},\Sigma_{\eta}) 
+\end{align*}
+This preference shock is also assumed to be independent of the consumption shocks, $\epsilon_C$.
+Aggregating these preferences shocks over all sharing households using connection, $C$, produces a joint shock, $\eta_C$, according to the convolution of these random normal variables with a variance equal to $\sum_{i=1}^{S} \sigma_{\eta}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \rho^{\eta}_{i,j} \sigma_{\eta}^2$.
+
 %To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.
@@
 
+Sharing households must negotiate over how to pay the monthly fixed costs (including the fixed fee paid to the firm and any unobserved costs of using a connection).
+The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement, allocating $F_i$ to each household.
+Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions and Section~\ref{section:watersourcechoice} later discusses how fixed costs are divided.
+
 Water sharing relationships impact monthly consumption choices through the budget constraint.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  The model assumes that the monthly water bill is split evenly between all sharing households.
-Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also exend across households.
+Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.
 Among owners of the water connection responding to the mobile survey, \input{tables/bill_split}\unskip\% report splitting the water bill evenly or alternating payment each month, \input{tables/bill_fixed}\unskip\% charge sharing households a fixed amount each month regardless of their consumption, and \input{tables/bill_usage}\unskip\% charge other users a price according to their usage.\footnote{The remaining households report ``I don't know'' or ``other.''}  Evenly splitting the bill, alternating payment, or charging a fixed amount provide easy ways to extract compensation without requiring specific information on the monthly consumption of each sharing household.
@@
 }
-
-Sharing households must negotiate over how to pay the monthly fixed costs (including the fixed fee paid to the firm and any unobserved costs of using a connection).
-The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement, allocating $F_i$ to each household.
-Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions and Section~\ref{section:watersourcechoice} later discusses how fixed costs are divided.
 
@@
 
-The full budget constraint is a piece-wise expression of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.
+The full budget constraint is a piece-wise expansion of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.
 $B_{C,k}$ represents the total water bill for connection $C$ given the tariff schedule.
@@
 \label{equation:firstordercondition}
-\begin{split}
- 0 =  w_i - \Gamma_i - \alpha_i H_{i} -  \frac{1}{S}  \sum_{j=1}^{K} \alpha_i  p^{j} \Big [ \Phi \Big( \frac{W_C - \overline{W}^{j}}{\sigma_{\epsilon_C}} \Big) - \Phi \Big( \frac{ W_C - \overline{W}^{j-1}}{\sigma_{\epsilon_C}} \Big)   \Big ]
-\end{split}
+%\begin{split}
+ 0 &= - w_i + \Gamma_i - \alpha_i \Big[H_{i} +  \frac{MP_C}{S} \Big]
  \end{align}
-The summation in equation (\ref{equation:firstordercondition}) calculates the expected marginal price faced by the connection, which is scaled by the number of households sharing the connection, $S$.
-This expression intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the household to higher prices in expectation.
+\hspace{2cm} Where 
+\begin{align}
+\label{equation:weightedmarginalprice}
+ MP_C &= \sum_{j=1}^{K}  p^{j} \Big [ \Phi \Big( \frac{W_C - \overline{W}^{j}}{\sigma_{\epsilon_C}} \Big) - \Phi \Big( \frac{ W_C - \overline{W}^{j-1}}{\sigma_{\epsilon_C}} \Big)   \Big ]
+%\end{split}
+\end{align}
+
+The first order condition in equation (\ref{equation:firstordercondition}) reveals that consumers balance their fixed preference for water, $\Gamma_i$, against their price sensitivity, $\alpha_i$, hassle costs, $H_i$, and expected marginal price, $MP_C$ (scaled by the number of sharing households, $S$).
+
+Expected marginal price $MP_C$ in equation (\ref{equation:weightedmarginalprice}) intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the household to higher prices in expectation.
 This first-order condition characterizes the best-response functions for each household.
@@
 
-To arrive at a tractable expression for water demand, I simplify the best-response function by assuming that households approximate the normal distribution with a simple uniform distribution.
+To arrive at a tractable expression for water demand, I simplify equation (\ref{equation:weightedmarginalprice}) by assuming that households approximate the normal distribution with a simple uniform distribution.
 This assumption implies that households give zero likelihood to extremely high or low consumption shocks and even likelihood to moderate consumption shocks.
@@
 I use the following piece-wise function form to approximate the normal cumulative distribution:
-
 \begin{align*}
@@
 \end{align*}
-
 % This  implies the additional economic assumption that household decision-makers approximate normally distributed shocks with .  
@@
 For example, when $\sigma_{\epsilon_C}$ is very large, demand becomes a function of all prices at every point because the consumption shocks are large enough to produce a positive probability of reaching every price segment regardless of where the households choose to consume.
-
 Appendix~\ref{appendix:linearapprox} graphs this approximation against a standard normal cumulative distribution function and simulates optimal demand under both distributions, finding negligible evidence that this approximation would substantially bias the estimates or affect welfare measures.
 
-After replacing the normal cdf $\Phi(.)$ for $g(.)$, the best-response function in equation (\ref{equation:firstordercondition}) now includes the weighted sum of piece-wise functions, $g(.)$, which may also overlap with each other.
-This weighted sum determines the marginal prices that each household must consider in choosing their optimal consumption-level.
-The degree of overlap depends on the variance in consumption shocks, $\sigma_{\epsilon_C}$.
-For example, when $\sigma_{\epsilon_C}$ is very large, the consumption shocks produce a positive probability reaching any price segment, ensuring full overlap in piece-wise functions.
-
-there is full overlap meaning that households consider all prices at every consumption level.
-
-In the opposite case, having zero consumption shocks produces zero overlap so that households only consider the single price local to their consumption level.
-
-Identifying a particular piece-wise best-response function requires imposing bounds on $\sigma_{\epsilon_C}$ ex-ante, ensuring a certain level of overlap.
-I take the approach of 1) assuming bounds on $\sigma_{\epsilon_C}$, 2) constructing the corresponding demand function, and 3) estimating the model to see if the estimated $\sigma_{\epsilon_C}$ lies within the bounds.
-Appendix~\ref{appendix:sigmanuassumptions} provides the results from this exercise finding that the results are robust to this ex-ante assumption.
-
- This section proceeds by describing the demand function that is most consistent with the data.
-
-% determine which prices enter the optimal demand function at each level of demand.
-
-The model also allows for idiosyncratic preference shocks for each household by decomposing the fixed preference of water demand for each household given by $\Gamma_{i}$, into a static, household-specific component, $\gamma_i$, and a normally distributed idiosyncratic component, $\eta_{i}$, which is assumed to follow a multivariate normal distribution among sharing partners:
-\begin{align*}
-\Gamma_{i} &= \gamma_i + \eta_{i} \\
-\eta_{i} &\sim \mathcal{N} (\textbf{0},\Sigma_{\eta}) 
-\end{align*}
-This component helps to capture unexplained fluctuations in consumption for households over time.
-This preference shock is also assumed to be independent of the consumption shocks, $\epsilon_C$.
-Aggregating these preferences shocks over all sharing households using connection, $C$, produces a joint shock, $\eta_C$, according to the convolution of these random normal variables with a variance equal to $\sum_{i=1}^{S} \sigma_{\eta}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \rho^{\eta}_{i,j} \sigma_{\eta}^2$.
-
-\subsubsection{Characterizing the Optimal Demand Function}
-
-The best-response functions for each household can be solved and summed across all sharing households $S$ to form demand at the level of each connection, $C$.
-The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs since in this case, the budget constraint is convex.
-Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments.
-I take this calculation into account when allowing for decreasing marginal prices in the counterfactual exercises.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
-\begin{align}\label{equation:generaldemand}
-\begin{split}
-w^{*}_C &=
-\begin{cases}
-D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
-\end{cases}\\
-\text{Where: } & \\
-D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{L,H} }   \\
-d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
-V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
-\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \sqrt{2} \sigma_{\epsilon_C} \\
-\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \sqrt{2} \sigma_{\epsilon_C} \\
-\end{split}
-\end{align}
-
-%\begin{align}\label{equation:generaldemand}
-%\begin{split}
-%w^{*}_C &=
-%\begin{cases}
-%D^{1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-%D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-%D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-%D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-%D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-%D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-%D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
-%\end{cases}\\
-%\text{Where: } & \\
-%D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{H,L} }   \\
-%d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} (\tfrac{\lambda_C - \overline{W}^{H}}{\lambda_C}) + p^{M} (\tfrac{\overline{W}^{H} - \overline{W}^{H}}{\lambda_C} ) -    p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\lambda_C})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\lambda_C})  ]  \Big )    \\
-%V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\lambda_C})  ,  \lambda_C = \sqrt{2}{\sigma_{\epsilon_C}} \\
-%\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \lambda_C \\
-%\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \lambda_C \\
-%\end{split}
-%\end{align}
-
-For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.
-
-In this expression, $d^{L,M,H}_C$ captures the deterministic component of demand while $D^{L,M,H}_C$ adds the stochastic component of fixed preferences.
-Connection-level fixed preferences $\gamma_C$, price sensitivities $\alpha_C$, and  hassle costs $H_C$ sum across their respective values for all households using a connection.
-A series of thresholds in the level of unobserved fixed preference, $\eta_C$, given by $\overline{\eta}^{j}_{l,L}$ and $\overline{\eta}^{j}_{l,U}$ work to determine which prices influence demand at each point in the schedule.
-Crossing a threshold means that the consumption shock now exposes the connection to a different set of prices.
-Figure~\ref{figure:intuitivedemand} graphs an example demand curve where the slope is determined by the functions $D^{L,M,H}_C$ and the changes in slope are given by the preference thresholds.
-
-%Also, the model assumes ex-ante that the parameter $\sigma_{\epsilon_C}$ satisfies two boundary conditions that is developed in more detail below as well as in Section~\ref{section:preferenceestimation}.
-
-\begin{figure}
-\caption{Example Demand Curve}\label{figure:intuitivedemand}
-\centering
-\begin{tikzpicture}[      
-        every node/.style={anchor=south west,inner sep=0pt},
-        x=1cm, y=1cm,
-      ]   
-     \node (fig1) at (0,0)
-       {\includegraphics[width=.66\textwidth,height=1\textheight,keepaspectratio]{tables/tariff_structure_1_no_label.pdf}};
-
-\draw [line width=0.2mm,color=red,dashed] (2.8,1.8) -- (2.8,7.6);
-\draw [line width=0.2mm,color=red,dashed] (3.8,1.8) -- (3.8,7.6);
-\draw [line width=0.2mm,color=red,dashed] (4.6,1.8) -- (4.6,7.6);
-\draw [line width=0.2mm,color=red,dashed] (5.5,1.8) -- (5.5,7.6);
-\draw [line width=0.2mm,color=red,dashed] (8.2,1.8) -- (8.2,7.6);
-\draw [line width=0.2mm,color=red,dashed] (9.1,1.8) -- (9.1,7.6);
-
-\node[align=center] at (2.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{1}_{1,L} $}};
-\node[align=center] at (3.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{2,L} $}};
-\node[align=center] at (4.5,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{1,U} $}};
-\node[align=center] at (5.4,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{2,U} $}};
-\node[align=center] at (8.1,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{3,L}  $}};
-\node[align=center] at (9,7.6)  { \text{\footnotesize  $\overline{\eta}^{4}_{3,U}  $}};
-
-\draw [line width=0.5mm] (1.2,7.6) -- (2.8,7) -- (3.8,6) -- (4.6,4.5) -- (5.2,2); %% curve
-
-\node[align=center] at (1.8,1)  { \text{\footnotesize  $D^{1}_C$}};
-\node[align=center] at (2.8,1) { \text{\footnotesize  $D^{1,2}_C$}};
-\node[align=center] at (3.8,1)  { \text{\footnotesize  $D^{1,2,3}_C $}};
-\node[align=center] at (4.8,1) { \text{\footnotesize  $D^{2,3}_C $}};
-\node[align=center] at (6.8,1)  { \text{\footnotesize  $D^{3}_C $}};
-\node[align=center] at (8.3,1)    { \text{\footnotesize  $D^{3,4}_C $}};
-\node[align=center] at (9.6,1)  { \text{\footnotesize  $D^{4}_C $}};
-
-\node[align=center] at (2.3,2.3) { \text{$p^1$} };
-\node[align=center] at (4,4.5)   { \text{$p^2$} };
-\node[align=center] at (6.6,6.4) { \text{$p^3$} };
-\node[align=center] at (10,7.6) { \text{$p^4$} };
-
-\end{tikzpicture}
-\end{figure}
-
-This section now discusses the separate parts of the demand function in more detail.
-
-\textbf{  Demand over a Single Price:  }  The first, third, and fourth price segments of the tariff schedule in Manila given in Figure~\ref{figure:intuitivedemand} exhibit large gaps of 20 $\text{m}^{3}$ between price changes.
-Within these segments, the consumption shocks are not large enough to ever bounce the households across a kink point in these regions.
-Therefore, households are exposed only to the current price for that segment.
-Setting the low, medium, and high prices all equal to $k$ in expression $D^{L,M,H}_C$, demand arrives at the following expression:
-\begin{align*}
-  D_C  =& \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{S} p^k + \eta_C 
+After substituting the normal cumulative distribution function $\Phi(.)$ for $g(.)$ in equation (\ref{equation:weightedmarginalprice}), expected marginal price becomes the sum of potentially overlapping piece-wise functions, $g(.)$.
+When households face small consumption shocks, there is no probability that these shocks will overlap and expose the household to multiple price levels.
+Therefore, solving the best-response function (summing across all households using connection $C$) yields a simple expression for the deterministic segment of connection-level demand:
+\begin{align*}
+d^{j}_C &= \gamma_C - \alpha_C [ H_{C} + \frac{p^{j}}{S}]  
 \end{align*}
@@
 Comparing demand among shared connections to individual connections, the extent of over-consumption at an average price of $p$ can be roughly summarized as $\frac{S-1}{S} \alpha_C p $.
-
-\textbf{ Demand over Many Prices: }  When households choose to consume close to price thresholds points, they become exposed to price segments both above and below the thresholds.
-Demand becomes a weighted average of these two price segments.
-In this case, demand takes the following form, setting low and medium prices equal to $k$, and the high price equal to $k+1$:
-\begin{align*}
-D_C &= \frac{ 1}{ V^{k,k+1} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{k} + p^{k+1} - \overline{W}^{k+1} (\frac{p^{k+1} - p^{k}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big ) + \frac{ \eta_C }{ V_{k+1,k} }
-\end{align*}
-Setting $L=M=k$ simplifies the demand expression so that only the single nearby kink point, $\overline{W}^{k+1}$, is considered.
-Under increasing mprices, a decrease in the kink point, $\overline{W}^{k+1}$, lowers demand by increasing the probability that the household faces a higher price.
-
-When the distance between price segments is relatively small compared to the size of the consumption shocks, then households are exposed to three prices when consuming on a particular segment.
-Despite locating far from the neighboring kink points, households still face some probability of crossing into another price segment either above or below their current price.
-This demand function applies to households locating between the second and third tariff blocks because this gap only spans 10 $\text{m}^{3}$ (as shown in Figure~\ref{figure:intuitivedemand}).
-The demand function corresponds to the full expression for demand, setting indices for the low price equal to $1$, the middle price equal to $2$, and the high price equal to $3$.
+%The first condition ensures that the connection's idiosyncratic preference for water, $\eta_C$, falls between the appropriate thresholds, $\overline{\eta}_{L}, \overline{\eta}_{U}$, to be exposed to this particular segment of the price schedule.
+The second two conditions ensure that these thresholds do not overlap with each other so that the connection is exposed to a single price for this level of demand.
+The thresholds are determined by the kink points, $\overline{W}$, as well as $\sqrt{2} \sigma_{\epsilon_C} $.
+
+%When households face large consumption shocks, these functions overlap across price thresholds, which means that households must consider multiple prices when choosing their consumption.  
+This expression for demand holds when total demand (including idiosyncratic preference $\eta_C$) falls sufficiently between two price thresholds: 
+\begin{align*}
+\overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}  \, \leq \, & d^{j}_C + \eta_C \, \leq  \, \overline{W}_{l+1} - \sqrt{2} \sigma_{\epsilon_C} 
+\end{align*}
+High variances of consumption shocks, $\sigma_{\epsilon_C}$, combined with small distances between kink points create cases where these conditions are not satisfied and households are forced to consider more than one price in choosing optimal consumption.
+Allowing for households to be exposed to price thresholds $j$ through $l$, the general solution to the best-response function for the connection $C$ again yields the deterministic segment of connection-level demand as follows:
+\begin{align*}
+d_{C}^{j,l}       		&= \frac{ 1}{ V^{j,l} } \Big ( \gamma_C - \alpha_C [ H_{C} - \frac{MP^{j,l}}{S} ] \Big )    \\
+\text{ Where : }& \\
+MP^{j,l} &=\frac{1}{2} \big  [ p^{j} + p^{l} - \sum_{k=l}^{j} \overline{W}^{k} (\frac{p^{k} - p^{k-1}}{\sqrt{2}{\sigma_{\epsilon_C}}}) \big ]  \\
+V^{j,l}	     	    &=  1 + \frac{\alpha_C}{2 S} ( \frac{p_j - p_l}{\sqrt{2}\sigma_{\epsilon_C}}) 
+\end{align*}
+The demand function takes a similar form to the linear case, including the fixed preference while weighting the marginal price by the price sensitivity and degree of sharing.
+Unlike in the linear case, connections face an average of all possible marginal prices, $MP^{j,l}$, that can be realized from their consumption shocks.
+All terms are also weighted by a variance term, which depends on the gap between the highest and lowest prices $j$ and $l$.
+This demand function holds for levels of demand between the following thresholds:
+\begin{align*}
+B_{j,l} \, & \leq \, D_C^{j,l} \, \leq \, T_{j,l} \\
+\text{Where :} & \\
+B_{j,l} &= max \{ x \in I_{j,l} \, | \, x \leq D_C^{j,l} \} \,\,\, , \,\,\, T_{j,l} = min  \{ y \in I_{j,l} \, | \, y \geq D_C^{j,l} \} \\
+I_{j,l} &= \{ \overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}, \overline{W}_{l} - \sqrt{2}\sigma_{\epsilon_C}, \overline{W}_{j} + \sqrt{2} \sigma_{\epsilon_C},  \overline{W}_{j} - \sqrt{2} \sigma_{\epsilon_C}  \} \\
+D_C^{j,l} &=  d_C^{j,l} + \frac{ \eta_C }{ V^{j,l} } 
+\end{align*}
+Bottom $B_{j,l}$ and top $T_{j,l}$ thresholds sandwich connection demand $D_C^{j,l}$ and are drawn from the full set of possible thresholds, $I_{j,l}$, above and below the tariff kink points, $\overline{W}_{l}$ and $\overline{W}_{j}$.
+In cases with high variance in consumption shocks, kink points $j$ and $l$ may span many other marginal prices, $k$.
+At the same time for small consumption shocks combined with far distances from price thresholds, this expression simplifies to the linear case described above.
+%T &= \{ \overline{W}_{0} + \sqrt{2} \sigma_{\epsilon_C}, ..., \overline{W}_{N} + \sqrt{2} \sigma_{\epsilon_C}, \overline{W}_{0} - \sqrt{2} \sigma_{\epsilon_C}, ..., \overline{W}_{N} - \sqrt{2} \sigma_{\epsilon_C}  \} \\
+%min \{ \overline{\eta}^{j}_{j,U}, \overline{\eta}^{j}_{l,U} , \overline{\eta}^{j}_{j,L}  , \overline{\eta}^{j}_{l,L} \} \, \leq \, &\frac{ \eta_C }{ V^{j,l} } \, \leq \, max  \{  \overline{\eta}^{j}_{j,U} , \overline{\eta}^{j}_{l,U} , \overline{\eta}^{j}_{j,L}, \overline{\eta}^{j}_{l,L} \}
+%The number of price segments between $j$ and $l$ depends on the extent to which
+
+Constructing a full demand function for a connection requires simply connecting piecewise demand segments to span the full range of consumption choices.
+However, since the degree of overlap between price segments depends on the variance in consumption shocks, there can be different optimal demand functions for different levels of consumption variance, $\sigma_{\epsilon_C}$.
+To determine a single piecewise demand function, I take the approach of (1) assuming ex-ante bounds on $\sigma_{\epsilon_C}$, (2) constructing the implied optimal demand function given these bounds, and (3) estimating the model to see if the estimated $\sigma_{\epsilon_C}$ rejects these bounds in the data.
+Appendix~\ref{appendix:sigmanuassumptions} provides the results of this exercise identifying a range of $\sigma_{\epsilon_C}$ that is consistent with the data.
+Appendix~\ref{appendix:optimaldemand} describes the demand function given these bounds along with a visual example demand curve in Figure~\ref{figure:intuitivedemand}.
+
+%Solving for the the best-response function, and summing across all households $C$ yields connection level demand:
+%\begin{align*}
+%d_{C}^{j,l}       		&= \frac{ 1}{ V^{j,l} } \Big ( \Gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2S} \big  [ p^{j} + p^%{l} - \sum_{k=l}^{j} \overline{W}^{k} (\frac{p^{k} - p^{k-1}}{\sqrt{2}{\sigma_{\epsilon_C}}}) \big ]  \Big )    \\
+%V_{C}^{j,l}	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p_j - p_l}{\sqrt{2}\sigma_{\epsilon_C}}) 
+%\end{align*}
 
@@
 
-These probabilities allow for the derivation the likelihood function for each consumption realization, using some additional notation.\footnote{By allowing households to anticipate exogenous shocks to their consumption, this approach builds on the standard framework of \cite{burtless1978effect} and \cite{moffitt1986econometrics} to estimate demand over non-linear budget constraints, which has been recently implemented by \cite{szabo2015value} and \cite{mcrae2014infrastructure}.}  Let demand within each segment in equation (\ref{equation:generaldemand}) simplify to $D_k = D^{l_k,m_k,h_k}_C$.
-Similarly, denote the variance term for each segment as $V_k = V^{l_k,h_k}$.
-Given by the conditions on $\eta_C$ defining each segment in equation (\ref{equation:generaldemand}), denote the bottom threshold for the preference shock as, $\overline{\eta}_{B,k} = \overline{\eta}^{B_p,k}_{B_{\overline{W},k},B_{\sigma}}$ and the top threshold as $\overline{\eta}_{T,k} = \overline{\eta}^{T_p,k}_{T_{\overline{W},k},T_{\sigma}}$.
-Define the variance-adjusted preference shock as $\Psi = \frac{\eta_C}{V_k}$.
+%\overline{\eta}^{B_p,k}_{B_{\overline{W},k},B_{\sigma}}
+%Similarly, denote the variance term for each segment as $V_k = V^{j_k,l_k}$. 
+% Let total demand within each segment simplify to $D_{j,l} = \frac{ d^{j,l} }{ V^{j,l} }  + \frac{ \eta_C }{ V^{j,l} } $.
+
+These probabilities allow for the derivation the likelihood function for each consumption realization, using some additional notation.\footnote{By allowing households to anticipate exogenous shocks to their consumption, this approach builds on the standard framework of \cite{burtless1978effect} and \cite{moffitt1986econometrics} to estimate demand over non-linear budget constraints, which has been recently implemented by \cite{szabo2015value} and \cite{mcrae2014infrastructure}.}  For each demand segment, denote the bottom threshold for the preference shock needed to reach that segment as, $\overline{\eta}_{B,j} = B_{j,l} - d^{j,l} $ and the top threshold as $\overline{\eta}_{T,l} = T_{j,l} - d^{j,l} $.\footnote{Conditions on $\eta_C$ defining each segment are given in more detail in Appendix~\ref{appendix:optimaldemand} equation (\ref{equation:generaldemand}).}  Define the variance-adjusted preference shock as $\Psi = \frac{\eta_C}{V_{j,l}}$.
 Let the sum of the two stochastic terms equal $\zeta = \Psi + \epsilon_C$.
@@
 \begin{align}\label{equation:llcontributionlinear}
-\sum_{k} f_{\zeta}( Q - D_k ) \Big [ F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{T,k}) - F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{B,k})  \Big ]
+\sum_{j} f_{\zeta}( Q - D^{j,l} ) \Big [ F_{ \Psi | \zeta = Q - D^{j,l} } (\overline{\eta}_{T,l}) - F_{ \Psi | \zeta = Q - D^{j,l} } (\overline{\eta}_{B,j})  \Big ]
 \end{align}
-This expression takes the sum of the densities of $\zeta$ for each consumption level weighted by the probability that the preference shock $\Psi$ locates the desired consumption level for that household between the two thresholds, $\overline{\eta}_{T,k}$ and $\overline{\eta}_{B,k}$ over all thresholds.
+This expression takes the sum of the densities of $\zeta$ for each consumption level weighted by the probability that the preference shock $\Psi$ locates the desired consumption level for that household between the two thresholds, $\overline{\eta}_{T,l}$ and $\overline{\eta}_{B,j}$ over all thresholds.
 Given that $\eta_C$ and $\epsilon_C$ are assumed to be independent and normally distributed, the terms in equation (\ref{equation:llcontributionlinear}) can be rewritten using both the convolution and conditional distributions of multivariate normals:
 \begin{align*}
-f_{\zeta}( Q - D_k ) &= \frac{1}{\sigma_{\zeta,k}} \phi(\frac{Q - D_k}{\sigma_{\zeta,k}} ) \\
-F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{k}) &= \int_{-\infty}^{\overline{\eta}_{k}} f_{\Psi | \zeta = Q - D_k} (x) dx \\
-&= \int_{-\infty}^{\overline{\eta}_{k}} \frac{1}{\sigma_{\zeta,k} \sqrt{1-\rho_k^2}}\phi \Big ( \big ( \frac{ x V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) dx \\
-&= \Phi \Big ( \big ( \frac{\overline{\eta}_{k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) \\
+f_{\zeta}( Q - D^{j,l} ) &= \frac{1}{\sigma_{\zeta}} \phi(\frac{Q - D^{j,l}}{\sigma_{\zeta}} ) \\
+F_{ \Psi | \zeta = Q - D^{j,l} } (\overline{\eta}_{T,l}) &= \int_{-\infty}^{\overline{\eta}_{T,l}} f_{\Psi | \zeta = Q - D^{j,l}} (x) dx \\
+&= \int_{-\infty}^{\overline{\eta}_{T,l}} \frac{1}{\sigma_{\zeta} \sqrt{1-\rho^2}}\phi \Big ( \big ( \frac{ x V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) dx \\
+&= \Phi \Big ( \big ( \frac{\overline{\eta}_{T,l} V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) \\
 \text{Where:} &\\
-q_k &= \frac{(Q - D_k)}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta,k} = \sqrt{ \frac{\sigma_{\eta}^2}{V_k^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho_{k} = \frac{ \sigma_{\eta}}{  \sigma_{\zeta,k} V_k  }
+q^{j,l} &= \frac{(Q - D^{j,l})}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta} = \sqrt{ \frac{\sigma_{\eta}^2}{V_{j,l}^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho = \frac{ \sigma_{\eta}}{  \sigma_{\zeta} V_{j,l}  }
 \end{align*}
@@
 \begin{split}
-LL &= \sum_{k=1}^{K}  \frac{1}{\sigma_{\zeta,k}} \phi (q_{k}) \Big[ \Phi \Big ( \big ( \frac{\overline{\eta}_{T,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) -  \Phi \Big( \big ( \frac{\overline{\eta}_{B,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big)\Big]
+LL &= \sum_{j}  \frac{1}{\sigma_{\zeta}} \phi (q^{j,l}) \Big[ \Phi \Big ( \big ( \frac{\overline{\eta}_{T,l} V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) -  \Phi \Big( \big ( \frac{\overline{\eta}_{B,j} V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big)\Big]
 \end{split}
@@
 
+% \begin{align*}
+% f_{\zeta}( Q - D_k ) &= \frac{1}{\sigma_{\zeta,k}} \phi(\frac{Q - D_k}{\sigma_{\zeta,k}} ) \\
+% F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{k}) &= \int_{-\infty}^{\overline{\eta}_{k}} f_{\Psi | \zeta = Q - D_k} (x) dx \\
+% &= \int_{-\infty}^{\overline{\eta}_{k}} \frac{1}{\sigma_{\zeta,k} \sqrt{1-\rho_k^2}}\phi \Big ( \big ( \frac{ x V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) dx \\
+% &= \Phi \Big ( \big ( \frac{\overline{\eta}_{k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) \\
+% \text{Where:} &\\
+% q_k &= \frac{(Q - D_k)}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta,k} = \sqrt{ \frac{\sigma_{\eta}^2}{V_k^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho_{k} = \frac{ \sigma_{\eta}}{  \sigma_{\zeta,k} V_k  }
+% \end{align*}
+% Given these terms, equation (\ref{equation:llcontributionlinear}) can be rewritten in the following way:
+% \begin{align}\label{equation:LLikelihood}
+% \begin{split}
+% LL &= \sum_{k=1}^{K}  \frac{1}{\sigma_{\zeta,k}} \phi (q_{k}) \Big[ \Phi \Big ( \big ( \frac{\overline{\eta}_{T,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) -  \Phi \Big( \big ( \frac{\overline{\eta}_{B,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big)\Big]
+% \end{split}
+% \end{align}
+
 \subsubsection{Households using from Water Small-Scale Providers}
 
-6\unskip\% of households source their water from small-scale water vendors.
-These sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed cost, $F_v$, and a marginal price, $p_v$.
+While the vast majority of households use piped water, around 6\unskip\% of households still source their water from small-scale water vendors.
+In this model, these small-scale sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed cost, $F_v$, and a single marginal price, $p_v$.
 The monthly fixed cost, $F_v$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.
@@
 
-\subsection{Water Source Choice}\label{section:watersourcechoice}
+\subsection{Choosing a Water Source}\label{section:watersourcechoice}
 
 This section describes a sequential game where households choose their water sources.
-This game results in a unique equilibrium of source choices given the preferences parameters for each household as well as the costs of using each water source.
+This game results in a unique equilibrium of source choices given the preference parameters for each household as well as the costs of using each water source.
 
@@
 
-With demand for water for each household, I am able to calculate the expected utility that each household receives from each water source, guiding their source choices.
+Recovering demand for water for each household allows for calculating the expected utility that each household receives from each water source, guiding their source choices.
 This choice becomes a strategic decision since each household's water connection can also serve as a water source for other households in a neighborhood.
@@
 The payoffs equal the expected utilities from each source over the duration of usage.
-Since the data do not measure the exact duration for which households reside in a location using a water source, the model includes two additional assumptions: (1) households do not discount their future utilities and (2) all households demand water for an equal number of months.
-These assumptions limit the extent to which this model can examine the timing of any one-time connection fees or other upfront costs of water connections.
+Since the data do not measure the exact duration for which households reside in a location using a water source, the model abstracts away from the timing of water use by assuming for simplicity that (1) households do not discount their future utilities and (2) all households demand water for an equal number of months.\footnote{These assumptions do not have a substantive impact on the results because all model primitives are independent of time.}  This approach limits the extent to which this model can examine the timing of any one-time connection fees or other upfront costs of water connections.
 Instead, the model collapses one-time fees into a single monthly fixed fee.
@@
 Let $u^{i}(v)$ capture this payoff.
-
 The payoff from owning a connection depends on whether other households choose to use the connection as well.
-Households are assumed to have perfect information about each other's preferences including distributions of preference and consumption shocks.
+Households are assumed to have perfect information about each other's preferences including the distributions of preference and consumption shocks.
 In order to calculate surplus from sharing, let the set $S^{i}$ contain all households that have chosen to use household $i$'s connection (including the owner).
+
 In this model, sharing affects the utility of the owner in three ways.
@@
 Second, under non-linear tariffs, including more consumption on the same connection may alter the marginal prices faced by all sharing households.
-
 Third, in this model, owning households ($i=1$) are assumed to pay the full fixed cost, $F$, and sharing households commit ex-ante to providing a fixed transfer to the owner each month to compensate the owner.
 This transfer allows sharing households to help contribute to the fixed costs of owning and maintaining the connection.
-\input{tables/fee_even_some}\unskip\% of sharing households in the mobile survey report splitting some or all of the initial connection fee with their neighbors; for the remaining share, the owner pays the full connection fee.
+\input{tables/fee_even_some}\unskip\% of sharing households in the mobile survey report splitting some or all of the initial connection fee with their neighbors; for the remaining households, the owner pays the full connection fee.
 
@@
 First, these sharing arrangements feature long-term relationships between close neighbors who are also often family members.
-Second, neighborhoods often feature multiple sharing opportunities for each household, creating some competitive pressure on sharing arrangements.
+Second, small areas often feature multiple sharing opportunities for each household, creating some competitive pressure on sharing arrangements.
 Third, in the mobile survey, sharing households appeal to an ethic of fairness as the primary reason for dividing monthly payments instead of other reasons such as matching tariff prices or conserving environmental resources.
@@
 Let $t_{j}(S^{i})$ denote the transfer from sharing household $j$ to the owning household $i$.
-Following the outcome of a Nash-Bargain with equal weights, define $  t_{j}(S^{i}) = \frac{S^{i}-1}{S^{i}} G^{j}  - \frac{1}{S^i} O^{i} - \sum_{k \in  S^{i} \setminus \{ 1,j \} } \frac{1}{S^i} G^{k}  $.
+Following the outcome of a Nash bargain with equal weights, define $  t_{j}(S^{i}) = \frac{S^{i}-1}{S^{i}} G^{j}  - \frac{1}{S^i} O^{i} - \sum_{k \in  S^{i} \setminus \{ 1,j \} } \frac{1}{S^i} G^{k}  $.
 The total transfer that the owner receives from all sharing partners equals $T (S^{i}) = \sum_{j \in S^{i} \setminus \{ 1 \} } t_{j} (S^{i})$.
@@
 This arrangement matches the intuition that households with the greatest incentives to own and maintain a water connection would likely be the first to purchase a connection.
-Table~\ref{descriptives} shows that for connections serving two households, the owner's household size is 8\% larger than the buyer's household size on average.
+Table~\ref{descriptives} shows that for connections serving two households, the owner's household size is 10\% larger than the buyer's household size on average.
 To the extent that household size serves as a proxy for demand, this finding provides suggestive evidence that larger demand households with greater utility from purchasing a water connection are also more likely to be owners.
@@
 The sequential game is solved using backward induction and considering only pure-strategy equilibria.
-First, the last mover, household $I$, identifies the choices that maximize its payoffs at each possible choice set reached by the game.\footnote{In rare cases where payoffs are equal, the tie-breaking rule prioritizes vendors, then individual connections, and finally shared connections ranked by the sequence of owners.}  Given these choices, the next-to-last mover, household $(I-1)$, can calculate its payoffs for each corresponding choice set.
+First, the last mover, household $I$, identifies the choices that maximize its payoffs at each possible choice set reached by the game.\footnote{In very rare cases where payoffs are equal, the tie-breaking rule prioritizes vendors, then individual connections, and finally shared connections ranked by the sequence of owners.}  Given these choices, the next-to-last mover, household $(I-1)$, can calculate its payoffs for each corresponding choice set.
 Iterating backwards, this process characterizes a unique equilibrium set of source choices for all households.
@@
 From the perspective of the sequential game, households experiencing leaks are assumed to be last-movers, which implies that other households cannot update their water source choices in response to a neighbor's leak.
-Additionally, the model assumes that households do not anticipate any risks of leaks in making their initial connection decisions.
-Since leaks are relatively rare events as discussed in Section~\ref{section:hasslecostestimation}, this assumption is unlikely to significantly affect predicted water source choices.
+Additionally, the model assumes that all households do not anticipate any risks of leaks in making their initial connection decisions.
+Since leaks are rare events as discussed in Section~\ref{section:hasslecostestimation}, this assumption is unlikely to significantly affect predicted water source choices.
 
@@
 $\xi_{A,l}$ captures the convenience of temporarily using each source following a sudden loss of water access.
-For example, the first term, $\xi_{A,l}$, may capture idiosyncratic, easy access to a neighbor's private deep well or a water refilling station.
-Similarly, the second term, $\xi_{A,l}$, might measure the relative social capital among potential sharing partners: nearby family members may be more willing to quickly share their connection.
+For example, $\xi_{A,v}$, may capture idiosyncratic, easy access to a neighbor's private deep well or a water refilling station.
+Similarly, $\xi_{A,l}$, might measure the relative social capital among potential sharing partners: nearby family members may be more willing to quickly share their connection.
 The model also includes the term $F^{S}$ to capture any fixed costs associated with setting up a temporary sharing relationship relative to simply fetching from a vendor.
@@
 \begin{split}
-U_{l}(A) &= \omega u_{l}(A) - \mathbbm{1}\{ A \neq v \} F^{S}  + \xi_{A,l} \\
+U_{l}(A) &= - \mathbbm{1}\{ A \neq v \} F^{S}  + \xi_{A,l} \\
 A & \in \{v,s^{1},...,s^{J}\}
@@
 This model includes the additional assumption that $\xi_{A,l}$ is distributed Type I Extreme Value and is independent of preferences for water usage.
-Under the distributional assumptions, the model predicts that conditional on choosing a sharing relationship, households evenly distribute between sharing partners as $\omega$ approaches zero.
-When $\omega$ equals zero, the probabilities of households choosing each alternative source simplify to the following:
+Under these distributional assumptions, the model predicts that conditional on choosing a sharing relationship, households evenly distribute between sharing partners.
+The probabilities of households choosing each alternative source can be written as:
 \begin{align*}
@@
 \end{align*}
-Let $L$ represent the total households affected by a leak.
+%as $\omega$ approaches zero.  When $\omega$ equals zero,
+Let $L$ represent the total households affected by a single leak.
 $L$ is greater than one in cases where connections serving multiple households experience a leak.
-All $L$ households are assumed to receive the same preference shock $\xi_{leak,A}$ so that they follow identical substitution patterns.
-This assumption may lead to a slight underestimation of the hassle costs since these households may actually distribute across different sharing relationships, exposing them to lower points on the tariff schedule than if all households were clustered on the same connection.
-
-These assumptions allow for the specification of a likelihood function that expresses neighbor's consumption following a leak as a function of household preferences and the hassle cost, $p_h$.
+All $L$ households in the neighborhood of a single leak are assumed to receive the same preference shock $\xi_{A,l}$ so that they follow identical substitution patterns.\footnote{This assumption may lead to a slight underestimation of the hassle costs since these households may actually distribute across different sharing relationships, exposing them to lower points on the tariff schedule than if all households were clustered on the same connection.}
+
+These assumptions allow for the specification of a likelihood function that expresses neighbor's consumption following a leak as a function of household preferences and the hassle cost, $H$.
 Define $LL(\gamma,\alpha,S)$ as the likelihood function in equation (\ref{equation:LLikelihood}) in terms of the preference parameters--- $\gamma$ and $\alpha$ --- as well as the number of households using the connection, $S$.
-Given the probabilities above, the likelihood for consumption from connection $j$ after a nearby leak can be expressed as follows:
+Given the probabilities above, the likelihood for consumption derived from connection $j$ after a nearby leak can be expressed as follows:
 \begin{align}\label{equation:hasslelikelihood}
@@
 This probability is multiplied by the likelihood corresponding to joint consumption, which includes both preference terms from connection $j$ as well from $L$ households.
-This approach recovers the hassle cost, $p_h$, by comparing the fixed preferences for households experiencing the leak before and after they start using from a neighbor.
+This approach recovers the hassle cost, $H$, by comparing the fixed preferences for households experiencing the leak before and after they start using from a neighbor.
 Let $pre$ take a value of one for months before a leak.
@@
 \end{align*}
-Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $H_i$ while other households $s \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.
+Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $H_i$ while other households $l \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.
 Therefore, this method identifies hassle costs from variation in exposure for owners of the connection.
@@
 In the first step, preference parameters --- fixed preferences $\gamma$, price sensitivities $\alpha$, as well as variances for the consumption and preference shocks, $\sigma_{\epsilon}$ and $\sigma_{\eta}$ respectively --- are recovered by combining monthly consumption patterns with price variation.
-The second step analyzes a quasi-experiment where households are exogenously switched from individual connections to shared connections to estimate the hassle cost, $p_h$, associated with sharing.
+The second step analyzes a quasi-experiment where households are exogenously switched from individual connections to shared connections in order to estimate the hassle cost, $H$, associated with sharing.
 In the third step, monthly fixed costs associated with an individual connection, $F$, and using a water vendor, $F_{V}$, as well as the marginal price from vendors, $p_V$, are chosen to best match cross-sectional moments in the data, including the shares of households choosing each source.
@@
 Since hassle costs do not vary over time or with prices, they are indistinguishable from fixed preferences for consumption in this step of the estimation.
-I later decompose these estimates into household-level preferences as detailed in Section~\ref{section:fixedcostestimation}.
+I later decompose these estimates into household-level preferences and hassle costs as detailed in Section~\ref{section:fixedcostestimation}.
 
 \textbf{Price Sensitivity} $\alpha_C$  :  The estimation parameterizes household price-sensitivity terms $\alpha_i$ as a linear function of a vector of observable characteristics $Z_i$ that may affect price sensitivity so that $\alpha_i = \alpha Z_i$.
-$Z_i$ includes dummy variables for household size, type of dwelling, whether a household member is employed in a low-skilled industry, number of employed household members, and age of the head of household as shown in Table~\ref{table:demandestimates}.\footnote{For shared connections, the data include information on household size separately for owners and sharing households; however, the other observables are recorded only for owners.
+$Z_i$ includes dummy variables for household size, type of dwelling, whether a household member is employed in a low-skilled industry, number of employed household members, and age of the head of household.
+Descriptive statistics for each variable are presented in Table~\ref{table:descriptivesestsample} in Appendix~\ref{appendix:descriptivesest}.
+For shared connections, the data include information on household size separately for owners and sharing households; however, the other observables are recorded only for owners.
 For these owner-specific measures, the estimation simply assigns the owner's characteristics to sharing households.
-While this imputation may be reasonable for spatially correlated characteristics like type of dwelling, this approach may introduce bias if sharing households have systematically different levels of employed individuals or ages.
-Estimates of $\alpha$ in Table~\ref{table:demandestimates} exhibit little heterogeneity across many of these dimensions, which suggests that any bias from mismeasurement may have small effects on the counterfactual exercises.}  Since household-specific price sensitivities $\alpha_i$ enter linearly into the connection-level demand function in equation (\ref{equation:generaldemand}), connection-level price sensitivity can be written simply as $\alpha_C = \alpha \sum_{i=1}^{S} Z_i$.\footnote{The model does not control for seasonality or calendar time since the raw data exhibit negligible trends in water usage over time.}
+While this imputation may be reasonable for spatially correlated characteristics like type of dwelling, this approach may introduce bias if sharing households have systematically different numbers of employed individuals or ages.
+Estimates of price sensitivities in Table~\ref{table:demandestimates} exhibit little heterogeneity across many of these dimensions, which suggests that any bias from mismeasurement may have small effects on the counterfactual exercises.
+Since household-specific price sensitivities $\alpha_i$ enter linearly into the connection-level demand function in equation (\ref{equation:generaldemand}), connection-level price sensitivity can be written simply as $\alpha_C = \alpha \sum_{i=1}^{S} Z_i$.\footnote{The model does not control for seasonality or calendar time since the raw data exhibit negligible trends in water usage over time.}
 
@@
 The estimation also allows $\sigma_{\eta}$ to vary non-parametrically according to quintiles of mean consumption at the connection-level.
-Since larger users naturally have higher variance in their consumption, estimating a single $\sigma_{\eta}$ across all connections produces a large bias in the price sensitivity coefficients, $\alpha$.
+Specifically, the estimation includes a separate variance term for the bottom quintile of consumption as well as a term for the top two quintiles of consumption.\footnote{There is too little variation in the data to separately identify a full set of quintiles while also allowing $\sigma_{\eta}$ to vary by sharing status.}  Since larger users naturally have higher variance in their consumption, estimating a single $\sigma_{\eta}$ across all connections produces large bias in the price sensitivity coefficients, $\alpha$.
 This bias results from constraining large and small users to receive similarly scaled shocks and therefore enforcing that these users respond to the non-linear tariff schedule in similar ways.
 While using quintiles of observed consumption may be problematic since consumption choices are themselves endogenous, this approach approximates connection-specific, $\sigma_{\eta}$ terms, which would be infeasible given limited months of data available for each connection.
-The results are robust to different non-parametric specifications for $\sigma_{\eta}$.
+%The results are robust to different non-parametric specifications for $\sigma_{\eta}$.
 
@@
 \end{align*}
-Although sharing relationships and neighborhoods are limited to a maximum of three households in this paper, this approach can be used to identify correlations between an arbitrary number of sharing partners.
+Although sharing relationships and neighborhoods are limited to a maximum of three households, this approach can be used to identify correlations between an arbitrary number of sharing partners.
 
@@
 The price sensitivity parameter, $\alpha$, exhibits some statistically significant heterogeneity across demographic measures although the magnitudes of these estimates are relatively small compared to the intercept.
-Moderately sized households have larger price sensitivities while employment among household members tends to lower price sensitivity estimates.
-Relative to living in a duplex, households in apartments and single houses exhibit greater price sensitivities with large standard errors.
+Moderately sized households have smaller price sensitivities while employment among household members tends to increase price sensitivity estimates.
 These estimates can be difficult to interpret economically since the elasticity of demand depends not only on these $\alpha$ terms, but also on variation in the fixed preferences for water across households.
+%Relative to living in a duplex, households in apartments and single houses exhibit greater price sensitivities with large standard errors.
 
@@
 This finding provides suggestive evidence that shocks to sharing households may be negatively correlated.
-The standard deviation of preference shocks, $\sigma_{\eta}$, increases dramatically with quintile of water usage.
-After controlling for quintile of water usage, increasing the number of households per connection has a very small effect on the term, $\sigma_{\eta}$.
-
+The standard deviation of preference shocks, $\sigma_{\eta}$, increases dramatically with average usage at baseline.
+After controlling for average usage at baseline, increasing the number of households per connection has a very small effect on the standard deviation of preference shocks.
 \begin{table}
@@
 According to this expression, increasing the fixed preference for water consumption, $\gamma_C$, while holding constant the price sensitivity, $\alpha_C$, mechanically reduces the elasticity.
-Many previous studies estimate heterogeneity in $\gamma_C$ alongside a single $\alpha_C$ parameter for the population (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).
-This paper builds on these previous studies by estimating heterogeneity in both terms to allow to for a broader range of possibilities, including that larger users may be relatively more sensitive to prices than smaller users.
-To compare estimates in this paper with previous papers under non-linear pricing schedules, this approach follows the same formula for computing elasticities by (1) taking draws of $\epsilon$ and $\eta$, (2) computing predicted demand under prices that are 1\% greater than current prices, and (3) comparing the average percentage change in demand before and after the price change.
-For tariff blocks equal to zero, prices are increased from 0 to 1 PhP following \cite{szabo2015value}.
+Many previous studies estimate heterogeneity in $\gamma_C$ according to demographics alongside a single $\alpha_C$ parameter for the population (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).
+I build on these previous studies by estimating heterogeneity in both terms, which allows for a broader range of possibilities, including that larger users may be relatively more sensitive to prices than smaller users.
+To compare estimates with previous research under non-linear pricing schedules, this approach follows the same formula for computing elasticities by (1) taking draws of $\epsilon$ and $\eta$, (2) computing predicted demand under prices that are 1\% greater than current prices, and (3) comparing the average percentage change in demand before and after the price change.
+For tariff blocks equal to zero, prices are increased from 0 to 1 PhP (\cite{szabo2015value}).
 
@@
 Elasticities exhibit little heterogeneity across imputed income levels, but substantial variation across usage levels with larger users appearing much less sensitive to prices than smaller users.
-Since many low-income households share connections with neighbors, there is a weak correlation between income and usage-levels, which helps account for these patterns of heterogeneity.\footnote{Noise in the income imputation process may also weaken any correlation between elasticity and income.}  Heterogeneity in elasticities according to monthly usage is consistent with moral hazard when households share a connection:  increasing the number of households per connection increases the water use for those connections while also exacerbating free-riding behavior.
+Since many low-income households share connections with neighbors, there is a weak correlation between income and usage-levels, which helps account for the lack of heterogeneity.\footnote{Noise in the income imputation process may also weaken any correlation between elasticity and income.}  Heterogeneity in elasticities according to monthly usage is consistent with moral hazard when households share a connection:  increasing the number of households per connection increases the water use for those connections while also exacerbating free-riding behavior.
 Different water using activities across the water demand profile may also produce this heterogeneity in elasticities.
 This heterogeneity provides a potential motivation for usage-based price discrimination.
-For example, matching larger, less price-sensitive users with higher prices may allow for a more efficient allocation of water while covering costs of production.
-
+For example, matching larger, less price-sensitive users with higher prices may allow for a more efficient allocation of water while still covering costs of production.
 \begin{table}
@@
 \end{table}
-
 The demand estimation yields an average elasticity of \input{tables/mean_elasticity}\unskip, which can be interpreted as the percentage decrease in quantity due to a one percentage increase in price.
@@
 Table~\ref{table:correstimates} presents correlation estimates decomposed from the consumption and preference shocks.
-Both the consumptions shocks, $\epsilon$ and preference shocks, $\eta$ demonstrate negative correlations between neighbors for owners and buyers.
+Both the consumption shocks, $\epsilon$ and preference shocks, $\eta$ demonstrate negative correlations between neighbors for owners and buyers.
 This finding suggests that neighboring households may intentionally form sharing relationships with whom their shocks are negatively correlated.
@@
 
-This section details how exogenous interruptions in water connections caused by leaks combine with billing records to provide a measure of hassle costs of sharing water.
-The estimation strategy compares a connection's demand before disconnection to the change in demand among neighboring connections after disconnection (as a result of sharing), attributing the extent to which neighbors may not fully offset their consumption to the hassle cost, $H_C$.
+Exogenous interruptions in water connections caused by leaks are combined with billing records to provide a measure of the marginal costs of sharing water.
+The estimation strategy compares a connection's demand before disconnection to the change in demand among neighboring connections after disconnection (as a result of sharing), identifying the hassle cost, $H$, from the extent to which neighbors may not fully offset their consumption onto their neighbors.
 Baseline preference parameters for both disconnecting connections and their neighbors are estimated in the procedure from Section~\ref{section:preferenceestimation}.
-Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $H_C$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).
+Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $H$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).
 
@@
 These complaints do not appear to be spatially correlated with only a handful of leaks occurring among direct neighbors.
-I consider any call identified as an excessive billing complaint as a leak.
+This approach considers any call identified as an excessive billing complaint as a leak.
 While some calls may not explicitly refer to leaks, in all cases these calls refer to billing errors, meter malfunctions, or other surprise events that may drive disconnection.
 Instances where leaks in main water pipes reduce access for entire neighborhoods at a time are coded separately and excluded from the sample.
-Leaks are limited to cases with at least 3 observations before the leak in order to calculate baseline water demand for these connections.
+Leaks are limited to cases with at least 3 months of recorded usage before the leak in order to calculate baseline water demand for these connections.
 Disconnection is defined as having 0 or missing consumption values for at least 90\% of the year following the leak date.
-Neighboring connections that connect after the leak has taken place are dropped, since these connections lack a pre-period to estimate their fixed preference for water.
+Neighboring connections that connect after the leak are dropped since these connections lack the pre-period needed to estimate their fixed preferences for water.
 The estimation includes observations within a year and a half of the leak event to avoid bias from possible reconnection of these households as well as changes in the composition of neighboring households.
@@
 
-To determine which neighbors to include, Appendix~\ref{appendix:sharingneighbor} ranks nearby households according to their distance from the leak and examine how the responsiveness of neighbors' consumption levels after a leak dissipates with distance.
+To determine which neighbors to include, Appendix~\ref{appendix:sharingneighbor} ranks nearby households according to their distance from the leak and examines how the responsiveness of neighbors' consumption levels after a leak dissipates with distance.
 Results indicate substitution is concentrated among the nearest four neighbors.
@@
 Given the set of leaking households, $J=4$, as well as their preferences, the final input to the likelihood function in equation (\ref{equation:hasslelikelihood}) is the probability that leaking households choose to use from vendors.
-This probability is calibrated directly from the hypothetical question in the mobile survey, which finds that 70\% of households would use a vendor in response to a sudden disconnection for over three months.
-Directly including this parameter in the estimation requires the assumption that this hypothetical response provides an accurate measure of true behavior.
-
-To capture heterogeneity in the hassle cost, $H_C$ is parameterized as a linear function of two summary characteristics of local neighborhoods defined as wards.
-First, the share of single houses or apartment buildings in a neighborhood may increase the per-unit cost of sharing since the buildings often require longer informal pipe networks with possibly more maintenance costs as compared with duplexes.
-Second, the average distance between water meters in a neighborhood provides another useful proxy for the average distance that informal pipe networks may need to extend between households.
-Importantly, this distance measure does not account measure the physical distances between sharing partners or unconnected households.
-These omissions are likely to overestimate the average distance between all neighbors.
-Furthermore, areas with smaller physical distances are likely to increase observed sharing as well as the observed distance between meters, which would bias the estimates against finding heterogeneity in the hassle costs.
+This probability is calibrated directly from a hypothetical question in the mobile survey, which finds that 70\% of households would use a vendor in response to a sudden disconnection for over three months.
+Directly including this parameter in the estimation requires the assumption that this hypothetical response provides an accurate measure of true behavior and is generalizable across the full population of households.
+
+To capture heterogeneity in the hassle cost, $H$ is parameterized as a linear function of two summary characteristics of local census wards.
+First, the share of single houses or apartment buildings in a local area may increase the per-unit cost of sharing since the buildings often require longer informal pipe networks with possibly more maintenance costs as compared with duplexes.
+Second, the average distance between water meters in a local area provides another useful proxy for the average distance that informal pipe networks may need to extend between households.
+Importantly, this distance measure does not account for the physical distances between sharing partners or unconnected households.
+These omissions mean that the primary distance measure is likely to overestimate the true distance between all neighbors.
+Furthermore, areas with smaller physical distances are likely to increase incentives to share as well as the observed distance between meters, which may bias the effect of distance towards zero.
 Table~\ref{table:descriptivesestsample} in Appendix~\ref{appendix:descriptivesest} includes descriptive statistics for these two measures.
 
-One additional concern would be that households select into sharing relationships conditional on unobserved heterogeneity in sharing costs (not modeled here).
+One additional concern would be that households select into sharing relationships conditional on unobserved heterogeneity in sharing costs, which is not modeled here.
 Since households included in this quasi-experiment have selected into purchasing connections at baseline, they may face higher hassle costs compared to households that select into sharing.
@@
 
-%his assumption ensures that the hassle cost identified from the subset of leaking households can be extended to the population of households.
+%  This assumption ensures that the hassle cost identified from the subset of leaking households can be extended to the population of households.
 One concern may be that heterogenous hassle costs induce households to select into sharing relationships conditional on these costs.
@@
 	\item \textit{ Leaks are uncorrelated with changes in neighborhood demand. }
-	\item \textit{  A leak for one household is uncorrelated with probability of a neighboring household experiencing a leak. }
+	\item \textit{ A leak for one household is uncorrelated with the probability of a neighboring household experiencing a leak. }
 \end{enumerate}
@@
 \begin{tablenotes}
-\item \footnotesize{Estimates include 548 leaking connections and 2,151 neighboring connections, making 20,299 connection-months.
+\item \footnotesize{Estimates include 548 leaking connections and 2,151 neighboring connections, totaling 20,299 connection-months.
 \% single/home and neighbor distance are averages within wards.
@@
 Table~\ref{table:step2estimates} shows the coefficient estimates for the hassle cost estimation.
-Consistent with the theory, the hassle cost rises with the share of households living in single homes or apartment buildings (instead of duplexes).
+The hassle cost rises quickly with the share of households living in single homes or apartment buildings (instead of duplexes).
 Similarly, increasing the average distance between households by one meter raises the predicted hassle cost by 17.59 PhP/m3.
@@
 
-Figure~\ref{figure:step2histogram} plots the histogram of predicted hassle costs across the population of households, finding substantial heterogeneity with a long tail of prohibitively expensive hassle costs.
-Predicted hassle costs also have a correlation of \input{tables/correlation_hassle} with household fixed water preferences.\footnote{Section~\ref{section:disaggregation} discusses how connection-level fixed preferences $\gamma_C$ are disaggregated into household components, $\gamma_i$.}  This correlation has substantive implications for the impacts of counterfactual pricing policies; for example, high hassle costs may drive large users to sort away from sharing while small users can happily share water at little additional cost.
-
-With only 548 connections that experience leaks, the estimation recovers wide standard errors for all three parameters.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  Taken together, these results suggest that the time-costs or other physical challenges transporting water to share with a neighbor may play an important role in the extent to which households choose to use water from a neighbor's tap.
+Figure~\ref{figure:step2histogram} plots a histogram of predicted hassle costs across the population of households, finding substantial heterogeneity with a long tail of prohibitively expensive hassle costs.
+Predicted hassle costs also have a correlation of \input{tables/correlation_hassle}with household fixed water preferences.\footnote{Section~\ref{section:disaggregation} later discusses how connection-level fixed preferences $\gamma_C$ are disaggregated into household-level components, $\gamma_i$.}  This correlation has substantive implications for the impacts of counterfactual pricing policies; for example, high hassle costs may drive large users to sort away from sharing while small users can happily share water at little additional cost.
+
+With only 548 connections that experience leaks, the estimation recovers wide standard errors for all three parameters.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  Taken together, these results suggest that the time-costs or other physical challenges associated with informally transporting water may play an important role in the extent to which households choose to use water from a neighbor's tap.
 
@@
 
-This section details how unobserved fixed costs of owning a connection are recovered from cross-sectional variation in water source choices.
+Unobserved fixed costs of owning a connection are recovered from cross-sectional variation in water source choices.
 The third step of the estimation uses the preference parameters recovered in Section~\ref{section:preferenceestimation} and hassle cost estimates from Section~\ref{section:hasslecostestimation} to simulate the initial water source choices for households.
@@
 
-In order to simulate these choices, I first need to recover household-level preferences from the connection-level preferences estimated in Section~\ref{section:preferenceestimation}.
-Household price sensitivity, $\alpha_i$, can be inferred as a linear function of the vector of demographics specific to each household, $Z_i$, and estimates of $\alpha_C$.
+Simulating these choices requires recovering household-level preferences from the connection-level preferences estimated in Section~\ref{section:preferenceestimation}.
+Household-level price sensitivity, $\alpha_i$, can be inferred as a linear function of the vector of demographics specific to each household, $Z_i$, and estimates of $\alpha_C$.
 Since fixed preferences $\hat{\gamma_C}$ are estimated non-parametrically at the connection-level, I specify a parametric method of splitting $\hat{\gamma_C}$ into $\gamma_i$ for all households using demographics, $Z_i$:
@@
 In this case, $Z_i$ consists of household size since it is the only demographic measure reported separately for connection owners and other users.
-I estimate a simple regression to recover estimates of $\lambda_{S}$, which provides predicted levels of $\gamma_i$ for each household.
+This approach estimates a simple regression to recover estimates of $\lambda_{S}$, which provides predicted levels of $\gamma_i$ for each household.
 Finally, this method needs to allocate any residual variation in preferences $\mu_{i}$ across the households.
-Instead of either allocating $\mu_i$ entirely to the connection owner or splitting $\mu_{i}$ evenly across households, I allocate $M \mu_{i}$ to the owner and $\frac{(1-M)}{S-1} \mu_{i}$ to neighboring users where $M$ is the ratio of average connection-level preferences for single users, $\gamma_{S=1}$ to average connection-level preferences for shared connections $\gamma_{S>1}$.
+Instead of either allocating $\mu_i$ entirely to the connection owner or splitting $\mu_{i}$ evenly across households, this method allocates $M \mu_{i}$ to the owner and $\frac{(1-M)}{S-1} \mu_{i}$ to neighboring users where $M$ is the ratio of average connection-level preferences for single users, $\gamma_{S=1}$ to average connection-level preferences for shared connections $\gamma_{S>1}$.
 This approach nests the assumption that connection owners are more likely than their sharing partners to resemble the water demand of single-users.
 Another limitation is that the data only provide the total number of people using a connection for shared connections.
-Therefore, in cases where three households use a connection, I assume that sharing people are allocated evenly between the two sharing households.
+Therefore, in cases where three households use a connection, this approach assumes that people are allocated evenly between the two sharing households.
 %%% , which is consistent with the discussion in Section~\ref{section:watersourcechoice}
@@
 Since vendors offer high marginal prices, this form of selection would likely lead the method to overestimate demand among households using from vendors.
-
-Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from \input{tables/totalhhsmm_group} connections to households.
+Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from 5,000 connections to \input{tables/totalhhsmm_group}households.
 
@@
 Those values are rounded to zero for calculating household utility.
-
 %\footnote{ Future versions will not condition on observed choices in this way, and instead sample households across sharing relationships. }
@@
 This sequential game is repeated \input{tables/sim_repetitions}times to construct a set of draws to compute simulated moments.
-The moments used in the estimation include the shares of households choosing different sources --- using an individual connection, using water from a neighbor, and using from a vendor --- as well as the covariance between each of these source choices and the fixed preference parameters for each household, $\gamma_i$.\footnote{I ensure that the estimation places heavier weight on matching the source-choice moments over the correlation moments because these correlations rely on possibly noisy measures of the preference parameters both due to incidental parameter issues in estimation as well as imputation for households using vended water.
-}  % Future versions will re-weight these moments given the boot-strapped variance-covariance matrix.
-
+The moments used in the estimation include the shares of households choosing different sources --- using an individual connection, using water from a neighbor, and using from a vendor --- as well as the correlation between each of these source choices and the fixed preference parameters for each household, $\gamma_i$.
+The estimation places heavier weight on matching the source-choice moments over the correlation moments because these correlations rely on possibly noisy measures of the preference parameters both due to incidental parameter issues in estimation as well as imputation for households using vended water.
+% Future versions will re-weight these moments given the boot-strapped variance-covariance matrix.
 \begin{table}
@@
 \end{table}
-
 Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee_group}PhP monthly fixed fee paid to the provider.
-This finding suggests that households face sizable barriers to connecting to the water network such as maintenance land tenure insecurity, or administrative costs.
+This finding suggests that households face sizable barriers to connecting to the water network such as land tenure insecurity or administrative costs.
 This total fixed fee is also comparable to the total variable price (tariff $\times$ volume) paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.
@@
 This exercise provides additional confidence that the vendor price estimates are within a reasonable range.
+Also, Appendix~\ref{appendix:modelfit} compares the predicted moments to the observe moments used in the estimation.
+While source moments are matched exactly by design, the estimation is able to approximate the size and direction of the correlation of fixed preference with proportion connected individually and proportion using from a neighbor.
 
@@
 
-This section reconstructs the economic problem faced by the regulator in order to investigate how alternative pricing policies might impact welfare.
-I consider the government regulator's maximization problem given by equation (\ref{equation:regulator}) where the regulator chooses a fixed fee, $Fee$ and a price schedule, $P$, to maximize consumer surplus while covering the costs of production (holding profits equal to zero).
+To reconstruct the economic problem faced by the regulator and investigate how alternative pricing policies might impact welfare, consider the government regulator's maximization problem given by equation (\ref{equation:regulator}).
+In this problem, the regulator chooses a fixed fee, $Fee$, and a price schedule, $P$, to maximize consumer surplus while covering the costs of production (holding profits equal to zero).
 Consumer welfare is defined as the expected sum of all households' utilities subject to welfare weights, $\delta_i$, for different subpopulations, which capture any preferences the regulator may have towards redistribution.
@@
 Giving preference to low-demand households intends to capture dual policy goals of ensuring access as well as minimum monthly usage for all households.
-Since low-demand households are also often low-income households, this preference also provides a proxy for standard preferences toward redistribution.\footnote{Using income directly is less informative due to noise in the imputation process, especially for households that are sharing with their neighbors.}  Similarly, this approach may capture efficiency gains if connecting low-users produces positive health externalities (\cite{galiani2005water,gamper2010impact}).
+Since low-demand households are also often low-income households, this approach also provides a proxy for standard preferences toward redistribution.\footnote{Using income directly is less informative due to noise in the imputation process, especially for households that are sharing with their neighbors.}  Similarly, this approach may capture efficiency gains if connecting low-users produces positive health externalities (\cite{galiani2005water,gamper2010impact}).
 For ease of exposition, the utility function below nests the water source choices of each household.
@@
 The budget constraint ensures that the fixed monthly fee, $Fee$, paid to the company for each connection as well as the revenue earned for each unit of water consumption (given the non-linear pricing scheme) outweighs the costs of servicing each connection, the marginal costs of providing a cubic meter of water, as well as any capital costs associated with the pipe-network, pumping stations, and dam maintenance.
-The water provider calculates that their marginal costs are equal to 5 PhP per $\text{m}^{3}$ and that the fixed fee exactly covers any installation/service costs.
-To determine the capital costs, I subtract the total marginal and services costs from the total revenue earned by the company, assigning the remainder to capital costs.
+The water provider calculates that their marginal costs are equal to 5 PhP per m3 and that the fixed fee exactly covers any installation/service costs.
+To determine the capital costs, this approach subtracts the total marginal and services costs from the total revenue earned by the company, assigning the remainder to capital costs.
 Capital costs include maintaining the pipes, pumping stations, and billing infrastructure.
-This calculation provides a close approximation to the Capital Expenditures regulatory structure implemented in this context, which exactly compensates the water provider for its costs through increases in the tariff.\footnote{This paper abstracts away from any principal agent problems between the company and the regulator by assuming that the regulator has perfect information over the firm's capital investments and operating costs (\cite{laffont1993theory}).}  This regulatory problem forms the basis for evaluating the following counterfactual policies.
+This calculation provides a close approximation to the Capital Expenditures regulatory structure implemented in this context, which exactly compensates the water provider for its costs through increases in the tariff.\footnote{This approach abstracts away from any principal agent problems between the company and the regulator by assuming that the regulator has perfect information over the firm's capital investments and operating costs (\cite{laffont1993theory}).}  This regulatory problem forms the basis for evaluating the following counterfactual policies.
 All counterfactual policies evaluated below hold firm profits equal to zero.
@@
 I first examine a counterfactual policy where the regulator discounts the upfront fee while increasing the tariff to remain revenue neutral.
-By discounting the fixed fee by \input{tables/c_fee_discount_group}PhP, this policy mimics the policy implemented by the water provider; however, while the provider's discount decreased overall revenue, this policy imposes the necessary tariff increase to fund the lower fixed fee.
+By discounting the fixed fee by \input{tables/c_fee_discount_group}PhP, this approach mimics the policy implemented by the water provider; however, while the provider's discount decreased overall revenue, this approach includes the necessary tariff increase to fund the lower fixed fee.
 This counterfactual also echoes recent recommendations from policymakers and researchers including the World Bank who have strongly advocated for lower connection fees as a way of extending access to piped water among the poor (\cite{wsup,komives2005water,jimenez2014factors,kayaga2007costs,mcintosh2003asian}).
-Figure~\ref{figure:discounttariff} indicates the current tariff and the compensated tariff, which is shifted upwards by \input{tables/discount_tariff_rise_group}PhP/$\text{m}^{3}$ to maintain revenue neutrality.
+Figure~\ref{figure:discounttariff} provides the current tariff and the compensated tariff, which is shifted upwards by \input{tables/discount_tariff_rise_group}PhP/m3 to maintain revenue neutrality.
 
@@
 
-To investigate mechanisms driving these optimal pricing schedules, this section considers how the optimal two-part tariff varies continuously with counterfactual levels of the hassle cost, $p_h$.
+To investigate mechanisms driving these optimal pricing schedules, this section considers how the optimal two-part tariff varies continuously with counterfactual levels of the hassle cost, $H$.
 I follow the same routine as in Sections~\ref{section:optimaltariffswithoutsharing} and \ref{section:optimaltariffswithsharing} by (1) calculating total revenue raised under the current tariff (in Figure~\ref{figure:tariff}) given the counterfactual hassle cost, (2) recalculating the implied capital costs from total revenue under this hassle cost, and (3) determining the optimal two-part tariff maximizing total consumer surplus while just covering costs.\footnote{As the hassle cost rises, the current tariff raises less revenue, lowering the capital costs.
@@
 
+%  Identifying a particular piece-wise best-response function requires imposing bounds on $\sigma_{\epsilon_C}$ ex-ante, ensuring a certain level of overlap.
+%  determining which prices households consider at each consumption level.
+For example, households with very large consumption shocks have a positive probability of reaching any price segment so the piece-wise functions fully overlap.
+Therefore, households consider all possible prices at every point.
+In the opposite case, zero variance in consumption shocks means that households only consider the single price local to their consumption level resulting in zero overlap.
+The variance term, $\sigma_{\epsilon_C}$ plays an important role in determining the degree of overlap.
+% determine which prices enter the optimal demand function at each level of demand.
+
+\subsection{Characterizing the Optimal Demand Function}\label{appendix:optimaldemand}
+
+The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs since in this case, the budget constraint is convex.
+Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments as in \cite{szabo2015value}.
+I extend this model to allow for decreasing marginal prices in the counterfactual exercises in Section~\ref{section:counterfactualexercises}.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
+%\begin{align}\label{equation:generaldemand}
+%\begin{split}
+%w^{*}_C &=
+%\begin{cases}
+%D^{1,1,1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+%D^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
+%D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
+%D^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
+%D^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
+%D^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
+%D^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
+%\end{cases}\\
+%\text{Where: } & \\
+%D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{L,H} }   \\
+%d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
+%V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
+%\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \sqrt{2} \sigma_{\epsilon_C} \\
+%\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \sqrt{2} \sigma_{\epsilon_C} \\
+%\end{split}
+%\end{align}
+
+\begin{align}\label{equation:generaldemand}
+\begin{split}
+w^{*}_C &=
+\begin{cases}
+D^{1,1,1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+D^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
+D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
+D^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
+D^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
+D^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
+D^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
+\end{cases}\\
+\text{Where: } & \\
+D^{L,M,H}_C        		&=  \frac{ d(P^{L,M,H}) }{ V^{L,H} }  + \frac{ \eta_C }{ V^{L,H} }   \\
+d(p) &= \gamma_C - \alpha_C [ H_{C} + \frac{p}{S}]  \\
+P^{L,M,H}  &= \dfrac{1}{2}[ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ] \\
+V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
+\overline{\eta}^{j}_{l,L}   &= \overline{W}_l -  d(p^j)  - \sqrt{2} \sigma_{\epsilon_C} \hspace{.1cm},\hspace{.2cm} \overline{\eta}^{j}_{l,U}   = \overline{W}_l - d(p^j)  + \sqrt{2} \sigma_{\epsilon_C} \\
+\end{split}
+\end{align}
+
+%For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.
+
+In this expression, $d^{L,M,H}_C$ captures the deterministic component of demand while $D^{L,M,H}_C$ adds the stochastic component of fixed preferences.
+Connection-level fixed preferences $\gamma_C$, price sensitivities $\alpha_C$, and  hassle costs $H_C$ sum across their respective values for all households using a connection.
+A series of thresholds in the level of unobserved fixed preference, $\eta_C$, given by $\overline{\eta}^{j}_{l,L}$ and $\overline{\eta}^{j}_{l,U}$ work to determine which prices influence demand at each point in the schedule.
+Crossing a threshold means that the consumption shock now exposes the connection to a different set of prices.
+Figure~\ref{figure:intuitivedemand} graphs an example demand curve where the slope is determined by the functions $D^{L,M,H}_C$ and the changes in slope are given by the preference thresholds.
+
+%Also, the model assumes ex-ante that the parameter $\sigma_{\epsilon_C}$ satisfies two boundary conditions that is developed in more detail below as well as in Section~\ref{section:preferenceestimation}.
+
+\begin{figure}
+\caption{Example Demand Curve}\label{figure:intuitivedemand}
+\centering
+\begin{tikzpicture}[      
+        every node/.style={anchor=south west,inner sep=0pt},
+        x=1cm, y=1cm,
+      ]   
+     \node (fig1) at (0,0)
+       {\includegraphics[width=.66\textwidth,height=1\textheight,keepaspectratio]{tables/tariff_structure_1_no_label.pdf}};
+
+\draw [line width=0.2mm,color=red,dashed] (2.8,1.8) -- (2.8,7.6);
+\draw [line width=0.2mm,color=red,dashed] (3.8,1.8) -- (3.8,7.6);
+\draw [line width=0.2mm,color=red,dashed] (4.6,1.8) -- (4.6,7.6);
+\draw [line width=0.2mm,color=red,dashed] (5.5,1.8) -- (5.5,7.6);
+\draw [line width=0.2mm,color=red,dashed] (8.2,1.8) -- (8.2,7.6);
+\draw [line width=0.2mm,color=red,dashed] (9.1,1.8) -- (9.1,7.6);
+
+\node[align=center] at (2.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{1}_{1,L} $}};
+\node[align=center] at (3.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{2,L} $}};
+\node[align=center] at (4.5,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{1,U} $}};
+\node[align=center] at (5.4,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{2,U} $}};
+\node[align=center] at (8.1,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{3,L}  $}};
+\node[align=center] at (9,7.6)  { \text{\footnotesize  $\overline{\eta}^{4}_{3,U}  $}};
+
+\draw [line width=0.5mm] (1.2,7.6) -- (2.8,7) -- (3.8,6) -- (4.6,4.5) -- (5.2,2); %% curve
+
+\node[align=center] at (1.8,1)  { \text{\footnotesize  $D^{1,1,1}_C$}};
+\node[align=center] at (2.8,1) { \text{\footnotesize  $D^{1,2,2}_C$}};
+\node[align=center] at (3.8,1)  { \text{\footnotesize  $D^{1,2,3}_C $}};
+\node[align=center] at (4.8,1) { \text{\footnotesize  $D^{2,3,3}_C $}};
+\node[align=center] at (6.8,1)  { \text{\footnotesize  $D^{3,3,3}_C $}};
+\node[align=center] at (8.3,1)    { \text{\footnotesize  $D^{3,4,4}_C $}};
+\node[align=center] at (9.6,1)  { \text{\footnotesize  $D^{4,4,4}_C $}};
+
+\node[align=center] at (2.3,2.3) { \text{$p^1$} };
+\node[align=center] at (4,4.5)   { \text{$p^2$} };
+\node[align=center] at (6.6,6.4) { \text{$p^3$} };
+\node[align=center] at (10,7.6) { \text{$p^4$} };
+
+\end{tikzpicture}
+\end{figure}
+
+This section now discusses the separate parts of the demand function in more detail.
+
+\textbf{  Demand over a Single Price:  }  The first, third, and fourth price segments of the tariff schedule in Manila given in Figure~\ref{figure:intuitivedemand} exhibit large gaps of 20 $\text{m}^{3}$ between price changes.
+Within these segments, the consumption shocks are not large enough to ever bounce the households across a kink point in these regions.
+Therefore, households are exposed only to the current price for that segment.
+Setting the low, medium, and high prices all equal to $k$ in expression $D^{L,M,H}_C$, demand arrives at the following expression:
+\begin{align*}
+  D_C  =& \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{S} p^k + \eta_C 
+\end{align*}
+This case produces a linear demand function where $\alpha_C$ can be readily interpreted as the price sensitivity parameter while $\gamma_C$ captures the portion of demand that is invariant to prices.
+This demand function captures moral hazard from bill-splitting by dividing the price sensitivity, $\alpha_C$, by the total number of households using the connection, $S$.
+Comparing demand among shared connections to individual connections, the extent of over-consumption at an average price of $p$ can be roughly summarized as $\frac{S-1}{S} \alpha_C p $.
+
+\textbf{ Demand over Many Prices: }  When households choose to consume close to price thresholds points, they become exposed to price segments both above and below the thresholds.
+Demand becomes a weighted average of these two price segments.
+In this case, demand takes the following form, setting low and medium prices equal to $k$, and the high price equal to $k+1$:
+\begin{align*}
+D_C &= \frac{ 1}{ V^{k,k+1} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{k} + p^{k+1} - \overline{W}^{k+1} (\frac{p^{k+1} - p^{k}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big ) + \frac{ \eta_C }{ V_{k+1,k} }
+\end{align*}
+Setting $L=M=k$ simplifies the demand expression so that only the single nearby kink point, $\overline{W}^{k+1}$, is considered.
+Under increasing prices, a decrease in the kink point, $\overline{W}^{k+1}$, lowers demand by increasing the probability that the household faces a higher price.
+
+When the distance between price segments is relatively small compared to the size of the consumption shocks, then households are exposed to three prices when consuming on a particular segment.
+Despite locating far from the neighboring kink points, households still face some probability of crossing into another price segment either above or below their current price.
+This demand function applies to households locating between the second and third tariff blocks because this gap only spans 10 $\text{m}^{3}$ (as shown in Figure~\ref{figure:intuitivedemand}).
+The demand function corresponds to the full expression for demand, setting indices for the low price equal to $1$, the middle price equal to $2$, and the high price equal to $3$.
+
 \section{Determining the Demand Function with Respect to Variance of Consumption Shocks}\label{appendix:sigmanuassumptions}
@@
 \begin{cases}
-D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
 D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{1,U}  \\
@@
 \begin{cases}
-D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
 D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\

### 2018-10-31 phil_paper/jmp_qje.tex
send to dan

--- 2018-10-29 phil_paper/jmp_wjv_v2.tex
@@
 
+\usepackage[notablist,nofiglist]{endfloat}
+%\renewcommand{\efloatseparator}{\mbox{}}
+
+\renewcommand{\thetable}{\Roman{table}}
+\renewcommand{\thefigure}{\Roman{figure}}
+
+\renewcommand{\thesection}{\Roman{section}} 
+\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
+\renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
+
 %\usepackage[dvipsnames]{xcolor}
@@
 \usepackage{natbib}  
-\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
-\author{William Violette}
-\affil{Brown University\thanks{ I am grateful to Andrew Foster, Matthew Turner, Jesse Shapiro, Daniel Bj\"{o}rkegren, and Bryce Steinberg for guidance and encouragement.
+%\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
+\title{ OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
+
+\author{William Violette\thanks{Contact: Federal Trade Commission, Washington, DC: william.j.violette@gmail.com \\ I am grateful to Andrew Foster, Matthew Turner, Jesse Shapiro, Daniel Bj\"{o}rkegren, and Bryce Steinberg for guidance and encouragement.
 For helpful conversations, I am also grateful to John Friedman, Edward Glaeser, Emily Oster, Brian Knight, and Lint Barrage.
@@
 This work was supported through the Watson Institute for International and Public Affairs.
-} \\ [Job Market Paper: \href{https://drive.google.com/file/d/1dM41qZLZY3EPtUqHbca6MIS-nT77hv_-/view?usp=sharing}{\textcolor{blue}{Link to Current Version}}]}
+Any opinions and conclusions expressed herein are those of the author and do not necessarily represent the views of the the Federal Trade Commission or its Commissioners.}
+ }
+%\\ 
+%[Job Market Paper: \href{https://drive.google.com/file/d/1dM41qZLZY3EPtUqHbca6MIS-nT77hv_-/view?usp=sharing}{\textcolor{blue}{Link to Current Version}}]}
 
@@
 The model predicts that low fixed fees and high marginal prices decrease access by weakening incentives to share water.
-In contrast, the optimal pricing policy features high fixed fees and low marginal prices, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
+In contrast, the optimal pricing policy features a high fixed fee and low marginal price, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
 This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.
@@
 Increasing marginal prices weaken incentives for households to extend water access to their neighbors through sharing (\cite{whittington1992possible}).
-Fixed fee subsidies may have limited impacts on water access when sharing households split connection fees with their neighbors.
+Fixed fee subsidies may have limited impacts on water access when sharing households already split connection fees with their neighbors.
 Since low-income households are more likely to use water from their neighbors, increasing marginal prices and low fixed fees may combine to act as regressive taxes in the presence of sharing.
@@
 These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections to install and maintain.
-Yet, since sharing involves costly redistribution of water, the optimal tariff subsidizes individual connections on the margin by pricing above marginal cost and setting the fixed fee below the cost of installing and maintaining each connection.
+%Yet, since sharing involves costly redistribution of water, the optimal tariff subsidizes individual connections on the margin by pricing above marginal cost and setting the fixed fee below the cost of installing and maintaining each connection.
 
@@
 Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
-Finally, the counterfactual exercises borrow the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
-Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of public funding for water (\cite{laffont2005regulation}).
+Finally, the counterfactual exercises simulate the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
+Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of using public funding for water infrastructure (\cite{laffont2005regulation}).
 
@@
 
-The next section describes the context of water provision in Manila.
+This paper proceeds by first describing the context of water provision in Manila.
 Section~\ref{section:data} describes the data.
@@
 
-Supplemental survey data from a subset of Manila include income measures that are used to approximate household income using the full set of demographic measures and their interactions.
+With information on water source and monthly expenditures as well as household income, the 2011 Community Based Monitoring System data cover over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown metro Manila.
+These data are used to impute income for households outside of the sample according to the following demographic measures: age of household head and indicators for low-skilled employment of household head, residing in a duplex, residing in a house, as well as all possible household sizes and number of employed household members.
+The imputation also includes all possible interactions between these measures.
+
+%Supplemental survey data from the Community Based Monitoring Survey in Pasay City --- a large city in the center of Metro Manila --- include household income measures for  that are used to approximate household income using the full set of demographic measures and their interactions.
 
@@
 For ease of notation, let the subscript $C$ indicate connection-level attributes, summing over all households using from connection $C$.
-
 This model does not allow for households to choose different water sources over time, which is consistent with large fixed costs involved in initially purchasing a connection or establishing a sharing relationship.
-Section~\ref{section:hasslemodel} extends the model to allow for cases where households exogenously lose access to their current water source and must substitute toward another nearby source.
+Section~\ref{section:hasslemodel} extends the model to allow for cases where households may exogenously lose access to their current water source and must substitute toward another nearby source.
 
 In the second step, each household then chooses how much water to use each month from their source.
-Since water sources provide utility through monthly consumption, the following section describes the decision process in reverse order, first characterizing monthly water consumption choices (taking the initial source choice as given) and second, describing the initial water source choices.
+Since water sources provide utility through monthly consumption, it is useful to describe the decision process in reverse order, first characterizing monthly water consumption choices (taking the initial source choice as given) and second, characterizing the initial water source choices.
 
@@
 
-As a simple way to capture this coordination task, let each household $i$ set a goal for water use each month, $w_i$, knowing that unobserved consumption shocks, $\epsilon_i$, may increase or decrease their realized amount of usage.
+As a simple way to capture this coordination task, let each household $i$ choose a goal for water use each month, $w_i$, knowing that unobserved consumption shocks, $\epsilon_i$, may increase or decrease their realized amount of usage.
 Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.
@@
 \end{align}
-Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as in Figure~\ref{figure:consumptionhistogram}.\footnote{This utility form builds on \cite{einav2013selection} who use a similar form to characterize extensive and intensive choices of health insurance.}   Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are price sensitive.
+Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as shown in Figure~\ref{figure:consumptionhistogram}.\footnote{This utility form builds on work by \cite{einav2013selection} who use a similar form to characterize extensive and intensive choices of health insurance.}   Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are sensitive to price.
 The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean and variance terms, $\sigma_{\epsilon}^2$, allowing for correlation with neighboring households $i$ and $j$ through term ${\rho}^{\epsilon}_{i,j}$.
@@
 
-To account for idiosyncratic preference shocks for water each month, let household's fixed preference, $\Gamma_{i}$, be decomposed into a static, household-specific component, $\gamma_i$, and a normally distributed, idiosyncratic component, $\eta_{i}$, which is assumed to follow a multivariate normal distribution among sharing partners:
+To account for idiosyncratic preference shocks for water each month, let household's fixed preference, $\Gamma_{i}$, be decomposed into a static, household-specific component, $\gamma_i$, and an idiosyncratic component, $\eta_{i}$, which is assumed to follow a multivariate normal distribution among sharing partners:
 \begin{align*}
@@
 This preference shock is also assumed to be independent of the consumption shocks, $\epsilon_C$.
-Aggregating these preferences shocks over all sharing households using connection, $C$, produces a joint shock, $\eta_C$, according to the convolution of these random normal variables with a variance equal to $\sum_{i=1}^{S} \sigma_{\eta}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \rho^{\eta}_{i,j} \sigma_{\eta}^2$.
+Aggregating these preferences shocks over all households sharing connection, $C$, produces a joint shock, $\eta_C$, according to the convolution of these random normal variables with a variance equal to $\sum_{i=1}^{S} \sigma_{\eta}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \rho^{\eta}_{i,j} \sigma_{\eta}^2$.
 
@@
 
-The household problem is additionally complicated by the presence of non-linear price schedules for water.
+The household problem is additionally complicated by the presence of an increasing price schedule for water; as a household uses more water in one month, they face higher marginal prices.
 Figure~\ref{figure:tariff} provides the increasing tariff in Manila.
-The non-linear price schedule produces kinks in household budget constraints leading to non-linear demand functions.
-Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.
+This price schedule produces kinks in household budget constraints leading to non-linear demand functions.
+Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe the tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.
 The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:\footnote{In this case in Manila, $\overline{W}^{0}$ is zero while $\overline{W}^{K}$ is infinity.}
@@
 Given prices and household utility, the final ingredient for characterizing consumption choices is the budget constraint.
-The budget constraint includes monthly household income, $Y_i$, and monthly fixed costs of using the water connection, $F_i$, which are assumed to capture three components: (1) monthly service fees, (2) initial connection fees amortized in monthly terms for the duration of the connection, and (3) unobserved, fixed hassle costs associated with setting up a connection, which are also amortized into monthly terms.
+The budget constraint includes monthly household income, $Y_i$, and monthly fixed costs of using the water connection, $F_i$, which are assumed to capture three components: (1) monthly service fees, (2) initial connection fees amortized into monthly terms for the duration of the connection, and (3) unobserved, fixed hassle costs associated with setting up a connection, which are also amortized into monthly terms.
 Data does not track household water source choices over time in a comprehensive way, which limits the extent to which the model can distinguish between one-time connection costs and monthly service/maintenance costs.
@@
 The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement, allocating $F_i$ to each household.
-Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions and Section~\ref{section:watersourcechoice} later discusses how fixed costs are divided.
+Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions and Section~\ref{section:watersourcechoice} later discusses how fixed costs are divided between sharing households.
 
@@
 Since data limitations prevent identifying the specific type of contract associated with each shared connection, the model assumes that all households evenly split the bill and explores the theoretical and empirical implications of alternate models in Appendix~\ref{appendix:fixedprice}.
-The model captures bill splitting by dividing the total monthly payment for a water connection across the $S$ sharing households.
+The model captures bill splitting by evenly dividing the total monthly payment for a water connection across the $S$ sharing households.
 
@@
 \end{align}
-
 The full budget constraint is a piece-wise expansion of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.
 $B_{C,k}$ represents the total water bill for connection $C$ given the tariff schedule.
-This term is calculated by subtracting the current price that the household faces, $p^{k}$, from the previous prices and multiplying by their exposure given by, $(\overline{W}^{j}-\overline{W}^{j-1})$.
+This term is calculated by multiplying each price by the volume of consumption exposed to that price.
 %\footnote{In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.
@@
 Since prices are non-linear, the total consumption level for each connection, $W_C$, determines the marginal price faced by all households.
-For example, with an increasing block tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.
-
-Substituting the numeraire good, $x_i$ for the budget constraint in household utility from equation (\ref{equation:umaxfirst}) simplifies the household's problem to a single choice variable --- targeted consumption, $w_i$.
+For example, with an increasing tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.
+
+Substituting the budget constraint (equation (\ref{equation:budgetconstraint})) into the household utility (equation (\ref{equation:umaxfirst})) for the numeraire good $x_i$ simplifies the household's maximization problem to a single choice variable --- targeted consumption, $w_i$.
 The household's expected utility problem over consumption shocks $\epsilon_C$ then takes the following form:
-
 %\scalebox{.88}{\parbox{1\linewidth}{
@@
 %}} \\
-
 % E[U(w_i)] = 
 \begin{align*}
-max_{w_i} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-{w_C}}^{\overline{W}^{k}-{w_C}} (Y_i - F_i) -  \dfrac{ B_{C,k} }{S_C}     + (1-p_s) W_i   - \frac{1}{2\alpha } ( W_i - \Gamma_i + \alpha_i )^2  d \epsilon_C
-\end{align*}
-
+max_{w_i} &\sum_{k=1}^{K} \int_{\overline{W}^{k-1}-{w_C}}^{\overline{W}^{k}-{w_C}} (Y_i - F_i) -  \dfrac{ B_{C,k} }{S_C}     + (1-p_s) W_i   - \frac{1}{2\alpha } ( W_i - \Gamma_i + \alpha_i )^2  d \epsilon_C
+\end{align*}
+%B_{C,k}  &= p^{k} (W_{C}^{*} - \overline{W}^{k-1}) +\sum_{j=1}^{k-1}  p^{j}(\overline{W}^{j}-\overline{W}^{j-1}) 
 Where $\epsilon_C$ is the convolution of consumption shocks across sharing households distributed as follows:
@@
 \end{align*}
-To solve this system, the model assumes that households follow a perfect information, pure-strategy Nash-Equilibrium in choosing consumption.
+To solve this system, this approach assumes that households follow a perfect information, pure-strategy Nash-Equilibrium in choosing consumption.
 Using this structure, households compute their best response consumption functions to arrive at a symmetric equilibrium taking consumption for their sharing partners as given.
@@
  \end{align}
-\hspace{2cm} Where 
+\hspace{2cm} Where:
 \begin{align}
@@
 
-The first order condition in equation (\ref{equation:firstordercondition}) reveals that consumers balance their fixed preference for water, $\Gamma_i$, against their price sensitivity, $\alpha_i$, hassle costs, $H_i$, and expected marginal price, $MP_C$ (scaled by the number of sharing households, $S$).
-
-Expected marginal price $MP_C$ in equation (\ref{equation:weightedmarginalprice}) intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the household to higher prices in expectation.
+The first order condition (equation (\ref{equation:firstordercondition})) reveals that consumers balance their fixed preference for water, $\Gamma_i$, against their price sensitivity, $\alpha_i$, hassle costs, $H_i$, and expected marginal price, $MP_C$ (scaled by the number of sharing households, $S$).
+Expected marginal price $MP_C$ (equation (\ref{equation:weightedmarginalprice})) intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the entire connection to higher prices in expectation.
 This first-order condition characterizes the best-response functions for each household.
@@
 
-To arrive at a tractable expression for water demand, I simplify equation (\ref{equation:weightedmarginalprice}) by assuming that households approximate the normal distribution with a simple uniform distribution.
+To arrive at a tractable expression for water demand, it is helpful to simplify equation (\ref{equation:weightedmarginalprice}) by assuming that households approximate the normal distribution with a simple uniform distribution.
 This assumption implies that households give zero likelihood to extremely high or low consumption shocks and even likelihood to moderate consumption shocks.
 From an empirical perspective, this function allows for an analytical solution to the demand function while ensuring that the estimation can rely on normally distributed errors to estimate rich preference heterogeneity.
-
 I use the following piece-wise function form to approximate the normal cumulative distribution:
@@
 Appendix~\ref{appendix:linearapprox} graphs this approximation against a standard normal cumulative distribution function and simulates optimal demand under both distributions, finding negligible evidence that this approximation would substantially bias the estimates or affect welfare measures.
-
-After substituting the normal cumulative distribution function $\Phi(.)$ for $g(.)$ in equation (\ref{equation:weightedmarginalprice}), expected marginal price becomes the sum of potentially overlapping piece-wise functions, $g(.)$.
-When households face small consumption shocks, there is no probability that these shocks will overlap and expose the household to multiple price levels.
-Therefore, solving the best-response function (summing across all households using connection $C$) yields a simple expression for the deterministic segment of connection-level demand:
-\begin{align*}
-d^{j}_C &= \gamma_C - \alpha_C [ H_{C} + \frac{p^{j}}{S}]  
-\end{align*}
+After substituting the normal cumulative distribution function $\Phi(.)$ for $g(.)$ in equation (\ref{equation:weightedmarginalprice}), expected marginal price becomes the sum of potentially overlapping piece-wise functions, meaning that the optimal demand will also be piece-wise.
+I proceed by describing the different pieces of demand before putting the pieces together to form the full demand schedule.
+
+When households face very small consumption shocks, there is no probability that these shocks expose households to multiple prices.
+Therefore, solving the best-response function (summing across all households using connection $C$) yields a simple expression for optimal targeted demand:
+\begin{align}
+\label{equation:demandlinear}
+w^{j}_C &= \gamma_C - \alpha_C [H_{C} + \frac{p^{j}}{S}]  
+\end{align}
 This case produces a linear demand function where $\alpha_C$ can be readily interpreted as the price sensitivity parameter while $\gamma_C$ captures the portion of demand that is invariant to prices.
+In this case, demand is only sensitive to the marginal price, $p^{j}$, local to each segment of the tariff schedule.
 This demand function captures moral hazard from bill-splitting by dividing the price sensitivity, $\alpha_C$, by the total number of households using the connection, $S$.
 Comparing demand among shared connections to individual connections, the extent of over-consumption at an average price of $p$ can be roughly summarized as $\frac{S-1}{S} \alpha_C p $.
+The price sensitivity, $\alpha_C$, also attenuates the extent to which the hassle cost, $H_C$, enters demand.
 %The first condition ensures that the connection's idiosyncratic preference for water, $\eta_C$, falls between the appropriate thresholds, $\overline{\eta}_{L}, \overline{\eta}_{U}$, to be exposed to this particular segment of the price schedule.
@@
 %When households face large consumption shocks, these functions overlap across price thresholds, which means that households must consider multiple prices when choosing their consumption.  
-This expression for demand holds when total demand (including idiosyncratic preference $\eta_C$) falls sufficiently between two price thresholds: 
-\begin{align*}
-\overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}  \, \leq \, & d^{j}_C + \eta_C \, \leq  \, \overline{W}_{l+1} - \sqrt{2} \sigma_{\epsilon_C} 
-\end{align*}
-High variances of consumption shocks, $\sigma_{\epsilon_C}$, combined with small distances between kink points create cases where these conditions are not satisfied and households are forced to consider more than one price in choosing optimal consumption.
-Allowing for households to be exposed to price thresholds $j$ through $l$, the general solution to the best-response function for the connection $C$ again yields the deterministic segment of connection-level demand as follows:
-\begin{align*}
-d_{C}^{j,l}       		&= \frac{ 1}{ V^{j,l} } \Big ( \gamma_C - \alpha_C [ H_{C} - \frac{MP^{j,l}}{S} ] \Big )    \\
+This expression for demand holds when total demand (including the fixed preference shock $\eta_C$) falls sufficiently between two price thresholds: 
+\begin{align*}
+\overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}  \, \leq \, & w^{j}_C + \eta_C \, \leq  \, \overline{W}_{l+1} - \sqrt{2} \sigma_{\epsilon_C} 
+\end{align*}
+These conditions are less likely to be satisfied when connections have high variance in their consumption shocks, $\sigma_{\epsilon_C}$,  and face small distances between price thresholds, $\overline{W}_{l}$ and $\overline{W}_{l+1}$.
+In this case, consumption shocks may expose the connection to different prices and households need to consider the probability of facing these prices in choosing their optimal consumption targets.
+Allowing for households to be exposed to price thresholds $j$ through $l$, the general solution to the best-response function for the connection $C$ again yields targeted demand as follows:
+\begin{align*}
+w_{C}^{j,l}       		&= \frac{ 1}{ V^{j,l} } \Big ( \gamma_C - \alpha_C [ H_{C} - \frac{MP^{j,l}}{S} ] \Big )    \\
 \text{ Where : }& \\
@@
 All terms are also weighted by a variance term, which depends on the gap between the highest and lowest prices $j$ and $l$.
-This demand function holds for levels of demand between the following thresholds:
-\begin{align*}
-B_{j,l} \, & \leq \, D_C^{j,l} \, \leq \, T_{j,l} \\
+This expression holds for levels of demand between the following thresholds:
+\begin{align*}
+B_{j,l} \, & \leq \, W_C^{j,l} \, \leq \, T_{j,l} \\
 \text{Where :} & \\
-B_{j,l} &= max \{ x \in I_{j,l} \, | \, x \leq D_C^{j,l} \} \,\,\, , \,\,\, T_{j,l} = min  \{ y \in I_{j,l} \, | \, y \geq D_C^{j,l} \} \\
+B_{j,l} &= max \{ x \in I_{j,l} \, | \, x \leq W_C^{j,l} \} \,\,\, , \,\,\, T_{j,l} = min  \{ y \in I_{j,l} \, | \, y \geq D_C^{j,l} \} \\
 I_{j,l} &= \{ \overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}, \overline{W}_{l} - \sqrt{2}\sigma_{\epsilon_C}, \overline{W}_{j} + \sqrt{2} \sigma_{\epsilon_C},  \overline{W}_{j} - \sqrt{2} \sigma_{\epsilon_C}  \} \\
-D_C^{j,l} &=  d_C^{j,l} + \frac{ \eta_C }{ V^{j,l} } 
-\end{align*}
-Bottom $B_{j,l}$ and top $T_{j,l}$ thresholds sandwich connection demand $D_C^{j,l}$ and are drawn from the full set of possible thresholds, $I_{j,l}$, above and below the tariff kink points, $\overline{W}_{l}$ and $\overline{W}_{j}$.
-In cases with high variance in consumption shocks, kink points $j$ and $l$ may span many other marginal prices, $k$.
-At the same time for small consumption shocks combined with far distances from price thresholds, this expression simplifies to the linear case described above.
+W_C^{j,l} &=  w_C^{j,l} + \frac{ \eta_C }{ V^{j,l} } 
+\end{align*}
+Bottom, $B_{j,l}$, and top, $T_{j,l}$, thresholds sandwich connection demand $W_C^{j,l}$ and are drawn from the full set of possible thresholds, $I_{j,l}$, above and below the tariff kink points, $\overline{W}_{l}$ and $\overline{W}_{j}$.
+In cases with high variance in consumption shocks, kink points $j$ and $l$ may span many other marginal prices, $k$ where $l \leq k \leq j$.
+At the same time for small consumption shocks and large distances between price thresholds, this expression simplifies to the linear case in equation (\ref{equation:demandlinear}).
 %T &= \{ \overline{W}_{0} + \sqrt{2} \sigma_{\epsilon_C}, ..., \overline{W}_{N} + \sqrt{2} \sigma_{\epsilon_C}, \overline{W}_{0} - \sqrt{2} \sigma_{\epsilon_C}, ..., \overline{W}_{N} - \sqrt{2} \sigma_{\epsilon_C}  \} \\
@@
 
-Constructing a full demand function for a connection requires simply connecting piecewise demand segments to span the full range of consumption choices.
-However, since the degree of overlap between price segments depends on the variance in consumption shocks, there can be different optimal demand functions for different levels of consumption variance, $\sigma_{\epsilon_C}$.
+Constructing the full demand schedule for each connection requires simply connecting these demand segments to span the full range of consumption choices.
+However since targeted demand depends on the variance in consumption shocks, $\sigma_{\epsilon_C}$, there can be different optimal demand functions for different levels of $\sigma_{\epsilon_C}$.
 To determine a single piecewise demand function, I take the approach of (1) assuming ex-ante bounds on $\sigma_{\epsilon_C}$, (2) constructing the implied optimal demand function given these bounds, and (3) estimating the model to see if the estimated $\sigma_{\epsilon_C}$ rejects these bounds in the data.
@@
 
-Given the optimal consumption choice, $w^{*}_C$, for each connection, observed consumption for a particular connection, $Q_C$, becomes the sum of optimal consumption and the total consumption shock for that connection, $\epsilon_C$:
+Given the optimal consumption choice, $W_C$, for each connection, observed consumption for a particular connection, $Q_C$, becomes the sum of optimal consumption and the total consumption shock for that connection, $\epsilon_C$:
 \begin{align}\label{equation:observeddemand}
-Q_C &= w^{*}_C + \epsilon_C
+Q_C &= W_C + \epsilon_C
 \end{align}
@@
 % Let total demand within each segment simplify to $D_{j,l} = \frac{ d^{j,l} }{ V^{j,l} }  + \frac{ \eta_C }{ V^{j,l} } $. 
-
-These probabilities allow for the derivation the likelihood function for each consumption realization, using some additional notation.\footnote{By allowing households to anticipate exogenous shocks to their consumption, this approach builds on the standard framework of \cite{burtless1978effect} and \cite{moffitt1986econometrics} to estimate demand over non-linear budget constraints, which has been recently implemented by \cite{szabo2015value} and \cite{mcrae2014infrastructure}.}  For each demand segment, denote the bottom threshold for the preference shock needed to reach that segment as, $\overline{\eta}_{B,j} = B_{j,l} - d^{j,l} $ and the top threshold as $\overline{\eta}_{T,l} = T_{j,l} - d^{j,l} $.\footnote{Conditions on $\eta_C$ defining each segment are given in more detail in Appendix~\ref{appendix:optimaldemand} equation (\ref{equation:generaldemand}).}  Define the variance-adjusted preference shock as $\Psi = \frac{\eta_C}{V_{j,l}}$.
+These probabilities allow for the derivation the likelihood function for each consumption realization, using some additional notation.\footnote{By allowing households to anticipate exogenous shocks to their consumption, this approach builds on the standard framework of \cite{burtless1978effect} and \cite{moffitt1986econometrics} to estimate demand over non-linear budget constraints, which has been recently implemented by \cite{szabo2015value} and \cite{mcrae2014infrastructure}.}  For each demand segment, denote the bottom threshold for the preference shock needed to reach that segment as, $\overline{\eta}_{B,j} = B_{j,l} - w^{j,l} $ and the top threshold as $\overline{\eta}_{T,l} = T_{j,l} - w^{j,l} $.\footnote{Conditions on $\eta_C$ defining each segment are given in more detail in Appendix~\ref{appendix:optimaldemand} equation (\ref{equation:generaldemand}).}  Define the variance-adjusted preference shock as $\Psi = \frac{\eta_C}{V_{j,l}}$.
 Let the sum of the two stochastic terms equal $\zeta = \Psi + \epsilon_C$.
@@
 \begin{align}\label{equation:llcontributionlinear}
-\sum_{j} f_{\zeta}( Q - D^{j,l} ) \Big [ F_{ \Psi | \zeta = Q - D^{j,l} } (\overline{\eta}_{T,l}) - F_{ \Psi | \zeta = Q - D^{j,l} } (\overline{\eta}_{B,j})  \Big ]
+\sum_{j} f_{\zeta}( Q - W^{j,l} ) \Big [ F_{ \Psi | \zeta = Q - W^{j,l} } (\overline{\eta}_{T,l}) - F_{ \Psi | \zeta = Q - W^{j,l} } (\overline{\eta}_{B,j})  \Big ]
 \end{align}
@@
 \begin{align*}
-f_{\zeta}( Q - D^{j,l} ) &= \frac{1}{\sigma_{\zeta}} \phi(\frac{Q - D^{j,l}}{\sigma_{\zeta}} ) \\
-F_{ \Psi | \zeta = Q - D^{j,l} } (\overline{\eta}_{T,l}) &= \int_{-\infty}^{\overline{\eta}_{T,l}} f_{\Psi | \zeta = Q - D^{j,l}} (x) dx \\
+f_{\zeta}( Q - W^{j,l} ) &= \frac{1}{\sigma_{\zeta}} \phi(\frac{Q - W^{j,l}}{\sigma_{\zeta}} ) \\
+F_{ \Psi | \zeta = Q - W^{j,l} } (\overline{\eta}_{T,l}) &= \int_{-\infty}^{\overline{\eta}_{T,l}} f_{\Psi | \zeta = Q - W^{j,l}} (x) dx \\
 &= \int_{-\infty}^{\overline{\eta}_{T,l}} \frac{1}{\sigma_{\zeta} \sqrt{1-\rho^2}}\phi \Big ( \big ( \frac{ x V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) dx \\
@@
 \text{Where:} &\\
-q^{j,l} &= \frac{(Q - D^{j,l})}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta} = \sqrt{ \frac{\sigma_{\eta}^2}{V_{j,l}^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho = \frac{ \sigma_{\eta}}{  \sigma_{\zeta} V_{j,l}  }
+q^{j,l} &= \frac{(Q - W^{j,l})}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta} = \sqrt{ \frac{\sigma_{\eta}^2}{V_{j,l}^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho = \frac{ \sigma_{\eta}}{  \sigma_{\zeta} V_{j,l}  }
 \end{align*}
@@
 The full log-likelihood is computed by summing the log of the likelihood in equation  (\ref{equation:LLikelihood}) over all connections and time periods.
-
 % \begin{align*}
@@
 % \end{align}
-
 \subsubsection{Households using from Water Small-Scale Providers}
@@
 While the vast majority of households use piped water, around 6\unskip\% of households still source their water from small-scale water vendors.
-In this model, these small-scale sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed cost, $F_v$, and a single marginal price, $p_v$.
-The monthly fixed cost, $F_v$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.
-Similarly, the marginal price, $p_v$, includes both the price per unit as well as any differences in water quality or ease of use relative to piped water.
+In this model, these small-scale sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed cost, $F_V$, and a single marginal price, $p_V$.
+The monthly fixed cost, $F_V$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.
+Similarly, the marginal price, $p_V$, includes both the price per unit as well as any differences in water quality or ease of use relative to piped water.
 Demand for this source becomes a simple linear function of prices given by equation (\ref{equation:vendordemand}).
 \begin{align}\label{equation:vendordemand}
-w^{*} = \Gamma_i - \alpha_i p_v
+w = \Gamma_i - \alpha_i p_V
 \end{align}
-Since the data do not record monthly consumption information for households using from vendors, these households do not contribute to the likelihood function above.
+Since the data do not record monthly consumption information for households using from vendors, these households do not contribute to the likelihood function (equation (\ref{equation:LLikelihood})).
 
@@
 
-This section describes a sequential game where households choose their water sources.
-This game results in a unique equilibrium of source choices given the preference parameters for each household as well as the costs of using each water source.
+This section describes a sequential game where households choose their water sources given their demands for water.
+This game results in a unique equilibrium of source choices according to the preference parameters for each household as well as the costs of using each water source.
 
@@
 
-Recovering demand for water for each household allows for calculating the expected utility that each household receives from each water source, guiding their source choices.
-This choice becomes a strategic decision since each household's water connection can also serve as a water source for other households in a neighborhood.
+%Recovering demand for water for each household allows for calculating the expected utility that each household receives from each water source, guiding their source choices.  
+Choosing a water source becomes a strategic decision since each household's water connection can also serve as a water source for other households in a neighborhood.
 The model assumes that each set of neighboring households plays a full-information, sequential game, deciding whether to purchase their own tap, share with a previously connected household, or purchase from a vendor.
@@
 
-For all other households, define the following function that maps a household's choice to connect into a sharing opportunity for the following households:
+For all other households, define the following function that maps a previous household's choice to connect into a possible sharing opportunity:
 \begin{align*}
@@
 This transfer allows sharing households to help contribute to the fixed costs of owning and maintaining the connection.
-\input{tables/fee_even_some}\unskip\% of sharing households in the mobile survey report splitting some or all of the initial connection fee with their neighbors; for the remaining households, the owner pays the full connection fee.
+\input{tables/fee_even_some}\unskip\% of sharing households in the mobile survey report splitting some or all of the initial connection fee with their neighbors; for the remaining households, the owner reports paying the full connection fee.
 
@@
 First, these sharing arrangements feature long-term relationships between close neighbors who are also often family members.
-Second, small areas often feature multiple sharing opportunities for each household, creating some competitive pressure on sharing arrangements.
+Second, small areas often feature multiple sharing opportunities for each household, creating some competitive pressures on sharing arrangements.
 Third, in the mobile survey, sharing households appeal to an ethic of fairness as the primary reason for dividing monthly payments instead of other reasons such as matching tariff prices or conserving environmental resources.
 
-Expected utility from using a connection alone is defined as $u^{i} (c|1)$.
+Expected utility from using a connection alone is defined as $u^{i}(c|1)$.
 This expression can be computed by inputting demand from equation (\ref{equation:generaldemand}) with $S=1$ into utility given by equation (\ref{equation:umaxfirst}).
-Expected utility from owning and sharing a connection is defined as $u^{i}(c | S^i ) $ and expected utility for household $j$ from using a connection owned by neighbor $i$ as $u^{j} ( s^{i} | S^i )$.
+Expected utility from owning and sharing a connection is defined as $u^{i}(c| S^i ) $ and expected utility for household $j$ from using a connection owned by neighbor $i$ as $u^{j}(s^{i} |S^i )$.
 %Sharing utilities can be calculated with the same method, substituting for $S$.
@@
 To the extent that household size serves as a proxy for demand, this finding provides suggestive evidence that larger demand households with greater utility from purchasing a water connection are also more likely to be owners.
-Given that transfers allow households to efficiently share surplus, the sequence is unlikely to have large impact on the overall efficiency of the resulting arrangements.
+Given that transfers allow households to efficiently share surplus, the sequence is unlikely to have large impacts on the overall efficiency of the resulting arrangements.
 However, moving earlier may affect the welfare of particular households.
@@
 The sequential game is solved using backward induction and considering only pure-strategy equilibria.
-First, the last mover, household $I$, identifies the choices that maximize its payoffs at each possible choice set reached by the game.\footnote{In very rare cases where payoffs are equal, the tie-breaking rule prioritizes vendors, then individual connections, and finally shared connections ranked by the sequence of owners.}  Given these choices, the next-to-last mover, household $(I-1)$, can calculate its payoffs for each corresponding choice set.
+First, the last mover, household $I$, identifies the choices that maximize its payoffs at each possible choice set reached by the game.\footnote{In very rare cases where payoffs are equal, the tie-breaking rule prioritizes vendors, then individual connections, and finally shared connections ranked by the sequence of movers.}  Given these choices, the next-to-last mover, household $(I-1)$, can calculate its payoffs for each corresponding choice set.
 Iterating backwards, this process characterizes a unique equilibrium set of source choices for all households.
@@
 \input{tables/neighbor}\unskip\% report that they would ``use a neighbor's tap'' while the remaining responses are roughly evenly split between using a public or private deep well, fetching from a water truck, or filling bottles at a water refilling shop.
-Although shared connections vastly outnumber households using from vendors in the population as shown in Table~\ref{descriptives}, using a neighbor's tap is less common in response to a sudden disconnection.
-Since sharing relationships often take the form of long-term contracts, households may often face high costs in reaching a temporary sharing agreement with a neighbor.
+Although shared connections vastly outnumber households using from vendors in the population as shown in Table~\ref{descriptives}, using a neighbor's tap is much less common in response to a sudden disconnection.
+Since sharing relationships often take the form of long-term contracts, households may face high costs in reaching a temporary sharing agreement with a neighbor.
 Additional descriptive findings discussed in Section~\ref{section:hasslecostestimation} suggest that the decision to share with a neighbor is uncorrelated with the features of water demand among both the household experiencing a leak as well as their neighbors.
@@
 The model also includes the term $F^{S}$ to capture any fixed costs associated with setting up a temporary sharing relationship relative to simply fetching from a vendor.
-Given these preference shocks, total utility for household $l$ for using alternative $A$ can be parameterized with the following:
+Given these preference shocks, total utility for household $l$ for using alternative $A$ can be parameterized with the following expression:
 \begin{align}\label{equation:hassleutilities} 
@@
 %as $\omega$ approaches zero.  When $\omega$ equals zero,
-Let $L$ represent the total households affected by a single leak.
-$L$ is greater than one in cases where connections serving multiple households experience a leak.
-All $L$ households in the neighborhood of a single leak are assumed to receive the same preference shock $\xi_{A,l}$ so that they follow identical substitution patterns.\footnote{This assumption may lead to a slight underestimation of the hassle costs since these households may actually distribute across different sharing relationships, exposing them to lower points on the tariff schedule than if all households were clustered on the same connection.}
+Let $L$ represent the total households affected by a single connection leak.\footnote{$L$ is greater than one in cases where connections serving multiple households experience a leak.}  All $L$ households in the neighborhood of a single leak are assumed to receive the same preference shock $\xi_{A,l}$ so that they follow identical substitution patterns.\footnote{This assumption may lead to a slight underestimation of the hassle costs since these households may actually distribute across many different sharing relationships, exposing them to lower points on the tariff schedule than if all households were clustered on the same connection.}
 
@@
 Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $H_i$ while other households $l \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.
-Therefore, this method identifies hassle costs from variation in exposure for owners of the connection.
 Section~\ref{section:hasslecostestimation} details potential limitations of this assumption.
+% Therefore, this method identifies hassle costs from variation in exposure for owners of the connection.
 
@@
 Household preferences for water are estimated by maximizing the likelihood function in equation (\ref{equation:LLikelihood}) for consumption recorded at each connection and month.
-This section first details how each set of parameters are parameterized in the estimation:
+This section first details how each set of preferences are parameterized in the estimation:
 
@@
 While this imputation may be reasonable for spatially correlated characteristics like type of dwelling, this approach may introduce bias if sharing households have systematically different numbers of employed individuals or ages.
-Estimates of price sensitivities in Table~\ref{table:demandestimates} exhibit little heterogeneity across many of these dimensions, which suggests that any bias from mismeasurement may have small effects on the counterfactual exercises.
+Estimates of price sensitivities in Table~\ref{table:demandestimates} exhibit little heterogeneity across many of these dimensions, which suggests that any bias from mismeasurement may have small effects in evaluating policies.
 Since household-specific price sensitivities $\alpha_i$ enter linearly into the connection-level demand function in equation (\ref{equation:generaldemand}), connection-level price sensitivity can be written simply as $\alpha_C = \alpha \sum_{i=1}^{S} Z_i$.\footnote{The model does not control for seasonality or calendar time since the raw data exhibit negligible trends in water usage over time.}
@@
 First, the non-linear pricing structure given by Figure~\ref{figure:tariff} forces households to decide whether to consume above or below tariff kink points as they face monthly shocks to their demand.
-Second, regulated tariff changes over time affecting all households generate time-series variation in the tariff, which can be seen in Appendix \ref{appendix:tariffvariation}.
+Second, regulated tariff changes over time affecting all households generate time-series variation in the tariff, which can be seen in Appendix~\ref{appendix:tariffvariation}.
 Third, I use rate-changes which affect individual connections differently over time described in more detail in Appendix~\ref{appendix:ratechangeelasticity}.
 The structural model combines all of these sources of price variation in the estimation.
-The identification assumption is that the consumption and preference shocks, $\epsilon,\eta$ are uncorrelated with these price changes.
-
-\textbf{Preference and Consumption Shocks} $\sigma_{\eta},\rho_{\eta},\sigma_{\epsilon},\rho_{\epsilon}$  :  This strategy also estimates parameters governing the distribution of preference and consumption shocks.
-
+The identification assumption is that the consumption and preference shocks, $\epsilon,\eta$ are normally distributed and uncorrelated with these price changes.
+
+\textbf{Preference and Consumption Shocks} $\sigma_{\eta},\rho_{\eta},\sigma_{\epsilon},\rho_{\epsilon}$  :  %This strategy also estimates parameters governing the distribution of preference and consumption shocks.
 %Household-level preference shocks $\eta_i$ can be aggregated to a connection-level preference shock $\eta_C$ which is composed of both the standard deviation of the $\eta_i$ terms as well as the extent to which these terms are correlated between sharing households.
-The estimation strategy recovers connection-level variance terms $\sigma_{\eta}$ for different types of connections, which are later decomposed into household variance and covariances between neighboring households below.
-Heterogeneity in $\sigma_{\eta}$ is estimated with respect to connections serving one, two, or three plus households.
+%For preference shocks, the estimation recovers variance estimates for different types of connections, which are later decomposed into variance and covariances between neighboring households. 
+Heterogeneity in $\sigma_{\eta}$ is separately according to connections serving one, two, or three plus households.
 The estimation also allows $\sigma_{\eta}$ to vary non-parametrically according to quintiles of mean consumption at the connection-level.
-Specifically, the estimation includes a separate variance term for the bottom quintile of consumption as well as a term for the top two quintiles of consumption.\footnote{There is too little variation in the data to separately identify a full set of quintiles while also allowing $\sigma_{\eta}$ to vary by sharing status.}  Since larger users naturally have higher variance in their consumption, estimating a single $\sigma_{\eta}$ across all connections produces large bias in the price sensitivity coefficients, $\alpha$.
+Specifically, the estimation includes a separate variance term for the bottom quintile of consumption as well as a term for the top two quintiles of consumption.\footnote{There is too little variation in the data to separately identify a full set of quintiles while also allowing $\sigma_{\eta}$ to vary by sharing status.}  Since larger users naturally have higher variances in their consumption, estimating a single $\sigma_{\eta}$ across all connections produces large bias in the price sensitivity coefficients, $\alpha$.
 This bias results from constraining large and small users to receive similarly scaled shocks and therefore enforcing that these users respond to the non-linear tariff schedule in similar ways.
-While using quintiles of observed consumption may be problematic since consumption choices are themselves endogenous, this approach approximates connection-specific, $\sigma_{\eta}$ terms, which would be infeasible given limited months of data available for each connection.
+While using quintiles of observed consumption may be problematic since consumption choices are themselves endogenous, this approach approximates connection-specific $\sigma_{\eta}$ terms, which would be infeasible given limited months of data available for each connection.
 %The results are robust to different non-parametric specifications for $\sigma_{\eta}$.
@@
 
-The $\sigma_{\eta}$ and $\sigma_{\epsilon}$ parameters are separately identified from the extent of clustering around price thresholds relative to the overall variance of consumption.
-Greater clustering near price thresholds implies that households face small consumption shocks, allowing them to accurately target price thresholds and lowering estimates of $\sigma_{\epsilon}$.
-Similarly, wide variance in overall consumption is attributed to large consumption shocks, increasing estimates of $\sigma_{\eta}$.
-Identification for these parameters as well as the preference parameters also relies heavily on the distributional assumptions of normality.
-
-To recover the correlations of preference and consumption shocks between neighboring households given by $\rho_{\eta}, \rho_{\epsilon}$, this method compares the estimates of $\sigma_{\epsilon}$ and $\sigma_{\eta}$ according to the number of households using each connection.
-This approach assumes that household-level shocks are drawn from distributions with the same standard deviations --- $\sigma_{\eta}$ and $\sigma_{\epsilon}$.
+The $\sigma_{\eta}$ and $\sigma_{\epsilon}$ parameters are separately identified from the extent of consumption clustering around price thresholds relative to the overall variance of consumption.
+Greater clustering of consumption near price thresholds implies that households face small consumption shocks, allowing them to accurately target price thresholds.
+Similarly, wide variance in overall consumption is attributed to large preference shocks.
+Identification for these variance parameters relies heavily on the assumption that these parameters are normally distributed and uncorrelated with each other.
+
+%estimates of $\sigma_{\epsilon}$ and $\sigma_{\eta}$ are  according to the number of households using each connection.  
+To recover correlations of preference and consumption shocks between neighboring households given by $\rho_{\eta}, \rho_{\epsilon}$, this approach assumes that all household-level shocks are drawn from distributions with the same standard deviations --- $\sigma_{\eta}$ and $\sigma_{\epsilon}$.
 Under this assumption, any differences in estimated standard deviations for connections serving different numbers of households can be attributed to correlations in shocks between households in the same neighborhood.
-Ordering households according to the sequential game in Section~\ref{section:watersourcechoice}, let the correlation terms between the first-mover and any other households in the neighborhood, $\rho_{l,1}$, be determined in terms of the following expression where the second subscripts on the $\sigma$ terms index the number of households using a connection:
+Ordering households according to the sequential game in Section~\ref{section:watersourcechoice} and assuming small neighborhoods of only three households, let the correlation terms between the first-mover and any other households in the neighborhood, $\rho_{l,1}$, be determined in terms of the following expression where the second subscripts on the $\sigma$ terms index the number of households using a connection:
 \begin{align*}
@@
 \textbf{Sample} : The estimation uses a 10\% sample of connections from the connection survey (5,000 connections), which serves as the primary sample for the counterfactual exercises.
-This sample is combined with 2,151 connections from the leak quasi-experiment used in Section~\ref{section:hasslecostestimation}, which takes preference estimates from this step as an input.
-Together these connections produce 349,265 months of consumption observations used in the preference estimation.
-All standard errors throughout this paper are bootstrapped using \input{tables/boot_max}repetitions.
+This sample is combined with 2,151 connections from the quasi-experiment examined in the second step of the estimation (Section~\ref{section:hasslecostestimation}), which takes preference estimates from this step as an input.
+Together, these connections produce 349,265 months of consumption observations used in the preference estimation.
+All standard errors are bootstrapped using \input{tables/boot_max}repetitions.
 This sample does not include households using water from vendors since the data do not include information on consumption for these households.
 Section~\ref{section:fixedcostestimation} details the imputation procedure used to infer preferences for these households.
-Appendix~\ref{appendix:sigmanuassumptions} determines the ex-ante assumptions on $\sigma_{\epsilon}$ needed to identify the particular demand function.
+%Appendix~\ref{appendix:sigmanuassumptions} determines the ex-ante assumptions on $\sigma_{\epsilon}$ needed to identify the particular demand function.
 %The estimates are robust to varying the total and relative sample sizes of these groups.
@@
 The price sensitivity parameter, $\alpha$, exhibits some statistically significant heterogeneity across demographic measures although the magnitudes of these estimates are relatively small compared to the intercept.
-Moderately sized households have smaller price sensitivities while employment among household members tends to increase price sensitivity estimates.
-These estimates can be difficult to interpret economically since the elasticity of demand depends not only on these $\alpha$ terms, but also on variation in the fixed preferences for water across households.
+Large households have smaller price sensitivities while employment among household members and age of household head tend to increase price sensitivity estimates.
+These estimates can be difficult to interpret economically since the elasticity of demand depends not only on these $\alpha$ terms, but also on the fixed preferences for water across households.
 %Relative to living in a duplex, households in apartments and single houses exhibit greater price sensitivities with large standard errors.
@@
 \end{table}
-To interpret these estimates in economic terms, I compute the elasticity of demand with respect to price at the connection-level.
+To interpret these estimates in economic terms and to compare to similar studies, I compute the elasticity of demand with respect to price at the connection-level.
 Given a linear demand structure, the elasticity of demand depends on both the price sensitivity and fixed preferences for water.
@@
 Many previous studies estimate heterogeneity in $\gamma_C$ according to demographics alongside a single $\alpha_C$ parameter for the population (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).
-I build on these previous studies by estimating heterogeneity in both terms, which allows for a broader range of possibilities, including that larger users may be relatively more sensitive to prices than smaller users.
+This approach builds on these previous studies by estimating heterogeneity in both terms, which allows for a broader range of possibilities, including that larger users may be relatively more sensitive to prices than smaller users.
 To compare estimates with previous research under non-linear pricing schedules, this approach follows the same formula for computing elasticities by (1) taking draws of $\epsilon$ and $\eta$, (2) computing predicted demand under prices that are 1\% greater than current prices, and (3) comparing the average percentage change in demand before and after the price change.
@@
 
-Table~\ref{table:elasticity} presents demand elasticity estimates across terciles of (1) imputed income for the connection owner and (2) average monthly usage for the connection.
+Table~\ref{table:elasticity} presents connection-level demand elasticity estimates across terciles of (1) imputed income for the connection owner and (2) average monthly usage for the connection.
 Elasticities exhibit little heterogeneity across imputed income levels, but substantial variation across usage levels with larger users appearing much less sensitive to prices than smaller users.
-Since many low-income households share connections with neighbors, there is a weak correlation between income and usage-levels, which helps account for the lack of heterogeneity.\footnote{Noise in the income imputation process may also weaken any correlation between elasticity and income.}  Heterogeneity in elasticities according to monthly usage is consistent with moral hazard when households share a connection:  increasing the number of households per connection increases the water use for those connections while also exacerbating free-riding behavior.
+Since many low-income households share connections with neighbors, there is a weak correlation between income and usage-level, which helps account for the lack of heterogeneity in elasticity.\footnote{Noise in the income imputation process may also weaken any correlation between elasticity and income.}  Heterogeneity in elasticities according to monthly usage is consistent with moral hazard when households share a connection:  increasing the number of households per connection increases the water use for those connections while also exacerbating free-riding behavior.
 Different water using activities across the water demand profile may also produce this heterogeneity in elasticities.
@@
 \begin{threeparttable}
-\caption{Elasticity Estimates}\label{table:elasticity}
+\caption{Demand Elasticities for Water Connections}\label{table:elasticity}
 \input{tables/elasticity_estimates} 
@@
 This estimate is in range of the 0.98 estimate from \cite{szabo2015value} as well as similar studies in the developing world that find elasticities between 0.01 and 0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).
-
-%is its inability to match zero consumption values observed in the data.
-
+%is its inability to match zero consumption values observed in the data
 \begin{table}
@@
 \end{table}
-
 Table~\ref{table:modelperformance} compares predicted consumption from the model to observed consumption in the data.
@@
 %\end{figure}
-
 %Figure~\ref{figure:predictedwateruse} compares the predicted histogram of consumption with observed values.
@@
 
-\subsection{Hassle Cost Estimation}\label{section:hasslecostestimation}
-
-Exogenous interruptions in water connections caused by leaks are combined with billing records to provide a measure of the marginal costs of sharing water.
-The estimation strategy compares a connection's demand before disconnection to the change in demand among neighboring connections after disconnection (as a result of sharing), identifying the hassle cost, $H$, from the extent to which neighbors may not fully offset their consumption onto their neighbors.
-Baseline preference parameters for both disconnecting connections and their neighbors are estimated in the procedure from Section~\ref{section:preferenceestimation}.
+\subsection{Estimating the Marginal Cost of Sharing}\label{section:hasslecostestimation}
+
+To measure the marginal costs of sharing water, this strategy examines how much demand changes when households use their own connection versus when they use from a neighbor's connection.
+In order to observe the same connection using from both sources, I focus on sudden pipe leaks that often force households to disconnect and use from their neighbors.
+Specifically, I compare a connection's usage before disconnecting (due to a leak) to the change in usage among neighboring connections after disconnection, identifying the marginal hassle cost from the extent to which a connection may not fully offset its usage by sharing with neighboring connections.
+
+%Baseline preference parameters for both disconnecting connections and their neighbors are estimated in the procedure from Section~\ref{section:preferenceestimation}.
 Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $H$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).
-
-Leveraging this variation requires identifying a sample of leaking connections, the timing of leaks/disconnection, and usage for neighboring connections.
-In 36 months, the water provider received 106,171 consumer complaints of excessive billing --- 34,927 of which can be precisely identified as underground pipe leaks along the service pipe through a text analysis of call transcripts.
+Leveraging substitution due to pipe leaks requires identifying a sample of leaking connections, the timing of leaks/disconnection, and usage for neighboring connections.
+Over 36 months, the water provider received 106,171 consumer complaints of excessive billing --- 34,927 of which can be precisely identified as underground pipe leaks along the service pipe through a text analysis of call transcripts.
 These complaints do not appear to be spatially correlated with only a handful of leaks occurring among direct neighbors.
-This approach considers any call identified as an excessive billing complaint as a leak.
-While some calls may not explicitly refer to leaks, in all cases these calls refer to billing errors, meter malfunctions, or other surprise events that may drive disconnection.
+This approach considers any call identified as an excessive billing complaint as a possible leak.
 Instances where leaks in main water pipes reduce access for entire neighborhoods at a time are coded separately and excluded from the sample.
@@
 Disconnection is defined as having 0 or missing consumption values for at least 90\% of the year following the leak date.
-Neighboring connections that connect after the leak are dropped since these connections lack the pre-period needed to estimate their fixed preferences for water.
-The estimation includes observations within a year and a half of the leak event to avoid bias from possible reconnection of these households as well as changes in the composition of neighboring households.
-Since many of these households are not included in the connection survey, demographic characteristics as well as sharing behavior are imputed using averages from small areas surrounding these connections; this process introduces additional noise into the estimation.
+Neighboring connections that connect after the leak are dropped since these connections lack the pre-period observations needed to estimate their fixed preferences for water.
+The estimation includes observations within a year and a half of the leak event to avoid bias from any possible reconnections as well as changes in the composition of neighboring households over time.
+Since many of these households are not included in the connection survey, demographic characteristics as well as sharing behavior are imputed using averages from small areas surrounding these connections.
+This imputation introduces noise in the estimation of price sensitivities for these households.
+%While some calls may not explicitly refer to leaks, in all cases these calls refer to billing errors, meter malfunctions, or other surprise events that may drive disconnection.
 
 To determine which neighbors to include, Appendix~\ref{appendix:sharingneighbor} ranks nearby households according to their distance from the leak and examines how the responsiveness of neighbors' consumption levels after a leak dissipates with distance.
-Results indicate substitution is concentrated among the nearest four neighbors.
+Results indicate that substitution is concentrated among the nearest four neighbors.
 Given these findings, the empirical exercise defines neighbors as the four closest connections.
-
 %\footnote{Neighbors ranked 6 through 8 are grouped together since there are very few of them in the radius.}
@@
 Importantly, this distance measure does not account for the physical distances between sharing partners or unconnected households.
-These omissions mean that the primary distance measure is likely to overestimate the true distance between all neighbors.
-Furthermore, areas with smaller physical distances are likely to increase incentives to share as well as the observed distance between meters, which may bias the effect of distance towards zero.
+These omissions mean that this average distance measure is likely to overestimate the true distance between all neighbors.
+Furthermore, areas with smaller physical distances are likely to increase incentives to share as well as the observed distance between meters, which may bias the effect of distance on marginal sharing costs towards zero.
 Table~\ref{table:descriptivesestsample} in Appendix~\ref{appendix:descriptivesest} includes descriptive statistics for these two measures.
-
-One additional concern would be that households select into sharing relationships conditional on unobserved heterogeneity in sharing costs, which is not modeled here.
+One additional concern would be that households select into sharing relationships conditional on some unobserved heterogeneity in sharing costs, which is not modeled here.
 Since households included in this quasi-experiment have selected into purchasing connections at baseline, they may face higher hassle costs compared to households that select into sharing.
@@
 Therefore, this exercise provides an upper-bound on hassle costs for the population.
-
 %The mobile survey finds a range of sharing access from fetching with containers to using the same plumbing, which suggests that households face different hassle costs.
@@
 
-With only 548 connections that experience leaks, the estimation recovers wide standard errors for all three parameters.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  Taken together, these results suggest that the time-costs or other physical challenges associated with informally transporting water may play an important role in the extent to which households choose to use water from a neighbor's tap.
+With only 548 connections that experience leaks, the estimation recovers wide standard errors for all three parameters.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  With this in mind, Section~\ref{section:tptsharingcosts} repeats counterfactual policy simulations for varying levels of the hassle cost.
+Taken together, these results suggest that the time-costs or other physical challenges associated with informally transporting water may play an important role in the extent to which households choose to use water from a neighbor's connection.
 
@@
 
-Unobserved fixed costs of owning a connection are recovered from cross-sectional variation in water source choices.
-The third step of the estimation uses the preference parameters recovered in Section~\ref{section:preferenceestimation} and hassle cost estimates from Section~\ref{section:hasslecostestimation} to simulate the initial water source choices for households.
-By matching observed with predicted source choices, the estimation recovers the fixed costs of using a connection as well as prices associated with fetching from a vendor.
-The fixed costs capture both one-time costs put into monthly terms --- connection fees, permitting with local governments, etc.
---- as well as monthly costs --- service fees, plumbing maintenance, etc.
-
-The fixed cost estimation sample includes the random sample of 5,000 connections from the preference estimation.\footnote{This sample excludes connections used to estimate hassle costs since the majority of these connections use imputed demographics.}  I merge the estimation sample with the subsample of households using water from small-scale vendors drawn from the Census of Population and Housing 2010 as described in Section~\ref{section:data}.
+By matching observed water source choices with predicted source choices (given preference parameters from Section~\ref{section:preferenceestimation} and hassle cost estimates from Section~\ref{section:hasslecostestimation}), this step recovers the fixed costs of using a connection as well as prices associated with fetching from a vendor.
+These fixed costs capture both monthly costs --- service fees, plumbing maintenance, etc.
+--- as well as one-time costs put into monthly terms --- connection fees, permitting with local governments, etc.
+
+The fixed cost estimation sample includes the random sample of 5,000 connections from the preference estimation.\footnote{This sample excludes connections used to estimate marginal sharing costs since the majority of these connections use imputed demographics.}  This sample is merged with a subsample of households using water from small-scale vendors drawn from the Census of Population and Housing 2010 as described in Section~\ref{section:data}.
 Neighborhoods of potential sharing partners are limited to groups of three households, which is consistent with the vast majority of households forming sharing relationships of three households or less.
@@
 
-\subsubsection{Disaggregating Connection-Level Preferences to Household-Level Preferences}\label{section:disaggregation}
-
-Simulating these choices requires recovering household-level preferences from the connection-level preferences estimated in Section~\ref{section:preferenceestimation}.
-Household-level price sensitivity, $\alpha_i$, can be inferred as a linear function of the vector of demographics specific to each household, $Z_i$, and estimates of $\alpha_C$.
+\subsubsection{Disaggregating Connection Preferences to Household Preferences}\label{section:disaggregation}
+
+Simulating water sources choices requires recovering household preferences from the connection preferences estimated in Section~\ref{section:preferenceestimation}.
+Household price sensitivity, $\alpha_i$, can be inferred as a linear function of the vector of demographics specific to each household, $Z_i$, and estimates of $\alpha_C$.
 Since fixed preferences $\hat{\gamma_C}$ are estimated non-parametrically at the connection-level, I specify a parametric method of splitting $\hat{\gamma_C}$ into $\gamma_i$ for all households using demographics, $Z_i$:
@@
 \hat{\gamma_C}  		   		& =  \sum_{i=1}^{S} ( \gamma_i - \alpha_i H_{i} ) \\
-\big [ \hat{\gamma_C} - \sum_{i=1}^{S}  \alpha_i H_{i} \big ]		& =  \sum_{i=1}^{S}  (\lambda_{S} Z_i + \mu_{i})  
+\hat{\gamma_C} + \sum_{i=1}^{S}  \alpha_i H_{i}		& =  \sum_{i=1}^{S}  (\lambda_{S} Z_i + \mu_{i})  
 \end{align*}
@@
 $\lambda_{S}$ are coefficients measuring the effect of these demographics on fixed preferences $\gamma_C$.
-These coefficients are allowed to differ across connections serving different numbers of households, $S$ as well as whether household $i$ is an owner of the connection.
+These coefficients are allowed to differ across connections serving different numbers of households as well as whether household $i$ is the owner of the connection.
 $\mu_{i}$ captures any residual variation that is unexplained by demographics.
-In this case, $Z_i$ consists of household size since it is the only demographic measure reported separately for connection owners and other users.
-This approach estimates a simple regression to recover estimates of $\lambda_{S}$, which provides predicted levels of $\gamma_i$ for each household.
-Finally, this method needs to allocate any residual variation in preferences $\mu_{i}$ across the households.
-Instead of either allocating $\mu_i$ entirely to the connection owner or splitting $\mu_{i}$ evenly across households, this method allocates $M \mu_{i}$ to the owner and $\frac{(1-M)}{S-1} \mu_{i}$ to neighboring users where $M$ is the ratio of average connection-level preferences for single users, $\gamma_{S=1}$ to average connection-level preferences for shared connections $\gamma_{S>1}$.
-This approach nests the assumption that connection owners are more likely than their sharing partners to resemble the water demand of single-users.
+In this case, $Z_i$ only consists of household size since it is the single demographic measure reported separately for connection owners and other users.
+A linear regression recovers $\lambda_{S}$, which provides predicted levels of $\gamma_i$ for each household.
+
+Finally, any residual variation in preferences $\mu_{i}$ needs to be allocated across owning and sharing households.
+Instead of either allocating $\mu_i$ entirely to the owner or splitting $\mu_{i}$ evenly across households, this approach allocates $M \times \mu_{i}$ to the owner and $\frac{(1-M)}{S-1} \times \mu_{i}$ to neighboring users where $M$ is the ratio of average fixed preferences for single users to shared connections.
+This approach nests the assumption that connection owners are more likely to resemble individually connected households than their sharing partners.
 Another limitation is that the data only provide the total number of people using a connection for shared connections.
-Therefore, in cases where three households use a connection, this approach assumes that people are allocated evenly between the two sharing households.
+Therefore, in cases where three households use a connection, people are assumed to allocated evenly between the two sharing households.
 %%% , which is consistent with the discussion in Section~\ref{section:watersourcechoice}
@@
 
-Given the full set of household-level demand parameters for connected households, I then impute preferences for households using from vendors.
-$\alpha_i$ can be computed simply from demographic measures, $Z_i$, for these households.
-Since $\gamma_i$ is estimated non-parametrically for connected households, I use a regression with location, demographic variables, and their full set of interactions to impute preferences for households using from vendors:
-\begin{align*}
-\gamma_i = \beta_0 Z_i + \beta_1 L_i + \beta_2 Z_i L_i + \zeta_i
-\end{align*}
-$Z_i$ contains demographics while $L_i$ includes dummy variables for small census areas.
-After recovering coefficients for the sample of connected households, I then compute predicted $\gamma_i$ for households using water from vendors.
-This method requires the assumption that unobserved variation in preferences $\zeta_i$ is uncorrelated between connected households and households using from vendors.
+Given the full set of household-level demand parameters for connected households, preferences are then estimated for households using from vendors.
+Projected $\alpha_i$ can be computed from demographic measures $Z_i$ multiplied by the estimated price sensitivities, $\alpha$.
+Since $\gamma_i$ is estimated non-parametrically for connected households, fixed preferences need to be imputed for unconnected households.
+Fixed preferences for connected households are regressed on census ward indicators, the full set of demographic indicators used in the demand estimation (Section~\ref{section:preferenceestimation}), and their full set of interactions.
+After recovering coefficients for the sample of connected households, predicted fixed preferences can be computed for households using water from vendors.
+This method requires the assumption any that unobserved variation in preferences is uncorrelated between connected households and households using from vendors.
 This assumption may not hold if unobservable aspects of preferences drive some households to use from vendors.
-Since vendors offer high marginal prices, this form of selection would likely lead the method to overestimate demand among households using from vendors.
+Since vendors offer high marginal prices possibly attracting households with unobservably low demand, this form of selection may lead this method to overestimate demand among households using from vendors.
 Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from 5,000 connections to \input{tables/totalhhsmm_group}households.
@@
 
-%Grouping households into sets of three produces some remainder households that I remove from the sample bringing the total number of households to \input{tables/totalhhsmm_group}.
-
+%Grouping households into sets of three produces some remainder households that I remove from the sample bringing the total number of households to \input{tables/totalhhsmm_group}.-
 With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors within each of the 599 wards.
@@
 One limitation of the model is that the linear demand structure with normal error terms also predicts occasional negative consumption values.
-Those values are rounded to zero for calculating household utility.
+Those values are rounded to zero in calculating household utility.
 %\footnote{ Future versions will not condition on observed choices in this way, and instead sample households across sharing relationships. }
@@
 The moments used in the estimation include the shares of households choosing different sources --- using an individual connection, using water from a neighbor, and using from a vendor --- as well as the correlation between each of these source choices and the fixed preference parameters for each household, $\gamma_i$.
-The estimation places heavier weight on matching the source-choice moments over the correlation moments because these correlations rely on possibly noisy measures of the preference parameters both due to incidental parameter issues in estimation as well as imputation for households using vended water.
+The estimation is designed to place heavier weight on matching the source-choice moments over the correlation moments because these correlations rely on possibly noisy measures of the preference parameters both due to incidental parameter issues in estimation as well as imputation for households using vended water.
 % Future versions will re-weight these moments given the boot-strapped variance-covariance matrix.
@@
 This finding suggests that households face sizable barriers to connecting to the water network such as land tenure insecurity or administrative costs.
-This total fixed fee is also comparable to the total variable price (tariff $\times$ volume) paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.
+This total fixed fee is also comparable to the total monthly water bill (tariff $\times$ volume) paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.
 
 The estimates also reveal a fixed cost for vendors equivalent to \input{tables/vendorfixedfee_group}PhP per month.
-This likely captures fixed quality differences between vended water and other water sources.
+This cost likely captures fixed quality differences between vended water and other water sources.
 The mean price for vended water of \input{tables/vendorprice_group}PhP per cubic meter is close to the highest tariff prices in Figure~\ref{figure:tariff}.
@@
 These sources may also be unevenly distributed throughout the city.
-
-Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option, particularly the marginal price, $p_v$.
+Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option.
 As a simple out-of-sample test, Appendix~\ref{appendix:vendorpriceestimates} finds that the estimate of $p_v$ in Table~\ref{table:smmestimates} matches closely with the implied $p_v$ from data on total water expenditures for vendor households using additional census data from part of Manila.
@@
 Also, Appendix~\ref{appendix:modelfit} compares the predicted moments to the observe moments used in the estimation.
-While source moments are matched exactly by design, the estimation is able to approximate the size and direction of the correlation of fixed preference with proportion connected individually and proportion using from a neighbor.
-
+While source moments are matched exactly by design, the estimation is able to roughly match the size and direction of the correlations of fixed preferences with the proportion connected individually and the proportion using from a neighbor.
 %Assuming that the vendor expenditures only reflect the marginal prices paid for water (excluding the fixed cost), I can express average expenditures, $E_v$, by multiplying average vendor demand by the vendor price, $E_v = (\gamma - \alpha p_v) p_v$.
@@
 
-\section{Counterfactual Exercises}\label{section:counterfactualexercises}
+\section{Counterfactual Policies}\label{section:counterfactualexercises}
 
@@
 Consumer welfare is defined as the expected sum of all households' utilities subject to welfare weights, $\delta_i$, for different subpopulations, which capture any preferences the regulator may have towards redistribution.
-The counterfactual exercises consider two sets of these preferences: (1) the regulator weights all utilities equally and (2) the regulator only considers utility for the bottom 50th percentile of water demand, summarized by the fixed water preferences $\gamma$ for each household.
-Giving preference to low-demand households intends to capture dual policy goals of ensuring access as well as minimum monthly usage for all households.
+The counterfactual exercises consider two sets of these preferences: (1) the regulator weights all households equally and (2) the regulator only gives positive weight to households from the bottom 50th percentile of water demand, summarized by the fixed water preference $\gamma$ for each household.
+Giving preference to low-demand households intends to capture dual policy goals of ensuring access as well as minimum monthly usage levels.
 Since low-demand households are also often low-income households, this approach also provides a proxy for standard preferences toward redistribution.\footnote{Using income directly is less informative due to noise in the imputation process, especially for households that are sharing with their neighbors.}  Similarly, this approach may capture efficiency gains if connecting low-users produces positive health externalities (\cite{galiani2005water,gamper2010impact}).
@@
 \begin{split}
-max_{Fee,p_{L},p_{H}} &\hspace{.4cm} E\text{\LARGE [} \sum_{i=1}^{N} \delta_i U_{i}(Fee,p_{L},p_{H}) \text{\LARGE ]} \\
+max_{Fee,p_{L},p_{H}} &\hspace{.4cm} E\text{\LARGE [} \sum_{i} \delta_i U_{i}(Fee,p_{L},p_{H}) \text{\LARGE ]} \\
 s.t. \hspace{.5cm} & \text{Total Connections} \times \big[ Fee - \text{Installation/Service Costs} \big] + \\
@@
 Capital costs include maintaining the pipes, pumping stations, and billing infrastructure.
-This calculation provides a close approximation to the Capital Expenditures regulatory structure implemented in this context, which exactly compensates the water provider for its costs through increases in the tariff.\footnote{This approach abstracts away from any principal agent problems between the company and the regulator by assuming that the regulator has perfect information over the firm's capital investments and operating costs (\cite{laffont1993theory}).}  This regulatory problem forms the basis for evaluating the following counterfactual policies.
+This calculation provides a close approximation to the capital-expenditures regulatory structure implemented in this context, which exactly compensates the water provider for its costs through increases in the tariff.\footnote{This approach abstracts away from any principal agent problems between the company and the regulator by assuming that the regulator has perfect information over the firm's capital investments and operating costs (\cite{laffont1993theory}).}  This regulatory problem forms the basis for evaluating the following counterfactual policies.
 All counterfactual policies evaluated below hold firm profits equal to zero.
@@
 
-I first examine a counterfactual policy where the regulator discounts the upfront fee while increasing the tariff to remain revenue neutral.
-By discounting the fixed fee by \input{tables/c_fee_discount_group}PhP, this approach mimics the policy implemented by the water provider; however, while the provider's discount decreased overall revenue, this approach includes the necessary tariff increase to fund the lower fixed fee.
-This counterfactual also echoes recent recommendations from policymakers and researchers including the World Bank who have strongly advocated for lower connection fees as a way of extending access to piped water among the poor (\cite{wsup,komives2005water,jimenez2014factors,kayaga2007costs,mcintosh2003asian}).
-Figure~\ref{figure:discounttariff} provides the current tariff and the compensated tariff, which is shifted upwards by \input{tables/discount_tariff_rise_group}PhP/m3 to maintain revenue neutrality.
+First consider a counterfactual policy where the regulator discounts the fixed fee while increasing the tariff to remain revenue neutral.
+By discounting the fixed fee by \input{tables/c_fee_discount_group}PhP, this approach mimics a policy implemented by the water provider; however, while the provider's discount decreased overall revenue, this approach offsets the discount with higher tariffs.\footnote{Appendix~\ref{section:oostest} analyzes the discount implemented by the provider as an out-of-sample test for the model, matching substitution patterns between water sources induced by the policy change.}  This counterfactual also echoes recent recommendations from policymakers and researchers including the World Bank who have advocated for lower connection fees as a way of extending access to piped water among the poor (WSUP [2013], \cite{komives2005water,jimenez2014factors,kayaga2007costs,mcintosh2003asian}).
+Figure~\ref{figure:discounttariff} provides the current tariff and the compensated tariff, which is shifted upwards by \input{tables/discount_tariff_rise_group}PhP/m3 for each tariff block to maintain revenue neutrality.
 
@@
 \centering
-\caption{Tariff Shift from Connection Fee Discount}\label{figure:discounttariff}
+\caption{Revenue-Neutral Tariffs \\ Pre/Post Connection Fee Discount}\label{figure:discounttariff}
 \includegraphics[scale=.7]{tables/discount_tariff_groups.pdf}
@@
 
-Table~\ref{table:fixedfeediscount} summarizes the impacts of this change on source choices and consumer welfare measured in terms of the difference between current utility and utility from using the outside vendor option as in Section~\ref{section:oostest}.
-While the increase in the tariff drives large users to substitute toward vendor options, the decrease in the fixed price allows some small users to join together and purchase shared connections, resulting in no change in the share of households using from a neighbor.
-The third row indicates even greater substitution toward water vendors of around \input{tables/discount_vendor_change_group}percentage points in response to the higher tariff.
+Table~\ref{table:fixedfeediscount} summarizes the impacts of this change on source choices and consumer welfare, which is measured in terms of utility relative to using from a water vendor.
+While the increase in the tariff drives large users to disconnect and substitute toward vendors, the decrease in the fixed price allows some small users to jointly purchase shared connections, resulting in no change in the proportion of households using from a neighbor.
+The second row indicates substitution toward water vendors of around \input{tables/discount_vendor_change_group}percentage points in response to the higher tariff.
 These effects combine to reduce average consumer surplus by \input{tables/discount_avg_surplus_change_group}PhP per month, which is over half of the initial fixed fee discount of \input{tables/c_fee_discount_group}PhP.
@@
 Households in the bottom \input{tables/group_percentile_group}\unskip th percentile of water users also experience lower consumer surplus although the magnitude is much less, amounting to \input{tables/discount_low_welfare_change_group}percent of monthly household income.
-Taken together, these results suggest that connection fee discount policies in this context can have unintended distributional consequences by reducing both access to piped water and welfare for the intended beneficiaries.
+Taken together, these results suggest that connection fee discount policies in this context can have unintended distributional consequences by reducing both access to piped water and even welfare for the intended beneficiaries.
 %\footnote{Consumer surplus is measured relative to utility from using vended water.}
@@
 
-This section considers the welfare impacts of six tariff structures in order to inform water regulators who face a variety of institutional settings and redistributional priorities: while some regulators may be restricted to simple two-part tariffs, others can allow for complex, non-linear price schedules as in Manila (\cite{hoque2013state}).
-Similarly, while encouraging efficient use, many developing countries also include distributional motivations for their tariff structures such as ensuring all households reach a certain minimum level of usage (\cite{szabo2015value}).
-
-As a benchmark, this exercise first examines a First-Best tariff informed by the industrial organization literature where (1) the marginal price per unit of water equals the marginal cost of production, (2) every household pays a fixed fee just equal to costs of installing and maintaining a connection, and (3) the regulator is able to perfectly price discriminate according to household demand, extracting additional transfers from households to exactly fund the fixed capital costs (\cite{auerbach1978two,oi1971disneyland}).
-Without sharing, this tariff follows economic theory to maximize efficiency.
-I then compare how the current tariff in Manila performs relative to this First-Best tariff structure.
+This section considers the welfare impacts of six tariff structures in order to inform regulators facing a variety of institutional settings and redistributional priorities: while some regulators may be restricted to imposing simple two-part tariffs, others may allow for complex, non-linear price schedules like the current tariff in Manila (\cite{hoque2013state}).
+While encouraging efficient use, many developing countries also include distributional motivations for their tariff structures such as ensuring that most households reach a minimum level of usage (\cite{szabo2015value}).
+
+As a benchmark, this exercise examines a first-best tariff where (1) the marginal price equals the marginal cost, (2) every household pays a fixed fee equal to the fixed costs of installing and maintaining a connection, and (3) the regulator is able to perfectly price discriminate according to household demand, extracting additional transfers from high-demand households to exactly fund the fixed capital costs.
+According to standard industrial organization theory, this tariff is designed to perfectly maximize welfare in a world without sharing (\cite{auerbach1978two,oi1971disneyland}).
+I then compare how the current tariff in Manila performs relative to this first-best tariff structure.
 %Additionally in this case, I assume that the regulator can use these costless transfers to reallocate surplus from high users to low users in order to achieve distributional goals as well.
 
-The next tariff imposes restrictions on the regulator by only allowing for a simple two-part tariff with a monthly fixed component and a single variable component.
-First, I look for the two-part tariff that maximizes overall consumer surplus.
-Second, I define a social two-part tariff, which maximizes surplus for low users and provides a means of summarizing regulator preferences toward redistribution or ensuring basic levels of access.
-Low users are classified as households with fixed preferences for water usage, $\gamma$, below the average level.
-Since households exhibit little heterogeneity in their price sensitivities, $\alpha$, this approach provides a simple method to summarize water demand across the population.
+The next tariff imposes restrictions on the regulator by only allowing for a simple two-part tariff --- Part (1) a monthly fixed fee and; Part (2) a marginal price.
+First, I identify the two-part tariff that maximizes overall consumer surplus.
+Second, I define a social two-part tariff that maximizes surplus only for low users, capturing regulator preferences toward redistribution and ensuring basic levels of access.
+Low users are defined as households with fixed preferences for water usage, $\gamma$, below the average level.
+Since households exhibit little heterogeneity in their price sensitivities, this approach provides a simple way of summarizing water demand across the population.
 %An alternative approach may be to examine welfare impacts by household incomes; however, the data only allow for noisy imputations of income, which may mask larger distributional effects.
@@
 
-Finally, I calculate optimal three-part tariffs, which include a fixed fee and separate marginal prices for consumption below and above a 20 cubic meter threshold.
-This structure more closely mirrors the current tariff implemented in Manila.\footnote{I calculate optimal tariffs for a 5\% subset of the sample since non-linear budget constraints make this process computationally expensive.
+Finally, this exercise calculates optimal three-part tariffs --- Part (1) a monthly fixed fee; Part (2) a marginal price for any usage below 20 m3 per month, and; Part (3) a marginal price for any usage above 20 m3 per month.
+This structure more closely mirrors the current tariff implemented in Manila.
+Optimal three-part tariffs are computed both to maximize surplus overall and to maximize surplus only for low-demand households.\footnote{I calculate optimal tariffs for a 5\% subset of the sample since non-linear budget constraints make this process computationally expensive.
 Preliminary tests suggest that the results are robust to this sampling technique.}
 
+Does the presence of informal water sharing affect optimal prices in this context?
+To test this hypothesis, I compare optimal tariffs in a counterfactual setting where sharing is prohibitively expensive (Section~\ref{section:optimaltariffswithoutsharing}) to optimal tariffs in the current setting in Manila (Section~\ref{section:optimaltariffswithsharing}).
+
 \subsubsection{Optimal Tariffs Without Sharing}\label{section:optimaltariffswithoutsharing}
 
-This section computes optimal tariffs when sharing is prohibitively expensive.
-This counterfactual setting without sharing allows me to (1) verify optimal tariff designs from the economics literature without sharing and (2) examine the extent to which these tariff designs resemble current pricing policies in Manila.
-When households are unable to share, the provider raises less revenue at the current tariff.
-Therefore, I recalculate a lower level of capital costs according to revenue generated by imposing the current tariff without sharing.
-This procedure allows for direct welfare comparisons between the current tariff and counterfactual tariffs; however, because of this procedure, the magnitudes of the results in this section are not directly comparable to counterfactuals with sharing in Section~\ref{section:optimaltariffswithsharing}.
-
-Figure~\ref{figure:optimaltariffnosharing} provides the optimal tariffs without sharing, and Table~\ref{table:optimaltariffnosharing} includes the corresponding monthly fixed fees as well as the impacts of these tariff structures on the share of households using vendors and using neighboring connections.
+Identifying optimal tariffs without sharing requires an additional assumption about the costs to the water provider in this counterfactual setting.
+When households are unable to share, the provider raises less revenue at current prices.
+To account for this lost revenue, capital costs are recalculated to match the revenue raised from implementing the current tariff when sharing is not possible.
+This procedure allows for direct welfare comparisons between the current tariff and counterfactual tariffs; however, the magnitudes of these results are not directly comparable to counterfactuals with sharing explored later in Section~\ref{section:optimaltariffswithsharing}.
+
+Figure~\ref{figure:optimaltariffnosharing} provides the optimal tariffs without sharing, and Table~\ref{table:optimaltariffnosharing} includes the corresponding optimal monthly fixed fees as well as the impacts of these tariff structures on the share of households using vendors and using neighboring connections.
 The last two rows include consumer surplus measures for the average household as well as the bottom 50\% of users.
@@
 \end{figure}
-
-The First-Best tariff schedule produces the highest level of consumer surplus reaching \input{tables/first_best_surplus_group}PhP/month or \input{tables/first_best_surplus_percent_income_group}\unskip\% of household income.
-This tariff also produces the minimum share of households using vended water at \input{tables/first_best_percent_vendor_group}\unskip\%.
-With costless transfers, the regulator could theoretically reallocate all surplus to the lowest users providing an upper bound on redistribution through pricing at almost double the average surplus.
 
@@
 }	\\
-\footnotesize{$\text{ }^{*}$ The First-Best fee does not include individual transfers imposed by the regulator.
-\\  Social tariffs place all welfare weight on the bottom 50\% of water users.
-All terms are monthly.}
-\end{table}
-
-Relative to the First-Best, implementing the current tariff in this context without sharing reduces average surplus dramatically and increases the share of households using vended water by raising the average marginal price.
-The optimal two-part tariff in column three features a higher fixed fee affording a lower marginal price at all consumption levels.
-Compared to the current tariff, the optimal two-part tariff brings consumer surplus up to \input{tables/tpt_surplus_improvement_group}\unskip\% of the First-Best surplus.
-These welfare gains are primarily driven by increased consumption for large users since surplus for low-users is cut in half and the share of households connected to the network declines substantially.
-
-The optimal social tariff in column four attempts to offset these welfare losses for low users by reducing the fixed fee just below zero and doubling the marginal price.
-The low fees incentivize small users to connect to the network, reducing the share using from vendors to the First-Best levels.
+\footnotesize{The first-best fee does not include individual transfers imposed by the regulator. \\  Social tariffs place all welfare weight on the bottom 50\% of water users. All terms are monthly.}
+\end{table}
+
+The first-best tariff schedule produces the highest level of consumer surplus reaching \input{tables/first_best_surplus_group}PhP/month or \input{tables/first_best_surplus_percent_income_group}\unskip\% of household income.
+This tariff also produces the minimum share of households using vended water at \input{tables/first_best_percent_vendor_group}\unskip\%.
+With costless transfers, the regulator could theoretically reallocate all surplus to the lowest users providing an upper bound on redistribution through pricing at one and a half times the average surplus.
+
+Relative to the first-best, implementing the current tariff without sharing reduces average surplus dramatically and increases the share of households using vended water by raising the average marginal price.
+The optimal two-part tariff (third column) features a higher fixed fee which affords a lower marginal price at all consumption levels.
+Compared to the current tariff, the optimal two-part tariff brings consumer surplus up to \input{tables/tpt_surplus_improvement_group}\unskip\% of the first-best average surplus.
+These welfare gains are primarily driven by increased consumption for large users since surplus for low-users is cut in half and the share of households using from vendors increases by 8 percentage points.
+
+The optimal social tariff (fourth column) maximizes surplus for households with below average demand.
+This social tariff improves welfare for low-users by reducing the fixed fee dramatically and almost doubling the marginal price.
+Low fixed fees incentivize small users to connect to the network, reducing the share of households using from vendors by around 14 percentage points.
 Average surplus declines since high marginal prices reduce consumption for large users; however, surplus for low users more than doubles.
@@
 
-By adding an extra segment to the tariff schedule, the fifth column tests the extent to which more complex linear tariffs can improve efficiency.
+By adding an extra segment to the tariff schedule, the optimal three-part tariff (fifth column) tests the extent to which more complex pricing schedules can improve efficiency.
 Figure~\ref{figure:optimaltariffnosharing} graphs this three-part tariff relative to the current tariff.
-The shape of the optimal three-part tariff resembles the current tariff with a low first segment followed by a higher second segment (although the optimal three-part tariff maximizes total surplus while the current tariff is motivated by distributional concerns).
-The intuition for this finding is that a low first price segment combined with a high fixed fee provides an additional mechanism for the regulator to price discriminate on the extensive margin; under this pricing regime, only relatively large users connect and their high usage allows the regulator to further lower prices (since the marginal price well exceeds marginal cost).
-Despite this attempt to improve welfare, surplus changes are negligible.
-
-The social three-part tariff in column six has slightly more success in redistributing surplus by using an additional tariff block extract greater revenue from large users and improve reallocation to low users.
+The shape of the optimal three-part tariff resembles the current tariff structure with a low first segment followed by a higher second segment (although the optimal three-part tariff maximizes total surplus while the current tariff is likely motivated by distributional concerns).
+The intuition for this finding is that a low first price segment combined with a high fixed fee provides an additional mechanism for the regulator to price discriminate on the extensive margin; under this pricing regime, only relatively large users connect and their high usage levels allow the regulator to further lower prices (since the marginal price well exceeds marginal cost).
+Despite this attempt to improve welfare, surplus improvements are negligible relative to the optimal two-part tariff.
+
+%%%% FIX THIS DISCUSSION HERE !!! %%%%
+Compared to the social two-part tariff, the social three-part tariff (sixth column) uses a higher fixed fee to achieve a slightly lower marginal price for water usage up to 20 m3.
+The higher fixed fee drives another 2\% of households to use from vendors; however, the lower marginal price benefits low-users who remain connected.
+Relative to the social two-part tariff, the social three-part tariff achieves a surplus gain of over 8 PhP/month for low-users while lowering average surplus by around 25 PhP/month.
+
+% has more success in redistributing surplus by using an additional tariff block to extract greater revenue from large users and improve reallocation to low users.
 Relative to the social two-part tariff, the social three-part tariff achieves this goal by offsetting a lower first price segment with a higher second price segment.
 
+These results provide empirical support for the widespread practice of using non-linear pricing schedules to achieve goals of redistribution (\cite{hoque2013state}).
+When sharing is prohibitively expensive, non-linear pricing is able to over double surplus for the bottom half of water users (relative to optimal pricing that weights all users equally).
+
+%With a lower fixed fee and increasing marginal price schedule, the social three-part tariff is the counterfactual tariff that most closely resembles the shape of the current tariff in Manila.
+
 \subsubsection{Optimal Tariffs With Sharing}\label{section:optimaltariffswithsharing}
-
-This section calculates the optimal tariff structure in the current environment in Manila (when sharing is possible subject to the estimated hassle costs).
-Figure~\ref{figure:optimaltariffsharing} plots the marginal prices associated with each counterfactual tariff.
-Table~\ref{table:optimaltariffsharing} computes the impacts of these tariffs on source choices as well as welfare.
-Comparing columns two and three of Table~\ref{table:optimaltariffsharing}, I find large welfare improvements on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income from shifting from the current tariff schedule to an optimal two-part tariff schedule.
-These gains are mainly enjoyed by large users benefiting from a lower marginal price relative to the current tariff.
-At the same time, flattening the tariff greatly reduces the implicit ``tax'' on shared connections, allowing small demand households to also benefit from lower marginal prices through their neighbors' connections.
-These lower marginal prices almost compensate for the higher hassle and free-rider costs facing low-demand households, leaving surplus for these households unchanged.
-%zooming in on tariffs below 20 PhP/$\text{m}^{3}$ in order to highlight distinctions between the two-part and three-part tariffs.
-
-The optimal fixed fee lies below the current fixed fee, which is priced at the cost of installing and maintaining a connection.
-Since households incur hassle costs and free-rider distortions from splitting the bill in sharing connections, pricing below cost allows the regulator to encourage households to substitute away from shared connections toward individual connections and avoid these hassle costs at the margin.
-By subsidizing individual connections, the two-part tariff in column three performs very close to the First-Best tariff in terms of average consumer surplus.
-
- Moving to a social two-part tariff in column four, I find that maximizing welfare for low users counterintuitively involves increasing the fixed fee in order to subsidize a very low marginal price.
-This tariff maximizes the share of households using from neighbors while also driving a significant share of households toward water vendors.
-Since low-users are able to split the fixed fee with their sharing partner, they can enjoy greater consumption at the low marginal price.
-Despite this relatively extreme pricing schedule, surplus for low users only increases by \input{tables/tpt_social_surplus_change_low_sharing_group}PhP/month while average surplus declines by \input{tables/tpt_social_surplus_change_avg_sharing_group}PhP/month.
-While manipulating the two-part tariff proved to be an effective redistributive strategy without sharing in Section~\ref{section:optimaltariffswithoutsharing}, this finding suggests that informal sharing networks act to constrain the effectiveness of non-linear pricing in redistributing surplus.
 
@@
 
-An optimal three-part tariff with sharing in column five follows the same pattern as in the case without sharing: moving to an increasing tariff structure selects for high-usage connections, which provide greater revenue to cover the fixed costs.
-As before, this tariff produces negligible changes in welfare.
-Figure~\ref{figure:optimaltariffsharing} indicates an optimal three-part tariff with an almost zero first price segment followed by a much higher second price segment, which again broadly aligns with the current tariff structure.
-This tariff structure supports the ``life-line'' tariff as a way of efficiently maximizing surplus (rather than achieving distributional goals).
-Column six (along with Figure~\ref{figure:optimaltariffsharing}) finds no difference in the optimal social two and three part tariffs.
-This result points to the extent to which sharing networks constrain the ability of cities to achieve redistribution through complex, non-linear pricing strategies.
-
 \begin{table}[!hbp]
@@
 }
-\footnotesize{$\text{ }^{*}$ The First-Best fee does not include individual transfers imposed by the regulator.
+\footnotesize{The first-best fee does not include individual transfers imposed by the regulator.
 \\  Social tariffs place all welfare weight on the bottom 50\% of water users.
@@
 
-\subsubsection{Optimal Two-Part Tariffs and Sharing Hassle Costs}
-
+This section calculates optimal tariffs in the current environment in Manila (where households may choose to share).
+Figure~\ref{figure:optimaltariffsharing} plots the marginal prices associated with each counterfactual tariff.
+Table~\ref{table:optimaltariffsharing} computes the impacts of these tariffs on source choices as well as welfare.
+Moving from the current tariff schedule (second column) to an optimal two-part tariff (third column), I find large welfare improvements on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.
+These gains are mainly enjoyed by large users benefiting from a lower marginal price relative to the current tariff since average consumption nearly doubles.
+At the same time, flattening the tariff reduces the implicit ``tax'' on pooling consumption on a shared connection, allowing low-users to enjoy lower marginal prices from their neighbors' connections.
+These lower marginal prices compensate for the higher hassle and free-rider costs from sharing, boosting surplus for low-users by around 50\% and reducing the share of households using from vendors from 4\% to 1\%.
+Low marginal prices combined with higher fixed fees both work to increase the share of households using from a neighbor's connection from 25\% to 44\%.
+
+%zooming in on tariffs below 20 PhP/$\text{m}^{3}$ in order to highlight distinctions between the two-part and three-part tariffs. 
+%The optimal fixed fee lies below the current fixed fee, which is priced at the cost of installing and maintaining a connection.
+Since households incur hassle costs and free-rider distortions from splitting the bill in sharing connections, pricing below cost allows the regulator to encourage households to substitute away from shared connections toward individual connections and avoid these hassle costs at the margin.
+By subsidizing individual connections, the two-part tariff in column three performs very close to the first-best tariff in terms of average consumer surplus.
+
+A social two-part tariff (fourth column) reallocates surplus to low-users by subsidizing fixed connection fees with a higher marginal price.
+Compared to an optimal tariff, this social tariff brings the percentage using from vendors to zero while also decreasing the share using from neighbors by 7 percentage points.
+These improvements in access come at a small cost to average consumption, but only increase surplus for low-users by a modest \input{tables/tpt_social_surplus_change_low_sharing_group}PhP/month.
+By contrast, social tariffs almost doubled low-user surplus in a world without sharing (Section~\ref{section:optimaltariffswithoutsharing}).
+These findings suggest that informal sharing networks may constrain the effectiveness of non-linear pricing in redistributing surplus.
+
+%While manipulating the two-part tariff proved to be an effective redistributive strategy in a world without sharing ,
+%while average surplus declines by \input{tables/tpt_social_surplus_change_avg_sharing_group}PhP/month.   
+%maximizing welfare for low users counterintuitively involves increasing the fixed fee in order to subsidize a very low marginal price.  
+%This tariff maximizes the share of households using from neighbors while also driving a significant share of households toward water vendors.
+Since low-users are able to split the fixed fee with their sharing partner, they can enjoy greater consumption at the low marginal price.
+%Despite this relatively extreme pricing schedule,
+
+An optimal three-part tariff with sharing (fifth column) follows the same pattern as in the case without sharing: increasing marginal prices select for high-usage households to connect, which provide greater revenue to cover the fixed costs.
+As before in Section~\ref{section:optimaltariffswithoutsharing}, this tariff produces negligible changes in welfare.
+Figure~\ref{figure:optimaltariffsharing} indicates an optimal three-part tariff with an almost zero first price segment followed by a much higher second price segment, which again broadly aligns with the current tariff structure.
+This tariff structure supports the ``life-line'' tariff as a way of efficiently maximizing surplus (rather than achieving distributional goals).
+Column six (along with Figure~\ref{figure:optimaltariffsharing}) finds that a social three-part tariff subsidizes entry with a negative fixed price, which is offset by a high marginal price for usage up to 20 m3.
+This tariff reduces average surplus by over 8 PhP/month to produce only 0.1 PhP/month of additional surplus for low-users.
+This result underscores the extent to which sharing networks constrain the ability of cities to achieve redistribution through complex, non-linear pricing strategies.
+
+%finds no difference in the optimal social two and three part tariffs.
+
+\subsubsection{Optimal Two-Part Tariffs and Marginal Sharing Costs}\label{section:tptsharingcosts}
+%and \ref{section:optimaltariffswithsharing} 
 To investigate mechanisms driving these optimal pricing schedules, this section considers how the optimal two-part tariff varies continuously with counterfactual levels of the hassle cost, $H$.
-I follow the same routine as in Sections~\ref{section:optimaltariffswithoutsharing} and \ref{section:optimaltariffswithsharing} by (1) calculating total revenue raised under the current tariff (in Figure~\ref{figure:tariff}) given the counterfactual hassle cost, (2) recalculating the implied capital costs from total revenue under this hassle cost, and (3) determining the optimal two-part tariff maximizing total consumer surplus while just covering costs.\footnote{As the hassle cost rises, the current tariff raises less revenue, lowering the capital costs.
+I follow the same routine as in Section~\ref{section:optimaltariffswithoutsharing} by (1) calculating total revenue raised under the current tariff (in Figure~\ref{figure:tariff}) given the counterfactual hassle cost, (2) recalculating the implied capital costs from total revenue under this hassle cost, and (3) determining the optimal two-part tariff maximizing total consumer surplus while just covering costs.\footnote{As the hassle cost rises, the current tariff raises less revenue, lowering the capital costs.
 The patterns below are robust to instead holding the capital costs fixed while increasing the hassle costs.}
@@
 Figure~\ref{figure:tptshrcosts} plots the optimal marginal price, fixed fee, and share of the population choosing each water source as a function of the hassle cost.
-The vertical gray lines show the estimated hassle cost of 15.14 from Section~\ref{section:hasslecostestimation}.
+The vertical gray lines show the average estimated hassle cost of 15.93 from Section~\ref{section:hasslecostestimation}.
 When hassle costs are very low, the regulator chooses a relatively high marginal price and low fixed fee.
@@
 The high marginal price serves as an way to mitigate overconsumption from free-riding on these shared connections: when three households share a tap, they respond to one third of the marginal price through spitting the bill.
-Therefore, setting a price around 13 PhP/$\text{m}^3$ ensures that households actually respond close to the marginal cost of 5 PhP/$\text{m}^3$.
+Therefore, setting a price around 11.5 PhP/$\text{m}^3$ ensures that households actually respond closer to the marginal cost of 5 PhP/$\text{m}^3$.
 This high marginal price also raises greater revenue allowing the regulator to lower the fixed fee.
@@
 
-As the hassle cost increases from 5 PhP/$\text{m}^3$ to around 17 PhP/$\text{m}^3$, it becomes optimal for the regulator to increase the marginal price as a way of taxing shared connections and subsidizing individual connections.
+As the hassle cost increases from 5 PhP/$\text{m}^3$ to around 13 PhP/$\text{m}^3$, it becomes optimal for the regulator to increase the marginal price as a way of taxing shared connections and subsidizing individual connections.
 In this range, households are not able to internalize the extent to which costly sharing relationships reduce their own contributions to the capital costs.
@@
 
-Above 17 PhP/$\text{m}^3$, the hassle cost becomes large enough to disincentivize sharing on the margin, allowing the regulator to begin lowering the marginal price again.
+Above 13 PhP/$\text{m}^3$, the hassle cost becomes large enough to disincentivize sharing on the margin, allowing the regulator to begin lowering the marginal price again.
 Yet, at these high levels of hassle cost, some households begin substituting toward vended water, providing a new incentive for subsidizing access by keeping prices above the marginal cost (consistent with theoretical work by \cite{auerbach1978two}).
 The slow decline in marginal price over this range helps to offset the increasing hassle cost, reducing the rate of substitution away from shared connections.
-From a distributional perspective, I find that a hassle cost of around 18 PhP/$\text{m}^3$ represents a threshold where the bottom 50\% of users transition from preferring a very high fixed fee as in Section~\ref{section:optimaltariffswithsharing} to preferring fixed fee subsidies as in Section~\ref{section:optimaltariffswithoutsharing}.
+%From a distributional perspective, I find that a hassle cost of around 18 PhP/$\text{m}^3$ represents a threshold where the bottom 50\% of users transition from preferring a very high fixed fee as in Section~\ref{section:optimaltariffswithsharing} to preferring fixed fee subsidies as in Section~\ref{section:optimaltariffswithoutsharing}.
 
@@
 This paper demonstrates that pricing policies intended to increase water access especially among the poor can have unintended consequences when low-income households can simply access the piped water network through their neighbors.
-The counterfactual exercise finds that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water and total welfare while leaving welfare among low-users unchanged.
+The counterfactual exercises find that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water, total welfare, and even welfare among the bottom half of water users.
 In this counterfactual, high fixed costs of accessing an individual connection allow for sharing networks to play an important role in extending water access despite sizable hassle costs.
@@
 From this perspective, cities may benefit from considering how prices not only might encourage access and redistribute consumer surplus, but also may affect the endogenous formation of water sharing networks.
-For example, price discriminating according to neighborhood income instead of by level of monthly usage may achieve similar goals of redistribution without distorting sharing networks.
+For example, price discriminating according to neighborhood income instead of by monthly usage levels may achieve similar goals of redistribution without distorting sharing networks.
 While this policy may not be appropriate in Manila since neighborhoods are often very heterogeneous in income, this approach may work well in other contexts where neighborhoods are more segregated, such as in Colombia where electricity rates vary according to the social category of each neighborhood (\cite{mcrae2014infrastructure}).
@@
 \begin{appendices}
+%\appendix
+
+%\renewcommand\thefigure{\thesection.\arabic{figure}}
+%\renewcommand\thetable{\thesection.\arabic{table}}
+
+\renewcommand{\thesection}{A.\Roman{section}} 
+\renewcommand{\thesubsection}{\thesection.\roman{subsection}}
 
@@
 
-This section assesses the extent to which the connection survey constitutes a random sample of connected households.
+This section assesses the extent to which the connection survey constitutes a representative sample of connected households.
 The documentation for the connection survey indicates that sampling was stratified based on geographic areas, assigning a target number of households owning connection to be survey according to the Census population for each area.
 Households owning connections were randomly interviewed until these targets were reached.
-While ensuring a random sample of connections with areas, this method may oversample areas with few connections per population.
+While ensuring a random sample of connections within areas, this method may oversample areas with few connections.
 To test this hypothesis, the following equation predicts the share of connections surveyed in each Meter Reading Unit (MRU) --- the smallest geographical unit used by the water provider including a couple hundred water connections on average --- according to demographics of households owning connections, $Z_{MRU,i}$, in each of these MRUs:
@@
 Although many coefficients are statistically significant consistent with large sample sizes for this estimation, the magnitudes of the effects are small in economic terms across most measures.
-For example, increasing the average number of households per connection by a standard deviation (0.65) results in a 0.0021 percentage point decrease in the probability of being surveyed; given a mean survey probability of 6\%, this change represents only a 3.3\% decrease.
-Dwelling types are the strongest predictor of coverage, indicating that surveyors may have oversampled apartments possibly due to easier availability.
+For example, increasing the average number of households per connection by a standard deviation (0.65) results in a 0.0021 percentage point decrease in the probability of being surveyed; given a mean survey probability of 6 percentage points, this change represents only a 3.3 percent decrease.
+Dwelling types are the strongest predictor of coverage, indicating that surveyors may have oversampled apartments possibly due to easier availability to survey.
 Taken together, these results suggest that to the extent that non-random sampling may affect results, it will lead to an underestimation of the importance of sharing networks in Manila.
@@
 Vendor households captured in the final column of Table~\ref{table:pawstocensus} closely resemble shared-use households across age, employment, and income measures.
-These households are especially likely to reside in a single house, which may lead to easier access to vendors as well as more difficult access to neighboring connections.
+These households are especially likely to reside in single houses, which may lead to easier access to vendors as well as more difficult access to neighboring connections.
 
@@
 
-Since this survey is not designed to be representative of the population of households in Manila, the following tables compare descriptive statistics between the mobile survey and the Public Assessment of Water Services (PAWS) survey.
+Since this survey is not designed to be representative of the population of households in Manila, the following tables compare descriptive statistics between the mobile survey and the connection  survey (Public Assessment of Water Services (PAWS)).
 Table~\ref{table:pollfishpawsmeans} compares the shares of households choosing each water source --- individual, sharing with 1 other household, or sharing with 2 other households --- across the two datasets, adjusting for the fact that the connection survey was conducted at the water connection-level.
@@
 Since the connection survey only captures demographics for water connection owners while the mobile survey covers all users, this trend may capture differences between these groups.
-Taken together, these findings suggest that the mobile and connection surveys are broadly consistent in capturing the population of water users despite differences in survey methods and timing.
+These findings suggest that the mobile and connection surveys are broadly consistent in capturing the population of water users despite differences in survey methods and timing.
 
@@
 
-This section now investigates the extent to which this linear approximation might impact coefficient estimates as well as welfare calculations.
+This section now investigates the extent to which the linear approximation might impact coefficient estimates as well as welfare calculations.
 The following figure compares the linear approximation to the standard normal CDF function over the range $(-3,3)$:
@@
 Sampling error can help explain why the estimates in column three do not exactly match the true parameters.
-The last column finds small differences between estimates in columns two and three, providing some evidence that the linear approximation does not introduce substantial bias in the estimation.
+The last column finds small differences between estimates in columns two and three, providing some evidence that the linear approximation may not introduce substantial bias in the estimation.
 Welfare differences between following  approximated versus actual versus are negligible, totaling \input{tables/approx_welfare}PhP per month.
@@
 Fixed price contracts may lead to a different allocation of surplus from sharing contracts depending on the size of the fixed price $Z$.
-Yet, since the model assumes that households are able to split expected surplus from the sharing relationship through fixed monthly transfers in Section~\ref{section:watersourcechoice}, the type of contract likely has little effect on empirical or welfare estimates.
+Yet, since the model assumes that households are able to split expected surplus from the sharing relationship through fixed monthly transfers in Section~\ref{section:watersourcechoice}, the type of contract may have little effect on empirical or welfare estimates.
 
@@
 
-\section{Descriptive for Estimation Sample}\label{appendix:descriptivesest}
-
-Table~\ref{table:descriptivesestsample} provides descriptive statistics for the connection-level sample used in the simulated method of moments estimation.
+\section{Descriptive Statistics for Estimation Sample}\label{appendix:descriptivesest}
+
+Table~\ref{table:descriptivesestsample} provides descriptive statistics for the connection-level sample used in the demand estimation (Section~\ref{section:preferenceestimation}) and simulated method of moments estimation (Section~\ref{section:fixedcostestimation}).
 Demographic variables are expressed in terms of dummy variables capturing various features that might drive demand for water.
@@
 
-Figure~\ref{figure:consumptionhistogram} shows a histogram of monthly consumption choices across all water connections and months in the data alongside the tariff schedule (censored below 50).
-Usage hovers around 20 cubic meters per month; by comparison, households in the United States use closer to 50 cubic meters per month.
+Figure~\ref{figure:consumptionhistogram} provides a histogram of monthly consumption choices across all water connections and months in the data alongside the tariff schedule (censored below 60 m3).
+Usage hovers around 20 m3 per month; by comparison, households in the United States use closer to 50 m3 per month.
 Intuitively, households may be less willing to consume an additional cubic meter on the margin if the price for that unit is much higher.
-The histogram provides some evidence of bunching at 10 and 20 cubic meters, although the magnitudes are quite small.
+The histogram provides some evidence of bunching at 10 and 20 m3, although the magnitudes are small.
 Many households are also observed to consume below 10 units where the marginal price is actually zero.
-Taken together, this evidence suggests households may be unresponsive to price.
+%Taken together, this evidence suggests households may be unresponsive to price.
 
@@
 A simple differences-in-differences estimate calculates a sizable price elasticity of 0.5 from this change, indicating significant demand responsiveness to time-series variation in the tariff.
-This elasticity is very similar to the structural estimates in Section~\ref{section:preferenceestimation}.
+This elasticity is smaller than the structural estimates in Section~\ref{section:preferenceestimation}.
 
@@
 
-The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs since in this case, the budget constraint is convex.
-Tariffs that include both increasing and decreasing block tariffs require comparing indirect utilities across all segments as in \cite{szabo2015value}.
-I extend this model to allow for decreasing marginal prices in the counterfactual exercises in Section~\ref{section:counterfactualexercises}.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
+The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs like the one in Manila.
+Tariffs that include both increasing and decreasing blocks require comparing indirect utilities across all segments as in \cite{szabo2015value}.
+I extend the model to allow for decreasing marginal prices in the counterfactual exercises in Section~\ref{section:counterfactualexercises}.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
 %\begin{align}\label{equation:generaldemand}
@@
 \begin{split}
-w^{*}_C &=
+D^{*}_C &=
 \begin{cases}
-D^{1,1,1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-D^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-D^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-D^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-D^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-D^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
+W^{1,1,1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+W^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
+W^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
+W^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
+W^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
+W^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
+W^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
 \end{cases}\\
 \text{Where: } & \\
-D^{L,M,H}_C        		&=  \frac{ d(P^{L,M,H}) }{ V^{L,H} }  + \frac{ \eta_C }{ V^{L,H} }   \\
-d(p) &= \gamma_C - \alpha_C [ H_{C} + \frac{p}{S}]  \\
+W^{L,M,H}_C        		&=  \frac{ w(P^{L,M,H}) }{ V^{L,H} }  + \frac{ \eta_C }{ V^{L,H} }   \\
+w(p) &= \gamma_C - \alpha_C [ H_{C} + \frac{p}{S}]  \\
 P^{L,M,H}  &= \dfrac{1}{2}[ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ] \\
 V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
-\overline{\eta}^{j}_{l,L}   &= \overline{W}_l -  d(p^j)  - \sqrt{2} \sigma_{\epsilon_C} \hspace{.1cm},\hspace{.2cm} \overline{\eta}^{j}_{l,U}   = \overline{W}_l - d(p^j)  + \sqrt{2} \sigma_{\epsilon_C} \\
+\overline{\eta}^{j}_{l,L}   &= \overline{W}_l -  w(p^j)  - \sqrt{2} \sigma_{\epsilon_C} \hspace{.1cm},\hspace{.2cm} \overline{\eta}^{j}_{l,U}   = \overline{W}_l - w(p^j)  + \sqrt{2} \sigma_{\epsilon_C} \\
 \end{split}
 \end{align}
-
 %For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.
-
-In this expression, $d^{L,M,H}_C$ captures the deterministic component of demand while $D^{L,M,H}_C$ adds the stochastic component of fixed preferences.
+In this expression, $w^{L,M,H}_C$ captures the deterministic component of demand while $W^{L,M,H}_C$ adds the stochastic component of fixed preferences.
 Connection-level fixed preferences $\gamma_C$, price sensitivities $\alpha_C$, and  hassle costs $H_C$ sum across their respective values for all households using a connection.
@@
 Crossing a threshold means that the consumption shock now exposes the connection to a different set of prices.
-Figure~\ref{figure:intuitivedemand} graphs an example demand curve where the slope is determined by the functions $D^{L,M,H}_C$ and the changes in slope are given by the preference thresholds.
-
+Figure~\ref{figure:intuitivedemand} graphs an example demand curve where the slope is determined by the functions $W^{L,M,H}_C$ and the changes in slope are given by the preference thresholds.
 %Also, the model assumes ex-ante that the parameter $\sigma_{\epsilon_C}$ satisfies two boundary conditions that is developed in more detail below as well as in Section~\ref{section:preferenceestimation}.
-
 \begin{figure}
@@
 
-\node[align=center] at (1.8,1)  { \text{\footnotesize  $D^{1,1,1}_C$}};
-\node[align=center] at (2.8,1) { \text{\footnotesize  $D^{1,2,2}_C$}};
-\node[align=center] at (3.8,1)  { \text{\footnotesize  $D^{1,2,3}_C $}};
-\node[align=center] at (4.8,1) { \text{\footnotesize  $D^{2,3,3}_C $}};
-\node[align=center] at (6.8,1)  { \text{\footnotesize  $D^{3,3,3}_C $}};
-\node[align=center] at (8.3,1)    { \text{\footnotesize  $D^{3,4,4}_C $}};
-\node[align=center] at (9.6,1)  { \text{\footnotesize  $D^{4,4,4}_C $}};
+\node[align=center] at (1.8,1)  { \text{\footnotesize  $W^{1,1,1}_C$}};
+\node[align=center] at (2.8,1) { \text{\footnotesize  $W^{1,2,2}_C$}};
+\node[align=center] at (3.8,1)  { \text{\footnotesize  $W^{1,2,3}_C $}};
+\node[align=center] at (4.8,1) { \text{\footnotesize  $W^{2,3,3}_C $}};
+\node[align=center] at (6.6,1)  { \text{\footnotesize  $W^{3,3,3}_C $}};
+\node[align=center] at (8.3,1)    { \text{\footnotesize  $W^{3,4,4}_C $}};
+\node[align=center] at (9.6,1)  { \text{\footnotesize  $W^{4,4,4}_C $}};
 
@@
 \textbf{  Demand over a Single Price:  }  The first, third, and fourth price segments of the tariff schedule in Manila given in Figure~\ref{figure:intuitivedemand} exhibit large gaps of 20 $\text{m}^{3}$ between price changes.
-Within these segments, the consumption shocks are not large enough to ever bounce the households across a kink point in these regions.
+Within these segments, the consumption shocks are not large enough to ever bounce the households across a tariff kink point.
 Therefore, households are exposed only to the current price for that segment.
-Setting the low, medium, and high prices all equal to $k$ in expression $D^{L,M,H}_C$, demand arrives at the following expression:
-\begin{align*}
-  D_C  =& \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{S} p^k + \eta_C 
+Setting the low, medium, and high prices all equal to $k$ in expression $W^{L,M,H}_C$, demand arrives at the following expression:
+\begin{align*}
+  W_C  =& \gamma_C - \alpha_C [ H_{C} + \frac{p^k}{S} ] + \eta_C 
 \end{align*}
@@
 \begin{align*}
-D_C &= \frac{ 1}{ V^{k,k+1} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{k} + p^{k+1} - \overline{W}^{k+1} (\frac{p^{k+1} - p^{k}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big ) + \frac{ \eta_C }{ V_{k+1,k} }
+W_C &= \frac{ 1}{ V^{k,k+1} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{k} + p^{k+1} - \overline{W}^{k+1} (\frac{p^{k+1} - p^{k}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big ) + \frac{ \eta_C }{ V_{k+1,k} }
 \end{align*}
@@
 \begin{split}
-w^{*}_C &=
+D^{*}_C &=
 \begin{cases}
-D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{1,U}  \\
-D^{2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-D^{3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }   
+W^{1,1,1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+W^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{1,U}  \\
+W^{2,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
+W^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
+W^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
+W^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
+W^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }   
 \end{cases}\\
@@
 \begin{split}
-w^{*}_C &=
+D^{*}_C &=
 \begin{cases}
-D^{1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-D^{1,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-D^{2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-D^{2,3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{2,4} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-D^{3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-D^{4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
+W^{1,1,1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
+W^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
+W^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
+W^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
+W^{2,3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{2,4} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
+W^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
+W^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
 \end{cases}\\
@@
 	\item \textit{ Connections that experience a leak are representative of the population of connections.
-}  This assumption is supported by minimal economic differences in means of observables between connections with leaks and without in Table~\ref{table:leakbalance} (although some differences are statistically significant).
+}  This assumption is supported by small economic differences in means of observable measures between connections with leaks and without in Table~\ref{table:leakbalance} although some differences are statistically significant.
 \begin{table}
@@
 	\item  \textit{ The decision to disconnect conditional on experiencing a leak is uncorrelated with water demand.
-}  Table~\ref{table:leakbalancedc} provides partial support by showing few large differences in characteristics between those that disconnect and those that remain connected other than the size of leak.
+}  Table~\ref{table:leakbalancedc} provides partial support by showing few large differences in characteristics between those that disconnect and those that remain connected other than the size of the leak.
 This evidence suggests that the disconnection decision is driven primarily by variation in the magnitude of the leak.
@@
 The first column predicts strong increases in consumption for smaller users (ranks 1 and 2) while large users (ranks 3 and 4) exhibit small and even negative demand responses.
-These differential responses are only exaggerated in the second column, suggesting that mean reversion may play a large role in biasing estimates.
-The third columns shows that after adjusting for mean reversion bias, the demand response of neighboring connections is roughly equal as the relative demand increases for these connections.
+These differential responses are amplified in the second column (with placebo treatment dates), suggesting that mean reversion may play a large role in biasing estimates.
+The third column shows that after adjusting for mean reversion bias, the demand response of neighboring connections is roughly equal as the relative demand increases for these connections.
 This finding provides suggestive evidence that households are not selecting sharing partners conditional on their neighbors' water demands.
@@
 
-\subsection{Out-of-Sample Test: A Connection Fee Discount Program}\label{section:oostest}
+\section{Out-of-Sample Test: A Connection Fee Discount Program}\label{section:oostest}
 
@@
 Since the data do not identify precisely which local areas or specific households were eligible for the discount, additional assumptions are necessary to measure eligibility.
-First, I define treated areas as any meter reading unit that receives at least one discounted connection over the full duration while control areas include any meter reading units that never receive discounts.
-Meter reading units (MRUs) are common geographical designations used by the water provider and include between 100 and 500 meters.
+First, I define treated areas as any meter reading unit (MRU) that receives at least one discounted connection over the full duration while control areas include any MRUs that never receive discounts.
+MRUs are common geographical designations used by the water provider and include between 100 and 500 meters.
 There are 3,757 MRUs in the service area.
@@
 Figure~\ref{figure:discountreducedform} provides the graphical estimates from this equation.
-The untreated group on the left-hand side exhibits a very stable trend in new connections with no changes relative to the discount program.
-This finding is consistent with steady population growth generating a constant rise in the total number of connections.
-
-The treated group on the right-hand side shows a relatively stable pre-trend interrupted by a substantial increase in the number of connections just following the discount program implementation.
+The differences-in-differences estimate shows a relatively stable pre-trend interrupted by a substantial increase in the number of connections just following the discount program implementation.
 This increase lasts for a couple years before returning to pre-program levels.
-These trends provide evidence that households who are sharing water or purchasing from vendors are gradually learning about the price change and choosing to purchase their own connections.
+This trend provides evidence that households who are sharing water or purchasing from vendors are gradually learning about the price change and choosing to purchase their own connections.
 After a couple years, this additional demand for connections has been satisfied, letting migration take over as the sole driver of new connections.
@@
 A simple difference-in-differences estimate provided by Table~\ref{table:diffdiscountreducedform} calculates an increase of 0\input{tables/red_form_est}new connections per month for the treated areas on a base average of 0\input{tables/red_form_base}new connections per month.
-Aggregated over the full \input{tables/treated_months}months of the program, this program led to a total of \input{tables/total_effect}new connections per Meter Reading Unit.
-Given that the average Meter Reading Unit has \input{tables/mru_size}connections over the full time period, this program generated about a \input{tables/percent_increase_discount}\unskip\% increase in the number of new connections.
+Aggregated over the full \input{tables/treated_months}months of the program, this program led to a total of \input{tables/total_effect}new connections per MRU.
+Given that the average MRU has \input{tables/mru_size}connections over the full time period, this program generated about a \input{tables/percent_increase_discount}\unskip\% increase in the number of new connections.
 
 To compare results from this policy to counterfactual estimates from the model, I now convert the change in number of connections induced by the policy to a shift from shared and vendor connections to individual connections.
-Given that \input{tables/share_2_hhs}\unskip\% of connections serve two households and \input{tables/share_3_hhs}\unskip\% of connections serve three or more households, and 5\% of households access water from vendors, then \input{tables/mru_size}connections per Meter Reading Unit are calculated to serve an average population of around \input{tables/population_served}households.
+Given that \input{tables/share_2_hhs}\unskip\% of connections serve two households and \input{tables/share_3_hhs}\unskip\% of connections serve three or more households, and 6\% of households access water from vendors, then \input{tables/mru_size}connections per MRU are calculated to serve an average population of around \input{tables/population_served}households.
 This policy results in a \input{tables/increase_in_individual_connections}percentage point increase in the share of households owning a connection, which can be directly compared to predictions from the counterfactual exercise.
@@
 
-Despite these caveats, the fact that the reduced-form and model-based estimates are similar in magnitude lends support to the counterfactual exercises in Section~\ref{section:counterfactualexercises}.
+Despite these caveats, the fact that the reduced-form and model-based estimates are similar in magnitude lends support to the counterfactual exercises implemented in Section~\ref{section:counterfactualexercises}.
 Table~\ref{table:oosestimates} calculates the impacts of this connection fee discount on water source choices as well as consumer welfare.
-Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended.
+Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended water.
 Since utility is assumed to be quasi-linear, consumer welfare is measured in PhP/month.
@@
 The estimation strategy relies heavily on connection-specific fixed preference terms estimated in the Section~\ref{section:preferenceestimation} to recover parameters in Section~\ref{section:hasslecostestimation} and Section~\ref{section:fixedcostestimation}.
-Since the data contain a limited number of months of consumption for each connection (averaging around 77 months), noise in the estimation of these preference terms may produce bias in latter estimates.
+Since the data contain a limited number of months of consumption for each connection (averaging around 50 months), noise in the estimation of these preference terms may produce bias in latter estimates.
 I test for this type of bias by simulating data given true parameters close to the estimates and reestimating the model on this simulated data.
@@
 
-The first column presents the true assumed parameter values, the second column provides the estimations results for the simulated data using the full sample, and the third column includes estimates for a subsample of the data where I have dropped half of the observations for each connection.
-Examining the second column and percent deviations in the third column, I find that the incidental parameters do not seem to lead to a large degree of bias in any of the coefficients with the maximum occurring for the variance estimate for the vendor price.
+The first column presents the true assumed parameter values, the second column provides the estimation results for the simulated data using the full sample, and the third column includes estimates for a subsample of the data where I have dropped half of the observations for each connection.
+Examining the second column and percent deviations from the true parameters in the third column, I find that the incidental parameters do not seem to lead to a large degree of bias in any of the coefficients with the maximum occurring for the variance estimate for the vendor price.
 Dropping half of the time periods, the fourth and fifth columns indicate that the hassle cost and connection fee parameters would be the most sensitive to any possible bias from incidental parameters.
@@
 \begin{table}
-
 \centering
@@
 
-As a simple out-of-sample test, I compare the estimate of $p_v$ in Table~\ref{table:smmestimates} to the implied $p_v$ from data on total water expenditures for vendor households using additional census data from a section of Manila.
-The 2011 Community Based Monitoring System data covers over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown Manila --- and includes information on income (used to compute imputed income) as well as water source and monthly expenditures.
+As a simple out-of-sample test, I compare the estimate of $p_V$ in Table~\ref{table:smmestimates} to the implied $p_V$ from data on total water expenditures for vendor households using additional census data from a section of Manila.
+The 2011 Community Based Monitoring System data cover over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown Manila --- and includes information on income (used to compute imputed income) as well as water source and monthly expenditures.
 In this data, households using from vendors report expenditures of 365 PhP/month while households using individual connections report expenditures of 470 PhP/month and households sharing connections report expenditures of 365 PhP/month.
@@
 Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=37$, and price sensitivity, $\alpha=.91$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 7.9 PhP/$\text{m}^{3}$ or 32.8 PhP/$\text{m}^{3}$.
-The latter price almost perfectly matches the estimated price of 32.85 PhP/$\text{m}^3$, providing additional support for the structural estimates.
+The latter price almost perfectly matches the estimated price of 32.85 PhP/$\text{m}^3$, providing additional support for the structural estimates from Section~\ref{section:fixedcostestimation}.
 
@@
 
-By weighting the first three moments highly, the model almost exactly matches moments shown in Table~\ref{table:modelfit}.
-The model is also able to match the direction but predicts stronger correlations with fixed preferences for water $\beta_i$ and percent owning connections and percent using from a neighbor.
-One interpretation is that there may be other factors besides simply water preferences and heterogeneity in hassle costs that are driving source decisions.
-The model has difficulty matching correlation between fixed preferences and share using from vendors, which may be partially due to noise generated in the process of projecting fixed preferences.
+By weighting the first three moments (water source choices) highly by design, the model almost exactly matches moments shown in Table~\ref{table:modelfit}.
+The model is also able to match the direction of correlations between fixed preferences for water $\beta_i$ and percent owning connections as well as  percent using from a neighbor; however, the model predicts stronger correlations in both cases.
+One interpretation is that there may be other factors besides simply water preferences and heterogeneity in hassle costs that are driving water source decisions.
+The model has difficulty matching correlation between fixed preferences and share using from vendors, which may be partially due to noise generated in the process of imputing fixed preferences for households using from vendors.
 

### 2018-11-08 phil_paper/jmp_wjv_v3.tex
lots of paper edits

--- 2018-10-31 phil_paper/jmp_qje.tex
@@
 
-\usepackage[notablist,nofiglist]{endfloat}
+%\usepackage[notablist,nofiglist]{endfloat}
 %\renewcommand{\efloatseparator}{\mbox{}}
 
-\renewcommand{\thetable}{\Roman{table}}
-\renewcommand{\thefigure}{\Roman{figure}}
-
-\renewcommand{\thesection}{\Roman{section}} 
-\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
-\renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
+%\renewcommand{\thetable}{\Roman{table}}
+%\renewcommand{\thefigure}{\Roman{figure}}
+
+%\renewcommand{\thesection}{\Roman{section}} 
+%\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
+%\renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
 
@@
 %\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
-\title{ OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
+\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
 
@@
 Section~\ref{section:fixedcostestimation} details the imputation procedure used to infer preferences for these households.
+Computationally, the estimation minimizes the likelihood function using a trust-region algorithm provided with the analytical gradient vector and Hessian matrix of the likelihood function.
 %Appendix~\ref{appendix:sigmanuassumptions} determines the ex-ante assumptions on $\sigma_{\epsilon}$ needed to identify the particular demand function.
@@
 \begin{table}
+\centering
 \caption{Model Performance}\label{table:modelperformance}

### 2018-11-12 phil_paper/jmp_qje.tex
polishing jmp intro

@@
 %\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
-\title{ OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
+\title{OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
 
@@
 In contrast, the optimal pricing policy features a high fixed fee and low marginal price, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
-This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.
+
+	%This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus.
+
+	% or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income
 
@@
 \end{abstract} 
+\vspace{1cm}
 {\bf JEL-Classification:} H23, L95, L98, O13, O17, O18 \\
@@
 \section{Introduction}
-
-Despite large investments in piped water throughout the developing world, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries for at least the past decade (World Bank [2015]).
-Given health, time-savings, and other benefits from piped water, how can water utilities set prices to ensure access while covering costs?\footnote{\cite{gamper2010impact,cutler2005role}, and \cite{galiani2005water} find health improvements in both developed and developing settings while \cite{devoto2012happiness} find time savings and other utility benefits.}  A popular approach particularly in developing cities is to subsidize upfront connection fees with high marginal prices.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
+ % \footnote{\cite{laffont2005regulation} emphasizes high costs of public funds in developing countries (with a deadweight loss of 2.5 for the Philippines) due to limited ability to enter long-term contracts with government, credit constraints, inefficient taxation, and corruption.}
+ % To ensure widespread access while covering costs, a 
+Improving access to piped water generates substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  However, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
+While external health and other benefits may merit subsidizing piped water, government subsidies are often limited by high costs of public funds and risk of regulatory capture in these countries (\cite{laffont2005regulation}).
+Instead, prices must often be set to fully recover costs.
+A popular solution is to subsidize upfront connection fees with high marginal prices for monthly usage.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
 Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  Over 70\% of developing cities also increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}).
-\cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.}  Recent empirical papers in South Africa and C{\^o}te d'Ivoire predict gains in both access and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).
-
-Conventional pricing policies often rely on the assumption that each water connection serves a single household; however, many households in developing cities share with neighbors instead of purchasing their own connections.
-For example, 70\% of African cities report frequent water sharing (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
-While previous studies have focused on specific suburbs, this paper is the first to my knowledge to measure the role of water sharing in extending access across an urban population.
-
-Water sharing has important implications for the welfare impacts of common pricing policies.
-Increasing marginal prices weaken incentives for households to extend water access to their neighbors through sharing (\cite{whittington1992possible}).
-Fixed fee subsidies may have limited impacts on water access when sharing households already split connection fees with their neighbors.
-Since low-income households are more likely to use water from their neighbors, increasing marginal prices and low fixed fees may combine to act as regressive taxes in the presence of sharing.
-
-%  Shared connections record high levels of monthly consumption, which can expose them to high prices when marginal prices increase with usage . 
-This paper analyzes the welfare impacts of pricing policies in the presence of informal water sharing.
-Welfare impacts depend not only on heterogeneity in demand for water across the population, but also on costs associated with forming and maintaining water sharing relationships.
+\cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.
+The statistic comes from author calculations with data kindly provided by \cite{hoque2013state}.}  These pricing approaches have been shown to work well when each water connection serves a single household.
+Recent empirical papers in South Africa and C{\^o}te d'Ivoire predict gains in both access and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).
+
+However, many households in developing cities share connections with their neighbors, which can have large implications for water pricing.
+Land-tenure issues, credit-constraints, and administrative costs often prevent disadvantaged households from purchasing their own connections (\cite{devoto2012happiness}).
+Also, many cities maintain high upfront fees despite policy recommendations otherwise.
+As a result, 70\% of African utilities report frequent water sharing between households (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of informal sharing, previous research has not yet examined the importance of informal sharing for optimal pricing policy.
+
+This paper analyzes the welfare effects of pricing policies in the presence of informal water sharing.
+I build a model of household water demand that includes both (1) the upfront choice of whether to purchase a connection, share with a neighbor, or use non-piped sources as well as (2) monthly consumption choices.
+I also collect new survey evidence on informal sharing contracts to inform several features of the model design.
+The structural estimation leverages administrative data from 1.5 million water connections in Manila, which link to survey data on households owning and sharing connections.
+
+These estimates allow me to solve a standard regulator pricing problem: setting prices to cover both fixed and marginal costs while maximizing consumer surplus.
+I also allow the regulator to place extra weight on surplus for smaller, poorer users.
+In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
+Instead, these households substitute toward non-piped water sources, which have lower marginal prices, but varying quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
+The model collapses all non-piped sources into a single ``vendor'' option.}  The opposite approach --- high fixed fees and low marginal prices --- improves both access and welfare even for smaller users.
+High fixed fees are paid in full by households who connect individually and are split between sharing households.
+Informal sharing arrangements allow small-users to access piped water from their neighbors at low marginal prices.
+Shared connections also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.
+
+%By using from their neighbors, smaller-users also benefit from low marginal prices and avoid sourcing from non-piped water.  
+% Non-linear pricing helps policymakers achieve both efficiency (by targeting more inelastic households with higher prices) as well as equity (by targeting poorer households with lower prices).
+% excluding many smaller-users from piped water.\footnote{In the model, households can substitute to a vendor option that encompasses all non-piped sources of water, which commonly include deepwells, tanker trucks, and water refilling stations.}
+%The model is designed to match several features from new survey evidence on sharing contracts that I fielded as part of this study.
+
+%In the context of Manila, I find that the most disadvantaged households are also most likely to fetch water from their neighbors.
+%In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
+
+Manila
+
 To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2010 to 2015 with detailed survey data on the number of households and people using each water connection.
+
 With comprehensive geographic coverage of half of Manila and a variety of price variation, these data allow for a rich characterization of water demand.
 Additional variation in water source choices identify the relative fixed and marginal costs associated with sharing water with a neighbor.
-I find that despite relatively high marginal costs of sharing, shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.
-At the same time, informal sharing networks serve as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
+
+I find that shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.
+
+%At the same time, informal sharing networks serve as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
+
+%  Shared connections record high levels of monthly consumption, which can expose them to high prices when marginal prices increase with usage .
+
+Welfare impacts depend not only on heterogeneity in demand for water across the population, but also on costs associated with forming and maintaining water sharing relationships.
+[DONT LIKE THIS SENTENCE ANYMORE]
 
 To evaluate the impacts of different pricing policies, I build a model of household water demand that includes both initial source choices as well as monthly consumption choices.
+
 This model expands on the demand estimation literature for public utilities that focuses almost exclusively on quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
@@
 \caption{Model Performance}\label{table:modelperformance}
+\centering
 \input{tables/sample_prediction}

### 2018-11-14 phil_paper/jmp_qje.tex
better intro

@@
  % To ensure widespread access while covering costs, a 
-Improving access to piped water generates substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  However, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
+Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  However, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
 While external health and other benefits may merit subsidizing piped water, government subsidies are often limited by high costs of public funds and risk of regulatory capture in these countries (\cite{laffont2005regulation}).
-Instead, prices must often be set to fully recover costs.
+In many cases, prices must be set to fully recover costs.
 A popular solution is to subsidize upfront connection fees with high marginal prices for monthly usage.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
@@
 Recent empirical papers in South Africa and C{\^o}te d'Ivoire predict gains in both access and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).
-
 However, many households in developing cities share connections with their neighbors, which can have large implications for water pricing.
+
 Land-tenure issues, credit-constraints, and administrative costs often prevent disadvantaged households from purchasing their own connections (\cite{devoto2012happiness}).
-Also, many cities maintain high upfront fees despite policy recommendations otherwise.
+Also, many cities maintain high upfront fees despite policy recommendations otherwise (\cite{hoque2013state}).
 As a result, 70\% of African utilities report frequent water sharing between households (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of informal sharing, previous research has not yet examined the importance of informal sharing for optimal pricing policy.
@@
 I also collect new survey evidence on informal sharing contracts to inform several features of the model design.
-The structural estimation leverages administrative data from 1.5 million water connections in Manila, which link to survey data on households owning and sharing connections.
-
-These estimates allow me to solve a standard regulator pricing problem: setting prices to cover both fixed and marginal costs while maximizing consumer surplus.
-I also allow the regulator to place extra weight on surplus for smaller, poorer users.
+The structural estimation leverages administrative data from 1.5 million water connections in Manila from 2010 to 2015, which link to additional survey data on households sharing connections.
+
+These estimates allow me to solve a standard regulator pricing problem: setting prices to cover fixed and marginal costs while maximizing consumer surplus.
+I also let the regulator place extra weight on surplus for smaller, poorer users.
 In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
 Instead, these households substitute toward non-piped water sources, which have lower marginal prices, but varying quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
-The model collapses all non-piped sources into a single ``vendor'' option.}  The opposite approach --- high fixed fees and low marginal prices --- improves both access and welfare even for smaller users.
+The model collapses all non-piped sources into a single ``vendor'' option.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access and welfare even for smaller users.
 High fixed fees are paid in full by households who connect individually and are split between sharing households.
-Informal sharing arrangements allow small-users to access piped water from their neighbors at low marginal prices.
-Shared connections also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.
-
-%By using from their neighbors, smaller-users also benefit from low marginal prices and avoid sourcing from non-piped water.  
-% Non-linear pricing helps policymakers achieve both efficiency (by targeting more inelastic households with higher prices) as well as equity (by targeting poorer households with lower prices).
-% excluding many smaller-users from piped water.\footnote{In the model, households can substitute to a vendor option that encompasses all non-piped sources of water, which commonly include deepwells, tanker trucks, and water refilling stations.}
-%The model is designed to match several features from new survey evidence on sharing contracts that I fielded as part of this study.
-
-%In the context of Manila, I find that the most disadvantaged households are also most likely to fetch water from their neighbors.
-%In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
-
-Manila
-
-To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2010 to 2015 with detailed survey data on the number of households and people using each water connection.
-
-With comprehensive geographic coverage of half of Manila and a variety of price variation, these data allow for a rich characterization of water demand.
-Additional variation in water source choices identify the relative fixed and marginal costs associated with sharing water with a neighbor.
-
-I find that shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.
-
-%At the same time, informal sharing networks serve as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
-
-%  Shared connections record high levels of monthly consumption, which can expose them to high prices when marginal prices increase with usage .
-
-Welfare impacts depend not only on heterogeneity in demand for water across the population, but also on costs associated with forming and maintaining water sharing relationships.
-[DONT LIKE THIS SENTENCE ANYMORE]
-
-To evaluate the impacts of different pricing policies, I build a model of household water demand that includes both initial source choices as well as monthly consumption choices.
-
-This model expands on the demand estimation literature for public utilities that focuses almost exclusively on quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
-I specify a sequential game where households choose whether to connect individually, share with their neighbors, or purchase from a water vendor.
-For sharing households, I develop a simple model of the water sharing contract that captures two key features of these relationships: (1) households face challenges in observing each other's demand and (2) households often split the monthly water bill evenly.
+Informal sharing arrangements allow small-users to access piped water from their neighbors for even lower marginal prices than those offered by non-piped sources.
+Shared connections also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.\footnote{Cost savings are passed on to consumers through lower prices.}
+
+The welfare impacts of these pricing policies depend not only on household-level demand, but also on the relative costs of sharing water; these may include both marginal costs (ie.
+time spent fetching from neighbors or reduced pressure from re-piping water) as well as savings from splitting the fixed costs of a connection.
+Measuring demand and sharing costs presents two central challenges: how can we recover household-level demand when we only observe water consumption for each connection, and how can we separately identify the costs of sharing from preferences for water?
+The empirical approach addresses these challenges in three steps.
+
+The first step builds a tractable model of water sharing to estimate household-level demand from monthly usage data for each connection.
+Informed by a new survey, this model embeds how (1) households face challenges in observing each other's monthly demand and (2) households often split the monthly water bill evenly.
+These assumptions on sharing behavior ensure that connection-level demand can be expressed as a sum of underlying household demands even in the presence of non-linear prices.
+I use variation in the non-linear price schedule (both across and within connections) to identify water demand for each connection before disaggregating preferences to the household-level.
+This approach extends previous models of optimization over non-linear prices by including sharing and allowing households to anticipate unobserved shocks to their demand (\cite{moffitt1986econometrics,burtless1978effect}).
+
+To estimate the marginal costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to neighbors' connections.
+I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal costs of sharing.
+This exercise recovers sizable marginal costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.\footnote{This revealed-preference approach builds on a descriptive literature that identifies potential sources of water sharing frictions (\cite{whittington1992possible,nauges2006water}).}
+
+The third step maps the share of households using from each source --- connecting alone, sharing with a neighbor, or using from a non-piped vendor --- into an estimate of each source's relative fixed cost.
+The empirical approach leverages the assumption that given water preferences (from step one) and marginal sharing costs (from step two), any remaining variation in water source choices must be due to differences in their fixed costs.
+Since sharing decisions are strategic in nature, I specify a simple game where households sequentially choose their sources and agree to split any surplus from sharing.
+This revealed-preference approach to estimating fixed costs is especially relevant in a developing context because on top of the initial connection and monthly service fees, households often face fixed costs that are difficult to observe, including permitting fees, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.
+In fact, I estimate that the connection and service fees account for only around half of the total fixed costs facing households.
+This structural approach complements previous experimental evidence of fixed costs presented in \cite{devoto2012happiness}.
+By considering both source and quantity choices, this model also expands on the demand estimation literature for public utilities that has so far focused almost exclusively on monthly quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
+
+%The third step estimates these fixed costs by simulating the sequential game to match cross-sectional variation in water source choices.
+
+With these estimates, I simulate a series of counterfactual policies.
+First, I consider a connection fee subsidy policy consistent with recommendations from the World Bank, NGOs, and other researchers to improve water access for the poor (\cite{komives2005water,jimenez2014factors,mcintosh2003asian}).
+I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.
+This policy actually reduces access by incentivizing households to substitute toward non-piped vendors.
+Next, I compute an optimal tariff schedule to maximize consumer surplus while exactly covering production costs.
+Compared to the current tariff, I find that a simple, two-part tariff characterized by a fixed fee and low, flat marginal price can produce gains on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus.\footnote{With quasi-linear utility, consumer surplus for a given tariff is calculated as the difference between household utility under this tariff and household utility from using the non-piped, vendor option.}  These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections to install and maintain.
+Finally, I compare the optimal tariff with a social tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.
+With sharing, social tariffs are ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, social tariffs achieve substantial redistribution.
+These findings suggest that informal sharing networks constrain the extent to which non-linear prices can redistribute surplus.
+
+%Yet, since sharing involves costly redistribution of water, the optimal tariff subsidizes individual connections on the margin by pricing above marginal cost and setting the fixed fee below the cost of installing and maintaining each connection.
+
+% analyzes a quasi-experiment where households face leaks in their service pipes, forcing them to substitute to a neighbor's connection.
+
+% The model maps the extent to which these households are able to offset their consumption to a neighbor's connection into an estimate of the marginal costs of fetching water.
+This exercise recovers sizable sharing costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.
+This quasi-experimental approach builds on a descriptive literature pointing to potential costs of sharing water (\cite{whittington1992possible,nauges2006water}).
+
+% In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
+Time spent fetching water or reduced pressure-levels from informally re-piping both increase the marginal cost of sharing.
+%--- what is the relative fixed cost of
+
+%combines monthly usage to recover household-level demand.
+% recover household-level from connection usage,
+
+% I develop a simple model of the water sharing contract that captures two key features of these relationships informed by survey data:
+
+% The model characterizes monthly consumption choices when households face non-linear budget constraints and imperfect control over their exact consumption levels.
+
+% Greater demand heterogeneity increases the scope for usage-based price discrimination to both redistribute surplus and efficiently raise revenue.
+
+% Sharing costs determine how households can respond by changing their water source alongside their consumption patterns.
+
+%  while low sharing costs allow households
+
+% To evaluate the impacts of different pricing policies, I build a model of household water demand that includes both initial source choices as well as monthly consumption choices.
+
+%For sharing households, I develop a simple model of the water sharing contract that captures two key features of these relationships: (1) households face challenges in observing each other's demand and (2) households often split the monthly water bill evenly.
 The model characterizes monthly consumption choices when households face non-linear budget constraints and imperfect control over their exact consumption levels.
@@
 
-The estimation combines water source and consumption decisions to structurally recover preferences and unobserved costs of water sharing.
+% The estimation combines water source and consumption decisions to structurally recover preferences and unobserved costs of water sharing.
 To include reduced-form approaches to identification within the context of a structural model, I divide the estimation into three steps.
 The first step uses variation in the non-linear price schedule (both across and within households) to identify water demand for each household using monthly consumption data.
-To measure the shadow costs of fetching water from a shared connection, the second step analyzes a quasi-experiment where households face leaks in their service pipes, forcing them to substitute to a neighbor's connection.
-The model maps the extent to which these households are able to offset their consumption to a neighbor's connection into an estimate of the marginal costs of fetching water.
-This exercise recovers sizable sharing costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.
-This quasi-experimental approach builds on a descriptive literature pointing to potential costs of sharing water (\cite{whittington1992possible,nauges2006water}).
-On top of an initial connection fee and monthly service fee, households may face unobserved fixed costs in owning a connection, which may include application costs, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.
-The third step estimates these fixed costs by simulating the sequential game to match cross-sectional variation in water source choices.
-This strategy provides a structural, revealed-preference approach to recovering unobserved fixed costs, complementing previous reduced-form evidence in \cite{devoto2012happiness}.
-
-Combining the model and estimates, I simulate a series of counterfactual policies.
-First, I consider a connection fee subsidy policy consistent with recommendations from the World Bank, NGOs, and other researchers to improve water access for the poor (\cite{komives2005water,wsup,jimenez2014factors,mcintosh2003asian}).
-I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.
-This policy reduces access by incentivizing households to substitute toward water vendors, which mainly include deepwells and water refilling stations.
 
@@
 %This policy reduces access by incentivizing households to substitute away from sharing arrangements toward both individual connections and water vendors (which mainly include deepwells and water refilling stations).
-
-Next, I compute an optimal tariff schedule to maximize consumer surplus while exactly covering production costs.
-Compared to the current tariff, I find that a simple, two-part tariff characterized by a fixed fee and low, flat marginal price can produce gains on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.
-These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections to install and maintain.
-%Yet, since sharing involves costly redistribution of water, the optimal tariff subsidizes individual connections on the margin by pricing above marginal cost and setting the fixed fee below the cost of installing and maintaining each connection.
-
-Finally, I compare the optimal tariff with a social tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.
-With sharing, social tariffs are ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, social tariffs achieve substantial redistribution, over doubling consumer surplus for small users.
-This evidence suggests that the presence of informal sharing networks constrains non-linear pricing as an effective tool for redistribution.
 
@@
 These results provide evidence that the presence of informal sharing networks constrains pricing policy as an effective tool for redistribution.
-
-In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal water pricing.
-First, I do not directly model environmental, health, or other externalities associated with piped water use.
-Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
-Finally, the counterfactual exercises simulate the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
-Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of using public funding for water infrastructure (\cite{laffont2005regulation}).
-
-% Despite the relevance of water sharing arrangements to pricing policy, previous studies have provided either a descriptive analysis of water sharing (\cite{whittington1992possible}) or 
-% in fixed fee incentivizes households to substitute away from water sharing arrangements toward individual connections as well as  , it also increases the share of households using from a local 
-%among low-demand households by as much as \input{tables/discount_low_welfare_change}\unskip\% of monthly income.  
-%%%% WHAT IS ACCESS DUDE!!!!!!!
 
@@
 Section~\ref{section:conclusion} concludes.
+
+% Despite the relevance of water sharing arrangements to pricing policy, previous studies have provided either a descriptive analysis of water sharing (\cite{whittington1992possible}) or 
+% in fixed fee incentivizes households to substitute away from water sharing arrangements toward individual connections as well as  , it also increases the share of households using from a local 
+%among low-demand households by as much as \input{tables/discount_low_welfare_change}\unskip\% of monthly income.  
+%%%% WHAT IS ACCESS DUDE!!!!!!!
+
+%By using from their neighbors, smaller-users also benefit from low marginal prices and avoid sourcing from non-piped water.  
+% Non-linear pricing helps policymakers achieve both efficiency (by targeting more inelastic households with higher prices) as well as equity (by targeting poorer households with lower prices).
+% excluding many smaller-users from piped water.\footnote{In the model, households can substitute to a vendor option that encompasses all non-piped sources of water, which commonly include deepwells, tanker trucks, and water refilling stations.}
+%The model is designed to match several features from new survey evidence on sharing contracts that I fielded as part of this study.
+%In the context of Manila, I find that the most disadvantaged households are also most likely to fetch water from their neighbors.
+%In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
+% Manila 
+% To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2010 to 2015 with detailed survey data on the number of households and people using each water connection.
+% With comprehensive geographic coverage of half of Manila and a variety of price variation, these data allow for a rich characterization of water demand.
+Additional variation in water source choices identify the relative fixed and marginal costs associated with sharing water with a neighbor.
+% I find that shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.  
+%At the same time, informal sharing networks serve as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
+%  Shared connections record high levels of monthly consumption, which can expose them to high prices when marginal prices increase with usage .
+
+%%% OLD
 
@@
 This section describes an extension of the model to allow for exogenous interruptions in a water source that induce households to substitute toward another water source.
-Exogenous interruptions produce useful variation in the types of water sources used by each household, serving an important role in estimating the hassle costs of transporting water from a neighbor.
+Exogenous interruptions produce useful variation in the types of water sources used by each household, serving an important role in estimating the marginal costs of transporting water from a neighbor.
 Due to shifts in the geology, road construction, or aging infrastructure, households sometimes experience underground breaks in the service pipe between the main line and the water meter.
@@
 This paper demonstrates that pricing policies intended to increase water access especially among the poor can have unintended consequences when low-income households can simply access the piped water network through their neighbors.
+
 The counterfactual exercises find that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water, total welfare, and even welfare among the bottom half of water users.
@@
 Cities may be able to similarly achieve substantial welfare gains by streamlining administrative requirements for new connections and by allowing households to pay connection fees in smaller increments.
+
+In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal water pricing.
+First, I do not directly model environmental, health, or other externalities associated with piped water use.
+Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
+Finally, the counterfactual exercises simulate the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
+Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of using public funding for water infrastructure (\cite{laffont2005regulation}).
 

### 2018-12-06 phil_paper/jmp_wjv.tex
fixing stuff

--- 2018-11-14 phil_paper/jmp_qje.tex
@@
 
-	Public utilities subsidize fixed connection fees with high marginal prices to provide access especially for the poor, but this policy can have the opposite effect when many households share connections.
-Using data on 1.5 million water connections in Manila, I establish that informal sharing networks provide \input{tables/shr_use_from_neighbor}\unskip\%
-	of total access.
-I structurally estimate household water demand across three sources: purchasing directly from the provider, sharing with a neighbor's tap, or buying from a small-scale vendor.
-The model predicts that low fixed fees and high marginal prices decrease access by weakening incentives to share water.
-In contrast, the optimal pricing policy features a high fixed fee and low marginal price, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
+	In developing cities, high costs of connecting to piped water lead many households to use low-quality, non-piped sources.
+In response, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
+This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for these pricing strategies.
+With microdata from 1.5 million water connections in Manila, I structurally estimate water demand in the presence of water sharing and solve the city's pricing problem.
+I find that high marginal prices weaken incentives to share water between neighbors.
+In contrast, the optimal pricing policy features high fixed and low marginal prices, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
+
+% 	However, I find that these prices
+
+% I find that
+
+% 	In particular, I find that high marginal prices weaken incentives to share connections,
+
+% 	access and welfare by weakening incentives to share water.
+
+% 	or share with their neighbors' connections.
+
+% 	.  I then analyze the regulator's pricing problem: choosing fixed and marginal prices to maximize welfare while covering costs.
+
+% 	With these estimates, I find that the presence of sharing reverses
+
+% 	At the same time, cities must choose relative fixed and marginal prices cover production costs by ,
+
+% 	which have large implications for piped water access and usage.  Cities often subsidize
+
+% 	 low fixed and high marginal prices to offset other connection costs and provide access especially for the poor; however, I find that
+
+% 	often leading them to use from low-quality vendors or share with their neighbors' connections.
+
+% 	In developing cities, households face many costs of connecting to piped water, often leading them to use from low-quality vendors or share with their neighbors' connections.
+At the same time, many cities must set prices to cover production costs.
+
+% 	Many cities respond by adjusting fixed and marginal prices to ensure access while covering costs.
+
+% 	To ensure piped water access, cities are often constrained to adjusting fixed and marginal prices while covering production costs.
+
+% 	The primary way cities can respond is by  setting fixed and marginal prices still
+
+% 	respond by adjusting the fixed and marginal prices
+
+% 	Since water utilities must often cover their costs, cities are constrained to
+
+% 	With data from 1.5 million water connections in Manila, I structurally estimate household water demand to analyze optimal fixed and marginal prices for piped water in the presence of water sharing.
+Cities often set low fixed and high marginal prices to offset other connection costs and provide access especially for the poor; however, I find that
+
+% 	To offset connection costs, cities often subsidize the fixed price with high marginal prices
+
+% 	 to provide access especially for the poor; however,
+
+% 	Using data on 1.5 million water connections in Manila, I structurally estimate household water demand across three sources: purchasing directly from the provider, sharing with a neighbor's tap, or buying from a small-scale vendor.
+
+% to maximize welfare while covering their costs
+
+% 	This paper analyzes how
+
+% 	To offset these connection costs, cities often subsidize their fixed connection fees with high marginal prices to provide access especially for the poor; however,
+
+% 	Public utilities choose fixed and marginal prices to recover costs.
+
+% 	This paper analyzes the welfare effects of pricing policies for piped water in the presence of water sharing.
+
+% 	Public utilities subsidize fixed connection fees with high marginal prices to provide access especially for the poor.
+
+% 	 but this policy can have the opposite effect when many households share connections.
+
+% 	The model predicts that low fixed fees and high marginal prices decrease access and welfare by weakening incentives to share water.
+
+% 	In contrast, the optimal pricing policy features a high fixed fee and low marginal price, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
+
+% 	I establish that informal sharing networks provide \input{tables/shr_use_from_neighbor}\unskip\% 
+% 	of total piped water access.
 
@@
  % To ensure widespread access while covering costs, a 
-Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  However, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
-While external health and other benefits may merit subsidizing piped water, government subsidies are often limited by high costs of public funds and risk of regulatory capture in these countries (\cite{laffont2005regulation}).
+Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  Yet, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
+While external health and other benefits may merit subsidizing piped water, any subsidies are often limited by high costs of public funds and risk of regulatory capture in developing countries (\cite{laffont2005regulation}).
 In many cases, prices must be set to fully recover costs.
-A popular solution is to subsidize upfront connection fees with high marginal prices for monthly usage.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
-Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  Over 70\% of developing cities also increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}).
+To ensure access to piped water while covering costs, cities often subsidize upfront connection fees with high marginal prices for monthly usage.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
+Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  Over 70\% of developing cities increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}).
 \cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.
@@
 
-Land-tenure issues, credit-constraints, and administrative costs often prevent disadvantaged households from purchasing their own connections (\cite{devoto2012happiness}).
+% often increase the costs of purchasing a water connection particularly for disadvantaged households
+
+Insecure land-tenure, credit-constraints, and administrative costs often make it difficult for disadvantaged households to purchase water connections (\cite{devoto2012happiness}).
 Also, many cities maintain high upfront fees despite policy recommendations otherwise (\cite{hoque2013state}).
-As a result, 70\% of African utilities report frequent water sharing between households (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of informal sharing, previous research has not yet examined the importance of informal sharing for optimal pricing policy.
-
-This paper analyzes the welfare effects of pricing policies in the presence of informal water sharing.
+As a result, 70\% of African utilities report frequent water sharing between households (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
+
+This paper integrates sharing behavior into water demand in order to analyze the welfare effects of pricing policies.
 I build a model of household water demand that includes both (1) the upfront choice of whether to purchase a connection, share with a neighbor, or use non-piped sources as well as (2) monthly consumption choices.
-I also collect new survey evidence on informal sharing contracts to inform several features of the model design.
+I also collect new survey evidence on sharing contracts to inform several features of the model design.
 The structural estimation leverages administrative data from 1.5 million water connections in Manila from 2010 to 2015, which link to additional survey data on households sharing connections.
@@
 In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
-Instead, these households substitute toward non-piped water sources, which have lower marginal prices, but varying quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
-The model collapses all non-piped sources into a single ``vendor'' option.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access and welfare even for smaller users.
+Instead, these households substitute toward non-piped water sources, which have lower marginal prices, but varying quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access and welfare even for smaller users.
 High fixed fees are paid in full by households who connect individually and are split between sharing households.
-Informal sharing arrangements allow small-users to access piped water from their neighbors for even lower marginal prices than those offered by non-piped sources.
+Informal sharing arrangements enable small-users to access piped water from their neighbors for lower marginal prices than those offered by non-piped sources.
 Shared connections also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.\footnote{Cost savings are passed on to consumers through lower prices.}
@@
 time spent fetching from neighbors or reduced pressure from re-piping water) as well as savings from splitting the fixed costs of a connection.
-Measuring demand and sharing costs presents two central challenges: how can we recover household-level demand when we only observe water consumption for each connection, and how can we separately identify the costs of sharing from preferences for water?
+Measuring these features presents two central challenges: how can we recover household-level demand when we only observe water consumption for each connection, and how can we separately identify the costs of sharing and preferences for water?
 The empirical approach addresses these challenges in three steps.
@@
 The first step builds a tractable model of water sharing to estimate household-level demand from monthly usage data for each connection.
-Informed by a new survey, this model embeds how (1) households face challenges in observing each other's monthly demand and (2) households often split the monthly water bill evenly.
+Informed by new survey evidence, this model embeds how (1) households face challenges in observing each other's monthly demand and (2) households often split the monthly water bill evenly.
 These assumptions on sharing behavior ensure that connection-level demand can be expressed as a sum of underlying household demands even in the presence of non-linear prices.
@@
 
-To estimate the marginal costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to neighbors' connections.
+To estimate the marginal costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to their neighbors' connections.
 I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal costs of sharing.
@@
 
-The third step maps the share of households using from each source --- connecting alone, sharing with a neighbor, or using from a non-piped vendor --- into an estimate of each source's relative fixed cost.
+The third step maps the share of households using from each source --- connecting alone, sharing with a neighbor, or using from a non-piped vendor --- into an estimate of each source's relative fixed cost to consumers.
 The empirical approach leverages the assumption that given water preferences (from step one) and marginal sharing costs (from step two), any remaining variation in water source choices must be due to differences in their fixed costs.
 Since sharing decisions are strategic in nature, I specify a simple game where households sequentially choose their sources and agree to split any surplus from sharing.
-This revealed-preference approach to estimating fixed costs is especially relevant in a developing context because on top of the initial connection and monthly service fees, households often face fixed costs that are difficult to observe, including permitting fees, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.
-In fact, I estimate that the connection and service fees account for only around half of the total fixed costs facing households.
-This structural approach complements previous experimental evidence of fixed costs presented in \cite{devoto2012happiness}.
+
+This revealed-preference approach to estimating fixed costs is especially relevant in a developing context because on top of the initial connection and monthly service fees, households often face other fixed costs that are difficult to observe, including permitting fees, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.
+In fact, I estimate that the connection and service fees account for only around half of the total fixed costs.
+This structural approach complements previous experimental evidence of fixed costs by \cite{devoto2012happiness}.
 By considering both source and quantity choices, this model also expands on the demand estimation literature for public utilities that has so far focused almost exclusively on monthly quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
@@
 Next, I compute an optimal tariff schedule to maximize consumer surplus while exactly covering production costs.
-Compared to the current tariff, I find that a simple, two-part tariff characterized by a fixed fee and low, flat marginal price can produce gains on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus.\footnote{With quasi-linear utility, consumer surplus for a given tariff is calculated as the difference between household utility under this tariff and household utility from using the non-piped, vendor option.}  These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections to install and maintain.
-Finally, I compare the optimal tariff with a social tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.
-With sharing, social tariffs are ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, social tariffs achieve substantial redistribution.
+Compared to the current tariff, I find that a simple, two-part tariff characterized by a fixed fee and low, flat marginal price can produce gains on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus.\footnote{With quasi-linear utility, consumer surplus for a given tariff is calculated as the difference between household utility under this tariff and household utility from using the non-piped, vendor option.}  These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections installed and maintained by the utility.
+
+Finally, I compute a tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.
+With sharing, this tariff is ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, this tariff achieves substantial redistribution.
 These findings suggest that informal sharing networks constrain the extent to which non-linear prices can redistribute surplus.
@@
 
-This paper demonstrates that pricing policies intended to increase water access especially among the poor can have unintended consequences when low-income households can simply access the piped water network through their neighbors.
-
-The counterfactual exercises find that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water, total welfare, and even welfare among the bottom half of water users.
-In this counterfactual, high fixed costs of accessing an individual connection allow for sharing networks to play an important role in extending water access despite sizable hassle costs.
-I also find that complex non-linear price schedules are largely ineffective in terms of achieving both efficiency and equity goals when sharing networks are readily available.
-
-Taken together, these results suggest that households may act as efficient subcontractors in redistributing water to their neighbors.
+Observing that ``connection fees are too high, and lump sum upfront payments exclude the poor,'' the Asian Development Bank has argued for steeply increasing water prices and has emphasized that ``the irony of the situation is that the main way to help the poor is to substantially raise tariffs.''\footnote{This quote is from \cite{mcintosh2003asian} pages 40 \& 45.
+The authors advocate for a ``three-block system with the lifeline consumption rate at 0-6 m3 (tariff limited to 5\% of household income for the lowest 10th percentile), consumption of 6-20 m3 charged at a rate to recover all financial costs, and consumption of more than 20 m3 charged at a penalty rate equal to about \$1/m3 (to conserve water)'' (\cite{mcintosh2003asian} p.76).}  In this paper, I show that the presence of informal sharing reverses this common intuition among policymakers: high-fixed fees no longer act as a barrier for low-income households when they can split these fees by sharing with their neighbors.
+Moreover, low marginal prices help to prevent low-income households from substituting toward non-piped, vendor sources.
+
+By capturing demand heterogeneity, the costs of sharing, as well as source choices, the structural model provides additional insights into how a range of non-linear pricing policies affect both access and welfare.
+In the presence of sharing, the model finds that complex non-linear pricing is largely ineffective in achieving either efficiency or equity; sharing provides a resale market, undermining any goals of price discrimination with non-linear pricing.
+The structural model also allows me to forecast how sharing costs affect optimal prices.
+I find that optimal prices balance competing goals of pricing at marginal cost and taxing sharing when it is costly.
+
+In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal water pricing.
+First, I do not directly model environmental, health, or other externalities associated with piped water use.
+Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that the government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
+Finally, the counterfactual exercises simulate the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
+Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of using public subsidies for water infrastructure (\cite{laffont2005regulation}).
+
+Taken together, this paper suggests that households may act as efficient subcontractors in redistributing water to their neighbors.
 Instead of sending trained engineers to install and maintain connections in dense neighborhoods, providers can instead rely on informal networks to extend water distribution.
@@
 
-In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal water pricing.
-First, I do not directly model environmental, health, or other externalities associated with piped water use.
-Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
-Finally, the counterfactual exercises simulate the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
-Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of using public funding for water infrastructure (\cite{laffont2005regulation}).
+%On top of the broad recommendation for high fixed fees and low marginal prices, the structural model also
+
+% lowering fixed fees and increasing block prices to improve access to piped water.
+
+% This paper demonstrates that pricing policies intended to increase water access especially among the poor can have unintended consequences when low-income households can simply access the piped water network through their neighbors.
+
+% The counterfactual exercises find that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water, total welfare, and even welfare among the bottom half of water users.
+In this counterfactual, high fixed costs of accessing an individual connection allow for sharing networks to play an important role in extending water access despite sizable hassle costs.
 

### 2018-12-09 phil_paper/jmp_wjv.tex
matlab est baby steps

@@
 
-%How should public utilities set fixed fees and marginal prices to provide access while covering costs?
-%Why are there fixed vs. marginal?
-%Public utilities recover fixed and marginal costs through a combination of fixed and marginal %prices.
-%WHY CARE?! THE POOR!
-
 	In developing cities, high costs of connecting to piped water lead many households to use low-quality, non-piped sources.
@@
 This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for these pricing strategies.
-With microdata from 1.5 million water connections in Manila, I structurally estimate water demand in the presence of water sharing and solve the city's pricing problem.
-I find that high marginal prices weaken incentives to share water between neighbors.
+With microdata from 1.5 million water connections in Manila, I structurally estimate water demand in the presence of water sharing and solve the regulator's problem: setting prices to maximize consumer surplus while covering production costs.
+I find that low fixed and high marginal prices weaken incentives to share water between neighbors.
 In contrast, the optimal pricing policy features high fixed and low marginal prices, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
-
-% 	However, I find that these prices
-
-% I find that
-
-% 	In particular, I find that high marginal prices weaken incentives to share connections,
-
-% 	access and welfare by weakening incentives to share water.
-
-% 	or share with their neighbors' connections.
-
-% 	.  I then analyze the regulator's pricing problem: choosing fixed and marginal prices to maximize welfare while covering costs.
-
-% 	With these estimates, I find that the presence of sharing reverses
-
-% 	At the same time, cities must choose relative fixed and marginal prices cover production costs by ,
-
-% 	which have large implications for piped water access and usage.  Cities often subsidize
-
-% 	 low fixed and high marginal prices to offset other connection costs and provide access especially for the poor; however, I find that
-
-% 	often leading them to use from low-quality vendors or share with their neighbors' connections.
-
-% 	In developing cities, households face many costs of connecting to piped water, often leading them to use from low-quality vendors or share with their neighbors' connections.
-At the same time, many cities must set prices to cover production costs.
-
-% 	Many cities respond by adjusting fixed and marginal prices to ensure access while covering costs.
-
-% 	To ensure piped water access, cities are often constrained to adjusting fixed and marginal prices while covering production costs.
-
-% 	The primary way cities can respond is by  setting fixed and marginal prices still
-
-% 	respond by adjusting the fixed and marginal prices
-
-% 	Since water utilities must often cover their costs, cities are constrained to
-
-% 	With data from 1.5 million water connections in Manila, I structurally estimate household water demand to analyze optimal fixed and marginal prices for piped water in the presence of water sharing.
-Cities often set low fixed and high marginal prices to offset other connection costs and provide access especially for the poor; however, I find that
-
-% 	To offset connection costs, cities often subsidize the fixed price with high marginal prices
-
-% 	 to provide access especially for the poor; however,
-
-% 	Using data on 1.5 million water connections in Manila, I structurally estimate household water demand across three sources: purchasing directly from the provider, sharing with a neighbor's tap, or buying from a small-scale vendor.
-
-% to maximize welfare while covering their costs
-
-% 	This paper analyzes how
-
-% 	To offset these connection costs, cities often subsidize their fixed connection fees with high marginal prices to provide access especially for the poor; however,
-
-% 	Public utilities choose fixed and marginal prices to recover costs.
-
-% 	This paper analyzes the welfare effects of pricing policies for piped water in the presence of water sharing.
-
-% 	Public utilities subsidize fixed connection fees with high marginal prices to provide access especially for the poor.
-
-% 	 but this policy can have the opposite effect when many households share connections.
-
-% 	The model predicts that low fixed fees and high marginal prices decrease access and welfare by weakening incentives to share water.
-
-% 	In contrast, the optimal pricing policy features a high fixed fee and low marginal price, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
-
-% 	I establish that informal sharing networks provide \input{tables/shr_use_from_neighbor}\unskip\% 
-% 	of total piped water access.
-
-	%This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus.
-
-	% or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income
-
-%	When households frequently share connections, this strategy may reduce access by weakening incentives to share.
-%weaken incentives for households to extend water access to their neighbors through sharing 
-%this strategy may have the opposite effect when connections are frequently shared between households.  
-%	I analyze the welfare impacts of pricing for piped water in a context where households may choose to share their water connections with their neighbors.  
-%	based on first-world experience
-
-	%This policy improves welfare by up to \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.
 
@@
 
-These estimates allow me to solve a standard regulator pricing problem: setting prices to cover fixed and marginal costs while maximizing consumer surplus.
+These estimates allow me to solve a standard constrained regulator pricing problem: setting prices to cover fixed and marginal costs while maximizing consumer surplus.
 I also let the regulator place extra weight on surplus for smaller, poorer users.
 In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
-Instead, these households substitute toward non-piped water sources, which have lower marginal prices, but varying quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access and welfare even for smaller users.
+Instead, these households substitute toward non-piped water sources, which are easy to access, have relatively lower marginal prices, and provide varying water quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
+Without fixed prices, land-tenure requirements, or administrative expenses, these sources often have low costs of access.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access to piped water and welfare even for smaller users.
 High fixed fees are paid in full by households who connect individually and are split between sharing households.
-Informal sharing arrangements enable small-users to access piped water from their neighbors for lower marginal prices than those offered by non-piped sources.
-Shared connections also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.\footnote{Cost savings are passed on to consumers through lower prices.}
-
-The welfare impacts of these pricing policies depend not only on household-level demand, but also on the relative costs of sharing water; these may include both marginal costs (ie.
+Informal sharing arrangements enable small-users to access piped water from their neighbors for relatively lower marginal prices than those offered by non-piped sources.
+By reducing the total number of connections, sharing arrangements also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.\footnote{In this regulatory arrangement, cost savings are passed on to consumers through lower prices.}
+
+The welfare impacts of these pricing policies depend not only on household-level demand, but also on the relative costs of sharing water; these may include both marginal hassle costs (ie.
 time spent fetching from neighbors or reduced pressure from re-piping water) as well as savings from splitting the fixed costs of a connection.
-Measuring these features presents two central challenges: how can we recover household-level demand when we only observe water consumption for each connection, and how can we separately identify the costs of sharing and preferences for water?
+Measuring these features presents two central challenges: how can we recover household-level demand when we observe water consumption for connections serving multiple households, and how can we separately identify the costs of sharing and preferences for water?
 The empirical approach addresses these challenges in three steps.
@@
 Informed by new survey evidence, this model embeds how (1) households face challenges in observing each other's monthly demand and (2) households often split the monthly water bill evenly.
-These assumptions on sharing behavior ensure that connection-level demand can be expressed as a sum of underlying household demands even in the presence of non-linear prices.
+These assumptions on sharing behavior ensure that connection-level demand can be expressed as a simple function of underlying household demands even in the presence of non-linear prices.
 I use variation in the non-linear price schedule (both across and within connections) to identify water demand for each connection before disaggregating preferences to the household-level.
@@
 
-To estimate the marginal costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to their neighbors' connections.
-I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal costs of sharing.
-This exercise recovers sizable marginal costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.\footnote{This revealed-preference approach builds on a descriptive literature that identifies potential sources of water sharing frictions (\cite{whittington1992possible,nauges2006water}).}
-
-The third step maps the share of households using from each source --- connecting alone, sharing with a neighbor, or using from a non-piped vendor --- into an estimate of each source's relative fixed cost to consumers.
+To estimate the marginal hassle costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to their neighbors' connections.
+I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal hassle costs of sharing.
+This exercise recovers sizable marginal hassle costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.\footnote{This revealed-preference approach builds on a descriptive literature that identifies potential sources of water sharing frictions (\cite{whittington1992possible,nauges2006water}).}
+
+The third step maps the share of households using from each source --- connecting alone, sharing with a neighbor, or using from a non-piped source --- into an estimate of each source's relative fixed cost to consumers.
 The empirical approach leverages the assumption that given water preferences (from step one) and marginal sharing costs (from step two), any remaining variation in water source choices must be due to differences in their fixed costs.
@@
 I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.
-This policy actually reduces access by incentivizing households to substitute toward non-piped vendors.
+This policy actually reduces access because households stop sharing connections and substitute towards non-piped sources.
 Next, I compute an optimal tariff schedule to maximize consumer surplus while exactly covering production costs.
@@
 These findings suggest that informal sharing networks constrain the extent to which non-linear prices can redistribute surplus.
-
-%Yet, since sharing involves costly redistribution of water, the optimal tariff subsidizes individual connections on the margin by pricing above marginal cost and setting the fixed fee below the cost of installing and maintaining each connection.
-
-% analyzes a quasi-experiment where households face leaks in their service pipes, forcing them to substitute to a neighbor's connection.
-
-% The model maps the extent to which these households are able to offset their consumption to a neighbor's connection into an estimate of the marginal costs of fetching water.
-This exercise recovers sizable sharing costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.
-This quasi-experimental approach builds on a descriptive literature pointing to potential costs of sharing water (\cite{whittington1992possible,nauges2006water}).
-
-% In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
-Time spent fetching water or reduced pressure-levels from informally re-piping both increase the marginal cost of sharing.
-%--- what is the relative fixed cost of
-
-%combines monthly usage to recover household-level demand.
-% recover household-level from connection usage,
-
-% I develop a simple model of the water sharing contract that captures two key features of these relationships informed by survey data:
-
-% The model characterizes monthly consumption choices when households face non-linear budget constraints and imperfect control over their exact consumption levels.
-
-% Greater demand heterogeneity increases the scope for usage-based price discrimination to both redistribute surplus and efficiently raise revenue.
-
-% Sharing costs determine how households can respond by changing their water source alongside their consumption patterns.
-
-%  while low sharing costs allow households
-
-% To evaluate the impacts of different pricing policies, I build a model of household water demand that includes both initial source choices as well as monthly consumption choices.
-
-%For sharing households, I develop a simple model of the water sharing contract that captures two key features of these relationships: (1) households face challenges in observing each other's demand and (2) households often split the monthly water bill evenly.
-The model characterizes monthly consumption choices when households face non-linear budget constraints and imperfect control over their exact consumption levels.
-This approach extends previous models of optimization over non-linear budget constraints by allowing households to anticipate unobserved shocks to their demand (\cite{moffitt1986econometrics,burtless1978effect}).
-
-% The estimation combines water source and consumption decisions to structurally recover preferences and unobserved costs of water sharing.
-To include reduced-form approaches to identification within the context of a structural model, I divide the estimation into three steps.
-The first step uses variation in the non-linear price schedule (both across and within households) to identify water demand for each household using monthly consumption data.
-
-%substitute away from sharing arrangements toward both individual connections and
-%This policy reduces access by incentivizing households to substitute away from sharing arrangements toward both individual connections and water vendors (which mainly include deepwells and water refilling stations).
-
-%features a much lower fixed fee and higher marginal price and redistributes substantial surplus to low users as compared to the optimal tariff.
-
-%features a slightly lower fixed fee and higher marginal price, produces universal access to piped water and reduces sharing, but reallocates little consumer surplus to low-demand households.
-
-%and increasing marginal prices; it also increases access and efficiently redistributes consumer surplus to low users as compared the optimal tariff.
-These results provide evidence that the presence of informal sharing networks constrains pricing policy as an effective tool for redistribution.
-
-%The social tariff features a much higher fixed fee and lower marginal price, does not improve access to piped water, and reallocates little consumer surplus to low-demand households at a large cost to average welfare.
-By contrast, in a counterfactual world without sharing, the social tariff features a fixed fee subsidy and increasing marginal prices; it also increases access and efficiently redistributes consumer surplus to low users as compared the optimal tariff.
-These results provide evidence that the presence of informal sharing networks constrains pricing policy as an effective tool for redistribution.
 
@@
 Section~\ref{section:conclusion} concludes.
-
-% Despite the relevance of water sharing arrangements to pricing policy, previous studies have provided either a descriptive analysis of water sharing (\cite{whittington1992possible}) or 
-% in fixed fee incentivizes households to substitute away from water sharing arrangements toward individual connections as well as  , it also increases the share of households using from a local 
-%among low-demand households by as much as \input{tables/discount_low_welfare_change}\unskip\% of monthly income.  
-%%%% WHAT IS ACCESS DUDE!!!!!!!
-
-%By using from their neighbors, smaller-users also benefit from low marginal prices and avoid sourcing from non-piped water.  
-% Non-linear pricing helps policymakers achieve both efficiency (by targeting more inelastic households with higher prices) as well as equity (by targeting poorer households with lower prices).
-% excluding many smaller-users from piped water.\footnote{In the model, households can substitute to a vendor option that encompasses all non-piped sources of water, which commonly include deepwells, tanker trucks, and water refilling stations.}
-%The model is designed to match several features from new survey evidence on sharing contracts that I fielded as part of this study.
-%In the context of Manila, I find that the most disadvantaged households are also most likely to fetch water from their neighbors.
-%In Manila, I establish that 23\% of households access water through a neighbor's connection by connecting plumbing directly to the meter (\input{tables/access_pipes}\unskip\%), extending plastic pipes (\input{tables/access_single_tap}\unskip\%), or fetching water with containers (\input{tables/access_fetch}\unskip\%).
-% Manila 
-% To measure these features, I merge administrative data covering 1.5 million water connections in Manila from 2010 to 2015 with detailed survey data on the number of households and people using each water connection.
-% With comprehensive geographic coverage of half of Manila and a variety of price variation, these data allow for a rich characterization of water demand.
-Additional variation in water source choices identify the relative fixed and marginal costs associated with sharing water with a neighbor.
-% I find that shared connections allow the city to save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households at low marginal prices.  
-%At the same time, informal sharing networks serve as resale markets for water, undermining the extent to which cities can redistribute surplus through increasing marginal prices.
-%  Shared connections record high levels of monthly consumption, which can expose them to high prices when marginal prices increase with usage .
-
-%%% OLD
-
-%%  This strategy has counterintuitive effects in a context with widespread sharing by subsidizing costs for high
-
-%%  Served by a large, government-regulated water monopoly, Manila provides an ideal setting since over \input{tables/shr_1or2hh}\unskip\% of households share water connections.
-Given many positive health exernalities from access to safe, reliable water (\cite{galiani2005water,gamper2010impact,kremer2011spring}), redesigning pricing regimes to boost access and usage especially among the poor can have significant welfare consequences.
-
-%%  Over 70\% of developing cities have water pricing regimes characterized by high fixed connection fees and marginal prices that increase with monthly usage to cross-subsidize low-income users (\cite{hoque2013state}).
-From a theoretical perspective, the optimal pricing strategy to maximize surplus especially for low-income households while covering costs of production depends on the frictions associated with sharing water.
-These sharing frictions may include time costs fetching water from a neighbor as well as difficulties dividing the monthly water bill among sharing households.
-If sharing frictions are large, policymakers may want to disincentivize sharing by implementing a low fixed fee and increasing the marginal price schedule.
-On the other hand if sharing frictions are small, policymakers may instead use a high fixed fee and alongside a decreasing marginal price schedule in order to encourage sharing networks, set marginal prices closer to marginal costs, and minimize the number of connections that would need to be installed.
-This paper provides empirical estimates of these sharing frictions in an effort to guide these pricing decisions.
-
-%%  From a theoretical perspective, the impacts of this pricing regime depend on the frictions associated both with sharing water as well as connecting to the network.
-These sharing frictions may include time costs fetching water from a neighbor as well as difficulties dividing the monthly water bill among sharing households.
-If sharing frictions are high, policymakers may want to disincentivize sharing by implementing a low fixed fee and increasing marginal price schedule.
-COME BACK TO THIS ISSUE: DO I WANT TO GET INTO OPTIMAL SO SOON!?
-NOT SURE....
-
-%%  While low-cost sharing networks constrain the set of efficient pricing strategies available to the regulator, these networks ultimately improve welfare for low-income households by providing an additional mechanism for these households to access low-cost piped water.
-
-%%  This paper contributes most directly to an expanding literature on estimating demand for public utilities in developing countries, including water in South Africa (\cite{szabo2015value}) and C{\^o}te d'Ivoire (\cite{diakite2009proposal}) and electricity in Colombia (\cite{mcrae2014infrastructure}).
-Previous work has focused on how pricing affects monthly consumption decisions.
-This paper extends these models by allowing households to also choose their initial water source.
-By structurally modeling source choice, this paper also connects to a small reduced-form literature that emphasizes the importance of fixed costs associated with connecting to a piped water network (\cite{devoto2012happiness,jimenez2014factors,kayaga2007costs}).
 
@@
 
-Observing that ``connection fees are too high, and lump sum upfront payments exclude the poor,'' the Asian Development Bank has argued for steeply increasing water prices and has emphasized that ``the irony of the situation is that the main way to help the poor is to substantially raise tariffs.''\footnote{This quote is from \cite{mcintosh2003asian} pages 40 \& 45.
-The authors advocate for a ``three-block system with the lifeline consumption rate at 0-6 m3 (tariff limited to 5\% of household income for the lowest 10th percentile), consumption of 6-20 m3 charged at a rate to recover all financial costs, and consumption of more than 20 m3 charged at a penalty rate equal to about \$1/m3 (to conserve water)'' (\cite{mcintosh2003asian} p.76).}  In this paper, I show that the presence of informal sharing reverses this common intuition among policymakers: high-fixed fees no longer act as a barrier for low-income households when they can split these fees by sharing with their neighbors.
+Observing that ``connection fees are too high, and lump sum upfront payments exclude the poor,'' the Asian Development Bank has argued for cutting upfront payments and steeply increasing water prices, emphasizing that ``the irony of the situation is that the main way to help the poor is to substantially raise tariffs.''\footnote{This quote is from \cite{mcintosh2003asian} pages 40 \& 45.
+The authors advocate for a ``three-block system with the lifeline consumption rate at 0-6 m3 (tariff limited to 5\% of household income for the lowest 10th percentile), consumption of 6-20 m3 charged at a rate to recover all financial costs, and consumption of more than 20 m3 charged at a penalty rate equal to about \$1/m3 (to conserve water)'' (\cite{mcintosh2003asian} p.76).}  In this paper, I show that the presence of informal sharing reverses this common intuition among policymakers: high-fixed fees are less of a barrier for low-income households when they can split these fees by sharing with their neighbors.
 Moreover, low marginal prices help to prevent low-income households from substituting toward non-piped, vendor sources.
@@
 For example, price discriminating according to neighborhood income instead of by monthly usage levels may achieve similar goals of redistribution without distorting sharing networks.
-While this policy may not be appropriate in Manila since neighborhoods are often very heterogeneous in income, this approach may work well in other contexts where neighborhoods are more segregated, such as in Colombia where electricity rates vary according to the social category of each neighborhood (\cite{mcrae2014infrastructure}).
-
-Since sharing networks constrain the menu of pricing policies available to policymakers, cities may benefit from considering a broader range of policies to improve welfare from water use.
+While this policy may not be appropriate in Manila since neighborhoods are often very heterogeneous in income, this approach may work well in other contexts where neighborhoods are more segregated.\footnote{For example in Colombia, electricity rates vary according to the social category of each neighborhood (\cite{mcrae2014infrastructure}).}
+
+Since sharing networks make usage-based price discrimination more difficult, cities may benefit from considering a broader range of policies to improve welfare from water use.
 For example, cities may be able to lower the frictions associated with these sharing networks by providing technical resources for managing plumbing networks or distributing extra water meters to assist households in accurately splitting the bill.

### 2018-12-13 phil_paper/jmp_wjv.tex
jmp fixes for qje reject

@@
 In response, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
-This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for these pricing strategies.
-With microdata from 1.5 million water connections in Manila, I structurally estimate water demand in the presence of water sharing and solve the regulator's problem: setting prices to maximize consumer surplus while covering production costs.
+This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for optimal water pricing.
+With microdata from 1.5 million water connections in Manila, I structurally estimate water demand in the presence of water sharing and solve the regulator's problem: setting prices to maximize consumer surplus while funding production costs.
 I find that low fixed and high marginal prices weaken incentives to share water between neighbors.
@@
 
-These estimates allow me to solve a standard constrained regulator pricing problem: setting prices to cover fixed and marginal costs while maximizing consumer surplus.
+These estimates allow me to solve a standard regulator pricing problem: setting prices to cover fixed and marginal costs while maximizing consumer surplus.
 I also let the regulator place extra weight on surplus for smaller, poorer users.
 In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
-Instead, these households substitute toward non-piped water sources, which are easy to access, have relatively lower marginal prices, and provide varying water quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
-Without fixed prices, land-tenure requirements, or administrative expenses, these sources often have low costs of access.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access to piped water and welfare even for smaller users.
+Instead, these households substitute toward non-piped water sources, which have relatively lower marginal prices, zero upfront costs, and varying water quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
+Without fixed prices, land-tenure requirements, or administrative expenses, these sources often have low costs of access.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access to piped water and welfare, even for smaller users.
 High fixed fees are paid in full by households who connect individually and are split between sharing households.
@@
 To estimate the marginal hassle costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to their neighbors' connections.
-I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal hassle costs of sharing.
-This exercise recovers sizable marginal hassle costs on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.\footnote{This revealed-preference approach builds on a descriptive literature that identifies potential sources of water sharing frictions (\cite{whittington1992possible,nauges2006water}).}
+I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal hassle costs of sharing per cubic meter of usage.
+This exercise recovers sizable marginal hassle costs per cubic meter on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.\footnote{This revealed-preference approach builds on a descriptive literature that identifies potential sources of water sharing frictions (\cite{whittington1992possible,nauges2006water}).}
 
@@
 Since sharing decisions are strategic in nature, I specify a simple game where households sequentially choose their sources and agree to split any surplus from sharing.
+By considering both source and quantity choices, this model expands on the demand estimation literature for public utilities that has so far focused almost exclusively on monthly quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
 
 This revealed-preference approach to estimating fixed costs is especially relevant in a developing context because on top of the initial connection and monthly service fees, households often face other fixed costs that are difficult to observe, including permitting fees, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.
-In fact, I estimate that the connection and service fees account for only around half of the total fixed costs.
+In fact, I estimate that the fixed fees paid to the provider (connection and service fees) account for only around half of the total fixed costs.
 This structural approach complements previous experimental evidence of fixed costs by \cite{devoto2012happiness}.
-By considering both source and quantity choices, this model also expands on the demand estimation literature for public utilities that has so far focused almost exclusively on monthly quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
 
@@
 First, I consider a connection fee subsidy policy consistent with recommendations from the World Bank, NGOs, and other researchers to improve water access for the poor (\cite{komives2005water,jimenez2014factors,mcintosh2003asian}).
-I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensuring that the water provider exactly covers costs.
+I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensure that the water provider exactly covers costs.
 This policy actually reduces access because households stop sharing connections and substitute towards non-piped sources.
@@
 With sharing, this tariff is ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, this tariff achieves substantial redistribution.
-These findings suggest that informal sharing networks constrain the extent to which non-linear prices can redistribute surplus.
+These findings suggest that informal sharing networks may constrain the extent to which non-linear prices can redistribute surplus.
 
@@
 \centering
-\caption{Water Tariff in Manila}\label{figure:tariff}
+\caption{Marginal Prices in Manila}\label{figure:tariff}
 \begin{center}
@@
 By capturing demand heterogeneity, the costs of sharing, as well as source choices, the structural model provides additional insights into how a range of non-linear pricing policies affect both access and welfare.
-In the presence of sharing, the model finds that complex non-linear pricing is largely ineffective in achieving either efficiency or equity; sharing provides a resale market, undermining any goals of price discrimination with non-linear pricing.
+In the presence of sharing, the model finds that complex non-linear pricing is largely ineffective at achieving efficiency and equity gains because sharing provides a water resale market, undermining any usage-based price discrimination.
 The structural model also allows me to forecast how sharing costs affect optimal prices.
-I find that optimal prices balance competing goals of pricing at marginal cost and taxing sharing when it is costly.
+I find that optimal prices balance competing goals of pricing at marginal cost and taxing sharing when it is too costly.
 
@@
 
-Since sharing networks make usage-based price discrimination more difficult, cities may benefit from considering a broader range of policies to improve welfare from water use.
+Since sharing networks make it more difficult to implement usage-based price discrimination, cities may benefit from considering a broader range of policies to improve welfare from piped water use.
 For example, cities may be able to lower the frictions associated with these sharing networks by providing technical resources for managing plumbing networks or distributing extra water meters to assist households in accurately splitting the bill.

### 2019-01-29 phil_paper/paper_wjv.tex
new motivation (pre-stef)

--- 2018-12-13 phil_paper/jmp_wjv.tex
@@
 
-	In developing cities, high costs of connecting to piped water lead many households to use low-quality, non-piped sources.
-In response, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
-This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for optimal water pricing.
-With microdata from 1.5 million water connections in Manila, I structurally estimate water demand in the presence of water sharing and solve the regulator's problem: setting prices to maximize consumer surplus while funding production costs.
-I find that low fixed and high marginal prices weaken incentives to share water between neighbors.
-In contrast, the optimal pricing policy features high fixed and low marginal prices, increases shared connections, and ensures nearly universal access to piped water compared to current prices in Manila.
+%	High costs of connecting to public utilities often
+
+%	lead households to share a connection with their neighbors instead of purchasing their own connection.
+
+	Households often share connections to public utilities with their neighbors in order to split set-up and maintenance costs.
+This paper analyzes how sharing connections affects optimal pricing for water utilities.
+With microdata from 1.5 million water connections in Manila, I estimate water demand in the presence of water sharing and solve for prices that maximize consumer surplus while funding production costs.
+In practice, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
+Instead, the optimal policy uses high fixed prices to cover costs and low marginal prices to encourage greater consumption.
+Sharing households split fixed prices and enjoy inexpensive piped water with their neighbors instead of using low-quality, non-piped water.
+Counterfactual exercises find increases in shared connections, total piped water consumption, and social welfare from optimal prices compared to current prices in Manila.
+
+%	Yet, I find that low fixed and high marginal prices also weaken incentives to share water between neighbors.
+
+%	Shared connections may have large implications for optimal pricing for public utilities especially 
+%	Households often offset the costs of connecting to public utilities by sharing a connection with their neighbors.  
+%	Sharing neighbor's connections 
+% In developing cities, high costs of connecting to piped water lead many households to use low-quality, non-piped sources.  
+% In response, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.  
+% This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for optimal water pricing.
 
@@
  % To ensure widespread access while covering costs, a
+
+%  For example, when households can easily share connections, public utilities can charge larger upfront fees for the same levels of access as when sharing is .  [UNCLEAR COMPARISON!!]
+
+% Households also share connections to public utilities with their neighbors (piped water, electricity, mobile phones, etc.) especially in developing countries.\footnote{70\% of African water utilities report frequent sharing of water taps between households.
+Over 14\% of urban households in Arba-Minch, Ethiopia report sourcing electricity from their neighbors instead of purchasing directly from the utility (\cite{mustefa2016energy}).
+In South Africa as of 2012, 11.9\% of the population report sharing their mobile phone with others.
+This percentage jumps to 19.9\% among those living in poverty (\cite{calandro2012mobile}).}
+
+% Connection sharing can have important implications for the optimal balance of fixed and marginal prices for these services.
+
+% Understanding how this sharing behavior may affect optimal prices may have large consequences for public policy since governments actively regulate prices charged by public utilities.
+
+% In developing countries, households often 
+% Faced with fixed costs of accessing a good or service, consumers are increasingly .  
+% In developing countries, these .
+
+Faced with high fixed costs of purchasing and maintaining durable goods, consumers often share these goods with each other.
+While online platforms have accelerated peer-to-peer rentals of cars, apartments, and storage space (\cite{horton2016owning}), households in developing countries often share connections to public utilities like water and electricity with their neighbors.\footnote{70\% of African water utilities report frequent sharing of water taps between households.
+Over 14\% of urban households in Arba-Minch, Ethiopia report sourcing electricity from their neighbors instead of purchasing directly from the utility (\cite{mustefa2016energy}).
+In South Africa as of 2012, 11.9\% of the population report sharing their mobile phone with others.
+This percentage jumps to 19.9\% among those living in poverty (\cite{calandro2012mobile}).}  Sharing can have large consequences for optimal pricing, particularly for public utilities.
+Public utility pricing is especially salient in developing countries because prices must often be set to fully cover costs (\cite{laffont2005regulation}) and because prices determine not only monthly consumption, but also which households can access these basic services.
+For example, when households cannot share connections, they may prefer relatively low fixed prices (ie.
+installation and maintenance fees) so that each household can afford a connection and high marginal prices (ie.
+prices per gallon or watt) to cover production costs.
+However, when households can easily share connections, they may prefer splitting high fixed prices with their neighbors and enjoying low marginal prices from shared connections.
+%The optimal pricing policy depends both on consumer demand and on the costs of sharing connections between neighbors.
+
+This paper focuses empirically on pricing piped water in Manila, Philippines to increase access and welfare when households share connections.
 Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  Yet, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
-While external health and other benefits may merit subsidizing piped water, any subsidies are often limited by high costs of public funds and risk of regulatory capture in developing countries (\cite{laffont2005regulation}).
-In many cases, prices must be set to fully recover costs.
+While external health and other benefits may merit subsidizing piped water, any subsidies to public utilities are often limited by high costs of public funds and risk of regulatory capture in developing countries (\cite{laffont2005regulation}).
+
 To ensure access to piped water while covering costs, cities often subsidize upfront connection fees with high marginal prices for monthly usage.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
@@
 The statistic comes from author calculations with data kindly provided by \cite{hoque2013state}.}  These pricing approaches have been shown to work well when each water connection serves a single household.
-Recent empirical papers in South Africa and C{\^o}te d'Ivoire predict gains in both access and total welfare from increasing marginal prices (\cite{szabo2015value,diakite2009proposal}).
+Recent empirical papers in C{\^o}te d'Ivoire and South Africa predict gains in both access and total welfare from increasing marginal prices (\cite{diakite2009proposal,szabo2015value}).
 However, many households in developing cities share connections with their neighbors, which can have large implications for water pricing.
 
+Insecure land-tenure, credit-constraints, and administrative costs often make it difficult for disadvantaged households to purchase their own water connections (\cite{devoto2012happiness}).
+As a result, households frequently share connections ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
+
 % often increase the costs of purchasing a water connection particularly for disadvantaged households
-
-Insecure land-tenure, credit-constraints, and administrative costs often make it difficult for disadvantaged households to purchase water connections (\cite{devoto2012happiness}).
-Also, many cities maintain high upfront fees despite policy recommendations otherwise (\cite{hoque2013state}).
-As a result, 70\% of African utilities report frequent water sharing between households (\cite{keener2010provision}) ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
+% Also, many cities maintain high upfront fees despite policy recommendations otherwise (\cite{hoque2013state}).
 

### 2019-01-31 phil_paper/paper_wjv.tex
new motivation (post-stef)

@@
 
-\usepackage[notablist,nofiglist]{endfloat}
+%\usepackage[notablist,nofiglist]{endfloat}
+
 %\renewcommand{\efloatseparator}{\mbox{}}
@@
 
+%This paper analyzes how sharing connections affects optimal pricing for water utilities.
+
 	Households often share connections to public utilities with their neighbors in order to split set-up and maintenance costs.
-This paper analyzes how sharing connections affects optimal pricing for water utilities.
-With microdata from 1.5 million water connections in Manila, I estimate water demand in the presence of water sharing and solve for prices that maximize consumer surplus while funding production costs.
+With microdata from 1.5 million water connections in Manila, this paper estimates water demand when connections are shared and solves the regulator's problem: setting prices that maximize consumer surplus while covering production costs.
 In practice, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
-Instead, the optimal policy uses high fixed prices to cover costs and low marginal prices to encourage greater consumption.
-Sharing households split fixed prices and enjoy inexpensive piped water with their neighbors instead of using low-quality, non-piped water.
-Counterfactual exercises find increases in shared connections, total piped water consumption, and social welfare from optimal prices compared to current prices in Manila.
+Instead, the optimal policy covers production costs with high fixed prices, which are split between sharing households, and sets low marginal prices to encourage consumption.
+Counterfactual exercises find increases in shared connections, total piped water consumption, and social welfare from the optimal policy compared to current prices in Manila.
+
+%Sharing households split fixed prices with their neighbors to access the low marginal prices.
 
@@
 This percentage jumps to 19.9\% among those living in poverty (\cite{calandro2012mobile}).}  Sharing can have large consequences for optimal pricing, particularly for public utilities.
-Public utility pricing is especially salient in developing countries because prices must often be set to fully cover costs (\cite{laffont2005regulation}) and because prices determine not only monthly consumption, but also which households can access these basic services.
+This paper focuses empirically on pricing for piped water in Manila, Philippines in order to increase access and welfare when households share connections.
+
+Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  Yet, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
+While external health and other benefits may merit subsidizing piped water, any subsidies to public utilities are often limited by high costs of public funds and risk of regulatory capture in developing countries (\cite{laffont2005regulation}).
+In many cases, prices must be set to fully recover costs.
+
+%Instead of piped water, these households often resort to local deepwells or water vendors.  CITE THE ADB HERE!
+
+%Public utility pricing is especially salient in developing countries because prices must often be set to fully cover costs (\cite{laffont2005regulation}) and because prices determine not only monthly consumption, but also which households can access these basic services.
 For example, when households cannot share connections, they may prefer relatively low fixed prices (ie.
@@
 %The optimal pricing policy depends both on consumer demand and on the costs of sharing connections between neighbors.
-
-This paper focuses empirically on pricing piped water in Manila, Philippines to increase access and welfare when households share connections.
-Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  Yet, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
-While external health and other benefits may merit subsidizing piped water, any subsidies to public utilities are often limited by high costs of public funds and risk of regulatory capture in developing countries (\cite{laffont2005regulation}).
 
@@
 Insecure land-tenure, credit-constraints, and administrative costs often make it difficult for disadvantaged households to purchase their own water connections (\cite{devoto2012happiness}).
-As a result, households frequently share connections ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
+As a result, households frequently share connections including fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) and drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
 
@@
 In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
-Instead, these households substitute toward non-piped water sources, which have relatively lower marginal prices, zero upfront costs, and varying water quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
-Without fixed prices, land-tenure requirements, or administrative expenses, these sources often have low costs of access.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access to piped water and welfare, even for smaller users.
+Instead, these households substitute toward non-piped water sources, which have relatively lower marginal prices, zero upfront costs, and varying water quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access to piped water and welfare, even for smaller users.
 High fixed fees are paid in full by households who connect individually and are split between sharing households.
@@
 By reducing the total number of connections, sharing arrangements also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.\footnote{In this regulatory arrangement, cost savings are passed on to consumers through lower prices.}
+%  Without fixed prices, land-tenure requirements, or administrative expenses, these sources often have low costs of access.
 
@@
 With sharing, this tariff is ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, this tariff achieves substantial redistribution.
-These findings suggest that informal sharing networks may constrain the extent to which non-linear prices can redistribute surplus.
+These findings suggest that informal sharing networks may constrain the extent to which non-linear prices can redistribute consumer surplus.
 
@@
 This paper focuses on one of the providers which serves 1.5 million connections and around 5 million people.
-Figure~\ref{figure:tariff} shows the regulated tariff in Manila.
-The increasing marginal price is thought to cross-subsidize consumption among low-demand, poorer households through higher bills from large users.
+Figure~\ref{figure:tariff} shows the regulated tariff in Manila.\footnote{Marginal prices continue increasing gradually at 20 m3 intervals above 50 m3, which are not pictured in Figure~\ref{figure:tariff}.
+Appendix~\ref{appendix:connectionfeeamortization} includes the full tariff as presented to consumers.}  The increasing marginal price is thought to cross-subsidize consumption among low-demand, poorer households through higher bills from large users.
 The regulator assigns zero marginal price to the first 10 cubic meters of monthly usage, which is called the ``lifeline'' rate.
@@
 \centering
-\caption{Marginal Prices in Manila}\label{figure:tariff}
+\caption{Tariff in Manila}\label{figure:tariff}
 \begin{center}
 \includegraphics[scale=.7]{tables/tariff_structure.pdf}\\
-\footnotesize{1 USD = 50 PhP}
+\footnotesize{Figure includes average marginal prices from 2010 to 2015. \\  1 USD $\sim$ 50 PhP}
 \end{center}
@@
 First, the non-linear pricing structure given by Figure~\ref{figure:tariff} forces households to decide whether to consume above or below tariff kink points as they face monthly shocks to their demand.
+Although the full tariff schedule includes seven segments as described in Figure~\ref{figure:tarifftrue} in Appendix~\ref{appendix:connectionfeeamortization}, the model includes only the first four tariff segments, applying the fourth tariff segment to all greater consumption levels.
+Any biases caused by this assumption may be limited both because households rarely consume above 60 m3 per month and because marginal prices increase gradually at higher levels of consumption.
+Also, the estimation abstracts away from a discrete increase in the fixed fee that occurs for consumption above 10 m3 per month as shown in Figure~\ref{figure:tarifftrue} in Appendix~\ref{appendix:connectionfeeamortization}.
+Taken together, these limitations may lead the model to overestimate price elasticities since some households may be responding to higher marginal prices than those included in the model.
+
 Second, regulated tariff changes over time affecting all households generate time-series variation in the tariff, which can be seen in Appendix~\ref{appendix:tariffvariation}.
@@
 
-\section{Connection Fee}\label{appendix:connectionfeeamortization}
-
-This section constructs a total fee paid to the water provider each month as the sum of the monthly service fee, 150 PhP/month on average, and the connection fee of 6,000 PhP, amortized over the duration of the water connection.
+\section{Tariff and Fee Structure}\label{appendix:connectionfeeamortization}
+
+\begin{figure}
+\caption{Residential Tariff Presented to Consumers}\label{figure:tarifftrue}
+\begin{center}
+\includegraphics[scale=.8]{tables/tariff_pic_png.png} \\
+\footnotesize{``conn.'' refers to connection, ``cu.m.'' refers to cubic meters of usage \\ per month, and \textbf{P} refers to Philippine Pesos.}
+\end{center}
+\end{figure}
+
+Figure~\ref{figure:tarifftrue} includes the current tariff as it is presented to consumers.
+The average total fee paid to the water provider each month includes the sum of the monthly service fee, 150 PhP/month on average between 2010 and 2015 (including water meter replacement charges and disconnection and reconnection fees not listed in Figure~\ref{figure:tarifftrue}), and the connection fee of 6,000 PhP, amortized over the duration of the water connection.
+%Although the fixed fee listed on the bill increases for households consuming above 10 m3 as indicated in Figure~\ref{figure:tarifftrue}, the empirical strategy assumes one fixed fee at this higher level
+%includes the fixed fee for households using above 10 m3 in the calculation since the bulk of
+
 To amortize the connection fee without information on full durations of residence for all households, I assume that households move to Manila, use a water connection for 80 months, then leave the city.

### 2019-02-01 phil_paper/paper_wjv.tex
restud

@@
 
-%\usepackage[notablist,nofiglist]{endfloat}
+\usepackage[notablist,nofiglist]{endfloat}
 
@@
 \usepackage{natbib}  
-%\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
-\title{OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
+\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
+%\title{OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
 
@@
 
+%like water and electricity
+
 Faced with high fixed costs of purchasing and maintaining durable goods, consumers often share these goods with each other.
-While online platforms have accelerated peer-to-peer rentals of cars, apartments, and storage space (\cite{horton2016owning}), households in developing countries often share connections to public utilities like water and electricity with their neighbors.\footnote{70\% of African water utilities report frequent sharing of water taps between households.
+While online platforms have accelerated peer-to-peer rentals of cars, apartments, and storage space (\cite{horton2016owning}), households in developing countries often share connections to public utilities with their neighbors.\footnote{70\% of African water utilities report frequent sharing of water taps between households.
 Over 14\% of urban households in Arba-Minch, Ethiopia report sourcing electricity from their neighbors instead of purchasing directly from the utility (\cite{mustefa2016energy}).
@@
 This percentage jumps to 19.9\% among those living in poverty (\cite{calandro2012mobile}).}  Sharing can have large consequences for optimal pricing, particularly for public utilities.
-This paper focuses empirically on pricing for piped water in Manila, Philippines in order to increase access and welfare when households share connections.
-
+This paper focuses empirically on pricing for piped water when households share connections.
 Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  Yet, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
@@
 Insecure land-tenure, credit-constraints, and administrative costs often make it difficult for disadvantaged households to purchase their own water connections (\cite{devoto2012happiness}).
-As a result, households frequently share connections including fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) and drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
+As a result, households frequently share connections by fetching from neighbors with hoses and buckets like in Tangiers, Morocco (\cite{devoto2012happiness}) and drawing from single taps that serve many dwellings like in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
 

### 2020-05-12 phil_paper/paper_booster_pumps_wjv.tex
pressure running

--- 2019-01-29 phil_paper/paper_wjv.tex
@@
 
-\usepackage[notablist,nofiglist]{endfloat}
+% \usepackage[notablist,nofiglist]{endfloat}
+
 %\renewcommand{\efloatseparator}{\mbox{}}
 
-\renewcommand{\thetable}{\Roman{table}}
-\renewcommand{\thefigure}{\Roman{figure}}
+% \renewcommand{\thetable}{\Roman{table}}
+% \renewcommand{\thefigure}{\Roman{figure}}
 
-\renewcommand{\thesection}{\Roman{section}} 
-\renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
-\renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
+% \renewcommand{\thesection}{\Roman{section}} 
+% \renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
+% \renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
 
@@
 
-\date{November, 2017}
+\date{Current Version: March, 2019}
 \begin{document}
@@
 
-	Households often share connections to public utilities with their neighbors in order to split set-up and maintenance costs.
-This paper analyzes how sharing connections affects optimal pricing for water utilities.
-With microdata from 1.5 million water connections in Manila, I estimate water demand in the presence of water sharing and solve for prices that maximize consumer surplus while funding production costs.
+%This paper analyzes how sharing connections affects optimal pricing for water utilities.
+
+	% Households often share connections to public utilities with their neighbors in order to split set-up and maintenance costs.
+With microdata from 1.5 million water connections in Manila, this paper estimates water demand when connections are shared and solves the regulator's problem: setting prices that maximize consumer surplus while covering production costs.
 In practice, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
-Instead, the optimal policy uses high fixed prices to cover costs and low marginal prices to encourage greater consumption.
-Sharing households split fixed prices and enjoy inexpensive piped water with their neighbors instead of using low-quality, non-piped water.
-Counterfactual exercises find increases in shared connections, total piped water consumption, and social welfare from optimal prices compared to current prices in Manila.
+Instead, the optimal policy covers production costs with high fixed prices, which are split between sharing households, and sets low marginal prices to encourage consumption.
+Counterfactual exercises find increases in shared connections, total piped water consumption, and social welfare from the optimal policy compared to current prices in Manila.
+
+%Sharing households split fixed prices with their neighbors to access the low marginal prices.
 
@@
 \section{Introduction}
- % \footnote{\cite{laffont2005regulation} emphasizes high costs of public funds in developing countries (with a deadweight loss of 2.5 for the Philippines) due to limited ability to enter long-term contracts with government, credit constraints, inefficient taxation, and corruption.}
- % To ensure widespread access while covering costs, a
 
-%  For example, when households can easily share connections, public utilities can charge larger upfront fees for the same levels of access as when sharing is .  [UNCLEAR COMPARISON!!]
+- Discusses use of booster pumps in Clean Water Act 2004:  https://www.manilatimes.net/2018/11/04/legal-advice/dearpao/use-of-booster-pumps/461829/  http://r12.emb.gov.ph/ra-9275-the-philippine-clean-water-act/
 
-% Households also share connections to public utilities with their neighbors (piped water, electricity, mobile phones, etc.) especially in developing countries.\footnote{70\% of African water utilities report frequent sharing of water taps between households.
-Over 14\% of urban households in Arba-Minch, Ethiopia report sourcing electricity from their neighbors instead of purchasing directly from the utility (\cite{mustefa2016energy}).
-In South Africa as of 2012, 11.9\% of the population report sharing their mobile phone with others.
-This percentage jumps to 19.9\% among those living in poverty (\cite{calandro2012mobile}).}
+- https://idl-bnc-idrc.dspacedirect.org/bitstream/handle/10625/14878/108376.pdf?sequence=5
 
-% Connection sharing can have important implications for the optimal balance of fixed and marginal prices for these services.
+- illegal booster pumps :  Consequence of El Niño 1997-98 on Manila water resources: new perspectives in water shortage management
 
-% Understanding how this sharing behavior may affect optimal prices may have large consequences for public policy since governments actively regulate prices charged by public utilities.
-
-% In developing countries, households often 
-% Faced with fixed costs of accessing a good or service, consumers are increasingly .  
-% In developing countries, these .
-
-Faced with high fixed costs of purchasing and maintaining durable goods, consumers often share these goods with each other.
-While online platforms have accelerated peer-to-peer rentals of cars, apartments, and storage space (\cite{horton2016owning}), households in developing countries often share connections to public utilities like water and electricity with their neighbors.\footnote{70\% of African water utilities report frequent sharing of water taps between households.
-Over 14\% of urban households in Arba-Minch, Ethiopia report sourcing electricity from their neighbors instead of purchasing directly from the utility (\cite{mustefa2016energy}).
-In South Africa as of 2012, 11.9\% of the population report sharing their mobile phone with others.
-This percentage jumps to 19.9\% among those living in poverty (\cite{calandro2012mobile}).}  Sharing can have large consequences for optimal pricing, particularly for public utilities.
-Public utility pricing is especially salient in developing countries because prices must often be set to fully cover costs (\cite{laffont2005regulation}) and because prices determine not only monthly consumption, but also which households can access these basic services.
-For example, when households cannot share connections, they may prefer relatively low fixed prices (ie.
-installation and maintenance fees) so that each household can afford a connection and high marginal prices (ie.
-prices per gallon or watt) to cover production costs.
-However, when households can easily share connections, they may prefer splitting high fixed prices with their neighbors and enjoying low marginal prices from shared connections.
-%The optimal pricing policy depends both on consumer demand and on the costs of sharing connections between neighbors.
-
-This paper focuses empirically on pricing piped water in Manila, Philippines to increase access and welfare when households share connections.
-Improving access to piped water can generate substantial health benefits\footnote{\cite{zhang2016long,kosec2014child,gamper2010impact}, and \cite{galiani2005water} focus on health improvements in developing countries while \cite{cutler2005role} look historically at the US.} as well as improvements in household well-being through time savings and reduced intra-household conflict.\footnote{\cite{devoto2012happiness} provide water through a randomized-controlled trial in Morocco finding few health effects but large benefits to household welfare.}  Yet, the share of urban households without piped water has remained stable at 5\% for middle income countries and at 20\% for low income countries (World Bank [2015]).
-While external health and other benefits may merit subsidizing piped water, any subsidies to public utilities are often limited by high costs of public funds and risk of regulatory capture in developing countries (\cite{laffont2005regulation}).
-
-To ensure access to piped water while covering costs, cities often subsidize upfront connection fees with high marginal prices for monthly usage.\footnote{\cite{mcintosh2003asian} and \cite{komives2006distributional} from the World Bank and Asian Development Bank argue for low connection fees.
-Using a randomized controlled trial from Morocco, \cite{devoto2012happiness} confirm that modest assistance with connection fees can lead to increases in new water connections.}  Over 70\% of developing cities increase marginal prices with monthly usage so that large users cross-subsidize access and usage for smaller, poorer users.\footnote{This strategy is also commonly referred to as ``Increasing Block Tariffs'' or  ``Convex Pricing'' (\cite{borenstein2012redistributional}).
-\cite{hoque2013state} and \cite{boland2000political} provide overviews of the use of increasing marginal prices in the water sector in developing countries.
-The statistic comes from author calculations with data kindly provided by \cite{hoque2013state}.}  These pricing approaches have been shown to work well when each water connection serves a single household.
-Recent empirical papers in C{\^o}te d'Ivoire and South Africa predict gains in both access and total welfare from increasing marginal prices (\cite{diakite2009proposal,szabo2015value}).
-However, many households in developing cities share connections with their neighbors, which can have large implications for water pricing.
-
-Insecure land-tenure, credit-constraints, and administrative costs often make it difficult for disadvantaged households to purchase their own water connections (\cite{devoto2012happiness}).
-As a result, households frequently share connections ranging from fetching from neighbors with hoses and buckets in Tangiers, Morocco (\cite{devoto2012happiness}) to drawing from single taps that each serve compounds in Kumasi, Ghana (\cite{whittington1992possible}).\footnote{\cite{nauges2006water} finds further evidence of widespread water sharing in Sri Lanka.}  While documenting the prevalence of these  sharing networks, research has not yet examined the importance of water sharing for optimal pricing policy.
-
-% often increase the costs of purchasing a water connection particularly for disadvantaged households
-% Also, many cities maintain high upfront fees despite policy recommendations otherwise (\cite{hoque2013state}).
-
-This paper integrates sharing behavior into water demand in order to analyze the welfare effects of pricing policies.
-I build a model of household water demand that includes both (1) the upfront choice of whether to purchase a connection, share with a neighbor, or use non-piped sources as well as (2) monthly consumption choices.
-I also collect new survey evidence on sharing contracts to inform several features of the model design.
-The structural estimation leverages administrative data from 1.5 million water connections in Manila from 2010 to 2015, which link to additional survey data on households sharing connections.
-
-These estimates allow me to solve a standard regulator pricing problem: setting prices to cover fixed and marginal costs while maximizing consumer surplus.
-I also let the regulator place extra weight on surplus for smaller, poorer users.
-In the presence of sharing, the standard approach --- low fixed fees and high marginal prices --- excludes many small-users from piped water by reducing incentives to share connections.
-Instead, these households substitute toward non-piped water sources, which have relatively lower marginal prices, zero upfront costs, and varying water quality.\footnote{Common non-piped water sources in Manila include deepwells, tanker trucks, and water refilling stations.
-Without fixed prices, land-tenure requirements, or administrative expenses, these sources often have low costs of access.}  The opposite approach --- high fixed fees and low marginal prices --- maximizes both access to piped water and welfare, even for smaller users.
-High fixed fees are paid in full by households who connect individually and are split between sharing households.
-Informal sharing arrangements enable small-users to access piped water from their neighbors for relatively lower marginal prices than those offered by non-piped sources.
-By reducing the total number of connections, sharing arrangements also let the city save on installation and maintenance costs, providing an efficient means for extending piped water to low-demand households.\footnote{In this regulatory arrangement, cost savings are passed on to consumers through lower prices.}
-
-The welfare impacts of these pricing policies depend not only on household-level demand, but also on the relative costs of sharing water; these may include both marginal hassle costs (ie.
-time spent fetching from neighbors or reduced pressure from re-piping water) as well as savings from splitting the fixed costs of a connection.
-Measuring these features presents two central challenges: how can we recover household-level demand when we observe water consumption for connections serving multiple households, and how can we separately identify the costs of sharing and preferences for water?
-The empirical approach addresses these challenges in three steps.
-
-The first step builds a tractable model of water sharing to estimate household-level demand from monthly usage data for each connection.
-Informed by new survey evidence, this model embeds how (1) households face challenges in observing each other's monthly demand and (2) households often split the monthly water bill evenly.
-These assumptions on sharing behavior ensure that connection-level demand can be expressed as a simple function of underlying household demands even in the presence of non-linear prices.
-I use variation in the non-linear price schedule (both across and within connections) to identify water demand for each connection before disaggregating preferences to the household-level.
-This approach extends previous models of optimization over non-linear prices by including sharing and allowing households to anticipate unobserved shocks to their demand (\cite{moffitt1986econometrics,burtless1978effect}).
-
-To estimate the marginal hassle costs of sharing water, the second step analyzes a quasi-experiment where breaks in service pipes force some households to switch from their own water connections to their neighbors' connections.
-I then measure how much less water households use from their neighbors' connections and attribute this gap to the marginal hassle costs of sharing per cubic meter of usage.
-This exercise recovers sizable marginal hassle costs per cubic meter on the order of \input{tables/hassle_percentage}\unskip\% of the average marginal water price.\footnote{This revealed-preference approach builds on a descriptive literature that identifies potential sources of water sharing frictions (\cite{whittington1992possible,nauges2006water}).}
-
-The third step maps the share of households using from each source --- connecting alone, sharing with a neighbor, or using from a non-piped source --- into an estimate of each source's relative fixed cost to consumers.
-The empirical approach leverages the assumption that given water preferences (from step one) and marginal sharing costs (from step two), any remaining variation in water source choices must be due to differences in their fixed costs.
-Since sharing decisions are strategic in nature, I specify a simple game where households sequentially choose their sources and agree to split any surplus from sharing.
-By considering both source and quantity choices, this model expands on the demand estimation literature for public utilities that has so far focused almost exclusively on monthly quantity choices (\cite{diakite2009proposal,mcrae2014infrastructure,olmstead2009reduced,szabo2015value}).
-
-This revealed-preference approach to estimating fixed costs is especially relevant in a developing context because on top of the initial connection and monthly service fees, households often face other fixed costs that are difficult to observe, including permitting fees, plumbing maintenance, as well as land-tenure issues in qualifying for a water connection.
-In fact, I estimate that the fixed fees paid to the provider (connection and service fees) account for only around half of the total fixed costs.
-This structural approach complements previous experimental evidence of fixed costs by \cite{devoto2012happiness}.
-
-%The third step estimates these fixed costs by simulating the sequential game to match cross-sectional variation in water source choices.
-
-With these estimates, I simulate a series of counterfactual policies.
-First, I consider a connection fee subsidy policy consistent with recommendations from the World Bank, NGOs, and other researchers to improve water access for the poor (\cite{komives2005water,jimenez2014factors,mcintosh2003asian}).
-I discount the fixed fee by 12\% while increasing the tariff schedule proportionally to ensure that the water provider exactly covers costs.
-This policy actually reduces access because households stop sharing connections and substitute towards non-piped sources.
-Next, I compute an optimal tariff schedule to maximize consumer surplus while exactly covering production costs.
-Compared to the current tariff, I find that a simple, two-part tariff characterized by a fixed fee and low, flat marginal price can produce gains on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus.\footnote{With quasi-linear utility, consumer surplus for a given tariff is calculated as the difference between household utility under this tariff and household utility from using the non-piped, vendor option.}  These gains are driven both by pricing closer to marginal cost as well as by increasing sharing, which reduces the number of connections installed and maintained by the utility.
-
-Finally, I compute a tariff that maximizes consumer surplus only for the bottom 50\% of users and is intended to capture goals of ensuring minimum usage and access as well as income redistribution.
-With sharing, this tariff is ineffective at reallocating surplus from large to small users; however in a counterfactual without sharing, this tariff achieves substantial redistribution.
-These findings suggest that informal sharing networks may constrain the extent to which non-linear prices can redistribute surplus.
-
-This paper proceeds by first describing the context of water provision in Manila.
-Section~\ref{section:data} describes the data.
-Section~\ref{section:patternsofwateruse} presents stylized facts about water usage in Manila.
-Section~\ref{section:modelofhouseholdwateruse} introduces a model of household water usage and source choices.
-The estimation is divided into three steps in Section~\ref{section:specificationandestimation}.
-Section~\ref{section:preferenceestimation} uses monthly quantity choices and price variation to estimate preferences.
-Section~\ref{section:hasslecostestimation} analyzes a quasi-experiment to recover an estimate of the marginal costs of sharing with a neighbor.
-Given these estimates, Section~\ref{section:fixedcostestimation} recovers the relative fixed costs of owning a connection or using from a vendor.
-Section~\ref{section:counterfactualexercises} uses these estimates to examine counterfactual pricing policies.
-Section~\ref{section:conclusion} concludes.
-
-\section{Water Provision in Manila}
-
-In 1997, citing poor service quality and low coverage of the public water provider, the Philippines conducted the largest water privatization in the developing world.
-Two private companies evenly divided the city into east and west zones as part of a public-private partnership.
-Both companies invested heavily in infrastructure, which has resulted in near universal availability of piped water services for Manila.
-A government regulator oversees these companies and implements rate-of-return regulation: water tariffs are revised periodically in order to ensure that providers recover all operating costs as well as earn a percentage return on any capital investments.
-Rate-of-return regulation is common in developing countries since high costs of public funds as well as high risks of regulatory capture limit funding of utilities through government revenue (\cite{laffont2005regulation}).
-
-This paper focuses on one of the providers which serves 1.5 million connections and around 5 million people.
-Figure~\ref{figure:tariff} shows the regulated tariff in Manila.
-The increasing marginal price is thought to cross-subsidize consumption among low-demand, poorer households through higher bills from large users.
-The regulator assigns zero marginal price to the first 10 cubic meters of monthly usage, which is called the ``lifeline'' rate.
-This policy is intended to provide a minimum level of consumption for all households.
-This tariff may also perform efficient price discrimination if low-usage households are more price-sensitive.
-\begin{figure}
-\centering
-\caption{Marginal Prices in Manila}\label{figure:tariff}
-\begin{center}
-\includegraphics[scale=.7]{tables/tariff_structure.pdf}\\
-\footnotesize{1 USD = 50 PhP}
-\end{center}
-\end{figure}
-% detail more about how to get water, with the fixed fee and conne{}ction fee?!
-On top of this tariff schedule, the regulator also charges a fixed fee independent of usage totaling 225 PhP/month.
-This fee includes both the monthly service charge and the initial connection fee that I have put into monthly terms for the duration of the water connection.\footnote{Appendix~\ref{appendix:connectionfeeamortization} provides more details about how this monthly fee is calculated and amortized.}  The fixed fee allows the provider to recover any operating costs associated with serving the connection.
-This form of increasing tariff and fixed fee combination is implemented in over 70\% of developing cities as well as over 50\% of developed cities (\cite{hoque2013state}).
-
-Faced with this fixed fee as well as other costs associated with getting and maintaining a connection such as additional application costs or land tenure insecurity, I find that over 23\unskip\% of households use a neighbor's tap in Manila.
-Sharing a connection with a neighbor mechanically increases the total monthly consumption recorded per connection, often doubling the marginal prices faced by these households compared to using a connection alone.
-Although most households use piped water either through their own or neighboring connections, \input{tables/vendor_total}\unskip\% of households remain unconnected to the network and instead fetch water primarily from nearby deepwells while some use water refilling stations or other vendors.
-
-\section{Data}\label{section:data}
-
-%Monthly quantity choices across different households and at different prices reveal information about household demand.
-Observing multiple quantities choices for the same household allows for a rich characterization of demand heterogeneity at the household-level.
-Evaluating different pricing policies requires measuring demand at the household level as well as costs associated with providing piped water.
-Data was gathered through a partnership with one of the two regulated, private providers in Manila who provided both billing records as well as information about the regulatory structure, pricing, and production costs.
-Complete billing records for each water connection including the monthly meter reading, the total bill charged, and the precise location for each meter serve as the primary measure of quantity choices.
-These data span 2010 to 2015, during which connections grew from 900,000 to 1.5 million water connections, generating nearly 100 million transaction records.
-Connections are divided into residential (90\%), semi-business (4\%), commercial (5\%), and industrial (1\%).
-This paper focuses on residential and semi-business connections.\footnote{Semi-business connections are largely composed of households that own small roadside stands.
-These connections provide a useful source of price variation which is described in Appendix~\ref{appendix:ratechangeelasticity}.}  The monthly meter reading is used as the measure of consumption for each connection.
-Meter readings are rounded to the nearest cubic meter limited to monthly readings below 100 $\text{m}^{3}$ in order to exclude pipe leaks as well as meter reading errors (readings above 100 $\text{m}^{3}$ compose less than 0.7\% of the sample).
-
-Since the object of interest for welfare is household-level demand, the billing records are merged to survey data recording information on households using each connection as well as demographics for the owners of each connection.
-To evaluate the performance of the water provider, the regulator contracted with a local university to conduct the Public Assessment of Water Services survey in three waves from 2008 to 2012, surveying around 50,000 water connections.\footnote{Appendix~\ref{appendix:pawssampling} describes the sampling design and tests the extent to which it may be correlated with demographic characteristics.
-This exercise finds relatively weak correlations in economic terms with key characteristics.}  The connection survey records the total number of households and people using each connection, providing the primary measure of sharing behavior.
-The connection survey also includes basic demographics for the owner of the connection.
-The demographics used in the analysis include household size, dwelling type (whether apartment, duplex, or single house), number of employed household members, and whether the head of household is employed in a low-skill profession.
-%consumption and water source choices at the household-level.  
-%To examine both consumption decisions and water source choices at the household-level, I construct a dataset that merges (1) monthly water usage for around 50,000 connections, (2) demographics and water sharing measures for households using these connections, and (3) a cross-section of all households and their water source choices.
-Put together, these data form a representative sample of households in half of Metro Manila.
-
-A full analysis of water usage in Manila also requires measuring households that are unconnected to the bulk water system and instead use water from local vendors.
-The 2010 Census of Population and Housing records demographics for households that are using water from alternative sources.
-Households are defined as connected to the piped network if they report using a ``faucet community water system'' for their cooking, laundry, or bathing needs.\footnote{The census was designed largely for rural populations so it does not directly ask whether households are connected to a piped water network.}  Alternatively, households are considered to be using from a water vendor if they report any other category, which includes deep wells, peddlers, or other sources.\footnote{Since demographic questions in the census and connection surveys are worded differently, Table~\ref{table:pawstocensus} of Appendix~\ref{appendix:pawstocensus} compares measures across the two data sources for households that own connections finding broadly similar patterns.}  Census data is merged geographically with the connection survey for 599 wards in Manila.
-
-%To construct a profile of water source choices for the full population, I randomly sample from the pool of households using from vendors in 599 wards of the city so that the data form a representative sample when combined with households covered by the connection survey in each small area.
-%\footnote{Regions are chosen to overlap with ward administrative/political boundaries while ensuring that I am able to obtain a large enough sample of vendor households for each area to perform the counterfactual analysis in Section~\ref{section:fixedcostestimation}.}
-
-For additional information on water sharing relationships between households, I fielded a small, non-representative survey of 600 households via mobile phone application.
-This survey asks about issues associated with using different water sources, basic demographics, as well as how the bill and connection fee are paid for sharing households.
-Appendix~\ref{appendix:pollfish} compares this survey to the connection survey finding roughly similar rates of sharing and demographic characteristics.
-
-%includes additional details on this survey and finds roughly similar measures between the connection survey and the mobile survey, suggesting that the mobile survey may provide a reasonable descriptive picture of sharing in Manila.
-
-The water provider also maintains call records of all service complaints, which can be linked to individual connections.
-This data is used to measure instances where households face unanticipated shocks to their water source, which are used to identify the marginal costs of using water from a neighbor.
-Finally, the water provider tracks data on the marginal cost of pumping an additional cubic meter of water as well as the costs associated with installing new connections.
-These data provide inputs into the provider's budget constraint, which are necessary for computing counterfactual pricing regimes.
-
-With information on water source and monthly expenditures as well as household income, the 2011 Community Based Monitoring System data cover over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown metro Manila.
-These data are used to impute income for households outside of the sample according to the following demographic measures: age of household head and indicators for low-skilled employment of household head, residing in a duplex, residing in a house, as well as all possible household sizes and number of employed household members.
-The imputation also includes all possible interactions between these measures.
-
-%Supplemental survey data from the Community Based Monitoring Survey in Pasay City --- a large city in the center of Metro Manila --- include household income measures for  that are used to approximate household income using the full set of demographic measures and their interactions.
-
-\section{Patterns of Water Use}\label{section:patternsofwateruse}
-
-The welfare consequences of informal sharing networks depend on both the types of households that choose to share with neighbors as well as the costs of these networks.
-To provide some descriptive evidence, Table~\ref{descriptives} merges the connection survey of water connections with billing records associated with each connection.
-The columns group connections by the number of households they serve: one, two, or at least three.
-Demographics for connection owners indicate that smaller, slightly younger, and poorer households are more likely to share water with neighbors.
-Sharing households are over twice as likely to reside in duplexes possibly because transporting water between neighbors requires less effort for duplex residents.
-
-Larger numbers of households sharing a water connection are correlated with more total water usage, but less water per person.\footnote{Total People Served by a connection includes both the owning household and any other households using a connection.}  This decline may have many possible drivers: (1) sharing households face higher prices by locating at a higher point on the tariff schedule (Figure~\ref{figure:tariff}), (2) sharing households may face hassle costs in fetching water from neighboring taps, (3) these price effects may incentivize low-demand households to select into sharing relationships, consistent with the demographic patterns, and (4) low-demand households may have idiosyncratic preferences for sharing relationships.
-On average, monthly water bills (inclusive of service fees) take up around \input{tables/incshr}\unskip\% of household income, which does not include other unobserved costs in accessing water.
-These findings suggest that policies which affect sharing choices can have significant impacts on water consumption as well as monthly expenditures.
-
-%Demographics for connection owners indicate that smaller and younger households are more likely to share water with neighbors.
-Because household size is a strong proxy for water demand, this finding suggests that sharing a connection is negatively correlated with household water demand.
-Households with lower imputed income more commonly share water connections.
-Sharing households are over twice as likely to reside in duplexes possibly because transporting water between neighbors requires less effort for duplex residents.
-
-\begin{table}
-\centering
-%\captionsetup{justification=centering}
-\begin{threeparttable}
-\caption{ Water Connections  by Number of Households Served}\label{descriptives}
-\input{tables/new_descriptives}
-\begin{tablenotes}
-\item \footnotesize{The data include billing records merged with the connection survey.  Income is imputed using location, demographic variables, and their interactions.}
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-%Table~\ref{descriptives} summarizes water use and sharing behavior for these connections, merging information from the connection survey with the billing records.
-
-%Also, the mobile survey indicates that only around 30\% of sharing households would substitute to toward a neighbor's connection if they no longer had access to their primary water source.
-For this reason, I treat connections reported to serve more than three households as only serving three households.
-Table~\ref{descriptives} also computes the total number of households using from each source.
-This calculation requires the additional assumption that households sharing with one or two other households are uniquely linked to one connection.
-This way, the population of households connected to the network can be computed by summing the number of households across all connections.
-This assumption is consistent with the presence of fixed costs in setting up a connection or a sharing relationship so that households stay committed to one water source.
-To the extent that households are drawing water from multiple connections, this assumption may lead to an overestimation of the population engaged in sharing relationships.
-With this assumption, \input{tables/shr_individual}\unskip\% of connected households receive their water from an individual connection, \input{tables/shr_1hh}\unskip\% are involved in a sharing relationship with a single neighbor, and \input{tables/shr_2hh}\unskip\% are in a sharing relationship with 2 or more other households.
-These proportions do not take into consideration households that are using from water vendors, which are discussed in more detail below.
-Each water connection contributes over four years of billing records on average.
-
-Since the connection survey only includes households connected to piped water, census of population and housing data is required to learn about households using from water vendors.
-In this data, \input{tables/vendor_total}\unskip\% of the population report using vendors, which is composed of \input{tables/vendor_well}\unskip\% of households using from a ``deep well'' and \input{tables/vendor_peddler}\unskip\% using from a ``peddler'' while the remaining fall into an ``other'' category.
-Anecdotal evidence suggests that groundwater from wells often has very low quality.
-Appendix Table~\ref{table:pawstocensus} compares means of demographic variables between connection owners from the connection survey and all households from the census.
-Demographic variables are similar between connection owners in the connection survey and the census data.
-Households using from vendors have lower imputed incomes, greater probability of low-skill employment, and slightly fewer members than own-use households.
-Across most dimensions, households using from vendors more closely resemble households that share with their neighbors as opposed to households that use their connections individually.
-
-%  While demographics are broadly similar between the first and second columns, any differences are likely driven by two factors.
-First, connection owners may have different demographic characteristics than households using from a neighbor's tap.
-This explanation is consistent with larger household sizes and lower rates of low skilled employment among connection owners in the first column relative to connection owners and other users captured in the second column.
-Second, demographic measures may not be exactly comparable across these surveys.
-Consistent with this theory, easily measured demographics like age of household head, household size, and total household members employed are very similar across the first and second columns; however, more subjective measures such as level of skill in employment and type of dwelling exhibit greater variation across data sources.
-For this reason, the imputation strategy used in Section~\ref{section:fixedcostestimation} also relies on local geographic measures alongside these demographic measures.
-
-\section{A Model of Household Water Use}\label{section:modelofhouseholdwateruse}
-% Given that households derive utility from a water source through a stream of water use, 
-% Taking these observed choices as inputs, this model is designed to recover both preference parameters for water as well as the shadow costs of using different water sources.
-
-This section presents a stylized model of water source choice and monthly quantity decisions at the household level.
-This model allows for an analysis of the impacts of pricing policies on both source and quantity margins, which are often equally relevant to policymakers (\cite{mcintosh2003asian,komives2005water}).
-Using both margins also enables the estimation to include cross-sectional variation in sources alongside time-series variation in quantities to recover a broad set of demand and cost parameters.
-
-Let the city of Manila be partitioned into neighborhoods, where each neighborhood is defined by a set of households that are physically close enough to share water connections with each other.
-In the context of Manila, these neighborhoods are often characterized by dense clusters of houses or duplexes.
-This partition embeds the assumption that neighborhoods are mutually exclusive so that a household located in one neighborhood cannot share water with households in a nearby neighborhood.
-Restricting the choice set in this way is necessary for computation but may in some cases overestimate the costs that households face in finding a sharing partner.\footnote{This limitation is discussed in more detail in Section~\ref{section:fixedcostestimation}.}
-
-In the first step, each household makes a one-time decision about their water source between 1) purchasing a connection, 2) using a neighbor's connection, or 3) buying from a local water vendor.
-These decisions result in a set of water connections for each neighborhood ranging from an empty set (if all households use from a vendor) to the whole neighborhood (if each household uses an individual connection).
-Let each connection, $C$, serve $S$ households that have decided to share the connection.
-For ease of notation, let the subscript $C$ indicate connection-level attributes, summing over all households using from connection $C$.
-This model does not allow for households to choose different water sources over time, which is consistent with large fixed costs involved in initially purchasing a connection or establishing a sharing relationship.
-Section~\ref{section:hasslemodel} extends the model to allow for cases where households may exogenously lose access to their current water source and must substitute toward another nearby source.
-
-In the second step, each household then chooses how much water to use each month from their source.
-Since water sources provide utility through monthly consumption, it is useful to describe the decision process in reverse order, first characterizing monthly water consumption choices (taking the initial source choice as given) and second, characterizing the initial water source choices.
-
-\subsection{Consumption Choices for Households Using Piped Water}\label{section:consumptionchoice}
-% The goal is to take water consumption data and map it into preferences...
-% Water consumption data for each connection aggregates the monthly consumption for all households as well as individuals within these households. 
-% Modeling this behavior is not only useful for accurately characterizing demand, but may also play an important role in measuring the potential welfare losses from these non-linear pricing schedules.
-%(CITE JAYACHANDRAN AND JACK)
-
-%This section details how households choose their monthly quantities of consumption holding their water source fixed.
-
-%For households using piped water, they have to consider four aspects when choosing how much to use each month:  (1) households may have difficulty targeting their exact monthly consumption levels since meters can be hard to observe and many family members use the same tap; (2) increasing marginal prices in the water tariff mean that households face non-linear budget constraints; (3) households that share a connection need to determine how to divide the monthly water bill; and (4) households fetching from a neighbor may face additional hassle costs in transporting water.
-
-%Since the data record monthly consumption for each connection, this model first introduces individual household demand before aggregating household demand at the connection-level for estimation.
-
-In choosing how much water to consume each month, households using piped water face the difficult task of coordinating water consumption among all household members.
-For example, consider the head of a household trying to manage water consumption across all of their household members each month.
-This task would involve monitoring the meter located outside of their dwelling and coordinating water use among all members.\footnote{Given that many developing countries feature steeply increasing prices with monthly usage, these coordination challenges may magnify any distortions caused by non-linear pricing.}  Consistent with these challenges, mobile survey data indicate that \input{tables/no_info}\unskip\% of surveyed household members do not recall how much they paid for water in the last month while \input{tables/no_use}\unskip\% do not recall the amount that their household consumed in the previous month.
-
-As a simple way to capture this coordination task, let each household $i$ choose a goal for water use each month, $w_i$, knowing that unobserved consumption shocks, $\epsilon_i$, may increase or decrease their realized amount of usage.
-Consumption shocks, $\epsilon_i$, are assumed to be unobserved to the household and independent across time, bringing the total realized water consumption each month to, $W_i=w_i+\epsilon_i$.
-Household utility over total water, $W_i$ and a numeraire good, $x_i$ is assumed to take the following shape:
-\begin{align}\label{equation:umaxfirst}
-\begin{split}
-U(x_i,W_i) &=  x_i + (1-H_i) W_i - \frac{1}{2\alpha_i } ( W_i - \Gamma_i + \alpha_i )^2  \\
-W_i &= w_i + \epsilon_i \\
-\epsilon_i &\sim \mathcal{N}(0,\Sigma_{\epsilon})
-\end{split}
-\end{align}
-Following from quasi-linear preferences, this quadratic form for utility eliminates income effects and includes a natural satiation point for water consumption, capturing the tendency of households to target specific consumption levels despite low or zero marginal prices as shown in Figure~\ref{figure:consumptionhistogram}.\footnote{This utility form builds on work by \cite{einav2013selection} who use a similar form to characterize extensive and intensive choices of health insurance.}   Household preferences for water are characterized by $\Gamma_i$, which can be interpreted as a fixed preference for water each month and $\alpha_i$, which captures the extent to which households are sensitive to price.
-The exogenous shock to consumption, $\epsilon_i$, is assumed to be drawn from a multivariate normal distribution, $\Sigma_{\epsilon}$ with zero mean and variance terms, $\sigma_{\epsilon}^2$, allowing for correlation with neighboring households $i$ and $j$ through term ${\rho}^{\epsilon}_{i,j}$.
-Although households cannot anticipate the exact realization of $\epsilon_i$, they are assumed to understand the distribution of possible consumption shocks, allowing them to maximize expected utility.
-
-Households that are using water from a neighbor's tap may face an additional utility cost per gallon of water $H_i$.
-This hassle cost captures any inconvenience associated with using an additional unit of water from a neighbor's tap.\footnote{Accordingly, the connection owner is assumed to face zero hassle cost.}  The mobile survey reveals that among households accessing water from a neighbor's connection, \input{tables/access_fetch}\unskip\% fetch water with containers, \input{tables/access_single_tap}\unskip\% access water from a single hose/pipe provided by the connection owner, and \input{tables/access_pipes}\unskip\% are able to fully connect their household plumbing near the water meter.
-These different modes of access suggest that sharing households may face higher time costs fetching water or lower water pressure from piping water additional distances.
-
-To account for idiosyncratic preference shocks for water each month, let household's fixed preference, $\Gamma_{i}$, be decomposed into a static, household-specific component, $\gamma_i$, and an idiosyncratic component, $\eta_{i}$, which is assumed to follow a multivariate normal distribution among sharing partners:
-\begin{align*}
-\Gamma_{i} &= \gamma_i + \eta_{i} \\
-\eta_{i} &\sim \mathcal{N} (\textbf{0},\Sigma_{\eta}) 
-\end{align*}
-This preference shock is also assumed to be independent of the consumption shocks, $\epsilon_C$.
-Aggregating these preferences shocks over all households sharing connection, $C$, produces a joint shock, $\eta_C$, according to the convolution of these random normal variables with a variance equal to $\sum_{i=1}^{S} \sigma_{\eta}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \rho^{\eta}_{i,j} \sigma_{\eta}^2$.
-
-%To develop notation for sharing, normalize $i=1$ to be the owner of the connection and define the total number of sharing households for a particular connection as $S$.
-Therefore, all households, $i\neq1$, using from a neighbor's tap have a positive hassle cost, $H$, while the connection owner, $i=1$, has zero hassle cost.
-
-%FIX HERE!
-
-%Without data on the sharing mode and distance between households for each connection, the model assumes all sharing households face a homogeneous hassle cost, $H_i$, from using a neighbor's connection.\footnote{Section~\ref{section:hasslecostestimation} discusses the extent to which this assumption may bias estimates.
-The partitioning of the city into sharing neighborhoods also imposes the implicit assumption that hassle costs rise substantially between neighborhoods so that no household has an incentive to share with households in another neighborhood.}
-
-% , normalized as $i>1$,
-
-\subsubsection{Determining the Budget Constraint}
-
-The household problem is additionally complicated by the presence of an increasing price schedule for water; as a household uses more water in one month, they face higher marginal prices.
-Figure~\ref{figure:tariff} provides the increasing tariff in Manila.
-This price schedule produces kinks in household budget constraints leading to non-linear demand functions.
-Let $P(W_C) = \{ p^{1},...,p^{K},\overline{W}^{0},...,\overline{W}^{K}\}$ describe the tariff schedule as a function of total consumption for the water connection, $W_C = \sum_{i=1}^{S} W_i$.
-The tariff includes $K$ segments where segment $k$ corresponds to price $p^{k}$ for water consumption between the consumption thresholds (or kink points), $\overline{W}^{k-1}$ and $\overline{W}^{k}$:\footnote{In this case in Manila, $\overline{W}^{0}$ is zero while $\overline{W}^{K}$ is infinity.}
-\begin{align*}
-P(W_C)=&  
-\begin{cases}
-      p^{1} &\text{ if } W_C \in [\overline{W}^{0},\overline{W}^{1}], \\
-      p^{2} &\text{ if } W_C \in [\overline{W}^{1},\overline{W}^{2}], \\
-      ...   &\text{ ...}, \\
-      p^{K} &\text{ if } W_C \in[\overline{W}^{K-1},\overline{W}^{K}]
-    \end{cases}
-\end{align*}
-Given prices and household utility, the final ingredient for characterizing consumption choices is the budget constraint.
-The budget constraint includes monthly household income, $Y_i$, and monthly fixed costs of using the water connection, $F_i$, which are assumed to capture three components: (1) monthly service fees, (2) initial connection fees amortized into monthly terms for the duration of the connection, and (3) unobserved, fixed hassle costs associated with setting up a connection, which are also amortized into monthly terms.
-Data does not track household water source choices over time in a comprehensive way, which limits the extent to which the model can distinguish between one-time connection costs and monthly service/maintenance costs.
-This limitation means that the model cannot address the optimal timing of fixed payments or capture potential heterogeneity in monthly fixed costs.
-
-Sharing households must negotiate over how to pay the monthly fixed costs (including the fixed fee paid to the firm and any unobserved costs of using a connection).
-The model assumes that households commit to dividing any fixed costs at the start of the sharing arrangement, allocating $F_i$ to each household.
-Under quasi-linear utility, any fixed transfers are exogenous to monthly consumption decisions and Section~\ref{section:watersourcechoice} later discusses how fixed costs are divided between sharing households.
-
-Water sharing relationships impact monthly consumption choices through the budget constraint.\footnote{While the formation of these relationships is discussed in more detail in Section~\ref{section:watersourcechoice}, this section takes these sharing relationships as exogenously given.}  The model assumes that the monthly water bill is split evenly between all sharing households.
-Descriptive evidence suggests that challenges observing and coordinating usage within members of a household also extend across households.
-Among owners of the water connection responding to the mobile survey, \input{tables/bill_split}\unskip\% report splitting the water bill evenly or alternating payment each month, \input{tables/bill_fixed}\unskip\% charge sharing households a fixed amount each month regardless of their consumption, and \input{tables/bill_usage}\unskip\% charge other users a price according to their usage.\footnote{The remaining households report ``I don't know'' or ``other.''}  Evenly splitting the bill, alternating payment, or charging a fixed amount provide easy ways to extract compensation without requiring specific information on the monthly consumption of each sharing household.
-Yet, these methods also introduce free-rider incentives since households do not have to fully pay for their contributions to the total water bill.
-Since data limitations prevent identifying the specific type of contract associated with each shared connection, the model assumes that all households evenly split the bill and explores the theoretical and empirical implications of alternate models in Appendix~\ref{appendix:fixedprice}.
-The model captures bill splitting by evenly dividing the total monthly payment for a water connection across the $S$ sharing households.
-
-%\footnote{Under the additional assumption that households never directly observe the $\epsilon$ shocks, splitting the bill provides an intuitive way to ensure all households account for at least some of their usage.
-}
-
-Normalizing the price of the numeraire good, $x$, to one, the budget constraint for household, $i$, using a connection with households, $S$, takes the following form given that total consumption for their connection, $W_C$, falls between thresholds, $\overline{W}^{k-1}$ and $\overline{W}^{k}$:
-%\begin{align*}
-%Y_i - F_i &=  
-%\begin{cases}
-%      x_i + H_{i} W_i + \frac{1}{S} p^{1} W_C   &\text{ if }   W_C \in [0,\overline{W}^{1}], \\
-%      x_i +  H_{i} W_i +  \frac{1}{S} \big [p^{k} W_C -  E_{k} \big]     &\text{ if } W_C \in [\overline{W}^{k-1},\overline{W}^{k}], \\
-%      ...   &\text{ ... }      
-%\end{cases} \\
-%E_{k} &= \big  [\sum_{j=1}^{k-1}  (p^{k} - p^{j})(\overline{W}^{j}-\overline{W}^{j-1})  \big ]
-%\end{align*}
-\begin{align}
-\label{equation:budgetconstraint}
-\begin{split}
-(Y_i - F_i) &= x_i +   \dfrac{  B_{C,k}  }{S_C}    \hspace{.3cm} \text{ if } \hspace{.1cm} W_C \in [\overline{W}^{k-1},\overline{W}^{k}] \\
-\text{Where: }& \\
-B_{C,k}  &= p^{k} (W_{C}^{*} - \overline{W}^{k-1}) +\sum_{j=1}^{k-1}  p^{j}(\overline{W}^{j}-\overline{W}^{j-1}) 
-\end{split}
-\end{align}
-The full budget constraint is a piece-wise expansion of equation (\ref{equation:budgetconstraint}) over all $K$ price thresholds.
-$B_{C,k}$ represents the total water bill for connection $C$ given the tariff schedule.
-This term is calculated by multiplying each price by the volume of consumption exposed to that price.
-%\footnote{In the case where a household uses a connection individually, this expression simplifies by setting the index, $i$, and the total using households, $S$, both equal to one.
-In this scenario, the household does not face any hassle costs, $H_i$, and pays the total bill from its corresponding consumption.}
-
-\subsubsection{Maximizing Expected Utility}
-
-When households share a water connection, the consumption choice for each household becomes a strategic decision.
-Since prices are non-linear, the total consumption level for each connection, $W_C$, determines the marginal price faced by all households.
-For example, with an increasing tariff like Figure~\ref{figure:tariff}, one household's choice to increase consumption may produce a higher marginal price for other sharing households.
-
-Substituting the budget constraint (equation (\ref{equation:budgetconstraint})) into the household utility (equation (\ref{equation:umaxfirst})) for the numeraire good $x_i$ simplifies the household's maximization problem to a single choice variable --- targeted consumption, $w_i$.
-The household's expected utility problem over consumption shocks $\epsilon_C$ then takes the following form:
-%\scalebox{.88}{\parbox{1\linewidth}{
-%\begin{align*}
-%E[U(x_i,w_i)] = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C -  E_{k} \big] d \epsilon_C + \int_{-\infty}^{\infty} W_i - H_{i} W_i - \frac{1}{2\alpha_i} ( W_i - \Gamma_i + \alpha_i )^2 d \epsilon_i  \\
- %         = &  (Y_i - F_i)  - \frac{1}{S} \sum_{k=1}^{K} \int_{\overline{W}^{k-1}-W_C}^{\overline{W}^{k}-W_C}\big [p^{k} W_C d -  E_{k} \big] d \epsilon_C+ w_i - H_{i} w_i - \frac{1}{2\alpha_i} ( w_i - \Gamma_i + \alpha_i )^2 + \sigma_{\epsilon}^{2}
-%\end{align*}
-%}} \\
-% E[U(w_i)] = 
-\begin{align*}
-max_{w_i} &\sum_{k=1}^{K} \int_{\overline{W}^{k-1}-{w_C}}^{\overline{W}^{k}-{w_C}} (Y_i - F_i) -  \dfrac{ B_{C,k} }{S_C}     + (1-p_s) W_i   - \frac{1}{2\alpha } ( W_i - \Gamma_i + \alpha_i )^2  d \epsilon_C
-\end{align*}
-%B_{C,k}  &= p^{k} (W_{C}^{*} - \overline{W}^{k-1}) +\sum_{j=1}^{k-1}  p^{j}(\overline{W}^{j}-\overline{W}^{j-1}) 
-Where $\epsilon_C$ is the convolution of consumption shocks across sharing households distributed as follows:
-\begin{align*}
-          \epsilon_C &\sim \mathcal{N}(0,\sigma_{\epsilon_C}^2 = \sum_{i=1}^{S} \sigma_{\epsilon}^2 + \sum_{i=1}^{S} \sum_{j>i}^{S} \sigma_{\epsilon}^2 \rho^{\epsilon}_{i,j} )
-\end{align*}
-To solve this system, this approach assumes that households follow a perfect information, pure-strategy Nash-Equilibrium in choosing consumption.
-Using this structure, households compute their best response consumption functions to arrive at a symmetric equilibrium taking consumption for their sharing partners as given.
-% % % % % % % % % % % % % % % % \footnote{  APPENDIX PROVES THIS;  NEED TO GO DEEPER PLEASE!!! SHOW EXPLICITLY }  % % % % % % % % % % % % % % % % % % %
-%Because of the quadratic shape of the utility function, the exogenous shock to consumption, $\epsilon_s$, only affects the optimal consumption choice to the extent that it pushes the household across price thresholds.
-Therefore, the solution to equation (\ref{equation:umaxfirst}) is isomorphic to removing the $\epsilon_s$ terms from the utility function and only allowing these shocks to enter through the budget constraint.
-This simplification ensures that the $\epsilon_s$ terms enter linearly into the optimization problem through the budget constraint.
-
-Taking the derivative of expected utility with respect to $w_i$ (holding sharing partners' choices $w_{-i}$ fixed) while letting $\Phi(.)$ equal the standard normal cumulative distribution function produces the following first-order condition:
-\begin{align}
-\label{equation:firstordercondition}
-%\begin{split}
- 0 &= - w_i + \Gamma_i - \alpha_i \Big[H_{i} +  \frac{MP_C}{S} \Big]
- \end{align}
-\hspace{2cm} Where:
-\begin{align}
-\label{equation:weightedmarginalprice}
- MP_C &= \sum_{j=1}^{K}  p^{j} \Big [ \Phi \Big( \frac{W_C - \overline{W}^{j}}{\sigma_{\epsilon_C}} \Big) - \Phi \Big( \frac{ W_C - \overline{W}^{j-1}}{\sigma_{\epsilon_C}} \Big)   \Big ]
-%\end{split}
-\end{align}
-
-The first order condition (equation (\ref{equation:firstordercondition})) reveals that consumers balance their fixed preference for water, $\Gamma_i$, against their price sensitivity, $\alpha_i$, hassle costs, $H_i$, and expected marginal price, $MP_C$ (scaled by the number of sharing households, $S$).
-Expected marginal price $MP_C$ (equation (\ref{equation:weightedmarginalprice})) intuitively captures the extent to which increasing household consumption, $w_i$ --- lifting total consumption, $W_C$ --- exposes the entire connection to higher prices in expectation.
-This first-order condition characterizes the best-response functions for each household.
-%Higher total consumption, $W_C$, raises the probability that the exogenous shock, $\epsilon_C$, places the households in a higher price range.
-
-To arrive at a tractable expression for water demand, it is helpful to simplify equation (\ref{equation:weightedmarginalprice}) by assuming that households approximate the normal distribution with a simple uniform distribution.
-This assumption implies that households give zero likelihood to extremely high or low consumption shocks and even likelihood to moderate consumption shocks.
-From an empirical perspective, this function allows for an analytical solution to the demand function while ensuring that the estimation can rely on normally distributed errors to estimate rich preference heterogeneity.
-I use the following piece-wise function form to approximate the normal cumulative distribution:
-\begin{align*}
-%\label{equation:approximation}
-\begin{split}
-g(z)=& 
-\begin{cases}
-       0  							  & \text{ if } z    < -\sqrt{2}                       \\
-     \frac{1}{2} + \frac{z}{2\sqrt2}  & \text{ if } z \geq -\sqrt{2} \text{ and } z \leq \sqrt{2}  \\
-       1 						      & \text{ if } z    >  \sqrt{2}
-    \end{cases}
-\end{split}
-\end{align*}
-% This  implies the additional economic assumption that household decision-makers approximate normally distributed shocks with .  
-% This approach recovers rich heterogeneity in preferences through a tractable likelihood function.  
-% I impose an ex-ante assumption on the size of consumption shocks, $\sigma_{\epsilon_C}$. 
-%are partially determined by the variance of the consumption shocks, $\sigma_{\epsilon_C}$.
-For example, when $\sigma_{\epsilon_C}$ is very large, demand becomes a function of all prices at every point because the consumption shocks are large enough to produce a positive probability of reaching every price segment regardless of where the households choose to consume.
-Appendix~\ref{appendix:linearapprox} graphs this approximation against a standard normal cumulative distribution function and simulates optimal demand under both distributions, finding negligible evidence that this approximation would substantially bias the estimates or affect welfare measures.
-After substituting the normal cumulative distribution function $\Phi(.)$ for $g(.)$ in equation (\ref{equation:weightedmarginalprice}), expected marginal price becomes the sum of potentially overlapping piece-wise functions, meaning that the optimal demand will also be piece-wise.
-I proceed by describing the different pieces of demand before putting the pieces together to form the full demand schedule.
-
-When households face very small consumption shocks, there is no probability that these shocks expose households to multiple prices.
-Therefore, solving the best-response function (summing across all households using connection $C$) yields a simple expression for optimal targeted demand:
-\begin{align}
-\label{equation:demandlinear}
-w^{j}_C &= \gamma_C - \alpha_C [H_{C} + \frac{p^{j}}{S}]  
-\end{align}
-This case produces a linear demand function where $\alpha_C$ can be readily interpreted as the price sensitivity parameter while $\gamma_C$ captures the portion of demand that is invariant to prices.
-In this case, demand is only sensitive to the marginal price, $p^{j}$, local to each segment of the tariff schedule.
-This demand function captures moral hazard from bill-splitting by dividing the price sensitivity, $\alpha_C$, by the total number of households using the connection, $S$.
-Comparing demand among shared connections to individual connections, the extent of over-consumption at an average price of $p$ can be roughly summarized as $\frac{S-1}{S} \alpha_C p $.
-The price sensitivity, $\alpha_C$, also attenuates the extent to which the hassle cost, $H_C$, enters demand.
-%The first condition ensures that the connection's idiosyncratic preference for water, $\eta_C$, falls between the appropriate thresholds, $\overline{\eta}_{L}, \overline{\eta}_{U}$, to be exposed to this particular segment of the price schedule.
-The second two conditions ensure that these thresholds do not overlap with each other so that the connection is exposed to a single price for this level of demand.
-The thresholds are determined by the kink points, $\overline{W}$, as well as $\sqrt{2} \sigma_{\epsilon_C} $.
-
-%When households face large consumption shocks, these functions overlap across price thresholds, which means that households must consider multiple prices when choosing their consumption.  
-This expression for demand holds when total demand (including the fixed preference shock $\eta_C$) falls sufficiently between two price thresholds: 
-\begin{align*}
-\overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}  \, \leq \, & w^{j}_C + \eta_C \, \leq  \, \overline{W}_{l+1} - \sqrt{2} \sigma_{\epsilon_C} 
-\end{align*}
-These conditions are less likely to be satisfied when connections have high variance in their consumption shocks, $\sigma_{\epsilon_C}$,  and face small distances between price thresholds, $\overline{W}_{l}$ and $\overline{W}_{l+1}$.
-In this case, consumption shocks may expose the connection to different prices and households need to consider the probability of facing these prices in choosing their optimal consumption targets.
-Allowing for households to be exposed to price thresholds $j$ through $l$, the general solution to the best-response function for the connection $C$ again yields targeted demand as follows:
-\begin{align*}
-w_{C}^{j,l}       		&= \frac{ 1}{ V^{j,l} } \Big ( \gamma_C - \alpha_C [ H_{C} - \frac{MP^{j,l}}{S} ] \Big )    \\
-\text{ Where : }& \\
-MP^{j,l} &=\frac{1}{2} \big  [ p^{j} + p^{l} - \sum_{k=l}^{j} \overline{W}^{k} (\frac{p^{k} - p^{k-1}}{\sqrt{2}{\sigma_{\epsilon_C}}}) \big ]  \\
-V^{j,l}	     	    &=  1 + \frac{\alpha_C}{2 S} ( \frac{p_j - p_l}{\sqrt{2}\sigma_{\epsilon_C}}) 
-\end{align*}
-The demand function takes a similar form to the linear case, including the fixed preference while weighting the marginal price by the price sensitivity and degree of sharing.
-Unlike in the linear case, connections face an average of all possible marginal prices, $MP^{j,l}$, that can be realized from their consumption shocks.
-All terms are also weighted by a variance term, which depends on the gap between the highest and lowest prices $j$ and $l$.
-This expression holds for levels of demand between the following thresholds:
-\begin{align*}
-B_{j,l} \, & \leq \, W_C^{j,l} \, \leq \, T_{j,l} \\
-\text{Where :} & \\
-B_{j,l} &= max \{ x \in I_{j,l} \, | \, x \leq W_C^{j,l} \} \,\,\, , \,\,\, T_{j,l} = min  \{ y \in I_{j,l} \, | \, y \geq D_C^{j,l} \} \\
-I_{j,l} &= \{ \overline{W}_{l} + \sqrt{2} \sigma_{\epsilon_C}, \overline{W}_{l} - \sqrt{2}\sigma_{\epsilon_C}, \overline{W}_{j} + \sqrt{2} \sigma_{\epsilon_C},  \overline{W}_{j} - \sqrt{2} \sigma_{\epsilon_C}  \} \\
-W_C^{j,l} &=  w_C^{j,l} + \frac{ \eta_C }{ V^{j,l} } 
-\end{align*}
-Bottom, $B_{j,l}$, and top, $T_{j,l}$, thresholds sandwich connection demand $W_C^{j,l}$ and are drawn from the full set of possible thresholds, $I_{j,l}$, above and below the tariff kink points, $\overline{W}_{l}$ and $\overline{W}_{j}$.
-In cases with high variance in consumption shocks, kink points $j$ and $l$ may span many other marginal prices, $k$ where $l \leq k \leq j$.
-At the same time for small consumption shocks and large distances between price thresholds, this expression simplifies to the linear case in equation (\ref{equation:demandlinear}).
-%T &= \{ \overline{W}_{0} + \sqrt{2} \sigma_{\epsilon_C}, ..., \overline{W}_{N} + \sqrt{2} \sigma_{\epsilon_C}, \overline{W}_{0} - \sqrt{2} \sigma_{\epsilon_C}, ..., \overline{W}_{N} - \sqrt{2} \sigma_{\epsilon_C}  \} \\
-%min \{ \overline{\eta}^{j}_{j,U}, \overline{\eta}^{j}_{l,U} , \overline{\eta}^{j}_{j,L}  , \overline{\eta}^{j}_{l,L} \} \, \leq \, &\frac{ \eta_C }{ V^{j,l} } \, \leq \, max  \{  \overline{\eta}^{j}_{j,U} , \overline{\eta}^{j}_{l,U} , \overline{\eta}^{j}_{j,L}, \overline{\eta}^{j}_{l,L} \}
-%The number of price segments between $j$ and $l$ depends on the extent to which
-
-Constructing the full demand schedule for each connection requires simply connecting these demand segments to span the full range of consumption choices.
-However since targeted demand depends on the variance in consumption shocks, $\sigma_{\epsilon_C}$, there can be different optimal demand functions for different levels of $\sigma_{\epsilon_C}$.
-To determine a single piecewise demand function, I take the approach of (1) assuming ex-ante bounds on $\sigma_{\epsilon_C}$, (2) constructing the implied optimal demand function given these bounds, and (3) estimating the model to see if the estimated $\sigma_{\epsilon_C}$ rejects these bounds in the data.
-Appendix~\ref{appendix:sigmanuassumptions} provides the results of this exercise identifying a range of $\sigma_{\epsilon_C}$ that is consistent with the data.
-Appendix~\ref{appendix:optimaldemand} describes the demand function given these bounds along with a visual example demand curve in Figure~\ref{figure:intuitivedemand}.
-
-%Solving for the the best-response function, and summing across all households $C$ yields connection level demand:
-%\begin{align*}
-%d_{C}^{j,l}       		&= \frac{ 1}{ V^{j,l} } \Big ( \Gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2S} \big  [ p^{j} + p^%{l} - \sum_{k=l}^{j} \overline{W}^{k} (\frac{p^{k} - p^{k-1}}{\sqrt{2}{\sigma_{\epsilon_C}}}) \big ]  \Big )    \\
-%V_{C}^{j,l}	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p_j - p_l}{\sqrt{2}\sigma_{\epsilon_C}}) 
-%\end{align*}
-
-\subsubsection{Deriving the Likelihood Function}
-
-Given the optimal consumption choice, $W_C$, for each connection, observed consumption for a particular connection, $Q_C$, becomes the sum of optimal consumption and the total consumption shock for that connection, $\epsilon_C$:
-\begin{align}\label{equation:observeddemand}
-Q_C &= W_C + \epsilon_C
-\end{align}
-The probability of observing any consumption outcome, $Q_C$, can be expressed as the sum of the probability that the preference shock, $\eta_C$, locates the households within a particular price segment multiplied by the joint probability that the consumption shock, $\epsilon_C$, and the preference shock are equal to $Q_C$ conditional on being in this price segment.
-
-%\overline{\eta}^{B_p,k}_{B_{\overline{W},k},B_{\sigma}}
-%Similarly, denote the variance term for each segment as $V_k = V^{j_k,l_k}$. 
-% Let total demand within each segment simplify to $D_{j,l} = \frac{ d^{j,l} }{ V^{j,l} }  + \frac{ \eta_C }{ V^{j,l} } $. 
-These probabilities allow for the derivation the likelihood function for each consumption realization, using some additional notation.\footnote{By allowing households to anticipate exogenous shocks to their consumption, this approach builds on the standard framework of \cite{burtless1978effect} and \cite{moffitt1986econometrics} to estimate demand over non-linear budget constraints, which has been recently implemented by \cite{szabo2015value} and \cite{mcrae2014infrastructure}.}  For each demand segment, denote the bottom threshold for the preference shock needed to reach that segment as, $\overline{\eta}_{B,j} = B_{j,l} - w^{j,l} $ and the top threshold as $\overline{\eta}_{T,l} = T_{j,l} - w^{j,l} $.\footnote{Conditions on $\eta_C$ defining each segment are given in more detail in Appendix~\ref{appendix:optimaldemand} equation (\ref{equation:generaldemand}).}  Define the variance-adjusted preference shock as $\Psi = \frac{\eta_C}{V_{j,l}}$.
-Let the sum of the two stochastic terms equal $\zeta = \Psi + \epsilon_C$.
-For any random variable, $x$, denote the cumulative distribution function as $F_x$ and the corresponding probability distribution function as $f_x$.
-Also, let $\phi$ and $\Phi$ denote the standard normal p.d.f.
-and c.d.f.
-respectively.
-Given equation (\ref{equation:generaldemand}), the contribution to the likelihood function for consumption observation for each connection can be written as:
-\begin{align}\label{equation:llcontributionlinear}
-\sum_{j} f_{\zeta}( Q - W^{j,l} ) \Big [ F_{ \Psi | \zeta = Q - W^{j,l} } (\overline{\eta}_{T,l}) - F_{ \Psi | \zeta = Q - W^{j,l} } (\overline{\eta}_{B,j})  \Big ]
-\end{align}
-This expression takes the sum of the densities of $\zeta$ for each consumption level weighted by the probability that the preference shock $\Psi$ locates the desired consumption level for that household between the two thresholds, $\overline{\eta}_{T,l}$ and $\overline{\eta}_{B,j}$ over all thresholds.
-Given that $\eta_C$ and $\epsilon_C$ are assumed to be independent and normally distributed, the terms in equation (\ref{equation:llcontributionlinear}) can be rewritten using both the convolution and conditional distributions of multivariate normals:
-\begin{align*}
-f_{\zeta}( Q - W^{j,l} ) &= \frac{1}{\sigma_{\zeta}} \phi(\frac{Q - W^{j,l}}{\sigma_{\zeta}} ) \\
-F_{ \Psi | \zeta = Q - W^{j,l} } (\overline{\eta}_{T,l}) &= \int_{-\infty}^{\overline{\eta}_{T,l}} f_{\Psi | \zeta = Q - W^{j,l}} (x) dx \\
-&= \int_{-\infty}^{\overline{\eta}_{T,l}} \frac{1}{\sigma_{\zeta} \sqrt{1-\rho^2}}\phi \Big ( \big ( \frac{ x V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) dx \\
-&= \Phi \Big ( \big ( \frac{\overline{\eta}_{T,l} V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) \\
-\text{Where:} &\\
-q^{j,l} &= \frac{(Q - W^{j,l})}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta} = \sqrt{ \frac{\sigma_{\eta}^2}{V_{j,l}^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho = \frac{ \sigma_{\eta}}{  \sigma_{\zeta} V_{j,l}  }
-\end{align*}
-Given these terms, equation (\ref{equation:llcontributionlinear}) can be rewritten in the following way:
-\begin{align}\label{equation:LLikelihood}
-\begin{split}
-LL &= \sum_{j}  \frac{1}{\sigma_{\zeta}} \phi (q^{j,l}) \Big[ \Phi \Big ( \big ( \frac{\overline{\eta}_{T,l} V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big ) -  \Phi \Big( \big ( \frac{\overline{\eta}_{B,j} V_{j,l}}{\sigma_\eta} -  \rho q^{j,l} \big )\frac{1}{\sqrt{1-\rho^2}}   \Big)\Big]
-\end{split}
-\end{align}
-Summing each part of the demand function in equation (\ref{equation:generaldemand}) in the likelihood expression in equation (\ref{equation:LLikelihood}) computes the probability of observing consumption outcomes for each connection.
-In order to include multiple time periods, the model captures variation in consumption over time by assuming that each household receives independent draws of preference shocks, $\eta_{i,t}$, and consumption shocks, $\epsilon_{i,t}$, which aggregate at the connection-level to $\eta_{C,t}$ and $\epsilon_{C,t}$ respectively for each month, $t$.
-All other parameters are assumed to remain stable over time.
-The full log-likelihood is computed by summing the log of the likelihood in equation  (\ref{equation:LLikelihood}) over all connections and time periods.
-% \begin{align*}
-% f_{\zeta}( Q - D_k ) &= \frac{1}{\sigma_{\zeta,k}} \phi(\frac{Q - D_k}{\sigma_{\zeta,k}} ) \\
-% F_{ \Psi | \zeta = Q - D_k } (\overline{\eta}_{k}) &= \int_{-\infty}^{\overline{\eta}_{k}} f_{\Psi | \zeta = Q - D_k} (x) dx \\
-% &= \int_{-\infty}^{\overline{\eta}_{k}} \frac{1}{\sigma_{\zeta,k} \sqrt{1-\rho_k^2}}\phi \Big ( \big ( \frac{ x V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) dx \\
-% &= \Phi \Big ( \big ( \frac{\overline{\eta}_{k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) \\
-% \text{Where:} &\\
-% q_k &= \frac{(Q - D_k)}{\sigma_\zeta}, \hspace{.4cm}  \sigma_{\zeta,k} = \sqrt{ \frac{\sigma_{\eta}^2}{V_k^2} + \sigma_{\epsilon_C}^2}, \hspace{.4cm} \rho_{k} = \frac{ \sigma_{\eta}}{  \sigma_{\zeta,k} V_k  }
-% \end{align*}
-% Given these terms, equation (\ref{equation:llcontributionlinear}) can be rewritten in the following way:
-% \begin{align}\label{equation:LLikelihood}
-% \begin{split}
-% LL &= \sum_{k=1}^{K}  \frac{1}{\sigma_{\zeta,k}} \phi (q_{k}) \Big[ \Phi \Big ( \big ( \frac{\overline{\eta}_{T,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big ) -  \Phi \Big( \big ( \frac{\overline{\eta}_{B,k} V_k}{\sigma_\eta} -  \rho_k q_{k} \big )\frac{1}{\sqrt{1-\rho_k^2}}   \Big)\Big]
-% \end{split}
-% \end{align}
-\subsubsection{Households using from Water Small-Scale Providers}
-
-While the vast majority of households use piped water, around 6\unskip\% of households still source their water from small-scale water vendors.
-In this model, these small-scale sources are collapsed into a single vendor category, which is modeled as a perfect substitute to piped water and is characterized by a monthly fixed cost, $F_V$, and a single marginal price, $p_V$.
-The monthly fixed cost, $F_V$, is assumed to capture primarily fixed differences in quality of service between vended water and other sources.
-Similarly, the marginal price, $p_V$, includes both the price per unit as well as any differences in water quality or ease of use relative to piped water.
-Demand for this source becomes a simple linear function of prices given by equation (\ref{equation:vendordemand}).
-\begin{align}\label{equation:vendordemand}
-w = \Gamma_i - \alpha_i p_V
-\end{align}
-Since the data do not record monthly consumption information for households using from vendors, these households do not contribute to the likelihood function (equation (\ref{equation:LLikelihood})).
-
-\subsection{Choosing a Water Source}\label{section:watersourcechoice}
-
-This section describes a sequential game where households choose their water sources given their demands for water.
-This game results in a unique equilibrium of source choices according to the preference parameters for each household as well as the costs of using each water source.
-
-%This game also allows for a mapping between the fixed costs of setting up and maintaining each water source and cross-sectional variation in source choices, which informs the third step of the estimation strategy.
-The fundamental assumption of this model is that the decision to share a water connection balances splitting the fixed costs among many households against facing higher marginal costs --- hassle costs in fetching water and free-rider costs splitting the water bill.
-
-%Recovering demand for water for each household allows for calculating the expected utility that each household receives from each water source, guiding their source choices.  
-Choosing a water source becomes a strategic decision since each household's water connection can also serve as a water source for other households in a neighborhood.
-The model assumes that each set of neighboring households plays a full-information, sequential game, deciding whether to purchase their own tap, share with a previously connected household, or purchase from a vendor.
-Assuming a sequential order of moves acts a refinement to rule out situations with multiple equilibria.
-Eliminated equilibria mainly include cases that are both strictly dominated and unrealistic such as having all households use from vendors when they would prefer to share a connection.
-
-Let superscripts index households by the order in which they move.
-Let $a^{i}$ denote the water source choice for each household $i$.
-The choices consist of (1) using from a vendor, $v$, (2) purchasing a connection, $c$, or (3) sharing with neighbor, $j$, given by $s^{j}$.
-The first mover faces a simple choice set defined by $A^{1} = \{  v, c  \}$.
-
-For all other households, define the following function that maps a previous household's choice to connect into a possible sharing opportunity:
-\begin{align*}
-g( a^{j} ) &=
-\begin{cases}
-s^j        &  \text{ if } a^{j} = c \\
-\emptyset  &  \text{ else } 
-\end{cases}
-\end{align*}
-Given this function, the choice sets for households $i>1$ consist of $A^{i} = \{ v,c,g(a^{1}),...,g(a^{i-1}) \} $ where households only have the option to share with neighbors that have previously connected.
-
-The payoffs equal the expected utilities from each source over the duration of usage.
-Since the data do not measure the exact duration for which households reside in a location using a water source, the model abstracts away from the timing of water use by assuming for simplicity that (1) households do not discount their future utilities and (2) all households demand water for an equal number of months.\footnote{These assumptions do not have a substantive impact on the results because all model primitives are independent of time.}  This approach limits the extent to which this model can examine the timing of any one-time connection fees or other upfront costs of water connections.
-Instead, the model collapses one-time fees into a single monthly fixed fee.
-Any heterogeneity in either the duration of demand or discount factors is captured by estimates of this monthly fixed fee.
-%This section now describes the payoffs in more detail.
-%% Potential limitations of this approach are discussed in more detail in the estimation section.
-
-To compute the payoffs from using vended water, households simply compute their expected utility given by equation (\ref{equation:umaxfirst}) according to their demand in equation (\ref{equation:vendordemand}).
-Let $u^{i}(v)$ capture this payoff.
-The payoff from owning a connection depends on whether other households choose to use the connection as well.
-Households are assumed to have perfect information about each other's preferences including the distributions of preference and consumption shocks.
-In order to calculate surplus from sharing, let the set $S^{i}$ contain all households that have chosen to use household $i$'s connection (including the owner).
-
-In this model, sharing affects the utility of the owner in three ways.
-First, increasing the number of sharing households splits the total water bill over more households, exacerbating any moral hazard distortions as illustrated in equation (\ref{equation:generaldemand}).
-Second, under non-linear tariffs, including more consumption on the same connection may alter the marginal prices faced by all sharing households.
-Third, in this model, owning households ($i=1$) are assumed to pay the full fixed cost, $F$, and sharing households commit ex-ante to providing a fixed transfer to the owner each month to compensate the owner.
-This transfer allows sharing households to help contribute to the fixed costs of owning and maintaining the connection.
-\input{tables/fee_even_some}\unskip\% of sharing households in the mobile survey report splitting some or all of the initial connection fee with their neighbors; for the remaining households, the owner reports paying the full connection fee.
-
-To capture this behavior, the model assumes that sharing households offer transfers to the owner which equally split their surpluses from using the connection.
-This setup is analogous to a Nash-Bargaining framework with equal bargaining weights.
-While the division of surplus does not affect the efficiency of sharing relationships, it has normative implications for the types of households that are able to benefit from these arrangements.
-Three features of the context in Manila support this assumption of a roughly equal division of surplus.
-First, these sharing arrangements feature long-term relationships between close neighbors who are also often family members.
-Second, small areas often feature multiple sharing opportunities for each household, creating some competitive pressures on sharing arrangements.
-Third, in the mobile survey, sharing households appeal to an ethic of fairness as the primary reason for dividing monthly payments instead of other reasons such as matching tariff prices or conserving environmental resources.
-
-Expected utility from using a connection alone is defined as $u^{i}(c|1)$.
-This expression can be computed by inputting demand from equation (\ref{equation:generaldemand}) with $S=1$ into utility given by equation (\ref{equation:umaxfirst}).
-Expected utility from owning and sharing a connection is defined as $u^{i}(c| S^i ) $ and expected utility for household $j$ from using a connection owned by neighbor $i$ as $u^{j}(s^{i} |S^i )$.
-%Sharing utilities can be calculated with the same method, substituting for $S$.
-
-Sharing surplus for the owner of the connection can be represented as $ O^{i} = u^{i} ( c | S^{i} ) - max \{ u^{i} (c | 1), u^{i}(v) \} $ while surplus for each other sharing household $j$ takes the form $ G^{j} = u^{j} ( s^{i} | S^{i} ) - max \{ u^{j}(c | 1), u^{j}(v) \} $.
-Let $t_{j}(S^{i})$ denote the transfer from sharing household $j$ to the owning household $i$.
-Following the outcome of a Nash bargain with equal weights, define $  t_{j}(S^{i}) = \frac{S^{i}-1}{S^{i}} G^{j} - \frac{1}{S^i} O^{i} - \sum_{k \in  S^{i} \setminus \{ 1,j \} } \frac{1}{S^i} G^{k}  $.
-The total transfer that the owner receives from all sharing partners equals $T (S^{i}) = \sum_{j \in S^{i} \setminus \{ 1 \} } t_{j} (S^{i})$.
-For example, when only two households use the connection, then $T(\{1,2\}) = t_{2}(\{1,2\}) = \frac{1}{2} (G^2 - G^{1})$, which simply divides the surplus in two.
-While these transfers are usually positive since the owner is assumed to shoulder all of the fixed costs of maintaining a connection, there may be cases where the owner will offer payment to other households to use their connection: for example, if the owner has a much larger demand for water than other users, the owner may benefit substantially from splitting the bill evenly with these other households.
-This case would be captured through a negative transfer.
-
-From a welfare perspective, these transfers help to ensure that households form efficient sharing relationships.
-For example, transfers allow neighbors to incentivize others to purchase a connection in cases when owners would not otherwise be willing to own and share a water connection.
-Transfers also serve to reconcile a tension introduced by the sequential structure of the game where a first mover may be compelled into a sharing relationship by a second mover although the first mover would rather use the connection alone.
-Transfers eliminate this possibility by calculating surplus from sharing relative to the maximum expected utility from using a vendor or using a water connection alone.
-
-Given these transfers, the payoff for household $i$ choosing to connect takes the form $u^{i} (c|S^{i}) + T(S^{i})$.
-Meanwhile, the payoff for household $j$ sharing a connection with household $i$ is $u^{j} (s^{i}|S^{i}) + t_{j}(S^{i})$.
-Both the past and future decisions of all other households enter these payoffs by determining the resulting set of sharing households, $S^{i}$, which affects expected utilities directly as well as through transfers.
-
-The last step in the specification of this game is determining the order in which households choose water sources.
-The model sequences households according to their expected net utility from owning a connection alone relative to using from a vendor, $u^{i}(c|1) - u^{i}(v)$.
-This arrangement matches the intuition that households with the greatest incentives to own and maintain a water connection would likely be the first to purchase a connection.
-Table~\ref{descriptives} shows that for connections serving two households, the owner's household size is 10\% larger than the buyer's household size on average.
-To the extent that household size serves as a proxy for demand, this finding provides suggestive evidence that larger demand households with greater utility from purchasing a water connection are also more likely to be owners.
-Given that transfers allow households to efficiently share surplus, the sequence is unlikely to have large impacts on the overall efficiency of the resulting arrangements.
-However, moving earlier may affect the welfare of particular households.
-On one hand, early movers can select to join high-value sharing relationships, crowding out these opportunities for later movers.
-On the other hand, later movers have a broader choice set of already-connected households to establish a sharing relationship.
-
-The sequential game is solved using backward induction and considering only pure-strategy equilibria.
-First, the last mover, household $I$, identifies the choices that maximize its payoffs at each possible choice set reached by the game.\footnote{In very rare cases where payoffs are equal, the tie-breaking rule prioritizes vendors, then individual connections, and finally shared connections ranked by the sequence of movers.}  Given these choices, the next-to-last mover, household $(I-1)$, can calculate its payoffs for each corresponding choice set.
-Iterating backwards, this process characterizes a unique equilibrium set of source choices for all households.
-Appendix Figure~\ref{figure:fullgametree} provides an extensive form for the game that is simulated in this paper.
-
-\subsubsection{Exogenous Interruptions to a Water Source}\label{section:hasslemodel}
-
-This section describes an extension of the model to allow for exogenous interruptions in a water source that induce households to substitute toward another water source.
-Exogenous interruptions produce useful variation in the types of water sources used by each household, serving an important role in estimating the marginal costs of transporting water from a neighbor.
-Due to shifts in the geology, road construction, or aging infrastructure, households sometimes experience underground breaks in the service pipe between the main line and the water meter.
-These leaks result in repair costs and water bills borne by households that can be large enough to force affected households to switch to an alternative water source.
-
-Descriptive evidence suggests that the decision process to choose an alternative water source in response to a leak is much different from the initial choice households face in deciding on a long-term water source.
-The mobile survey asks households which source they would substitute towards if they were to be disconnected for at least three months.
-\input{tables/neighbor}\unskip\% report that they would ``use a neighbor's tap'' while the remaining responses are roughly evenly split between using a public or private deep well, fetching from a water truck, or filling bottles at a water refilling shop.
-Although shared connections vastly outnumber households using from vendors in the population as shown in Table~\ref{descriptives}, using a neighbor's tap is much less common in response to a sudden disconnection.
-Since sharing relationships often take the form of long-term contracts, households may face high costs in reaching a temporary sharing agreement with a neighbor.
-Additional descriptive findings discussed in Section~\ref{section:hasslecostestimation} suggest that the decision to share with a neighbor is uncorrelated with the features of water demand among both the household experiencing a leak as well as their neighbors.
-These patterns indicate that substitution may be driven less by minimizing the long-term costs of using each source and more by convenience such as immediate access or relationships between neighbors.
-
-From the perspective of the sequential game, households experiencing leaks are assumed to be last-movers, which implies that other households cannot update their water source choices in response to a neighbor's leak.
-Additionally, the model assumes that all households do not anticipate any risks of leaks in making their initial connection decisions.
-Since leaks are rare events as discussed in Section~\ref{section:hasslecostestimation}, this assumption is unlikely to significantly affect predicted water source choices.
-
-Let $l$ index households experiencing a leak while $j$ indexes connections in the same neighborhood (reaching a total of $J$ connections).
-This model deviates from the initial water source choice by assigning an idiosyncratic preference term, $\xi_{A,l}$, to each alternative water source $A$ --- either using from a vendor, $v$, or sharing with a neighbor, $s^{j}$.
-$\xi_{A,l}$ captures the convenience of temporarily using each source following a sudden loss of water access.
-For example, $\xi_{A,v}$, may capture idiosyncratic, easy access to a neighbor's private deep well or a water refilling station.
-Similarly, $\xi_{A,l}$, might measure the relative social capital among potential sharing partners: nearby family members may be more willing to quickly share their connection.
-The model also includes the term $F^{S}$ to capture any fixed costs associated with setting up a temporary sharing relationship relative to simply fetching from a vendor.
-Given these preference shocks, total utility for household $l$ for using alternative $A$ can be parameterized with the following expression:
-\begin{align}\label{equation:hassleutilities} 
-\begin{split}
-U_{l}(A) &= - \mathbbm{1}\{ A \neq v \} F^{S}  + \xi_{A,l} \\
-A & \in \{v,s^{1},...,s^{J}\}
-\end{split}
-\end{align}
-$F^{S}$ captures the relative substitution to sharing relationships and to water vendors.
-This model includes the additional assumption that $\xi_{A,l}$ is distributed Type I Extreme Value and is independent of preferences for water usage.
-Under these distributional assumptions, the model predicts that conditional on choosing a sharing relationship, households evenly distribute between sharing partners.
-The probabilities of households choosing each alternative source can be written as:
-\begin{align*}
-Pr[A=v] &= \frac{e^{-F^{S}}}{e^{-F^{S}}+e J} = G \\
-Pr[A=s^{j}] &= \frac{e}{e^{-F^{S}}+eJ} = \frac{(1-G)}{J}  \\
-\text{ for } j &= 1..J
-\end{align*}
-%as $\omega$ approaches zero.  When $\omega$ equals zero,
-Let $L$ represent the total households affected by a single connection leak.\footnote{$L$ is greater than one in cases where connections serving multiple households experience a leak.}  All $L$ households in the neighborhood of a single leak are assumed to receive the same preference shock $\xi_{A,l}$ so that they follow identical substitution patterns.\footnote{This assumption may lead to a slight underestimation of the hassle costs since these households may actually distribute across many different sharing relationships, exposing them to lower points on the tariff schedule than if all households were clustered on the same connection.}
-
-These assumptions allow for the specification of a likelihood function that expresses neighbor's consumption following a leak as a function of household preferences and the hassle cost, $H$.
-Define $LL(\gamma,\alpha,S)$ as the likelihood function in equation (\ref{equation:LLikelihood}) in terms of the preference parameters--- $\gamma$ and $\alpha$ --- as well as the number of households using the connection, $S$.
-Given the probabilities above, the likelihood for consumption derived from connection $j$ after a nearby leak can be expressed as follows:
-\begin{align}\label{equation:hasslelikelihood}
-\begin{split}
-LL_{j,PostLeak} = & \frac{J-(1-G)}{J} \overbrace{LL(\gamma_j,\alpha_j,S_j)}^{\text{$L$ do not share with $j$}} + \\
-	    & \frac{(1-G)}{J}  \underbrace{LL(\gamma_j + \gamma_{L},\alpha_j+\alpha_{L},S_j+S_L)}_{\text{$L$ share with $j$}}
-\end{split}
-\end{align}
-The first term multiplies the standard likelihood for this connection by the probability that households $L$ do not share with connection $j$.
-The second term adds the probability that $L$ households choose to share with connection $j$ following the leak.
-This probability is multiplied by the likelihood corresponding to joint consumption, which includes both preference terms from connection $j$ as well from $L$ households.
-This approach recovers the hassle cost, $H$, by comparing the fixed preferences for households experiencing the leak before and after they start using from a neighbor.
-Let $pre$ take a value of one for months before a leak.
-Fixed preferences for $L$ households take the following form:
-\begin{align*}
-\gamma_{L} = &  \sum_{l=1}^{\overline{L}} ( \gamma_{l} - \alpha_{l} H_l ) \\
-H_{l} = & 
-	\begin{cases}
-	0     &  \text{ if } l=1 \text{ and } pre=1 \\
-	H   &  \text{ else }
-	\end{cases}
-\end{align*}
-Substituting to a neighbor's connection newly exposes the owner, $l=1$, to the hassle cost $H_i$ while other households $l \neq 1$ are assumed to be exposed to the hassle cost both before and after the leak.
-Section~\ref{section:hasslecostestimation} details potential limitations of this assumption.
-% Therefore, this method identifies hassle costs from variation in exposure for owners of the connection.
-
-\section{Specification and Estimation}\label{section:specificationandestimation}
-
-The estimation strategy takes place in three steps.
-In the first step, preference parameters --- fixed preferences $\gamma$, price sensitivities $\alpha$, as well as variances for the consumption and preference shocks, $\sigma_{\epsilon}$ and $\sigma_{\eta}$ respectively --- are recovered by combining monthly consumption patterns with price variation.
-The second step analyzes a quasi-experiment where households are exogenously switched from individual connections to shared connections in order to estimate the hassle cost, $H$, associated with sharing.
-In the third step, monthly fixed costs associated with an individual connection, $F$, and using a water vendor, $F_{V}$, as well as the marginal price from vendors, $p_V$, are chosen to best match cross-sectional moments in the data, including the shares of households choosing each source.
-
-\subsection{Preference Estimation}\label{section:preferenceestimation}
-
-Household preferences for water are estimated by maximizing the likelihood function in equation (\ref{equation:LLikelihood}) for consumption recorded at each connection and month.
-This section first details how each set of preferences are parameterized in the estimation:
-
-\textbf{Fixed Preferences} $\hat{\gamma_C} = (\gamma_C - \alpha_C H_C)$  :  Since consumption data is recorded for connections rather than for households, this approach estimates a separate $\hat{\gamma_C}$ for each connection from the mean observed usage for each connection.
-$\hat{\gamma_C}$ includes not only the total fixed preference parameters for households sharing a connection $\gamma_C$, but also any hassle costs faced by shared households weighted by the price sensitivity, $\alpha_C H_C$.
-Since hassle costs do not vary over time or with prices, they are indistinguishable from fixed preferences for consumption in this step of the estimation.
-I later decompose these estimates into household-level preferences and hassle costs as detailed in Section~\ref{section:fixedcostestimation}.
-
-\textbf{Price Sensitivity} $\alpha_C$  :  The estimation parameterizes household price-sensitivity terms $\alpha_i$ as a linear function of a vector of observable characteristics $Z_i$ that may affect price sensitivity so that $\alpha_i = \alpha Z_i$.
-$Z_i$ includes dummy variables for household size, type of dwelling, whether a household member is employed in a low-skilled industry, number of employed household members, and age of the head of household.
-Descriptive statistics for each variable are presented in Table~\ref{table:descriptivesestsample} in Appendix~\ref{appendix:descriptivesest}.
-For shared connections, the data include information on household size separately for owners and sharing households; however, the other observables are recorded only for owners.
-For these owner-specific measures, the estimation simply assigns the owner's characteristics to sharing households.
-While this imputation may be reasonable for spatially correlated characteristics like type of dwelling, this approach may introduce bias if sharing households have systematically different numbers of employed individuals or ages.
-Estimates of price sensitivities in Table~\ref{table:demandestimates} exhibit little heterogeneity across many of these dimensions, which suggests that any bias from mismeasurement may have small effects in evaluating policies.
-Since household-specific price sensitivities $\alpha_i$ enter linearly into the connection-level demand function in equation (\ref{equation:generaldemand}), connection-level price sensitivity can be written simply as $\alpha_C = \alpha \sum_{i=1}^{S} Z_i$.\footnote{The model does not control for seasonality or calendar time since the raw data exhibit negligible trends in water usage over time.}
-
-The empirical setting in Manila provides a broad range of price variation to identify these price sensitivity terms separately from the fixed preferences.
-First, the non-linear pricing structure given by Figure~\ref{figure:tariff} forces households to decide whether to consume above or below tariff kink points as they face monthly shocks to their demand.
-Second, regulated tariff changes over time affecting all households generate time-series variation in the tariff, which can be seen in Appendix~\ref{appendix:tariffvariation}.
-Third, I use rate-changes which affect individual connections differently over time described in more detail in Appendix~\ref{appendix:ratechangeelasticity}.
-The structural model combines all of these sources of price variation in the estimation.
-The identification assumption is that the consumption and preference shocks, $\epsilon,\eta$ are normally distributed and uncorrelated with these price changes.
-
-\textbf{Preference and Consumption Shocks} $\sigma_{\eta},\rho_{\eta},\sigma_{\epsilon},\rho_{\epsilon}$  :  %This strategy also estimates parameters governing the distribution of preference and consumption shocks.
-%Household-level preference shocks $\eta_i$ can be aggregated to a connection-level preference shock $\eta_C$ which is composed of both the standard deviation of the $\eta_i$ terms as well as the extent to which these terms are correlated between sharing households.
-%For preference shocks, the estimation recovers variance estimates for different types of connections, which are later decomposed into variance and covariances between neighboring households. 
-Heterogeneity in $\sigma_{\eta}$ is separately according to connections serving one, two, or three plus households.
-The estimation also allows $\sigma_{\eta}$ to vary non-parametrically according to quintiles of mean consumption at the connection-level.
-Specifically, the estimation includes a separate variance term for the bottom quintile of consumption as well as a term for the top two quintiles of consumption.\footnote{There is too little variation in the data to separately identify a full set of quintiles while also allowing $\sigma_{\eta}$ to vary by sharing status.}  Since larger users naturally have higher variances in their consumption, estimating a single $\sigma_{\eta}$ across all connections produces large bias in the price sensitivity coefficients, $\alpha$.
-This bias results from constraining large and small users to receive similarly scaled shocks and therefore enforcing that these users respond to the non-linear tariff schedule in similar ways.
-While using quintiles of observed consumption may be problematic since consumption choices are themselves endogenous, this approach approximates connection-specific $\sigma_{\eta}$ terms, which would be infeasible given limited months of data available for each connection.
-%The results are robust to different non-parametric specifications for $\sigma_{\eta}$.
-
-Following a similar strategy, the estimation recovers separate standard deviation terms at the connection-level for consumption shocks $\sigma_{\epsilon}$ according to the number of households using each connection.
-Since consumption shocks exhibit little heterogeneity with respect to observed consumption quintiles, I exclude these terms from the estimation to preserve parsimony.
-
-The $\sigma_{\eta}$ and $\sigma_{\epsilon}$ parameters are separately identified from the extent of consumption clustering around price thresholds relative to the overall variance of consumption.
-Greater clustering of consumption near price thresholds implies that households face small consumption shocks, allowing them to accurately target price thresholds.
-Similarly, wide variance in overall consumption is attributed to large preference shocks.
-Identification for these variance parameters relies heavily on the assumption that these parameters are normally distributed and uncorrelated with each other.
-
-%estimates of $\sigma_{\epsilon}$ and $\sigma_{\eta}$ are  according to the number of households using each connection.  
-To recover correlations of preference and consumption shocks between neighboring households given by $\rho_{\eta}, \rho_{\epsilon}$, this approach assumes that all household-level shocks are drawn from distributions with the same standard deviations --- $\sigma_{\eta}$ and $\sigma_{\epsilon}$.
-Under this assumption, any differences in estimated standard deviations for connections serving different numbers of households can be attributed to correlations in shocks between households in the same neighborhood.
-Ordering households according to the sequential game in Section~\ref{section:watersourcechoice} and assuming small neighborhoods of only three households, let the correlation terms between the first-mover and any other households in the neighborhood, $\rho_{l,1}$, be determined in terms of the following expression where the second subscripts on the $\sigma$ terms index the number of households using a connection:
-\begin{align*}
-\rho_{l,1} &= \frac{\sigma_{l,2}^2 - 2\sigma_{l,1}^2}{2\sigma_{l,1}^2} \text{ for } l =  \eta, \epsilon 
-\end{align*}
-The next expression extends this framework to identify the correlation between the second mover and all other households in a neighborhood:
-\begin{align*}
-\rho_{l,2} &= \frac{\sigma_{l,3}^2 - 3\sigma_{l,1}^2- 4 \rho_{l,1} \sigma_{l,1}^2 }{2\sigma_{l,1}^2 } \text{ for } l =  \eta, \epsilon
-\end{align*}
-Although sharing relationships and neighborhoods are limited to a maximum of three households, this approach can be used to identify correlations between an arbitrary number of sharing partners.
-
-\textbf{Sample} : The estimation uses a 10\% sample of connections from the connection survey (5,000 connections), which serves as the primary sample for the counterfactual exercises.
-This sample is combined with 2,151 connections from the quasi-experiment examined in the second step of the estimation (Section~\ref{section:hasslecostestimation}), which takes preference estimates from this step as an input.
-Together, these connections produce 349,265 months of consumption observations used in the preference estimation.
-All standard errors are bootstrapped using \input{tables/boot_max}repetitions.
-This sample does not include households using water from vendors since the data do not include information on consumption for these households.
-Section~\ref{section:fixedcostestimation} details the imputation procedure used to infer preferences for these households.
-Computationally, the estimation minimizes the likelihood function using a trust-region algorithm provided with the analytical gradient vector and Hessian matrix of the likelihood function.
-%Appendix~\ref{appendix:sigmanuassumptions} determines the ex-ante assumptions on $\sigma_{\epsilon}$ needed to identify the particular demand function.
-%The estimates are robust to varying the total and relative sample sizes of these groups.
-
-\textbf{Estimates} : Table~\ref{table:demandestimates} provides estimates for the different parameters as well as bootstrapped standard errors.
-The price sensitivity parameter, $\alpha$, exhibits some statistically significant heterogeneity across demographic measures although the magnitudes of these estimates are relatively small compared to the intercept.
-Large households have smaller price sensitivities while employment among household members and age of household head tend to increase price sensitivity estimates.
-These estimates can be difficult to interpret economically since the elasticity of demand depends not only on these $\alpha$ terms, but also on the fixed preferences for water across households.
-%Relative to living in a duplex, households in apartments and single houses exhibit greater price sensitivities with large standard errors.
-
-Estimates of the variance of consumption shocks, $\sigma_{\epsilon}$ increase slowly as the number of households using a connection increases.
-This finding provides suggestive evidence that shocks to sharing households may be negatively correlated.
-The standard deviation of preference shocks, $\sigma_{\eta}$, increases dramatically with average usage at baseline.
-After controlling for average usage at baseline, increasing the number of households per connection has a very small effect on the standard deviation of preference shocks.
-\begin{table}
-\centering
-\caption{Demand Estimates}\label{table:demandestimates}
-\input{tables/step_1_estimates_group} \\
-\vspace{.2cm}
-{\footnotesize{Sample includes 349,265 billing months for 7,151 connections. } }
-\end{table}
-To interpret these estimates in economic terms and to compare to similar studies, I compute the elasticity of demand with respect to price at the connection-level.
-Given a linear demand structure, the elasticity of demand depends on both the price sensitivity and fixed preferences for water.
-As a simplified example, consider the calculation for elasticity under a single marginal price and linear demand specification:
-\begin{align*}
-\frac{\delta Q}{\delta P} \frac{P}{Q} = \alpha_{C} \frac{P}{\gamma_{C}-\alpha_{C} P}
-\end{align*}
-According to this expression, increasing the fixed preference for water consumption, $\gamma_C$, while holding constant the price sensitivity, $\alpha_C$, mechanically reduces the elasticity.
-Many previous studies estimate heterogeneity in $\gamma_C$ according to demographics alongside a single $\alpha_C$ parameter for the population (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).
-This approach builds on these previous studies by estimating heterogeneity in both terms, which allows for a broader range of possibilities, including that larger users may be relatively more sensitive to prices than smaller users.
-To compare estimates with previous research under non-linear pricing schedules, this approach follows the same formula for computing elasticities by (1) taking draws of $\epsilon$ and $\eta$, (2) computing predicted demand under prices that are 1\% greater than current prices, and (3) comparing the average percentage change in demand before and after the price change.
-For tariff blocks equal to zero, prices are increased from 0 to 1 PhP (\cite{szabo2015value}).
-
-Table~\ref{table:elasticity} presents connection-level demand elasticity estimates across terciles of (1) imputed income for the connection owner and (2) average monthly usage for the connection.
-Elasticities exhibit little heterogeneity across imputed income levels, but substantial variation across usage levels with larger users appearing much less sensitive to prices than smaller users.
-Since many low-income households share connections with neighbors, there is a weak correlation between income and usage-level, which helps account for the lack of heterogeneity in elasticity.\footnote{Noise in the income imputation process may also weaken any correlation between elasticity and income.}  Heterogeneity in elasticities according to monthly usage is consistent with moral hazard when households share a connection:  increasing the number of households per connection increases the water use for those connections while also exacerbating free-riding behavior.
-Different water using activities across the water demand profile may also produce this heterogeneity in elasticities.
-This heterogeneity provides a potential motivation for usage-based price discrimination.
-For example, matching larger, less price-sensitive users with higher prices may allow for a more efficient allocation of water while still covering costs of production.
-\begin{table}
-\centering
-\begin{threeparttable}
-\caption{Demand Elasticities for Water Connections}\label{table:elasticity}
-\input{tables/elasticity_estimates} 
-\begin{tablenotes}
-\item {\footnotesize Elasticities are calculated from 7,151 connections making 349,265 connection-months.
-Income is imputed based on demographics, locations, and their interactions.
-Standard errors are bootstrapped at the connection level.}
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-The demand estimation yields an average elasticity of \input{tables/mean_elasticity}\unskip, which can be interpreted as the percentage decrease in quantity due to a one percentage increase in price.
-This estimate also closely matches reduced-form elasticity estimates from price-change quasi-experiment detailed in Appendix~\ref{appendix:ratechangeelasticity}.
-This estimate is in range of the 0.98 estimate from \cite{szabo2015value} as well as similar studies in the developing world that find elasticities between 0.01 and 0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).
-%is its inability to match zero consumption values observed in the data
-\begin{table}
-\caption{Model Performance}\label{table:modelperformance}
-\centering
-\input{tables/sample_prediction}
-\end{table}
-Table~\ref{table:modelperformance} compares predicted consumption from the model to observed consumption in the data.
-This exercise finds negligible differences across average consumption and the variance of consumption for connections according to sharing status.
-Closely matching observed patterns, this model improves on previous approaches to demand estimation likely by recovering a separate fixed preference term for each connection as well as rich heterogeneity in the variance terms (\cite{szabo2015value}).
-
-%\begin{figure}
-%\caption{Comparing Predicted and Observed Water Use}\label{figure:predictedwateruse}
-%\begin{center}
-%\includegraphics[scale=.77]{tables/hist_both.pdf}
-%\end{center}
-%\end{figure}
-%Figure~\ref{figure:predictedwateruse} compares the predicted histogram of consumption with observed values.
-Vertical red lines indicate the price thresholds in the tariff schedule.
-By roughly matching the smoothness of the distributions especially across price thresholds, this model improves on standard models in the literature, which often predict excessive bunching at thresholds (\cite{mcrae2014infrastructure}, \cite{olmstead2009reduced}, \cite{szabo2015value}).
-The model has difficultly rationalizing low levels of consumption likely because households face zero prices below this threshold.
-Since preference and consumption shocks are assumed to be normally distributed, the model predicts some negative consumption values.
-In the counterfactual exercises, I treat these negative realizations as zero consumption choices.
-Likewise, the model also cannot account for bunching at zero (likely capturing households that go on vacation).
-The model also predicts greater bunching around the upper price threshold despite little observed bunching in the data as large users tend to ignore this smaller jump in price.
-
-Table~\ref{table:correstimates} presents correlation estimates decomposed from the consumption and preference shocks.
-Both the consumption shocks, $\epsilon$ and preference shocks, $\eta$ demonstrate negative correlations between neighbors for owners and buyers.
-This finding suggests that neighboring households may intentionally form sharing relationships with whom their shocks are negatively correlated.
-This behavior may provide an insurance benefit in the presence of non-linear prices, reducing the risk that joint consumption exceeds price thresholds each month.
-Alternatively, these negative consumption findings may stem from households that frequently travel ensuring that at least one user is home to take care of the connection.
-For example, given the high rate of overseas workers from the Philippines, it may be common for households to match with other households with different work schedules.
-%Since I have no information on the overseas work status of individuals, I am not able to test this hypothesis empirically.
-
-\begin{table}
-\centering
-\begin{threeparttable}
-\caption{Correlation Estimates}\label{table:correstimates}
-\input{tables/corr_table_group}
-\begin{tablenotes}
-\item { \footnotesize Errors are bootstrapped at the connection level. }
-\end{tablenotes}
-\end{threeparttable}
-%\vspace{.3cm}
-%\footnotesize{1 indexes correlations with first movers \\ while 2 indexes correlations with second movers}
-\end{table}
-
-\subsection{Estimating the Marginal Cost of Sharing}\label{section:hasslecostestimation}
-
-To measure the marginal costs of sharing water, this strategy examines how much demand changes when households use their own connection versus when they use from a neighbor's connection.
-In order to observe the same connection using from both sources, I focus on sudden pipe leaks that often force households to disconnect and use from their neighbors.
-Specifically, I compare a connection's usage before disconnecting (due to a leak) to the change in usage among neighboring connections after disconnection, identifying the marginal hassle cost from the extent to which a connection may not fully offset its usage by sharing with neighboring connections.
-
-%Baseline preference parameters for both disconnecting connections and their neighbors are estimated in the procedure from Section~\ref{section:preferenceestimation}.
-Given preference parameters estimated in Section~\ref{section:preferenceestimation}, the estimation chooses the level of hassle cost, $H$ that best maximizes the likelihood function given in equation (\ref{equation:hasslelikelihood}).
-Leveraging substitution due to pipe leaks requires identifying a sample of leaking connections, the timing of leaks/disconnection, and usage for neighboring connections.
-Over 36 months, the water provider received 106,171 consumer complaints of excessive billing --- 34,927 of which can be precisely identified as underground pipe leaks along the service pipe through a text analysis of call transcripts.
-These complaints do not appear to be spatially correlated with only a handful of leaks occurring among direct neighbors.
-This approach considers any call identified as an excessive billing complaint as a possible leak.
-Instances where leaks in main water pipes reduce access for entire neighborhoods at a time are coded separately and excluded from the sample.
-Leaks are limited to cases with at least 3 months of recorded usage before the leak in order to calculate baseline water demand for these connections.
-Disconnection is defined as having 0 or missing consumption values for at least 90\% of the year following the leak date.
-Neighboring connections that connect after the leak are dropped since these connections lack the pre-period observations needed to estimate their fixed preferences for water.
-The estimation includes observations within a year and a half of the leak event to avoid bias from any possible reconnections as well as changes in the composition of neighboring households over time.
-Since many of these households are not included in the connection survey, demographic characteristics as well as sharing behavior are imputed using averages from small areas surrounding these connections.
-This imputation introduces noise in the estimation of price sensitivities for these households.
-%While some calls may not explicitly refer to leaks, in all cases these calls refer to billing errors, meter malfunctions, or other surprise events that may drive disconnection.
-
-To determine which neighbors to include, Appendix~\ref{appendix:sharingneighbor} ranks nearby households according to their distance from the leak and examines how the responsiveness of neighbors' consumption levels after a leak dissipates with distance.
-Results indicate that substitution is concentrated among the nearest four neighbors.
-Given these findings, the empirical exercise defines neighbors as the four closest connections.
-%\footnote{Neighbors ranked 6 through 8 are grouped together since there are very few of them in the radius.}
-
-Given the set of leaking households, $J=4$, as well as their preferences, the final input to the likelihood function in equation (\ref{equation:hasslelikelihood}) is the probability that leaking households choose to use from vendors.
-This probability is calibrated directly from a hypothetical question in the mobile survey, which finds that 70\% of households would use a vendor in response to a sudden disconnection for over three months.
-Directly including this parameter in the estimation requires the assumption that this hypothetical response provides an accurate measure of true behavior and is generalizable across the full population of households.
-
-To capture heterogeneity in the hassle cost, $H$ is parameterized as a linear function of two summary characteristics of local census wards.
-First, the share of single houses or apartment buildings in a local area may increase the per-unit cost of sharing since the buildings often require longer informal pipe networks with possibly more maintenance costs as compared with duplexes.
-Second, the average distance between water meters in a local area provides another useful proxy for the average distance that informal pipe networks may need to extend between households.
-Importantly, this distance measure does not account for the physical distances between sharing partners or unconnected households.
-These omissions mean that this average distance measure is likely to overestimate the true distance between all neighbors.
-Furthermore, areas with smaller physical distances are likely to increase incentives to share as well as the observed distance between meters, which may bias the effect of distance on marginal sharing costs towards zero.
-Table~\ref{table:descriptivesestsample} in Appendix~\ref{appendix:descriptivesest} includes descriptive statistics for these two measures.
-One additional concern would be that households select into sharing relationships conditional on some unobserved heterogeneity in sharing costs, which is not modeled here.
-Since households included in this quasi-experiment have selected into purchasing connections at baseline, they may face higher hassle costs compared to households that select into sharing.
-Therefore, this exercise may provide an upper-bound on hassle costs for the population.
-
-%  This assumption ensures that the hassle cost identified from the subset of leaking households can be extended to the population of households.
-One concern may be that heterogenous hassle costs induce households to select into sharing relationships conditional on these costs.
-Since households included in this quasi-experiment have selected into purchasing connections at baseline, they may face higher hassle costs compared to households that select into sharing.
-Therefore, this exercise provides an upper-bound on hassle costs for the population.
-%The mobile survey finds a range of sharing access from fetching with containers to using the same plumbing, which suggests that households face different hassle costs.
-
-The following additional assumptions are required to ensure that this empirical setting accurately captures the model described in Section~\ref{section:hasslemodel}.
-These assumptions are discussed in more detail and tested empirically in Appendix~\ref{appendix:sharingcostassumptions}.
-\begin{enumerate}
-	\item \textit{ Connections that experience a leak are representative of the population of connections. } 
-	\item \textit{ The decision to disconnect conditional on experiencing a leak is uncorrelated with water demand. } 
-	\item \textit{ The timing of a leak is uncorrelated with any underlying changes in demand. } 
-	\item \textit{ The leaking household's choice of a sharing partner is uncorrelated with that partner's water demand.  }	
-	\item \textit{ Leaks are uncorrelated with changes in neighborhood demand. }
-	\item \textit{ A leak for one household is uncorrelated with the probability of a neighboring household experiencing a leak. }
-\end{enumerate}
-
-%%% ELABORATE ON ALL THE CAPTIONS TO MAKE THE FIGURES RELATIVELY SELF-CONTAINED!
-
-\begin{table}
-\centering
-\begin{threeparttable}
-\caption{Hassle Cost Estimates}\label{table:step2estimates}
-\input{tables/step_2_estimates}
-\begin{tablenotes}
-\item \footnotesize{Estimates include 548 leaking connections and 2,151 neighboring connections, totaling 20,299 connection-months.
-\% single/home and neighbor distance are averages within wards.
-Neighbor distance is in meters.
-Standard errors are bootstrapped at the level of the leaking connection (and neighbors).
-}
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-Table~\ref{table:step2estimates} shows the coefficient estimates for the hassle cost estimation.
-The hassle cost rises quickly with the share of households living in single homes or apartment buildings (instead of duplexes).
-Similarly, increasing the average distance between households by one meter raises the predicted hassle cost by 17.59 PhP/m3.
-For the average household, the hassle cost is estimated to be \input{tables/mean_hassle}PhP per cubic meter of usage, which is approximately \input{tables/hassle_percentage}\unskip\% of the average tariff.
-
-Figure~\ref{figure:step2histogram} plots a histogram of predicted hassle costs across the population of households, finding substantial heterogeneity with a long tail of prohibitively expensive hassle costs.
-Predicted hassle costs also have a correlation of \input{tables/correlation_hassle}with household fixed water preferences.\footnote{Section~\ref{section:disaggregation} later discusses how connection-level fixed preferences $\gamma_C$ are disaggregated into household-level components, $\gamma_i$.}  This correlation has substantive implications for the impacts of counterfactual pricing policies; for example, high hassle costs may drive large users to sort away from sharing while small users can happily share water at little additional cost.
-
-With only 548 connections that experience leaks, the estimation recovers wide standard errors for all three parameters.\footnote{Since Steps 2 and 3 of the estimation rely heavily on estimated preference terms, $\gamma$, from Step 1, Appendix~\ref{appendix:incidentalparametertest} tests for bias due to noisy estimation of these incidental parameters and finds little evidence of significant bias.}  With this in mind, Section~\ref{section:tptsharingcosts} repeats counterfactual policy simulations for varying levels of the hassle cost.
-Taken together, these results suggest that the time-costs or other physical challenges associated with informally transporting water may play an important role in the extent to which households choose to use water from a neighbor's connection.
-
-%, rejecting a hassle cost of zero with 10\% confidence
-%One possibility may be that estimating a single average hassle cost for the population of connections masks significant heterogeneity across household density and dwelling type among other factors.\footnote{Future versions will estimate this heterogeneity directly.}
-
-\begin{figure}
-\centering
-\caption{Predicted Hassle Cost Distribution}\label{figure:step2histogram}
-\includegraphics[scale=.7]{tables/hassle_cost_distribution.pdf} \\
-%\vspace{cm}
-\footnotesize{Excludes top and bottom 1\% outliers}
-\end{figure}
-
-%Appendix~\ref{appendix:hasslecostbootstrap} includes more details on the bootstrapping procedure.
-
-\subsection{Fixed Cost Estimation}\label{section:fixedcostestimation}
-
-By matching observed water source choices with predicted source choices (given preference parameters from Section~\ref{section:preferenceestimation} and hassle cost estimates from Section~\ref{section:hasslecostestimation}), this step recovers the fixed costs of using a connection as well as prices associated with fetching from a vendor.
-These fixed costs capture both monthly costs --- service fees, plumbing maintenance, etc.
---- as well as one-time costs put into monthly terms --- connection fees, permitting with local governments, etc.
-
-The fixed cost estimation sample includes the random sample of 5,000 connections from the preference estimation.\footnote{This sample excludes connections used to estimate marginal sharing costs since the majority of these connections use imputed demographics.}  This sample is merged with a subsample of households using water from small-scale vendors drawn from the Census of Population and Housing 2010 as described in Section~\ref{section:data}.
-Neighborhoods of potential sharing partners are limited to groups of three households, which is consistent with the vast majority of households forming sharing relationships of three households or less.
-Within a three person neighborhood, households can share with a maximum of two other households.
-Assuming a limited neighborhood size and restricting households to only share within their neighborhoods both work to reduce sharing opportunities for households.
-Since high fixed costs for new connections incentivize sharing, this approach may underestimate the true fixed costs faced by households.
-
-\subsubsection{Disaggregating Connection Preferences to Household Preferences}\label{section:disaggregation}
-
-Simulating water sources choices requires recovering household preferences from the connection preferences estimated in Section~\ref{section:preferenceestimation}.
-Household price sensitivity, $\alpha_i$, can be inferred as a linear function of the vector of demographics specific to each household, $Z_i$, and estimates of $\alpha_C$.
-Since fixed preferences $\hat{\gamma_C}$ are estimated non-parametrically at the connection-level, I specify a parametric method of splitting $\hat{\gamma_C}$ into $\gamma_i$ for all households using demographics, $Z_i$:
-\begin{align*}
-\hat{\gamma_C}  		   		& =  \sum_{i=1}^{S} ( \gamma_i - \alpha_i H_{i} ) \\
-\hat{\gamma_C} + \sum_{i=1}^{S}  \alpha_i H_{i}		& =  \sum_{i=1}^{S}  (\lambda_{S} Z_i + \mu_{i})  
-\end{align*}
-$Z_i$ captures demographic characteristics specific to each household.
-$\lambda_{S}$ are coefficients measuring the effect of these demographics on fixed preferences $\gamma_C$.
-These coefficients are allowed to differ across connections serving different numbers of households as well as whether household $i$ is the owner of the connection.
-$\mu_{i}$ captures any residual variation that is unexplained by demographics.
-In this case, $Z_i$ only consists of household size since it is the single demographic measure reported separately for connection owners and other users.
-A linear regression recovers $\lambda_{S}$, which provides predicted levels of $\gamma_i$ for each household.
-
-Finally, any residual variation in preferences $\mu_{i}$ needs to be allocated across owning and sharing households.
-Instead of either allocating $\mu_i$ entirely to the owner or splitting $\mu_{i}$ evenly across households, this approach allocates $M \times \mu_{i}$ to the owner and $\frac{(1-M)}{S-1} \times \mu_{i}$ to neighboring users where $M$ is the ratio of average fixed preferences for single users to shared connections.
-This approach nests the assumption that connection owners are more likely to resemble individually connected households than their sharing partners.
-Another limitation is that the data only provide the total number of people using a connection for shared connections.
-Therefore, in cases where three households use a connection, people are assumed to allocated evenly between the two sharing households.
-%%% , which is consistent with the discussion in Section~\ref{section:watersourcechoice}
-
-\subsubsection{Imputing Preferences for Households using from Water Vendors}
-
-Given the full set of household-level demand parameters for connected households, preferences are then estimated for households using from vendors.
-Projected $\alpha_i$ can be computed from demographic measures $Z_i$ multiplied by the estimated price sensitivities, $\alpha$.
-Since $\gamma_i$ is estimated non-parametrically for connected households, fixed preferences need to be imputed for unconnected households.
-Fixed preferences for connected households are regressed on census ward indicators, the full set of demographic indicators used in the demand estimation (Section~\ref{section:preferenceestimation}), and their full set of interactions.
-After recovering coefficients for the sample of connected households, predicted fixed preferences can be computed for households using water from vendors.
-This method requires the assumption any that unobserved variation in preferences is uncorrelated between connected households and households using from vendors.
-This assumption may not hold if unobservable aspects of preferences drive some households to use from vendors.
-Since vendors offer high marginal prices possibly attracting households with unobservably low demand, this form of selection may lead this method to overestimate demand among households using from vendors.
-Disaggregating connection-level preferences as well as including households using from vendors combine to expand the sample from 5,000 connections to \input{tables/totalhhsmm_group}households.
-
-\subsubsection{Simulation and Estimation}
-
-%Grouping households into sets of three produces some remainder households that I remove from the sample bringing the total number of households to \input{tables/totalhhsmm_group}.-
-With the full set of household preferences, the simulation routine first groups households into random sets of three neighbors within each of the 599 wards.
-The routine then orders households in the sequential game according to their utilities from using an individual connection.
-This assumption captures the intuition that households who would have connected in the absence of any sharing are likely to be the first to take-up a new connection.
-Random draws of the preference and consumption shocks, $\eta$ and $\epsilon$, are assigned to each household so that households can compute expected utilities over \input{tables/sim_time_periods}months for all possible water source choices.
-These shocks are sampled from a multivariate normal distribution taking into account the estimated correlation between sharing partners presented in Table~\ref{table:correstimates}.
-One limitation of the model is that the linear demand structure with normal error terms also predicts occasional negative consumption values.
-Those values are rounded to zero in calculating household utility.
-%\footnote{ Future versions will not condition on observed choices in this way, and instead sample households across sharing relationships. }
-
-Households calculate payoffs following Section~\ref{section:watersourcechoice} given all potential choice sets.
-Appendix~\ref{appendix:gametreefull} maps the full game tree with three players that is simulated in the estimation.
-This sequential game is repeated \input{tables/sim_repetitions}times to construct a set of draws to compute simulated moments.
-The moments used in the estimation include the shares of households choosing different sources --- using an individual connection, using water from a neighbor, and using from a vendor --- as well as the correlation between each of these source choices and the fixed preference parameters for each household, $\gamma_i$.
-The estimation is designed to place heavier weight on matching the source-choice moments over the correlation moments because these correlations rely on possibly noisy measures of the preference parameters both due to incidental parameter issues in estimation as well as imputation for households using vended water.
-% Future versions will re-weight these moments given the boot-strapped variance-covariance matrix.
-\begin{table}
-\centering
-\begin{threeparttable}
-\caption{Fixed Cost Estimates}\label{table:smmestimates}
-\input{tables/step_3_estimates_group}
-\begin{tablenotes}
-\item \footnotesize{  Fixed costs are in PhP/month and prices are in PhP/m3.
-\input{tables/totalhhsmm_group} households across 599 wards are included in simulated method of moment estimation using source choices.
-Standard errors are bootstrapped at the connection level }
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-Table~\ref{table:smmestimates} presents the estimation results, finding a total estimated monthly fixed cost of \input{tables/fixedfee_group}PhP, which is around 50\% higher than the \input{tables/cfee_group}PhP monthly fixed fee paid to the provider.
-This finding suggests that households face sizable barriers to connecting to the water network such as land tenure insecurity or administrative costs.
-This total fixed fee is also comparable to the total monthly water bill (tariff $\times$ volume) paid to the provider each month in Table~\ref{descriptives}, suggesting that fixed costs compose almost half of the total costs of using piped water.
-
-The estimates also reveal a fixed cost for vendors equivalent to \input{tables/vendorfixedfee_group}PhP per month.
-This cost likely captures fixed quality differences between vended water and other water sources.
-The mean price for vended water of \input{tables/vendorprice_group}PhP per cubic meter is close to the highest tariff prices in Figure~\ref{figure:tariff}.
-These estimates include a modest variance term for the vendor price, which is consistent with a competitive market for alternative water sources through deep wells, tanker trucks, and water refilling stations.
-
-%These sources may also be unevenly distributed throughout the city.
-%These estimates include a sizable variance term for the vendor price, which is consistent with the large variety of small-scale water sources that are collapsed into this measure, including primarily deep wells as well as tanker trucks and water refilling stations.
-These sources may also be unevenly distributed throughout the city.
-Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option.
-As a simple out-of-sample test, Appendix~\ref{appendix:vendorpriceestimates} finds that the estimate of $p_v$ in Table~\ref{table:smmestimates} matches closely with the implied $p_v$ from data on total water expenditures for vendor households using additional census data from part of Manila.
-This exercise provides additional confidence that the vendor price estimates are within a reasonable range.
-Also, Appendix~\ref{appendix:modelfit} compares the predicted moments to the observe moments used in the estimation.
-While source moments are matched exactly by design, the estimation is able to roughly match the size and direction of the correlations of fixed preferences with the proportion connected individually and the proportion using from a neighbor.
-%Assuming that the vendor expenditures only reflect the marginal prices paid for water (excluding the fixed cost), I can express average expenditures, $E_v$, by multiplying average vendor demand by the vendor price, $E_v = (\gamma - \alpha p_v) p_v$.
-Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=37$, and price sensitivity, $\alpha=.91$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 15.7 PhP/$\text{m}^{3}$ or 37.53 PhP/$\text{m}^{3}$.
-The latter price matches closely to the estimated price of 37.16 PhP/$\text{m}^3$, providing additional support to the structural estimates.
-
-\section{Counterfactual Policies}\label{section:counterfactualexercises}
-
-To reconstruct the economic problem faced by the regulator and investigate how alternative pricing policies might impact welfare, consider the government regulator's maximization problem given by equation (\ref{equation:regulator}).
-In this problem, the regulator chooses a fixed fee, $Fee$, and a price schedule, $P$, to maximize consumer surplus while covering the costs of production (holding profits equal to zero).
-Consumer welfare is defined as the expected sum of all households' utilities subject to welfare weights, $\delta_i$, for different subpopulations, which capture any preferences the regulator may have towards redistribution.
-The counterfactual exercises consider two sets of these preferences: (1) the regulator weights all households equally and (2) the regulator only gives positive weight to households from the bottom 50th percentile of water demand, summarized by the fixed water preference $\gamma$ for each household.
-Giving preference to low-demand households intends to capture dual policy goals of ensuring access as well as minimum monthly usage levels.
-Since low-demand households are also often low-income households, this approach also provides a proxy for standard preferences toward redistribution.\footnote{Using income directly is less informative due to noise in the imputation process, especially for households that are sharing with their neighbors.}  Similarly, this approach may capture efficiency gains if connecting low-users produces positive health externalities (\cite{galiani2005water,gamper2010impact}).
-For ease of exposition, the utility function below nests the water source choices of each household.
-\begin{align}
-\begin{split}
-max_{Fee,p_{L},p_{H}} &\hspace{.4cm} E\text{\LARGE [} \sum_{i} \delta_i U_{i}(Fee,p_{L},p_{H}) \text{\LARGE ]} \\
-s.t. \hspace{.5cm} & \text{Total Connections} \times \big[ Fee - \text{Installation/Service Costs} \big] + \\
-              & \text{Total Water} \times \big[ \text{Revenue per Unit}(p_{L},p_{H})  - \text{Marginal Cost}  \big] \\
-      & \hspace{5.5cm} \geq \text{Capital Costs}
-\end{split}
-\label{equation:regulator}
-\end{align}
-The budget constraint ensures that the fixed monthly fee, $Fee$, paid to the company for each connection as well as the revenue earned for each unit of water consumption (given the non-linear pricing scheme) outweighs the costs of servicing each connection, the marginal costs of providing a cubic meter of water, as well as any capital costs associated with the pipe-network, pumping stations, and dam maintenance.
-The water provider calculates that their marginal costs are equal to 5 PhP per m3 and that the fixed fee exactly covers any installation/service costs.
-To determine the capital costs, this approach subtracts the total marginal and services costs from the total revenue earned by the company, assigning the remainder to capital costs.
-Capital costs include maintaining the pipes, pumping stations, and billing infrastructure.
-This calculation provides a close approximation to the capital-expenditures regulatory structure implemented in this context, which exactly compensates the water provider for its costs through increases in the tariff.\footnote{This approach abstracts away from any principal agent problems between the company and the regulator by assuming that the regulator has perfect information over the firm's capital investments and operating costs (\cite{laffont1993theory}).}  This regulatory problem forms the basis for evaluating the following counterfactual policies.
-All counterfactual policies evaluated below hold firm profits equal to zero.
-
-\subsection{Compensated Fixed Fee Discount}
-
-First consider a counterfactual policy where the regulator discounts the fixed fee while increasing the tariff to remain revenue neutral.
-By discounting the fixed fee by \input{tables/c_fee_discount_group}PhP, this approach mimics a policy implemented by the water provider; however, while the provider's discount decreased overall revenue, this approach offsets the discount with higher tariffs.\footnote{Appendix~\ref{section:oostest} analyzes the discount implemented by the provider as an out-of-sample test for the model, matching substitution patterns between water sources induced by the policy change.}  This counterfactual also echoes recent recommendations from policymakers and researchers including the World Bank who have advocated for lower connection fees as a way of extending access to piped water among the poor (WSUP [2013], \cite{komives2005water,jimenez2014factors,kayaga2007costs,mcintosh2003asian}).
-Figure~\ref{figure:discounttariff} provides the current tariff and the compensated tariff, which is shifted upwards by \input{tables/discount_tariff_rise_group}PhP/m3 for each tariff block to maintain revenue neutrality.
-
-\begin{figure}
-\centering
-\caption{Revenue-Neutral Tariffs \\ Pre/Post Connection Fee Discount}\label{figure:discounttariff}
-\includegraphics[scale=.7]{tables/discount_tariff_groups.pdf}
-\end{figure}
-
-Table~\ref{table:fixedfeediscount} summarizes the impacts of this change on source choices and consumer welfare, which is measured in terms of utility relative to using from a water vendor.
-While the increase in the tariff drives large users to disconnect and substitute toward vendors, the decrease in the fixed price allows some small users to jointly purchase shared connections, resulting in no change in the proportion of households using from a neighbor.
-The second row indicates substitution toward water vendors of around \input{tables/discount_vendor_change_group}percentage points in response to the higher tariff.
-These effects combine to reduce average consumer surplus by \input{tables/discount_avg_surplus_change_group}PhP per month, which is over half of the initial fixed fee discount of \input{tables/c_fee_discount_group}PhP.
-This decline translates into a \input{tables/discount_avg_welfare_change_group}percent loss of monthly household income.
-Households in the bottom \input{tables/group_percentile_group}\unskip th percentile of water users also experience lower consumer surplus although the magnitude is much less, amounting to \input{tables/discount_low_welfare_change_group}percent of monthly household income.
-Taken together, these results suggest that connection fee discount policies in this context can have unintended distributional consequences by reducing both access to piped water and even welfare for the intended beneficiaries.
-%\footnote{Consumer surplus is measured relative to utility from using vended water.}
-% a drop of \input{tables/discount_sharing_change_group}percentage points in households using water from their neighbors The decrease in the fixed fee and increase in the tariff both act to decrease the incentives for sharing a connection and leading to no change in households using water from their neighbors.
-\begin{table}
-	\centering
-	\caption{Fixed Fee Discount Counterfactual}\label{table:fixedfeediscount}
-	\input{tables/discount_estimates_group} \\
-	\vspace{.2cm}
-	\footnotesize{Low Users include the bottom 50\% of water users. \\
-	Surplus and fixed fee are in PhP/month.}
-\end{table}
-
-\subsection{Characterizing Optimal Tariff Schedules}
-
-This section considers the welfare impacts of six tariff structures in order to inform regulators facing a variety of institutional settings and redistributional priorities: while some regulators may be restricted to imposing simple two-part tariffs, others may allow for complex, non-linear price schedules like the current tariff in Manila (\cite{hoque2013state}).
-While encouraging efficient use, many developing countries also include distributional motivations for their tariff structures such as ensuring that most households reach a minimum level of usage (\cite{szabo2015value}).
-
-As a benchmark, this exercise examines a first-best tariff where (1) the marginal price equals the marginal cost, (2) every household pays a fixed fee equal to the fixed costs of installing and maintaining a connection, and (3) the regulator is able to perfectly price discriminate according to household demand, extracting additional transfers from high-demand households to exactly fund the fixed capital costs.
-According to standard industrial organization theory, this tariff is designed to perfectly maximize welfare in a world without sharing (\cite{auerbach1978two,oi1971disneyland}).
-I then compare how the current tariff in Manila performs relative to this first-best tariff structure.
-%Additionally in this case, I assume that the regulator can use these costless transfers to reallocate surplus from high users to low users in order to achieve distributional goals as well.
-
-The next tariff imposes restrictions on the regulator by only allowing for a simple two-part tariff --- Part (1) a monthly fixed fee and; Part (2) a marginal price.
-First, I identify the two-part tariff that maximizes overall consumer surplus.
-Second, I define a social two-part tariff that maximizes surplus only for low users, capturing regulator preferences toward redistribution and ensuring basic levels of access.
-Low users are defined as households with fixed preferences for water usage, $\gamma$, below the average level.
-Since households exhibit little heterogeneity in their price sensitivities, this approach provides a simple way of summarizing water demand across the population.
-%An alternative approach may be to examine welfare impacts by household incomes; however, the data only allow for noisy imputations of income, which may mask larger distributional effects.
-Additionally, placing extra welfare weight on smaller users captures the spirit of recent goals by policymakers to ensure a basic right to water.
-
-Finally, this exercise calculates optimal three-part tariffs --- Part (1) a monthly fixed fee; Part (2) a marginal price for any usage below 20 m3 per month, and; Part (3) a marginal price for any usage above 20 m3 per month.
-This structure more closely mirrors the current tariff implemented in Manila.
-Optimal three-part tariffs are computed both to maximize surplus overall and to maximize surplus only for low-demand households.\footnote{I calculate optimal tariffs for a 5\% subset of the sample since non-linear budget constraints make this process computationally expensive.
-Preliminary tests suggest that the results are robust to this sampling technique.}
-
-Does the presence of informal water sharing affect optimal prices in this context?
-To test this hypothesis, I compare optimal tariffs in a counterfactual setting where sharing is prohibitively expensive (Section~\ref{section:optimaltariffswithoutsharing}) to optimal tariffs in the current setting in Manila (Section~\ref{section:optimaltariffswithsharing}).
-
-\subsubsection{Optimal Tariffs Without Sharing}\label{section:optimaltariffswithoutsharing}
-
-Identifying optimal tariffs without sharing requires an additional assumption about the costs to the water provider in this counterfactual setting.
-When households are unable to share, the provider raises less revenue at current prices.
-To account for this lost revenue, capital costs are recalculated to match the revenue raised from implementing the current tariff when sharing is not possible.
-This procedure allows for direct welfare comparisons between the current tariff and counterfactual tariffs; however, the magnitudes of these results are not directly comparable to counterfactuals with sharing explored later in Section~\ref{section:optimaltariffswithsharing}.
-
-Figure~\ref{figure:optimaltariffnosharing} provides the optimal tariffs without sharing, and Table~\ref{table:optimaltariffnosharing} includes the corresponding optimal monthly fixed fees as well as the impacts of these tariff structures on the share of households using vendors and using neighboring connections.
-The last two rows include consumer surplus measures for the average household as well as the bottom 50\% of users.
-Since producer surplus is always held to be zero in these exercises, these consumer surplus measures fully capture welfare.
-For ease of comparison, Table~\ref{table:optimaltariffnosharing} also includes the average tariff level in the second row.
-
-\begin{figure}[!htp]
-\centering
-\caption{Optimal Tariffs Without Sharing}\label{figure:optimaltariffnosharing}
-\includegraphics{tables/no_shr_tariff_groups.pdf}  
-\end{figure}
-
-\begin{table}[!hbp]
-\centering
-\caption{Optimal Tariffs Without Sharing}\label{table:optimaltariffnosharing}
-\resizebox{\textwidth}{!}{%
-\input{tables/welfare_no_sharing_groups}
-}	\\
-\footnotesize{The first-best fee does not include individual transfers imposed by the regulator. \\  Social tariffs place all welfare weight on the bottom 50\% of water users. All terms are monthly.}
-\end{table}
-
-The first-best tariff schedule produces the highest level of consumer surplus reaching \input{tables/first_best_surplus_group}PhP/month or \input{tables/first_best_surplus_percent_income_group}\unskip\% of household income.
-This tariff also produces the minimum share of households using vended water at \input{tables/first_best_percent_vendor_group}\unskip\%.
-With costless transfers, the regulator could theoretically reallocate all surplus to the lowest users providing an upper bound on redistribution through pricing at one and a half times the average surplus.
-
-Relative to the first-best, implementing the current tariff without sharing reduces average surplus dramatically and increases the share of households using vended water by raising the average marginal price.
-The optimal two-part tariff (third column) features a higher fixed fee which affords a lower marginal price at all consumption levels.
-Compared to the current tariff, the optimal two-part tariff brings consumer surplus up to \input{tables/tpt_surplus_improvement_group}\unskip\% of the first-best average surplus.
-These welfare gains are primarily driven by increased consumption for large users since surplus for low-users is cut in half and the share of households using from vendors increases by 8 percentage points.
-
-The optimal social tariff (fourth column) maximizes surplus for households with below average demand.
-This social tariff improves welfare for low-users by reducing the fixed fee dramatically and almost doubling the marginal price.
-Low fixed fees incentivize small users to connect to the network, reducing the share of households using from vendors by around 14 percentage points.
-Average surplus declines since high marginal prices reduce consumption for large users; however, surplus for low users more than doubles.
-This result points to the attractiveness of using non-linear pricing to achieve normative goals of redistribution when shared connections are infeasible.
-
-By adding an extra segment to the tariff schedule, the optimal three-part tariff (fifth column) tests the extent to which more complex pricing schedules can improve efficiency.
-Figure~\ref{figure:optimaltariffnosharing} graphs this three-part tariff relative to the current tariff.
-The shape of the optimal three-part tariff resembles the current tariff structure with a low first segment followed by a higher second segment (although the optimal three-part tariff maximizes total surplus while the current tariff is likely motivated by distributional concerns).
-The intuition for this finding is that a low first price segment combined with a high fixed fee provides an additional mechanism for the regulator to price discriminate on the extensive margin; under this pricing regime, only relatively large users connect and their high usage levels allow the regulator to further lower prices (since the marginal price well exceeds marginal cost).
-Despite this attempt to improve welfare, surplus improvements are negligible relative to the optimal two-part tariff.
-
-%%%% FIX THIS DISCUSSION HERE !!! %%%%
-Compared to the social two-part tariff, the social three-part tariff (sixth column) uses a higher fixed fee to achieve a slightly lower marginal price for water usage up to 20 m3.
-The higher fixed fee drives another 2\% of households to use from vendors; however, the lower marginal price benefits low-users who remain connected.
-Relative to the social two-part tariff, the social three-part tariff achieves a surplus gain of over 8 PhP/month for low-users while lowering average surplus by around 25 PhP/month.
-
-% has more success in redistributing surplus by using an additional tariff block to extract greater revenue from large users and improve reallocation to low users.
-Relative to the social two-part tariff, the social three-part tariff achieves this goal by offsetting a lower first price segment with a higher second price segment.
-
-These results provide empirical support for the widespread practice of using non-linear pricing schedules to achieve goals of redistribution (\cite{hoque2013state}).
-When sharing is prohibitively expensive, non-linear pricing is able to over double surplus for the bottom half of water users (relative to optimal pricing that weights all users equally).
-
-%With a lower fixed fee and increasing marginal price schedule, the social three-part tariff is the counterfactual tariff that most closely resembles the shape of the current tariff in Manila.
-
-\subsubsection{Optimal Tariffs With Sharing}\label{section:optimaltariffswithsharing}
-
-\begin{figure}[!htp]
-\centering
-\caption{Optimal Tariffs With Sharing}\label{figure:optimaltariffsharing}
-\includegraphics{tables/shr_tariff_groups.pdf}
-\end{figure}
-
-\begin{table}[!hbp]
-\centering
-\caption{Optimal Tariffs With Sharing}\label{table:optimaltariffsharing}
-\resizebox{\textwidth}{!}{%
-\input{tables/welfare_sharing_groups}
-}
-\footnotesize{The first-best fee does not include individual transfers imposed by the regulator.
-\\  Social tariffs place all welfare weight on the bottom 50\% of water users.
-\\ Surplus is measured in terms of PhP/month.}
-\end{table}
-
-This section calculates optimal tariffs in the current environment in Manila (where households may choose to share).
-Figure~\ref{figure:optimaltariffsharing} plots the marginal prices associated with each counterfactual tariff.
-Table~\ref{table:optimaltariffsharing} computes the impacts of these tariffs on source choices as well as welfare.
-Moving from the current tariff schedule (second column) to an optimal two-part tariff (third column), I find large welfare improvements on the order of \input{tables/tpt_improvement_percent_sharing_group}\unskip\% of consumer surplus or \input{tables/tpt_improvement_income_sharing_group}\unskip\% of household income.
-These gains are mainly enjoyed by large users benefiting from a lower marginal price relative to the current tariff since average consumption nearly doubles.
-At the same time, flattening the tariff reduces the implicit ``tax'' on pooling consumption on a shared connection, allowing low-users to enjoy lower marginal prices from their neighbors' connections.
-These lower marginal prices compensate for the higher hassle and free-rider costs from sharing, boosting surplus for low-users by around 50\% and reducing the share of households using from vendors from 4\% to 1\%.
-Low marginal prices combined with higher fixed fees both work to increase the share of households using from a neighbor's connection from 25\% to 44\%.
-
-%zooming in on tariffs below 20 PhP/$\text{m}^{3}$ in order to highlight distinctions between the two-part and three-part tariffs. 
-%The optimal fixed fee lies below the current fixed fee, which is priced at the cost of installing and maintaining a connection.
-Since households incur hassle costs and free-rider distortions from splitting the bill in sharing connections, pricing below cost allows the regulator to encourage households to substitute away from shared connections toward individual connections and avoid these hassle costs at the margin.
-By subsidizing individual connections, the two-part tariff in column three performs very close to the first-best tariff in terms of average consumer surplus.
-
-A social two-part tariff (fourth column) reallocates surplus to low-users by subsidizing fixed connection fees with a higher marginal price.
-Compared to an optimal tariff, this social tariff brings the percentage using from vendors to zero while also decreasing the share using from neighbors by 7 percentage points.
-These improvements in access come at a small cost to average consumption, but only increase surplus for low-users by a modest \input{tables/tpt_social_surplus_change_low_sharing_group}PhP/month.
-By contrast, social tariffs almost doubled low-user surplus in a world without sharing (Section~\ref{section:optimaltariffswithoutsharing}).
-These findings suggest that informal sharing networks may constrain the effectiveness of non-linear pricing in redistributing surplus.
-
-%While manipulating the two-part tariff proved to be an effective redistributive strategy in a world without sharing ,
-%while average surplus declines by \input{tables/tpt_social_surplus_change_avg_sharing_group}PhP/month.   
-%maximizing welfare for low users counterintuitively involves increasing the fixed fee in order to subsidize a very low marginal price.  
-%This tariff maximizes the share of households using from neighbors while also driving a significant share of households toward water vendors.
-Since low-users are able to split the fixed fee with their sharing partner, they can enjoy greater consumption at the low marginal price.
-%Despite this relatively extreme pricing schedule,
-
-An optimal three-part tariff with sharing (fifth column) follows the same pattern as in the case without sharing: increasing marginal prices select for high-usage households to connect, which provide greater revenue to cover the fixed costs.
-As before in Section~\ref{section:optimaltariffswithoutsharing}, this tariff produces negligible changes in welfare.
-Figure~\ref{figure:optimaltariffsharing} indicates an optimal three-part tariff with an almost zero first price segment followed by a much higher second price segment, which again broadly aligns with the current tariff structure.
-This tariff structure supports the ``life-line'' tariff as a way of efficiently maximizing surplus (rather than achieving distributional goals).
-Column six (along with Figure~\ref{figure:optimaltariffsharing}) finds that a social three-part tariff subsidizes entry with a negative fixed price, which is offset by a high marginal price for usage up to 20 m3.
-This tariff reduces average surplus by over 8 PhP/month to produce only 0.1 PhP/month of additional surplus for low-users.
-This result underscores the extent to which sharing networks constrain the ability of cities to achieve redistribution through complex, non-linear pricing strategies.
-
-%finds no difference in the optimal social two and three part tariffs.
-
-\subsubsection{Optimal Two-Part Tariffs and Marginal Sharing Costs}\label{section:tptsharingcosts}
-%and \ref{section:optimaltariffswithsharing} 
-To investigate mechanisms driving these optimal pricing schedules, this section considers how the optimal two-part tariff varies continuously with counterfactual levels of the hassle cost, $H$.
-I follow the same routine as in Section~\ref{section:optimaltariffswithoutsharing} by (1) calculating total revenue raised under the current tariff (in Figure~\ref{figure:tariff}) given the counterfactual hassle cost, (2) recalculating the implied capital costs from total revenue under this hassle cost, and (3) determining the optimal two-part tariff maximizing total consumer surplus while just covering costs.\footnote{As the hassle cost rises, the current tariff raises less revenue, lowering the capital costs.
-The patterns below are robust to instead holding the capital costs fixed while increasing the hassle costs.}
-
-Figure~\ref{figure:tptshrcosts} plots the optimal marginal price, fixed fee, and share of the population choosing each water source as a function of the hassle cost.
-The vertical gray lines show the average estimated hassle cost of 15.93 from Section~\ref{section:hasslecostestimation}.
-When hassle costs are very low, the regulator chooses a relatively high marginal price and low fixed fee.
-This equilibrium maximizes sharing so that one third of households purchase connections and each share their connection with two neighbors.
-The high marginal price serves as an way to mitigate overconsumption from free-riding on these shared connections: when three households share a tap, they respond to one third of the marginal price through spitting the bill.
-Therefore, setting a price around 11.5 PhP/$\text{m}^3$ ensures that households actually respond closer to the marginal cost of 5 PhP/$\text{m}^3$.
-This high marginal price also raises greater revenue allowing the regulator to lower the fixed fee.
-As the hassle cost increases to 5 PhP/$\text{m}^3$, the optimal marginal price decreases as more households substitute away from sharing arrangements.
-This substitution reduces the extent of free-rider distortions, driving the marginal price closer to the marginal cost.
-
-As the hassle cost increases from 5 PhP/$\text{m}^3$ to around 13 PhP/$\text{m}^3$, it becomes optimal for the regulator to increase the marginal price as a way of taxing shared connections and subsidizing individual connections.
-In this range, households are not able to internalize the extent to which costly sharing relationships reduce their own contributions to the capital costs.
-Therefore, a high marginal price serves as an additional disincentive for sharing.
-
-Above 13 PhP/$\text{m}^3$, the hassle cost becomes large enough to disincentivize sharing on the margin, allowing the regulator to begin lowering the marginal price again.
-Yet, at these high levels of hassle cost, some households begin substituting toward vended water, providing a new incentive for subsidizing access by keeping prices above the marginal cost (consistent with theoretical work by \cite{auerbach1978two}).
-The slow decline in marginal price over this range helps to offset the increasing hassle cost, reducing the rate of substitution away from shared connections.
-%From a distributional perspective, I find that a hassle cost of around 18 PhP/$\text{m}^3$ represents a threshold where the bottom 50\% of users transition from preferring a very high fixed fee as in Section~\ref{section:optimaltariffswithsharing} to preferring fixed fee subsidies as in Section~\ref{section:optimaltariffswithoutsharing}.
-
-This exercise demonstrates how the presence of water sharing can have additional implications for optimal water pricing.
-Free-rider behavior among sharing households creates an incentive for the regulator to maintain high marginal prices, and large hassle costs similarly motivate high marginal prices as an efficient tax on shared connections.
-
-\begin{figure}
-\caption{Two-Part Tariffs and Sharing Hassle Costs}\label{figure:tptshrcosts}
-\begin{center}
-\includegraphics[scale=.55,valign=t]{tables/tpt_full_graph_prices.pdf}
-\includegraphics[scale=.58,valign=t]{tables/tpt_full_graph_shares.pdf}\\
-{\footnotesize The vertical gray lines show the estimated hassle cost of 15.14 PhP/$\text{m}^3$ from Section~\ref{section:hasslecostestimation}.}
-% \\ Marginal prices and fixed fees are smoothed with a moving average.}
-\end{center}
-\end{figure}
-
-\section{Conclusion}\label{section:conclusion}
-
-% didnt show this yet....
-This paper finds that incorporating a model of informal sharing networks into a standard regulatory problem produces substantively different policy recommendations with potentially large welfare implications.
-
-Observing that ``connection fees are too high, and lump sum upfront payments exclude the poor,'' the Asian Development Bank has argued for cutting upfront payments and steeply increasing water prices, emphasizing that ``the irony of the situation is that the main way to help the poor is to substantially raise tariffs.''\footnote{This quote is from \cite{mcintosh2003asian} pages 40 \& 45.
-The authors advocate for a ``three-block system with the lifeline consumption rate at 0-6 m3 (tariff limited to 5\% of household income for the lowest 10th percentile), consumption of 6-20 m3 charged at a rate to recover all financial costs, and consumption of more than 20 m3 charged at a penalty rate equal to about \$1/m3 (to conserve water)'' (\cite{mcintosh2003asian} p.76).}  In this paper, I show that the presence of informal sharing reverses this common intuition among policymakers: high-fixed fees are less of a barrier for low-income households when they can split these fees by sharing with their neighbors.
-Moreover, low marginal prices help to prevent low-income households from substituting toward non-piped, vendor sources.
-
-By capturing demand heterogeneity, the costs of sharing, as well as source choices, the structural model provides additional insights into how a range of non-linear pricing policies affect both access and welfare.
-In the presence of sharing, the model finds that complex non-linear pricing is largely ineffective at achieving efficiency and equity gains because sharing provides a water resale market, undermining any usage-based price discrimination.
-The structural model also allows me to forecast how sharing costs affect optimal prices.
-I find that optimal prices balance competing goals of pricing at marginal cost and taxing sharing when it is too costly.
-
-In focusing on water sharing behavior, this approach abstracts away from several features that may also affect optimal water pricing.
-First, I do not directly model environmental, health, or other externalities associated with piped water use.
-Water shortages may lead policymakers to promote conservation through higher marginal prices while positive health externalities may motivate further subsidizing piped water (\cite{timmins2002measuring}, \cite{galiani2005water}).\footnote{\cite{bennett2012does} shows that piped water can also lead to negative externalities through worse sanitation, possibly motivating higher prices for piped water in some cases.}  Second, I assume that the government regulator is able to fully observe production costs for the water provider, eliminating scope for prices to correct for possible principal-agent frictions as characterized by \cite{laffont1993theory}.
-Finally, the counterfactual exercises simulate the public-private partnership regulatory framework in Manila by assuming that revenue must fully cover production costs.
-Additional data on the costs of raising public funds and risks of regulatory capture would allow for a more flexible analysis taking into account the possibility of using public subsidies for water infrastructure (\cite{laffont2005regulation}).
-
-Taken together, this paper suggests that households may act as efficient subcontractors in redistributing water to their neighbors.
-Instead of sending trained engineers to install and maintain connections in dense neighborhoods, providers can instead rely on informal networks to extend water distribution.
-From this perspective, cities may benefit from considering how prices not only might encourage access and redistribute consumer surplus, but also may affect the endogenous formation of water sharing networks.
-For example, price discriminating according to neighborhood income instead of by monthly usage levels may achieve similar goals of redistribution without distorting sharing networks.
-While this policy may not be appropriate in Manila since neighborhoods are often very heterogeneous in income, this approach may work well in other contexts where neighborhoods are more segregated.\footnote{For example in Colombia, electricity rates vary according to the social category of each neighborhood (\cite{mcrae2014infrastructure}).}
-
-Since sharing networks make it more difficult to implement usage-based price discrimination, cities may benefit from considering a broader range of policies to improve welfare from piped water use.
-For example, cities may be able to lower the frictions associated with these sharing networks by providing technical resources for managing plumbing networks or distributing extra water meters to assist households in accurately splitting the bill.
-The empirical results also confirm previous findings that substantial barriers exist for households to connect to the network (\cite{devoto2012happiness}).
-Cities may be able to similarly achieve substantial welfare gains by streamlining administrative requirements for new connections and by allowing households to pay connection fees in smaller increments.
-
-%On top of the broad recommendation for high fixed fees and low marginal prices, the structural model also
-
-% lowering fixed fees and increasing block prices to improve access to piped water.
-
-% This paper demonstrates that pricing policies intended to increase water access especially among the poor can have unintended consequences when low-income households can simply access the piped water network through their neighbors.
-
-% The counterfactual exercises find that a simple two-part tariff structure outperforms the increasing block tariff currently implemented in Manila in terms of overall access to water, total welfare, and even welfare among the bottom half of water users.
-In this counterfactual, high fixed costs of accessing an individual connection allow for sharing networks to play an important role in extending water access despite sizable hassle costs.
-
-\pagebreak
-
-%Taken together, these findings suggest that rather than serve as evidence of underdevelopment, shared water taps, which are common across the developing world, may instead act as an efficient solution to the ``last-mile'' problem of connecting the poor to bulk water infrastructure.
-
-\begin{appendices}
-%\appendix
-
-%\renewcommand\thefigure{\thesection.\arabic{figure}}
-%\renewcommand\thetable{\thesection.\arabic{table}}
-
-\renewcommand{\thesection}{A.\Roman{section}} 
-\renewcommand{\thesubsection}{\thesection.\roman{subsection}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Connection Fee}\label{appendix:connectionfeeamortization}
-
-This section constructs a total fee paid to the water provider each month as the sum of the monthly service fee, 150 PhP/month on average, and the connection fee of 6,000 PhP, amortized over the duration of the water connection.
-To amortize the connection fee without information on full durations of residence for all households, I assume that households move to Manila, use a water connection for 80 months, then leave the city.
-This assumption is roughly consistent with the hazard rate of disconnection for water connections.
-Dividing the connection fee by 80 months and adding it to the monthly service fee results in a total monthly fee of 225 PhP.
-Any credit constraints, discount rates, or other barriers to accessing a water connection are captured in monthly terms in the fixed cost estimates in Section~\ref{section:fixedcostestimation}.
-
-\section{Assessing the Sampling of the Connection Survey}\label{appendix:pawssampling}
-
-This section assesses the extent to which the connection survey constitutes a representative sample of connected households.
-The documentation for the connection survey indicates that sampling was stratified based on geographic areas, assigning a target number of households owning connection to be survey according to the Census population for each area.
-Households owning connections were randomly interviewed until these targets were reached.
-While ensuring a random sample of connections within areas, this method may oversample areas with few connections.
-To test this hypothesis, the following equation predicts the share of connections surveyed in each Meter Reading Unit (MRU) --- the smallest geographical unit used by the water provider including a couple hundred water connections on average --- according to demographics of households owning connections, $Z_{MRU,i}$, in each of these MRUs:
-\begin{align*}
-ShareSurveyed_{MRU} = \beta Z_{MRU,i} + \epsilon_{MRU,i}
-\end{align*}
-Table~\ref{table:pawssampling} provides the results for this regression.
-Although many coefficients are statistically significant consistent with large sample sizes for this estimation, the magnitudes of the effects are small in economic terms across most measures.
-For example, increasing the average number of households per connection by a standard deviation (0.65) results in a 0.0021 percentage point decrease in the probability of being surveyed; given a mean survey probability of 6 percentage points, this change represents only a 3.3 percent decrease.
-Dwelling types are the strongest predictor of coverage, indicating that surveyors may have oversampled apartments possibly due to easier availability to survey.
-Taken together, these results suggest that to the extent that non-random sampling may affect results, it will lead to an underestimation of the importance of sharing networks in Manila.
-
-\begin{table}
-\centering
-\caption{ Predicting Share of Connections Surveyed with \\ Connection Owner Demographics }\label{table:pawssampling}
-\input{tables/paws_sampling}
-\end{table}
-
-\section{Comparing Demographics in the Census to the Connection Survey}\label{appendix:pawstocensus}
-
-Census households are divided into three groups according to their water source for cooking, laundry, or bathing needs: the first group includes households that select ``own use, faucet community water system'' defined as own use, the second group includes ``shared use, faucet community water system'' defined as shared use, and the third group includes all other categories defined as vendor.
-I find a lower percentage of households sharing connections in Table~\ref{descriptives} than in Table~\ref{table:pawstocensus}.
-One reason is that all households sharing a connection may identify as owning the connection while the water provider only registers one household as the owner.
-Since the empirical strategy combines data from the connection survey with the census, I examine the first two columns for comparability across samples and find that demographics appear broadly similar.
-
-Comparing columns two and three, I find that shared-use households have lower imputed incomes, greater probability of low-skill employment, and slightly smaller households than own-use households.
-These trends mirror the findings from connection owners in Table~\ref{descriptives}.
-Vendor households captured in the final column of Table~\ref{table:pawstocensus} closely resemble shared-use households across age, employment, and income measures.
-These households are especially likely to reside in single houses, which may lead to easier access to vendors as well as more difficult access to neighboring connections.
-
-\begin{table}
-\centering
-\caption{Household Demographics across \\ Survey and Census Data by Water Source}\label{table:pawstocensus}
-\input{tables/descriptives_census_to_paws} \\
-\footnotesize{The data include connection survey data on households owning water connections \\ as well as 2010 Census data on households.
-This sample includes \\ overlapping wards between  surveys (67\%)}
-\end{table}
-
-\section{Details on Mobile Survey}\label{appendix:pollfish}
-
-The mobile survey was conducted using Pollfish--- an organization that advertises the opportunity to complete a survey for the chance to win an Amazon gift certificate.
-Pollfish reaches potential respondents through ads on mobile apps and Facebook.
-The survey was fielded in 6 batches of 100 respondents in July, 2017, which allowed for the addition and modification of questions across survey rounds.
-
-\begin{table}
-\centering
-\caption{Mobile and PAWS Water Source Choices}\label{table:pollfishpawsmeans}
-\input{tables/pollfish_paws_means} \\
-\vspace{.3cm}
-\footnotesize{The PAWS data have been adjusted to reflect that \\ shared connections serve multiple households.}
-\end{table}
-
-Since this survey is not designed to be representative of the population of households in Manila, the following tables compare descriptive statistics between the mobile survey and the connection  survey (Public Assessment of Water Services (PAWS)).
-Table~\ref{table:pollfishpawsmeans} compares the shares of households choosing each water source --- individual, sharing with 1 other household, or sharing with 2 other households --- across the two datasets, adjusting for the fact that the connection survey was conducted at the water connection-level.
-I find similar shares of households choosing these three water sources across these datasets with more households choosing to connect as single users in the Mobile survey data.
-Since the mobile survey was conducted over 8 years after the connection survey, this increase in single connections is consistent with a general substitution toward purchasing own connections (with increasing income and declining vendor opportunities).
-
-Table~\ref{table:pollfishpawssharing} compares demographics within each of these categories of water source.
-The first row indicates that Pollfish respondents tend to be much younger than connection survey respondents, which is consistent with higher mobile phone use among younger people as well as the fact that the connection survey largely targeted heads of household while any member could respond to Pollfish.
-Dwelling types and household size appear largely similar for single users with differences increasing as the number of households using each water connection increases.
-Since the connection survey only captures demographics for water connection owners while the mobile survey covers all users, this trend may capture differences between these groups.
-These findings suggest that the mobile and connection surveys are broadly consistent in capturing the population of water users despite differences in survey methods and timing.
-
-%Finally, while the number of users increases with the number of households drawing from each connection, this increase is greater for the mobile survey than for the connection survey.
-
-\begin{table}
-\centering
-\caption{Mobile and PAWS Descriptives by Water Sharing Status}\label{table:pollfishpawssharing}
-\input{tables/pollfish_paws_diff}
-\end{table}
-
-\section{Linear Approximation}\label{appendix:linearapprox}
-
-This section now investigates the extent to which the linear approximation might impact coefficient estimates as well as welfare calculations.
-The following figure compares the linear approximation to the standard normal CDF function over the range $(-3,3)$:
-\begin{center}
-\includegraphics[scale=.5]{tables/cdf_approx.png}
-\end{center}
-To ballpark the effects of this approximation, I simulate a dataset with two prices and one kink point as well as simulated parameters that are close to estimated values.
-Using this dataset, demand can be calculated in two ways: (1) according to the approximated function in equation (\ref{equation:generaldemand}) and (2) according to the exact demand function given by the numerical solution to the first order condition in equation (\ref{equation:firstordercondition}).
-Table~\ref{table:linapproxsim} provides the parameters used for simulation as well as the simulation results.
-The second and third columns provide estimates from the likelihood function in equation (\ref{equation:LLikelihood}).
-The second column shows estimates when consumption is generated through the exact numerical solution to the first order conditions.
-In this case, the likelihood function would be misspecified since the likelihood relies on the linear approximation.
-The third column shows estimates for when consumption is generated using the linear approximation, ensuring that the likelihood function is properly specified in this case.
-The estimates rely on a small sample of households in order to speed performance.
-Sampling error can help explain why the estimates in column three do not exactly match the true parameters.
-The last column finds small differences between estimates in columns two and three, providing some evidence that the linear approximation may not introduce substantial bias in the estimation.
-Welfare differences between following  approximated versus actual versus are negligible, totaling \input{tables/approx_welfare}PhP per month.
-
-\begin{table}
-\caption{Simulation Estimates for Linear Approximation}\label{table:linapproxsim}
-\centering
-\input{tables/approx_simulation} \\
-\footnotesize{The prices as well as the $\gamma$ terms are sampled from a uniform distribution on the given interval.
-Approx.
-DGP stands for approximated data generating process, which generates consumption values using the linear approximation.
-Exact DGP calculates consumption using the true demand function.
-}
-\end{table}
-
-\section{Alternative Sharing Contracts}\label{appendix:fixedprice}
-
-Two alternative sharing contracts include (1) alternating bill payment each month and (2) charging a fixed price to sharing households.
-Alternating bill payments can be thought of as a fixed price contract where each household faces a payment of zero each month.
-To model fixed price contract, consider a simple setting with two households and a linear budget constraint.
-Let household $1$ pay the full bill while household $2$ pays a fixed amount $Z$ each month regardless of their consumption:.
-
-The household optimization problems and solutions are as follows:
-\begin{align*}
-max_{x_1,w_1} \hspace{.2cm} & E\big[ U(x_1,w_1) \big] \\
-\text{s.t.  }\hspace{.3cm} Y_1 &=   x_1  + p (W_1 + W_{2})  \\
-w_1 &= \Gamma_1 - \alpha_1  p \\
-max_{x_2,w_2} \hspace{.2cm} & E\big[ U(x_2,w_2) \big] \\
-\text{s.t.  }\hspace{.3cm} Y_2 &=   x_1  + Z \\
-w_2 &= \Gamma_2
-\end{align*}
-Joint consumption takes the following form:
-\begin{align*}
-(w_1+w_2) = (\Gamma_1 + \Gamma_2) - \alpha_1 p
-\end{align*}
-In the case where price sensitivities are equal between households, $\alpha_1=\alpha_2=\alpha$, joint consumption under a fixed price contract is empirically identical to joint consumption under even bill-splitting.
-Therefore, assuming bill-splitting when households use fixed price contracts may bias price sensitivity estimates when these price sensitivities are very different from each other.
-This bias becomes less of a concern if households alternate paying the bill because the joint estimate of $\alpha$ will capture some weighted average of $\alpha_1$ and $\alpha_2$.
-Fixed price contracts may lead to a different allocation of surplus from sharing contracts depending on the size of the fixed price $Z$.
-Yet, since the model assumes that households are able to split expected surplus from the sharing relationship through fixed monthly transfers in Section~\ref{section:watersourcechoice}, the type of contract may have little effect on empirical or welfare estimates.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND  DEMAND 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Descriptive Statistics for Estimation Sample}\label{appendix:descriptivesest}
-
-Table~\ref{table:descriptivesestsample} provides descriptive statistics for the connection-level sample used in the demand estimation (Section~\ref{section:preferenceestimation}) and simulated method of moments estimation (Section~\ref{section:fixedcostestimation}).
-Demographic variables are expressed in terms of dummy variables capturing various features that might drive demand for water.
-Ward-level attributes include features that determine hassle-costs of sharing with a neighbor.
-The sample includes a random sample of 5,000 connections combined with a sample of unconnected households in order to ensure a representative sample of the population of households.
-
-\begin{table}
-\caption{Descriptives for Estimation Sample}\label{table:descriptivesestsample}
-\begin{center}
-\input{tables/new_descriptives_est_sample}
-\end{center}
-\end{table}
-
-\section{Price Variation}\label{appendix:pricevariation}
-
-\subsection{Targeting the Non-linear Tariff}
-
-Figure~\ref{figure:consumptionhistogram} provides a histogram of monthly consumption choices across all water connections and months in the data alongside the tariff schedule (censored below 60 m3).
-Usage hovers around 20 m3 per month; by comparison, households in the United States use closer to 50 m3 per month.
-Intuitively, households may be less willing to consume an additional cubic meter on the margin if the price for that unit is much higher.
-The histogram provides some evidence of bunching at 10 and 20 m3, although the magnitudes are small.
-Many households are also observed to consume below 10 units where the marginal price is actually zero.
-%Taken together, this evidence suggests households may be unresponsive to price.
-
-\begin{figure}
-\caption{Consumption Histogram}\label{figure:consumptionhistogram}
-\begin{center}
-\includegraphics[scale=.7]{tables/consumption_histogram.pdf}\\
-\footnotesize{Consumption values are truncated at 60 to highlight bunching at kink points.}
-\end{center}
-\end{figure}
-
-\subsection{Time Series Variation in Tariffs}\label{appendix:tariffvariation}
-This figure indicates time series variation in prices as a result of the government regulator raising prices incrementally to ensure production costs are covered.
-\begin{figure}
-\caption{Regulated Tariff Changes}\label{figure:regulatedtariffchanges}
-\begin{center}
-\includegraphics[scale=.7]{tables/tariff_time_series.pdf}
-\end{center}
-\end{figure}
-
-\subsection{Within Connection Price Variation}\label{appendix:ratechangeelasticity}
-
-This setting also provides quasi-experimental variation in the tariff over time at the connection-level, which serves as a useful setting to examine household demand response to price changes over time.
-Previous work estimating demand for public utilities has relied on time-series variation from regulated changes in the tariff (\cite{szabo2015value,mcrae2014infrastructure}).
-While the estimation strategy in this paper also includes this variation, regulated tariff changes are often relatively small, affect all households equally during the same month, and are anticipated well in advance.
-Through a quirk in the regulatory agreement, the water provider is able to upgrade households that are discovered engaging small businesses to a higher tariff class called the semi-business rate.
-The vast majority of these businesses are roadside stands, locally known as Sari-Sari stores.
-The connection survey covers \input{tables/semi_sample_size}connections that are upgraded from residential to semi-business status used in the analysis.
-
-Figure~\ref{figure:ressemi} compares the tariff structure between residential and semi-business rates.
-The tariffs mainly deviate between 10 and 20 cubic meters where the semi-business rate is about 30\% higher.
-
-\begin{figure}
-\caption{Residential and Semi-Business Tariffs}\label{figure:ressemi}
-\begin{center}
-\includegraphics[scale=.65]{tables/res_semi_tariff.pdf}
-\end{center}
-\end{figure}
-
-Table~\ref{table:semittests} provides summary statistics and t-tests comparing residential connections to semi-business connections, and semi-business connections to connections that are upgraded from semi-business to residential.
-Semi-business connections use more water, while having smaller households sizes, greater low-skilled employment, and higher likelihoods of living in a single house.
-Despite using more water, those upgraded to semi-business rates are broadly similar to the population of semi-business connections.
-%While many differences are statistically significant, the economic magnitudes of these differences are relatively small suggesting that demand responsiveness for this sub-population may be informative about the full population.
-
-\begin{table}
-\centering
-\caption{Summary Statistics and Comparison of Means for Residential, Semi-Business, and Upgraded Connections}\label{table:semittests}
-\resizebox{\textwidth}{!}{  
-\input{tables/sem_compare_means}
-}\\
-\footnotesize{Data are from the connection survey.}
-\end{table}
-
-The following equations estimate both event study and differences-in-differences strategies used to determine consumption response to changes in the rate class.
-For connections $i$ in month $t$, these equations predict consumption as a function of individual, $\theta_i$, and time, $\delta_t$ fixed effects.
-The event study in the first equation includes $\beta_r$ dummy variables for months to the rate change while the differences-in-differences approach in the second equation captures the $\beta$ effect on consumption of being after the rate-change, $Post_{i,t}$.
-\begin{align*}
-w_{i,t} &= \sum_{r=-12}^{12} \beta_{r} \mathbbm{1} \{t=r\}  +  \theta_{i} +\delta_t + \epsilon_{t,i} \\
-w_{i,t} &= \beta Post_{i,t} +  \lambda_{1} r_{i,t} + \lambda_{2} Post_{i,t} \times r_{i,t} + \theta_{i} +\delta_t  + \epsilon_{t,i}\\
-&r \text{ : month to upgrade to semi-business rate}
-\end{align*}
-
-Figure~\ref{figure:semieventstudy} plots average consumption for these connections relative to the month that they are upgraded to the semi-business tariff level.
-Before the upgrade consumption trends slightly upward, before dropping immediately following the tariff increase.
-A simple differences-in-differences estimate calculates a sizable price elasticity of 0.5 from this change, indicating significant demand responsiveness to time-series variation in the tariff.
-This elasticity is smaller than the structural estimates in Section~\ref{section:preferenceestimation}.
-
-\begin{figure}
-\caption{Demand Response to Time Series Price Variation}\label{figure:semieventstudy}
-\begin{center}
-\includegraphics[scale=.7]{tables/sem_event.pdf}
-\end{center}
-\end{figure}
-
-%  Identifying a particular piece-wise best-response function requires imposing bounds on $\sigma_{\epsilon_C}$ ex-ante, ensuring a certain level of overlap.
-%  determining which prices households consider at each consumption level.
-For example, households with very large consumption shocks have a positive probability of reaching any price segment so the piece-wise functions fully overlap.
-Therefore, households consider all possible prices at every point.
-In the opposite case, zero variance in consumption shocks means that households only consider the single price local to their consumption level resulting in zero overlap.
-The variance term, $\sigma_{\epsilon_C}$ plays an important role in determining the degree of overlap.
-% determine which prices enter the optimal demand function at each level of demand.
-
-\subsection{Characterizing the Optimal Demand Function}\label{appendix:optimaldemand}
-
-The optimal demand function takes a piecewise form depending on the proximity of different price segments.\footnote{This approach is only relevant for strictly increasing block tariffs like the one in Manila.
-Tariffs that include both increasing and decreasing blocks require comparing indirect utilities across all segments as in \cite{szabo2015value}.
-I extend the model to allow for decreasing marginal prices in the counterfactual exercises in Section~\ref{section:counterfactualexercises}.}  The aggregate demand function is as follows (where $L,M,H$ index low, medium, and high prices relative to each segment):
-%\begin{align}\label{equation:generaldemand}
-%\begin{split}
-%w^{*}_C &=
-%\begin{cases}
-%D^{1,1,1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V_{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-%D^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-%D^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-%D^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-%D^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-%D^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-%D^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
-%\end{cases}\\
-%\text{Where: } & \\
-%D^{L,M,H}_C        		&=  d^{L,M,H}_C + \frac{ \eta_C }{ V_{L,H} }   \\
-%d^{L,M,H}_C       		&= \frac{ 1}{ V^{L,H} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big )    \\
-%V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
-%\overline{\eta}^{j}_{l,L}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) - \sqrt{2} \sigma_{\epsilon_C} \\
-%\overline{\eta}^{j}_{l,U}   &= \overline{W}_l - ( \gamma_C - \alpha_C H_{C} -   \frac{\alpha_C}{S} p^j ) + \sqrt{2} \sigma_{\epsilon_C} \\
-%\end{split}
-%\end{align}
-
-\begin{align}\label{equation:generaldemand}
-\begin{split}
-D^{*}_C &=
-\begin{cases}
-W^{1,1,1}_C   & \text{ if } \hspace{1.7cm}                                               \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-W^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-W^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-W^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-W^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-W^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-W^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
-\end{cases}\\
-\text{Where: } & \\
-W^{L,M,H}_C        		&=  \frac{ w(P^{L,M,H}) }{ V^{L,H} }  + \frac{ \eta_C }{ V^{L,H} }   \\
-w(p) &= \gamma_C - \alpha_C [ H_{C} + \frac{p}{S}]  \\
-P^{L,M,H}  &= \dfrac{1}{2}[ p^{H} + p^{L} - \overline{W}^{H} (\frac{p^{H} - p^{M}}{\sqrt{2}{\sigma_{\epsilon_C}}})  - \overline{W}^{M} (\frac{p^{M} - p^{L}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ] \\
-V^{L,H} 	     	    &=   1 + \frac{\alpha_C}{2 S} ( \frac{p^{H} - p^{L}}{\sqrt{2}\sigma_{\epsilon_C}})   \\
-\overline{\eta}^{j}_{l,L}   &= \overline{W}_l -  w(p^j)  - \sqrt{2} \sigma_{\epsilon_C} \hspace{.1cm},\hspace{.2cm} \overline{\eta}^{j}_{l,U}   = \overline{W}_l - w(p^j)  + \sqrt{2} \sigma_{\epsilon_C} \\
-\end{split}
-\end{align}
-%For ease of exposition, I use notation where $D^{l}_C=D^{l,l,l}_C$ and $D^{l,j}_C=D^{l,j,j}_C$.
-In this expression, $w^{L,M,H}_C$ captures the deterministic component of demand while $W^{L,M,H}_C$ adds the stochastic component of fixed preferences.
-Connection-level fixed preferences $\gamma_C$, price sensitivities $\alpha_C$, and  hassle costs $H_C$ sum across their respective values for all households using a connection.
-A series of thresholds in the level of unobserved fixed preference, $\eta_C$, given by $\overline{\eta}^{j}_{l,L}$ and $\overline{\eta}^{j}_{l,U}$ work to determine which prices influence demand at each point in the schedule.
-Crossing a threshold means that the consumption shock now exposes the connection to a different set of prices.
-Figure~\ref{figure:intuitivedemand} graphs an example demand curve where the slope is determined by the functions $W^{L,M,H}_C$ and the changes in slope are given by the preference thresholds.
-%Also, the model assumes ex-ante that the parameter $\sigma_{\epsilon_C}$ satisfies two boundary conditions that is developed in more detail below as well as in Section~\ref{section:preferenceestimation}.
-\begin{figure}
-\caption{Example Demand Curve}\label{figure:intuitivedemand}
-\centering
-\begin{tikzpicture}[      
-        every node/.style={anchor=south west,inner sep=0pt},
-        x=1cm, y=1cm,
-      ]   
-     \node (fig1) at (0,0)
-       {\includegraphics[width=.66\textwidth,height=1\textheight,keepaspectratio]{tables/tariff_structure_1_no_label.pdf}};
-
-\draw [line width=0.2mm,color=red,dashed] (2.8,1.8) -- (2.8,7.6);
-\draw [line width=0.2mm,color=red,dashed] (3.8,1.8) -- (3.8,7.6);
-\draw [line width=0.2mm,color=red,dashed] (4.6,1.8) -- (4.6,7.6);
-\draw [line width=0.2mm,color=red,dashed] (5.5,1.8) -- (5.5,7.6);
-\draw [line width=0.2mm,color=red,dashed] (8.2,1.8) -- (8.2,7.6);
-\draw [line width=0.2mm,color=red,dashed] (9.1,1.8) -- (9.1,7.6);
-
-\node[align=center] at (2.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{1}_{1,L} $}};
-\node[align=center] at (3.7,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{2,L} $}};
-\node[align=center] at (4.5,7.6)  { \text{\footnotesize  $\overline{\eta}^{2}_{1,U} $}};
-\node[align=center] at (5.4,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{2,U} $}};
-\node[align=center] at (8.1,7.6)  { \text{\footnotesize  $\overline{\eta}^{3}_{3,L}  $}};
-\node[align=center] at (9,7.6)  { \text{\footnotesize  $\overline{\eta}^{4}_{3,U}  $}};
-
-\draw [line width=0.5mm] (1.2,7.6) -- (2.8,7) -- (3.8,6) -- (4.6,4.5) -- (5.2,2); %% curve
-
-\node[align=center] at (1.8,1)  { \text{\footnotesize  $W^{1,1,1}_C$}};
-\node[align=center] at (2.8,1) { \text{\footnotesize  $W^{1,2,2}_C$}};
-\node[align=center] at (3.8,1)  { \text{\footnotesize  $W^{1,2,3}_C $}};
-\node[align=center] at (4.8,1) { \text{\footnotesize  $W^{2,3,3}_C $}};
-\node[align=center] at (6.6,1)  { \text{\footnotesize  $W^{3,3,3}_C $}};
-\node[align=center] at (8.3,1)    { \text{\footnotesize  $W^{3,4,4}_C $}};
-\node[align=center] at (9.6,1)  { \text{\footnotesize  $W^{4,4,4}_C $}};
-
-\node[align=center] at (2.3,2.3) { \text{$p^1$} };
-\node[align=center] at (4,4.5)   { \text{$p^2$} };
-\node[align=center] at (6.6,6.4) { \text{$p^3$} };
-\node[align=center] at (10,7.6) { \text{$p^4$} };
-
-\end{tikzpicture}
-\end{figure}
-
-This section now discusses the separate parts of the demand function in more detail.
-
-\textbf{  Demand over a Single Price:  }  The first, third, and fourth price segments of the tariff schedule in Manila given in Figure~\ref{figure:intuitivedemand} exhibit large gaps of 20 $\text{m}^{3}$ between price changes.
-Within these segments, the consumption shocks are not large enough to ever bounce the households across a tariff kink point.
-Therefore, households are exposed only to the current price for that segment.
-Setting the low, medium, and high prices all equal to $k$ in expression $W^{L,M,H}_C$, demand arrives at the following expression:
-\begin{align*}
-  W_C  =& \gamma_C - \alpha_C [ H_{C} + \frac{p^k}{S} ] + \eta_C 
-\end{align*}
-This case produces a linear demand function where $\alpha_C$ can be readily interpreted as the price sensitivity parameter while $\gamma_C$ captures the portion of demand that is invariant to prices.
-This demand function captures moral hazard from bill-splitting by dividing the price sensitivity, $\alpha_C$, by the total number of households using the connection, $S$.
-Comparing demand among shared connections to individual connections, the extent of over-consumption at an average price of $p$ can be roughly summarized as $\frac{S-1}{S} \alpha_C p $.
-
-\textbf{ Demand over Many Prices: }  When households choose to consume close to price thresholds points, they become exposed to price segments both above and below the thresholds.
-Demand becomes a weighted average of these two price segments.
-In this case, demand takes the following form, setting low and medium prices equal to $k$, and the high price equal to $k+1$:
-\begin{align*}
-W_C &= \frac{ 1}{ V^{k,k+1} } \Big ( \gamma_C - \alpha_C H_{C} - \frac{\alpha_C}{2 S}  [ p^{k} + p^{k+1} - \overline{W}^{k+1} (\frac{p^{k+1} - p^{k}}{\sqrt{2}{\sigma_{\epsilon_C}}})  ]  \Big ) + \frac{ \eta_C }{ V_{k+1,k} }
-\end{align*}
-Setting $L=M=k$ simplifies the demand expression so that only the single nearby kink point, $\overline{W}^{k+1}$, is considered.
-Under increasing prices, a decrease in the kink point, $\overline{W}^{k+1}$, lowers demand by increasing the probability that the household faces a higher price.
-
-When the distance between price segments is relatively small compared to the size of the consumption shocks, then households are exposed to three prices when consuming on a particular segment.
-Despite locating far from the neighboring kink points, households still face some probability of crossing into another price segment either above or below their current price.
-This demand function applies to households locating between the second and third tariff blocks because this gap only spans 10 $\text{m}^{3}$ (as shown in Figure~\ref{figure:intuitivedemand}).
-The demand function corresponds to the full expression for demand, setting indices for the low price equal to $1$, the middle price equal to $2$, and the high price equal to $3$.
-
-\section{Determining the Demand Function with Respect to Variance of Consumption Shocks}\label{appendix:sigmanuassumptions}
-
-The specification of the demand function is sensitive to ex-ante assumptions on the standard deviation of the consumption shocks, $\sigma_{\epsilon}$.
-To identify the appropriate demand function in this empirical setting, I maximize the likelihood function in equation (\ref{equation:LLikelihood}) over three demand specifications with different assumptions on $\sigma_{\epsilon}$ before selecting equation (\ref{equation:generaldemand}) as the primary specification.
-
-I first construct and estimate demand under the limiting assumption that $\sigma_{\epsilon}$ falls below the minimum threshold, $min_{\forall k}\hspace{.2cm} \{ \frac{\overline{W}_{k+1} - \overline{W}_k}{2\sqrt{2}} \} = \frac{10}{2\sqrt{2}} = 3.53$.
-Under this assumption, households only consider one price at all segments and two prices near thresholds.
-This assumption produces the following demand function:
-\begin{align}\label{equation:demandalt1}
-\begin{split}
-D^{*}_C &=
-\begin{cases}
-W^{1,1,1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-W^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{1,U}  \\
-W^{2,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-W^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-W^{3,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-W^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-W^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }   
-\end{cases}\\
-\text{Assuming:}\\
- \sigma_{\epsilon_C} \leq &\frac{  \overline{W}^{2} - \overline{W}^{1} }{ 2\sqrt{2} } = \frac{ 10 }{ 2 \sqrt{2} } = 3.53 
-\end{split}
-\end{align}
-Estimates according to this demand function in the first column of Table~\ref{table:sigguess} find that the standard deviation for consumption shocks for connections serving single households through connections serving three or more households exceeds the 3.53 threshold in all cases.
-\begin{table}
-\centering
-\caption{Alternative Demand Specification Estimates}\label{table:sigguess}
-\input{tables/sig_guess_estimates}
-\end{table}
-Next, I estimate the primary specification in equation (\ref{equation:generaldemand}), which holds under the hypothesis that $\sigma_{\epsilon}$ falls between $3.53$ and $\frac{\overline{W}_{2} - \overline{W}_1}{2\sqrt{2}} = \frac{20}{2\sqrt{2}} = 7.06$.
-Estimates from the second column of Table~\ref{table:sigguess} fail to reject the hypothesis.
-
-Finally, I allow for greater variance of $\sigma_{\epsilon}$ exceeding $7.06$ and ensuring that the household responds to three prices at both interior price segments in the tariff schedule.
-This specification takes the following functional form:
-\begin{align}\label{equation:demandalt2}
-\begin{split}
-D^{*}_C &=
-\begin{cases}
-W^{1,1,1}_C   & \text{ if } \hspace{1.7cm}   \frac{ \eta_C }{ V^{1,1} }  \leq \overline{\eta}^{1}_{1,L}  \\
-W^{1,2,2}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{1}_{1,L} <    \frac{ \eta_C }{ V^{1,2} }    \leq \overline{\eta}^{2}_{2,L}  \\
-W^{1,2,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{2,L} <    \frac{ \eta_C }{ V^{1,3} }    \leq \overline{\eta}^{2}_{1,U}  \\
-W^{2,3,3}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{2}_{1,U} <    \frac{ \eta_C }{ V^{2,3} }    \leq \overline{\eta}^{3}_{3,L}  \\ 
-W^{2,3,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{3,L} <    \frac{ \eta_C }{ V^{2,4} }    \leq \overline{\eta}^{3}_{2,U}  \\ 
-W^{3,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{3}_{2,U} <    \frac{ \eta_C }{ V^{3,4} }    \leq \overline{\eta}^{4}_{3,U}  \\ 
-W^{4,4,4}_C   & \text{ if } \hspace{.5cm} \overline{\eta}^{4}_{3,U} <    \frac{ \eta_C }{ V^{4,4} }  
-\end{cases}\\
-\text{Assuming:}\\
- \sigma_{\epsilon_C} \geq &\frac{  \overline{W}^{2} - \overline{W}^{1} }{ \sqrt{2} } = \frac{ 10 }{  \sqrt{2} } = 7.06 \\
- \sigma_{\epsilon_C} \leq &\frac{  \overline{W}^{3} - \overline{W}^{2} }{ \sqrt{2} } = \frac{ 20 }{  \sqrt{2} } = 14.12
-\end{split}
-\end{align}
-The final column in Table~\ref{table:sigguess} again rejects this hypothesis finding estimates of $\sigma_{\epsilon}$ that fall below the 7.06 threshold.
-Comparing all of the parameter estimates across specifications, I find very minor differences according to the different demand functions, providing suggestive evidence that the estimation strategy is robust to ex-ante assumptions on $\sigma_{\epsilon}$.
-
-\section{Hassle Cost: Neighbor Radius}\label{appendix:sharingneighbor}
-
-The following equation predicts usage for neighboring households, $i$, relative to a nearby leak according to their distance rank, $DR$, relative to the leaking household with rank $1$ being closest and rank $D$ being furthest from the leaking household.
-To capture any spatial changes in consumption over time, the regression also allows for differential time trends before and after the leak according to distance rank, $DR$, captured by $\lambda^{d}_{1}$ and $\lambda^{d}_{2}$:
-\begin{align*}
-	w_{t,i} &= \sum_{d=1}^{D} \mathbbm{1}\{DR_{i}=d\} \Big [ \beta^{d} Post_{i,t} +  \lambda^{d}_{1} r_{i,t} + \lambda^{d}_{2} Post_{i,t} \times r_{i,t} \Big ] + \theta_{i}  + \epsilon_{t,i}\\
-r_{i,t} &\text{ : Months to leak} \\
-DR_{i} &\text{ : Distance Rank Relative to Leaking Connection} \\
-Post_{i,t} &\text{ : After leak}
-\end{align*}
-The coefficients of interest, $\beta^{d}$, are presented in Table~\ref{table:neighbordistance}.
-I find that the closest neighbor receives the most consumption from the leaking household, closely followed by the second and fourth neighbors.
-Substitution drops off quickly past the fourth neighbor, reaching statistically insignificant and economically smaller magnitudes for the fifth through eighth neighbors.
-\begin{table}
-\caption{Sharing and Distance to Leaking Connection}\label{table:neighbordistance}
-\centering
-\input{tables/neighbor_distance}
-\end{table}
-
-\section{Hassle Cost Assumptions}\label{appendix:sharingcostassumptions}
-
-The following additional assumptions are required to ensure that this empirical setting accurately captures the model described in Section~\ref{section:hasslemodel}:
-\begin{enumerate}
-
-	\item \textit{ Connections that experience a leak are representative of the population of connections.
-}  This assumption is supported by small economic differences in means of observable measures between connections with leaks and without in Table~\ref{table:leakbalance} although some differences are statistically significant.
-\begin{table}
-\centering
-\caption{Descriptives and Balance Test for Non-Leaking and Leaking Connections}\label{table:leakbalance}
-\input{tables/mean_diff_leak} \\
-\footnotesize{Drink is a dummy for drinking tap water.
-Water flow is a dummy for low water pressure.
-\\ Water storage is a dummy for owning a water storage container.
-Std.
-errors result from a T-test of differences in means.}
-\end{table}
-
-	\item  \textit{ The decision to disconnect conditional on experiencing a leak is uncorrelated with water demand.
-}  Table~\ref{table:leakbalancedc} provides partial support by showing few large differences in characteristics between those that disconnect and those that remain connected other than the size of the leak.
-This evidence suggests that the disconnection decision is driven primarily by variation in the magnitude of the leak.
-\begin{table}
-\centering
-\caption{Balance Test for Disconnection among Leaking Connections}\label{table:leakbalancedc}
-\input{tables/mean_diff_DC.tex} \\
-\footnotesize{Drink is a dummy for drinking tap water.
-Water flow is a dummy for low water pressure.
-\\ Water storage is a dummy for owning a water storage container.
-Std.
-errors result from a T-test of differences in means.}
-\end{table}
-
-	\item \textit{ The timing of a leak is uncorrelated with any underlying changes in demand.
-}  I test this assumption with a regression predicting a connection $i$'s consumption in the 30 months before the leak event controlling for a connection fixed effect, $\theta_{i}$:
-\begin{align*}
-w_{t,i} &=  \sum_{r=-30}^{0} \beta_{r} \mathbbm{1} \{t=r\}  +  \theta_{i} + \epsilon_{t,i} \\
-r 		 &\text{ : Month to leak}\\
-\theta_i &\text{ : Connection-level fixed effect}
-\end{align*}
-	I include a dummy variable for each month before the leak.
-Figure~\ref{figure:leakpretrend} plots demeaned monthly consumption relative to the month of the leak.
-This figure shows stable a consumption pattern interrupted by a large jump at the exact time of the leak.
-\begin{figure}
-\centering
-\caption{Pre-Trend in Leaker's Consumption}\label{figure:leakpretrend}
-\begin{center}
-\includegraphics[scale=.7]{tables/leakers_pre_2.pdf}
-\end{center}
-\end{figure}
-
-	\item \textit{ Leaks are uncorrelated with changes in neighborhood demand.
-}  A simple regression tests this assumption by predicting total consumption among four closest neighbors in neighborhood $N$, before and after a nearby leak, controlling for a neighborhood fixed effect, $\theta_{N}$.
-I include a dummy variable for each month relative to the month that the neighbor leaks:
-	\begin{align*}
-	w_{N,t} &= \sum_{r=-14}^{14} \beta_{r} \mathbbm{1} \{t=r\}  +  \theta_{N} + \epsilon_{N,t} \\
-	r &\text{ : Month to leak} \\
-	N &\text{ : Neighborhood }
-	\end{align*}
-	Figure~\ref{figure:leakeventstudy} plots the results of this regression indicating average total neighborhood consumption in the months just preceding and following the date that the leakis reported.
-I find a stable trend in neighbors' consumption before the leak followed by a quick leap as the leaking household starts to share with their neighbors.
-This sharing behavior remains persistent for at least a year after the initial pipe leak, providing a useful window of time to estimate the hassle cost.
-	\begin{figure}
-	\centering
-	\caption{Neighbors' Water Usage following a Leak Disconnection}\label{figure:leakeventstudy}
-	\begin{center}
-	\includegraphics[scale=.7]{tables/leakers_full_2.pdf}
-	\end{center}
-	\end{figure}
-
-	\item \textit{  The leaking household's choice of a sharing partner is uncorrelated with that partner's water demand.
-}  This assumption holds when the $\omega$ term in equation (\ref{equation:hassleutilities}) is equal to zero.
-If $\omega$ is nonzero allowing leaking households to weigh the utility from using each source in this decision, households may choose to share with low demand neighbors to enjoy lower points on the tariff in Figure~\ref{figure:tariff}.
-To test this hypothesis, I predict the heterogeneous increase in neighbor's consumption following a leak according to that neighbor's water demand, which is proxied by average consumption prior to the leak.
-The following regression equation tests this relationship by predicting changes in usage according to the rank of average consumption at baseline among all neighbors:
-\begin{align*}
-	w_{t,i} &= \sum_{d=1}^{4} \mathbbm{1}\{Rank_{i}=d\}  \beta^{q} Post_{i,t}  + \theta_{i}  + \epsilon_{t,i}\\
-r &\text{ : Month to leak} \\
-Rank &\text{ : Rank of avg. usage in the neighborhood at baseline} \\
-\theta_i &\text{ : Connection-level fixed effect}
-\end{align*}
-	One issue with this analysis is that predicting the usage response of a neighbor as a function of their previous consumption is likely to produce mean reversion bias: connections with low usage at baseline demonstrate larger increases in consumption than connections with high usage at baseline due to natural variation in preference shocks.
-To test for mean reversion, I create a random treatment date using only data before the leak has occurred.
-Table~\ref{table:neighborselection} presents the $\beta^{d}$ estimates of the true leak-date specification in the first column and the mean randomized leak-date estimates in the second column.
-The third column takes the difference of the first and second columns, which provides a coarse method of netting out any mean reversion bias.
-The first column predicts strong increases in consumption for smaller users (ranks 1 and 2) while large users (ranks 3 and 4) exhibit small and even negative demand responses.
-These differential responses are amplified in the second column (with placebo treatment dates), suggesting that mean reversion may play a large role in biasing estimates.
-The third column shows that after adjusting for mean reversion bias, the demand response of neighboring connections is roughly equal as the relative demand increases for these connections.
-This finding provides suggestive evidence that households are not selecting sharing partners conditional on their neighbors' water demands.
-\begin{table}
-\centering
-\caption{Leak Demand Response and Rank of Baseline Usage in Neighborhood}
-\input{tables/neighbor_selection}\label{table:neighborselection}
-\end{table}
-	\item \textit{ In response to a leak, the choice to share with a neighbor or use a vendor is uncorrelated with water demand.
-}  This assumption also holds when the $\omega$ term in equation (\ref{equation:hassleutilities}) is equal to zero.
-If water demand were correlated with substitution across these sources, then I would expect to find that the water demand of the leaking household predicts a differential rise in usage among neighbors following the leak.
-Since vended water is characterized by high prices and low fees, a simple model would predict that households with low water demand would substitute toward vendors at a higher rate and would therefore offset less consumption to neighboring households following a leak.
-To test this assumption, I use average consumption for a leaking household prior to the leak as a proxy for their water demand.\footnote{Using the same test as before, I detect no evidence of mean reversion given this demand proxy.}  The following equation predicts total usage in neighborhood, $N$, before and after a household in that neighborhood experiences a leak.
-The regression allows for separate impacts of a neighbor's leak, $\beta^d$ depending on that neighbor's quintile of average consumption (measured before the leak).
-\begin{align*}
-	w_{t,N} &= \sum_{d=1}^{5} \mathbbm{1}\{Quintile_{N}=d\}  \beta^{d} Post_{N,t}  + \theta_{N}  + \epsilon_{N,t}\\
-r &\text{ : Month to leak} \\
-Quintile &\text{ : Quintile of avg. usage for leaking connections at baseline} \\
-\theta_N &\text{ : Neighborhood-level fixed effect}
-\end{align*}
-	Table~\ref{table:leakerselection} presents the results from this regression in the first column.
-The size of the coefficients increase as the quintile of leaker demand increases, which is consistent with larger users at baseline using greater amounts of water from their neighbors.
-To compare the relative demand response for large and small users, column three divides this coefficient estimate by the average usage for each quintile at baseline to arrive at the percentage of water consumption that is offset among neighbors after a leak occurs.
-Column three finds no strong trends in the share of consumption that is offset to neighbors across water demand quintiles.
-This finding provides suggestive evidence that household's are left to use whichever source is most immediately available (neighbor or vendor) following a leak.
-\begin{table}
-\centering
-\caption{Neighborhood Usage Response and Quintile of Usage for Leaking Connection}\label{table:leakerselection}
-\input{tables/leaker_selection}
-\end{table}
-
-	\item \textit{  A leak for one household is uncorrelated with probability of a neighboring household experiencing a leak.
-}  While the data show little evidence that leaks  are spatially correlated, I cannot rule out unreported leaks affecting nearby households.
-The presence of unobserved spatial correlation in leaks would lead this method to overestimate the hassle costs associated with sharing a connection.
-\end{enumerate}
-
-%\section{Bootstrapping Procedure for Hassle Cost}\label{appendix:hasslecostbootstrap}
-
-%The bootstrapping procedure resamples at the level of full neighborhoods including both leaking connection and the neighboring connections, which treats each ``leak'' as its own cluster.
-In a small number of bootstrapped samples ($<5\%$), the estimation procedure for this step converges to extreme outliers; this is because these samples have a relatively high share of households choosing zero monthly consumption, which are difficult values for the model to fit.
-In these cases, I adjust the routine to drop zero consumption values ($<2\%$ of all values), which allows the procedure to converge to plausible parameter values.
-
-%\begin{align*}
-%w_{i}^{pre} &= \Gamma_{i} - \alpha_{i} p \\
-%w_{i}^{post} &= \Gamma_{i} - \alpha_{i} ( p + p_{h}) \\
-%\frac{w_{i}^{pre} - w_{i}^{post}}{\alpha_{i}} &= p_{h}
-%\end{align*}
-
-\section{Game Tree with Three Players}\label{appendix:gametreefull}
-
-This section maps the game tree for three players, $1$, $2$, and $3$ in Figure~\ref{figure:fullgametree}.
-
-%\begin{landscape}
-%\setcounter{figure}{10}
-
-\begin{figure}
-\caption{Sequential Game Choosing Water Sources}\label{figure:fullgametree}
-\centering
-\begin{turn}{90}
-\resizebox{1.1\textwidth}{!}{%
-\begin{tikzpicture}
-\node(0){ \textbf{HH  1}}
-child[level distance=8mm,sibling distance=150mm]{node{\textbf{HH2}} %%% HERE IS NODE 1 %%%
-child[level distance=20mm,sibling distance=25mm]{node{\textbf{HH3}}
-child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
-}  
-child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
-}
-edge from parent node[left]{ \scriptsize{Vendor}}
-}
-child[level distance=50mm,sibling distance=25mm]{node{\textbf{HH3}}
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
-}  
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$U_{2}(P_S,F-T_{3,2})$} \\ \scriptsize{$u^{3}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH2}}
-}
-child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]280: \scriptsize{$u^{1}(v)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
-}
-edge from parent node[right]{ \scriptsize{Connect}}
-}
-edge from parent node[below]{ \footnotesize{Vendor} }
-}
-child[level distance=8mm,sibling distance=80mm]{node{\textbf{HH2}} %%% HERE IS NODE 2 %%%
-child[level distance=10mm,sibling distance=50mm]{node{\textbf{HH3}}
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
-}  
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$U_{1}(P_S,F-T_{3,1})$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(s^{1}|\{ 1,3 \}) + T(\{ 1,3 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH1}}
-}
-child[level distance=15mm,sibling distance=15mm]{node[label={[align=left,label distance=.01cm]280: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(v)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
-}
-edge from parent node[right]{ \scriptsize{Vendor}}
-}
-child[level distance=40mm,sibling distance=50mm]{node{\textbf{HH3}}
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
-}
-child[level distance=15mm,sibling distance=35mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$U_{1}(P,F-T_{3,1})$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(s^{1}|\{ 1,3 \}) + T(\{ 1,3 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH1}}
-}  
-child[level distance=15mm,sibling distance=35mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$U_{2}(P_S,F-T_{3,2})$} \\ \scriptsize{$u^{3}(s^{2}|\{ 2,3 \}) + T(\{ 2,3 \})$}  }]{} edge from parent node[left]{\scriptsize{Shr HH2}}
-}
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]280: \scriptsize{$u^{1}(c|1)$} \\ \scriptsize{$u^{2}(c|1)$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Connect}}
-}
-edge from parent node[right]{ \scriptsize{Connect}}
-}
-child[level distance=10mm,sibling distance=60mm]{node{\textbf{HH3}}
-child[level distance=15mm,sibling distance=20mm]{node[label={[align=left,label distance=.01cm]240: \scriptsize{$u^{1}(c|\{ 1,2 \}) + T(\{ 2 \})$} \\ \scriptsize{$u^{2}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$} \\ \scriptsize{$u^{3}(v)$}  }]{} edge from parent node[left]{\scriptsize{Vendor}}
-}
-child[level distance=15mm,sibling distance=25mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(c|\{ 1,2,3 \}) + T(\{ 1,2,3 \})$} \\ \scriptsize{$u^{2}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$} \\ \scriptsize{$u^{3}(s^{1}|\{ 1,2,3 \}) + T(\{ 1,2,3 \})$}  }]{} edge from parent node[right]{\scriptsize{Shr HH1}}
-}  
-child[level distance=30mm,sibling distance=30mm]{node[label={[align=left,label distance=.01cm]270: \scriptsize{$u^{1}(c|\{ 1,2 \}) + T(\{ 2 \})$} \\ \scriptsize{$u^{2}(s^{2}|\{ 1,2 \}) + T(\{ 1,2 \})$} \\ \scriptsize{$u^{3}(c|1)$}  }]{} edge from parent node[right]{\scriptsize{Vendor}}
-}
-edge from parent node[right]{ \scriptsize{Shr HH1}}
-}
-edge from parent node[below]{ \footnotesize{Connect} }
-}
-;
-%\node at($(0-1)!.7!(0-2)$){ \textbf{HH 2} };
-%\node at($(2-1)!.5!(2-2)$){ \textbf{HH 3} };
-\end{tikzpicture}
-}
-\end{turn}
-%\begin{itemize}
-%\item $p_v$: Vendor Price
-%\item $F_v$: Vendor Fee/Disutility
-%\item $T_{i,j}$: Transfer from household $i$ to household $j$
-%\item $P, P_S$: Tariff schedules for single and joint users
-%\item $p_{h}$: Hassle Cost
-%\end{itemize}
-\end{figure}
-
-%\end{landscape}
-
-\section{Out-of-Sample Test: A Connection Fee Discount Program}\label{section:oostest}
-
-A connection fee discount program implemented by the water company provides a useful setting to test the out-of-sample predictions of the economic model: do predicted water source choices match observed choices in response to a discount in the fixed fee?
-According to the model, reducing the fixed fee would make individual connections more attractive relative to shared connections or water vendors.
-This section compares the predicted and observed increase in connections in response to the program.
-
-%To evaluate how well the model is able to match observed substitution patterns between water sources, I investigate reduced-form evidence from a connection-fee discount program since this variation is not used explicitly in any part of the estimation.
-%[chk] The fundamental assumption of the model is that the decision to share a water connection balances splitting the fixed fee among many households against facing marginal hassle costs in fetching water as well as free-rider costs in splitting the water bill.
-Under this assumption, reducing the fixed fee would lead to substitution away from shared connections toward individual connections.
-This section uses quasi-experimental variation in the connection-fee to test this assumption.
-
-In 2009, the government regulator issued new regulations reducing the connection fee from 6,000 to 2,400 PhP for low-income areas partially in an effort to extend access and affordability to low-income households.
-Under the assumption that households reside in Manila for 80 months and face negligible credit constraints, this discount lowered the monthly fixed fee faced by households by 45 PhP on average.
-In the presence of credit constraints, this estimate can be interpreted as a lower bound on the policy's impact on the monthly fixed price faced by households.
-Figure~\ref{figure:discountfirststage} indicates the share of new connections receiving discounted fees.
-The sudden rise by \input{tables/first_stage}percentage points coincides with the change in regulations and will be used to identify the timing of the discount policy.
-A small fraction of households are observed to receive connection fee discounts prior to the program as part of other, smaller pro-poor strategies implemented by the water provider.
-% and these households are excluded from the main analysis
-
-\begin{figure}
-\centering
-\caption{Share of New Connections Receiving a Discount}\label{figure:discountfirststage}
-\includegraphics[scale=.7]{tables/diff_595_first_stage.pdf}
-\end{figure}
-
-Since the data do not identify precisely which local areas or specific households were eligible for the discount, additional assumptions are necessary to measure eligibility.
-First, I define treated areas as any meter reading unit (MRU) that receives at least one discounted connection over the full duration while control areas include any MRUs that never receive discounts.
-MRUs are common geographical designations used by the water provider and include between 100 and 500 meters.
-There are 3,757 MRUs in the service area.
-I include only MRUs that were established long prior to the discount fee program to ensure that these areas are likely to be at saturation in terms of water connections prior to the program.
-Second, to identify the share of households in treated areas that were eligible, I conceptually divide new connections into two groups --- (1) households substituting away from shared connections or water vendors in response to the program and (2) new households migrating to the city.
-I then measure eligibility as the share of new migrants receiving discounted connections fees after the policy.
-
-This approach requires the following assumptions:
-\begin{enumerate}
-	\item Before the discount program, households that have already moved to the city have reached an equilibrium at the current prices; therefore, all new full-price connections in the pre-period are driven by migration to the city.
-This assumption is consistent with the large fixed costs incurred in setting up a new connection.
-	\item The rate of migration is unaffected by the policy, which is supported by the stable rate of new connections for untreated areas in Figure~\ref{figure:discountreducedform} below.  
-	\item After the discount policy is implemented, all new migrant households that are eligible take up the discounted connections.
-	\item Rates of eligibility are similar across migrant and non-migrant groups.
-\end{enumerate}
-Under these assumptions, I compute the impact of the policy on new full-price connections in the treated areas and interpret any reduction in the rate of new full-price connections as driven by new migrants receiving discounted connections.
-I estimate the following simple difference-in-differences equation across all treated and untreated Meter Reading Units, $m$, and months, $t$, pre and post policy implementation:
-\begin{align*}
-\text{New Full-Price Connections}_{t,m} &= \beta_1 \text{Post X Treated}_{t,m} + \beta_2 \text{Post}_{t,m} + \beta_3 \text{Treated}_{t,m} + \epsilon_{t,m}
-\end{align*}
-Table~\ref{table:difffullpriced} presents the results from this estimation.\footnote{These results do not exactly match reduced-form results from Table~\ref{table:diffdiscountreducedform} because the data only have information on the price per connection for about 80\% of new connections.}  Adding the coefficients in Table~\ref{table:difffullpriced} shows that in the absence of the policy, treated areas were expected to have added 0\input{tables/would_have_added}new full-price connections each month; yet, as a result of the policy, these areas actually experienced 0\input{tables/actually_added}new full-price connections with the remaining households receiving discounted connections.
-This discrepancy implies that \input{tables/substitution}\unskip\% of households were eligible for the program.
-
-\begin{table}
-\centering
-\caption{Difference-in-Differences Estimate for Full Priced Connections}\label{table:difffullpriced}
-\input{tables/diff_595_reg_secondary}
-\end{table}
-
-I next examine the reduced-form impacts of the policy using the following event-study regression equation, which computes the average number of new connections in bi-monthly intervals relative to the discount fee program for both treated and untreated areas:
-\begin{align*}
-\text{New Connections}_{t,m} &= \sum_{r=0}^{T} \beta^{\text{Treated}}_{r} \mathbbm{1} \{t=r\} + \sum_{r=0}^{T} \beta^{\text{Untreated}}_{r} \mathbbm{1} \{t=r\}  +  \theta_{m} + \epsilon_{t,m} \\
-t &= \text{2 Month Intervals}\\
-m &= \text{Meter Reading Unit}
-\end{align*}
-Figure~\ref{figure:discountreducedform} provides the graphical estimates from this equation.
-The differences-in-differences estimate shows a relatively stable pre-trend interrupted by a substantial increase in the number of connections just following the discount program implementation.
-This increase lasts for a couple years before returning to pre-program levels.
-This trend provides evidence that households who are sharing water or purchasing from vendors are gradually learning about the price change and choosing to purchase their own connections.
-After a couple years, this additional demand for connections has been satisfied, letting migration take over as the sole driver of new connections.
-\begin{figure}
-\centering
-\caption{Reduced Form: Connection Fee Discount}\label{figure:discountreducedform}
-\includegraphics[scale=.8]{tables/diff_595.pdf}
-%\includegraphics[scale=.57]{tables/diff_595_treated.pdf}
-\end{figure}
-
-\begin{table}
-\centering
-\caption{Difference-in-Differences Estimate}\label{table:diffdiscountreducedform}
-\input{tables/diff_595_reg_primary}
-\end{table}
-
-A simple difference-in-differences estimate provided by Table~\ref{table:diffdiscountreducedform} calculates an increase of 0\input{tables/red_form_est}new connections per month for the treated areas on a base average of 0\input{tables/red_form_base}new connections per month.
-Aggregated over the full \input{tables/treated_months}months of the program, this program led to a total of \input{tables/total_effect}new connections per MRU.
-Given that the average MRU has \input{tables/mru_size}connections over the full time period, this program generated about a \input{tables/percent_increase_discount}\unskip\% increase in the number of new connections.
-
-To compare results from this policy to counterfactual estimates from the model, I now convert the change in number of connections induced by the policy to a shift from shared and vendor connections to individual connections.
-Given that \input{tables/share_2_hhs}\unskip\% of connections serve two households and \input{tables/share_3_hhs}\unskip\% of connections serve three or more households, and 6\% of households access water from vendors, then \input{tables/mru_size}connections per MRU are calculated to serve an average population of around \input{tables/population_served}households.
-This policy results in a \input{tables/increase_in_individual_connections}percentage point increase in the share of households owning a connection, which can be directly compared to predictions from the counterfactual exercise.
-
-In order to relate the quasi-experimental results from the policy to the model outputs, I simulate the impacts of the connection-fee discount policy by (1) randomly selecting \input{tables/substitution}\unskip\% of households, (2) lowering the fixed fee by 45 PhP for these households, and (3) recomputing their water source choices.
-As a result of this policy, the share of households owning a water connection is calculated to rise by \input{tables/out_of_sample_inc_ind_conn_group}percentage points.
-This finding is smaller, but comparable to the reduced form results indicating a \input{tables/increase_in_individual_connections}percentage point increase.
-There may be many reasons that the counterfactual results lag behind the reduced-form estimates.
-First, the assumptions used to amortize the connection fee discount into monthly terms  may work to understate the impact of the discount, especially in cases where households face credit-constraints in funding large, lump-sum connection fees.
-Second, in practice, the discount policy targeted a low-income segment of the population, which may have different substitution patterns across water sources.
-
-Despite these caveats, the fact that the reduced-form and model-based estimates are similar in magnitude lends support to the counterfactual exercises implemented in Section~\ref{section:counterfactualexercises}.
-Table~\ref{table:oosestimates} calculates the impacts of this connection fee discount on water source choices as well as consumer welfare.
-Consumer welfare is computed as the difference between current utility and the utility that each household would receive from using vended water.
-Since utility is assumed to be quasi-linear, consumer welfare is measured in PhP/month.
-Lowering the fixed fee leads to substitution away from both vendor and neighbor water sources, which improves consumer welfare especially for the bottom \input{tables/group_percentile_group}\unskip\% of users.
-
-\begin{table}
-\centering
-\caption{Connection Fee Discount: Out-of-Sample Test Results}\label{table:oosestimates}
-\input{tables/oos_discount_estimates_group} \\ 
-\vspace{.2cm}
-\footnotesize{Fixed fee and consumer surplus are in PhP/month.}
-\end{table}
-
-\section{Test for Incidental Parameter Bias}\label{appendix:incidentalparametertest}
-
-The estimation strategy relies heavily on connection-specific fixed preference terms estimated in the Section~\ref{section:preferenceestimation} to recover parameters in Section~\ref{section:hasslecostestimation} and Section~\ref{section:fixedcostestimation}.
-Since the data contain a limited number of months of consumption for each connection (averaging around 50 months), noise in the estimation of these preference terms may produce bias in latter estimates.
-I test for this type of bias by simulating data given true parameters close to the estimates and reestimating the model on this simulated data.
-Table~\ref{table:incidentalparameters} provides results for this test.
-
-The first column presents the true assumed parameter values, the second column provides the estimation results for the simulated data using the full sample, and the third column includes estimates for a subsample of the data where I have dropped half of the observations for each connection.
-Examining the second column and percent deviations from the true parameters in the third column, I find that the incidental parameters do not seem to lead to a large degree of bias in any of the coefficients with the maximum occurring for the variance estimate for the vendor price.
-Dropping half of the time periods, the fourth and fifth columns indicate that the hassle cost and connection fee parameters would be the most sensitive to any possible bias from incidental parameters.
-
-\begin{table}
-\centering
-\caption{Simulation Test for Incidental Parameter Bias}\label{table:incidentalparameters}
-\input{tables/incidental_parameters}\\
-\footnotesize{T refers to months observed for each connections.
-The first sample includes half of the time periods per connection (around 35 months), while the second sample includes all months.
-Both samples include 5,000 accounts.}
-\end{table}
-
-\section{Out of Sample Test for Vendor Price Estimates}\label{appendix:vendorpriceestimates}
-
-%Since consumer surplus from using piped water is defined relative to using from a vendor, the magnitudes of the welfare calculations may be sensitive to the parameter estimates of the vendor option, particularly the marginal price, $p_v$.
-As a simple out-of-sample test, I compare this estimate of $p_v$ to the implied $p_v$ from data on total water expenditures for vendor households using additional census data from a section of Manila.
-
-As a simple out-of-sample test, I compare the estimate of $p_V$ in Table~\ref{table:smmestimates} to the implied $p_V$ from data on total water expenditures for vendor households using additional census data from a section of Manila.
-The 2011 Community Based Monitoring System data cover over 70\% of households in Pasay City --- a large area with a population of 500,000 in downtown Manila --- and includes information on income (used to compute imputed income) as well as water source and monthly expenditures.
-In this data, households using from vendors report expenditures of 365 PhP/month while households using individual connections report expenditures of 470 PhP/month and households sharing connections report expenditures of 365 PhP/month.
-I can express average marginal expenditures, $E_v$, by multiplying average vendor demand by the vendor price and adding the vendor fixed cost, $E_v = (\gamma - \alpha p_v) p_v + F_v$.
-Plugging in expenditures, $E_v =365$ PhP/$\text{m}^{3}$, average fixed preferences for vendors, $\gamma=37$, and price sensitivity, $\alpha=.91$, as well as solving the quadratic expression, I find that this level of expenditure is consistent with vendor prices of either 7.9 PhP/$\text{m}^{3}$ or 32.8 PhP/$\text{m}^{3}$.
-The latter price almost perfectly matches the estimated price of 32.85 PhP/$\text{m}^3$, providing additional support for the structural estimates from Section~\ref{section:fixedcostestimation}.
-
-\section{Simulated Method of Moments Model Fit}\label{appendix:modelfit}
-
-By weighting the first three moments (water source choices) highly by design, the model almost exactly matches moments shown in Table~\ref{table:modelfit}.
-The model is also able to match the direction of correlations between fixed preferences for water $\beta_i$ and percent owning connections as well as  percent using from a neighbor; however, the model predicts stronger correlations in both cases.
-One interpretation is that there may be other factors besides simply water preferences and heterogeneity in hassle costs that are driving water source decisions.
-The model has difficulty matching correlation between fixed preferences and share using from vendors, which may be partially due to noise generated in the process of imputing fixed preferences for households using from vendors.
-
-\begin{table}
-\centering
-\caption{Simulated Method of Moments Model Fit}\label{table:modelfit}
-\input{tables/smm_moments}
-\end{table}
-
-\end{appendices}
+- seizing booster pumps : https://timesofindia.indiatimes.com/city/navi-mumbai/booster-pumps-used-by-some-socs-leading-to-water-crunch/articleshow/68856763.cms , https://timesofindia.indiatimes.com/city/nagpur/215-booster-pumps-seized/articleshow/69804589.cms
 

### 2020-05-12 phil_matlab/new_sym.m

@@ -1,0 +1,249 @@
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes_pay/paper/tables/';
+
+
+% 
+% syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la
+% 
+% assume(r>0 & r<1)
+% assume(l>0)
+% assume(la>0)
+% assume(p1>0)
+% assume(p2>0)
+% 
+% assume(p1s>0)
+% assume(p2s>0)
+% 
+% assume(wc>0)
+% assume(w>0)
+% assume(x>0)
+% assume(wa>0)
+% assume(xa>0)
+% assume(y>0)
+% assume(alpha>0 & alpha<1)
+% assume(gamma>0)
+% assume(gammaa>0)
+% 
+% 
+% p = p1+p2*w;
+% BC = ( y - L -   (p*w+x) ) 
+% 
+% u = x + w - (1/(2*alpha))*( w + alpha - gamma )^2
+% lan  =  u  + l*BC
+% 
+% dw = simplify(diff(lan,w))
+% dx = diff(lan,x)
+% dl = diff(lan,l)
+% 
+% [ws,xs,ls]  =  solve([dw,dx,dl],[w,x,l])
+% 
+% %%% ASSUME NO EPSILON FOR NOW!
+% 
+% % UTILITY ALONE
+% u_alone = collect(simplify(subs(u,[w,x],[ws,xs])),gamma)
+% 
+% 
+% pa = p1+p2*(wa+wc);
+% BCa = ( y - L -   (pa*wa+xa) ) 
+% 
+% ua = xa + wa - (1/(2*alpha))*( wa + alpha - gammaa )^2
+% lana  =  ua  + la*BCa
+% 
+% dwa = simplify(diff(lana,wa))
+% dxa = diff(lana,xa)
+% dla = diff(lana,la)
+% 
+% [wsa,xsa,lsa]  =  solve([dwa,dxa,dla],[wa,xa,la])
+% 
+% wsac=subs(wsa,wc,ws);
+% xsac=subs(xsa,wc,ws);
+% 
+% u_share1 = collect(simplify(subs(ua,[wa,xa],[wsac,xsac])),[gammaa,gamma])
+
+
+
+syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la wca F
+
[…]

### 2020-05-12 phil_matlab/new_sym_1p.m

@@ -1,0 +1,155 @@
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes_pay/paper/tables/';
+
+syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la wca F
+
+assume(r>0 & r<1)
+assume(l>0)
+assume(la>0)
+assume(p1>0)
+assume(p2>0)
+
+assume(p1s>0)
+assume(p2s>0)
+
+assume(wc>0)
+assume(wca>0)
+assume(w>0)
+assume(x>0)
+assume(wa>0)
+assume(xa>0)
+assume(y>0)
+assume(alpha>0 & alpha<1)
+assume(gamma>0)
+assume(gammaa>0)
+assume(F>0)
+
+p = p1;
+BC = ( y -   (p*w+x) ) 
+
+u = x + w - (1/(2*alpha))*( w + alpha - gamma )^2
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[ws,xs,ls]  =  solve([dw,dx,dl],[w,x,l])
+
+%%% ASSUME NO EPSILON FOR NOW!
+
+% UTILITY SHARE
+u_alone1 = collect(simplify(subs(u,[w,x],[ws,xs])),gamma)
+u_share1 = subs(u_alone1,p1,p1s)
+
+u_alone2 = subs(u_alone1,gamma,gammaa)
+u_share2 = subs(u_share1,gamma,gammaa)
+
+simplify(u_share1 + u_share2 - u_alone1 - u_alone2 - F)
+
+
+
+
+% 
+% %[ws,xs,ls,pt,st]  =  solve([dw,dx,dl],[w,x,l],'ReturnConditions',true)
+% 
+% %s1=eval(subs(st,[p1,p2,y,alpha,A,Ap,r],[15,.2,30000,.02,-100,-100,.1]))
+% 
+% simplify(ws)
+% wt=eval(subs(ws,[p1,p2,y,alpha,A,Ap,L,k],[15,.2,30000,.02,100,100,100,0]))
+% xt=eval(subs(xs,[p1,p2,y,alpha,A,Ap,L,k],[15,.2,30000,.02,100,100,100,0]))
+% 
+% %wt=eval(subs(ws,[p1,p2,y,alpha,A,Ap,r],[15,.2,30000,.02,200,100,0]))
[…]

### 2020-05-12 phil_matlab/new_sym_2p.m

@@ -1,0 +1,249 @@
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes_pay/paper/tables/';
+
+
+% 
+% syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la
+% 
+% assume(r>0 & r<1)
+% assume(l>0)
+% assume(la>0)
+% assume(p1>0)
+% assume(p2>0)
+% 
+% assume(p1s>0)
+% assume(p2s>0)
+% 
+% assume(wc>0)
+% assume(w>0)
+% assume(x>0)
+% assume(wa>0)
+% assume(xa>0)
+% assume(y>0)
+% assume(alpha>0 & alpha<1)
+% assume(gamma>0)
+% assume(gammaa>0)
+% 
+% 
+% p = p1+p2*w;
+% BC = ( y - L -   (p*w+x) ) 
+% 
+% u = x + w - (1/(2*alpha))*( w + alpha - gamma )^2
+% lan  =  u  + l*BC
+% 
+% dw = simplify(diff(lan,w))
+% dx = diff(lan,x)
+% dl = diff(lan,l)
+% 
+% [ws,xs,ls]  =  solve([dw,dx,dl],[w,x,l])
+% 
+% %%% ASSUME NO EPSILON FOR NOW!
+% 
+% % UTILITY ALONE
+% u_alone = collect(simplify(subs(u,[w,x],[ws,xs])),gamma)
+% 
+% 
+% pa = p1+p2*(wa+wc);
+% BCa = ( y - L -   (pa*wa+xa) ) 
+% 
+% ua = xa + wa - (1/(2*alpha))*( wa + alpha - gammaa )^2
+% lana  =  ua  + la*BCa
+% 
+% dwa = simplify(diff(lana,wa))
+% dxa = diff(lana,xa)
+% dla = diff(lana,la)
+% 
+% [wsa,xsa,lsa]  =  solve([dwa,dxa,dla],[wa,xa,la])
+% 
+% wsac=subs(wsa,wc,ws);
+% xsac=subs(xsa,wc,ws);
+% 
+% u_share1 = collect(simplify(subs(ua,[wa,xa],[wsac,xsac])),[gammaa,gamma])
+
+
+
+syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la wca F
+
[…]

### 2020-05-12 phil_matlab/new_sym_better_util.m

@@ -1,0 +1,251 @@
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes_pay/paper/tables/';
+
+
+% 
+% syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la
+% 
+% assume(r>0 & r<1)
+% assume(l>0)
+% assume(la>0)
+% assume(p1>0)
+% assume(p2>0)
+% 
+% assume(p1s>0)
+% assume(p2s>0)
+% 
+% assume(wc>0)
+% assume(w>0)
+% assume(x>0)
+% assume(wa>0)
+% assume(xa>0)
+% assume(y>0)
+% assume(alpha>0 & alpha<1)
+% assume(gamma>0)
+% assume(gammaa>0)
+% 
+% 
+% p = p1+p2*w;
+% BC = ( y - L -   (p*w+x) ) 
+% 
+% u = x + w - (1/(2*alpha))*( w + alpha - gamma )^2
+% lan  =  u  + l*BC
+% 
+% dw = simplify(diff(lan,w))
+% dx = diff(lan,x)
+% dl = diff(lan,l)
+% 
+% [ws,xs,ls]  =  solve([dw,dx,dl],[w,x,l])
+% 
+% %%% ASSUME NO EPSILON FOR NOW!
+% 
+% % UTILITY ALONE
+% u_alone = collect(simplify(subs(u,[w,x],[ws,xs])),gamma)
+% 
+% 
+% pa = p1+p2*(wa+wc);
+% BCa = ( y - L -   (pa*wa+xa) ) 
+% 
+% ua = xa + wa - (1/(2*alpha))*( wa + alpha - gammaa )^2
+% lana  =  ua  + la*BCa
+% 
+% dwa = simplify(diff(lana,wa))
+% dxa = diff(lana,xa)
+% dla = diff(lana,la)
+% 
+% [wsa,xsa,lsa]  =  solve([dwa,dxa,dla],[wa,xa,la])
+% 
+% wsac=subs(wsa,wc,ws);
+% xsac=subs(xsa,wc,ws);
+% 
+% u_share1 = collect(simplify(subs(ua,[wa,xa],[wsac,xsac])),[gammaa,gamma])
+
+
+
+syms x w y p1 p2 p1s p2s r A l alpha Ap L k gamma gammaa p1s p2s wa xa wc la wca F
+
[…]

### 2020-05-12 phil_matlab_new/logit_test.m

@@ -1,0 +1,28 @@
+function  h = logit_test(a)
+
+
+global Y X0 X1 X2 X3 z div2 div3
+
+if length(a)==2
+    K=a(1,1);
+    F=a(1,2);
+end
+if length(a)==1
+    K=ones(z,1);
+    F=a(1,1);
+end
+
+v0=exp(K.*X0);
+v1=exp(K.*X1+F.*ones(z,1));
+v2=exp(K.*X2+(F./div2).*ones(z,1));
+v3=exp(K.*X3+(F./div3).*ones(z,1));
+
+p0=v0./(v1 + v2 + v3 + v0);
+p1=v1./(v1 + v2 + v3 + v0);
+p2=v2./(v1 + v2 + v3 + v0);
+p3=v3./(v1 + v2 + v3 + v0);
+
+h = -1.*sum((Y==0).*log(p0) + (Y==1).*log(p1) ...
+          + (Y==2).*log(p2) + (Y==3).*log(p3));
+
+end

### 2020-05-12 phil_matlab_new/lpost_3g2p.m

@@ -1,0 +1,91 @@
+function  h = lpost_3g2p(input,cobs,wobs,p1,p2,p3,y)
+
+a   = input(1);
+g   = input(2);
+sig = input(3);
+F   = input(4);
+
+
+u_ind = exp( u(a,g,p1,y)./y   +   u(a,g,p2,y )./y      + u(a,g,p3,y )./y ); % IND
+    w_p1_ind   = w(a,g,p1)              ;
+    w_p2_ind   = w(a,g,p2)              ;
+    w_p3_ind   = w(a,g,p3)              ;
+    
+u_12 =exp(  u(a,g,p1,y - F )./y + u(a,g,p1,y - F )./y + u(a,g,p3,y )./y ) ; % 1+2 SHR 
+    w_s_12  = w(a,g,p1) + w(a,g,p1)      ;
+    w_i_12  = w(a,g,p3)                  ;
+u_21 = exp( u(a,g,p2,y - F )./y + u(a,g,p2,y - F )./y + u(a,g,p3,y )./y ); % 2+1 SHR 
+    w_s_21  = w(a,g,p2) + w(a,g,p2)      ;
+    w_i_21  = w(a,g,p3)                  ;
+    
+u_13 = exp( u(a,g,p1,y - F )./y + u(a,g,p1,y - F )./y + u(a,g,p2,y )./y ); % 1+3 SHR 
+    w_s_13  = w(a,g,p1) + w(a,g,p1)     ;
+    w_i_13  = w(a,g,p2)                 ;
+u_31 =exp(  u(a,g,p3,y - F )./y + u(a,g,p3,y - F )./y + u(a,g,p2,y )./y ); % 3+1 SHR 
+    w_s_31  = w(a,g,p3) + w(a,g,p3)     ;
+    w_i_31  = w(a,g,p2)                 ;
+
+u_23 =exp(  u(a,g,p2,y - F )./y + u(a,g,p2,y - F )./y + u(a,g,p1,y )./y ); % 2+3 SHR 
+    w_s_23  = w(a,g,p2) + w(a,g,p2)     ;
+    w_i_23  = w(a,g,p1)                 ;
+u_32 =exp(  u(a,g,p3,y - F )./y + u(a,g,p3,y - F )./y + u(a,g,p1,y )./y ); % 3+2 SHR 
+    w_s_32  = w(a,g,p3) + w(a,g,p3)     ;
+    w_i_32  = w(a,g,p1)                 ;
+
[…]

### 2020-05-12 phil_matlab_new/ltest.m

@@ -1,0 +1,13 @@
+function  h = ltest(input,c,p1,p2)
+
+a = input(1);
+
+v1=exp(a.*p1);
+v2=exp(a.*p2);
+
+p1=v1./(v1 + v2);
+p2=v2./(v1 + v2);
+
+h = -1.*sum( (c==1).*log(p1) + (c==2).*log(p2) );
+
+end

### 2020-05-12 phil_matlab_new/ltest3.m

@@ -1,0 +1,32 @@
+function  h = ltest3(input,cobs,wobs,p1,p2,y)
+
+a   = input(1);
+g   = input(2);
+sig = input(3);
+F   = input(4);
+
+
+v1 = exp(u(a,g,p1,y )./y + u(a,g,p1,y    )./y);
+v2 = exp(u(a,g,p1,y - F )./y + u(a,g,p1,y - F)./y);
+v3 = exp(u(a,g,p1,y - F )./y + u(a,g,p1,y - F)./y);
+
+% cprob1=v1./(v1 + v2 + v3);
+% cprob2=v2./(v1 + v2 + v3);
+% cprob3=v3./(v1 + v2 + v3);
+
+cprob1_b=v1./(v1 + v2 + v3);
+cprob2_b=v2./(v1 + v2 + v3);
+cprob3_b=v3./(v1 + v2 + v3);
+
+cprob1 = 2.*cprob1_b./(2.*cprob1_b + cprob2_b + cprob3_b);
+cprob2 = cprob2_b./(2.*cprob1_b + cprob2_b + cprob3_b);
+cprob3 = cprob3_b./(2.*cprob1_b + cprob2_b + cprob3_b);
+
+wprob = normpdf( (wobs - w(a,g,p1)),0,sig ).*cprob1 ...
+      + normpdf( (wobs - w(a,g,p1) - w(a,g,p1)),0,sig ).*cprob2 ... 
+      + normpdf( (wobs - w(a,g,p1) - w(a,g,p1)),0,sig ).*cprob3 ;
+
+h = -1.*sum( (cobs==1).*log(cprob1) + (cobs==2).*log(cprob2) ...
+     + (cobs==3).*log(cprob3) + log(wprob) );
+
+end

### 2020-05-12 phil_matlab_new/ltest3_post_3g2p.m

@@ -1,0 +1,91 @@
+function  h = ltest3_post_3g2p(input,cobs,wobs,p1,p2,p3,y)
+
+a   = input(1);
+g   = input(2);
+sig = input(3);
+F   = input(4);
+
+
+u_ind = exp( u(a,g,p1,y)./y   +   u(a,g,p2,y )./y      + u(a,g,p3,y )./y ); % IND
+    w_p1_ind   = w(a,g,p1)              ;
+    w_p2_ind   = w(a,g,p2)              ;
+    w_p3_ind   = w(a,g,p3)              ;
+    
+u_12 =exp(  u(a,g,p1,y - F )./y + u(a,g,p1,y - F )./y + u(a,g,p3,y )./y ) ; % 1+2 SHR 
+    w_s_12  = w(a,g,p1) + w(a,g,p1)      ;
+    w_i_12  = w(a,g,p3)                  ;
+u_21 = exp( u(a,g,p2,y - F )./y + u(a,g,p2,y - F )./y + u(a,g,p3,y )./y ); % 2+1 SHR 
+    w_s_21  = w(a,g,p2) + w(a,g,p2)      ;
+    w_i_21  = w(a,g,p3)                  ;
+    
+u_13 = exp( u(a,g,p1,y - F )./y + u(a,g,p1,y - F )./y + u(a,g,p2,y )./y ); % 1+3 SHR 
+    w_s_13  = w(a,g,p1) + w(a,g,p1)     ;
+    w_i_13  = w(a,g,p2)                 ;
+u_31 =exp(  u(a,g,p3,y - F )./y + u(a,g,p3,y - F )./y + u(a,g,p2,y )./y ); % 3+1 SHR 
+    w_s_31  = w(a,g,p3) + w(a,g,p3)     ;
+    w_i_31  = w(a,g,p2)                 ;
+
+u_23 =exp(  u(a,g,p2,y - F )./y + u(a,g,p2,y - F )./y + u(a,g,p1,y )./y ); % 2+3 SHR 
+    w_s_23  = w(a,g,p2) + w(a,g,p2)     ;
+    w_i_23  = w(a,g,p1)                 ;
+u_32 =exp(  u(a,g,p3,y - F )./y + u(a,g,p3,y - F )./y + u(a,g,p1,y )./y ); % 3+2 SHR 
+    w_s_32  = w(a,g,p3) + w(a,g,p3)     ;
+    w_i_32  = w(a,g,p1)                 ;
+
[…]

### 2020-05-12 phil_matlab_new/new_sym_1p_clean.m

@@ -1,0 +1,160 @@
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p1 p2 a g g1 g2 w x F l
+assume(y>0)
+assume(p1>0)
+assume(p2>0)
+assume(a>0)
+assume(g>0)
+assume(g1>0)
+assume(g2>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+
+BC = ( y -   (p1*w+x) ) 
+
+u = x + w - (1/(2*a))*( w + a - g1 )^2
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[ws,xs,ls]  =  solve([dw,dx,dl],[w,x,l])
+
+%%% ASSUME NO EPSILON FOR NOW!
+
+% UTILITY SHARE
+u_alone1 = collect(simplify(subs(u,[w,x],[ws,xs])),g1)
+u_share1 = subs(u_alone1,p1,p2)
+
+u_alone2 = subs(u_alone1,g1,g2)
+u_share2 = subs(u_share1,g1,g2)
+
+
+simplify(u_share1 + u_share2 - u_alone1 - u_alone2 - F)
+
+
+
+solve(subs(simplify(u_share1 + u_share2 - u_alone1 - u_alone2 - F),[g1,g2],[g,g]),g)
+
+steps=10;
+
+
+
+matlabFunction(simplify(u_alone1,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','u.m')
+matlabFunction(simplify(ws,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','w.m')
+
+
+
+
+% matlabFunction(simplify(weq_opt,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','w_b_dkc.m')
+
+
+
+
+% 
+% %[ws,xs,ls,pt,st]  =  solve([dw,dx,dl],[w,x,l],'ReturnConditions',true)
+% 
+% %s1=eval(subs(st,[p1,p2,y,alpha,A,Ap,r],[15,.2,30000,.02,-100,-100,.1]))
+% 
+% simplify(ws)
+% wt=eval(subs(ws,[p1,p2,y,alpha,A,Ap,L,k],[15,.2,30000,.02,100,100,100,0]))
[…]

### 2020-05-12 phil_matlab_new/test2.m

@@ -1,0 +1,39 @@
+
+clear
+
+y = 1000;
+F = 100;
+
+sig = 3;
+g = 50;
+a = .4;
+n = 10000;
+p1v=50;
+p2v=10;
+p1 = repmat((1:p1v)',n/p1v,1);
+p2 = repmat((1:p2v)',n/p2v,1);
+
+rng(1);
+
+p1=normrnd(50,10,n,1);
+p2=normrnd(40,5,n,1);
+
+e  = evrnd(0,1,n,2);
+ep = normrnd(0,sig,n,2);
+
+u1 = u(a,g,p1,y)./y + e(:,1);
+u2 = u(a,g,p1,y)./y + e(:,2);
+
+w1 = w(a,g,p1) + ep(:,1);
+w2 = w(a,g,p2) + ep(:,2);
+
+
+cobs = 1.*(u1>u2) + 2.*(u2>u1);
+
+wobs = w1.*(u1>u2) + w2.*(u2>u1);
+
+obj=@(input1)ltest2(input1,cobs,wobs,p1,p2,y);
+
+input= .9.*[a g sig]
+
+out=fminunc(obj,input)

### 2020-05-12 phil_matlab_new/u3gen.m

@@ -1,0 +1,34 @@
+function U = u3gen(a1,a2,a3,g1,g2,g3,esq,...
+                y1,y2,y3,...
+                pi1,pr1,pi2,pr2,pi3,pr3)
+
+            % scale, then EXP! 
+
+u_ind = ua(a1,esq,g1,pi1,pr1,y1)  + ua(a2,esq,g2,pi2,pr2,y2) + ua(a3,esq,g3,pi3,pr3,y3) ; % IND
+
+% check 1 prefs, 2 prices
+
+u_12 = us2(a1,a2,esq,g1,g2,pi1,pr1,y1) + us2(a2,a1,esq,g2,g1,pi1,pr1,y2) + ua(a3,esq,g3,pi3,pr3,y3)  ; % 1+2 SHR 3 alone
+u_21 = us2(a1,a2,esq,g1,g2,pi2,pr2,y1) + us2(a2,a1,esq,g2,g1,pi2,pr2,y2) + ua(a3,esq,g3,pi3,pr3,y3)  ; % 2+1 SHR 3 alone
+
+u_13 = us2(a1,a3,esq,g1,g3,pi1,pr1,y1) + us2(a3,a1,esq,g3,g1,pi1,pr1,y3) + ua(a2,esq,g2,pi2,pr2,y2)  ; % 1+3 SHR 2 alone
+u_31 = us2(a1,a3,esq,g1,g3,pi3,pr3,y1) + us2(a3,a1,esq,g3,g1,pi3,pr3,y3) + ua(a2,esq,g2,pi2,pr2,y2)  ; % 3+1 SHR 2 alone
+
+u_23 = us2(a2,a3,esq,g2,g3,pi2,pr2,y2) + us2(a3,a2,esq,g3,g2,pi2,pr2,y3) + ua(a1,esq,g1,pi1,pr1,y1)  ; % 2+3 SHR 1 alone
+u_32 = us2(a2,a3,esq,g2,g3,pi3,pr3,y2) + us2(a3,a2,esq,g3,g2,pi3,pr3,y3) + ua(a1,esq,g1,pi1,pr1,y1)  ; % 3+2 SHR 1 alone
+
+u_1_3  =    us3(a1,a2,a3,esq,g1,g2,g3,pi1,pr1,y1) + ...
+            us3(a2,a1,a3,esq,g2,g1,g3,pi1,pr1,y2) + ...
+            us3(a3,a2,a1,esq,g3,g2,g1,pi1,pr1,y3) ; % all share with 1
+        
[…]

### 2020-05-12 phil_matlab_new/uS3.m

@@ -1,0 +1,21 @@
+function out1 = us3(a1,a2,a3,esq,g1,g2,g3,pi,pr,y)
+%US3
+%    OUT1 = US3(A1,A2,A3,ESQ,G1,G2,G3,PI,PR,Y)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    27-Apr-2020 15:16:32
+
+t2 = a1.^2;
+t3 = a1.^3;
+t4 = a2.^2;
+t5 = a3.^2;
+t6 = g1.^2;
+t7 = g2.^2;
+t8 = g3.^2;
+t9 = pi.^2;
+t10 = pr.^2;
+t11 = pr.^3;
+t13 = pr.^5;
+t12 = t10.^2;
+t14 = t10.^3;
+out1 = 1.0./(a1.*pr.*2.0+a2.*pr.*2.0+a3.*pr.*2.0+a1.*a2.*t10.*3.0+a1.*a3.*t10.*3.0+a2.*a3.*t10.*3.0+a1.*a2.*a3.*t11.*4.0+1.0).^2.*(a1.*(-1.0./2.0)+g1+y+(a1.*t9)./2.0-esq.*pr.*3.0-g1.*pi-pr.*t2.*2.0-pr.*t6-t3.*t10.*2.0-a1.*a2.*pr.*2.0-a1.*a3.*pr.*2.0+a1.*g1.*pr.*4.0+a2.*g1.*pr.*4.0+a3.*g1.*pr.*4.0-a1.*esq.*t10.*4.0-a2.*esq.*t10.*8.0-a3.*esq.*t10.*8.0-g1.*g2.*pr-g1.*g3.*pr-a2.*t2.*t10.*7.0-a1.*t4.*t10.*2.0-a3.*t2.*t10.*7.0-a1.*t5.*t10.*2.0-a2.*t3.*t11.*6.0-a1.*t6.*t10.*2.0-a3.*t3.*t11.*6.0+(a1.*t7.*t10)./2.0-a2.*t6.*t10.*3.0+(a1.*t8.*t10)./2.0-a3.*t6.*t10.*3.0+a1.*pr.*y.*4.0+a2.*pr.*y.*4.0+a3.*pr.*y.*4.0+esq.*t2.*t11.*4.0
[…]

### 2020-05-12 phil_matlab_pressure/ltest2.m

@@ -1,0 +1,31 @@
+function  h = ltest2(input,Bobs,wobs,p1,S,y,c,given)
+
+alpha0   = input(1);
+ alpha1   = input(2);
+ theta0   = input(3);
+ theta1   = input(4);
+  beta     = input(5);
+ sig      = input(6);
+
+% alpha1   = given(2);
+% theta0   = given(3);
+% theta1   = given(4);
+%  beta     = given(5);
+% sig      = given(6);
+
+v1 = exp( u( alpha0,alpha1,p1,theta0,theta1,S, 0 ,beta,y,c) );
+v2 = exp( u( alpha0,alpha1,p1,theta0,theta1,S, 1 ,beta,y,c) );
+
+Bprob1=v1./(v1 + v2);
+Bprob2=v2./(v1 + v2);
+
+w1 = normpdf( (wobs - w(alpha0,alpha1,p1,theta0,theta1,S,0,beta,y,c)),0,sig );
+w2 = normpdf( (wobs - w(alpha0,alpha1,p1,theta0,theta1,S,1,beta,y,c)),0,sig );
+
+% h = -1.*sum( (Bobs==1).*(log(Bprob1) + log(w1)) ...
+%            + (Bobs==2).*(log(Bprob2) + log(w2)) );
+
+h = -1.*sum( (Bobs==1).*(log(Bprob1) + 100000.*log(w1)) ...
+           + (Bobs==2).*(log(Bprob2) + 100000.*log(w2)) );
+
+end

### 2020-05-12 phil_matlab_pressure/ltest2a.m

@@ -1,0 +1,37 @@
+function  h = ltest2a(input,Bobs,wobs,p1,S,y,c,SC,given)
+
+alpha0   = input(1);
+alpha1   = input(2);
+theta0   = input(3);
+theta1   = input(4);
+gamma    = input(5);
+sig      = input(6);
+
+%  alpha0   = given(1);
+%  alpha1   = given(2);
+% %  theta0   = given(3);
+%  theta1   = given(4);
+% %  gamma    = given(5);
+%  sig      = given(6);
+
+
+
+v1 = exp( ua(  S,alpha0,alpha1,p1,theta0,theta1,y)./SC                );
+v2 = exp( ua(  S  + gamma,alpha0,alpha1,p1,theta0,theta1,y - c)./SC  );
+
+Bprob1=v1./(v1 + v2);
+Bprob2=v2./(v1 + v2);
+
+w1 = normpdf( (wobs - wa(  S,alpha0,alpha1,p1,theta0,theta1) ),0,sig );
+w2 = normpdf( (wobs - wa(  S  + gamma ,alpha0,alpha1,p1,theta0,theta1)   ),0,sig );
+
+% w1=1;
+% w2=1;
+
+h = -1.*sum( (Bobs==1).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==2).*(log(Bprob2) + log(w2)) );
+
+% h = -1.*sum( (Bobs==1).*(log(Bprob1) + 100000.*log(w1)) ...
+%            + (Bobs==2).*(log(Bprob2) + 100000.*log(w2)) );
+
+end

### 2020-05-12 phil_matlab_pressure/sym_test2a_1.m

@@ -1,0 +1,89 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p pi pr a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S
+syms alpha0 alpha1 p1 theta0 theta1
+assume(y>0)
+assume(p1>0)
+assume(pi>0)
+assume(pr>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=10;
+
+%%% ALONE %%%
+
+BC = ( y -   (p1*w+x) ) 
+
+u = x + theta0*S*(w - (1/(2*alpha1))*( w + alpha1 - alpha0 - theta1*S )^2)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+expand(wa)
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
+
+expand(ua)
+
+
+
+matlabFunction(simplify(wa,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','wa.m')
+matlabFunction(simplify(ua,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','ua.m')
+
+
+% ua_B = subs(ua,[y,S],[y-c,S+gamma])
+
+
+
+
+%%% ALONE %%%
+
+BC = ( y -   (p1*w+x) ) 
+
+u = x + (w - (1/(2*alpha1))*( w + alpha1 - alpha0  )^2)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[walt,xalt,lalt]  =  solve([dw,dx,dl],[w,x,l]);
+
+expand(walt)
+
+ualt = simplify(subs(u,[w,x],[walt,xalt]));
+
+expand(ualt)
+
+
+BC = ( y -   (p1*w+x) ) 
+
+u = x + (w - (1/(2*alpha1))*( w + alpha1 - alpha0 - theta0  )^2)
[…]

### 2020-05-12 phil_matlab_pressure/ua.m

@@ -1,0 +1,8 @@
+function out1 = ua(S,alpha0,alpha1,p1,theta0,theta1,y)
+%UA
+%    OUT1 = UA(S,ALPHA0,ALPHA1,P1,THETA0,THETA1,Y)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    09-May-2020 09:34:16
+
+out1 = y-alpha0.*p1+S.*alpha0.*theta0-(S.*alpha1.*theta0)./2.0-S.*p1.*theta1+S.^2.*theta0.*theta1+(alpha1.*p1.^2)./(S.*theta0.*2.0);

### 2020-05-12 phil_matlab_pressure/w.m

@@ -1,0 +1,4 @@
+function h = w(alpha0,alpha1,p1,theta0,theta1,S,B,beta,y,c)
+
+h = alpha0 + alpha1.*p1 + S.*(theta0+theta1.*B) + ...
+    + beta.*(y-c.*B)  ;

### 2020-05-12 pressure.py

@@ -1,0 +1,306 @@
+
+from sklearn.neighbors import NearestNeighbors
+from pysqlite2 import dbapi2 as sql
+import os, subprocess, shutil, multiprocessing, re, glob
+from functools import partial
+from itertools import product
+import numpy  as np
+import pandas as pd
+#from phil_subcode.spatial2sql import add_meter
+
+
+
+analysis = os.getcwd()[:os.getcwd().rfind('phil_code')]
+code = analysis + 'phil_code/'
+
+phil_folder = '/Users/williamviolette/Documents/Philippines/'
+database = phil_folder + 'database/'
+data = phil_folder + 'data/'
+
+gis_folder = data + 'gis/'
+generated = analysis + 'phil_generated/'
+db = generated+'phil.db'
+
+
+_1_IMPORT       = 0
+_2_DIST			= 1
+
+
+print range(0,1)
+
+
+if _1_IMPORT == 1:
+
+	print 'start'
+	def add_pipes(gis_folder,db):
+		cmd = ['ogr2ogr -f "SQLite" -update','-a_srs http://spatialreference.org/ref/epsg/25393/',
+		db, gis_folder+'PIPES.shp','-nln pipes', '-overwrite -skipfailures']
+		subprocess.call(' '.join(cmd),shell=True)
+		return 0
+
+	def add_valves(gis_folder,db):
+		cmd = ['ogr2ogr -f "SQLite" -update','-a_srs http://spatialreference.org/ref/epsg/25393/',
+		db, gis_folder+'VALVES.shp','-nln valves', '-overwrite -skipfailures']
+		subprocess.call(' '.join(cmd),shell=True)
+		return 0
+
+	def add_pipe_primary(gis_folder,db):
+		cmd = ['ogr2ogr -f "SQLite" -update','-a_srs http://spatialreference.org/ref/epsg/25393/',
+		db, gis_folder+'junk/pipe_primary_points.shp','-nln pipe_primary_points', '-overwrite -skipfailures']
+		subprocess.call(' '.join(cmd),shell=True)
+		return 0
+
+	def add_pipe_secondary(gis_folder,db):
+		cmd = ['ogr2ogr -f "SQLite" -update','-a_srs http://spatialreference.org/ref/epsg/25393/',
[…]

### 2020-07-16 phil_paper/paper_booster_pumps_wjv.tex
hessian runs, paper writing

@@
-\documentclass[12pt]{article}
-\usepackage[margin=1in] {geometry}                
-\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
-\pagestyle{plain}                           % Eliminates both the header and footer
-\usepackage[parfill]{parskip}
-\usepackage{graphicx}
-\usepackage{amssymb}
-\usepackage{epstopdf}
-\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
-\usepackage{amsmath, amsthm, amssymb}
-\usepackage{array}
-\usepackage{threeparttable}
-%\usepackage{pgfplots}
-\usepackage{tikz}
-\usepackage{tkz-euclide}
-\usepackage{longtable}
-\usepackage{caption}
-\usepackage{subcaption}
-\usepackage{verbatim}  %so that you can comment blocks of code
-\usepackage{setspace}  %change the spacing
-\usepackage[authoryear]{natbib}
-\usepackage{bbm}
-\usetikzlibrary{calc}
-%\usepackage{csvsimple}
-\usepackage[toc,page]{appendix}
-\usepackage{hyperref}
-\usepackage{cleveref}
-\usepackage{rotating}
-\usepackage{booktabs}
-\usepackage{authblk}
-\usepackage[bottom]{footmisc}
-\usepackage{titling}
-%% \newcommand{\KEYtitle}{Even Weights}
-%\usepackage[nomarkers]{endfloat}
-%\bibliography{library} 
-%\renewcommand{\efloatseparator}{\mbox{}}
-\usepackage{rotating}
-\usepackage{pdflscape}
-\usepackage[export]{adjustbox}
-\usetikzlibrary{positioning}
+\documentclass[12pt,table]{article}
 
-%\usepackage{datetime}
-%\newdateformat{monthyeardate}{\monthname[\THEMONTH]}
+\usepackage[table]{xcolor}
+% TEMPLATE DEFAULT PACKAGES
+\usepackage{amssymb,amsmath,amsfonts,eurosym,geometry,ulem,graphicx,xcolor,setspace,sectsty,comment,natbib,pdflscape,array,adjustbox,threeparttable}
 
-% \usepackage[notablist,nofiglist]{endfloat}
+% ADDED PACKAGES FOR THIS MANUSCRIPT
+\usepackage{palatino,newtxmath,multirow,titlesec,threeparttable,tabu,booktabs,titlesec,threeparttable,mathtools,bm,bbm,subcaption,pdflscape,tcolorbox,mathrsfs,float}
+% endfloat,
 
-%\renewcommand{\efloatseparator}{\mbox{}}
+%\usepackage{kbordermatrix}% http://www.hss.caltech.edu/~kcb/TeX/kbordermatrix.sty
+%\usepackage{amsmath}% http://ctan.org/pkg/amsmath
 
-% \renewcommand{\thetable}{\Roman{table}}
-% \renewcommand{\thefigure}{\Roman{figure}}
+\usepackage[colorinlistoftodos]{todonotes}
 
-% \renewcommand{\thesection}{\Roman{section}} 
-% \renewcommand{\thesubsection}{\thesection.\Alph{subsection}}
-% \renewcommand{\thesubsubsection}{\thesubsection.\roman{subsubsection}}
+\usepackage{afterpage}
+\usepackage[hyphens]{url}
+\usepackage[margin=1cm]{caption}
 
-%\usepackage[dvipsnames]{xcolor}
-%\usepackage{cite}
-\onehalfspacing
-\usepackage{natbib}  
-\title{ Optimal Pricing and Informal Sharing: \\ Evidence from Piped Water in Manila }
-%\title{OPTIMAL PRICING AND INFORMAL SHARING: \\ EVIDENCE FROM PIPED WATER IN MANILA}
+\usepackage[draft]{hyperref}
+\newcommand{\tim}{$\,\times\,$}
+% FIGURES & TABLES CAPTION STYLING
+\captionsetup[figure]{labelfont={bf},name={Figure},labelsep=period}
+\captionsetup[table]{labelfont={bf},name={Table},labelsep=period}
 
-\author{William Violette\thanks{Contact: Federal Trade Commission, Washington, DC: william.j.violette@gmail.com \\ I am grateful to Andrew Foster, Matthew Turner, Jesse Shapiro, Daniel Bj\"{o}rkegren, and Bryce Steinberg for guidance and encouragement.
-For helpful conversations, I am also grateful to John Friedman, Edward Glaeser, Emily Oster, Brian Knight, and Lint Barrage.
-In Manila, thank you to the staff of my water company partner, government regulators at MWSS, as well as the USAID Be-Secure project for access to data and excellent conversations.
-This work was supported through the Watson Institute for International and Public Affairs.
-Any opinions and conclusions expressed herein are those of the author and do not necessarily represent the views of the the Federal Trade Commission or its Commissioners.}
- }
-%\\ 
-%[Job Market Paper: \href{https://drive.google.com/file/d/1dM41qZLZY3EPtUqHbca6MIS-nT77hv_-/view?usp=sharing}{\textcolor{blue}{Link to Current Version}}]}
+% SECTION TITLE SETTINGS
+\titlelabel{\thetitle.\enskip}
+\titleformat*{\section}{\large\bfseries}
+\titleformat*{\subsection}{\normalsize\bfseries}
 
-\date{Current Version: March, 2019}
+% COLUMN TYPES
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}{>{\centering\arraybackslash}p{5.2em}}
+\newcolumntype{D}{>{\centering\arraybackslash}p{5em}}
+\newcolumntype{E}{>{\centering\arraybackslash}p{6em}}
+\newcolumntype{F}{>{\centering\arraybackslash}p{4em}}
+
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+
+\newcolumntype{J}{>{\raggedright\arraybackslash}p{5em}}
+\newcolumntype{K}{>{\raggedleft\arraybackslash}p{5em}}
+\newcolumntype{M}{>{\raggedleft\arraybackslash}p{6em}}
+
+\renewcommand{\arraystretch}{1.2}
+
+% MARGINS AND SPACING
+\normalem
+\geometry{left=1.1in,right=1.1in,top=1.0in,bottom=1.0in}
+\setlength{\parskip}{2.5pt}
+
+% SPECIAL CELL 
+\newcommand{\specialcell}[2][c]{%
+	\begin{tabular}[#1]{@{}l@{}}#2\end{tabular}}
+
+% NO INDENT ON FOOTNOTES
+\usepackage[hang,flushmargin]{footmisc}
+
 \begin{document}
 
+\begin{titlepage} 
+%\title{{Borrowing with Unpaid Bills}\thanks{}}
+%\title{{Microcredit from Delaying Bill Payments}\thanks{}}
+\title{Microcredit from Delaying Bill Payments}
+\author{\\[3em]
+  William Violette\thanks{Federal Trade Commission, Washington, DC.
+E-mail: william.j.violette@gmail.com   Any opinions and conclusions expressed herein are those of the author and do not necessarily represent the views of the Federal Trade Commission or its Commissioners.
+Many thanks to Matthew Panhans, Miriam Larson-Koester, Adrian Rubli-Ornelas, and Stefano Polloni.} \\
+ \\ 
+  }
+\vspace{30mm}
+\date{\vspace{5mm}This Version: \today}
 \maketitle
@@
 
-%	High costs of connecting to public utilities often
+Delaying bill payments to public utilities may provide an important strategy for households with volatile incomes to smooth their consumption.
+At the same time, tolerating late payments may reduce net revenues for utilities, which often leads to higher prices to cover costs.
+Using billing records from a large water utility in Manila, this paper estimates a household consumption and savings model to evaluate counterfactual payment policies.
+A popular proposal to ensure upfront payments --- prepaid metering --- recoups less revenue than is needed to compensate households for their loss of consumption smoothing.
+Alternatively, a revenue-neutral policy allowing more late payments increases welfare by encouraging greater consumption smoothing.
 
-%	lead households to share a connection with their neighbors instead of purchasing their own connection.
+\vspace{1in}
+\textbf{Keywords:} credit constraints; consumption smoothing; water utilities. \\
+\textbf{JEL Codes:} O13; E21; L95. \\
+\bigskip
+\end{abstract}
+\setcounter{page}{0}
+\thispagestyle{empty}
+\end{titlepage}
+\pagebreak \newpage
 
-%This paper analyzes how sharing connections affects optimal pricing for water utilities.
-
-	% Households often share connections to public utilities with their neighbors in order to split set-up and maintenance costs.
-With microdata from 1.5 million water connections in Manila, this paper estimates water demand when connections are shared and solves the regulator's problem: setting prices that maximize consumer surplus while covering production costs.
-In practice, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.
-Instead, the optimal policy covers production costs with high fixed prices, which are split between sharing households, and sets low marginal prices to encourage consumption.
-Counterfactual exercises find increases in shared connections, total piped water consumption, and social welfare from the optimal policy compared to current prices in Manila.
-
-%Sharing households split fixed prices with their neighbors to access the low marginal prices.
-
-%	Yet, I find that low fixed and high marginal prices also weaken incentives to share water between neighbors.
-
-%	Shared connections may have large implications for optimal pricing for public utilities especially 
-%	Households often offset the costs of connecting to public utilities by sharing a connection with their neighbors.  
-%	Sharing neighbor's connections 
-% In developing cities, high costs of connecting to piped water lead many households to use low-quality, non-piped sources.  
-% In response, cities often set low fixed prices so that more households connect and high marginal prices to cover production costs.  
-% This paper identifies a common alternative source --- sharing a neighbor's connection --- that has large implications for optimal water pricing.
-
-\end{abstract} 
-\vspace{1cm}
-{\bf JEL-Classification:} H23, L95, L98, O13, O17, O18 \\
-\vspace{.1cm}
-{\bf Keywords:} Water demand, non-linear pricing, informal sector, developing countries.
+%\spacing{1.5}
+\onehalfspacing
 
@@
 
-- Discusses use of booster pumps in Clean Water Act 2004:  https://www.manilatimes.net/2018/11/04/legal-advice/dearpao/use-of-booster-pumps/461829/  http://r12.emb.gov.ph/ra-9275-the-philippine-clean-water-act/
+Key notes to fill in later:
+- Ignore externalities of booster pumps
+- No quantity margin because of splitting of taps and because census data indicates really high coverage
+- Reweight by household number
+- Also measure by closest pipe for robustness
 
-- https://idl-bnc-idrc.dspacedirect.org/bitstream/handle/10625/14878/108376.pdf?sequence=5
+Section: Data
 
-- illegal booster pumps :  Consequence of El Niño 1997-98 on Manila water resources: new perspectives in water shortage management
+	- only households connected earlier (explain) (what share are those?!)
+	- consumption per HH
+	- reweight data for household level?!
 
-- seizing booster pumps : https://timesofindia.indiatimes.com/city/navi-mumbai/booster-pumps-used-by-some-socs-leading-to-water-crunch/articleshow/68856763.cms , https://timesofindia.indiatimes.com/city/nagpur/215-booster-pumps-seized/articleshow/69804589.cms
+	- Put in a table describing pipe-replacement;  describe staggered approach; predict pipe-replacement?
+
+Section: Descriptives and defending model and approach
+
+\section{Descriptives}
+
+Descriptive evidence indicates that fixing pipes improves water pressure, quality, and reliability, which may each affect consumer welfare.
+Table~\ref{table:descriptives} tracks water service improvements by comparing average household survey responses before and after pipe replacement.
+[summarize the findings]
+
+Consumers also invest in products and behaviors to compensate for low piped water service quality.
+These investments help reveal which aspects of piped water service are most valuable to consumers as well as most affected by pipe replacement.
+
+Large investments in booster pumps suggest that households strongly value water pressure.
+Before pipe replacement, 40\% of households invest in booster pumps that increase water pressure.
+Booster pumps are both expensive to purchase (PhP 6,000) and operate (benchmark with electricity costs).
+After pipe replacement, the share of households using booster pumps drops to 15\%.
+This finding is consistent with booster pumps providing an important substitute to pressure from new water pipes.
+
+Small investments in water filters combined with frequent purchases of filtered water both before and as well as after pipe replacement indicate that households may not derive large benefits from improvements in piped water quality.
+Only 12\% of households use water filters both before and after pipe replacements.
+Averaging ([cost of filters]), filters are also much less expensive than booster pumps.
+Low filter usage may stem from the fact that less than half of households report drinking from the tap while over 70\% of households report purchasing filtered water from local water-refilling stations.
+These behaviors remain constant after pipe replacements.
+Taken together, these findings indicate that water quality improvements from pipe replacements may not be primary drivers of changes in household welfare.
+
+Households cope with unreliable water supply by investing in water storage tanks.
+Before pipe replacement, 43\% of households report using water storage tanks.
+This percentage only drops to 36\% following pipe replacement, which is consistent with households continuing to report frequent water outages even after pipe replacement.
+While households seems to value reliable service, small changes in storage tank use suggest that reliability improvements are unlikely to account for a large share of the welfare gains from pipe replacements.
+
+\begin{table}[h!] 
+\centering
+\caption{Average Survey Responses Before and After Pipe Replacement}\label{table:descriptives}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{KKK}@{}}
+\toprule
+  & Before & After  & All \\
+\midrule
+Piped Water Quality \\[.5em]
+\hspace{1em}$\text{Water has strong pressure (6pm-12am)}^{\dagger}$ & \input{tables/yes_flow_6mid} \\
+\hspace{1em}$\text{Water has no pressure (6pm-12am)}^{\dagger}$  & \input{tables/no_flow_6mid} \\
+% \hspace{1em}$\text{Hours with pressure per day}^{\dagger}$ & \input{tables/flow_hrs} \\
+\hspace{1em}Water interruptions in last 3 months & \input{tables/stop_freq} \\
+\hspace{1em}Water has foreign bodies & \input{tables/foreign_bodies} \\
+\hspace{1em}Water is discolored & \input{tables/discolored} \\
+\hspace{1em}Water has unusual taste/smell & \input{tables/taste_smell} \\
+\\[-.5em]
+Private Water Quality Investments \\[.5em]
+\hspace{1em}Has booster pump & \input{tables/booster} \\
+\hspace{1em}Hours booster pump is used per day & \input{tables/booster_use} \\
+\hspace{1em}Has water storage tank & \input{tables/drum} \\
+\hspace{1em}Has water filter & \input{tables/filter} \\
+\hspace{1em}Purchases filtered water & \input{tables/station} \\
+\hspace{1em}Purchases from a deepwell & \input{tables/deepwell} \\
+\hspace{1em}Spending on non-piped water (PhP) & \input{tables/wrs_exp} \\
+\hspace{1em}Drinks from the tap & \input{tables/drink} \\
+% \hspace{1em}Boils tap water before drinking & \input{tables/boil} \\
+\\[-.5em]
+Demographics \\[.5em]
+\hspace{1em}Household size & \input{tables/hhsize} \\
+\hspace{1em}Employed members & \input{tables/hhemp} \\
+\hspace{1em}High-skilled employment & \input{tables/good_job} \\
+\hspace{1em}Lives in duplex& \input{tables/sub} \\
+\hspace{1em}Lives in single house& \input{tables/single} \\
+\hspace{1em}Other households sharing tap& \input{tables/SHO} \\
+\\[-.5em]
+Households & \input{tables/pawsn} \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item  $\dagger$ when not using booster pump.
+Bill, Unpaid Balance, Payment, and Income are in PhP.
+Measures exclude months where households remain disconnected through the end of the sample period.
+Billing data include households for household-month observations.
+Income data include households for household-month observations.
+45 PhP = 1 USD \,\,
+% See Appendix~\ref{appendix:sampleconstruction} for more details on the sample construction.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+Increases in water pressure from pipe replacements may lead households to increase their monthly water consumption.
+Rapid water flow allows households to complete a greater number of water-using activities (like cleaning and bathing) in the same amount of time.
+Greater water pressure may also allow households to engage in new activities that require minimum pressure levels such as showering.\footnote{By contrast, water quality improvements may have an ambiguous effect on water consumption.
+On one hand, cleaner water may induce households to use more tap water for cooking and cleaning.
+On the other hand, cleaner water may increase the productivity of cleaning and bathing, which may lead households to use less piped water.}  Figure~\ref{figure:pipecons} plots average monthly water usage per household in the 4 years before and 6 after pipe replacement.
+Usage increases from an average of \input{tables/c_pre}m3 before pipe replacement to \input{tables/c_post}m3 after pipe replacement, which represents an \input{tables/c_diff_per}\unskip\% increase.
+The increase in usage occurs abruptly at the year of pipe replacement and remains at roughly the same level in the following 6 years.
+This sustained increase in consumption suggests that pipe replacement may provide sustained impacts on household welfare.
+
+The absence of strong pre-trends in usage suggests that replacement projects are not targeted to areas with particular trends in local water demand.
+Instead, this pattern is consistent with the company's stated goal of sequentially replacing old pipes according to engineering specifications.
+Table~\ref{table:descriptives} further supports this theory by indicating few demographic differences between households that receive pipe replacement projects (columns (1) and (2)) and all households (column (3)).
+Also, demographic characteristics appear relatively similar before and after pipe replacement, which suggests that pipe replacements were not coupled with other policies that may have also affected demand for water.
+
+\begin{figure}
+\begin{center}
+\caption{Average Consumption per Household with Years to Pipe Replacement}\label{figure:pipecons}
+\includegraphics[scale=1]{tables/pipe_cons.pdf}
+\end{center}
+%%% add counts and average change in discussion
+\end{figure}
+% discuss dynamics!!! of figure!!
+
+Mapping these increases in consumption into household welfare requires measuring how households trade off water usage and price.
+Prices are determined by the government regulator who imposes an increasing tariff schedule according to monthly usage, which is standard among public utilities (\cite{hoque2013state}).
+Despite steep increases in marginal price at specific levels of usage, households do not appear to be sensitive to these price changes because households are not observed adjusting their consumption strategically to avoid higher prices (cite appendix).
+The regulator also increases prices gradually over time to ensure that the company continues to cover operating costs.
+Since households also gradually increase their average usage over this interval, it is unclear whether households are responsive to these price increases (cite appendix).
+
+The government regulator also gives the water company discretion to assign households to a high-price tariff schedule if they have any business activity at their residence, which provides a novel source of price variation in the context of public utilities.
+In the vast majority of cases, the high price tariff is applied to households that operate small food stands (or ``Sari-Sari'' stores).
+For a household with average monthly usage, the high-price tariff results in an average price of \input{tables/p_s}PhP/m3 while the regular tariff results in an average price of \input{tables/p_r}PhP/m3 (cite appendix for tariff).
+The water company periodically visits consumers and updates prices according to the activities observed at each consumer's residence.
+In some cases, consumers request price changes, which prompts the company to investigate the household and determine the appropriate price.
+Table~\ref{table:pricechangestatistics} provides average characteristics of households that are always observed with the regular price (in column (1)), that are always observed with the high price (in column (2)), and that are observed changing prices during the sample (in column (3)).
+While the 2,442 households that experience price changes use more water than other households, they share similar demographic characteristics, which suggests that they may also share similar price-sensitivities.
+
+Figure~\ref{figure:usagepricechanges} plots average usage 4 years before and after households are switched from the regular price to the high price (in red) as well as before and after households are switched from the high price to the regular price (in blue).
+Before the price change, average usage for both groups follows relatively constant trends.
+The price change is associated with a usage jump for households switched to the regular price and a corresponding usage slide for households switched to the high price.
+The changes in consumption appear relatively persistent up to 4 four years after the price changes.
+These patterns indicate that household water usage is sensitive to large, discrete price changes.
+
+\begin{table}[h!] % PUT IN DEMOGRAPHICS PLEASE ?!?!?
+\centering
+\caption{Average Household Characteristics by Prices Charged}\label{table:pricechangestatistics}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{KKK}@{}}
+\toprule
+  & Always Reg. Price & Always High Price  & Change Price \\
+\midrule
+Usage per Household (m3)& \input{tables/cv_rs} \\
+Household size & \input{tables/hhsize_rs} \\
+Employed members & \input{tables/hhemp_rs} \\
+High-skilled employment & \input{tables/good_job_rs} \\
+Lives in duplex& \input{tables/sub_rs} \\
+Lives in single house& \input{tables/single_rs} \\
+Other households sharing tap& \input{tables/SHO_rs} \\
+\\[-.5em]
+Households & \input{tables/N_rs} \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item  Reg. refers to regular price.
+
+Pressure is 6 to midnight!
+Bill, Unpaid Balance, Payment, and Income are in PhP.
+Measures exclude months where households remain disconnected through the end of the sample period.
+Billing data include households for household-month observations.
+Income data include households for household-month observations.
+45 PhP = 1 USD \,\,
+% See Appendix~\ref{appendix:sampleconstruction} for more details on the sample construction.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{figure}
+\begin{center}
+\caption{Usage and Price Changes}\label{figure:usagepricechanges}
+\includegraphics[scale=1]{tables/r_to_s_graph.pdf}
+\end{center}
+\end{figure}
+
+ % If households were sensitive to price increases at specific consumption levels, then households would be expected to frequently consume just below these levels.
+However, Appendix Figure plots the frequency
+
+% The welfare benefits of fixing water pipes depends on which dimensions of service quality are improved by pipe replacement.
+Table~\ref{table:descriptives} compares average household survey responses before and after pipe replacement.
+
+% Allow services that they couldn't before
+
+% Before pipe replacement, households experience weak water pressure and low water quality.
+30\% of households report generally having no water pressure from 6 pm to 12 am in the absence of an extra household pump to boost water pressure.
+23\% of households report that their piped water generally has foreign bodies.
+
+% To compensate for low piped water quality, many households invest in private water booster pumps, storage drums, water filters, and purchases of non-piped water.
+
+% Both pressure and water quality improve substantially following pipe replacement.
+The shares of households reporting no water pressure, water discoloration, foreign bodies, and unusual tastes/smells all drop to below 6\%.
+
+% - Quality complements more consumption
+% - Water quality implies that consume the same, just enjoy it wayyy more
+% 	- maybe need to clean things longer
+% 	- maybe clean things the same but get way more utility
+
+% - Pressure implies that quantity is positively linked to quality!
+% 	- has the same feature?
+% 	- use the same water, just less time...
+% 	- costly to push for that extra water..... from a time perspective
+% 		- Natural to think of relieving the pressure as leading to greater consumption!
+
+	% Table: 
+	% 	(A) What does pipe fixing mean?
+	% 		- Quality, Hours, Flow
+
+	% 	(B) How do households change their investments?
+
+	% 	(C) How do households use their water?
+
+	% 	(D) Household demographics including sharing
+	% 		* N 
+	% 	(E) Household consumption/payments/disconnection/standard deviation! (from billing data N)
+	% 		* N
+
+%%%% PIPE AGE %%%  possibly lower quality as well
+% http://www.mayniladwater.com.ph/news-article.php?id=656
+% West Zone concessionaire Maynilad Water Services, Inc.
+(Maynilad) replaced a total of 196 kilometers of old pipes in 2016, bringing the total length of pipes replaced within its concession area to 1,709 kilometers—about the same distance from Manila to Hanoi, Vietnam—since the company’s re-privatization in 2007.
+% Maynilad invested ₱1.85 billion for its pipe replacement projects in 2016 alone.
+The old pipelines rehabilitated last year were located mostly in Quezon City, Manila and Bacoor City, where “pipe age” ranged from 30 to 40 years.
+% http://www.mayniladwater.com.ph/news-article.php?id=366
+% Maynilad spends 77M to replace 24km pipes in Malabon
+% July 03, 2013
+
+% West Zone concessionaire Maynilad Water Services, Inc.
+(Maynilad) is replacing 23.6 kilometers of secondary and tertiary pipes in Malabon City to improve services to more than 12,800 households in the area.
+The water company is spending some P77 million to replace the 30-year old pipes by the 3rd quarter of 2013.
+
+% % doesn't dramatically change substitution to other sources!
+
+% Reference Hanoi for how households may care about water use
+% 	- percentages
+
+% --- Water pump depreciation!?
+
+% Figure consumption graph for effect dynamics (appendix with all other effect dynamics)
+
+% Figures no bunching; small changes over time
+% 	- Cite a bunch of other papers here... novel identification....
+
+% Figures price variation and selection into switchers...
+% 	- examine robustness to alternative alpha definitions...
+
+Section Model:
+	- What are the key model choices?
+		- Satiation in water consumption
+		- Linear term in quality
+			- need to include expectation?
+		- Booster error independence ! (keep assumption!) and sorting
+		- Booster externality assumption
+
+Section Estimation:
+	- show what happens when boosters are turned off
+
+Section Welfare:
+	- Welfare benefits with 10 yr 5\% loans (assume discount rates) or 50 yr 5\% loan?
+	- Welfare benefits with cash
+	- Are households willing to pay for pipe improvements?
+
+Robustness:
+	- Use nearest pipe replacement definition (selection into meter identification)
+
+% - Discusses use of booster pumps in Clean Water Act 2004:  https://www.manilatimes.net/2018/11/04/legal-advice/dearpao/use-of-booster-pumps/461829/  http://r12.emb.gov.ph/ra-9275-the-philippine-clean-water-act/
+% - https://idl-bnc-idrc.dspacedirect.org/bitstream/handle/10625/14878/108376.pdf?sequence=5
+% - illegal booster pumps :  Consequence of El Niño 1997-98 on Manila water resources: new perspectives in water shortage management
+% - seizing booster pumps : https://timesofindia.indiatimes.com/city/navi-mumbai/booster-pumps-used-by-some-socs-leading-to-water-crunch/articleshow/68856763.cms , https://timesofindia.indiatimes.com/city/nagpur/215-booster-pumps-seized/articleshow/69804589.cms
+
+\section{Appendix}
+
+\begin{figure}
+\caption{Price Time-Series}\label{figure:pricetimeseries}
+\begin{center}
+\includegraphics[scale=1]{tables/price_series.pdf}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\caption{Tariff Schedule}
+\begin{center}
+\includegraphics[scale=1]{tables/rs_prices.pdf}
+\end{center}
+\end{figure}
+
+\begin{figure}
+\begin{center}
+\caption{Consumption Histogram}
+\includegraphics[scale=1]{tables/consumption_histogram.pdf}
+\end{center}
+\end{figure}
 

### 2020-07-16 phil_matlab_pressure/GH.m

@@ -1,0 +1,1 @@
+function [valw,gw,hw] = GH(

### 2020-07-16 phil_matlab_pressure/booster1_2.m

@@ -1,0 +1,65 @@
+
+
+
+clear
+
+
+c = 1000;
+B=1;
+
+
+sig = 18;
+
+alpha1 = 1;
+
+theta1 =  2;
+theta2 =  2;
+theta3 = -1;
+
+theta1 =  0;
+theta2 =  0;
+theta3 =  0;
+
+SC = 100;
+
+y = 10000;
+
+data=1;
+if data==1
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1.csv');
+    cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1ch.csv');
+        wobs    = cs(:,1);
+        Bobs    = cs(:,2);
+        post    = cs(:,3);
+        p       = cs(:,4);
+        year    = cs(:,5);
+        cmax    = cs(:,6);
+        cmin    = cs(:,7);
+        hhsize  = cs(:,8);
+end
+
+        %  int year cmax cmin hhsize 
+alpha0 =  [28;   .1;  3;   -1.7;   2.5]  ;
+A  = [ ones(size(wobs,1),1)  year cmax cmin hhsize];
+
+
+alpha0 =  [16     ]  ;
+A  = [ ones(size(wobs,1),1)  ];
+
+alen = size(alpha0,1);
+
+% Nb = A*alpha0;
+
+given = [alpha0; alpha1; theta1; theta2; theta3; sig];
+
+obj=@(input1)lbooster1_2(input1,Bobs,wobs,p,y,SC,c,B,post,A,alen,given);
+
+
+input= [alpha0; alpha1; theta1; theta2; theta3; sig]
+
+input= [alpha0; alpha1]
+
+out=fminunc(obj,input)
+
+
+

### 2020-07-16 phil_matlab_pressure/booster1_3ghtest.m

@@ -1,0 +1,93 @@
+
+
+
+clear
+
+
+c = 500;
+B=1;
+
+
+
+
+% theta1 =  0;
+% theta2 =  0;
+% theta3 =  0;
+
+SC = 100;
+
+y = 10000;
+
+data=1;
+if data==1
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1.csv');
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1ch.csv');
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2.csv');
+        wobs    = cs(:,1);
+        Bobs    = cs(:,2);
+        post    = cs(:,3);
+        p       = cs(:,4);
+        year    = cs(:,5);
+        cmax    = cs(:,6);
+        cmin    = cs(:,7);
+        hhsize  = cs(:,8);
+        hhemp   = cs(:,9); 
+        good_job= cs(:,10);
+        sho     = cs(:,11);
+        
+end
+
+% alpha0 =  [28;   .1;  3;   -1.7;   2.5]  ;
+% A  = [ ones(size(wobs,1),1)  year cmax cmin hhsize];
+
+sig    = 14;
+alpha1 = .3;
+theta1 =  3.5;
+theta2 =  2.5;
+theta3 =  -1.5;
+
+alpha0 =  [18;                1.3;     .5;  3.3;   -3;  -.04; 2.4   ];
+A  = [ ones(size(wobs,1),1)  hhsize hhemp good_job sho year cmax  ];
+
+alpha0 =  [18;                1.5  ];
+A  = [ ones(size(wobs,1),1)  hhsize   ];
+
+
+% alpha0 =  [16     ]  ;
+% A  = [ ones(size(wobs,1),1) year cmax cmin hhsize ];
+% Nb = A*alpha0;
+
+given = [alpha0; sig; alpha1; theta1; theta2; theta3];
+
+% obj1=@(input1_1)lbooster1_3gh(input1_1,Bobs,wobs,pi,y,SC,c,post,A,given);
+obj=@(input1)lbooster1_3(input1,Bobs,wobs,p,y,SC,c,B,post,A,given);
+
+
+input= [alpha0; sig; alpha1; theta1; theta2; theta3]
+
+% obj1(input)
+obj(input)
+
[…]

### 2020-07-16 phil_matlab_pressure/booster1_4c.m

@@ -1,0 +1,120 @@
+
+
+
+clear
+
+
+c = 500;
+B=1;
+
+% to do:
+% (1) identify c? (understand identification in general) 
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?
+% (3) get the right solutions?
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period!
+     
+% (5) run counterfactuals?? COMPARE welfare with and without 
+
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+
+
+SC = 100;
+
+% y = 21907;
+y = 1000;
+
+data=1;
+if data==1
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1.csv');
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1ch.csv');
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2.csv');
+        wobs    = cs(:,1);
+        Bobs    = cs(:,2);
+        post    = cs(:,3);
+        p       = cs(:,4);
+        year    = cs(:,5);
+        cmax    = cs(:,6);
+        cmin    = cs(:,7);
+        hhsize  = cs(:,8);
+        hhemp   = cs(:,9); 
+        good_job= cs(:,10);
+        sho     = cs(:,11);
+        
+end
+
+% alpha0 =  [28;   .1;  3;   -1.7;   2.5]  ;
+% A  = [ ones(size(wobs,1),1)  year cmax cmin hhsize];
+
+sig    = 14;
+alpha1 = .3;
+theta1 =  3.5;
+theta2 =  2.5;
+theta3 =  -1.5;
+
+alpha0 =  [18;                1.3;     .5;  3.3;   -3;  -.04; 2.4   ];
[…]

### 2020-07-16 phil_matlab_pressure/booster1_4sa.m

@@ -1,0 +1,133 @@
+
+
+
+clear
+
+
+c = 500;
+B=1;
+
+% to do:
+% (1) identify c? (understand identification in general) 
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?
+% (3) get the right solutions?
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period!
+     
+% (5) run counterfactuals?? COMPARE welfare with and without 
+
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+
+
+SC = 100;
+
+% y = 21907;
+y = 1000;
+
+data=1;
+if data==1
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1.csv');
+%     cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_1ch.csv');
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2.csv');
+        wobs    = cs(:,1);
+        Bobs    = cs(:,2);
+        post    = cs(:,3);
+        p       = cs(:,4);
+        year    = cs(:,5);
+        cmax    = cs(:,6);
+        cmin    = cs(:,7);
+        hhsize  = cs(:,8);
+        hhemp   = cs(:,9); 
+        good_job= cs(:,10);
+        sho     = cs(:,11);
+        
+end
+
+% alpha0 =  [28;   .1;  3;   -1.7;   2.5]  ;
+% A  = [ ones(size(wobs,1),1)  year cmax cmin hhsize];
+
+sig    = 14;
+alpha1 = .3;
+theta1 =  3.5;
+theta2 =  2.5;
+theta3 =  -1.5;
+
[…]

### 2020-07-16 phil_matlab_pressure/booster1_6nl.m

@@ -1,0 +1,152 @@
+
+
+
+clear
+
+
+
+% to do:
+% (1) identify c? (understand identification in general) [ NO ASSUME IT! ]
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?   [ ESTIMATED! ]
+% (3) get the right solutions?   maybe dig deeper here...
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period! ! 
+     
+% (5) run counterfactuals?? COMPARE welfare with and without   [ yes! ]
+
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+
+% 1 HP engine uses 0.786 Kw/Hour , meaning a .5 HP engine uses .786/2=.3930
+% price .2 USD * 44 PhP/USD = 8.8 PhP per KwH
+% 30days*2.6hrs*8.8 per KwH * .393 Kwh = 269.8
+% btw .25 and 1 hp engines used in Manila
+%  .5*270/2 + .5*270*2 = 338 PhP
+     
+c = 338;
+
+% y = 21907;
+y = 1000;
+
+data=1;
+if data==1
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2nl.csv');
+        wobs    = cs(:,1);
+        Bobs    = cs(:,2);
+        post    = cs(:,3);
+        pi      = cs(:,4);
+        pr      = cs(:,5);
+        year    = cs(:,6);
+        cmax    = cs(:,7);
+        cmin    = cs(:,8);
+        hhsize  = cs(:,9);
+        hhemp   = cs(:,10); 
+        good_job= cs(:,11);
+        sho     = cs(:,12);
+        
+end
+
+% alpha0 =  [28;   .1;  3;   -1.7;   2.5]  ;
[…]

### 2020-07-16 phil_matlab_pressure/booster_gh10.m

@@ -1,0 +1,149 @@
+
+
+
+clear
+
+% to do:
+% (1) identify c? (understand identification in general) [ NO ASSUME IT! ]
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?   [ ESTIMATED! ]
+% (3) get the right solutions?   maybe dig deeper here...
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period! ! 
+% (5) run counterfactuals?? COMPARE welfare with and without   [ yes! ]
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+% 1 HP engine uses 0.786 Kw/Hour , meaning a .5 HP engine uses .786/2=.3930
+% price .2 USD * 44 PhP/USD = 8.8 PhP per KwH
+% 30days*2.6hrs*8.8 per KwH * .393 Kwh = 269.8
+% btw .25 and 1 hp engines used in Manila
+%  .5*270/2 + .5*270*2 = 338 PhP
+     
+data=1;
+if data==1
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2nl.csv');
+      
+       cs = cs(1:50000,:)  ;
+      
+        wobs    = cs(:,1);
+        bobs    = cs(:,2);
+        post    = cs(:,3);
+        p_i     = cs(:,4);
+        pr      = cs(:,5);
+        year    = cs(:,6);
+        cmax    = cs(:,7);
+        cmin    = cs(:,8);
+        hhsize  = cs(:,9);
+        hhemp   = cs(:,10); 
+        good_job= cs(:,11);
+        sho     = cs(:,12);
+      
+      p_i = p_i + 25.*pr;       
+
+      
[…]

### 2020-07-16 phil_matlab_pressure/booster_gh5.m

@@ -1,0 +1,106 @@
+
+
+
+clear
+
+
+
+% to do:
+% (1) identify c? (understand identification in general) [ NO ASSUME IT! ]
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?   [ ESTIMATED! ]
+% (3) get the right solutions?   maybe dig deeper here...
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period! ! 
+     
+% (5) run counterfactuals?? COMPARE welfare with and without   [ yes! ]
+
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+
+% 1 HP engine uses 0.786 Kw/Hour , meaning a .5 HP engine uses .786/2=.3930
+% price .2 USD * 44 PhP/USD = 8.8 PhP per KwH
+% 30days*2.6hrs*8.8 per KwH * .393 Kwh = 269.8
+% btw .25 and 1 hp engines used in Manila
+%  .5*270/2 + .5*270*2 = 338 PhP
+     
+data=0;
+if data==1
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2nl.csv');
+        wobs    = cs(:,1);
+        Bobs    = cs(:,2);
+        post    = cs(:,3);
+        p_i      = cs(:,4);
+        pr      = cs(:,5);
+        year    = cs(:,6);
+        cmax    = cs(:,7);
+        cmin    = cs(:,8);
+        hhsize  = cs(:,9);
+        hhemp   = cs(:,10); 
+        good_job= cs(:,11);
+        sho     = cs(:,12);
+else
+    rng(3)
+    n = 60000;
+%     A = 50 + rand(n,1);
+    p_i = 5 + 30.*rand(n,1);
+    p_r = .3;
+
+end
+
+% alpha0 =  [28;   .1;  3;   -1.7;   2.5]  ;
[…]

### 2020-07-16 phil_matlab_pressure/cbooster1_4.m

@@ -1,0 +1,35 @@
+function  h = cbooster1_4(input,Bobs,wobs,p,y,SC,c,post,A,given)
+
+B=1;
+alen=size(A,2);
+alpha0   = input(1:alen);
+sig      = input(alen +1);
+alpha1   = input(alen +2);
+theta1   = input(alen +3);
+theta2   = input(alen +4);
+theta3   = input(alen +5);
+
+
+% alpha0   = given(1:alen);
+% sig      = given(alen +1);
+% alpha1   = given(alen +2);
+% theta1   = given(alen +3);
+% theta2   = given(alen +4);
+% theta3   = given(alen +5);
+
+a0 = A*alpha0;
+
+v1 = exp( up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)./SC                );
+v2 = exp( up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c)./SC  );
+
+Bprob1=v1./(v1 + v2);
+Bprob2=v2./(v1 + v2);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) ),0,sig );
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  ),0,sig );
+
+h = -1.*sum( (Bobs==0).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==1).*(log(Bprob2) + log(w2)) );
+
+
+end

### 2020-07-16 phil_matlab_pressure/d2_alpha1.m

@@ -1,0 +1,8 @@
+function out1 = d2_alpha1(alpha0,alpha1,pi,pr,theta1)
+%D2_ALPHA1
+%    OUT1 = D2_ALPHA1(ALPHA0,ALPHA1,PI,PR,THETA1)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    28-Jun-2020 17:17:33
+
+out1 = pr.*1.0./(alpha1.*pr.*2.0+1.0).^3.*(pi+alpha0.*pr.*2.0+pr.*theta1.*2.0).*4.0;

### 2020-07-16 phil_matlab_pressure/gh1.m

@@ -1,0 +1,60 @@
+function [val,g,h] = gh1(alpha0,alpha1,nc,np,p_i,p_r,sig,theta1,wobs)
+%GH1
+%    [VAL,G,H] = GH1(ALPHA0,ALPHA1,NC,NP,P_I,P_R,SIG,THETA1,WOBS)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    29-Jun-2020 10:33:16
+
+t2 = alpha1.*p_i;
+t3 = alpha0.^2;
+t4 = alpha1.^2;
+t5 = p_i.^2;
+t6 = p_r.^2;
+t7 = sig.^2;
+t8 = theta1.^2;
+t9 = wobs.^2;
+t10 = alpha0.*p_r.*2.0;
+t11 = alpha1.*p_r.*2.0;
+t12 = alpha0.*p_r.*4.0;
+t13 = p_r.*theta1.*2.0;
+t14 = p_r.*theta1.*4.0;
+t15 = p_r.*wobs.*2.0;
+t16 = -alpha0;
+t18 = 1.0./sig.^3;
+t19 = -theta1;
+t17 = 1.0./t7;
+t20 = -t2;
+t21 = -t15;
+t22 = p_r.*t2.*2.0;
+t23 = t11.*wobs;
+t24 = -t7;
+t25 = t11+1.0;
+t27 = alpha1.*p_r.*t7.*4.0;
+t28 = alpha1.*t6.*wobs.*4.0;
+t35 = p_i+t10+t13;
+t36 = t4.*t6.*t7.*4.0;
+t26 = -t22;
+t29 = -t27;
+t30 = -t28;
+t31 = alpha0+t20+theta1;
+t32 = 1.0./t25;
+t37 = -t36;
+t38 = t2+t16+t19+t23+wobs;
+t33 = t32.^2;
+t34 = t32.^3;
+t39 = t31.*t32;
+val = -log(exp(t17.*(t39-wobs).^2.*(-1.0./2.0))./(nc.*sig));
+if nargout > 1
[…]

### 2020-07-16 phil_matlab_pressure/gh1_h.m

@@ -1,0 +1,13 @@
+function hh = gh1_h(alpha0,alpha1,es,pi,pr,theta1)
+%GH1_H
+%    HH = GH1_H(ALPHA0,ALPHA1,ES,PI,PR,THETA1)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    29-Jun-2020 09:22:46
+
+t2 = alpha1.*pr.*2.0;
+t3 = t2+1.0;
+t4 = 1.0./t3.^2;
+t5 = pr.*t4.*2.0;
+t6 = -t5;
+hh = [es,t6,t6,pr.^2.*1.0./t3.^3.*(alpha0+theta1-alpha1.*pi).*8.0+pi.*pr.*t4.*4.0];

### 2020-07-16 phil_matlab_pressure/gh3.m

@@ -1,0 +1,71 @@
+function [val,g,h] = gh3(AC,A_1,A_2,alpha1,alpha0_1,alpha0_2,nc,np,p_i,p_r,sig,theta1,wobs)
+%GH3
+%    [VAL,G,H] = GH3(AC,A_1,A_2,ALPHA1,ALPHA0_1,ALPHA0_2,NC,NP,P_I,P_R,SIG,THETA1,WOBS)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    29-Jun-2020 14:02:06
+
+t2 = A_1.*alpha0_1;
+t3 = A_2.*alpha0_2;
+t4 = alpha1.*p_i;
+t5 = A_1.^2;
+t6 = A_2.^2;
+t7 = alpha1.^2;
+t8 = p_r.^2;
+t9 = sig.^2;
+t10 = wobs.^2;
+t11 = AC.*p_r.*2.0;
+t12 = AC.*p_r.*4.0;
+t13 = alpha1.*p_r.*2.0;
+t14 = p_r.*theta1.*2.0;
+t15 = p_r.*theta1.*4.0;
+t16 = p_r.*wobs.*2.0;
+t17 = 1.0./nc;
+t19 = 1.0./sig.^3;
+t21 = -wobs;
+t32 = alpha1.*p_r.*wobs.*-2.0;
+t18 = 1.0./t9;
+t22 = -t4;
+t23 = -t16;
+t24 = p_r.*t2.*2.0;
+t25 = p_r.*t2.*4.0;
+t26 = p_r.*t3.*2.0;
+t27 = p_r.*t3.*4.0;
+t28 = p_r.*t4.*2.0;
+t29 = t13.*wobs;
+t30 = t13+1.0;
+t33 = alpha1.*t8.*wobs.*4.0;
+t20 = t18.^2;
+t31 = -t28;
+t34 = -t33;
+t35 = 1.0./t30;
+t38 = AC+t2+t3+t22+theta1;
+t40 = p_i+t11+t14+t24+t26;
+t36 = t35.^2;
+t37 = t35.^3;
+t41 = t35.*t38;
+t42 = t21+t32+t38;
+t48 = p_i+t12+t15+t23+t25+t27+t31+t34;
+t39 = A_1.*A_2.*np.*t18.*t36;
+t43 = -t41;
+t45 = (t41-wobs).^2;
[…]

### 2020-07-16 phil_matlab_pressure/ghu10.m

@@ -1,0 +1,434 @@
+function [val,g,h] = ghu10(AC,AVB,AVN,A_1,A_2,TCb,TCn,TVB,TVN,T_1b,T_2b,T_1n,T_2n,UV,alpha1,alpha0_1,alpha0_2,bobs,c,es,nc,np,p_i,sig,siga,theta0_1,theta0_2,wobs)
+%GHU10
+%    [VAL,G,H] = GHU10(AC,AVB,AVN,A_1,A_2,TCB,TCN,TVB,TVN,T_1B,T_2B,T_1N,T_2N,UV,ALPHA1,ALPHA0_1,ALPHA0_2,BOBS,C,ES,NC,NP,P_I,SIG,SIGA,THETA0_1,THETA0_2,WOBS)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    05-Jul-2020 13:43:53
+
+t2 = A_1.*alpha0_1;
+t3 = A_2.*alpha0_2;
+t4 = AVB.*bobs;
+t5 = AVN.*bobs;
+t6 = T_1b.*T_2b;
+t7 = T_1n.*T_2n;
+t8 = TCb.*p_i;
+t9 = TCn.*p_i;
+t10 = T_1b.*theta0_1;
+t11 = T_2b.*theta0_2;
+t12 = T_1n.*theta0_1;
+t13 = T_2n.*theta0_2;
+t14 = alpha1.*p_i;
+t15 = es.*np;
+t16 = AVB.^2;
+t17 = AVN.^2;
+t18 = A_1.^2;
+t19 = A_2.^2;
+t20 = TVB.^2;
+t21 = TVN.^2;
+t22 = T_1b.^2;
+t23 = T_2b.^2;
+t24 = T_1n.^2;
+t25 = T_2n.^2;
+t26 = UV.^2;
+t27 = UV.^3;
+t28 = bobs.*2.0;
+t29 = p_i.^2;
+t30 = siga.*2.0;
+t31 = sig.^2;
+t32 = siga.^2;
+t33 = wobs.^2;
+t34 = AVB.*T_1b;
+t35 = AVB.*T_2b;
+t36 = AVN.*T_1n;
+t37 = AVN.*T_2n;
+t39 = T_1n.*wobs.*2.0;
+t40 = T_2n.*wobs.*2.0;
+t49 = 1.0./pi;
+t50 = -TVN;
+t51 = -T_1n;
[…]

### 2020-07-16 phil_matlab_pressure/ghu10_input.m

@@ -1,0 +1,33 @@
+function [UV,AVB,AVN,TVB,TVN] = ghu10_input(AC,A_1,A_2,TCb,TCn,T_1b,T_2b,T_1n,T_2n,alpha1,alpha0_1,alpha0_2,c,p_i,theta0_1,theta0_2)
+%GHU10_INPUT
+%    [UV,AVB,AVN,TVB,TVN] = GHU10_INPUT(AC,A_1,A_2,TCB,TCN,T_1B,T_2B,T_1N,T_2N,ALPHA1,ALPHA0_1,ALPHA0_2,C,P_I,THETA0_1,THETA0_2)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    05-Jul-2020 13:52:53
+
+t2 = A_1.*alpha0_1;
+t3 = A_2.*alpha0_2;
+t4 = T_1b.*theta0_1;
+t5 = T_2b.*theta0_2;
+t6 = T_1n.*theta0_1;
+t7 = T_2n.*theta0_2;
+t8 = alpha1.*p_i;
+t9 = 1.0./alpha1;
+t10 = -t8;
+t11 = TCb+t4+t5;
+t12 = TCn+t6+t7;
+t13 = AC+t2+t3+t10+t11;
+t14 = AC+t2+t3+t10+t12;
+UV = -c-TCb.*p_i+TCn.*p_i-p_i.*t4-p_i.*t5+p_i.*t6+p_i.*t7+t9.*(t11.*t13-(t10+t11).^2./2.0)-t9.*(t12.*t14-(t10+t12).^2./2.0);
+if nargout > 1
+    AVB = t13;
+end
+if nargout > 2
+    AVN = t14;
+end
+if nargout > 3
+    TVB = t11;
+end
+if nargout > 4
+    TVN = t12;
+end

### 2020-07-16 phil_matlab_pressure/ghu6_input.m

@@ -1,0 +1,66 @@
+function [EV,OV,KV,UV,AV,AVB,TV,TVB] = ghu6_input(AC,A_1,A_2,TC,TCb,T_1,T_2,T_1b,T_2b,alpha1,alpha0_1,alpha0_2,nc,p_i,sig,siga,theta0_1,theta0_2,wobs,y,yb)
+%GHU6_INPUT
+%    [EV,OV,KV,UV,AV,AVB,TV,TVB] = GHU6_INPUT(AC,A_1,A_2,TC,TCB,T_1,T_2,T_1B,T_2B,ALPHA1,ALPHA0_1,ALPHA0_2,NC,P_I,SIG,SIGA,THETA0_1,THETA0_2,WOBS,Y,YB)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    30-Jun-2020 15:12:20
+
+t2 = A_1.*alpha0_1;
+t3 = A_2.*alpha0_2;
+t4 = TC.*p_i;
+t5 = TCb.*p_i;
+t6 = T_1.*theta0_1;
+t7 = T_2.*theta0_2;
+t8 = T_1b.*theta0_1;
+t9 = T_2b.*theta0_2;
+t10 = alpha1.*p_i;
+t15 = 1.0./alpha1;
+t16 = 1.0./sig.^2;
+t17 = -wobs;
+t11 = p_i.*t6;
+t12 = p_i.*t7;
+t13 = p_i.*t8;
+t14 = p_i.*t9;
+t18 = -t10;
+t19 = TC+t6+t7;
+t20 = TCb+t8+t9;
+t21 = t18+t19;
+t22 = t18+t20;
+t23 = t21.^2;
+t24 = t22.^2;
+t27 = AC+t2+t3+t21;
+t28 = AC+t2+t3+t22;
+t25 = t23./2.0;
+t26 = t24./2.0;
+t29 = t17+t27;
+t31 = t19.*t27;
+t32 = t20.*t28;
+t30 = t29.^2;
+t33 = -t31;
+t34 = -t32;
+t35 = t25+t33;
+t36 = t26+t34;
+t37 = t15.*t35;
+t38 = t15.*t36;
+EV = erf((sqrt(2.0).*(t4-t5+t11+t12-t13-t14+t37-t38+wobs-y+yb))./(siga.*2.0))./2.0+1.0./2.0;
+if nargout > 1
+    OV = exp(t16.*t30.*(-1.0./2.0))./(nc.*sig);
+end
[…]

### 2020-07-16 phil_matlab_pressure/ghu9_input.m

@@ -1,0 +1,33 @@
+function [UV,AVB,AVN,TVB,TVN] = ghu9_input(AC,A_1,A_2,TCb,TCn,T_1b,T_2b,T_1n,T_2n,alpha1,alpha0_1,alpha0_2,p_i,theta0_1,theta0_2,y,yb)
+%GHU9_INPUT
+%    [UV,AVB,AVN,TVB,TVN] = GHU9_INPUT(AC,A_1,A_2,TCB,TCN,T_1B,T_2B,T_1N,T_2N,ALPHA1,ALPHA0_1,ALPHA0_2,P_I,THETA0_1,THETA0_2,Y,YB)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    04-Jul-2020 14:21:00
+
+t2 = A_1.*alpha0_1;
+t3 = A_2.*alpha0_2;
+t4 = T_1b.*theta0_1;
+t5 = T_2b.*theta0_2;
+t6 = T_1n.*theta0_1;
+t7 = T_2n.*theta0_2;
+t8 = alpha1.*p_i;
+t9 = 1.0./alpha1;
+t10 = -t8;
+t11 = TCb+t4+t5;
+t12 = TCn+t6+t7;
+t13 = AC+t2+t3+t10+t11;
+t14 = AC+t2+t3+t10+t12;
+UV = -y+yb-TCb.*p_i+TCn.*p_i-p_i.*t4-p_i.*t5+p_i.*t6+p_i.*t7+t9.*(t11.*t13-(t10+t11).^2./2.0)-t9.*(t12.*t14-(t10+t12).^2./2.0);
+if nargout > 1
+    AVB = t13;
+end
+if nargout > 2
+    AVN = t14;
+end
+if nargout > 3
+    TVB = t11;
+end
+if nargout > 4
+    TVN = t12;
+end

### 2020-07-16 phil_matlab_pressure/ghu9_ns_t1.m

@@ -1,0 +1,200 @@
+function [val,g,h] = ghu9_ns_t1(AC,AVB,AVN,A_1,A_2,TCb,TCn,TVB,TVN,T_1b,T_2b,T_1n,T_2n,UV,alpha1,alpha0_1,alpha0_2,bobs,np,p_i,siga,theta0_1,theta0_2,y,yb)
+%GHU9_NS_T1
+%    [VAL,G,H] = GHU9_NS_T1(AC,AVB,AVN,A_1,A_2,TCB,TCN,TVB,TVN,T_1B,T_2B,T_1N,T_2N,UV,ALPHA1,ALPHA0_1,ALPHA0_2,BOBS,NP,P_I,SIGA,THETA0_1,THETA0_2,Y,YB)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    04-Jul-2020 12:22:48
+
+t2 = A_1.*alpha0_1;
+t3 = A_2.*alpha0_2;
+t4 = T_1b.*T_2b;
+t5 = T_1n.*T_2n;
+t6 = TCb.*p_i;
+t7 = TCn.*p_i;
+t8 = T_1b.*theta0_1;
+t9 = T_2b.*theta0_2;
+t10 = T_1n.*theta0_1;
+t11 = T_2n.*theta0_2;
+t12 = alpha1.*p_i;
+t13 = TVB.^2;
+t14 = TVN.^2;
+t15 = T_1b.^2;
+t16 = T_2b.^2;
+t17 = T_1n.^2;
+t18 = T_2n.^2;
+t19 = UV.^2;
+t20 = UV.^3;
+t21 = bobs.*2.0;
+t22 = siga.^2;
+t23 = AVB.*T_1b;
+t24 = AVB.*T_2b;
+t25 = AVN.*T_1n;
+t26 = AVN.*T_2n;
+t27 = UV.*siga.*2.0;
+t36 = 1.0./pi;
+t37 = 1.0./alpha1;
+t42 = bobs-1.0;
+t43 = 1.0./siga;
+t48 = -yb;
+t49 = AVB.*TVB.*2.0;
+t50 = AVN.*TVN.*2.0;
+t54 = sqrt(2.0);
+t57 = sqrt(pi);
+t28 = T_1b.*t12;
+t29 = T_2b.*t12;
+t30 = T_1n.*t12;
+t31 = T_2n.*t12;
+t32 = p_i.*t8;
[…]

### 2020-07-16 phil_matlab_pressure/gp.m

@@ -1,0 +1,8 @@
+function out1 = gp(A_1,A_2,A_3,A_4,A_5,A_6,A_7,SC,T_1,T_2,T_3,alpha1,alpha0_1,alpha0_2,alpha0_3,alpha0_4,alpha0_5,alpha0_6,alpha0_7,c,pi,theta1_1,theta1_2,theta1_3,y)
+%GP
+%    OUT1 = GP(A_1,A_2,A_3,A_4,A_5,A_6,A_7,SC,T_1,T_2,T_3,ALPHA1,ALPHA0_1,ALPHA0_2,ALPHA0_3,ALPHA0_4,ALPHA0_5,ALPHA0_6,ALPHA0_7,C,PI,THETA1_1,THETA1_2,THETA1_3,Y)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    22-Jun-2020 15:56:35
+
+out1 = [(A_1.*exp((alpha1.*y.*2.0+T_2.^2.*theta1_2.^2+alpha1.^2.*pi.^2+A_1.*T_2.*alpha0_1.*theta1_2.*2.0+A_2.*T_2.*alpha0_2.*theta1_2.*2.0+A_3.*T_2.*alpha0_3.*theta1_2.*2.0+A_4.*T_2.*alpha0_4.*theta1_2.*2.0+A_5.*T_2.*alpha0_5.*theta1_2.*2.0+A_6.*T_2.*alpha0_6.*theta1_2.*2.0+A_7.*T_2.*alpha0_7.*theta1_2.*2.0-A_1.*alpha1.*alpha0_1.*pi.*2.0-A_2.*alpha1.*alpha0_2.*pi.*2.0-A_3.*alpha1.*alpha0_3.*pi.*2.0-A_4.*alpha1.*alpha0_4.*pi.*2.0-A_5.*alpha1.*alpha0_5.*pi.*2.0-A_6.*alpha1.*alpha0_6.*pi.*2.0-A_7.*alpha1.*alpha0_7.*pi.*2.0-T_2.*alpha1.*pi.*theta1_2.*2.0)./(SC.*alpha1.*2.0)).*(T_1.*theta1_1+T_3.*theta1_3))./(SC.*alpha1.*(exp((alpha1.*c.*-2.0+alpha1.*y.*2.0+T_1.^2.*theta1_1.^2
[…]

### 2020-07-16 phil_matlab_pressure/grad1.m

@@ -1,0 +1,1 @@
+function grad1

### 2020-07-16 phil_matlab_pressure/gus.m

@@ -1,0 +1,8 @@
+function out1 = gus(A_1,A_2,A_3,A_4,A_5,A_6,A_7,T_1,T_2,T_3,alpha1,alpha0_1,alpha0_2,alpha0_3,alpha0_4,alpha0_5,alpha0_6,alpha0_7,g1,pi,theta1_1,theta1_2,theta1_3)
+%GUS
+%    OUT1 = GUS(A_1,A_2,A_3,A_4,A_5,A_6,A_7,T_1,T_2,T_3,ALPHA1,ALPHA0_1,ALPHA0_2,ALPHA0_3,ALPHA0_4,ALPHA0_5,ALPHA0_6,ALPHA0_7,G1,PI,THETA1_1,THETA1_2,THETA1_3)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    24-Jun-2020 11:46:37
+
+out1 = [(A_1.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,(A_2.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,(A_3.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,(A_4.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,(A_5.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,(A_6.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,(A_7.*(T_1.*theta1_1+T_3.*theta1_3))./alpha1,g1,1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3).*(A_1.*alpha0_1.*2.0+A_2.*alpha0_2.*2.0+A_3.*alpha0_3.*2.0+A_4.*alpha0_4.*2.0+A_5.*alpha0_5.*2.0+A_6.*alpha0_6.*2.0+A_7.*alpha0_7.*2.0+T_1.*theta1_1+T_2.*theta1_2.*2.0+T_3.*theta1_3).*(-1.0./2.0),(T_1.*(A_1.*alpha0_1+A_2.*alpha0_2+A_3.*alpha0_3+A_4.*alpha0_4+A_5.*alpha0_5+A_6.*alpha0_6+A_7.*alpha0_7+T_1.*theta1_1+T_2.*theta1_2+T_3.*theta1_3-alpha1.*pi))./alpha1,(T_2.*(T_1.*theta1_1
[…]

### 2020-07-16 phil_matlab_pressure/gwp.m

@@ -1,0 +1,8 @@
+function out1 = gwp(A_1,A_2,A_3,A_4,A_5,A_6,A_7,T_1,T_2,T_3,alpha1,alpha0_1,alpha0_2,alpha0_3,alpha0_4,alpha0_5,alpha0_6,alpha0_7,pi,sig,theta1_1,theta1_2,theta1_3,wobs)
+%GWP
+%    OUT1 = GWP(A_1,A_2,A_3,A_4,A_5,A_6,A_7,T_1,T_2,T_3,ALPHA1,ALPHA0_1,ALPHA0_2,ALPHA0_3,ALPHA0_4,ALPHA0_5,ALPHA0_6,ALPHA0_7,PI,SIG,THETA1_1,THETA1_2,THETA1_3,WOBS)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    22-Jun-2020 15:55:57
+
+out1 = [-A_1.*1.0./sig.^2.*(-wobs+A_1.*alpha0_1+A_2.*alpha0_2+A_3.*alpha0_3+A_4.*alpha0_4+A_5.*alpha0_5+A_6.*alpha0_6+A_7.*alpha0_7+T_1.*theta1_1+T_2.*theta1_2+T_3.*theta1_3-alpha1.*pi),-A_2.*1.0./sig.^2.*(-wobs+A_1.*alpha0_1+A_2.*alpha0_2+A_3.*alpha0_3+A_4.*alpha0_4+A_5.*alpha0_5+A_6.*alpha0_6+A_7.*alpha0_7+T_1.*theta1_1+T_2.*theta1_2+T_3.*theta1_3-alpha1.*pi),-A_3.*1.0./sig.^2.*(-wobs+A_1.*alpha0_1+A_2.*alpha0_2+A_3.*alpha0_3+A_4.*alpha0_4+A_5.*alpha0_5+A_6.*alpha0_6+A_7.*alpha0_7+T_1.*theta1_1+T_2.*theta1_2+T_3.*theta1_3-alpha1.*pi),-A_4.*1.0./sig.^2.*(-wobs+A_1.*alpha0_1+A_2.*alpha0_2+A_3.*alpha0_3+A_4.*alpha0_4+A_5.*alpha0_5+A_6.*alpha0_6+A_7.*alpha0_7+T_1.*theta1_1+T_2.*theta1_2+T_3.*theta1_3-alpha
[…]

### 2020-07-16 phil_matlab_pressure/hs.m

@@ -1,0 +1,20 @@
+function [g,h] =  hs(x,wobs,sig,dh01,dh10,dh11)
+
+% dh01 = FROM hess1
+% dh10
+% dh11
+
+pdf=1;
+[gx,dg,dg2] = ng_normalpdf(x,wobs,sig,pdf);
+
+%%%% log difference!
+df   =  1./gx      ;
+df2  = -1./(gx.^2) ;
+
+g =-1.*( dh01.*df.*dg);
+
+h = dh01.*dh10.*dg.^2.*df2  + ...
+dh01.*dh10.*dg2.*  df  + ...
+dh11.*      dg .*  df  ;
+
+

### 2020-07-16 phil_matlab_pressure/hus.m

@@ -1,0 +1,8 @@
+function out1 = hus(A_1,A_2,A_3,A_4,A_5,A_6,A_7,T_1,T_2,T_3,alpha1,alpha0_1,alpha0_2,alpha0_3,alpha0_4,alpha0_5,alpha0_6,alpha0_7,g1,theta1_1,theta1_2,theta1_3)
+%HUS
+%    OUT1 = HUS(A_1,A_2,A_3,A_4,A_5,A_6,A_7,T_1,T_2,T_3,ALPHA1,ALPHA0_1,ALPHA0_2,ALPHA0_3,ALPHA0_4,ALPHA0_5,ALPHA0_6,ALPHA0_7,G1,THETA1_1,THETA1_2,THETA1_3)
+
+%    This function was generated by the Symbolic Math Toolbox version 8.5.
+%    24-Jun-2020 11:46:37
+
+out1 = reshape([g1,g1,g1,g1,g1,g1,g1,g1,-A_1.*1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3),(A_1.*T_1)./alpha1,g1,(A_1.*T_3)./alpha1,g1,g1,g1,g1,g1,g1,g1,g1,-A_2.*1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3),(A_2.*T_1)./alpha1,g1,(A_2.*T_3)./alpha1,g1,g1,g1,g1,g1,g1,g1,g1,-A_3.*1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3),(A_3.*T_1)./alpha1,g1,(A_3.*T_3)./alpha1,g1,g1,g1,g1,g1,g1,g1,g1,-A_4.*1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3),(A_4.*T_1)./alpha1,g1,(A_4.*T_3)./alpha1,g1,g1,g1,g1,g1,g1,g1,g1,-A_5.*1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3),(A_5.*T_1)./alpha1,g1,(A_5.*T_3)./alpha1,g1,g1,g1,g1,g1,g1,g1,g1,-A_6.*1.0./alpha1.^2.*(T_1.*theta1_1+T_3.*theta1_3),(A_6.*T_1)./alpha1,g1,(A_6.*T_3)./alph
[…]

### 2020-07-16 phil_matlab_pressure/lbooster1_2.m

@@ -1,0 +1,42 @@
+function  h = lbooster1_2(input,Bobs,wobs,p,y,SC,c,B,post,A,given)
+
+alen=size(A,2);
+alpha0   = input(1:alen);
+% alpha1   = input(alen +1);
+% theta1   = input(alen +2);
+% theta2   = input(alen +3);
+% theta3   = input(alen +4);
+% sig      = input(alen +5);
+
+% alpha0   = given(1:alen);
+alpha1   = given(alen +1);
+theta1   = given(alen +2);
+theta2   = given(alen +3);
+theta3   = given(alen +4);
+sig      = given(alen +5);
+
+
+a0 = A*alpha0;
+
+v1 = exp( up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)./SC                );
+v2 = exp( up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c)./SC  );
+
+Bprob1=v1./(v1 + v2);
+Bprob2=v2./(v1 + v2);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3)  )./sig )./sig;
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  )./sig )./sig;
+
+% w1=1;
+% w2=1;
+
+h = -1.*sum( (Bobs==1).*( log(w1)) ...
+           + (Bobs==2).*( log(w2)) );
+
+% h = -1.*sum( (Bobs==1).*(log(Bprob1) + log(w1)) ...
+%            + (Bobs==2).*(log(Bprob2) + log(w2)) );
+
+% h = -1.*sum( (Bobs==1).*(log(Bprob1) + 100000.*log(w1)) ...
+%            + (Bobs==2).*(log(Bprob2) + 100000.*log(w2)) );
+
+end

### 2020-07-16 phil_matlab_pressure/lbooster1_3.m

@@ -1,0 +1,45 @@
+function  h = lbooster1_3(input,Bobs,wobs,p,y,SC,c,B,post,A,given)
+
+alen=size(A,2);
+alpha0   = input(1:alen);
+sig      = input(alen +1);
+alpha1   = input(alen +2);
+theta1   = input(alen +3);
+theta2   = input(alen +4);
+theta3   = input(alen +5);
+
+
+% alpha0   = given(1:alen);
+% sig      = given(alen +1);
+% alpha1   = given(alen +2);
+% theta1   = given(alen +3);
+% theta2   = given(alen +4);
+% theta3   = given(alen +5);
+
+
+
+a0 = A*alpha0;
+
+v1 = exp( up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)./SC                );
+v2 = exp( up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c)./SC  );
+
+Bprob1=v1./(v1 + v2);
+Bprob2=v2./(v1 + v2);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) ),0,sig );
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  ),0,sig );
+
+% mean(w1)
+% w1=1;
+% w2=1;
+
+% h = -1.*sum( (Bobs==0).*( log(w1)) ...
+%            + (Bobs==1).*( log(w2)) );
+
+h = -1.*sum( (Bobs==0).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==1).*(log(Bprob2) + log(w2)) );
+
+% h = -1.*sum( (Bobs==1).*(log(Bprob1) + 100000.*log(w1)) ...
+%            + (Bobs==2).*(log(Bprob2) + 100000.*log(w2)) );
+
+end

### 2020-07-16 phil_matlab_pressure/lbooster1_4c.m

@@ -1,0 +1,54 @@
+function  [h,um,bm] = lbooster1_4c(input,Bobs,wobs,p,y,SC,post,A,given)
+
+B=1;
+alen=size(A,2);
+alpha0   = input(1:alen);
+sig      = input(alen +1);
+alpha1   = input(alen +2);
+theta1   = input(alen +3);
+theta2   = input(alen +4);
+theta3   = input(alen +5);
+c        = input(alen +6);
+
+
+% alpha0   = given(1:alen);
+% sig      = given(alen +1);
+% alpha1   = given(alen +2);
+% theta1   = given(alen +3);
+% theta2   = given(alen +4);
+% theta3   = given(alen +5);
+
+a0 = A*alpha0;
+
+v1 = exp( up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)./SC  );
+v2 = exp( up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c)./SC    );
+
+Bprob1=v1./(v1 + v2);
+Bprob2=v2./(v1 + v2);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) ),0,sig );
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  ),0,sig );
+
+h = -1.*sum( (Bobs==0).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==1).*(log(Bprob2) + log(w2)) );
+
+
+if nargout>1
+    rng(3);
+    n = size(A,1);
+    e  = evrnd(0,1,n,2);
+%     ep = normrnd(0,sig,n,2);
+   upn1= up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y);
+   upn2= up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c);
+
+    v1s = up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)./SC  + e(:,1);
+    v2s = up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c)./SC + e(:,2);
[…]

### 2020-07-16 phil_matlab_pressure/lbooster1_4sa.m

@@ -1,0 +1,54 @@
+function  [h,um,bm] = lbooster1_4sa(input,Bobs,wobs,p,y,c,post,A,given)
+
+B=1;
+alen=size(A,2);
+alpha0   = input(1:alen);
+sig      = input(alen +1);
+alpha1   = input(alen +2);
+theta1   = input(alen +3);
+theta2   = input(alen +4);
+theta3   = input(alen +5);
+siga      = input(alen +6);
+
+
+% alpha0   = given(1:alen);
+% sig      = given(alen +1);
+% alpha1   = given(alen +2);
+% theta1   = given(alen +3);
+% theta2   = given(alen +4);
+% theta3   = given(alen +5);
+
+a0 = A*alpha0;
+
+v1 =  up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y) ;
+v2 =  up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c) ;
+
+Bprob1=normcdf(v1-v2,0,siga);
+Bprob2=1-normcdf(v1-v2,0,siga);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) ),0,sig );
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  ),0,sig );
+
+h = -1.*sum( (Bobs==0).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==1).*(log(Bprob2) + log(w2)) );
+
+
+if nargout>1
+    rng(3);
+    n = size(A,1);
+    e  = evrnd(0,1,n,2);
+%     ep = normrnd(0,sig,n,2);
+   upn1= up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y);
+   upn2= up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c);
+
+    v1s = up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)./SC  + e(:,1);
[…]

### 2020-07-16 phil_matlab_pressure/lbooster1_5c.m

@@ -1,0 +1,50 @@
+function  [h,um,bm] = lbooster1_5c(input,Bobs,wobs,p,y,c,post,A,given)
+
+B=1;
+alen=size(A,2);
+alpha0   = input(1:alen);
+sig      = input(alen +1);
+alpha1   = input(alen +2);
+theta1   = input(alen +3);
+theta2   = input(alen +4);
+theta3   = input(alen +5);
+siga     = input(alen +6);
+
+% alpha0   = given(1:alen);
+% sig      = given(alen +1);
+% alpha1   = given(alen +2);
+% theta1   = given(alen +3);
+% theta2   = given(alen +4);
+% theta3   = given(alen +5);
+
+a0 = A*alpha0;
+
+v1 =  up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y) ;
+v2 =  up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c) ;
+
+Bprob1=normcdf(v1-v2,0,siga);
+Bprob2=1-normcdf(v1-v2,0,siga);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) ),0,sig );
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  ),0,sig );
+
+h = -1.*sum( (Bobs==0).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==1).*(log(Bprob2) + log(w2)) );
+
+if nargout>1
+    rng(3);
+    n = size(A,1);
+    e  = normrnd(0,siga,n,2);
+%     ep = normrnd(0,sig,n,2);
+
+    v1s = up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)  + e(:,1);
+    v2s = up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c) + e(:,2);
+%     w1s = wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) + ep(:,1);
[…]

### 2020-07-16 phil_matlab_pressure/lbooster1_6.m

@@ -1,0 +1,53 @@
+function  [h,um,bm] = lbooster1_6(input,Bobs,wobs,p,y,c,post,A,T,given)
+
+B=1;
+alen=size(A,2);
+% tlen=size(T,2);
+alpha0   = input(1:alen);
+sig      = input(alen +1);
+alpha1   = input(alen +2);
+theta1   = input(alen +3);
+theta3   = input(alen +4);
+siga     = input(alen +5);
+t2   = input(alen +6:end);
+
+% alpha0   = given(1:alen);
+% sig      = given(alen +1);
+% alpha1   = given(alen +2);
+% theta1   = given(alen +3);
+% theta2   = given(alen +4);
+% theta3   = given(alen +5);
+
+a0 = A*alpha0;
+theta2=T*t2;
+
+v1 =  up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y) ;
+v2 =  up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c) ;
+
+Bprob1=normcdf(v1-v2,0,siga);
+Bprob2=1-normcdf(v1-v2,0,siga);
+
+w1 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) ),0,sig );
+w2 = normpdf( (wobs - wp1( a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3)  ),0,sig );
+
+h = -1.*sum( (Bobs==0).*(log(Bprob1) + log(w1)) ...
+           + (Bobs==1).*(log(Bprob2) + log(w2)) );
+
+
+if nargout>1
+    rng(3);
+    n = size(A,1);
+    e  = normrnd(0,siga,n,2);
+%     ep = normrnd(0,sig,n,2);
+
+    v1s = up1(  a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3,y)  + e(:,1);
+    v2s = up1(  a0,alpha1,p,theta1.*B + post.*theta2  + post.*(B).*theta3,y - c) + e(:,2);
+%     w1s = wp1( a0,alpha1,p,theta1.*(1-B) + post.*theta2  + post.*(1-B).*theta3) + ep(:,1);
[…]

### 2020-07-16 phil_matlab_pressure/lbooster_gh4.m

@@ -1,0 +1,187 @@
+function  [VAL,G,H] = lbooster_gh4(input,A,T,wobs,p_i,p_r,given)
+
+
+sa = size(A,2);
+st = size(T,2);
+a0       = input(1:sa);
+t0       = input(sa+1:sa+st);
+alpha1   = input(sa+st+1);
+sig      = input(sa+st+2);
+
+% alpha0 = A*a0;
+
+% es=zeros(1,size(A,2));
+% yb=y-c;
+% theta1b=theta1;
+
+nc = sqrt(pi*2);
+np = ones(size(wobs,1),1);
+es = zeros(size(wobs,1),1);
+
+
+% VAL
+G = zeros(1,size(input,1));
+H = zeros(size(input,1),size(input,1));
+
+% G=(1:10)
+% G([2 4 7:end])=[0 1 1 1 1 1]
+
+for i=1:size(A,2)
+    for k=1:size(A,2)
+        if k>i
+%             k=2
+%             i=1
+            A_1 = A(:,i);
+            A_2 = A(:,k);
+            alpha0_1 = a0(i);
+            alpha0_2 = a0(k);
+            AC  = A*a0 - A_1.*alpha0_1 - A_2.*alpha0_2;
+            
+            T_1 = 0;
+            T_2 = 0;
+            theta0_1 = 0;
+            theta0_2 = 0;
+            TC  = T*t0 ;
+            
+            [valw,gw,hw] = gh4(AC,A_1,A_2,TC,T_1,T_2,alpha1,alpha0_1,alpha0_2,nc,np,p_i,p_r,sig,theta0_1,theta0_2,wobs);
+           
+            if i==1
+                VAL= sum(valw );
+            end
+            gwt = sum(gw );
+            G([i k (sa+st+1):end]) = [gwt(1:2) gwt(end-(size(input,1)-(sa+st+1)):end)] ;
+            h = sum(hw);
+            h = reshape(h,sqrt(size(h,2)),sqrt(size(h,2)));
+            
+            H(i,i) = h(1,1);
+            H(k,k) = h(2,2);
+            H(i,k) = h(1,2);
+            H(i,(sa+st+1):end)=h(1,end-(size(input,1)-(sa+st+1)):end);
+            H(k,(sa+st+1):end)=h(2,end-(size(input,1)-(sa+st+1)):end);
[…]

### 2020-07-16 phil_matlab_pressure/ng_normalpdf.m

@@ -1,0 +1,22 @@
+function [gx,dg,dg2] = ng_normalpdf(x,wobs,sig,pdf)
+
+pii=3.14;
+
+if pdf==1
+    gx   = normpdf(wobs-x,0,sig);
+    dg   =  ((wobs-x)./(sqrt(2.*pii).*sig.^3)) ...
+        .*exp( (-(wobs-x).^2)./(2.*sig.^2)  ) ;
+    
+    dg2  =  ( ((wobs-x).^2)./(sqrt(2.*pii).*sig.^5)) ...
+        .*exp( (-(wobs-x).^2)./(2.*sig.^2)  )  - ... 
+        (1./(sqrt(2.*pii).*sig.^3)) ...
+        .*exp( (-(wobs-x).^2)./(2.*sig.^2)  ) ;
+else
+    
+    gx   = normcdf(wobs-x,0,sig);
+    dg   = normpdf(wobs-x,0,sig);
+    
+    dg2  = ((wobs-x)./(sqrt(2.*pii).*sig.^3)) ...
+        .*exp( (-(wobs-x).^2)./(2.*sig.^2)  ) ; % is it wobs negative?!
+end
+

### 2020-07-16 phil_matlab_pressure/sym_booster.m

@@ -1,0 +1,123 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p pi pr a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1 theta0 theta1
+assume(y>0)
+assume(p1>0)
+assume(pi>0)
+assume(pr>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=10;
+
+%%% ALONE %%%
+
+% p = pi+pr*w;
+p = pi ;
+
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*S*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+expand(wa)
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
+
+expand(ua)
+
+u_pre  = eval(subs(ua,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,0,20,1000]))
+u_post = eval(subs(ua,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,3,20,1000]))
+
+wp = subs(wa,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,0,20,1000]) - 3;
+xp = 1000 - 20*wp;
+
+u_alt = subs(u,[x,w,alpha0,alpha1,theta1,S],[xp,wp,30,.5,1,0])
+
+wa
+
+expand(wa)
+
+alpha0h = alpha0/(2*alpha1*pr+1)
+alpha1h = alpha1/(2*alpha1*pr+1)
+thetah  = theta1/(2*alpha1*pr+1)
+
+% [a0s,a1s,ts]=solve([alpha0h-a0h,alpha1h-a1h,thetah-th],[alpha0,alpha1,theta1])
+
+simplify(ua)
+
+expand(ua)
+
+diff(ua,S)
+
[…]

### 2020-07-16 phil_matlab_pressure/sym_booster6nl.m

@@ -1,0 +1,182 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p pi pr a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1
+syms alpha0_1 alpha0_2 alpha0_3 alpha0_4 alpha0_5 alpha0_6 alpha0_7
+syms A_1 A_2 A_3 A_4 A_5 A_6 A_7
+
+syms theta1
+syms theta1_1 theta1_2 theta1_3
+syms T_1 T_2 T_3
+
+syms wobs
+syms Bobs
+syms sig
+syms SC
+
+syms c
+
+
+
+assume(sig>0)
+assume(y>0)
+assume(p1>0)
+assume(pi>0)
+assume(pr>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=1;
+
+%%% ALONE %%%
+
+p = pi+pr*w;
+% p = pi ;
+
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+expand(wa)
+ua = simplify(subs(u,[w,x],[wa,xa]));
+expand(ua)
+
+matlabFunction(simplify(wa,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','wpnl.m')
+matlabFunction(simplify(ua,'IgnoreAnalyticConstraints',true,'Steps',steps),'File','upnl.m')
+
+
+
+
+% u_pre  = eval(subs(ua,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,0,20,1000]))
+% u_post = eval(subs(ua,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,3,20,1000]))
+
[…]

### 2020-07-16 phil_matlab_pressure/sym_booster_gh10.m

@@ -1,0 +1,122 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p p_i p_r a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1
+syms alpha0_1 alpha0_2 alpha0_3 alpha0_4 alpha0_5 alpha0_6 alpha0_7
+syms A_1 A_2 A_3 A_4 A_5 A_6 A_7 A  AC
+
+syms theta1   theta1b yb
+syms theta0_1 theta0_2 theta0_3
+syms T_1 T_2 T_3  T TC  T_1b T_2b T_3b  Tb TCb
+syms T_1n T_2n TCn
+
+syms wobs
+syms bobs
+syms sig siga
+syms SC
+
+syms c   nc   np
+syms EV  AV AVB  TV TVB DV UV  A1UV A2UV OV KV  AVN TVN
+
+syms JJ1 JJ2 JJ3 JJ4 JJ5 JJ6 JJ7 JJ8 JJ9 JJ10 JJ11
+
+assume(siga>0)
+assume(sig>0)
+assume(y>0)
+assume(p1>0)
+assume(p_i>0)
+assume(p_r>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=1;
+
+%%% ALONE %%%
+
+%  p = p_i+p_r*w;
+ p = p_i ;
+alpha0 = alpha0_1*A_1+alpha0_2*A_2+AC;
+theta1 = theta0_1*T_1+theta0_2*T_2+TC;
+ 
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
+uab = subs(ua,[T_1,T_2,TC,y],[T_1b,T_2b,TCb,y - c]);
[…]

### 2020-07-16 phil_matlab_pressure/sym_booster_gh7.m

@@ -1,0 +1,119 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p p_i p_r a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1
+syms alpha0_1 alpha0_2 alpha0_3 alpha0_4 alpha0_5 alpha0_6 alpha0_7
+syms A_1 A_2 A_3 A_4 A_5 A_6 A_7 A  AC
+
+syms theta1   theta1b yb
+syms theta0_1 theta0_2 theta0_3
+syms T_1 T_2 T_3  T TC  T_1b T_2b T_3b  Tb TCb
+
+syms wobs
+syms bobs
+syms sig siga
+syms SC
+
+syms c   nc   np
+syms EV  AV AVB  TV TVB DV UV  A1UV A2UV OV KV
+
+syms JJ1 JJ2 JJ3 JJ4 JJ5 JJ6 JJ7 JJ8 JJ9 JJ10 JJ11
+
+assume(siga>0)
+assume(sig>0)
+assume(y>0)
+assume(p1>0)
+assume(p_i>0)
+assume(p_r>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=1;
+
+%%% ALONE %%%
+
+%  p = p_i+p_r*w;
+ p = p_i ;
+alpha0 = alpha0_1*A_1+alpha0_2*A_2+AC;
+theta1 = theta0_1*T_1+theta0_2*T_2+TC;
+ 
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
+uab = subs(ua,[T_1,T_2,TC,y],[T_1b,T_2b,TCb,yb]);
+
+ud = simplify(ua-uab)
+
[…]

### 2020-07-16 phil_matlab_pressure/sym_booster_gh9.m

@@ -1,0 +1,159 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p p_i p_r a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1
+syms alpha0_1 alpha0_2 alpha0_3 alpha0_4 alpha0_5 alpha0_6 alpha0_7
+syms A_1 A_2 A_3 A_4 A_5 A_6 A_7 A  AC
+
+syms theta1   theta1b yb
+syms theta0_1 theta0_2 theta0_3
+syms T_1 T_2 T_3  T TC  T_1b T_2b T_3b  Tb TCb
+syms T_1n T_2n TCn
+
+syms wobs
+syms bobs
+syms sig siga
+syms SC
+
+syms c   nc   np
+syms EV  AV AVB  TV TVB DV UV  A1UV A2UV OV KV  AVN TVN
+
+syms JJ1 JJ2 JJ3 JJ4 JJ5 JJ6 JJ7 JJ8 JJ9 JJ10 JJ11
+
+assume(siga>0)
+assume(sig>0)
+assume(y>0)
+assume(p1>0)
+assume(p_i>0)
+assume(p_r>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=1;
+
+%%% ALONE %%%
+
+%  p = p_i+p_r*w;
+ p = p_i ;
+alpha0 = alpha0_1*A_1+alpha0_2*A_2+AC;
+theta1 = theta0_1*T_1+theta0_2*T_2+TC;
+ 
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
[…]

### 2020-07-16 phil_matlab_pressure/sym_booster_gh9works_linearity.m

@@ -1,0 +1,204 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p p_i p_r a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1
+syms alpha0_1 alpha0_2 alpha0_3 alpha0_4 alpha0_5 alpha0_6 alpha0_7
+syms A_1 A_2 A_3 A_4 A_5 A_6 A_7 A  AC
+
+syms theta1   theta1b yb
+syms theta0_1 theta0_2 theta0_3
+syms T_1 T_2 T_3  T TC  T_1b T_2b T_3b  Tb TCb
+syms T_1n T_2n TCn
+
+syms wobs
+syms bobs
+syms sig siga
+syms SC
+
+syms c   nc   np
+syms EV  AV AVB  TV TVB DV UV  A1UV A2UV OV KV  AVN TVN
+
+syms JJ1 JJ2 JJ3 JJ4 JJ5 JJ6 JJ7 JJ8 JJ9 JJ10 JJ11
+
+assume(siga>0)
+assume(sig>0)
+assume(y>0)
+assume(p1>0)
+assume(p_i>0)
+assume(p_r>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=1;
+
+%%% ALONE %%%
+
+%  p = p_i+p_r*w;
+ p = p_i ;
+% alpha0 = alpha0_1*A_1+alpha0_2*A_2+AC;
+% theta1 = theta0_1*T_1+theta0_2*T_2+TC;
+ 
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
+
+expand(ua)
[…]

### 2020-07-16 phil_matlab_pressure/sym_booster_gh9works_linearity_1.m

@@ -1,0 +1,205 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p p_i p_r a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1
+syms alpha0_1 alpha0_2 alpha0_3 alpha0_4 alpha0_5 alpha0_6 alpha0_7
+syms A_1 A_2 A_3 A_4 A_5 A_6 A_7 A  AC
+
+syms theta1   theta1b yb
+syms theta0_1 theta0_2 theta0_3
+syms T_1 T_2 T_3  T TC  T_1b T_2b T_3b  Tb TCb
+syms T_1n T_2n TCn
+
+syms wobs
+syms bobs
+syms sig siga
+syms SC
+
+syms c   nc   np
+syms EV  AV AVB  TV TVB DV UV  A1UV A2UV OV KV  AVN TVN gamma
+
+syms JJ1 JJ2 JJ3 JJ4 JJ5 JJ6 JJ7 JJ8 JJ9 JJ10 JJ11 t f 
+
+assume(siga>0)
+assume(sig>0)
+assume(y>0)
+assume(p1>0)
+assume(p_i>0)
+assume(p_r>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=1;
+
+%%% ALONE %%%
+
+%  p = p_i+p_r*w;
+ p = p_i ;
+% alpha0 = alpha0_1*A_1+alpha0_2*A_2+AC;
+% theta1 = theta0_1*T_1+theta0_2*T_2+TC;
+ 
+BC = ( y -   (p*f*t+x) ) 
+
+u = x + (1/alpha1).*(f*t - .5*( f*t - alpha0 )^2) - gamma.*t
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dt = simplify(diff(lan,t))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[ta,xa,la]  =  solve([dt,dx,dl],[t,x,l]);
+
+ua = simplify(subs(u,[t,x],[ta,xa]));
+
[…]

### 2020-07-16 phil_matlab_pressure/sym_storage.m

@@ -1,0 +1,118 @@
+
+
+
+clear;
+% cd_dir ='/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_matlab_new/';
+
+syms y p pi pr a1 a2 a3 g g1 g2 g3 w x F l ws wbar1 wbar2 wbar3 es esq t1 t2 S a0h a1h th
+syms alpha0 alpha1 p1 theta0 theta1
+assume(y>0)
+assume(p1>0)
+assume(pi>0)
+assume(pr>0)
+assume(a1>0)
+assume(g1>0)
+assume(w>0)
+assume(x>0)
+assume(l>0)
+assume(t1>0)
+assume(t2>0)
+assume(S>0)
+
+steps=10;
+
+%%% ALONE %%%
+
+% p = pi+pr*w;
+p = pi ;
+
+BC = ( y -   (p*w+x) ) 
+
+u = x + (1/alpha1).*(theta1*S*w - .5*( w - alpha0 )^2)
+
+% u = x + alpha1*sqrt(w)
+lan  =  u  + l*BC
+
+dw = simplify(diff(lan,w))
+dx = diff(lan,x)
+dl = diff(lan,l)
+
+[wa,xa,la]  =  solve([dw,dx,dl],[w,x,l]);
+
+expand(wa)
+
+ua = simplify(subs(u,[w,x],[wa,xa]));
+
+expand(ua)
+
+u_pre  = eval(subs(ua,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,0,20,1000]))
+u_post = eval(subs(ua,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,3,20,1000]))
+
+wp = subs(wa,[alpha0,alpha1,theta1,S,pi,y],[30,.5,1,0,20,1000]) - 3;
+xp = 1000 - 20*wp;
+
+u_alt = subs(u,[x,w,alpha0,alpha1,theta1,S],[xp,wp,30,.5,1,0])
+
+wa
+
+expand(wa)
+
+alpha0h = alpha0/(2*alpha1*pr+1)
+alpha1h = alpha1/(2*alpha1*pr+1)
+thetah  = theta1/(2*alpha1*pr+1)
+
+% [a0s,a1s,ts]=solve([alpha0h-a0h,alpha1h-a1h,thetah-th],[alpha0,alpha1,theta1])
+
+
+
+simplify(ua)
+
+
+expand(ua)
+
+diff(ua,S)
+
+
[…]

### 2020-07-16 phil_matlab_pressure/wp.m

@@ -1,8 +1,8 @@
-function out1 = wp(S,alpha0,alpha1,p1,theta1)
+function out1 = wp(S,alpha0,alpha1,pi,theta1)
 %WP
-%    OUT1 = WP(S,ALPHA0,ALPHA1,P1,THETA1)
+%    OUT1 = WP(S,ALPHA0,ALPHA1,PI,THETA1)
 
 %    This function was generated by the Symbolic Math Toolbox version 8.5.
-%    01-Jun-2020 17:03:49
+%    18-Jun-2020 16:22:28
 
-out1 = alpha0+S.*theta1-alpha1.*p1;
+out1 = alpha0+S.*theta1-alpha1.*pi;

### 2020-07-29 phil_paper/paper_booster_pumps_wjv.tex
try full structural, doesn't work great unfort

@@
 \renewcommand{\arraystretch}{1.2}
+
+\newcommand{\regtext}{
+Standard errors are clustered at the small-area level (in parentheses).  The water service area is divided into 2,974 small-areas.
+\textsuperscript{c} p$<$0.10,\textsuperscript{b} p$<$0.05,\textsuperscript{a} p$<$0.01 \,\,
+}
 
@@
 
+\section{Data}
+
 Section: Data
@@
 
-Section: Descriptives and defending model and approach
+Consumption is measured according to average consumption for not-shared households!  What extra assumption is that!!!  NEED ROBUSTNESS!!!
+
+MEASURING AVERAGE PRICES
 
@@
 Large investments in booster pumps suggest that households strongly value water pressure.
-Before pipe replacement, 40\% of households invest in booster pumps that increase water pressure.
-Booster pumps are both expensive to purchase (PhP 6,000) and operate (benchmark with electricity costs).
+Booster pumps are both expensive to purchase and operate.
+In Manila, booster pumps range in price from 1,200 to 15,000 PhP, which represents a large expense given average monthly household incomes of \input{tables/median_inc}PhP.\footnote{Figures come from scraping results from the first page of searching ``booster pumps'' on the popular online marketplace in Manila, \url{https://www.lazada.com.ph/},  yielding 22 entries with horsepower listed.
+Median monthly household income is computed for Metro Manila using the 2015 Family Income and Expenditure Survey.}  The median booster pump uses a 0.75 horsepower engine, which generates monthly costs of around 405 PhP at prevailing energy prices.\footnote{A 1 horsepower engine uses around 0.786 Kw per hour.
+Table~\ref{table:descriptives} indicates that households use their booster pumps for 2.6 hrs per day, which implies around 78 hours per month.
+In 2012, tariffs for the electricity utility in Manila averaged around 8.8 PhP per KwH.}   Before pipe replacement, 40\% of households invest in booster pumps that increase water pressure.
 After pipe replacement, the share of households using booster pumps drops to 15\%.
@@
 Only 12\% of households use water filters both before and after pipe replacements.
-Averaging ([cost of filters]), filters are also much less expensive than booster pumps.
 Low filter usage may stem from the fact that less than half of households report drinking from the tap while over 70\% of households report purchasing filtered water from local water-refilling stations.
@@
 \midrule
-Piped Water Quality \\[.5em]
+Piped Water Service Quality \\[.5em]
 \hspace{1em}$\text{Water has strong pressure (6pm-12am)}^{\dagger}$ & \input{tables/yes_flow_6mid} \\
@@
 \\[-.5em]
-Private Water Quality Investments \\[.5em]
+Household Service Quality Investments \\[.5em]
 \hspace{1em}Has booster pump & \input{tables/booster} \\
@@
 Increases in water pressure from pipe replacements may lead households to increase their monthly water consumption.
-Rapid water flow allows households to complete a greater number of water-using activities (like cleaning and bathing) in the same amount of time.
+Rapid water flow allows households to complete a greater number of water-using activities like cleaning and bathing in the same amount of time.
 Greater water pressure may also allow households to engage in new activities that require minimum pressure levels such as showering.\footnote{By contrast, water quality improvements may have an ambiguous effect on water consumption.
@@
 
+\section{Model}
+
+A simple model of household water demand connects changes in water usage to changes in household welfare as a result of pipe replacements.
+In this model, households choose their monthly water usage as well as whether to use a booster pump to boost water pressure.
+
+Each month, household utility takes the following form
+\begin{align}
+\label{eq:utility}
+U\,=\,\frac{1}{\alpha} \, \Big[ \,  ( \theta_1 B \, +  \, \theta_2 R + \, \theta_3 B R ) \,  w  \, -\, \frac{1}{2}(w - \gamma + \epsilon)^2 \, \Big] \, + \, x
+\end{align}
+where $w$ is water consumption and $x$ represents a bundle of all other goods consumed by the household.
+Water service quality is captured by $( \theta_1 B \, +  \, \theta_2 R + \, \theta_3 B R )$ where $B$ equals 1 if the household uses a booster pump (and zero otherwise) and $R$ equals 1 after pipe replacement (and zero otherwise).
+The $\theta$ terms capture the household's preference for water service quality from booster pumps, pipe replacements, and the combination of the two.
+For example, $\theta_3<0$ implies that booster pumps and pipe replacements are substitutable in producing water service quality.
+Water service quality enters multiplicatively with water consumption, which nests the assumption that each unit of water consumption is affected equally by water service quality.
+$\alpha$ reflects price sensitivity, and $\gamma$ reflects the satiation amount of water usage.
+$\epsilon$ captures idiosyncratic monthly variation in satiation water usage such as changes in weather or in the number of household members using water.
+$\epsilon$ is assumed to follow a normal distribution with zero mean and standard deviation $\sigma_{\epsilon}$.
+This approach assumes that preferences for water are quasi-linear, which implies that water consumption does not depend on household income [ back this up with more evidence?
+].
+
+Households maximize utility subject to the following budget constraint
+\begin{align}
+\label{eq:bc}
+p\,w \,+\, x \, + (F + \upsilon) B \, = y 
+\end{align}
+where $p$ is the average price of water while the price of all other goods, $x$, is normalized to 1.
+This approach includes the simplifying assumption that households respond to a single, average water price $p$ despite facing marginal prices that increase with monthly consumption.
+This assumption is consistent with descriptive evidence that households appear unresponsive to marginal prices (cite appendix).
+$F$ is total cost of renting and using a booster pump each month.
+This approach assumes that Manila has a competitive market for renting/selling booster pumps.
+$\upsilon$ captures idiosyncratic monthly variation the booster pump cost such as changes in the electricity price or variation in installation costs.
+$\upsilon$ is assumed to follow a normal distribution that is assumed to be uncorrelated with $\epsilon$ and has zero mean and standard deviation $\sigma_{\upsilon}$.
+$y$ is monthly household income.
+
+% as well as other research on public utility price responsiveness (\cite{ito2014consumers}, and the water ito paper?).
+
+Maximizing household utility in equation $(\ref{eq:utility})$ subject to the budget constraint in equation $(\ref{eq:bc})$ for a given choice of booster pump usage, $B$, yields the following expression for monthly water demand
+\begin{align}
+w^{*} \, = \, \gamma \, - \, \alpha p +  \theta_1 B \, + \, \theta_2 R  \,+ \, \theta_3 B R \,  + \, \epsilon
+\end{align}
+Water demand depends linearly on the satiation preference, $\gamma$, as well as price, booster pump use, and pipe repairs.
+Given optimal water demand, $w^{*}$, households can then choose whether to use a booster pump by comparing expected utilities with and without booster pumps.
+Households use booster pumps when the following expression is greater than zero
+\begin{align}
+E\Big[ \,V_{B=1 - B=0}^{*}\,\Big]  = (\theta_1 + \theta_3 R) \Big(  \frac{\theta_1 + \theta_3 R}{2\alpha} + \frac{\gamma +  \theta_2 R}{\alpha} - p  \, \Big) \, - \, (F \, + \upsilon)
+\end{align}
+% Since $\epsilon$ is assumed to be  normal, it falls out of the equation
+When booster pumps increase service quality $\theta_1>0$, booster pump use is increasing in household's fixed water preference, $\gamma$, and decreasing in the water price, $p$.
+Booster pump use decreases following pipe replacements if $\theta_3$ is sufficiently negative.
+
+Given booster pump demand, the probability of observing a household choose to use a booster pump, $B^{*}$ can be expressed as follows
+\begin{align}
+Pr[B^{*}=1] \,\, = \,\, \Phi\Bigg( \, \frac{ (\theta_1 \theta_2 + \theta_1 \theta_3 + \theta_2 \theta_3) R + \frac{1}{2}(\theta_1^2 + \theta_3^2)  + \gamma (\theta_1 + \theta_3 R) \Big] - (\theta_1 + \theta_3 R) p \, - \, F }{\sigma_{\upsilon}} \, \Bigg)
+\end{align}
+where $\Phi(.)$ is the cumulative distribution function of the standard normal distribution.
+Conditional on booster pump use, the probabilities of observing households use a particular amount of water, $w^{obs}$, can be expressed as follows
+\begin{align}
+Pr[w^{*}=w^{obs} \,|\, B^{*}=1] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p +  \theta_1  + \, \theta_2 R  \,+ \, \theta_3 R )}{\sigma_\epsilon} \, \Bigg) \\
+Pr[w^{*}=w^{obs} \,|\, B^{*}=0] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p \, + \, \theta_2 R   )}{\sigma_\epsilon} \, \Bigg)
+\end{align}
+Combining these expressions, the log-likelihood of observing each pair of booster pump use and water use across households, $i$, is as follows
+\begin{align}
+\begin{split}
+LL = \sum_i & \mathbbm{1}\{ B^{obs}_i = 1 \} \,\Big[ \ln\big( Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=1] \big) \Big] \, + \\
+ & \mathbbm{1}\{ B^{obs}_i = 0 \} \,\Big[ \ln\big( 1- Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=0] \big) \Big] 
+ \end{split}
+\end{align}
+
+\section{Empirical Specification and Identification}
+
+% ($\gamma, \alpha, \sigma_{\epsilon}$) ($\theta_2$)  ($\theta_1, \theta_3$) ($\sigma_{\upsilon}$)
+The estimation recovers preferences for water, preferences for water service quality, as well as booster pump effectiveness and cost variability.
+
+Fixed preferences for water, $\gamma$, are allowed to vary according to six demographic characteristics: household size, number of employed household members, whether the head of household has high-skilled employment, whether the household is ever assigned a high water price, and whether the household ever receives pipe replacement, as well as indicators for calendar months.\footnote{Preferences do not depend on time because usage does not exhibit strong trends over time.}  Fixed preferences are identified primarily from average usage levels for each demographic group.
+Month indicators capture seasonality in water demand, and year indicators capture how water preferences evolve over time.
+Monthly variation in water usage identifies variation in fixed preferences, $\sigma_{\epsilon}$.
+
+Since calendar month indicators absorb all of the time-series variation in price schedules, price sensitivity, $\alpha$, is identified primarily through household changes in usage as the company switches households between regular and high average prices.
+This approach relies on the assumption that switching between prices is not correlated with other factors that may affect demand.
+For example, households may increase their water demand as they open a roadside food-stand and switch to the high price.
+Conversely, households that close their roadside food-stand may decrease their consumption at the same time as they are switched to the low price.
+Both cases suggest that this approach would underestimate household price sensitivities.
+
+Both cases would also likely predict strong pre-trends in usage for the years leading up to price changes.
+Figure~\ref{figure:usagepricechanges} plots usage pre-trends providing little evidence of salient trends before price changes.
+Appendix Table~\ref{table:usageregs} further finds that the correlation between price and household usage remains stable after controlling for household demographics, small-area fixed effects, or household fixed effects.
+This approach also assumes that price sensitivities identified for households that switch prices are representative of the full population of households.
+Table~\ref{table:pricechangestatistics} provides some support for this assumption by finding broadly similar demographics across households exposed to different prices.
+
+Preference for water service quality from pipe replacements, $\theta_2$, is identified by the change in usage observed before and after pipe replacements.
+Identification of $\theta_2$ requires assuming that this change in consumption can be entirely attributed to pipe replacements and not to changes in other factors that may affect household demand for water at the same time.
+One concern may be that pipe improvements are paired with other infrastructure investments that drive increases in local income, population, and water demand.
+Alternatively, the water company may strategically target pipe improvements to either boost areas with declining demand or accelerate areas with growing demand.
+Figure~\ref{figure:pipecons} traces a sharp break in average usage at the year of pipe replacement with little evidence of strong trends before or after replacement projects.
+These patterns are consistent with company reports that pipe replacements were not explicitly linked to other infrastructure projects and were instead planned primarily to minimize engineering costs.
+
+Preferences for booster pumps before pipe replacement, $\theta_1$, and after pipe replacement, $(\theta_1+\theta_3)$, are identified both from cross-sectional differences in usage for households with and without booster pumps as well as from changes in booster pump usage before and after pipe replacement projects.
+Identification requires assuming that booster pump use accounts for all of the average differences in usage between households with and without booster pumps after conditioning on households' observable characteristics and pipe replacement status.
+This assumption may not hold if households choose to use booster pumps to cope with unobserved variation in water service quality specific to their neighborhoods.
+To partially test this assumption, Appendix Table~\ref{table:boosterregs} finds that the positive correlation between water use and booster pump use remains stable even after controlling for calendar month fixed effects as well as small-area fixed effects, which may both capture local variation in water service quality.
+
+Identification of booster pump preferences also requires assuming that changes in booster pump use before and after pipe replacement projects are driven entirely by these projects and not by any other factors such as shifts in water preferences that may also be correlated with these projects.
+Appendix Table~\ref{table:boosterregs} finds that the negative correlation between booster pump use and pipe replacement projects remains stable after accounting for household demographics and small-area fixed effects.
+
+This approach also assumes that booster pumps do not impose substantial negative externalities on local water service quality.
+A recent engineering literature has raised the possibility that booster pumps interfere with water flow in pipe mainlines, reducing pressure along the entire pipe (\cite{taylor2014reducing}).
+However, this problem may not be as salient in the context of Manila.
+The water company has not raised booster pumps as a policy problem in any of their internal documents.\footnote{Booster pumps are sometimes mentioned in water company investigations of consumer complaints as an explanation for household water pressure and never as problem to be addressed.}  Moreover, externalities would predict large water usage gaps between those with and without booster pumps in the same neighborhood.
+By contrast, Table~\ref{table:usageregs} finds a similar association of booster pump use and water usage with and without small-area fixed effects.
+% Taken together, the empirical evidence is supportive of the relatively strong assumptions necessary to identify booster pump preferences.
+
+While fixed monthly costs of booster pumps, $F$, are calibrated to equal the expected monthly cost of operating a booster pump, the estimation strategy recovers the distribution of these costs, $\sigma_{\upsilon}$, that best matches the observed shares of households using booster pumps.
+Identification of $\sigma_{\upsilon}$ requires the assumption that cost variation, $\upsilon$, is uncorrelated with taste variation, $\epsilon$.
+This assumption implies that after accounting for observed demographic and other factors, differences in booster pump use are entirely driven by unobserved costs rather than unobserved preferences.
+
+\section{Results}
+
+\begin{table}[h!] 
+\centering
+\caption{Structural Estimates}\label{table:estimates}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{c}@{}}
+\toprule
+  &  (1)   \\
+\midrule
+Fixed Preferences & \\
+\hspace{1em}Intercept & \input{tables/est_gamma_1_1} \\
+ 						& (\input{tables/est_gamma_sd_1_1}) \\
+\hspace{1em}Household Size & \input{tables/est_gamma_2_1} \\
+ 							& (\input{tables/est_gamma_sd_2_1}) \\
+\hspace{1em}Employed Household Members & \input{tables/est_gamma_3_1} \\
+ 						& (\input{tables/est_gamma_sd_3_1}) \\
+\hspace{1em}High Skill Employment & \input{tables/est_gamma_4_1} \\
+ 						& (\input{tables/est_gamma_sd_4_1}) \\
+\hspace{1em}Ever High Price & \input{tables/est_gamma_5_1} \\
+ 						& (\input{tables/est_gamma_sd_5_1}) \\
+\hspace{1em}Pipe Replacement Area & \input{tables/est_gamma_6_1} \\
+ 						& (\input{tables/est_gamma_sd_6_1}) \\[.5em]
+Price Sensitivity & \input{tables/est_alpha_1} \\
+ 						& (\input{tables/est_alpha_sd_1}) \\[.5em]
+Service Quality Preferences & \\
+\hspace{1em}Post Replacement & \input{tables/est_theta_1_1} \\
+ 						& (\input{tables/est_theta_sd_1_1}) \\
+\hspace{1em}Booster Use & \input{tables/est_theta_2_1} \\
+ 							& (\input{tables/est_theta_sd_2_1}) \\
+\hspace{1em}Post Replacement $\times$ Booster Use & \input{tables/est_theta_3_1} \\
+ 						& (\input{tables/est_theta_sd_3_1}) \\[.5em]
+Usage Variability & \input{tables/est_sig_ep_1} \\
+ 						& (\input{tables/est_sig_ep_sd_1}) \\[.5em]
+Booster Cost Variability & \input{tables/est_sig_up_1} \\
+ 						& (\input{tables/est_sig_up_sd_1}) \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item This table predicts usage per household with pipe replacement, booster pump use, and price with different fixed effects.   \regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+Need to fix the weighting of the estimates!!!!!!!!
+
+Section Estimation:
+	- show what happens when boosters are turned off
+
+Section Welfare:
+	- Welfare benefits with 10 yr 5\% loans (assume discount rates) or 50 yr 5\% loan?
+	- Welfare benefits with cash
+	- Are households willing to pay for pipe improvements?
+
+Robustness:
+	- Use nearest pipe replacement definition (selection into meter identification)
+
+% - Discusses use of booster pumps in Clean Water Act 2004:  https://www.manilatimes.net/2018/11/04/legal-advice/dearpao/use-of-booster-pumps/461829/  http://r12.emb.gov.ph/ra-9275-the-philippine-clean-water-act/
+% - https://idl-bnc-idrc.dspacedirect.org/bitstream/handle/10625/14878/108376.pdf?sequence=5
+% - illegal booster pumps :  Consequence of El Niño 1997-98 on Manila water resources: new perspectives in water shortage management
+% - seizing booster pumps : https://timesofindia.indiatimes.com/city/navi-mumbai/booster-pumps-used-by-some-socs-leading-to-water-crunch/articleshow/68856763.cms , https://timesofindia.indiatimes.com/city/nagpur/215-booster-pumps-seized/articleshow/69804589.cms
+
  % If households were sensitive to price increases at specific consumption levels, then households would be expected to frequently consume just below these levels.
@@
 
-Section Model:
-	- What are the key model choices?
-		- Satiation in water consumption
-		- Linear term in quality
-			- need to include expectation?
-		- Booster error independence ! (keep assumption!) and sorting
-		- Booster externality assumption
+\section{Appendix}
 
-Section Estimation:
-	- show what happens when boosters are turned off
+\begin{table}[h!] 
+\centering
+\caption{Usage per Household Regression Estimates}\label{table:usageregs}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{cccc}@{}}
+\toprule
+  & (1) & (2) & (3) & (4) \\
+\midrule
+\input{tables/cv_reg}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item This table predicts usage per household with pipe replacement, booster pump use, and price with different fixed effects.   \regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
 
-Section Welfare:
-	- Welfare benefits with 10 yr 5\% loans (assume discount rates) or 50 yr 5\% loan?
-	- Welfare benefits with cash
-	- Are households willing to pay for pipe improvements?
-
-Robustness:
-	- Use nearest pipe replacement definition (selection into meter identification)
-
-% - Discusses use of booster pumps in Clean Water Act 2004:  https://www.manilatimes.net/2018/11/04/legal-advice/dearpao/use-of-booster-pumps/461829/  http://r12.emb.gov.ph/ra-9275-the-philippine-clean-water-act/
-% - https://idl-bnc-idrc.dspacedirect.org/bitstream/handle/10625/14878/108376.pdf?sequence=5
-% - illegal booster pumps :  Consequence of El Niño 1997-98 on Manila water resources: new perspectives in water shortage management
-% - seizing booster pumps : https://timesofindia.indiatimes.com/city/navi-mumbai/booster-pumps-used-by-some-socs-leading-to-water-crunch/articleshow/68856763.cms , https://timesofindia.indiatimes.com/city/nagpur/215-booster-pumps-seized/articleshow/69804589.cms
-
-\section{Appendix}
+\begin{table}[h!] 
+\centering
+\caption{Booster Pump Use Regression Estimates}\label{table:boosterregs}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{ccc}@{}}
+\toprule
+  & (1) & (2) & (3)  \\
+\midrule
+\input{tables/B_reg}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item This table predicts household booster pump use with pipe replacement including demographic controls and small-area fixed effects.   \regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
 

### 2020-07-29 phil_matlab_pressure/booster_gh9_1p.m

@@ -1,0 +1,156 @@
+
+
+
+clear
+
+% to do:
+% (1) identify c? (understand identification in general) [ NO ASSUME IT! ]
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?   [ ESTIMATED! ]
+% (3) get the right solutions?   maybe dig deeper here...
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period! ! 
+% (5) run counterfactuals?? COMPARE welfare with and without   [ yes! ]
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+% 1 HP engine uses 0.786 Kw/Hour , meaning a .5 HP engine uses .786/2=.3930
+% price .2 USD * 44 PhP/USD = 8.8 PhP per KwH
+% 30days*2.6hrs*8.8 per KwH * .393 Kwh = 269.8
+% btw .25 and 1 hp engines used in Manila
+%  .5*270/2 + .5*270*2 = 338 PhP
+     
+data=1;
+if data==1
+      cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample1_2.csv');
+      
+       cs = cs(1:100000,:)  ;
+      
+        wobs    = cs(:,1);
+        bobs    = cs(:,2);
+        post    = cs(:,3);
+        p_i     = cs(:,4);
+        year    = cs(:,5);
+        cmax    = cs(:,6);
+        cmin    = cs(:,7);
+        hhsize  = cs(:,8);
+        hhemp   = cs(:,9); 
+        good_job= cs(:,10);
+        sho     = cs(:,11);
+        treated = cs(:,12);
+
+      
+%      alpha0 = [ 0;               0;     0;   0;      0;    0   ];
[…]

### 2020-07-29 phil_matlab_pressure/booster_gh9_pa1_iterate.m

@@ -1,0 +1,188 @@
+
+
+
+clear
+
+% to do:
+% (1) identify c? (understand identification in general) [ NO ASSUME IT! ]
+    % * FROM FUNCTIONAL FORM see whether the estimates are reasonable
+% (2) robust to SC?   [ ESTIMATED! ]
+% (3) get the right solutions?   maybe dig deeper here...
+% (4) DO EXPECTED UTILITY! DO NON-LINEAR PRICING! (think about rental of booster pump)
+     % no expected utility!  rental market each period! ! 
+% (5) run counterfactuals?? COMPARE welfare with and without   [ yes! ]
+% order:  do counterfactuals with current model
+     %    then test assumptions of model
+            % model assumes that large users are more likeily
+     %    then think about adding proper utility and price 
+% 1 HP engine uses 0.786 Kw/Hour , meaning a .5 HP engine uses .786/2=.3930
+% price .2 USD * 44 PhP/USD = 8.8 PhP per KwH
+% 30days*2.6hrs*8.8 per KwH * .393 Kwh = 269.8
+% btw .25 and 1 hp engines used in Manila
+%  .5*270/2 + .5*270*2 = 338 PhP
+
+% .786*.75engine = .5895 kwH * 8.8 PhP * 30 days * 2.6 hrs = 405 PhP
+
+     
+data=1;
+if data==1
+    
+    for r=1:1
+          
+        cs = readmatrix('/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/booster_sample_date_pa1.csv');
+
+         if r==1
+            cs = cs(1:50000,:)  ;
+         end
+         if r==2
+            cs = cs(1:10000,:)  ;  
+         end
+            wobs    = cs(:,1);
+            bobs    = cs(:,2);
+            post    = cs(:,3);
+            p_i     = cs(:,4);
+            date    = cs(:,5);
+            cmax    = cs(:,6);
+            cch     = cs(:,7);
+            hhsize  = cs(:,8);
+            hhemp   = cs(:,9); 
+            good_job= cs(:,10);
[…]

### 2020-07-29 phil_matlab_pressure/print_counter.m

@@ -1,0 +1,32 @@
+function [h]=print_counter(cd_dir,out,A,Tb,Tn,Pi,y,c  )
+
+
+% [ut,bobs,wobs] = counter_gh9( out ,A,Tb,Tn,p_i,y,c);
+%     mean(ut(post==1)) - mean(ut(post==0))
+
+Tb     = [ones(size(wobs,1),Thet)  zeros(size(wobs,1),Thet)   zeros(size(wobs,1),Thet)  ]; % 2.5s, 60s
+Tn     = Tb.*[zeros(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  zeros(size(wobs,1),Thet) ];
+[utpre,bobspre,wobspre] = counter_gh9( out ,A,Tb,Tn,p_i,y,c);
+
+Tb     = [ones(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  ]; % 2.5s, 60s
+Tn     = Tb.*[zeros(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  zeros(size(wobs,1),Thet) ];
+[utpost,bobspost,wobspost] = counter_gh9( out ,A,Tb,Tn,p_i,y,c);
+
+mean(utpost(post==1)-utpre(post==1))
+mean(bobspost(post==1)-bobspre(post==1))
+mean(wobspost(post==1)-wobspre(post==1))
+
+
+%%% NO booster!? welfare effects are bigger!! (by 20 PhP) %%%
+Tb     = [zeros(size(wobs,1),Thet)  zeros(size(wobs,1),Thet)   zeros(size(wobs,1),Thet)  ]; % 2.5s, 60s
+Tn     = Tb.*[zeros(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  zeros(size(wobs,1),Thet) ];
+[utpre,bobspre,wobspre] = counter_gh9( out ,A,Tb,Tn,p_i,y,c);
+
+Tb     = [zeros(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  zeros(size(wobs,1),Thet)  ]; % 2.5s, 60s
+Tn     = Tb.*[zeros(size(wobs,1),Thet)  ones(size(wobs,1),Thet)  zeros(size(wobs,1),Thet) ];
+[utpost,bobspost,wobspost] = counter_gh9( out ,A,Tb,Tn,p_i,y,c);
+
+
[…]

### 2020-08-07 phil_paper/paper_booster_pumps_wjv.tex
derivative approach which is nice!

@@
 Booster pumps are both expensive to purchase and operate.
-In Manila, booster pumps range in price from 1,200 to 15,000 PhP, which represents a large expense given average monthly household incomes of \input{tables/median_inc}PhP.\footnote{Figures come from scraping results from the first page of searching ``booster pumps'' on the popular online marketplace in Manila, \url{https://www.lazada.com.ph/},  yielding 22 entries with horsepower listed.
-Median monthly household income is computed for Metro Manila using the 2015 Family Income and Expenditure Survey.}  The median booster pump uses a 0.75 horsepower engine, which generates monthly costs of around 405 PhP at prevailing energy prices.\footnote{A 1 horsepower engine uses around 0.786 Kw per hour.
+In Manila, booster pumps range in price from 1,200 to 15,000 PhP, which represents a large expense given average monthly household incomes of \input{tables/median_inc}PhP.\footnote{Figures come from scraping results from the first page of searching ``booster pumps'' on the popular online marketplace in Manila, \url{https://www.lazada.com.ph/},  yielding 24 entries with horsepower listed.
+Average monthly household income is computed for Metro Manila using the 2015 Family Income and Expenditure Survey.}  The average booster pump uses a 0.9 horsepower engine, which generates monthly costs of around 486 PhP at prevailing energy prices.\footnote{A 1 horsepower engine uses around 0.786 Kw per hour.
 Table~\ref{table:descriptives} indicates that households use their booster pumps for 2.6 hrs per day, which implies around 78 hours per month.
@@
 This finding is consistent with booster pumps providing an important substitute to pressure from new water pipes.
-
+% = .9*.786*78*8.8
+% \footnote{A 1 horsepower engine uses around 0.786 Kw per hour.
+Table~\ref{table:descriptives} indicates that households use their booster pumps for 2.6 hrs per day, which implies around 78 hours per month.
+In 2012, tariffs for the electricity utility in Manila averaged around 8.8 PhP per KwH.}
 Small investments in water filters combined with frequent purchases of filtered water both before and as well as after pipe replacement indicate that households may not derive large benefits from improvements in piped water quality.
@@
 \hspace{1em}Lives in single house& \input{tables/single} \\
-\hspace{1em}Other households sharing tap& \input{tables/SHO} \\
+\hspace{1em}Number of other households sharing tap& \input{tables/SHO} \\
 \\[-.5em]
@@
 \label{eq:utility}
-U\,=\,\frac{1}{\alpha} \, \Big[ \,  ( \theta_1 B \, +  \, \theta_2 R + \, \theta_3 B R ) \,  w  \, -\, \frac{1}{2}(w - \gamma + \epsilon)^2 \, \Big] \, + \, x
+U\,=\,\frac{1}{\alpha} \, \Big[ \,  Q(B,R) \,  w  \, -\, \frac{1}{2}(w - \gamma + \epsilon)^2 \, \Big] \, + \, x 
 \end{align}
 where $w$ is water consumption and $x$ represents a bundle of all other goods consumed by the household.
-Water service quality is captured by $( \theta_1 B \, +  \, \theta_2 R + \, \theta_3 B R )$ where $B$ equals 1 if the household uses a booster pump (and zero otherwise) and $R$ equals 1 after pipe replacement (and zero otherwise).
-The $\theta$ terms capture the household's preference for water service quality from booster pumps, pipe replacements, and the combination of the two.
-For example, $\theta_3<0$ implies that booster pumps and pipe replacements are substitutable in producing water service quality.
-Water service quality enters multiplicatively with water consumption, which nests the assumption that each unit of water consumption is affected equally by water service quality.
+Water service quality given by $Q(B,R)$ depends on booster pump use where $B$ equals 1 if the household chooses to use a booster pump (and zero otherwise) and as well as pipe replacements where $R$ equals 1 after pipe replacement (and zero otherwise).
+Water service quality enters multiplicatively with water consumption, which nests the assumption that each unit of water consumption is affected equally and positively by water service quality.
+This assumption also excludes the possibility that improved water service quality affects household utility in ways that are not directly proportional to household water consumption such as by increasing housing values.
+In this case, the approach would underestimate the welfare benefits of improved service quality.
 $\alpha$ reflects price sensitivity, and $\gamma$ reflects the satiation amount of water usage.
-$\epsilon$ captures idiosyncratic monthly variation in satiation water usage such as changes in weather or in the number of household members using water.
-$\epsilon$ is assumed to follow a normal distribution with zero mean and standard deviation $\sigma_{\epsilon}$.
 This approach assumes that preferences for water are quasi-linear, which implies that water consumption does not depend on household income [ back this up with more evidence?
 ].
+
+% $\epsilon$ captures idiosyncratic monthly variation in satiation water usage such as changes in weather or in the number of household members using water.
+$\epsilon$ is assumed to follow a normal distribution with zero mean and standard deviation $\sigma_{\epsilon}$.
+% The $\theta$ terms capture the household's preference for water service quality from booster pumps, pipe replacements, and the combination of the two.  
+% For example, $\theta_3<0$ implies that booster pumps and pipe replacements are substitutable in producing water service quality.
 
@@
 \label{eq:bc}
-p\,w \,+\, x \, + (F + \upsilon) B \, = y 
+p\,w \,+\, x \, +  B \, F \, = y 
 \end{align}
@@
 $F$ is total cost of renting and using a booster pump each month.
-This approach assumes that Manila has a competitive market for renting/selling booster pumps.
-$\upsilon$ captures idiosyncratic monthly variation the booster pump cost such as changes in the electricity price or variation in installation costs.
+This approach assumes that Manila has a competitive market for renting/selling booster pumps that is unaffected by improvements in service quality.\footnote{This assumption is consistent with local service quality improvements and a city-wide market for booster pumps.}  $y$ is monthly household income.
+
+% $\upsilon$ captures idiosyncratic monthly variation the booster pump cost such as changes in the electricity price or variation in installation costs.
 $\upsilon$ is assumed to follow a normal distribution that is assumed to be uncorrelated with $\epsilon$ and has zero mean and standard deviation $\sigma_{\upsilon}$.
-$y$ is monthly household income.
 
@@
 \begin{align}
-w^{*} \, = \, \gamma \, - \, \alpha p +  \theta_1 B \, + \, \theta_2 R  \,+ \, \theta_3 B R \,  + \, \epsilon
+\label{eq:demand}
+w^{*} \, = \, \gamma \, - \, \alpha p +  Q(B,R)
 \end{align}
-Water demand depends linearly on the satiation preference, $\gamma$, as well as price, booster pump use, and pipe repairs.
-Given optimal water demand, $w^{*}$, households can then choose whether to use a booster pump by comparing expected utilities with and without booster pumps.
-Households use booster pumps when the following expression is greater than zero
+Water demand depends linearly on the satiation preference, $\gamma$, price, and service quality.
+
+Given optimal water demand, the indirect utility function at the optimal booster pump choice, $B^{*}$, is given by 
 \begin{align}
-E\Big[ \,V_{B=1 - B=0}^{*}\,\Big]  = (\theta_1 + \theta_3 R) \Big(  \frac{\theta_1 + \theta_3 R}{2\alpha} + \frac{\gamma +  \theta_2 R}{\alpha} - p  \, \Big) \, - \, (F \, + \upsilon)
+V\,=\,\frac{\alpha p^2}{2} - \gamma p + \frac{Q(B^{*},R)^{2}}{2\alpha} - p Q(B^{*},R) + \frac{\gamma Q(B^{*},R)}{\alpha} + y - B^{*} F
 \end{align}
+
+\begin{align}
+\label{eq:dvdr}
+\frac{dV}{dR}\,=\,\frac{w^{*}}{\alpha} \frac{dQ}{dR} - F \frac{dB^{*}}{dR}
+\end{align}
+
+Advantage in terms of unobservables, disadvantage in terms of counterfactuals...
+
+- Surplus is increasing in consumption
+-
+
+% Given optimal water demand, $w^{*}$, households can then choose whether to use a booster pump by comparing expected utilities with and without booster pumps.  
+% Households use booster pumps when the following expression is greater than zero
+% \begin{align}
+% E\Big[ \,V_{B=1 - B=0}^{*}\,\Big]  = (Q(1,R)-Q(0,R)) \Big(  \frac{Q(1,R)-Q(0,R)}{2\alpha} + \frac{\gamma +  \theta_2 R}{\alpha} - p  \, \Big) \, - \, F
+% \end{align}
 % Since $\epsilon$ is assumed to be  normal, it falls out of the equation
-When booster pumps increase service quality $\theta_1>0$, booster pump use is increasing in household's fixed water preference, $\gamma$, and decreasing in the water price, $p$.
-Booster pump use decreases following pipe replacements if $\theta_3$ is sufficiently negative.
 
-Given booster pump demand, the probability of observing a household choose to use a booster pump, $B^{*}$ can be expressed as follows
-\begin{align}
-Pr[B^{*}=1] \,\, = \,\, \Phi\Bigg( \, \frac{ (\theta_1 \theta_2 + \theta_1 \theta_3 + \theta_2 \theta_3) R + \frac{1}{2}(\theta_1^2 + \theta_3^2)  + \gamma (\theta_1 + \theta_3 R) \Big] - (\theta_1 + \theta_3 R) p \, - \, F }{\sigma_{\upsilon}} \, \Bigg)
-\end{align}
-where $\Phi(.)$ is the cumulative distribution function of the standard normal distribution.
+% Given booster pump demand, the probability of observing a household choose to use a booster pump, $B^{*}$ can be expressed as follows
+% \begin{align}
+% Pr[B^{*}=1] \,\, = \,\, \Phi\Bigg( \, \frac{ (\theta_1 \theta_2 + \theta_1 \theta_3 + \theta_2 \theta_3) R + \frac{1}{2}(\theta_1^2 + \theta_3^2)  + \gamma (\theta_1 + \theta_3 R) \Big] - (\theta_1 + \theta_3 R) p \, - \, F }{\sigma_{\upsilon}} \, \Bigg)
+% \end{align}
+% where $\Phi(.)$ is the cumulative distribution function of the standard normal distribution.
 Conditional on booster pump use, the probabilities of observing households use a particular amount of water, $w^{obs}$, can be expressed as follows
-\begin{align}
-Pr[w^{*}=w^{obs} \,|\, B^{*}=1] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p +  \theta_1  + \, \theta_2 R  \,+ \, \theta_3 R )}{\sigma_\epsilon} \, \Bigg) \\
-Pr[w^{*}=w^{obs} \,|\, B^{*}=0] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p \, + \, \theta_2 R   )}{\sigma_\epsilon} \, \Bigg)
-\end{align}
-Combining these expressions, the log-likelihood of observing each pair of booster pump use and water use across households, $i$, is as follows
-\begin{align}
-\begin{split}
-LL = \sum_i & \mathbbm{1}\{ B^{obs}_i = 1 \} \,\Big[ \ln\big( Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=1] \big) \Big] \, + \\
- & \mathbbm{1}\{ B^{obs}_i = 0 \} \,\Big[ \ln\big( 1- Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=0] \big) \Big] 
- \end{split}
-\end{align}
+% \begin{align}
+% Pr[w^{*}=w^{obs} \,|\, B^{*}=1] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p +  \theta_1  + \, \theta_2 R  \,+ \, \theta_3 R )}{\sigma_\epsilon} \, \Bigg) \\
+% Pr[w^{*}=w^{obs} \,|\, B^{*}=0] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p \, + \, \theta_2 R   )}{\sigma_\epsilon} \, \Bigg)
+% \end{align}
+% Combining these expressions, the log-likelihood of observing each pair of booster pump use and water use across households, $i$, is as follows
+% \begin{align}
+% \begin{split}
+% LL = \sum_i & \mathbbm{1}\{ B^{obs}_i = 1 \} \,\Big[ \ln\big( Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=1] \big) \Big] \, + \\
+%  & \mathbbm{1}\{ B^{obs}_i = 0 \} \,\Big[ \ln\big( 1- Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=0] \big) \Big] 
+%  \end{split}
+% \end{align}
 

### 2020-08-11 phil_paper/paper_booster_pumps_wjv.tex
tables pretty much done

@@
 - Also measure by closest pipe for robustness
+- Measure cost savings from less NRW! 
+	-- flag potential spillovers in NRW that we're missing...
+- could do non-linear pricing robustness check
+
+% This paper focuses on the costs of imperfect maintenance. Most of the large literature on water and
+% health has focused on initial access, not disruptions in water supply, and much of the work on water in
+% the developing world has focused either on point of use solutions or on rural areas (see, e.g. Ashraf, Berry
+% and Shapiro, 2010, Kremer et al, 2011). Fewtrell et al. (2005) and Esray et al. (1991) both provide
+% meta-analyses of the public health literatures on water and health. Typically, the papers that measure the
+% impact of piped water infrastructure find a negative correlation between piped water and disease (Merrick,
+% 1985; Galiani, Gertler and Schardrogsky, 2005; Gamper-Rabindran, Khan and Timmings, 2010), but not
+% in all cases (Fewtrell et al., 2005), perhaps because of maintenance problems, or perhaps because better
+% water reduces the incentives to engage in sanitary behavior (Bennett, 2012). Devoto et al. (2012) find
+% that increased household connections in urban areas lead to no difference in health but an improvement in
+% subjective well-being. Sasaki et al. (2008) also examine Lusaka, and test the impact of rainfall and poor
+% drainage on cholera epidemics in Lusaka.
 
@@
 
-- Surplus is increasing in consumption
--
+- Surplus is increasing in consumption (by assumption! given the multiplicative aspect)
 
@@
 
+Fixed costs:
+
+On average, pipe replacement projects replace 25.3 km of pipes at a cost of 166 million PhP.
+The average cost per pipe length is 9 million PhP per kilometer.
+Since around 0.73 km of pipes are replaced per small area, total project costs per small area are around 6.6 million PhP.
+With 275 connections per small area, project costs average 24,000 PhP per connection.
+
+New Revenues:
+
+Residential connections are billed 68 PhP more per month while commercial connections are billed 145 PhP more per month.
+Given that 94\% of connections are residential and 6\% of commercial, the total billing increase is around 73 PhP per month per connection.
+
+Decrease in Marginal Costs:
+
+After pipe-replacement, usage per connection decreases by 21 m3 per month.  Given marginal costs of 5 PhP per m3, then this decrease implies a cost reduction of 105 PhP per month.
+
+((73 )*12)/24000
+((400)*12)/24000
+((73 + 105 + 80)*12)/24000
+
 \begin{table}[h!] 
 \centering
-\caption{Structural Estimates}\label{table:estimates}
+\caption{Water and Booster Pump Use per Household Estimates}\label{table:mainregs}
 \vspace{-2mm}
 \begin{threeparttable}
-\begin{tabular}{@{}l*{1}{c}@{}}
+\begin{tabular}{@{}l*{1}{CCC}@{}}
 \toprule
-  &  (1)   \\
+  & (1)   & (2)   & (3)  \\
+  & Water Use & Water Use & Booster Pump Use \\
 \midrule
-Fixed Preferences & \\
-\hspace{1em}Intercept & \input{tables/est_gamma_1_1} \\
- 						& (\input{tables/est_gamma_sd_1_1}) \\
-\hspace{1em}Household Size & \input{tables/est_gamma_2_1} \\
- 							& (\input{tables/est_gamma_sd_2_1}) \\
-\hspace{1em}Employed Household Members & \input{tables/est_gamma_3_1} \\
- 						& (\input{tables/est_gamma_sd_3_1}) \\
-\hspace{1em}High Skill Employment & \input{tables/est_gamma_4_1} \\
- 						& (\input{tables/est_gamma_sd_4_1}) \\
-\hspace{1em}Ever High Price & \input{tables/est_gamma_5_1} \\
- 						& (\input{tables/est_gamma_sd_5_1}) \\
-\hspace{1em}Pipe Replacement Area & \input{tables/est_gamma_6_1} \\
- 						& (\input{tables/est_gamma_sd_6_1}) \\[.5em]
-Price Sensitivity & \input{tables/est_alpha_1} \\
- 						& (\input{tables/est_alpha_sd_1}) \\[.5em]
-Service Quality Preferences & \\
-\hspace{1em}Post Replacement & \input{tables/est_theta_1_1} \\
- 						& (\input{tables/est_theta_sd_1_1}) \\
-\hspace{1em}Booster Use & \input{tables/est_theta_2_1} \\
- 							& (\input{tables/est_theta_sd_2_1}) \\
-\hspace{1em}Post Replacement $\times$ Booster Use & \input{tables/est_theta_3_1} \\
- 						& (\input{tables/est_theta_sd_3_1}) \\[.5em]
-Usage Variability & \input{tables/est_sig_ep_1} \\
- 						& (\input{tables/est_sig_ep_sd_1}) \\[.5em]
-Booster Cost Variability & \input{tables/est_sig_up_1} \\
- 						& (\input{tables/est_sig_up_sd_1}) \\
+\input{tables/reg}
 \bottomrule
@@
 \footnotesize
-\item This table predicts usage per household with pipe replacement, booster pump use, and price with different fixed effects.   \regtext 45 PhP = 1 USD \,\,
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\regtext 45 PhP = 1 USD \,\,
 \end{tablenotes}
@@
 
-Need to fix the weighting of the estimates!!!!!!!!
+\begin{table}[h!] 
+\centering
+\caption{Usage per Household Regression Estimates}\label{table:nrwregs}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{CCCCC}@{}}
+\toprule
+  & (1)   & (2)   & (3) \\
+  & Volume Billed  & Volume Supplied & \% Non-Revenue Water \\
+\midrule
+\input{tables/nrw}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Say it includes both fixed effects (Describe fixed effects...) .
+Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
 
-Section Estimation:
-	- show what happens when boosters are turned off
+\begin{table}[h!] 
+\centering
+\caption{Usage per Connection Regression Estimates}\label{table:profitregs}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{cccc}@{}}
+\toprule
+  & (1) & (2) & (3) & (4)  \\
+  & Usage (m3) & Bill (PhP) & Usage (m3) & Bill (PhP) \\
+\midrule
+\input{tables/profitreg}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
 
@@
 	- Are households willing to pay for pipe improvements?
+
+	- How do welfare estimates compare to traditional estimates from health measures?
 
@@
 
-\begin{table}[h!] 
-\centering
-\caption{Usage per Household Regression Estimates}\label{table:usageregs}
-\vspace{-2mm}
-\begin{threeparttable}
-\begin{tabular}{@{}l*{1}{cccc}@{}}
-\toprule
-  & (1) & (2) & (3) & (4) \\
-\midrule
-\input{tables/cv_reg}
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item This table predicts usage per household with pipe replacement, booster pump use, and price with different fixed effects.   \regtext 45 PhP = 1 USD \,\,
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-\begin{table}[h!] 
-\centering
-\caption{Booster Pump Use Regression Estimates}\label{table:boosterregs}
-\vspace{-2mm}
-\begin{threeparttable}
-\begin{tabular}{@{}l*{1}{ccc}@{}}
-\toprule
-  & (1) & (2) & (3)  \\
-\midrule
-\input{tables/B_reg}
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item This table predicts household booster pump use with pipe replacement including demographic controls and small-area fixed effects.   \regtext 45 PhP = 1 USD \,\,
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
+% \begin{table}[h!] 
+% \centering
+% \caption{Booster Pump Use Regression Estimates}\label{table:boosterregs}
+% \vspace{-2mm}
+% \begin{threeparttable}
+% \begin{tabular}{@{}l*{1}{ccc}@{}}
+% \toprule
+%   & (1) & (2) & (3)  \\
+% \midrule
+% \input{tables/B_reg}
+% \bottomrule
+% \end{tabular}
+% \begin{tablenotes}
+% \footnotesize
+% \item This table predicts household booster pump use with pipe replacement including demographic controls and small-area fixed effects.   \regtext 45 PhP = 1 USD \,\,
+% \end{tablenotes}
+% \end{threeparttable}
+% \end{table}
 

### 2020-11-13 phil_paper/paper_booster_pumps_wjv.tex
get IV approach going

@@
 
-\section{Data}
+\section{Data and Setting}
+
+As a pioneer in water infrastructure investments among developing cities, Manila provides a useful context to study the welfare effects of these types of investments.
+In 1997, Manila awarded private concession contracts to two private companies to take over for the existing public utility.
+Each company is assigned to provide water to their assigned halves of Metro Manila.
+Both companies have gradually replaced the decaying pipe infrastructure inherited from the public utility.
+
+To measure the effect of pipe replacements, one of the companies has provided a map of their water pipes including the installation year for each pipe as well as water billing records for their 1.5 million water connections from January, 2008 to June, 2015.
+To measure each water connection's exposure to pipe replacement projects, connections are first located within ``small areas'' --- the smallest geographic designations used by the company each containing around 270 connections.
+Next, since projects often replace many pipes in the same place at the same time, each small area is assigned a ``pipe replacement year'' according to the year when the greatest total length of tertiary pipes were installed within that small area.\footnote{Tertiary pipes installed in the replacement year account for 85\% of the total tertiary pipe length in small areas.}  Tertiary pipes act as local feeders transporting water from large primary and secondary pipes directly to households.
+Therefore, tertiary pipe replacements likely affect service quality within local areas while primary and secondary pipe replacements may have diffuse impacts throughout the pipe network.
+By excluding primary and secondary pipe replacements, this approach limits the potential for spillover effects of pipe replacements onto neighboring areas at the cost of potentially underestimating the total welfare gains from these projects.
+
+Billing records measure monthly water prices and usage for each water connection, which may serve multiple households.
+In order to link connection-level consumption to household welfare, billing records for each connection are merged to a survey of water connections conducted by an independent evaluator to monitor compliance with the water utility's service obligations.
+This connection survey records demographics for the household that owns the connection as well as the number of other households and people that also use the connection.
+Household-level water usage is calculated by dividing total connection usage by the number of households sharing the connection.
+The survey also includes household demographics for the connection owner, different measures of water service quality, as well as household investments in booster pumps, water filters, and water storage tanks.
+
+The survey randomly interviewed water connection owners covering 15,000 connections in 2008, 24,000 connections in 2010, and 23,000 connections in 2012.
+Because a similar sampling design was followed across survey rounds, 13\% of connections were interviewed in two years, and 1.4\% of connections were interviewed in three years while remaining connections were interviewed in only one year.
+Since billing records form a monthly-panel, survey responses must be interpolated
+
+Since billing records are
+
+To examine household demographics, billing data are merged at the connection-level to a water connection survey conducted independently to monitor the quality of the utility's service.
+
+\footnote{Households using connections alone tend to be larger and wealthier than households that share connections with other households according to previous research (\cite{wjv}).}
+
+% The connection survey includes demographics for the households that own their water connections.
+Table~\ref{table:sampleconstruction} in Appendix~\ref{appendix:sampleconstruction} includes more details on how the final sample is constructed for the analysis.
+% This sample restriction ensures that connection-level is equal to household-level.
+
+The water connection survey also includes measures
+
+Additional survey data also includes information on demographics and water quality as well as investments!
+
+Water pipes are linked to areas... 
+The utility locates water connections within small areas each containing around 270 connections.
+
+Each small-area is assigned a pipe replacement year as the year when the greatest total length of tertiary pipes are installed within the small area.   This pattern is consistent with
+
+  This calculation includes only tertiary pipes (excluding )
+
+ which allows for linking
+
+The pipe map documents the installation year for each length of pipe, which forms the basis for the pipe replacement measure.   The
+
+% For the company, these efforts ramped up dramatically between 2008 and 2015.  
+% Identifying the effects of water pipe investments requires detailed information on the condition and location of water pipes that are often kept confidential out of security concerns.  
+% A regulated water utility serving half of the area of Metro Manila, Philippines has provided confidential access to a map of the water pipes as well as water billing records for 1.5 million water connections.
+
+% This utility provided access to monthly billing records for each connection as well as detailed information covering the regulatory structure and costs of production.
+Monthly billing records include meter readings, billing amount, outstanding balances, and payments spanning January, 2008 to May, 2015.
+Over this period, the total number of connections increased from 900,000 to 1,500,000 as the water utility expanded service access.
+Water connections are split into four categories: residential (90\%), semi-business (4\%), commercial (5\%), and industrial (1\%).
+% To focus on household consumption decisions, only residential connections are included in the analysis.
+
+% A household panel survey from Pasay City provides information on household income dynamics in Manila.
+Pasay City is a centrally located sub-municipality of Metro Manila accounting for 3.2\% of the population of Metro Manila as of 2015 and is roughly representative of households living in the utility's service area.
+The panel survey covers over 60\% of the population of Pasay City and is the only survey to provide a household-level income panel over a similar time frame in Manila.
+The analysis includes data from \input{tables/total_inc_hhs_all}households that were interviewed in both 2008 and 2011.
 
@@
 	- consumption per HH
-	- reweight data for household level?!
-
+	- reweight data for household level?! YES!
+	- survey panel and other panel; date representation, how its imputed, etc.
 	- Put in a table describing pipe-replacement;  describe staggered approach; predict pipe-replacement?
+	- industrial/commercial footnote later!!
 
@@
 
-A simple model of household water demand connects changes in water usage to changes in household welfare as a result of pipe replacements.
-In this model, households choose their monthly water usage as well as whether to use a booster pump to boost water pressure.
+A simple model of household water demand connects changes in water usage and investments in water booster pumps to changes in household welfare as a result of pipe replacements.
+In this model, households choose their monthly water usage as well as whether to use a booster pump to boost their water pressure.
 
@@
 \label{eq:utility}
-U\,=\,\frac{1}{\alpha} \, \Big[ \,  Q(B,R) \,  w  \, -\, \frac{1}{2}(w - \gamma + \epsilon)^2 \, \Big] \, + \, x 
+U\,=\,\frac{1}{\alpha} \, \Big[ \,  Q(B,R) \,  w  \, -\, \frac{1}{2}(w - \gamma)^2 \, \Big] \, + \, x 
 \end{align}
 where $w$ is water consumption and $x$ represents a bundle of all other goods consumed by the household.
-Water service quality given by $Q(B,R)$ depends on booster pump use where $B$ equals 1 if the household chooses to use a booster pump (and zero otherwise) and as well as pipe replacements where $R$ equals 1 after pipe replacement (and zero otherwise).
+Water service quality given by the function, $Q(B,R)$, depends on booster pump use where $B$ equals 1 if the household chooses to use a booster pump (and zero otherwise) and as well as pipe replacements where $R$ equals 1 after pipe replacement (and zero otherwise).
+$Q(B,R)$ is assumed to be differentiable in $R$.
 Water service quality enters multiplicatively with water consumption, which nests the assumption that each unit of water consumption is affected equally and positively by water service quality.
@@
 $\alpha$ reflects price sensitivity, and $\gamma$ reflects the satiation amount of water usage.
-This approach assumes that preferences for water are quasi-linear, which implies that water consumption does not depend on household income [ back this up with more evidence?
-].
+This approach assumes that preferences for water are quasi-linear, which implies that water consumption does not depend on household income [ Footnote to heterogeneity table ].
 
@@
 \label{eq:bc}
-p\,w \,+\, x \, +  B \, F \, = y 
+p\,w \,+\, x \, +  B \, F \, = Y
 \end{align}
@@
 $F$ is total cost of renting and using a booster pump each month.
-This approach assumes that Manila has a competitive market for renting/selling booster pumps that is unaffected by improvements in service quality.\footnote{This assumption is consistent with local service quality improvements and a city-wide market for booster pumps.}  $y$ is monthly household income.
+This approach assumes that Manila has a competitive market for renting/selling booster pumps that is unaffected by improvements in piped water service quality.\footnote{This assumption is consistent with local service quality improvements and a city-wide market for booster pumps.}  $Y$ is monthly household income.
 
@@
 \end{align}
-
+The derivative of $V$ with respect to pipe replacements, $R$, reflects the change in consumer welfare associated with pipe replacements.
+This derivative takes the following form after substituting terms for $w^{*}$
 \begin{align}
@@
 \end{align}
+This expression summarizes the consumer welfare effects of pipe replacements in terms of (1) the marginal effect on service quality weighted by water consumption and price sensitivity as well as (2) the marginal effect on booster pump usage weighted by the cost of booster pumps.
+This approach assumes that welfare effects are proportional to consumption, $w^{*}$, implying that service quality improvements affect all units of water consumption.
+Welfare effects are decreasing in price sensitivity, $\alpha$, which captures the intuition that households with many substitute water sources (ie.
+high $\alpha$) may benefit less from improvements in service quality.
+According to this approach, welfare changes do not require measuring fixed preferences, $\gamma$, separately from levels of service quality, $Q(B^{*},R)$.
+Therefore, this approach is robust to different patterns of selection into booster pump use based on different levels of service quality or fixed preferences for water consumption.
 
-Advantage in terms of unobservables, disadvantage in terms of counterfactuals...
+% This feature is especially useful in the empirical setting where booster pump use is non-random across households.  
+% The advantage of this approach is that welfare estimates do not require 
+% Advantage in terms of unobservables, disadvantage in terms of counterfactuals...
+% - Surplus is increasing in consumption (by assumption! given the multiplicative aspect)
 
-- Surplus is increasing in consumption (by assumption! given the multiplicative aspect)
+\section{Empirical Strategy}
 
-% Given optimal water demand, $w^{*}$, households can then choose whether to use a booster pump by comparing expected utilities with and without booster pumps.  
-% Households use booster pumps when the following expression is greater than zero
-% \begin{align}
-% E\Big[ \,V_{B=1 - B=0}^{*}\,\Big]  = (Q(1,R)-Q(0,R)) \Big(  \frac{Q(1,R)-Q(0,R)}{2\alpha} + \frac{\gamma +  \theta_2 R}{\alpha} - p  \, \Big) \, - \, F
-% \end{align}
-% Since $\epsilon$ is assumed to be  normal, it falls out of the equation
+The estimation strategy recovers household price sensitivity as well as the changes in service quality and booster pump use in response to pipe replacement projects.
+These estimated quantities along with observed water use and booster pump costs summarize the change in consumer welfare from pipe replacement projects as given by equation (\ref{eq:dvdr}).
+The estimating equation takes the following form
+\begin{align}
+\label{eq:esteq}
+y_{itl} \,=\, \beta_1 \, \text{After Pipe Replacement}_{tl} \,+\, \beta_2 \, p_{it} \, + \, \theta_t \, + \, \lambda_i \, + \epsilon_{itl}
+\end{align}
+where the outcome, $y_{itl}$, is either monthly water consumption or booster pump use.
+Outcomes are measured for household, $i$, in small area, $l$, at calendar month, $t$.
+After Pipe $\text{Replacement}_{tl} $ takes a value of one for months after pipe replacement and zero otherwise.
+Since the data identify only the year that pipes were replaced, all months from the replacement year onwards are considered after pipe replacement.
+$p_{it}$ measures the average price faced by each household in each month.
+$\theta_t$ includes calendar month fixed effects while $\lambda_i$ includes household fixed effects.
 
-% Given booster pump demand, the probability of observing a household choose to use a booster pump, $B^{*}$ can be expressed as follows
-% \begin{align}
-% Pr[B^{*}=1] \,\, = \,\, \Phi\Bigg( \, \frac{ (\theta_1 \theta_2 + \theta_1 \theta_3 + \theta_2 \theta_3) R + \frac{1}{2}(\theta_1^2 + \theta_3^2)  + \gamma (\theta_1 + \theta_3 R) \Big] - (\theta_1 + \theta_3 R) p \, - \, F }{\sigma_{\upsilon}} \, \Bigg)
-% \end{align}
-% where $\Phi(.)$ is the cumulative distribution function of the standard normal distribution.
-Conditional on booster pump use, the probabilities of observing households use a particular amount of water, $w^{obs}$, can be expressed as follows
-% \begin{align}
-% Pr[w^{*}=w^{obs} \,|\, B^{*}=1] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p +  \theta_1  + \, \theta_2 R  \,+ \, \theta_3 R )}{\sigma_\epsilon} \, \Bigg) \\
-% Pr[w^{*}=w^{obs} \,|\, B^{*}=0] \,\, &= \,\, \frac{1}{\sigma_{\epsilon}} \phi\Bigg( \, \frac{ w^{obs} - (\gamma \, - \, \alpha p \, + \, \theta_2 R   )}{\sigma_\epsilon} \, \Bigg)
-% \end{align}
-% Combining these expressions, the log-likelihood of observing each pair of booster pump use and water use across households, $i$, is as follows
-% \begin{align}
-% \begin{split}
-% LL = \sum_i & \mathbbm{1}\{ B^{obs}_i = 1 \} \,\Big[ \ln\big( Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=1] \big) \Big] \, + \\
-%  & \mathbbm{1}\{ B^{obs}_i = 0 \} \,\Big[ \ln\big( 1- Pr[B^{*}=1] \big) + \ln\big( Pr[w^{*}=w^{obs}_i \,|\, B^{*}=0] \big) \Big] 
-%  \end{split}
-% \end{align}
+When the outcome is monthly water consumption, the estimating equation maps directly onto the equation for optimal household consumption given by equation ($\ref{eq:demand}$).
+$\beta_1$ captures the effect of pipe replacement on service quality, $\frac{dQ}{dR}$.
+Likewise, $\beta_2$ captures the negative of household price sensitivity, $\alpha$.
+Remaining fixed preferences for water and levels of service quality are absorbed in household and month fixed effects, $\lambda_i$ and $\theta_t$.
+These fixed effects ensure that the effect of pipe replacements is identified from variation in water consumption for the same household before and after pipes are fixed while accounting for any temporal consumption patterns common to all households.
+Likewise, price sensitivity is estimated from variation in price for the same household switching between regular and high prices.
+Calendar month fixed effects absorb price variation affecting all households equally over time as the company updates water tariffs.
 
-\section{Empirical Specification and Identification}
-
-% ($\gamma, \alpha, \sigma_{\epsilon}$) ($\theta_2$)  ($\theta_1, \theta_3$) ($\sigma_{\upsilon}$)
-The estimation recovers preferences for water, preferences for water service quality, as well as booster pump effectiveness and cost variability.
-
-Fixed preferences for water, $\gamma$, are allowed to vary according to six demographic characteristics: household size, number of employed household members, whether the head of household has high-skilled employment, whether the household is ever assigned a high water price, and whether the household ever receives pipe replacement, as well as indicators for calendar months.\footnote{Preferences do not depend on time because usage does not exhibit strong trends over time.}  Fixed preferences are identified primarily from average usage levels for each demographic group.
-Month indicators capture seasonality in water demand, and year indicators capture how water preferences evolve over time.
-Monthly variation in water usage identifies variation in fixed preferences, $\sigma_{\epsilon}$.
-
-Since calendar month indicators absorb all of the time-series variation in price schedules, price sensitivity, $\alpha$, is identified primarily through household changes in usage as the company switches households between regular and high average prices.
-This approach relies on the assumption that switching between prices is not correlated with other factors that may affect demand.
-For example, households may increase their water demand as they open a roadside food-stand and switch to the high price.
-Conversely, households that close their roadside food-stand may decrease their consumption at the same time as they are switched to the low price.
-Both cases suggest that this approach would underestimate household price sensitivities.
-
-Both cases would also likely predict strong pre-trends in usage for the years leading up to price changes.
-Figure~\ref{figure:usagepricechanges} plots usage pre-trends providing little evidence of salient trends before price changes.
-Appendix Table~\ref{table:usageregs} further finds that the correlation between price and household usage remains stable after controlling for household demographics, small-area fixed effects, or household fixed effects.
-This approach also assumes that price sensitivities identified for households that switch prices are representative of the full population of households.
-Table~\ref{table:pricechangestatistics} provides some support for this assumption by finding broadly similar demographics across households exposed to different prices.
-
-Preference for water service quality from pipe replacements, $\theta_2$, is identified by the change in usage observed before and after pipe replacements.
-Identification of $\theta_2$ requires assuming that this change in consumption can be entirely attributed to pipe replacements and not to changes in other factors that may affect household demand for water at the same time.
+Identifying $\beta_1$ and $\beta_2$ requires assuming that pipe replacements and household-specific price changes are not correlated with any other factors that may also affect water demand at the same time.
 One concern may be that pipe improvements are paired with other infrastructure investments that drive increases in local income, population, and water demand.
@@
 
-Preferences for booster pumps before pipe replacement, $\theta_1$, and after pipe replacement, $(\theta_1+\theta_3)$, are identified both from cross-sectional differences in usage for households with and without booster pumps as well as from changes in booster pump usage before and after pipe replacement projects.
-Identification requires assuming that booster pump use accounts for all of the average differences in usage between households with and without booster pumps after conditioning on households' observable characteristics and pipe replacement status.
-This assumption may not hold if households choose to use booster pumps to cope with unobserved variation in water service quality specific to their neighborhoods.
-To partially test this assumption, Appendix Table~\ref{table:boosterregs} finds that the positive correlation between water use and booster pump use remains stable even after controlling for calendar month fixed effects as well as small-area fixed effects, which may both capture local variation in water service quality.
+Another concern is that households may increase their water demand as they are switched to the high price because they often open roadside food-stands.
+Conversely, households that close their roadside food-stands may decrease their consumption at the same time as they are switched to the low price.
+Both cases suggest that the empirical approach would underestimate household price sensitivities.
+Figure~\ref{figure:usagepricechanges} provides little evidence of strong pre-trends leading up to price changes.
+While this evidence is suggestive that these events are uncorrelated with long-term trends in water demand, this approach is unable to exclude the possibility that other factors may influence water demand at the same time as these events.
 
-Identification of booster pump preferences also requires assuming that changes in booster pump use before and after pipe replacement projects are driven entirely by these projects and not by any other factors such as shifts in water preferences that may also be correlated with these projects.
-Appendix Table~\ref{table:boosterregs} finds that the negative correlation between booster pump use and pipe replacement projects remains stable after accounting for household demographics and small-area fixed effects.
+When the outcome is booster pump use, the estimating equation captures the effect of pipe replacements on booster pump use.
+This approach assumes that demand for booster pumps can be linearly approximated by the estimating equation such that $\beta_1$ reflects $\frac{dB}{dR}$.
+Since booster pump use is a binary outcome, this approach represents a linear probability model.
+Time fixed effects account for variation in booster pump usage over time common to all households while household fixed effects account for differences in booster pump use across households.
+$\beta_1$ reflects the effect of pipe replacements on booster pump use under the assumption that no other factors independently affect booster pump use at the same time.
+One concern may be that the prices for booster pumps change in response to pipe replacement projects.
+Pipe replacements occur in small geographic areas while markets for booster pumps are likely to cover much wider areas.\footnote{Online markets span the entire city.}  Therefore, individual pipe replacement projects are unlikely to influence prices for booster pumps.
 
-This approach also assumes that booster pumps do not impose substantial negative externalities on local water service quality.
+% This approach also assumes that booster pumps do not impose substantial negative externalities on local water service quality.
 A recent engineering literature has raised the possibility that booster pumps interfere with water flow in pipe mainlines, reducing pressure along the entire pipe (\cite{taylor2014reducing}).
@@
 
-While fixed monthly costs of booster pumps, $F$, are calibrated to equal the expected monthly cost of operating a booster pump, the estimation strategy recovers the distribution of these costs, $\sigma_{\upsilon}$, that best matches the observed shares of households using booster pumps.
-Identification of $\sigma_{\upsilon}$ requires the assumption that cost variation, $\upsilon$, is uncorrelated with taste variation, $\epsilon$.
-This assumption implies that after accounting for observed demographic and other factors, differences in booster pump use are entirely driven by unobserved costs rather than unobserved preferences.
+\section{Results}
 
-\section{Results}
+Table~\ref{table:mainregs} includes results of the effect of price and pipe replacements.
+Column (1) provides results on household water use finding an increase of 1.79 m3 per household per month after pipe replacement.
+The estimate is statistically significant at the 1\% and economically large representing an 8\% increase in average consumption.
+The estimated increase is smaller than the descriptive increase in Figure~\ref{figure:pipecons} likely because the regression approach controls for increasing trends in water use over the sample period.
+
+Column (1) also provides an estimated price sensitivity of 0.17, which is statistically significant at the 1\% level.
+Given an average price of 21.5 PhP/m3, this estimate also implies a price elasticity of 0.17.
+This elasticity estimate is on the lower end of similar studies in the developing world, which find elasticities ranging from 0.01 to 0.98.\footnote{See \cite{szabo2015value}, \cite{diakite2009proposal}, and \cite{strand2005water}.}
+
+Column (2) finds that pipe replacement projects are associated with a 20\% decrease in booster pump use, which is statistically significant at the 5\% level.
+This decline is smaller than the descriptive decline in Table~\ref{table:descriptives} likely since the regression approach accounts for decreasing booster pump use over the sample period.
+
+% While previous studies largely focus on cities in low-income countries (\cite{diakite2009proposal} ) or low-income neighborhoods within larger cities, this estimate  which may explain
+
+% dQ/Q / dP/P  =  (.17/22.14) /  (1/21.5)
+% This estimate is in range of the 0.98 estimate from \cite{szabo2015value} as well as similar studies in the developing world that find elasticities between 0.01 and 0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).
+
+\begin{table}[h!] 
+\centering
+\caption{Household Water and Booster Pump Use Estimates}\label{table:mainregs}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{CC}@{}}
+\toprule
+  & (1)       & (2)              \\
+  & Water Use & Booster Pump Use \\
+\midrule
+\input{tables/reg}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{table}[h!] 
+\centering
+\caption{Change in Consumer Surplus}\label{table:mainregs}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{CCC}@{}}
+\toprule
+            & Service Quality              & Booster Pump Use & Total             \\
+\midrule
+Expression  & $\frac{w^{*}}{\alpha} \frac{dQ}{dR}$ &   $- F \frac{dB^{*}}{dR}$  & $\frac{dV}{dR}$ \\[1em]
+Estimates   &  \input{tables/est_welfare} \\
+            &  \input{tables/sd_welfare}  \\
+% Evaluated Estimates \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
 
@@
 \centering
-\caption{Water and Booster Pump Use per Household Estimates}\label{table:mainregs}
-\vspace{-2mm}
-\begin{threeparttable}
-\begin{tabular}{@{}l*{1}{CCC}@{}}
-\toprule
-  & (1)   & (2)   & (3)  \\
-  & Water Use & Water Use & Booster Pump Use \\
-\midrule
-\input{tables/reg}
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
-This table predicts usage per household with pipe replacement and price with different fixed effects.
-\regtext 45 PhP = 1 USD \,\,
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-\begin{table}[h!] 
-\centering
-\caption{Usage per Household Regression Estimates}\label{table:nrwregs}
+\caption{Total Water Supplied and Billed Estimates}\label{table:nrwregs}
 \vspace{-2mm}
@@
 
+\begin{table}[h!] 
+\centering
+\caption{Water and Booster Pump Use per Household Estimates}\label{table:mainregshet}
+\vspace{-2mm}
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{CCCC}@{}}
+\toprule
+  & (1)       & (2)  & (3) & (4)            \\
+  & Water Use & Water Use  & Booster Pump Use & Booster Pump Use \\
+\midrule
+\input{tables/reghet}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
 {

### 2020-12-14 phil_paper/booster_presentation.tex
get new draft rippin (writing welfare section)

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Beamer Presentation
% LaTeX Template
% Version 1.0 (10/11/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND THEMES
%----------------------------------------------------------------------------------------

\documentclass[aspectratio=32]{beamer}
\usefonttheme[onlymath]{serif}

\mode<presentation> {

% The Beamer class comes with a number of default slide themes
% which change the colors and layouts of slides. Below this is a list
% of all the themes, uncomment each in turn to see what they look like.

\usetheme{default}
%\usetheme{AnnArbor}
%\usetheme{Antibes}
%\usetheme{Bergen}
%\usetheme{Berkeley}
%\usetheme{Berlin}
%\usetheme{Boadilla}
%\usetheme{CambridgeUS}
%\usetheme{Copenhagen}
%\usetheme{Darmstadt}
%\usetheme{Dresden}
%\usetheme{Frankfurt}
%\usetheme{Goettingen}
%\usetheme{Hannover}
%\usetheme{Ilmenau}
%\usetheme{JuanLesPins}
%\usetheme{Luebeck}
%\usetheme{Malmoe}
%\usetheme{Marburg}
%\usetheme{Montpellier}
%\usetheme{PaloAlto}
%\usetheme{Pittsburgh}
%\usetheme{Rochester}
%\usetheme{Singapore}
%\usetheme{Szeged}
%\usetheme{Warsaw}

% As well as themes, the Beamer class has a number of color themes
% for any slide theme. Uncomment each of these in turn to see how it
% changes the colors of your current slide theme.

%\usecolortheme{albatross}
%\usecolortheme{beaver}
\usecolortheme{spruce}
%\usecolortheme{beetle}
%\usecolortheme{crane}
%\usecolortheme{dolphin}
%\usecolortheme{dove}
%\usecolortheme{fly}
%\usecolortheme{lily}
%\usecolortheme{orchid}
%\usecolortheme{rose}
%\usecolortheme{seagull}
%\usecolortheme{seahorse}
%\usecolortheme{whale}
%\usecolortheme{wolverine}

%\setbeamertemplate{footline} % To remove the footer line in all slides uncomment this line
%\setbeamertemplate{footline}[page number] % To replace the footer line in all slides with a simple slide count uncomment this line

%\setbeamertemplate{navigation symbols}{} % To remove the navigation symbols from the bottom of all slides uncomment this line
}

\usepackage{graphicx} % Allows including images
\usepackage{booktabs} % Allows the use of \toprule, \midrule and \bottomrule in tables
\usepackage{verbatim}
\usepackage{colortbl}

\usepackage{mathtools} 
\usepackage{amssymb}
\usepackage{mathrsfs}
\usepackage{amsmath}
\usepackage{bm}

\usepackage{ragged2e}
\usepackage{etoolbox}
\usepackage{lipsum}

\usepackage{siunitx,booktabs}
\usepackage{pifont}
\usepackage{array}
\usepackage{tabu,booktabs}
\usepackage{tikz,threeparttable}
\usetikzlibrary{arrows,shapes}

\setbeamertemplate{enumerate items}[circle]
\usepackage{tikz}
\usepackage{adjustbox}

\newcommand\mynum[1]{
  \usebeamercolor{enumerate item}
  \tikzset{beameritem/.style={circle,inner sep=0,minimum size=2ex,text=enumerate item.bg,fill=enumerate item.fg,font=\footnotesize}}%
  \tikz[baseline=(n.base)]\node(n)[beameritem]{#1};
}

\newcommand\mynumm[1]{
  \usebeamercolor{enumerate item}
  \tikzset{beameritem/.style={rectangle,inner sep=0,minimum size=2ex,text=enumerate item.bg,fill=enumerate item.fg,font=\footnotesize}}%
  \tikz[baseline=(n.base)]\node(n)[beameritem]{#1};
}
% COLUMN TYPES
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}{>{\centering\arraybackslash}p{5.2em}}
\newcolumntype{D}{>{\centering\arraybackslash}p{5em}}
\newcolumntype{G}{>{\centering\arraybackslash}p{6em}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}

\def\Put(#1,#2)#3{\leavevmode\makebox(0,0){\put(#1,#2){#3}}}

\setbeamertemplate{footline}[frame number]

\AtBeginSection[]{
  \begin{frame}
  \vfill
  \centering
  \begin{beamercolorbox}[sep=8pt,center,shadow=true,rounded=true]{title}
    \usebeamerfont{title}\insertsectionhead\par%
  \end{beamercolorbox}
  \vfill
  \end{frame}
}

%----------------------------------------------------------------------------------------
%	TITLE PAGE
%----------------------------------------------------------------------------------------

\title{The Welfare Effects of Infrastructure Quality: \\ Evidence from Water Pipe Replacements in Manila} % The short title appears at the bottom of every slide, the full title is only on the title page

\author{\\Will Violette \\ Federal Trade Commission \\ wviolette@ftc.gov \\[2em] Any opinions expressed herein are those of the authors
and do not necessarily represent the views of the
Federal Trade Commission.}

 % Your institution as it will appear on the bottom of every slide, may be shorthand to save space

\date{November 2020} %\today} % Date, can be changed to a custom date

\begin{document}

\beamertemplatenavigationsymbolsempty

\begin{frame}
\titlepage % Print the title page as the first slide
\end{frame}

%\begin{frame}
%\frametitle{Overview} % Table of contents slide, comment this block out to remove it
%\tableofcontents % Throughout your presentation, if you choose to use \section{} and \subsection{} commands, these will automatically be printed on this slide as an overview of your presentation
%\end{frame}

%----------------------------------------------------------------------------------------
%	PRESENTATION SLIDES
%----------------------------------------------------------------------------------------
%------------------------------------------------

% Mitlin, D., V.A. Beard,
% D. Satterthwaite, and J. Du. 2019. "Unaffordable and
% Undrinkable: Rethinking Urban Water Access in
% the Global South." Working Paper. Washington, DC:
% World Resources Institute. Available online at www.
% citiesforall.org.

\begin{frame}
\frametitle{Replacing Water Pipes}
\centering

% HIGHLIGHT PUBLIC FINANCE

% push punchline at the MOTIVATION!!

\begin{itemize}
  \item 12 out of 15 developing cities have intermittent water supply 
    \begin{itemize}
      \item Most people boil tap water before drinking [WRI, 2019]
    \end{itemize}
  \vspace{2mm}
  \item Fixing water pipes has high fixed costs, but produces marginal cost savings and health benefits
  \vspace{2mm}
\begin{center}
\includegraphics[scale=.5]{tables/nytimespic.png} \\
New York Times, Nov. 10th, 2017
\end{center}
  \vspace{2mm}

  \item Consumer surplus is often absent from the policy dialogue 
  % Policymakers Water quality can affect health (infant mortality, disease)
  %   \vspace{2mm}
  % \item This paper focuses on consumer surplus from water quality

  %%% THIS IS FINE BUT NOT THE KEY REASON!
\end{itemize}
\end{frame}

% https://www.nytimes.com/2017/11/10/climate/water-pipes-plastic-lead.html

% % %------------------------------------------------

\begin{frame}
\frametitle{This paper}
\centering
% In developing countries, 30\% of urban pop live in slums (UN, 2015)

%%% SUBHEADINGS! %%%

% multidimensional water quality at the front

\begin{itemize}
  \item \textbf{Research Question}: how do pipe replacement projects affect welfare?
    \begin{itemize}
      \item Households consume more water 
      \item Households spend less on substitutes for water quality \\
      (filters, storage containers, booster pumps)
      \item Pumping costs decrease and billing increases for the utility
    \end{itemize}
  \vspace{2mm}
  \item \textbf{Method}: analyze the staggered roll-out of 600 km of new pipe in Manila with billing records and survey data on water quality
  \vspace{2mm}
  \item \textbf{Preview of Findings}: pipe replacements lead to 10\% more water consumption and 54\% less booster pump use
    \begin{itemize}
      \item Cost savings alone $<$ Fixed costs
      \item Cost savings + Consumer surplus $>$ Fixed costs
    \end{itemize}
  % \vspace{2mm}
  % \item \textbf{Welfare}: consumer surplus increase equals 40\% of an average water bill
  %   \begin{itemize}
  %     \item 1/3 from better water quality and 2/3 from less spending on booster pumps
  %     \item Consumer surplus + Cost reductions $>$ Fixed costs
  %   \end{itemize}

\end{itemize}

\end{frame}

% % %------------------------------------------------

\begin{frame}
\frametitle{Data on Piped Water in Manila}
\centering

\begin{itemize}
  \item A large, regulated monopoly in Manila provided billing records for 1.5 mil. connections from 2008-2015
  \vspace{3mm}
  \item Billing records merge with survey data on 50,000 total residential connections spread across 2008, 2010, and 2011
    \begin{itemize}
      \item Outcomes measured per household and weighted by household
    \end{itemize}
  \vspace{3mm}
  \item The pipe replacement year is identified for each small-area ($\sim$2,900) according to the year  that accounts for the greatest amount of pipe replacement in each area
    \begin{itemize}
      \item Only consider replacements for areas with pre/post data
      \item Robust to using nearest pipe to each connection
    \end{itemize}
\end{itemize}

% smalla rea size

\end{frame}

% % %------------------------------------------------

\begin{frame}
\frametitle{Water Quality Before/After Pipe Replacement}
\centering

% treatment areas

\begin{table}[h!] 
\centering
% \caption{Average Survey Responses Before and After Pipe Replacement}
\vspace{-2mm}
\begin{threeparttable}
\begin{tabular}{@{}l*{1}{ccc}@{}}
\toprule
  & Before & After  & All \\
\midrule
% Piped Water Service Quality \\[.5em]
$\text{Water has strong pressure (6pm-12am)}^{\dagger}$ & \input{tables/yes_flow_6mid} \\
$\text{Water has no pressure (6pm-12am)}^{\dagger}$  & \input{tables/no_flow_6mid} \\
Water interruptions in last 3 months & \input{tables/stop_freq} \\
Water has foreign bodies & \input{tables/foreign_bodies} \\
Water is discolored & \input{tables/discolored} \\
Water has unusual taste/smell & \input{tables/taste_smell} \\
\\[-.5em]
Households & \input{tables/pawsn} \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item  $\dagger$ when not using booster pump.\,\,
% See Appendix~\ref{appendix:sampleconstruction} for more details on the sample construction.
\end{tablenotes}
\end{threeparttable}
\end{table}
\begin{itemize}
  \item Large quality improvements
\end{itemize}

\end{frame}
% % \begin{frame}
% % \frametitle{Public Housing in South Africa}
% % % \centering
% % \centering
% % \begin{itemize}
% %   \item Large 
% %     \vspace{2mm}
% %   \item 
% %     \vspace{2mm}
% %   \item 
% % \end{itemize}
% % \end{frame}

% % %------------------------------------------------

\begin{frame}
\frametitle{Quality Substitutes Before/After Pipe Replacement}
\centering

\begin{table}[h!] 
\centering
% \caption{Average Quality Substitutes Before/After Pipe Replacement}
% \vspace{-2mm}
\begin{threeparttable}
\begin{tabular}{@{}l*{1}{ccc}@{}}
\toprule
  & Before & After  & All \\
\midrule
Uses booster pump & \input{tables/booster} \\
Hours booster pump is used per day & \input{tables/booster_use} \\
Uses water storage tank & \input{tables/drum} \\
Uses water filter & \input{tables/filter} \\
Purchases filtered water & \input{tables/station} \\
Purchases from a deepwell & \input{tables/deepwell} \\
Spending on non-piped water (PhP) & \input{tables/wrs_exp} \\
Drinks from the tap & \input{tables/drink} \\
Boils tap water before drinking & \input{tables/boil} \\
\\[-.5em]
Households & \input{tables/pawsn} \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item 
% See Appendix~\ref{appendix:sampleconstruction} for more details on the sample construction.
\end{tablenotes}
\end{threeparttable}
\end{table}
\begin{itemize}
  \item Much less booster pump use
  \item Small changes in other substitutes
\end{itemize}

\end{frame}

% % %------------------------------------------------

\begin{frame}
\frametitle{Average Usage per Household with Years to Pipe Replacement}
\begin{figure}
\begin{center}
% \caption{Average Consumption per Household with Years to Pipe Replacement}\label{figure:pipecons}
\includegraphics[scale=.73]{tables/pipe_cons.pdf}
\end{center}
%%% add counts and average change in discussion
\end{figure}
\end{frame}

% % %------------------------------------------------

% \begin{frame}
% \frametitle{Price Variation}

% \begin{itemize}
% \item 
%   \begin{itemize}
%   \item Mainly occurs when households start 
%   \end{itemize}
% \item 
% \end{itemize}

% \end{frame}

% % %------------------------------------------------

\begin{frame}
\frametitle{Average Usage per Household with Months to Price Change}
%%% estimate dmeand only for households with a price change

\begin{figure}
\begin{center}
% \caption{Average Consumption per Household with Years to Pipe Replacement}\label{figure:pipecons}
\includegraphics[scale=.54]{tables/r_to_s_only_graph.pdf}
\end{center}
\begin{itemize}
\item 729 households are switched to a high-price tariff when they are detected with businesses (ie. roadside stands)
\item Switched households use more water but have similar demographics to other households
\end{itemize}
%%% add counts and average change in discussion
\end{figure}
\end{frame}

% % %------------------------------------------------

\begin{frame}
\frametitle{Household Demand for Water}

\begin{align*}
\label{eq:utility}
max_{w,x,B} &\hspace{.5cm}\frac{1}{\alpha} \, \Big[ \,  Q(B,R) \,  w  \, -\, \frac{1}{2}(w - \gamma)^2 \, \Big] \, + \, x  \\
s.t.& \\
&p\,w \,+\, x \, +  B \, F \, = Y
\end{align*}

\begin{itemize}
  \item $\alpha$ is the price-sensitivity
  \item $Q(B,R)$ is water quality depending on booster pump use ($B$) and pipe replacements ($R$)
  \item $w$ is water usage
  \item $x$ is all other goods
  \item $\gamma$ is the fixed preference for water
  % \vspace{2mm}
  \item $p$ is the water price (assumed to be constant)
  \item $F$ is the monthly cost of the booster pump
  \item $Y$ is income
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Solve for the Welfare Effect of Pipe Replacements }

\begin{itemize}
  \item Water demand as a function of booster pump choice
      \begin{align*}
      w \, = \, \gamma \, - \, \alpha p +  Q(B,R)
      \end{align*}
  \item Effect of pipe replacements on consumer welfare
      % \begin{align*}
      % V\,=\,\frac{\alpha p^2}{2} - \gamma p + \frac{Q(B,R)^{2}}{2\alpha} - p Q(B,R) + \frac{\gamma Q(B,R)}{\alpha} + y - B F
      % \end{align*}
      \begin{align*}
      \frac{dV}{dR}\,=\,\frac{w}{\alpha} \frac{dQ}{dR} - F \frac{dB}{dR}
      \end{align*}
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Estimating Demand}

%%% LINK BACK TO BEFORE, PREVIOUS SHOWING VARIATION

% \begin{itemize}
%   \item Water Demand
% \end{itemize}
\begin{align*}
&\text{First Stage}\\
p_{it} &= \phi_1 \text{Post Pipe}_{tl}  +  \phi_3 \text{Post p ch}_{it} +  \phi_1\text{Pre t}_{it} +\phi_2\text{Post t}_{it} +  \phi_t +  \phi_i + \epsilon_{itl}  \\[.5em]
&\text{Second Stage}\\
w_{itl} &= \gamma_1  \text{Post Pipe}_{tl} + \gamma_2  \hat{p}_{it} + \gamma_3\text{Pre t}_{it} +\gamma_4\text{Post t}_{it} +    \gamma_t +  \gamma_i +  \varepsilon_{itl} \\
b_{itl} &= \beta_1  \text{Post Pipe}_{tl} + \beta_2  \hat{p}_{it} + \beta_3\text{Pre t}_{it} +\beta_4\text{Post t}_{it} +    \beta_t +  \beta_i +  \varepsilon_{itl} 
\end{align*}
\begin{itemize}
  \item $w_{itl}$ is water consumption and $b_{itl}$ is booster pump use
  \item $i$ is household, $t$ is month, and $l$ is location
  \item $\text{Post Pipe}_{tl}$ indicates months after pipe replacements
  \item $\text{Pre t}_{it}$ and $\text{Post t}_{it}$ are pre and post trends relative to the first price change
  \item $\text{Post p ch}_{it}$ indicates months after the first price change
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Estimating Water Demand}
Second stage
  \begin{align*}
  w_{itl} &= \gamma_1  \text{Post Pipe}_{tl} + \gamma_2  \hat{p}_{it} + \gamma_3\text{Pre t}_{it} +\gamma_4\text{Post t}_{it} +    \gamma_t +  \gamma_i +  \varepsilon_{itl} \\
  b_{itl} &= \beta_1  \text{Post Pipe}_{tl} + \beta_2  \hat{p}_{it} + \beta_3\text{Pre t}_{it} +\beta_4\text{Post t}_{it} +    \beta_t +  \beta_i +  \varepsilon_{itl} 
  \end{align*}
Effect of pipe replacements on consumer welfare
  \begin{align*}
  \frac{dV}{dR}\,=\,\frac{w}{\alpha} \frac{dQ}{dR} - F \frac{dB}{dR}
  \end{align*}

\begin{itemize}
  \item $\gamma_1 = \frac{dQ}{dR} $
  \item $\beta_1  = \frac{dB}{dR}$
  \item $\gamma_2 = \alpha +  \frac{dQ}{dB} \frac{dB}{dp}$
  \item $\beta_2 = \frac{dB}{dp}$
\end{itemize}

\end{frame}

\begin{frame}
\frametitle{Results}

\begin{table}[h!] 
\centering
% \caption{Household Water and Booster Pump Use Estimates}\label{table:mainregs}
\vspace{-2mm}
\begin{threeparttable}
\begin{tabular}{@{}l*{1}{CC}@{}}
\toprule
  % & (1)       &  (2)              \\
  & Water Use & Booster Pump Use \\
\midrule
\input{tables/reg_stars}
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item Includes connection and calendar month fixed effects.  Standard errors are clustered at the small-area level.
\end{tablenotes}
\end{threeparttable}
\end{table}

%%% CALCULATE ELASTICITY

\end{frame}

\begin{frame}
\frametitle{Heterogeneous Effects}

\begin{table}[h!] 
\centering
% \caption{Household Water and Booster Pump Use Estimates}\label{table:mainregs}
% \vspace{-2mm}
    \begin{adjustbox}{width=\textwidth, totalheight=\textheight-2\baselineskip,keepaspectratio}
\begin{threeparttable}
\begin{tabular}{@{}l*{1}{CC}@{}}
\toprule
  % & (1)       &  (2)              \\
  & Water Use &  Booster Pump Use  \\
\midrule
\input{tables/reghet_stars_int}
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item
% \item Includes connection and calendar month fixed effects.  Standard errors are clustered at the small-area level.
\end{tablenotes}
\end{threeparttable}
    \end{adjustbox}
\end{table}

\end{frame}

\begin{frame}
\frametitle{Effects on Consumer Welfare}

\begin{table}[h!] 
\centering
% \caption{Change in Consumer Surplus}\label{table:mainregs}
\vspace{-2mm}
\begin{threeparttable}
\begin{tabular}{@{}l*{1}{CCC}@{}}
\toprule
            & Better Water Quality              &  Less Spending on Booster Pumps & Total             \\
\midrule
Expression  & $\frac{w}{\alpha} \frac{dQ}{dR}$ &   $- F \frac{dB}{dR}$  & $\frac{dV}{dR}$ \\[1em]
Estimates (in PhP)   &  \input{tables/est_welfare} \\
            &  \input{tables/sd_welfare}  \\
% Evaluated Estimates \\
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item 
% Weighting, discussion of different samples, clustering, controls (especially rate classes).  This table predicts usage per household with pipe replacement and price with different fixed effects.  
\end{tablenotes}
\end{threeparttable}

\begin{itemize}
  \item Average water bill per household is 532 PhP
  \vspace{.5mm}
  \item Average monthly household income is \input{tables/median_inc}PhP
    \vspace{.5mm}
  \item The monthly operating cost of booster pumps, $F$, is 486 PhP
    \vspace{.5mm}
  \begin{itemize}
    \item Electricity is expensive and pumps are used for 2.6 hrs per day
    \item Does not include upfront price ranging from 1,200 to 15,000 PhP
  \end{itemize}
\end{itemize}

\end{table}

\end{frame}

% %------------------------------------------------

\begin{frame}
\frametitle{Do pipe replacements pay for themselves?}

\begin{table}[h!] 
\centering
% \caption{Total Water Supplied and Billed Estimates}\label{table:nrwregs}
% \vspace{-2mm}
\begin{threeparttable}
\begin{tabular}{@{}l*{1}{CCCCC}@{}}
\toprule
  % & (1)   & (2)   & (3) \\
  & Billing  & Supply Costs \\
\midrule
\input{tables/savings}
\bottomrule
\end{tabular}
\begin{tablenotes}
\footnotesize
\item 
% Say it includes both fixed effects (Describe fixed effects...) .  Weighting, discussion of different samples, clustering, controls (especially rate classes).  This table predicts usage per household with pipe replacement and price with different fixed effects.   \regtext 45 PhP = 1 USD \,\,
\end{tablenotes}
\end{threeparttable}
\end{table}

\begin{itemize}
  \item Fixed costs equal 17,021 PhP per household
  \item 10 year loan at 5\% interest implies monthly payments of 181 PhP
  \item Consumer surplus of 161 PhP + Cost savings of 131 PhP $>$ Loan payments of 181 PhP
  \item Does not include health benefits, commercial users (6\%), other infrastructure benefits
\end{itemize}

\end{frame}

\begin{frame}

\frametitle{Takeaways}

\begin{itemize}
  \item Consumer surplus matters for pipe replacement policies
  \item Important to measure both direct effects (ie. consumption) and indirect effects (ie. quality substitutes) of quality investments
  \item Thanks for coming and for your feedback!
\end{itemize}

\end{frame}

% Section Welfare:
%   - Welfare benefits with 10 yr 5\% loans (assume discount rates) or 50 yr 5\% loan?
%   - Welfare benefits with cash
%   - Are households willing to pay for pipe improvements?

%   - How do welfare estimates compare to traditional estimates from health measures?

\end{document}

### 2020-12-14 phil_paper/paper_booster_pumps_wjv.tex
get new draft rippin (writing welfare section)

@@
 
+[ RE-WRITE WITH NEW DEFINITION! ]
 The government regulator also gives the water company discretion to assign households to a high-price tariff schedule if they have any business activity at their residence, which provides a novel source of price variation in the context of public utilities.
@@
 \toprule
-  & Always Reg. Price & Always High Price  & Change Price \\
+  & Always Reg. Price & Always High Price  & Change Reg. to High Price \\
 \midrule
@@
 
+6.6 million PhP/(275*1.41)
+
 New Revenues:
@@
 \end{table}
+
+%%% leave out booster pumps?
+\section{Counterfactuals}
+
+% We're focusing on a part of the natural monopoly where the costs are easy to measure (you replace pipes), but the benefits are less well understood.
+Different from the standard Laffont and Tirole model; closer to the Spence model which is a real contribution!
+(luckily high cost areas also have high benefit)
+
+% Set aside all other aspects of regulation to focus on quality!  Usually, capital is thought of as an input to deliver a certain quantity of the product.  Here we're focusing on a particular
+
+The following counterfactuals identify the welfare effects of optimal pipe replacements under five different information environments.
+The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
+In the \textit{regular-replacement} counterfactual, the regulator simply replaces all pipes at a fixed interval.
+In the \textit{quality-standards} counterfactual, the regulator establishes a minimum water pressure threshold and replaces pipes when pressure falls below the threshold.
+In the \textit{cost-recovery} counterfactual, the regulator schedules replacements to balance savings from lower pumping costs against upfront costs of the pipe replacements.
+In the \textit{firm-level} counterfactual, the regulator lets the firm decide when to replace pipes under the assumption that the firm has full demand and cost information.
+
+% - hold price fixed!
+% - decide replacements independently for each area
+% -
+
+% - Not permitted expenses, similar to a price-cap [that's fair] (under invest)
+% - Rate of return (allow for overlapping loans...?) --> no, don't ; make the point that the firm will want to replace pipes as soon as loans come due because the projects generate more than enough revenue to meet reasonable rates of return.
+
+% - permitted expenses or not? hard to know..
+% - rate of return when we don't know the production function; 
+% - high power --> redistribute little but keep costs down
+% - low power --> redistribute a lot but high costs
+% --- where are we?
+
+% --> low power: all the surplus goes to consumers, but decisions are based on limited information
+% --> high power: firm can get the surplus, but decisions are based on detailed consumer information; provides a strong incentive for the firm to figure out exactly the benefits of the investments
+%%% in practice, it's somewhere between
+%%% note that with the high power incentive, the prices are high, and the wedges get smaller if the prices are lower!
+%%% footnote explaining distinction with standard high versus low-powered incentives.
+
+% Since these projects generate streams of revenues in excess of their costs, then rate-of-return regulation would likely lead firms to very frequently replace pipes.\footnote{We do not explicitly model rate of return regulation here because the constraint would depend on whether the company could take out multiple loans, and the cost of capital for those loans.}
+
+The \textit{full-information} counterfactual simulates how often a regulator would optimally replace pipes in order to maximize welfare under full information.
+For each section of the service area, the regulator maximizes present-discounted welfare indefinitely given by the following expression
+% doublecheck the tau's and t's
+\begin{align*}
+max_{R_t\in\{0,1\}} \,\, &\sum_{\tau = t}^{\infty} (1+\delta)^{t-\tau} [CS(k_{t}) + V(k_{t})]  \\
+V(k_{t}) &= W(k_{t}) - E(k_{t}) - L(k_{t})\\ 
+k_{t+1} &=  (1 + k_t) \, (1-R_t \mathbbm{1} \{ k_{t}> l\}) \\
+L(k_t) &= \frac{r(1+r)^{l} }{(1+r)^{l} -1 }\overline{L} \, \mathbbm{1} \{ k_{t}\leq l \}
+\end{align*}
+where $t$ indexes month, $\delta(>0)$ is the discount factor, and $k_t$ is the age of the pipes.
+$CS(k_{t})$ is consumer surplus and $V(k_t)$ is net revenue, which depends on revenue from water sales, $W(k_{t})$, costs of water leakage, $E(k_{t})$, and payments on any loans to fund pipe replacements, $L(k_t)$.
+Due to pipe deterioration, consumer surplus and water revenue are both assumed to be decreasing in pipe age while water leakage is assumed to increase with pipe page.
+$L(k_{t})$ is the payment on the loan needed to fund a pipe replacement.
+Each month, the regulator chooses whether to replace pipes ($R_t = 1$) or not ($R_t = 0$).
+Replacing pipes sets the pipe age, $k_t$, back to zero and is only possible if the regulator has paid off any debt from a previous pipe replacement where $l$ indexes the duration of the debt.
+The regulator is assumed to fund a pipe replacement with a loan of total size, $\overline{L}$, at monthly interest rate, $r$, over duration, $l$.
+The expression for $L(k_t)$ calculates the size of the monthly loan payments.
+In this framework, the optimal schedule of pipe replacements balances net revenue against consumer surplus from new pipes.
+
+In this framework, net revenues for a section of the service area can be positive, negative, or zero.
+In practice, the regulator is likely to stagger pipe replacements across different sections of the service area so that total net revenues across all service areas are close to zero.
+However, in some periods, total net revenues may still be negative or positive.
+In these cases, the model implicitly assumes that the regulator adjusts fixed monthly service charges
+
+is able to maintain revenue neutrality by adjusting fixed monthly service charges paid by consumers.
+
+% Since this framework does not assume a revenue constraint at zero,
+
+% While in practice, regulators may adjust both marginal prices and fixed monthly service charges, the model focuses only on fixed monthly service charges  
+% The model implicitly assumes that the regulator is able to implement fixed transfers to and from consumers without distorting their water consumption.
+For example, the regulator may offer all consumers fixed rebates in months with budget surpluses and higher fixed water charges in months with budget deficits.
+% Allowing negative net revenues in the model provides an approximation for this scheduling optimization.
+
+% While the model does not explicitly capture scheduling optimization, it 
+This framework also holds the water tariff fixed.
+
+In the \textit{regular-replacement} counterfactual, the regulator is uninformed about consumer surplus and revenues.
+Instead, the regulator only knows the age of the pipes and chooses to replace pipes as soon as they reach a certain age, $\overline{K}$.
+In the \textit{quality-standards} counterfactual, the regulator observes not only the age of the pipes, but also the water pressure reaching consumers, $P(k_t)$.
+The regulator then chooses to replace pipes once the water pressure falls below a certain threshold, $\overline{P}$.
+In the \textit{cost-recovery} counterfactual, the regulator does not observe water pressure, but instead observes the part of producer surplus attributable to leakage costs, $E(k_t)$.
+The regulator then replaces pipes to minimize leakage costs and pipe replacement costs.
+
+The marginal price is enough to cover the other fixed costs, and the firm gets to keep the leftovers!
+
+In the \textit{firm-level} counterfactual, the regulated firm is assumed to be fully aware of producer surplus, $PS(k)$, and the regulator allows the firm to maximize producer surplus, $PS(k) - L(k_{t})$.
+
+Total welfare versus producer/consumer divide?
+
+% Mermelstein et al. (2012) for dynamic merger analysis
+%%% in some months, it may be negative..
+
+In the empirical set-up, ...
+
+Discuss the empirical set up!  Discuss the limitations in the empirical set-up. Roughly correspond to natural divisions of the service area.
+
+Consumer surplus and producer surplus are assumed to linearly decline in pipe age, $k_t$.
+This assumption is consistent with civil engineering research documenting a roughly linear relationship between pipe failure and age.\footnote{See \cite{ward2017deterioration}, \cite{kleiner2001comprehensive}, and \cite{aydogdu2015estimation}.}
+
+Since the majority of pipes are replaced
+
+Appendix on decom.
+
+Results are discussed below in Table [x].
+
+ then the regulator maximization problem has an interior solution where the regulator choses whether to .  In practice, simulations solve the maximization problem recursively using
+
+% This approach abstracts away from many other features (price, independent decisions, maintenance, expectations about the future)
+
+% where $t$ indexes month, $\delta>0$ is the discount factor, and $k_t$ is the age of the pipes.
+$CS(k_{t})$ is consumer surplus and $PS(k_{t})$ is producer surplus, which are both assumed to be decreasing in pipe age as pipes deteriorate.
+$L(k_{t})$ is the payment on the loans needed to fund upfront pipe replacements.
+Each month, the regulator chooses whether to replace pipes ($R_t = 1$) or not ($R_t = 0$).
+Replacing pipes sets the pipe age, $k_t$, back to zero and is only possible if the regulator has paid off any debt from a previous pipe replacement where $l$ indexes the duration of the debt.
+The regulator is assumed to fund pipe replacements with a loan of total size, $\overline{L}$, at monthly interest rate, $r$, over duration, $l$.
+The expression for $L(k_t)$ calculates the monthly loan payment for the duration of the loan.
+In this framework, the optimal schedule of pipe replacements balances the (decreasing) consumer and producer surplus from new pipes against the upfront cost of replacing pipes.
+
+% In the \textit{regular-replacement} counterfactual, the regulator is uninformed about consumer and producer surplus.
+Instead, the regulator only knows the age of the pipes and chooses to replace pipes as soon as they reach a certain age, $\overline{K}$.
+In the \textit{quality-standards} counterfactual, the regulator observes not only the age of the pipes, but also the water pressure reaching consumers, $P(k_t)$.
+The regulator then chooses to replace pipes once the water pressure falls below a certain threshold, $\overline{P}$.
+In the \textit{cost-recovery} counterfactual, the regulator does not observe water pressure, but instead observes the part of producer surplus attributable to leakage costs, $E(k_t)$.
+The regulator then replaces pipes to minimize leakage costs and pipe replacement costs.
+
+% In the \textit{firm-level} counterfactual, the regulated firm is assumed to be fully aware of producer surplus, $PS(k)$, and the regulator allows the firm to maximize producer surplus, $PS(k) - L(k_{t})$.
+
+% Total welfare versus producer/consumer divide?
+
+% k_{t+1} &= \begin{cases}
+% k_t + 1 &\text{ if } R_t=0 \\
+% 0 &\text{ if } R_t=1 \text{ and } k_{t}> l
+% \end{cases}\\
+% \begin{align*}
+% L(k_t) = \begin{cases}
+% \overline{L}\frac{r(1+r)^{l} }{(1+r)^{l} -1 } &\text{ if } k_{t}\leq l \\
+% 0 &\text{ if } k_{t}> l
+% \end{cases}
+% \end{align*}
+% d = (((1+r)^(12*loan_term))-1)/(r*(1+r)^(12*loan_term));
+% F  = total_loan/d;
+
+The fourth counterfactual imagines an uninformed regulator and a fully informed firm where the firm decides when to replace pipes.
+The regulator does not adjust prices to compensate the firm for pipe replacements, which leaves the firm to maximize its own surplus from replacing pipes.\footnote{Strong incentive to reduce costs: This may occur when the regulator can't credibly commit to price increases or when the firm has a strong incentive to inflate costs which the regulator cannot verify.}
+
+according to advice from water engineers who measure costs of replacements as well as pumping cost savings.
+The regulator then replaces pipes to optimize upfront replacement costs against marginal savings in pumping costs.
+
+without knowing the replacement costs or how replacements would affect water demand.
+However, the regulator is able to measure water pressure either through consumer surveys, consumer complaints, or pressure gauges.
+The regulator then establishes a minimum pressure threshold and replaces pipes when the pressure drops below the threshold.
 

### 2020-12-14 phil_subcode/ajeffect.m

@@ -1,0 +1,26 @@
+syms k r alpha s  lambda
+
+assume(alpha>0)
+assume(alpha<1)
+
+% R(k) - rk
+% s = R(k)/k
+
+opt = k^.5 - r*k
+con = k^.5 - s*k
+
+ll = opt+lambda*con
+
+dk=diff(ll,k)
+dl=diff(ll,lambda)
+
+[s1,s2]=solve([dk,dl],[k,lambda])
+
+s1
+s2
+
+
+
+
+
+

### 2020-12-14 phil_subcode/reps.m

@@ -1,0 +1,93 @@
+
+
+
+
+
+beta_up = .1;
+
+beta = 1/( 1 + beta_up );
+
+N = 200;
+A = repmat((0:N)',1,N+1)';
+Aprime = A';
+nA = size(A,1);
+
+% (161+131) - slope*(50) = 0
+slope = (161+131)/50;
+
+Q0 = 161+131;
+Q1 = slope;
+
+F  = 181;
+
+util1 = (Q0 - A.*Q1 - F).*(Aprime==0) + (Q0 - A.*Q1).*(A<Aprime & Aprime~=0) + -1000000.*(A>=Aprime & Aprime~=0);
+
+v       = zeros(nA,1);
+decis   = zeros(nA,1);
+metric=1000;
+
+
+while metric > 1e-7
+
+  [tv1,tdecis1]=max(util1 + beta.*repmat(v,1,nA));
+
+  tdecis=tdecis1';
+  tv=tv1';
+  
+  metric=max(max(abs((tv-v)./tv)));
+  v=tv;
+  decis=tdecis;
+end
+
+[(1:nA)' decis]
+
+% 
+% decis=(decis-1)*inA + minA; %%% try to understand this better...
+% 
+% Amark = size(Agrid,1);
+% Athis = Agrid(Amark,1);        % initial level of assets        
+% states   = zeros(n-1,2);
+% controls = zeros(n-1,2);
+% for i = 1:n-1
+%     Aprime = decis(Amark,chain(i));
+%     Amark  = tdecis(Amark,chain(i));
+%     
+%     [~,~,~,~,cons1,cons2,cons3,cons4] = ...
+%     u_w1loan3(Athis,Aprime,alpha,p,r_high,r_low,r_lend,Y_high,Y_low,lambda_high,lambda_low,m);
+%     
+%     cons_full = [cons1 cons2 cons3 cons4];
+%     cons = cons_full(chain(i));
+%     
+%     states(i,:) = [ Athis chain(i) ];
+%     controls(i,:) = [ cons Aprime ];
+%     Athis = Aprime;
+% end
+% 
+% 
+% w_debt_max = p.*controls(:,1);
+% w_debt = ( controls(:,2).*(controls(:,2)>w_debt_max) + ...
+%             w_debt_max.*(controls(:,2)<=w_debt_max) ).* ...
[…]

### 2020-12-14 phil_subcode/reps_4.m

@@ -1,0 +1,114 @@
+
+
+loc = '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/';
+
+M = csvread(strcat(loc,'mat_counter.csv'),1);
+CSt = M(:,1)+M(:,2);
+PSt = M(:,3)+74;
+TLt = M(:,4);
+% CSe BSe Ae CPe 
+
+%%% simulate every 30!
+
+
+beta_up = .04/12;
+beta = 1/( 1 + beta_up );
+
+N = 500;
+
+A = repmat((0:N)',1,N+1)';
+Aprime = A';
+nA = size(A,1);
+
+pipe_age  =  28*12;
+
+loan_term = 8;
+r = .05/12;
+
+Q0_CS = 161 ;
+Q0_PS = 131 ;
+total_loan = 17021;
+
+[h,v,v_PS,v_CS]=sim_reps(Q0_PS,Q0_CS,pipe_age,total_loan,r,loan_term,nA,Aprime,A,beta);
+
+h
+v(1,1)/1000
+v_PS(1,1)/1000
+v_CS(1,1)/1000
+
+results = zeros(size(CSt,1),4);
+
+for i=1:size(CSt,1)
+    
+    [ht,vt,v_PSt,v_CSt]=sim_reps(  PSt(i)  ,  CSt(i)  ,pipe_age,  TLt(i) ,r,loan_term,nA,Aprime,A,beta);
+    results(i,:) = [ht vt(1) v_PSt(1) v_CSt(1) ];
+    
+end
+
+[results(:,1) results(:,2:4)/1000]
+
+
+% [h]=sim_reps(Q0,Q1,F,Aprime,A,loan_term,beta);
+
+
+
+% pay=0;
+% for i=0:loan_term*12-1
+%     pay = pay + surplus_rec - slope_rec*i;
+% end
+% pay = pay/(loan_term*12);
+
+
+
+
+
+% 
+% decis=(decis-1)*inA + minA; %%% try to understand this better...
+% 
+% Amark = size(Agrid,1);
+% Athis = Agrid(Amark,1);        % initial level of assets        
+% states   = zeros(n-1,2);
+% controls = zeros(n-1,2);
+% for i = 1:n-1
+%     Aprime = decis(Amark,chain(i));
+%     Amark  = tdecis(Amark,chain(i));
+%     
+%     [~,~,~,~,cons1,cons2,cons3,cons4] = ...
[…]

### 2020-12-14 phil_subcode/reps_pa_5.m

@@ -1,0 +1,205 @@
+
+
+loc = '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/';
+
+
+ 
+
+M   = csvread(strcat(loc,'mat_counter.csv'),1);
+% NRW = csvread(strcat(loc,'mat_counter_nrw.csv'),1);
+NRW = 117.*ones(size(M,1),1);
+CSt = M(:,1) + M(:,2);
+PSt = M(:,3) + NRW;
+TLt = M(:,4);
+Wm  = M(:,5);
+We  = M(:,6);
+Wbar=.2;
+
+MC = csvread(strcat(loc,'mat_counter_comm.csv'),1);
+PSc = MC(:,1).*MC(:,2);
+
+PSt=PSc+PSt;
+
+
+% CSe BSe Ae CPe 
+
+%%% simulate every 30!
+
+
+beta_up = .04/12;
+beta = 1/( 1 + beta_up );
+
+N = 500;
+
+A = repmat((0:N)',1,N+1)';
+Aprime = A';
+nA = size(A,1);
+
+pipe_age  =  28*12;
+
+loan_term = 5;
+r = .05/12;
+
+Q0_CS = 161 ;
+Q0_PS = 131 ;
+total_loan = 17021;
+
+wbar=0;
+t=0;
+wm=0;
+we=0;
+
+alt = 10*12;
+
+%%% TEST FULL WELFARE
+welfare=1;
+
+[h,v,v_PS,v_CS] = sim_reps_pa(welfare,Q0_PS,Q0_CS,pipe_age,total_loan,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t, NRW(1) )
+h
+v(1,1)/1000
+v_PS(1,1)/1000
+v_CS(1,1)/1000
+
+%%%% FULL WELFARE %%%%
+
+welfare=1;
+
+results = zeros(size(CSt,1),4);
+results_alt = zeros(size(CSt,1),4);
+
+for i=1:size(CSt,1)
+    [ht,vt,v_PSt,v_CSt]=sim_reps_pa(welfare,  PSt(i)  ,  CSt(i)  ,  pipe_age,  TLt(i)  ,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t, NRW(i) );
+    results(i,:) = [ht vt(1) v_PSt(1) v_CSt(1) ];
[…]

### 2020-12-14 phil_subcode/sim_reps_pa.m

@@ -1,0 +1,175 @@
+function [h,v,v_PS,v_CS]=sim_reps_pa(welfare,Q0_PS,Q0_CS,pipe_age,total_loan,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t,NRW)
+ 
+sim_length= nA;
+
+Q1_CS = Q0_CS/pipe_age;
+Q1_PS = Q0_PS/pipe_age;
+
+d = (((1+r)^(12*loan_term))-1)/(r*(1+r)^(12*loan_term));
+F  = total_loan/d;
+
+util1_PS =  (Q0_PS - A.*Q1_PS - F).*(Aprime==0 & A>=loan_term*12) + ...
+            (Q0_PS - A.*Q1_PS - F).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
+            (Q0_PS - A.*Q1_PS).*(Aprime==A+1 & Aprime>=loan_term*12) + ...
+            -1000000.*(1-((Aprime==0 & A>loan_term*12)+(Aprime==A+1)));
+
+util1_NRW = (NRW - (A.*NRW./pipe_age) - F).*(Aprime==0 & A>=loan_term*12) + ...
+            (NRW - (A.*NRW./pipe_age) - F).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
+            (NRW - (A.*NRW./pipe_age)).*(Aprime==A+1 & Aprime>=loan_term*12) + ...
+            -1000000.*(1-((Aprime==0 & A>loan_term*12)+(Aprime==A+1)));
+
+util1_CS =  (Q0_CS - A.*Q1_CS ).*(Aprime==0 & A>=loan_term*12) + ...
+            (Q0_CS - A.*Q1_CS ).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
+            (Q0_CS - A.*Q1_CS ).*(Aprime==A+1 & Aprime>=loan_term*12) + ...
+            -1000000.*(1-((Aprime==0 & A>loan_term*12)+(Aprime==A+1)));
+
+    
+v    = zeros(nA,1);
+v_PS = zeros(nA,1);
+v_CS = zeros(nA,1);
+decis   = zeros(nA,1);
+
+
+% t=3000;
+% wbar=.1;
+% welfare=2;
+
+
+%%%% quality standard %%%%
+
+if welfare==2 || welfare==4
+    v = zeros(1,sim_length);
+    v_PS = zeros(1,sim_length);
[…]

### 2020-12-14 phil_subcode/sim_reps_ror.m

@@ -1,0 +1,185 @@
+function [h,v,v_PS,v_CS]=sim_reps_ror(welfare,Q0_PS,Q0_CS,pipe_age,total_loan,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t,NRW)
+
+sim_length= nA;
+
+Q1_CS = Q0_CS/pipe_age;
+Q1_PS = Q0_PS/pipe_age;
+
+d = (((1+r)^(12*loan_term))-1)/(r*(1+r)^(12*loan_term));
+F  = total_loan/d;
+
+
+
+PSt = Q0_PS - A.*Q1_PS - F;
+
+util1_ROR =  ror.*F.*(PSt>=ror.*F).*(Aprime==0 & A>=loan_term*12) + ...
+            (Q0_PS - A.*Q1_PS - F).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
+            (Q0_PS - A.*Q1_PS).*(Aprime==A+1 & Aprime>=loan_term*12) + ...
+            -1000000.*(1-((Aprime==0 & A>loan_term*12)+(Aprime==A+1)));
+        
+        
+util1_PS =  (Q0_PS - A.*Q1_PS - F).*(Aprime==0 & A>=loan_term*12) + ...
+            (Q0_PS - A.*Q1_PS - F).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
+            (Q0_PS - A.*Q1_PS).*(Aprime==A+1 & Aprime>=loan_term*12) + ...
+            -1000000.*(1-((Aprime==0 & A>loan_term*12)+(Aprime==A+1)));
+
+util1_NRW = (NRW - (A.*NRW./pipe_age) - F).*(Aprime==0 & A>=loan_term*12) + ...
+            (NRW - (A.*NRW./pipe_age) - F).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
+            (NRW - (A.*NRW./pipe_age)).*(Aprime==A+1 & Aprime>=loan_term*12) + ...
+            -1000000.*(1-((Aprime==0 & A>loan_term*12)+(Aprime==A+1)));
+
+util1_CS =  (Q0_CS - A.*Q1_CS ).*(Aprime==0 & A>=loan_term*12) + ...
+            (Q0_CS - A.*Q1_CS ).*(Aprime==A+1 & Aprime<loan_term*12) + ... 
[…]

### 2021-01-04 phil_paper/paper_booster_pumps_wjv.tex
empirical strategy looks good

@@
 
-As a pioneer in water infrastructure investments among developing cities, Manila provides a useful context to study the welfare effects of these types of investments.
-In 1997, Manila awarded private concession contracts to two private companies to take over for the existing public utility.
-Each company is assigned to provide water to their assigned halves of Metro Manila.
-Both companies have gradually replaced the decaying pipe infrastructure inherited from the public utility.
+As a pioneer in water infrastructure investments among developing cities, Manila provides a useful context to study the welfare effects of these types of pipe replacements.
+Before 1997, a single government utility provided water to Manila resulting in low levels of service quality (\cite{dumol2000manila}).
+In 1997, Manila awarded private concession contracts to two private companies to take over for the public utility.
+Each company was assigned to provide water to their assigned halves of Metro Manila.
+The two companies are regulated by a government agency who sets the water tariff in order to ensure that the companies are able to cover their costs while earning a fair rate of return on their assets.
+The regulator also reserves the right to disallow costs that it views as inessential to water provision.
+Privatization led to large improvements in water access such that by 2015, piped water usage was almost universal.\footnote{Less than 2\% of households report using well water, water peddlers, or other alternative water sources for cooking according to the 2015 Census of Population and Housing.}  This paper analyzes data provided by one of the companies.
 
-To measure the effect of pipe replacements, one of the companies has provided a map of their water pipes including the installation year for each pipe as well as water billing records for their 1.5 million water connections from January, 2008 to June, 2015.
-To measure each water connection's exposure to pipe replacement projects, connections are first located within ``small areas'' --- the smallest geographic designations used by the company each containing around 270 connections.
-Next, since projects often replace many pipes in the same place at the same time, each small area is assigned a ``pipe replacement year'' according to the year when the greatest total length of tertiary pipes were installed within that small area.\footnote{Tertiary pipes installed in the replacement year account for 85\% of the total tertiary pipe length in small areas.}  Tertiary pipes act as local feeders transporting water from large primary and secondary pipes directly to households.
+In 2008 in agreement with the government regulator, the water company started aggressively replacing the decaying pipe infrastructure that it inherited from the public utility.
+Guided by hydrological concerns, the company separated the service area into smaller sections and replaced most pipes in each section on a sequential basis.
+The existing pipes were mostly installed between 1980 and 1990 with an average year of 1986.\footnote{DISCUSS APPENDIX ABOUT PIPE AGE.}  Between 2008 and 2015, the water company replaced over 57\% of its nearly 6,000 km of pipes.
+
+To measure the effect of pipe replacements, the company provided a map of their water pipes including the installation year for each pipe as well as water billing records for their 1.5 million water connections from January, 2008 to June, 2015.\footnote{Data is missing for the month of June, 2014.}  To measure each water connection's exposure to pipe replacement projects, connections are first located within ``small areas'' --- the smallest geographic designations used by the company with 2,976 total areas each containing around 270 connections.
+Next, since projects often replace many pipes in the same place at the same time, each small area is assigned a ``pipe replacement year'' according to the year when at least 80\% of the total length of tertiary pipes were installed within that small area.
+576 small areas are observed before and after their ``pipe replacement year.''  Tertiary pipes act as local feeders transporting water from large primary and secondary pipes directly to households.
 Therefore, tertiary pipe replacements likely affect service quality within local areas while primary and secondary pipe replacements may have diffuse impacts throughout the pipe network.
 By excluding primary and secondary pipe replacements, this approach limits the potential for spillover effects of pipe replacements onto neighboring areas at the cost of potentially underestimating the total welfare gains from these projects.
+% \footnote{Tertiary pipes installed in the replacement year account for 85\% of the total tertiary pipe length in small areas.}
 
 Billing records measure monthly water prices and usage for each water connection, which may serve multiple households.
-In order to link connection-level consumption to household welfare, billing records for each connection are merged to a survey of water connections conducted by an independent evaluator to monitor compliance with the water utility's service obligations.
-This connection survey records demographics for the household that owns the connection as well as the number of other households and people that also use the connection.
-Household-level water usage is calculated by dividing total connection usage by the number of households sharing the connection.
+In order to link connection-level consumption to household welfare, billing records for each connection are merged to a survey of residential water connections conducted by an independent evaluator to monitor compliance with the water utility's service obligations.\footnote{The billing records also cover commercial and industrial accounts.}  This connection survey records demographics for the household that owns the connection as well as the number of other households and people that also use the connection.
 The survey also includes household demographics for the connection owner, different measures of water service quality, as well as household investments in booster pumps, water filters, and water storage tanks.
+
+The main outcome of interest is household-level water usage, which is calculated by dividing total connection usage by the number of households sharing the connection.
+Outlier months with over 200 m3 of consumption are excluded from the analysis.
+All empirical results are weighted at the household-level to ensure that results are representative of the population of households.
 
@@
 Because a similar sampling design was followed across survey rounds, 13\% of connections were interviewed in two years, and 1.4\% of connections were interviewed in three years while remaining connections were interviewed in only one year.
-Since billing records form a monthly-panel, survey responses must be interpolated
+The connection survey is merged to the billing records by the connection id number and the interview month.
+For billing-record months without corresponding interviews, survey responses are interpolated with responses from the most recent interview.
 
-Since billing records are
+Since households face an increasing block water tariff, the average water price faced by households is calculated as the average  amount paid per cubic meter of water usage for each calendar month and tariff category after dropping outlier values below 5 PhP/m3 and above 100 PhP/m3.\footnote{Households either face a standard tariff or a high-price tariff depending on whether they are observed with business activities at their residence.
+See Section~\ref{section:descriptives} for more discussion.}  Outliers are often due to billing credits/errors.
+To measure savings from pipe replacements, the water company also provided records of project costs as well as the quantity of water supplied, which often exceeds the quantity of water billed.
+These attributes are measured according to ``district metering areas,'' which are around three times larger than small areas and are delineated based on hydrological considerations in order to monitor water loss.
 
-To examine household demographics, billing data are merged at the connection-level to a water connection survey conducted independently to monitor the quality of the utility's service.
+% DISCUSS NRW AND COMM ACCOUNTS HERE!!
 
-\footnote{Households using connections alone tend to be larger and wealthier than households that share connections with other households according to previous research (\cite{wjv}).}
+% MENTION LATER!: The billing records also measure consumption for commercial and industrial connections, which are used to measure
+
+% A household panel survey from Pasay City provides information on household income dynamics in Manila.
+Pasay City is a centrally located sub-municipality of Metro Manila accounting for 3.2\% of the population of Metro Manila as of 2015 and is roughly representative of households living in the utility's service area.
+The panel survey covers over 60\% of the population of Pasay City and is the only survey to provide a household-level income panel over a similar time frame in Manila.
+The analysis includes data from \input{tables/total_inc_hhs_all}households that were interviewed in both 2008 and 2011.
+
+% MEASURING AVERAGE PRICES
+
+% To examine household demographics, billing data are merged at the connection-level to a water connection survey conducted independently to monitor the quality of the utility's service.
+
+% \footnote{Households using connections alone tend to be larger and wealthier than households that share connections with other households according to previous research (\cite{wjv}).}
 
@@
 % This sample restriction ensures that connection-level is equal to household-level.
-
-The water connection survey also includes measures
-
-Additional survey data also includes information on demographics and water quality as well as investments!
-
-Water pipes are linked to areas... 
-The utility locates water connections within small areas each containing around 270 connections.
-
-Each small-area is assigned a pipe replacement year as the year when the greatest total length of tertiary pipes are installed within the small area.   This pattern is consistent with
-
-  This calculation includes only tertiary pipes (excluding )
-
- which allows for linking
-
-The pipe map documents the installation year for each length of pipe, which forms the basis for the pipe replacement measure.   The
 
@@
 
-% A household panel survey from Pasay City provides information on household income dynamics in Manila.
-Pasay City is a centrally located sub-municipality of Metro Manila accounting for 3.2\% of the population of Metro Manila as of 2015 and is roughly representative of households living in the utility's service area.
-The panel survey covers over 60\% of the population of Pasay City and is the only survey to provide a household-level income panel over a similar time frame in Manila.
-The analysis includes data from \input{tables/total_inc_hhs_all}households that were interviewed in both 2008 and 2011.
+% Section: Data
 
-Section: Data
+	% - only households connected earlier (explain) (what share are those?!)
+	% - consumption per HH
+	% - reweight data for household level?! YES!
+	% - survey panel and other panel; date representation, how its imputed, etc.
+	% - Put in a table describing pipe-replacement; describe staggered approach; predict pipe-replacement?
+	% - industrial/commercial footnote later!!
 
-	- only households connected earlier (explain) (what share are those?!)
-	- consumption per HH
-	- reweight data for household level?! YES!
-	- survey panel and other panel; date representation, how its imputed, etc.
-	- Put in a table describing pipe-replacement;  describe staggered approach; predict pipe-replacement?
-	- industrial/commercial footnote later!!
+% Consumption is measured according to average consumption for not-shared households!  What extra assumption is that!!!  NEED ROBUSTNESS!!!
 
-Consumption is measured according to average consumption for not-shared households!  What extra assumption is that!!!  NEED ROBUSTNESS!!!
-
-MEASURING AVERAGE PRICES
-
-\section{Descriptives}
+\section{Descriptives}\label{section:descriptives}
 
 Descriptive evidence indicates that fixing pipes improves water pressure, quality, and reliability, which may each affect consumer welfare.
-Table~\ref{table:descriptives} tracks water service improvements by comparing average household survey responses before and after pipe replacement.
-[summarize the findings]
+Table~\ref{table:descriptives} tracks water service improvements by comparing average household survey responses before and after pipe replacement for areas that are observed both before and after.\footnote{Areas that may have experienced pipe replacements before the start of the sample are included in the ``All'' category.}  The share of households reporting strong water pressure during peak evening usage from 6pm to 12am increases from 25\% to 58\% after pipe replacements.
+Likewise, the share reporting no pressure over the same interval decreases from 29\% to 4\%.
+Water interruptions decline slightly from 2.28 to 1.93 in the last three months, which is consistent with the water company facing periodic droughts.
+Water quality shows large improvements with the share of respondents reporting discolored, unusual tasting, or contaminated water dropping by at least 5 percentage points for each measure.
 
-Consumers also invest in products and behaviors to compensate for low piped water service quality.
+Households often invest in products and behaviors to compensate for low piped water service quality.
 These investments help reveal which aspects of piped water service are most valuable to consumers as well as most affected by pipe replacement.
 
-Large investments in booster pumps suggest that households strongly value water pressure.
+Large investments in booster pumps suggest that households strongly value water pressure and reliability.
 Booster pumps are both expensive to purchase and operate.
@@
 In 2012, tariffs for the electricity utility in Manila averaged around 8.8 PhP per KwH.}
-Small investments in water filters combined with frequent purchases of filtered water both before and as well as after pipe replacement indicate that households may not derive large benefits from improvements in piped water quality.
+
+Small investments in water filters combined with frequent purchases of filtered water both before and as well as after pipe replacement indicate that households may derive fewer benefits from improvements in piped water quality.
 Only 12\% of households use water filters both before and after pipe replacements.
@@
 Rapid water flow allows households to complete a greater number of water-using activities like cleaning and bathing in the same amount of time.
-Greater water pressure may also allow households to engage in new activities that require minimum pressure levels such as showering.\footnote{By contrast, water quality improvements may have an ambiguous effect on water consumption.
-On one hand, cleaner water may induce households to use more tap water for cooking and cleaning.
-On the other hand, cleaner water may increase the productivity of cleaning and bathing, which may lead households to use less piped water.}  Figure~\ref{figure:pipecons} plots average monthly water usage per household in the 4 years before and 6 after pipe replacement.
+Greater water pressure may also allow households to engage in new activities that require minimum pressure levels such as showering.
+Cleaner water may induce households to use more tap water for cooking and cleaning.
+Figure~\ref{figure:pipecons} plots average monthly water usage per household in the 4 years before and 6 after pipe replacement.
 Usage increases from an average of \input{tables/c_pre}m3 before pipe replacement to \input{tables/c_post}m3 after pipe replacement, which represents an \input{tables/c_diff_per}\unskip\% increase.
 The increase in usage occurs abruptly at the year of pipe replacement and remains at roughly the same level in the following 6 years.
-This sustained increase in consumption suggests that pipe replacement may provide sustained impacts on household welfare.
+This sustained increase in consumption suggests that pipe replacements may provide long-term impacts on household welfare.
 
 The absence of strong pre-trends in usage suggests that replacement projects are not targeted to areas with particular trends in local water demand.
-Instead, this pattern is consistent with the company's stated goal of sequentially replacing old pipes according to engineering specifications.
+Instead, this pattern is consistent with the company's stated goal of sequentially replacing old pipes according to hydrological specifications.
 Table~\ref{table:descriptives} further supports this theory by indicating few demographic differences between households that receive pipe replacement projects (columns (1) and (2)) and all households (column (3)).
@@
 Prices are determined by the government regulator who imposes an increasing tariff schedule according to monthly usage, which is standard among public utilities (\cite{hoque2013state}).
-Despite steep increases in marginal price at specific levels of usage, households do not appear to be sensitive to these price changes because households are not observed adjusting their consumption strategically to avoid higher prices (cite appendix).
-The regulator also increases prices gradually over time to ensure that the company continues to cover operating costs.
-Since households also gradually increase their average usage over this interval, it is unclear whether households are responsive to these price increases (cite appendix).
+Despite steep increases in marginal price at specific levels of usage, households do not appear to be sensitive to these price changes because households are not observed adjusting their consumption strategically to avoid higher prices.\footnote{Appendix Figure~\ref{figure:tariffschedule} includes the average tariff schedule for users facing low and high prices.
+Appendix Figure~\ref{figure:conshist} includes a histogram of usage per connection and finds little evidence of significant bunching at the tariff kink points at 10, 20, and 40 m3.}  The regulator also increases prices gradually over time to ensure that the company continues to cover operating costs.
+Since households also gradually increase their average usage over this interval, it is unclear whether households are responsive to these price increases.\footnote{Appendix Figure~\ref{figure:pricetimeseries} plots average prices and usage per household over time.}
 
-[ RE-WRITE WITH NEW DEFINITION! ]
-The government regulator also gives the water company discretion to assign households to a high-price tariff schedule if they have any business activity at their residence, which provides a novel source of price variation in the context of public utilities.
+% [ RE-WRITE WITH NEW DEFINITION! ]
+The empirical exercise analyzes an event-study where the same households are exposed to very different price levels over time.
+The government regulator gives the water company discretion to assign households to a high-price tariff schedule if they have any business activity at their residence, which provides a novel source of price variation in the context of public utilities.
 In the vast majority of cases, the high price tariff is applied to households that operate small food stands (or ``Sari-Sari'' stores).
-For a household with average monthly usage, the high-price tariff results in an average price of \input{tables/p_s}PhP/m3 while the regular tariff results in an average price of \input{tables/p_r}PhP/m3 (cite appendix for tariff).
-The water company periodically visits consumers and updates prices according to the activities observed at each consumer's residence.
-In some cases, consumers request price changes, which prompts the company to investigate the household and determine the appropriate price.
-Table~\ref{table:pricechangestatistics} provides average characteristics of households that are always observed with the regular price (in column (1)), that are always observed with the high price (in column (2)), and that are observed changing prices during the sample (in column (3)).
-While the 2,442 households that experience price changes use more water than other households, they share similar demographic characteristics, which suggests that they may also share similar price-sensitivities.
+For a household with average monthly usage, the high-price tariff results in an average price of \input{tables/p_s}PhP/m3 while the regular tariff results in an average price of \input{tables/p_r}PhP/m3.\footnote{Appendix~\ref{figure:tariffschedule} plots the tariff.}  The water company occasionally visits consumers and assigns consumers to the high-price tariff if business activity is observed at the residence.\footnote{In some cases, consumers request price decreases when they close their businesses.
+These price-decrease events are not the focus of the analysis because consumers directly anticipate these events and may otherwise have adjusted their water usage accordingly.}  Table~\ref{table:pricechangestatistics} provides average characteristics of households that are observed with the regular price (in column (1)), that are observed with the high price (in column (2)), and that are observed increasing prices during the sample (in column (3)).
+While the 724 households that experience price increases use more water than other households, they share similar demographic characteristics, which suggests that they may also share similar price-sensitivities.
 
-Figure~\ref{figure:usagepricechanges} plots average usage 4 years before and after households are switched from the regular price to the high price (in red) as well as before and after households are switched from the high price to the regular price (in blue).
-Before the price change, average usage for both groups follows relatively constant trends.
-The price change is associated with a usage jump for households switched to the regular price and a corresponding usage slide for households switched to the high price.
-The changes in consumption appear relatively persistent up to 4 four years after the price changes.
-These patterns indicate that household water usage is sensitive to large, discrete price changes.
+Figure~\ref{figure:usagepricechanges} plots average usage and marginal prices 4 years before and after households are first switched from the regular price to the high price.\footnote{In very few cases, households are later switched back to the regular price, and then switched again to the high price.}  Before the price change, average usage increases likely due to some households using additional water for their small-businesses.
+The price change at month 0 is associated with a sharp drop in usage and increase in average prices that persist for at least 24 months.
+These patterns indicate that household water usage is sensitive to large, discrete price changes over time.
 
@@
 \caption{Usage and Price Changes}\label{figure:usagepricechanges}
-\includegraphics[scale=1]{tables/r_to_s_graph.pdf}
+\includegraphics[scale=1]{tables/r_to_s_only_graph.pdf}
 \end{center}
@@
 \end{align}
-where $w$ is water consumption and $x$ represents a bundle of all other goods consumed by the household.
+where $w$ is water usage and $x$ represents a bundle of all other goods consumed by the household.
 Water service quality given by the function, $Q(B,R)$, depends on booster pump use where $B$ equals 1 if the household chooses to use a booster pump (and zero otherwise) and as well as pipe replacements where $R$ equals 1 after pipe replacement (and zero otherwise).
 $Q(B,R)$ is assumed to be differentiable in $R$.
-Water service quality enters multiplicatively with water consumption, which nests the assumption that each unit of water consumption is affected equally and positively by water service quality.
-This assumption also excludes the possibility that improved water service quality affects household utility in ways that are not directly proportional to household water consumption such as by increasing housing values.
+Water service quality enters multiplicatively with water usage, which nests the assumption that each unit of water usage is affected equally and positively by water service quality.
+This assumption also excludes the possibility that improved water service quality affects household utility in ways that are not directly proportional to household water usage such as by increasing housing values.
 In this case, the approach would underestimate the welfare benefits of improved service quality.
 $\alpha$ reflects price sensitivity, and $\gamma$ reflects the satiation amount of water usage.
-This approach assumes that preferences for water are quasi-linear, which implies that water consumption does not depend on household income [ Footnote to heterogeneity table ].
+This approach assumes that preferences for water are quasi-linear, which implies that water usage does not depend on household income [ Footnote to heterogeneity table ].
 
@@
 where $p$ is the average price of water while the price of all other goods, $x$, is normalized to 1.
-This approach includes the simplifying assumption that households respond to a single, average water price $p$ despite facing marginal prices that increase with monthly consumption.
-This assumption is consistent with descriptive evidence that households appear unresponsive to marginal prices (cite appendix).
-$F$ is total cost of renting and using a booster pump each month.
-This approach assumes that Manila has a competitive market for renting/selling booster pumps that is unaffected by improvements in piped water service quality.\footnote{This assumption is consistent with local service quality improvements and a city-wide market for booster pumps.}  $Y$ is monthly household income.
+This approach includes the simplifying assumption that households respond to a single, average water price $p$ despite facing marginal prices that increase with monthly usage.
+This assumption is consistent with descriptive evidence that households appear unresponsive to marginal prices.\footnote{Appendix Figure~\ref{figure:conshist} includes a histogram of usage per connection and finds little evidence of significant bunching at the tariff kink points at 10, 20, and 40 m3.}   $F$ is total cost of renting and using a booster pump each month.
+This approach assumes that Manila has a competitive market for renting and selling booster pumps that is unaffected by improvements in piped water service quality.\footnote{This assumption is consistent with local service quality improvements and a city-wide market for booster pumps.}  $Y$ is monthly household income.
 
@@
 \label{eq:demand}
-w^{*} \, = \, \gamma \, - \, \alpha p +  Q(B,R)
+w(B) \, = \, \gamma \, - \, \alpha p +  Q(B,R)
 \end{align}
@@
 
-Given optimal water demand, the indirect utility function at the optimal booster pump choice, $B^{*}$, is given by 
+Given optimal water demand, the indirect utility function at a given booster pump choice, $B$, is given by 
 \begin{align}
-V\,=\,\frac{\alpha p^2}{2} - \gamma p + \frac{Q(B^{*},R)^{2}}{2\alpha} - p Q(B^{*},R) + \frac{\gamma Q(B^{*},R)}{\alpha} + y - B^{*} F
+V(B)\,=\,\frac{\alpha p^2}{2} - \gamma p + \frac{Q(B,R)^{2}}{2\alpha} - p Q(B,R) + \frac{\gamma Q(B,R)}{\alpha} + y - B F
 \end{align}
 The derivative of $V$ with respect to pipe replacements, $R$, reflects the change in consumer welfare associated with pipe replacements.
-This derivative takes the following form after substituting terms for $w^{*}$
+This derivative takes the following form after substituting terms for $w(B)$
 \begin{align}
 \label{eq:dvdr}
-\frac{dV}{dR}\,=\,\frac{w^{*}}{\alpha} \frac{dQ}{dR} - F \frac{dB^{*}}{dR}
+\frac{dV(B)}{dR}\,=\,\frac{w(B)}{\alpha} \frac{dQ}{dR} - F \frac{dB}{dR}
 \end{align}
-This expression summarizes the consumer welfare effects of pipe replacements in terms of (1) the marginal effect on service quality weighted by water consumption and price sensitivity as well as (2) the marginal effect on booster pump usage weighted by the cost of booster pumps.
-This approach assumes that welfare effects are proportional to consumption, $w^{*}$, implying that service quality improvements affect all units of water consumption.
+This expression summarizes the consumer welfare effects of pipe replacements in terms of (1) the marginal effect on service quality weighted by water usage and price sensitivity as well as (2) the marginal effect on booster pump usage weighted by the cost of booster pumps.
+This approach assumes that welfare effects are proportional to usage, $w^{*}$, implying that service quality improvements affect all units of water usage.
 Welfare effects are decreasing in price sensitivity, $\alpha$, which captures the intuition that households with many substitute water sources (ie.
 high $\alpha$) may benefit less from improvements in service quality.
-According to this approach, welfare changes do not require measuring fixed preferences, $\gamma$, separately from levels of service quality, $Q(B^{*},R)$.
-Therefore, this approach is robust to different patterns of selection into booster pump use based on different levels of service quality or fixed preferences for water consumption.
+According to this approach, welfare changes do not require measuring fixed preferences, $\gamma$, separately from levels of service quality, $Q(B,R)$.
+Therefore, this approach is robust to different patterns of selection into booster pump use based on different levels of service quality or fixed preferences for water usage.
 
@@
 
-The estimation strategy recovers household price sensitivity as well as the changes in service quality and booster pump use in response to pipe replacement projects.
-These estimated quantities along with observed water use and booster pump costs summarize the change in consumer welfare from pipe replacement projects as given by equation (\ref{eq:dvdr}).
-The estimating equation takes the following form
+The empirical strategy estimates household price sensitivity as well as changes in water usage and booster pump use in response to pipe replacement projects.
+These estimated quantities inform the effect on consumer welfare of pipe replacement projects given by equation (\ref{eq:dvdr}).
+Using an instrumental variables approach, the empirical strategy isolates price variation from connections being switched into high price tariffs.
+The first stage equation takes the following form
 \begin{align}
-\label{eq:esteq}
-y_{itl} \,=\, \beta_1 \, \text{After Pipe Replacement}_{tl} \,+\, \beta_2 \, p_{it} \, + \, \theta_t \, + \, \lambda_i \, + \epsilon_{itl}
+\label{eq:1ststage}
+p_{it} &= \phi_1 \text{Post Pipe}_{tl}  +  \phi_2 \text{Post Price}_{it} +  \phi_3\text{Pre Trend}_{it} +\phi_4 \, \text{Post Trend}_{it} +  \phi_t  +  \phi_{il} + \epsilon_{itl} 
 \end{align}
-where the outcome, $y_{itl}$, is either monthly water consumption or booster pump use.
-Outcomes are measured for household, $i$, in small area, $l$, at calendar month, $t$.
-After Pipe $\text{Replacement}_{tl} $ takes a value of one for months after pipe replacement and zero otherwise.
-Since the data identify only the year that pipes were replaced, all months from the replacement year onwards are considered after pipe replacement.
-$p_{it}$ measures the average price faced by each household in each month.
-$\theta_t$ includes calendar month fixed effects while $\lambda_i$ includes household fixed effects.
+where $i$ indexes the water connection, $t$ indexes calendar month, and $l$ indexes small area.
+$p_{it}$ is the average price per cubic meter of monthly water use.
+$\text{Post Pipe}_{tl}$ is an indicator for months during and after January of the pipe replacement year.
+$\text{Post Price}_{it}$ is an indicator for months after a connection is first switched into a high-price tariff.\footnote{In rare instances, connections may be switched into high-price tariffs more than once during the study period.
+The instrumental variables design ensures that the estimation uses price variation only from the first price increase, which is more likely to be unexpected by households than later price increases.}  $\text{Post Price}_{it}$ is the instrumental variable that is excluded in the second stage.
+To account for trends in water usage around the time of the price change, $\text{Pre Trend}_{it}$ counts the months leading up to the first price increase and takes a value of zero otherwise.
+Likewise, $\text{Post Trend}_{it}$ counts months after the first price increase and takes a value of zero otherwise.
+$\phi_t$ are calendar month fixed effects.
+$\phi_{il}$ are connection fixed effects when the second stage has water usage as an outcome.
+$\phi_{il}$ are small-area fixed effects when the second stage has booster pump use as an outcome because booster pump use is only observed in months where the connection survey was fielded.
 
-When the outcome is monthly water consumption, the estimating equation maps directly onto the equation for optimal household consumption given by equation ($\ref{eq:demand}$).
+Given predicted prices from the first stage equation, the second stage equations take the following form
+\begin{align}
+w_{itl} &= \gamma_1  \text{Post Pipe}_{tl} + \gamma_2  \hat{p}_{it} + \gamma_3\text{Pre Trend}_{it} +\gamma_4\text{Post Trend}_{it} +    \gamma_t +  \gamma_i +  \varepsilon_{itl}  \label{eq:2ndstage1} \\
+b_{itl} &= \beta_1  \text{Post Pipe}_{tl} + \beta_2  \hat{p}_{it} + \beta_3\text{Pre Trend}_{it} +\beta_4\text{Post Trend}_{it} +    \beta_t +  \beta_l +  \varepsilon_{itl} \label{eq:2ndstage2}
+\end{align}
+where $w_{itl}$ is water usage per household in cubic meters per month and $b_{itl}$ is an indicator for connection booster pump usage.
+
+The coefficients of interest for the impacts of pipe replacement are given by $\gamma_1$ and $\beta_1$ for water and booster pump use respectively.
+After controlling for calendar month and connection fixed effects, these coefficients are identified from differential changes in outcomes for areas that experienced pipe replacements compared to areas that did not over the same interval.
+These coefficients reflect the causal effect of pipe replacements under the assumption that no other factors changed at the same time that would otherwise affect the outcomes.
+This assumption is supported by qualitative evidence that pipe replacements are often driven by hydrological, engineering concerns rather than strategic responses to changes in local water demand or other consumer characteristics.
+Supporting this assumption, Figure~\ref{figure:pipecons} traces a sharp break in average usage at the year of pipe replacement with little evidence of strong trends before or after replacement projects.
+
+The effects of prices on outcomes are given by $\gamma_2$ and $\beta_2$ for water and booster pump use respectively where $\hat{p}_{it}$ is the predicted price from the equation (\ref{eq:1ststage}).
+The effects are identified from changes just before and after connections are switched to a high-price tariff after controlling for trends leading up to and after the tariff change.
+The validity of this instrumental variables approach requires both that the tariff change produces a large impact on prices and that no other factors affect demand for water or booster pumps at the same time as the price change.
+This approach assumes that while households may increase their water usage as they start small home businesses, households are unable to anticipate the exact timing of the price change so that any changes in water usage in the months just following the price change can be attributed to the higher prices.
+Figure~\ref{figure:usagepricechanges} traces a smooth, increasing trend leading up to the price change.
+Usage then drops abruptly at the same time as the price change, consistent with a surprise increase in prices.
+
+The estimated coefficients directly inform the expression for welfare in equation (\ref{eq:dvdr}).
+According to equation (\ref{eq:demand}), water quality linearly affects water demand.
+Therefore, by capturing the effect of pipe replacements on water demand, $\gamma_1$ measures the total change in water quality from pipe replacements, $\frac{dQ}{dR}$.
+$\beta_1$ measures the reduced form impact of pipe replacements on booster pump usage, $\frac{dB}{dR}$.
+
+The remaining term to be estimated in equation (\ref{eq:dvdr}) is the price sensitivity, $\alpha$.
+$\gamma_2$ captures the reduced form effect of prices on water usage.
+By taking the derivative of equation (\ref{eq:1ststage}) with respect to price, this effect can be expressed as a function of the price sensitivity as well as the effect of price on water quality through endogenous changes in booster pump use, according to the following equation
+\begin{align*}
+  \gamma_2 = \alpha +  \frac{dQ}{dB} \frac{dB}{dp}
+\end{align*}
+where $\frac{dQ}{dB}$ is the effect of booster pump use on water quality, which is unobserved.
+$\frac{dB}{dp}$ is the effect of prices on booster pump use, which is estimated by $\beta_2$.
+If $\frac{dB}{dp}$ is zero, then the expression reduces to $\gamma_2=\alpha$.
+Although the booster pump decision is not explicitly modeled, $\frac{dB}{dp}$ may be zero or close to zero when booster pump use is primarily driven by other factors besides the price of water.
+For example, booster pumps may be a perfect substitute for water quality such that all households below a certain water quality level choose to use booster pumps while all households above this level do not use booster pumps.
+In this example, the booster pump decision is orthogonal to water prices.
+
+Given fixed effects the are identified from
+
+When the outcome is monthly water usage, the estimating equation maps directly onto the equation for optimal household usage given by equation ($\ref{eq:demand}$).
 $\beta_1$ captures the effect of pipe replacement on service quality, $\frac{dQ}{dR}$.
@@
 Remaining fixed preferences for water and levels of service quality are absorbed in household and month fixed effects, $\lambda_i$ and $\theta_t$.
-These fixed effects ensure that the effect of pipe replacements is identified from variation in water consumption for the same household before and after pipes are fixed while accounting for any temporal consumption patterns common to all households.
+These fixed effects ensure that the effect of pipe replacements is identified from variation in water usage for the same household before and after pipes are fixed while accounting for any temporal usage patterns common to all households.
 Likewise, price sensitivity is estimated from variation in price for the same household switching between regular and high prices.
 Calendar month fixed effects absorb price variation affecting all households equally over time as the company updates water tariffs.
-
-Identifying $\beta_1$ and $\beta_2$ requires assuming that pipe replacements and household-specific price changes are not correlated with any other factors that may also affect water demand at the same time.
-One concern may be that pipe improvements are paired with other infrastructure investments that drive increases in local income, population, and water demand.
-Alternatively, the water company may strategically target pipe improvements to either boost areas with declining demand or accelerate areas with growing demand.
-Figure~\ref{figure:pipecons} traces a sharp break in average usage at the year of pipe replacement with little evidence of strong trends before or after replacement projects.
-These patterns are consistent with company reports that pipe replacements were not explicitly linked to other infrastructure projects and were instead planned primarily to minimize engineering costs.
-
-Another concern is that households may increase their water demand as they are switched to the high price because they often open roadside food-stands.
-Conversely, households that close their roadside food-stands may decrease their consumption at the same time as they are switched to the low price.
-Both cases suggest that the empirical approach would underestimate household price sensitivities.
-Figure~\ref{figure:usagepricechanges} provides little evidence of strong pre-trends leading up to price changes.
-While this evidence is suggestive that these events are uncorrelated with long-term trends in water demand, this approach is unable to exclude the possibility that other factors may influence water demand at the same time as these events.
 
@@
 Pipe replacements occur in small geographic areas while markets for booster pumps are likely to cover much wider areas.\footnote{Online markets span the entire city.}  Therefore, individual pipe replacement projects are unlikely to influence prices for booster pumps.
+
+% \begin{align}
+% \label{eq:1ststage}
+% p_{it} &= \phi_1 \text{Post Pipe Rep}_{tl}  +  \phi_2 \text{Post Price Inc}_{it} +  \phi_3\, t\text{ Post Price Inc}_{it} +\phi_4 \,t \,\text{Pre Price Inc}_{it} +  \phi_t  +  \phi_i + \epsilon_{itl}
+% \end{align}
+% \begin{align}
+% \label{eq:1ststage}
+% p_{it} &= \phi_1 \mathbbm{1} \{t\geq \text{Pipe Rep}_{tl}  \} +  \phi_2 \mathbbm{1} \{t\geq \text{High Price}_{tl}  \} +  \phi_3\, t \, \{t\geq \text{High Price}_{tl}  \} +\phi_4 \,t \,\{t< \text{High Price}_{tl}  \} +  \phi_t  +  \phi_i + \epsilon_{itl}
+% \end{align}
+% The estimating equation takes the following form
+% \begin{align}
+% \label{eq:esteq}
+% y_{itl} \,=\, \beta_1 \, \text{After Pipe Replacement}_{tl} \,+\, \beta_2 \, p_{it} \, + \, \theta_t \, + \, \lambda_i \, + \epsilon_{itl}
+% \end{align}
+% where the outcome, $y_{itl}$, is either monthly water usage or booster pump use.
+Outcomes are measured for household, $i$, in small area, $l$, at calendar month, $t$.
+After Pipe $\text{Replacement}_{tl} $ takes a value of one for months after pipe replacement and zero otherwise.
+Since the data identify only the year that pipes were replaced, all months from the replacement year onwards are considered after pipe replacement.
+$p_{it}$ measures the average price faced by each household in each month.
+$\theta_t$ includes calendar month fixed effects while $\lambda_i$ includes household fixed effects.
 
@@
 Column (1) provides results on household water use finding an increase of 1.79 m3 per household per month after pipe replacement.
-The estimate is statistically significant at the 1\% and economically large representing an 8\% increase in average consumption.
+The estimate is statistically significant at the 1\% and economically large representing an 8\% increase in average usage.
 The estimated increase is smaller than the descriptive increase in Figure~\ref{figure:pipecons} likely because the regression approach controls for increasing trends in water use over the sample period.
@@
 The following counterfactuals identify the welfare effects of optimal pipe replacements under five different information environments.
-The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
+The counterfactuals focus on the role of pipe replacements by holding fixed other aspects of water utility regulation.
+The full population of Manila is assumed to remain connected to service indefinitely.
+The water tariff is assumed to be determined independently of pipe replacements and to exactly cover all costs of water production (except pipe replacements).
+Unless otherwise specified, any cost savings or cost overruns as a result of the pipe replacements are assumed to be passed on to consumers in the form of fixed rebates or charges, which do not affect consumers' marginal incentives to consume water.
+Pipe replacements are assumed to be independent of operating costs such as labor or maintenance expenditures.
+
+% The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
 In the \textit{regular-replacement} counterfactual, the regulator simply replaces all pipes at a fixed interval.
@@
 The \textit{full-information} counterfactual simulates how often a regulator would optimally replace pipes in order to maximize welfare under full information.
-For each section of the service area, the regulator maximizes present-discounted welfare indefinitely given by the following expression
+For each section of the service area, the regulator maximizes present-discounted consumer welfare indefinitely given by the following expression
 % doublecheck the tau's and t's
@@
 where $t$ indexes month, $\delta(>0)$ is the discount factor, and $k_t$ is the age of the pipes.
-$CS(k_{t})$ is consumer surplus and $V(k_t)$ is net revenue, which depends on revenue from water sales, $W(k_{t})$, costs of water leakage, $E(k_{t})$, and payments on any loans to fund pipe replacements, $L(k_t)$.
+$CS(k_{t})$ is the consumer surplus from pipe replacements as defined in equation (ref!), which is assumed to be decreasing in pipe age.
+$V(k_t)$ is the net revenue from pipe replacements, which depends on revenue from (increased) water sales, $W(k_{t})$, costs of water leakage, $E(k_{t})$, and payments on any loans to fund pipe replacements, $L(k_t)$.
+$V(k_t)$ is passed on to consumers as a fixed rebate or charge (ie.
+by adjusting the monthly service charge).
 Due to pipe deterioration, consumer surplus and water revenue are both assumed to be decreasing in pipe age while water leakage is assumed to increase with pipe page.
-$L(k_{t})$ is the payment on the loan needed to fund a pipe replacement.
+
 Each month, the regulator chooses whether to replace pipes ($R_t = 1$) or not ($R_t = 0$).
@@
 In this framework, the optimal schedule of pipe replacements balances net revenue against consumer surplus from new pipes.
-
-In this framework, net revenues for a section of the service area can be positive, negative, or zero.
-In practice, the regulator is likely to stagger pipe replacements across different sections of the service area so that total net revenues across all service areas are close to zero.
-However, in some periods, total net revenues may still be negative or positive.
-In these cases, the model implicitly assumes that the regulator adjusts fixed monthly service charges
-
-is able to maintain revenue neutrality by adjusting fixed monthly service charges paid by consumers.
-
-% Since this framework does not assume a revenue constraint at zero,
 
@@
 % While the model does not explicitly capture scheduling optimization, it 
-This framework also holds the water tariff fixed.
+% This framework also holds the water tariff fixed.
 
-In the \textit{regular-replacement} counterfactual, the regulator is uninformed about consumer surplus and revenues.
-Instead, the regulator only knows the age of the pipes and chooses to replace pipes as soon as they reach a certain age, $\overline{K}$.
-In the \textit{quality-standards} counterfactual, the regulator observes not only the age of the pipes, but also the water pressure reaching consumers, $P(k_t)$.
+In the \textit{regular-replacement} counterfactual, the regulator only observes the age of the pipes and chooses to replace pipes as soon as they reach a certain age, $\overline{K}$.
+In the \textit{quality-standards} counterfactual, the regulator also observes the water pressure reaching consumers, $P(k_t)$.
 The regulator then chooses to replace pipes once the water pressure falls below a certain threshold, $\overline{P}$.
-In the \textit{cost-recovery} counterfactual, the regulator does not observe water pressure, but instead observes the part of producer surplus attributable to leakage costs, $E(k_t)$.
-The regulator then replaces pipes to minimize leakage costs and pipe replacement costs.
+In the \textit{cost-recovery} counterfactual, the regulator does not observe water pressure, but instead observes leakage costs.
+The regulator then replaces pipes to minimize leakage costs, $E(k_{t})$ and pipe replacement costs, $L(k_{t})$.
 
-The marginal price is enough to cover the other fixed costs, and the firm gets to keep the leftovers!
+% The marginal price is enough to cover the other fixed costs, and the firm gets to keep the leftovers!
 
-In the \textit{firm-level} counterfactual, the regulated firm is assumed to be fully aware of producer surplus, $PS(k)$, and the regulator allows the firm to maximize producer surplus, $PS(k) - L(k_{t})$.
+In the \textit{firm-level} counterfactual, the regulated firm is assumed to be fully aware of not only leakage costs, $E(k_t)$, but also revenue from water sales as result of pipe replacements, $W(k_t)$.
+To incentivize the firm to act on this information, the regulator allows the firm to enjoy the net revenues from pipe replacements, $V(k_t)$.
+The firm then chooses replacement rates to maximize, $V(k_t)$.
+In this case, consumer surplus, $CS(k_t)$ is equal to consumer welfare because consumers no longer receive transfers equal to net revenues.
+This arrangement is equivalent to ``price-cap'' regulation where the regulator sets a maximum price and firm is able to enjoy profits at prices up to the maximum while incurring investment costs.\footnote{See \cite{joskow2007regulation}.}
 
-Total welfare versus producer/consumer divide?
+Specify, exactly what is allowed to vary across places and what isn't!
+
+The simulations assume an annual discount factor of $\delta$=4\% and an annual interest rate of $r=5\%$, which is consistent with loans covering recent water investments.
+
+Costs, $L_()$, are measured...
+
+% and the regulator allows the firm to maximize producer surplus, $PS(k) - L(k_{t})$.
+
+% Total welfare versus producer/consumer divide?
 
@@
 
-In the empirical set-up, ...
-
-Discuss the empirical set up!  Discuss the limitations in the empirical set-up. Roughly correspond to natural divisions of the service area.
+% Discuss the empirical set up!  Discuss the limitations in the empirical set-up. Roughly correspond to natural divisions of the service area.
 
@@
 \begin{figure}
+\begin{center}
 \caption{Price Time-Series}\label{figure:pricetimeseries}
-\begin{center}
-\includegraphics[scale=1]{tables/price_series.pdf}
+\includegraphics[scale=1]{tables/price_time_series.pdf}
 \end{center}
@@
 \begin{figure}
-\caption{Tariff Schedule}
 \begin{center}
+\caption{Tariff Schedule}\label{figure:tariffschedule}
 \includegraphics[scale=1]{tables/rs_prices.pdf}
@@
 \begin{center}
-\caption{Consumption Histogram}
-\includegraphics[scale=1]{tables/consumption_histogram.pdf}
+\caption{Usage Histogram}\label{figure:conshist}
+\includegraphics[scale=1]{tables/cons_histogram.pdf}
 \end{center}

### 2021-02-09 phil_paper/paper_booster_pumps_wjv.tex
draft except conclusion

@@
 %\title{{Microcredit from Delaying Bill Payments}\thanks{}}
-\title{Microcredit from Delaying Bill Payments}
+\title{Infrastructure Quality and Imperfect Information: Evidence from Piped Water in Manila}
 \author{\\[3em]
@@
 E-mail: william.j.violette@gmail.com   Any opinions and conclusions expressed herein are those of the author and do not necessarily represent the views of the Federal Trade Commission or its Commissioners.
-Many thanks to Matthew Panhans, Miriam Larson-Koester, Adrian Rubli-Ornelas, and Stefano Polloni.} \\
+} \\ % Many thanks to Matthew Panhans, Miriam Larson-Koester, Adrian Rubli-Ornelas, and Stefano Polloni.
  \\ 
@@
 
-Delaying bill payments to public utilities may provide an important strategy for households with volatile incomes to smooth their consumption.
-At the same time, tolerating late payments may reduce net revenues for utilities, which often leads to higher prices to cover costs.
-Using billing records from a large water utility in Manila, this paper estimates a household consumption and savings model to evaluate counterfactual payment policies.
-A popular proposal to ensure upfront payments --- prepaid metering --- recoups less revenue than is needed to compensate households for their loss of consumption smoothing.
-Alternatively, a revenue-neutral policy allowing more late payments increases welfare by encouraging greater consumption smoothing.
+Public utilities often need to make large investments in infrastructure quality without knowing exactly how much they will benefit consumers.
+Using data from a water utility in Manila, this paper estimates the effect of large-scale pipe replacements on consumer surplus both directly through increased water consumption and indirectly through lower spending on private water pumps.
+Detailed cost data allow for evaluating counterfactual pipe replacement policies.
+Minimizing engineering costs and/or maintaining strict quality standards lead to more infrequent pipe replacements, but small welfare losses relative to a full-information, optimal benchmark.
 
 \vspace{1in}
-\textbf{Keywords:} credit constraints; consumption smoothing; water utilities. \\
-\textbf{JEL Codes:} O13; E21; L95. \\
+\textbf{Keywords:} water utility; product quality; imperfect information. \\
+\textbf{JEL Codes:} O13; L51; L95. \\
 \bigskip
@@
 \section{Introduction}
+
+  % For example, pipe cost, sewer cost, power line costs.  , \cite{frauendorfer2010issues}
+% For example, out of the \$472.6 billion USD needed for US water infrastructure in the next 20 years, the bulk of the funding would support large projects such as pipe replacements, water treatment plants, and storage facilities.\footnote{See \cite{epa2015}.}
+% health and productivity 
+To ensure service quality, public utilities often require large upfront investments such as replacing water pipes, building power generators, or expanding sewage treatment plants.
+The social benefits of these investments are  difficult to measure because investments are infrequent, it can be challenging to precisely locate affected consumers, benefits may be external to consumer demand, and public utilities are often natural monopolies, which means that consumers cannot turn to other providers for better service quality (\cite{spence1975monopoly}).
+Without knowing these social benefits, public utilities instead base their investments on meeting service quality benchmarks and/or minimizing engineering cost calculations.
+Alternatively, public utility regulators may allow private companies to determine and profit from quality investments if companies are better able to measure the benefits and costs of investments.
+It remains an empirical question which regulatory policies best ensure socially efficient levels of infrastructure quality.
+
+Quality regulation may have particularly large welfare consequences in developing cities where aging infrastructure and underinvestment contribute to persistently low levels of service quality.
+For example, over 20\% of the piped water supplied in developing cities leaks from pipes before reaching consumers, resulting in low water pressure and intrusion of contaminants (\cite{liemberger2006challenge}).
+Longterm quality deficits have led households to invest in private substitutes for service quality.
+In Mexico City, 45\% of households use rooftop storage tanks to deal with intermittent water supply (\cite{baisa2010welfare}) while households in urban India turn to a combination of private water tanks, pumps, and/or tube wells (\cite{mckenzie2009urban}).
+While difficult to measure, spending on quality substitutes may be an important part of the welfare costs of low service quality.
+% Recent research in developing countries also links improvements in infrastructure quality to external benefits such as improved health\footnote{See \cite{bhalotra2017urban}, \cite{galiani2005water}, \cite{ashraf2017water}.} and productivity.\footnote{See \cite{allcott2016electricity} and \cite{hardy}.}
+
+This paper estimates the effect of water pipe replacements on consumer welfare in Manila, Philippines and then evaluates alternative pipe replacement policies.
+Like many developing cities, Manila initially suffered from low levels of quality investment by the public utility, which was privatized through a public-private parternship in 1997 (\cite{dumol2000manila}).
+Unlike in many developing cities, the public-private partnership launched a massive infrastructure upgrading program around 2008, which replaced at least 50\% of the existing pipes by 2015.
+This paper analyzes billing and location records from 1.5 million water connections over this period as well as cost, pipe location, and survey data.
+Analyzing the impacts of these investments may provide useful lessons for other developing cities weighing similar programs.
+
+The empirical strategy leverages the staggered roll-out of pipe replacements to identify its effects on household water consumption and electric booster pump use --- a common substitute for low water pressure.
+The estimation strategy recovers the causal effect of replacements from pre/post changes in outcomes compared to changes in areas without replacements under the assumption that areas would have evolved similarly in the absence of replacements.
+This assumption is supported by the fact that engineers organized the pipe replacement program to meet hydrological constraints, which were unlikely to have been related to trends in local water demand.
+% This assumption is further supported by evidence of relatively flat trends in outcomes leading up to replacement projects.
+
+Translating consumption changes into consumer surplus also requires estimating the price elasticity of demand.
+The empirical strategy analyzes novel price variation where some households are suddenly switched to 22\% higher prices at different times.
+These switches occur when the water company notices any business activity at households' residences, which usually entails small, roadside food stands.
+This event-study approach complements the largely cross-sectional and time-series approaches to estimating price elasticities in the literature.\footnote{See \cite{szabo2015value} and \cite{mcrae2015infrastructure} as well as \cite{olmstead2009reduced} for a review.}
+
+Results indicate that pipe replacements have large effects on consumer welfare driven in particular by lower spending on quality substitutes.
+Pipe replacements are associated with a 10\% increase in household water consumption and a 30 percentage point decline in booster pump use.
+Guided by a simple model of household water demand, these estimates suggest economically large increases in monthly consumer surplus on the order of 175 PhP or 35\% of an average household water bill.
+Consumer utility from greater consumption and from savings on booster pumps both contribute roughly equally to the total increase in consumer surplus, highlighting the importance of private quality substitutes in evaluating infrastructure projects.
+Gains in consumer surplus also appear concentrated among lower socioeconomic status households.
+% (68+107)/500
+
+The paper calculates the longterm welfare consequences of replacing pipes more or less frequently in different areas of the city.
+To calculate longterm welfare, the paper assumes that pipes deteriorate linearly over time and leverages how the observed pipe replacements effectively reset the age of the pipes from 25 years old to zero.
+Therefore, the estimated effects of pipe replacements on revenue, leakage costs, and consumer surplus summarize how welfare evolves over time.
+Estimates are conducted separately for 11 different areas of the city to simulate the spatially targeted nature of infrastructure investments.
+% according to maximize different criteria
+
+The paper then compares welfare and pipe replacement frequencies under imperfect information to those under a full-information benchmark holding fixed all other aspects of water provision.
+In the first case, the government regulator only observes the age of the pipes and chooses to replace pipes every 25 years, which matches the observed experience in Manila.
+By replacing pipes much less frequently, this policy lowers monthly welfare by around 20\% of an average water bill compared to the full-information benchmark.
+This result suggests that Manila would have experienced substantial welfare gains by replacing its pipes sooner.
+
+In the second case, the regulator observes the water pressure reaching consumers and sets a minimum pressure threshold, replacing pipes when pressure falls below this threshold.
+While the pressure threshold outperforms 25-year replacements, welfare is very sensitive to the exact threshold levels.
+The third case allows the regulator to observe and minimize pipe replacement and leakage costs, further improving welfare by replacing pipes more frequently on average.
+However, monthly welfare still lags behind the full-information benchmark by an amount equal to 6\% of an average water bill.
+
+The last case allows a regulated, private firm to schedule pipe replacements in order to maximize profits (ie.
+revenues minus costs) under the assumption that the firm is able to perfectly and freely observe demand and costs.
+Since prices in Manila are set above marginal costs, extra consumption generated by pipe replacements would give the firm an additional incentive to replace pipes quickly.
+This context emulates ``price-cap'' regulation where the regulator sets a maximum price to cover operating costs and the firm is able to profit from additional investments.\footnote{See \cite{joskow2007regulation}.}  Profit maximization results in the next most frequent pipe replacements aside from the full-information benchmark.
+As a result, monthly welfare lags behind the full-information benchmark by an amount equal to only 2\% of an average water bill.
+Consumer welfare is only slightly smaller than total welfare because high pipe replacement costs limit any potential profits earned by the firm.
+
+This paper builds on a long literature on public utility regulation in industrial organization.
+While previous research, pioneered by \cite{laffont1993theory}, largely focuses on information asymmetries between firms and regulators (\cite{mcrae2015infrastructure}, \cite{lim2018dynamic}), this paper examines the case where both the regulator and the firm have imperfect information, which may be especially relevant to infrastructure quality.
+This paper also provides an empirical examination of the regulatory challenges inherent in measuring and regulating quality outlined by \cite{spence1975monopoly}.
+
+This paper also contributes to a recent development literature studying the impacts of improved public utility service quality.
+Recent research has mainly focused on the impact of public utilities on health (\cite{bhalotra2017urban}, \cite{kosec2014child}, \cite{ashraf2017water}), education (\cite{zhang2016long}), and  productivity (\cite{allcott2016electricity}, \cite{hardy}).
+This paper measures the direct consumer surplus from improved water service quality in a similar way to how \cite{mcrae2015infrastructure} recovers demand for continuous electricity service.
+Like \cite{baisa2010welfare}, this paper also studies the welfare implications of spending on private substitutes to water service quality.
+
+The paper proceeds with a discussion of the context in Manila and the datasets in Section~\ref{section:data}.
+Section~\ref{section:descriptives} provides descriptive statistics on water use in Manila.
+Section~\ref{section:model} develops a simple model of water demand and Section~\ref{section:empiricalstrategy} outlines the empirical strategy to estimate the model.
+Section~\ref{section:results} discusses the results.
+Section~\ref{section:counter} incorporates the results into counterfactual policy simulations and Section~\ref{section:conclusion} concludes.
+
+% \cite{mcrae2015infrastructure} considers the value of power outages to consumers but not . 
+% \cite{mcrae2015infrastructure}
+% \cite{laffont2005regulation}
+% DEVELOPMENT CONTRIBUTION mostly focuses on externalities; this one is 
+% The paper also abstracts away from potential health or productivity externalities associated with water quality improvements.
+
+% The counterfactual results are likely to be most relevant to urban settings with little investment in pipe maintenance, rapid development, and little health or productivity externalities from water use.
+In Manila, pipe replacements have large impacts on consumer surplus .
+These large impacts likely stem from
+% The counterfactuals predict very short replacement rates of 8 to 12 years compared to an engineering literature in the US that predicts at least 50 year pipe replacement rates.  
+% Since the counterfactuals rely on estimated pipe replacement effects, the counterfactual results assume that
+
+% EXTERNAL VALIDITY
+% These results are only valid for the levels of maintenance during the public utility, especially while the public utility was there...
+% relative results may be instructive
+
+% Costs of gathering the information ! 
+% External validity broadly !  when and when not...
+
+PUT FOOTNOTES IN TO EXPLAIN THE AMOUNTS!!
+
+  % The counterfactuals then choose the optimal pipe replacement rates to satisfy their welfare criteria for each area.
+
+% The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
+In the \textit{regular-replacement} counterfactual, the regulator simply replaces all pipes at a fixed interval, which loosely follows the approach taken in Manila.
+In the \textit{quality-standards} counterfactual, the regulator establishes a minimum water pressure threshold and replaces pipes when pressure falls below the threshold.
+In the \textit{cost-minimization} counterfactual, the regulator schedules replacements to minimize leakage costs over time as well as upfront replacement costs.
+In the \textit{firm-level} counterfactual, the regulator lets the firm decide when to replace pipes under the assumption that the firm has full demand and cost information.
+
+%%% goal: by 1, first draft intro; goal by evening: first draft conclusion
+
+Conclusion should discuss REGULATION THEORY!!
+
+% The government regulator gives the water company discretion to assign households to a high-price tariff schedule if they have any business activity at their residence, which provides a novel source of price variation in the context of public utilities.
+In the vast majority of cases, the high price tariff is applied to households that operate small food stands (or ``Sari-Sari'' stores).
+
+% Public utilities cope with this uncertainty by delaying investments,  and/or relying on engineering 
+% quality is provided in a monopoly setting where consumers face few alternatives.  
+% first because there's a monopoly.
+% Since the welfare benefits of these investments are often difficult to measure, 
+% Information is really hard to get for water pipes...; degrade over time; leakage detection systems are costly, etc.
 
@@
 
-\section{Data and Setting}
+\section{Data and Setting}\label{section:data}
 
@@
 This finding is consistent with booster pumps providing an important substitute to pressure from new water pipes.
+
 % = .9*.786*78*8.8
@@
 \hspace{1em}Employed members & \input{tables/hhemp} \\
-\hspace{1em}High-skilled employment & \input{tables/good_job} \\
+\hspace{1em}Respondent has high-skilled employment & \input{tables/good_job} \\
 \hspace{1em}Lives in duplex& \input{tables/sub} \\
@@
 \begin{center}
-\caption{Average Consumption per Household with Years to Pipe Replacement}\label{figure:pipecons}
+\caption{Average Water Usage per Household with Years to Pipe Replacement}\label{figure:pipecons}
 \includegraphics[scale=1]{tables/pipe_cons.pdf}
@@
 \midrule
-Usage per Household (m3)& \input{tables/cv_rs} \\
+Usage per household (m3)& \input{tables/cv_rs} \\
 Household size & \input{tables/hhsize_rs} \\
 Employed members & \input{tables/hhemp_rs} \\
-High-skilled employment & \input{tables/good_job_rs} \\
-Lives in duplex& \input{tables/sub_rs} \\
-Lives in single house& \input{tables/single_rs} \\
+Respondent has high-skill employment & \input{tables/good_job_rs} \\
+Lives in a duplex& \input{tables/sub_rs} \\
+Lives in a single house& \input{tables/single_rs} \\
 Other households sharing tap& \input{tables/SHO_rs} \\
@@
 \begin{center}
-\caption{Usage and Price Changes}\label{figure:usagepricechanges}
+\caption{Water Usage and Price Changes}\label{figure:usagepricechanges}
 \includegraphics[scale=1]{tables/r_to_s_only_graph.pdf}
@@
 
-\section{Model}
+\section{Model}\label{section:model}
 
@@
 
-\section{Empirical Strategy}
+\section{Empirical Strategy}\label{section:empiricalstrategy}
 
@@
 
+To estimate the effects of pipe replacement change over time, additional specifications replace the terms, $\gamma_1  \text{Post Pipe}_{tl} $ and $\beta_1  \text{Post Pipe}_{tl} $, with the terms, $\sum_{k=0}^{K} \gamma_1^{k}  \text{Post Pipe}_{tl}^{k} $ and  $\sum_{k=0}^{K} \beta_1^{k}  \text{Post Pipe}_{tl}^{k} $, where $k$ indexes years after pipe replacement, $\text{Post Pipe}_{tl}^{k}$ is an indicator variable for each $k$ year after pipe replacement, and coefficients, $\gamma_1^{k}$ and $\beta_1^{k}$, measure the lasting effects at each $k$ year after pipe replacement.
+
+To estimate heterogeneity according to household characteristics, further specifications replace the terms, $\gamma_1  \text{Post Pipe}_{tl} $ and $\beta_1  \text{Post Pipe}_{tl} $, with the terms, $\sum_{j=1}^{J} \gamma_1^{j} \mathbbm{1}\{D^{j}=1\} \times \text{Post Pipe}_{tl} $ and  $\sum_{j=1}^{J} \beta_1^{j} \mathbbm{1}\{D^{j}=1\} \times \text{Post Pipe}_{tl} $, where $j$ indexes household characteristics, $\mathbbm{1}\{D^{j}=1\}$ is an indicator variable for households with characteristic, $j$, and coefficients, $\gamma_1^{j}$ and $\beta_1^{j}$, measure the effects of pipe replacements for households with characteristic, $j$.
+
 The effects of prices on outcomes are given by $\gamma_2$ and $\beta_2$ for water and booster pump use respectively where $\hat{p}_{it}$ is the predicted price from the equation (\ref{eq:1ststage}).
@@
 By taking the derivative of equation (\ref{eq:1ststage}) with respect to price, this effect can be expressed as a function of the price sensitivity as well as the effect of price on water quality through endogenous changes in booster pump use, according to the following equation
-\begin{align*}
+\begin{align}
+\label{eq:psens}
   \gamma_2 = \alpha +  \frac{dQ}{dB} \frac{dB}{dp}
-\end{align*}
+\end{align}
 where $\frac{dQ}{dB}$ is the effect of booster pump use on water quality, which is unobserved.
@@
 
-Given fixed effects the are identified from
-
-When the outcome is monthly water usage, the estimating equation maps directly onto the equation for optimal household usage given by equation ($\ref{eq:demand}$).
-$\beta_1$ captures the effect of pipe replacement on service quality, $\frac{dQ}{dR}$.
-Likewise, $\beta_2$ captures the negative of household price sensitivity, $\alpha$.
-Remaining fixed preferences for water and levels of service quality are absorbed in household and month fixed effects, $\lambda_i$ and $\theta_t$.
-These fixed effects ensure that the effect of pipe replacements is identified from variation in water usage for the same household before and after pipes are fixed while accounting for any temporal usage patterns common to all households.
-Likewise, price sensitivity is estimated from variation in price for the same household switching between regular and high prices.
-Calendar month fixed effects absorb price variation affecting all households equally over time as the company updates water tariffs.
-
-When the outcome is booster pump use, the estimating equation captures the effect of pipe replacements on booster pump use.
-This approach assumes that demand for booster pumps can be linearly approximated by the estimating equation such that $\beta_1$ reflects $\frac{dB}{dR}$.
-Since booster pump use is a binary outcome, this approach represents a linear probability model.
-Time fixed effects account for variation in booster pump usage over time common to all households while household fixed effects account for differences in booster pump use across households.
-$\beta_1$ reflects the effect of pipe replacements on booster pump use under the assumption that no other factors independently affect booster pump use at the same time.
-One concern may be that the prices for booster pumps change in response to pipe replacement projects.
-Pipe replacements occur in small geographic areas while markets for booster pumps are likely to cover much wider areas.\footnote{Online markets span the entire city.}  Therefore, individual pipe replacement projects are unlikely to influence prices for booster pumps.
-
-% \begin{align}
-% \label{eq:1ststage}
-% p_{it} &= \phi_1 \text{Post Pipe Rep}_{tl}  +  \phi_2 \text{Post Price Inc}_{it} +  \phi_3\, t\text{ Post Price Inc}_{it} +\phi_4 \,t \,\text{Pre Price Inc}_{it} +  \phi_t  +  \phi_i + \epsilon_{itl}
-% \end{align}
-% \begin{align}
-% \label{eq:1ststage}
-% p_{it} &= \phi_1 \mathbbm{1} \{t\geq \text{Pipe Rep}_{tl}  \} +  \phi_2 \mathbbm{1} \{t\geq \text{High Price}_{tl}  \} +  \phi_3\, t \, \{t\geq \text{High Price}_{tl}  \} +\phi_4 \,t \,\{t< \text{High Price}_{tl}  \} +  \phi_t  +  \phi_i + \epsilon_{itl}
-% \end{align}
-% The estimating equation takes the following form
-% \begin{align}
-% \label{eq:esteq}
-% y_{itl} \,=\, \beta_1 \, \text{After Pipe Replacement}_{tl} \,+\, \beta_2 \, p_{it} \, + \, \theta_t \, + \, \lambda_i \, + \epsilon_{itl}
-% \end{align}
-% where the outcome, $y_{itl}$, is either monthly water usage or booster pump use.
-Outcomes are measured for household, $i$, in small area, $l$, at calendar month, $t$.
-After Pipe $\text{Replacement}_{tl} $ takes a value of one for months after pipe replacement and zero otherwise.
-Since the data identify only the year that pipes were replaced, all months from the replacement year onwards are considered after pipe replacement.
-$p_{it}$ measures the average price faced by each household in each month.
-$\theta_t$ includes calendar month fixed effects while $\lambda_i$ includes household fixed effects.
-
-% This approach also assumes that booster pumps do not impose substantial negative externalities on local water service quality.
-A recent engineering literature has raised the possibility that booster pumps interfere with water flow in pipe mainlines, reducing pressure along the entire pipe (\cite{taylor2014reducing}).
-However, this problem may not be as salient in the context of Manila.
-The water company has not raised booster pumps as a policy problem in any of their internal documents.\footnote{Booster pumps are sometimes mentioned in water company investigations of consumer complaints as an explanation for household water pressure and never as problem to be addressed.}  Moreover, externalities would predict large water usage gaps between those with and without booster pumps in the same neighborhood.
-By contrast, Table~\ref{table:usageregs} finds a similar association of booster pump use and water usage with and without small-area fixed effects.
-% Taken together, the empirical evidence is supportive of the relatively strong assumptions necessary to identify booster pump preferences.
-
-\section{Results}
-
-Table~\ref{table:mainregs} includes results of the effect of price and pipe replacements.
-Column (1) provides results on household water use finding an increase of 1.79 m3 per household per month after pipe replacement.
-The estimate is statistically significant at the 1\% and economically large representing an 8\% increase in average usage.
-The estimated increase is smaller than the descriptive increase in Figure~\ref{figure:pipecons} likely because the regression approach controls for increasing trends in water use over the sample period.
-
-Column (1) also provides an estimated price sensitivity of 0.17, which is statistically significant at the 1\% level.
-Given an average price of 21.5 PhP/m3, this estimate also implies a price elasticity of 0.17.
-This elasticity estimate is on the lower end of similar studies in the developing world, which find elasticities ranging from 0.01 to 0.98.\footnote{See \cite{szabo2015value}, \cite{diakite2009proposal}, and \cite{strand2005water}.}
-
-Column (2) finds that pipe replacement projects are associated with a 20\% decrease in booster pump use, which is statistically significant at the 5\% level.
-This decline is smaller than the descriptive decline in Table~\ref{table:descriptives} likely since the regression approach accounts for decreasing booster pump use over the sample period.
-
-% While previous studies largely focus on cities in low-income countries (\cite{diakite2009proposal} ) or low-income neighborhoods within larger cities, this estimate  which may explain
-
-% dQ/Q / dP/P  =  (.17/22.14) /  (1/21.5)
-% This estimate is in range of the 0.98 estimate from \cite{szabo2015value} as well as similar studies in the developing world that find elasticities between 0.01 and 0.81 (\cite{diakite2009proposal}, \cite{strand2005water}).
+\section{Results}\label{section:results}
+% Columns (1) and (3) provide average effects while Columns (2) and (4) provide separate effects for each year after pipe replacements.
+
+Table~\ref{table:mainregs} includes the main estimates of the effects of average price and pipe replacements on water and booster pump use.
+The first row of Column (1) finds an average increase in household water usage of 2 m3 per month after pipe replacement.
+The estimate is statistically significant at the 1\% level and economically large, representing a 10\% increase in average household water use.
+The first row of Column (2) finds that pipe replacement projects are associated with a 22 percentage point average decrease in booster pump use, which is statistically significant at the 1\% level.
+This estimate also represents an economically significant decrease given that the average level of booster pump use across the full sample is 16\%.
+
+Columns (2) and (4) provide separate effects for each year after pipe replacements.
+According to Column (2), the effect on water use is highest in the first two years after pipe replacement at around 2.3 m3 before declining linearly to around 2 m3 at 6 years after pipe replacement.
+Column (4) finds a similar declining pattern for booster pump use between one and two years after pipe replacement.
+Booster pump effects beyond two years are unavailable because the connection survey only covers a limited time period.
+Columns (2) and (4) find a relatively smaller effect in the year of construction likely because many projects were completed at some point during this year.
+
+The declining effect over time is consistent with pipes gradually deteriorating.
+The linear trend in the decline matches civil engineering research documenting a roughly linear relationship between pipe failure and pipe age especially within the first 50 years after installation.\footnote{See \cite{ward2017deterioration}, \cite{kleiner2001comprehensive}, and \cite{aydogdu2015estimation}.}  Extrapolating the linear trend suggests that households would return to their pre-replacement consumption levels within around 37 years.
+In contrast, the average age of the replaced pipes is around 25 years, which suggests that the new pipes may be more durable or subject to better maintenance than the replaced pipes.
+
+In terms of estimating price sensitivity, the second row of column (1) provides a reduced form effect of prices on water use of 0.59, which is statistically significant at the 1\% level.\footnote{Appendix Table~\ref{table:regstages} indicates that the first-stage is statistically significant and the t-statistic is at least 17 across specifications.}  Since the second row of column (2) finds zero effect of price on booster pump use,\footnote{Although the price effect is identified from only the 208 connections that are surveyed after being switched into a high price tariff, the estimate is relatively precise ruling out effects above 3.7\% and below -2\% with 95\% confidence.} then the reduced form effect of price on usage can be interpreted directly as household price sensitivity according to equation (\ref{eq:psens}).
+Given an average price of 21.5 PhP/m3, this estimate implies a price elasticity of 0.64.
+This elasticity estimate is in the middle of the range from 0.01 to 0.98 in the developing world.\footnote{See \cite{szabo2015value}, \cite{diakite2009proposal}, and \cite{strand2005water}.}
+
+These results allow for benchmarking the average effect of pipe replacements on consumer welfare over 6 years according to equation (\ref{eq:dvdr}).
+Using inputs from column (1) of Table~\ref{table:mainregs}, consumer surplus from improved water quality computes to around 68 PhP per household/month while consumer surplus from lower booster pump usage computes to around 107 PhP per household/month.
+This result suggests that both factors are similarly important in driving changes in consumer welfare.
+
+% is equal to the product of average water use and the effect of pipe replacements on water use weighted by the price sensitivity,
 
@@
 \begin{threeparttable}
-\begin{tabular}{@{}l*{1}{CC}@{}}
+\begin{tabular}{@{}l*{1}{CCCC}@{}}
 \toprule
-  & (1)       & (2)              \\
-  & Water Use & Booster Pump Use \\
+  & (1)       & (2)       & (3)              & (4)              \\
+  & Water Use & Water Use & Booster Pump Use & Booster Pump Use \\
 \midrule
-\input{tables/reg}
+\input{tables/reg_wtime}
 \bottomrule
@@
 
+Table~\ref{table:mainregshet} tests for heterogeneity in responses to pipe replacements according to household demographic characteristics.
+Columns (1) and (2) include results for water use and Columns (3) and (4) include results for the natural logarithm of water use plus one to account for months with zero consumption.
+Coefficients in Columns (3) and (4) can be interpreted approximately as percentage effects.
+The effects of pipe replacements on water use are stronger for households living in subdivided or freestanding houses relative to those living in apartment buildings.
+Apartment buildings may invest in large-scale water pumps or small water towers to ensure water flow while houses may be unable to make these large investments and are often located further from central water pipes.
+The effects on water use are weaker for households where the household head is employed in a high-skilled job as well as for households with more employed household members relative to other households.
+This finding is consistent with higher income households investing in water quality substitutes or locating in areas with better service quality.
+Columns (5) and (6) test for heterogeneous effects on booster pump use, finding no evidence of differential responses according to household characteristics.
+Overall, these results suggest that pipe replacements have positive distributional effects since water quality benefits appear to accrue more strongly for lower income households.
+
 \begin{table}[h!] 
 \centering
-\caption{Change in Consumer Surplus}\label{table:mainregs}
+\caption{Heterogeneity in Estimates by Household Characteristics}\label{table:mainregshet}
+\vspace{-2mm}
+\resizebox{\textwidth}{!}{
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{CCCCCC}@{}}
+\toprule
+  & (1)       & (2)  & (3) & (4)   & (5) & (6)            \\
+  & Water Use & Water Use  & log(Water Use + 1) & log(Water Use + 1) & Booster Pump Use & Booster Pump Use \\
+\midrule
+\input{tables/reghet_after}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\regtext 45 PhP = 1 USD \,\,
+\end{tablenotes}
+\end{threeparttable}
+}
+\end{table}
+
+\section{Policy Counterfactuals}\label{section:counter}
+
+% We're focusing on a part of the natural monopoly where the costs are easy to measure (you replace pipes), but the benefits are less well understood.
+Different from the standard Laffont and Tirole model; closer to the Spence model which is a real contribution!
+(luckily high cost areas also have high benefit)
+% Set aside all other aspects of regulation to focus on quality!  Usually, capital is thought of as an input to deliver a certain quantity of the product.  Here we're focusing on a particular
+
+This section uses the empirical estimates to simulate the welfare effects often five policies for replacing pipes.
+Section~\ref{section:countermodel} discusses a simple framework and assumptions for simulating each policy.
+Section~\ref{section:counterinputs} outlines the empirical inputs.
+Section~\ref{section:counterresults} discusses the results of the simulations.
+
+% The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
+In the \textit{regular-replacement} counterfactual, the regulator simply replaces all pipes at a fixed interval.
+In the \textit{quality-standards} counterfactual, the regulator establishes a minimum water pressure threshold and replaces pipes when pressure falls below the threshold.
+In the \textit{cost-recovery} counterfactual, the regulator schedules replacements to balance savings from lower pumping costs against upfront costs of the pipe replacements.
+In the \textit{firm-level} counterfactual, the regulator lets the firm decide when to replace pipes under the assumption that the firm has full demand and cost information.
+
+\subsection{Policy Framework}\label{section:countermodel}
+
+% The following counterfactuals identify the welfare effects of optimal pipe replacements under five different information environments. 
+The counterfactuals focus on the role of pipe replacements by holding fixed other aspects of water utility operation and regulation.
+The full population of Manila is assumed to remain connected to service indefinitely.
+The water tariff is assumed to be determined independently of pipe replacements and to exactly cover all other costs of water production except pipe replacements.
+Except for the \textit{profit-maximization} counterfactual where the firm enjoys any profits from pipe investments, any cost savings or cost overruns as a result of the pipe replacements are assumed to be passed on to consumers in the form of fixed rebates or charges, which do not affect consumers' marginal incentives to consume water.
+Pipe replacements are assumed to be independent of operating costs such as labor or maintenance expenditures.
+
+% The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
+In the \textit{regular-replacement} counterfactual, the regulator simply replaces all pipes at a fixed interval.
+In the \textit{quality-standards} counterfactual, the regulator establishes a minimum water pressure threshold and replaces pipes when pressure falls below the threshold.
+In the \textit{cost-recovery} counterfactual, the regulator schedules replacements to balance savings from lower pumping costs against upfront costs of the pipe replacements.
+In the \textit{firm-level} counterfactual, the regulator lets the firm decide when to replace pipes under the assumption that the firm has full demand and cost information.
+
+% - hold price fixed!
+% - decide replacements independently for each area
+% - Not permitted expenses, similar to a price-cap [that's fair] (under invest)
+% - Rate of return (allow for overlapping loans...?) --> no, don't ; make the point that the firm will want to replace pipes as soon as loans come due because the projects generate more than enough revenue to meet reasonable rates of return.
+
+% - permitted expenses or not? hard to know..
+% - rate of return when we don't know the production function; 
+% - high power --> redistribute little but keep costs down
+% - low power --> redistribute a lot but high costs
+% --- where are we?
+
+% --> low power: all the surplus goes to consumers, but decisions are based on limited information
+% --> high power: firm can get the surplus, but decisions are based on detailed consumer information; provides a strong incentive for the firm to figure out exactly the benefits of the investments
+%%% in practice, it's somewhere between
+%%% note that with the high power incentive, the prices are high, and the wedges get smaller if the prices are lower!
+%%% footnote explaining distinction with standard high versus low-powered incentives.
+
+% Since these projects generate streams of revenues in excess of their costs, then rate-of-return regulation would likely lead firms to very frequently replace pipes.\footnote{We do not explicitly model rate of return regulation here because the constraint would depend on whether the company could take out multiple loans, and the cost of capital for those loans.}
+
+The \textit{full-information} counterfactual simulates how often a regulator would optimally replace pipes in order to maximize welfare under full information.
+For each zone of the service area, the regulator maximizes present-discounted consumer welfare indefinitely given by the following expression
+% doublecheck the tau's and t's
+\begin{align*}
+max_{R_t\in\{0,1\}} \,\, &\sum_{\tau = t}^{\infty} (1+\delta)^{t-\tau} [CS(k_{t}) + V(k_{t})]  \\
+V(k_{t}) &= W(k_{t}) - E(k_{t}) - L(k_{t})\\ 
+k_{t+1} &=  (1 + k_t) \, (1-R_t \mathbbm{1} \{ k_{t}> l\}) \\
+L(k_t) &= \frac{r(1+r)^{l} }{(1+r)^{l} -1 }\overline{L} \, \mathbbm{1} \{ k_{t}\leq l \}
+\end{align*}
+where $t$ indexes month.
+$\delta$ is the discount factor which is assumed to be 5\% in annual terms (0.42\% in monthly terms).
+$k_t$ is the age of the pipes.
+$CS(k_{t})$ is the consumer surplus from pipe replacements as defined in equation (\ref{eq:dvdr}), which is assumed to be decreasing in pipe age.
+$V(k_t)$ is the net revenue from pipe replacements, which depends on revenue from (increased) water sales, $W(k_{t})$, costs of water leakage, $E(k_{t})$, and payments on any loans to fund pipe replacements, $L(k_t)$.
+$V(k_t)$ is passed on to consumers as a fixed rebate or charge (ie.
+by adjusting the monthly service charge).
+Due to pipe deterioration, consumer surplus and water revenue are both assumed to be decreasing in pipe age while water leakage is assumed to increase with pipe page.
+
+Each month, the regulator chooses whether to replace pipes ($R_t = 1$) or not ($R_t = 0$).
+Replacing pipes sets the pipe age, $k_t$, back to zero and is only possible if the regulator has paid off any debt from a previous pipe replacement where $l$ indexes the duration of the debt.
+The regulator is assumed to fund a pipe replacement with a loan of total size, $\overline{L}$, at monthly interest rate, $r$, over duration, $l$.
+$r$ is assumed to equal  5\% in annual terms (0.42\% in monthly terms), consistent with the terms of the loans currently held by the water company.
+$l$ is assumed to equal 5 years, which provides a lower bound on the replacement frequency.
+The expression for $L(k_t)$ calculates the size of the monthly loan payments.
+In this framework, the optimal schedule of pipe replacements balances net revenue against consumer surplus from new pipes.
+
+% While in practice, regulators may adjust both marginal prices and fixed monthly service charges, the model focuses only on fixed monthly service charges  
+% The model implicitly assumes that the regulator is able to implement fixed transfers to and from consumers without distorting their water consumption.
+For example, the regulator may offer all consumers fixed rebates in months with budget surpluses and higher fixed water charges in months with budget deficits.
+% Allowing negative net revenues in the model provides an approximation for this scheduling optimization.
+
+% While the model does not explicitly capture scheduling optimization, it 
+% This framework also holds the water tariff fixed.
+
+In the \textit{regular-replacement} counterfactual, the regulator only observes the age of the pipes and chooses to replace pipes as soon as they reach a certain age, $\overline{K}$.
+In the \textit{quality-standards} counterfactual, the regulator also observes the water pressure reaching consumers, $P(k_t)$.
+The regulator then chooses to replace pipes once the water pressure falls below a certain threshold, $\overline{P}$.
+In the \textit{cost-minimization} counterfactual, the regulator does not observe water pressure, but instead observes leakage costs.
+The regulator then replaces pipes to minimize leakage costs, $E(k_{t})$ and pipe replacement costs, $L(k_{t})$.
+
+% The marginal price is enough to cover the other fixed costs, and the firm gets to keep the leftovers!
+
+In the \textit{profit-maximization} counterfactual, the regulated firm is assumed to be fully aware of not only leakage costs, $E(k_t)$, but also revenue from water sales as result of pipe replacements, $W(k_t)$.
+To incentivize the firm to act on this information, the regulator allows the firm to enjoy the net revenues from pipe replacements, $V(k_t)$.
+The firm then chooses replacement rates to maximize, $V(k_t)$.
+In this case, consumer surplus, $CS(k_t)$ is equal to consumer welfare because consumers no longer receive transfers equal to net revenues.
+This arrangement is similar to ``price-cap'' regulation where the regulator sets a maximum price and the firm is able to enjoy profits at prices up to the maximum while incurring investment costs.\footnote{See \cite{joskow2007regulation}.}
+
+\subsection{Empirical Inputs}\label{section:counterinputs}
+
+The counterfactuals have four key empirical inputs: consumer surplus, $CS(k_t)$, revenue, $W(k_{t})$, leakage savings, $-E(k_{t})$, water pressure, $P(k_t)$, and replacement costs, $\overline{L}$.
+The first four inputs depend on pipe age.
+The counterfactuals assume that each of these inputs declines at a linear rate with pipe age.
+This assumption is consistent with a linear decay over time in the effect of pipe replacements on water use as observed in Table~\ref{table:mainregs}.
+The rate of decay is measured by the effect of pipe replacements on each input.
+The effect of pipe replacements measures the difference between new pipes and old pipes that have already decayed for 25 years (or 300 months).
+Each input is then summarized as $G(k_t) = \frac{k_t}{330}\Delta g$ where $\Delta g$ is the estimated pipe replacement effect for each input, $g$.
+This expression normalizes the intercept to zero.
+
+% In addition to determining the slope, $\Delta g$ also enters the expression as the intercept.
+Therefore with new pipes (ie.
+zero pipe age), each quantity represents the additional benefit of having new pipes relative to 28-year-old pipes.
+% NEED TO EXPLAIN BETTER!
+
+The empirical inputs are estimated separately for 11 different zones of the service area in order to capture how regulators may tailor their policies to particular areas of the service area.
+The zones meet the criteria of having at least 50 households observed in the connection survey both before and 1 to 3 years after pipe replacement projects.
+These zones come from the set of geographic areas that the water utility uses to determine regional policies.
+The zones account for 46\% of the total sample and aim to capture geographic heterogeneity while still ensuring there are enough observations in each zone to reliably estimate the effects of pipe replacements.
+% water usage, booster pump use, revenue for residential and commercial connections, and the share of households reporting no water flow (from 6pm to midnight)  % Since regulators may tailor their policies to particular areas of the service area,
+
+The effects of pipe replacements are estimated for each zone using the following equation
+\begin{align}
+y_{itl} = \sum_{z=0}^{11} \psi_1^{z}\, \text{Post Pipe (1 to 3 yrs)}^{z}_{tl} \, + \, \psi_2^{z}\, \text{Post Pipe (0 or 4+ yrs)}^{z}_{tl}  + \psi_t +  \psi_i +  \varepsilon_{itl}  \label{eq:counterest}
+\end{align}
+where $z$ indexes the 11 zones of interest (with all other zones collapsed into $z=0$).
+$y_{itl}$ is the outcome measured at the household, month, and small-area level.
+$\psi_1^{z}$ is the coefficient of interest for zone $z$ capturing the difference in outcomes between old pipes and newly installed pipes (ie.
+$\frac{dG}{dR}$) by focusing on 1 to 3 years after replacement.
+Measuring effects for this time window intends to ensure that there is a large enough sample to precisely measure impacts for each outcome while omitting the year of replacement (when effects are still ramping up) and later years (when pipes begin degrading).
+$\psi_2^{z}$ controls for differences in outcomes at years 0 (the year of replacement), 4, 5, or 6 after pipe replacement for each zone.
+$\psi_t$ and $\psi_i$ include calendar month and household fixed effects respectively.
+
+Table~\ref{table:counterinputs} reports the estimated effects across the 11 zones on booster pump use, water use, household and commercial water bills, and households reporting low pressure.
+These estimates allow for measuring the effects of pipe replacements on consumer surplus and revenue captured in Table~\ref{table:geoinputs}.
+
+\subsubsection{Consumer Surplus}\label{section:countercs}
+
+\begin{table}[h!] 
+\centering
+\caption{Effects of Pipe Replacements by Zone}\label{table:counterinputs}
 \vspace{-2mm} 
 \begin{threeparttable} 
-\begin{tabular}{@{}l*{1}{CCC}@{}}
+\begin{tabular}{@{}l*{1}{CCCCCC}@{}}
 \toprule
-            & Service Quality              & Booster Pump Use & Total             \\
+	& (1) & (2) & (3) & (4) & (5) \\
+Zone   & Booster Pump Use & Water Use   &  Household Revenues & Commercial Revenues & Low Pressure  \\
 \midrule
-Expression  & $\frac{w^{*}}{\alpha} \frac{dQ}{dR}$ &   $- F \frac{dB^{*}}{dR}$  & $\frac{dV}{dR}$ \\[1em]
-Estimates   &  \input{tables/est_welfare} \\
-            &  \input{tables/sd_welfare}  \\
-% Evaluated Estimates \\
+\input{tables/reg_geo}
 \bottomrule
@@
 
-Fixed costs:
-
-On average, pipe replacement projects replace 25.3 km of pipes at a cost of 166 million PhP.
-The average cost per pipe length is 9 million PhP per kilometer.
-Since around 0.73 km of pipes are replaced per small area, total project costs per small area are around 6.6 million PhP.
-With 275 connections per small area, project costs average 24,000 PhP per connection.
-
-6.6 million PhP/(275*1.41)
-
-New Revenues:
-
-Residential connections are billed 68 PhP more per month while commercial connections are billed 145 PhP more per month.
-Given that 94\% of connections are residential and 6\% of commercial, the total billing increase is around 73 PhP per month per connection.
-
-Decrease in Marginal Costs:
-
-After pipe-replacement, usage per connection decreases by 21 m3 per month.  Given marginal costs of 5 PhP per m3, then this decrease implies a cost reduction of 105 PhP per month.
-
-((73 )*12)/24000
-((400)*12)/24000
-((73 + 105 + 80)*12)/24000
-
 \begin{table}[h!] 
 \centering
-\caption{Total Water Supplied and Billed Estimates}\label{table:nrwregs}
+\caption{Welfare Inputs by Zone}\label{table:geoinputs}
 \vspace{-2mm} 
@@
 \toprule
-  & (1)   & (2)   & (3) \\
-  & Volume Billed  & Volume Supplied & \% Non-Revenue Water \\
+	& (1) & (2) & (3) & (4) & (5) \\
+ Zone & Share of Population & $\Delta$Consumer Surplus   & $\Delta$Total Revenue & $\Delta$Leakage Savings & Replacement Costs \\
 \midrule
-\input{tables/nrw}
-\bottomrule
-\end{tabular}
-\begin{tablenotes}
-\footnotesize
-\item Say it includes both fixed effects (Describe fixed effects...) .
-Weighting, discussion of different samples, clustering, controls (especially rate classes).
-This table predicts usage per household with pipe replacement and price with different fixed effects.
-\regtext 45 PhP = 1 USD \,\,
-\end{tablenotes}
-\end{threeparttable}
-\end{table}
-
-\begin{table}[h!] 
-\centering
-\caption{Usage per Connection Regression Estimates}\label{table:profitregs}
-\vspace{-2mm}
-\begin{threeparttable}
-\begin{tabular}{@{}l*{1}{cccc}@{}}
-\toprule
-  & (1) & (2) & (3) & (4)  \\
-  & Usage (m3) & Bill (PhP) & Usage (m3) & Bill (PhP) \\
-\midrule
-\input{tables/profitreg}
+\input{tables/geo_inputs}
 \bottomrule
@@
 This table predicts usage per household with pipe replacement and price with different fixed effects.
-\regtext 45 PhP = 1 USD \,\,
 \end{tablenotes}
@@
 
-%%% leave out booster pumps?
-\section{Counterfactuals}
-
-% We're focusing on a part of the natural monopoly where the costs are easy to measure (you replace pipes), but the benefits are less well understood.
-Different from the standard Laffont and Tirole model; closer to the Spence model which is a real contribution!
-(luckily high cost areas also have high benefit)
-
-% Set aside all other aspects of regulation to focus on quality!  Usually, capital is thought of as an input to deliver a certain quantity of the product.  Here we're focusing on a particular
-
-The following counterfactuals identify the welfare effects of optimal pipe replacements under five different information environments.
-The counterfactuals focus on the role of pipe replacements by holding fixed other aspects of water utility regulation.
-The full population of Manila is assumed to remain connected to service indefinitely.
-The water tariff is assumed to be determined independently of pipe replacements and to exactly cover all costs of water production (except pipe replacements).
-Unless otherwise specified, any cost savings or cost overruns as a result of the pipe replacements are assumed to be passed on to consumers in the form of fixed rebates or charges, which do not affect consumers' marginal incentives to consume water.
-Pipe replacements are assumed to be independent of operating costs such as labor or maintenance expenditures.
-
-% The \textit{full-information} counterfactual provides an optimal benchmark where the regulator chooses when to replace pipes to maximize total welfare given full information on demand and costs.
-In the \textit{regular-replacement} counterfactual, the regulator simply replaces all pipes at a fixed interval.
-In the \textit{quality-standards} counterfactual, the regulator establishes a minimum water pressure threshold and replaces pipes when pressure falls below the threshold.
-In the \textit{cost-recovery} counterfactual, the regulator schedules replacements to balance savings from lower pumping costs against upfront costs of the pipe replacements.
-In the \textit{firm-level} counterfactual, the regulator lets the firm decide when to replace pipes under the assumption that the firm has full demand and cost information.
-
-% - hold price fixed!
-% - decide replacements independently for each area
-% -
-
-% - Not permitted expenses, similar to a price-cap [that's fair] (under invest)
-% - Rate of return (allow for overlapping loans...?) --> no, don't ; make the point that the firm will want to replace pipes as soon as loans come due because the projects generate more than enough revenue to meet reasonable rates of return.
-
-% - permitted expenses or not? hard to know..
-% - rate of return when we don't know the production function; 
-% - high power --> redistribute little but keep costs down
-% - low power --> redistribute a lot but high costs
-% --- where are we?
-
-% --> low power: all the surplus goes to consumers, but decisions are based on limited information
-% --> high power: firm can get the surplus, but decisions are based on detailed consumer information; provides a strong incentive for the firm to figure out exactly the benefits of the investments
-%%% in practice, it's somewhere between
-%%% note that with the high power incentive, the prices are high, and the wedges get smaller if the prices are lower!
-%%% footnote explaining distinction with standard high versus low-powered incentives.
-
-% Since these projects generate streams of revenues in excess of their costs, then rate-of-return regulation would likely lead firms to very frequently replace pipes.\footnote{We do not explicitly model rate of return regulation here because the constraint would depend on whether the company could take out multiple loans, and the cost of capital for those loans.}
-
-The \textit{full-information} counterfactual simulates how often a regulator would optimally replace pipes in order to maximize welfare under full information.
-For each section of the service area, the regulator maximizes present-discounted consumer welfare indefinitely given by the following expression
-% doublecheck the tau's and t's
-\begin{align*}
-max_{R_t\in\{0,1\}} \,\, &\sum_{\tau = t}^{\infty} (1+\delta)^{t-\tau} [CS(k_{t}) + V(k_{t})]  \\
-V(k_{t}) &= W(k_{t}) - E(k_{t}) - L(k_{t})\\ 
-k_{t+1} &=  (1 + k_t) \, (1-R_t \mathbbm{1} \{ k_{t}> l\}) \\
-L(k_t) &= \frac{r(1+r)^{l} }{(1+r)^{l} -1 }\overline{L} \, \mathbbm{1} \{ k_{t}\leq l \}
-\end{align*}
-where $t$ indexes month, $\delta(>0)$ is the discount factor, and $k_t$ is the age of the pipes.
-$CS(k_{t})$ is the consumer surplus from pipe replacements as defined in equation (ref!), which is assumed to be decreasing in pipe age.
-$V(k_t)$ is the net revenue from pipe replacements, which depends on revenue from (increased) water sales, $W(k_{t})$, costs of water leakage, $E(k_{t})$, and payments on any loans to fund pipe replacements, $L(k_t)$.
-$V(k_t)$ is passed on to consumers as a fixed rebate or charge (ie.
-by adjusting the monthly service charge).
-Due to pipe deterioration, consumer surplus and water revenue are both assumed to be decreasing in pipe age while water leakage is assumed to increase with pipe page.
-
-Each month, the regulator chooses whether to replace pipes ($R_t = 1$) or not ($R_t = 0$).
-Replacing pipes sets the pipe age, $k_t$, back to zero and is only possible if the regulator has paid off any debt from a previous pipe replacement where $l$ indexes the duration of the debt.
-The regulator is assumed to fund a pipe replacement with a loan of total size, $\overline{L}$, at monthly interest rate, $r$, over duration, $l$.
-The expression for $L(k_t)$ calculates the size of the monthly loan payments.
-In this framework, the optimal schedule of pipe replacements balances net revenue against consumer surplus from new pipes.
-
-% While in practice, regulators may adjust both marginal prices and fixed monthly service charges, the model focuses only on fixed monthly service charges  
-% The model implicitly assumes that the regulator is able to implement fixed transfers to and from consumers without distorting their water consumption.
-For example, the regulator may offer all consumers fixed rebates in months with budget surpluses and higher fixed water charges in months with budget deficits.
-% Allowing negative net revenues in the model provides an approximation for this scheduling optimization.
-
-% While the model does not explicitly capture scheduling optimization, it 
-% This framework also holds the water tariff fixed.
-
-In the \textit{regular-replacement} counterfactual, the regulator only observes the age of the pipes and chooses to replace pipes as soon as they reach a certain age, $\overline{K}$.
-In the \textit{quality-standards} counterfactual, the regulator also observes the water pressure reaching consumers, $P(k_t)$.
-The regulator then chooses to replace pipes once the water pressure falls below a certain threshold, $\overline{P}$.
-In the \textit{cost-recovery} counterfactual, the regulator does not observe water pressure, but instead observes leakage costs.
-The regulator then replaces pipes to minimize leakage costs, $E(k_{t})$ and pipe replacement costs, $L(k_{t})$.
-
-% The marginal price is enough to cover the other fixed costs, and the firm gets to keep the leftovers!
-
-In the \textit{firm-level} counterfactual, the regulated firm is assumed to be fully aware of not only leakage costs, $E(k_t)$, but also revenue from water sales as result of pipe replacements, $W(k_t)$.
-To incentivize the firm to act on this information, the regulator allows the firm to enjoy the net revenues from pipe replacements, $V(k_t)$.
-The firm then chooses replacement rates to maximize, $V(k_t)$.
-In this case, consumer surplus, $CS(k_t)$ is equal to consumer welfare because consumers no longer receive transfers equal to net revenues.
-This arrangement is equivalent to ``price-cap'' regulation where the regulator sets a maximum price and firm is able to enjoy profits at prices up to the maximum while incurring investment costs.\footnote{See \cite{joskow2007regulation}.}
-
-Specify, exactly what is allowed to vary across places and what isn't!
-
-The simulations assume an annual discount factor of $\delta$=4\% and an annual interest rate of $r=5\%$, which is consistent with loans covering recent water investments.
-
-Costs, $L_()$, are measured...
+Consumer surplus with respect to pipe age, $CS(k_t)$, depends on the effect of pipe replacements on water use and booster pump use.
+The first and second columns of Table~\ref{table:counterinputs} reports these effects separately by zone.
+Effects range widely across zones spanning from -7 to -59 percentage point declines in booster pump use and from 4.7 to 1.7 cubic meter increases in monthly household water use.
+This heterogeneity may be driven by differences in preferences for quality service and/or by differential rates of pipe deterioration across areas.
+
+Combining these effects with earlier estimates of the price sensitivity (0.6) and cost of booster pumps (486 PhP/month) according to equation (\ref{eq:dvdr}) yields the effect of pipe replacements on consumer surplus (ie.
+$\Delta cs$) captured in column (1) of Table~\ref{table:geoinputs}.
+
+% These results inform expressions for $CS(k_t) = \Delta cs - \frac{k_t}{336}\Delta cs$ unique to each zone.
+
+\subsubsection{Revenue}
+
+Revenue with respect to pipe age, $W(k_{t})$, depends on the effect of pipe replacements on total revenue including both revenues earned per household and per commercial water connection.
+The third and fourth columns of Table~\ref{table:counterinputs} report these effects separately by zone.\footnote{The revenue measure for commercial connections keeps only observations between 0 and 10,000 PhP to account for potential bias of outliers because the distribution has a long right tail and large billing errors/corrections, which removes 9\% of the observations.}  Effects on revenues from households in column (3) are roughly proportional to the effect on water usage in column (2).\footnote{Differences are likely due to the fact that the non-linear structure of the water tariff, which causes high-use households to be exposed to higher marginal prices.}  Column (4) of Table~\ref{table:counterinputs} includes results for commercial water connections, which range from small shops to large factories.
+In some zones, commercial effects are large and positive while in other zones, results are close to zero or even below zero.
+Small effects may be explained by private investments in pumping stations by commercial entities.
+Negative coefficients may be explained by large concentrations of water refilling stations in particular zones.
+Composing over 5\% of commercial connections, water refilling stations filter and bottle piped water for resale, serving as possible substitutes to high quality tap water.
+
+Column (2) of Table~\ref{table:geoinputs} calculates the effect of pipe replacements on revenue (ie.
+$\Delta w$) by adding effects on revenues per household and effects on revenues per commercial connection weighted by commercial connections per household in each zone.
+On average for each household, there are around 0.18 commercial connections.
+
+\subsubsection{Leakage Savings}
+
+Leakage savings with respect to pipe age, $-E(k_{t})$ depend on the extent to which pipe replacements reduce the amount of water leaking from pipes.
+Pipe leakage is measured by comparing the amount of water supplied before and after pipe replacements.
+Water supply is measured at the monthly level for 1,242 hydrological areas for a total of 64,844 area-month observations.\footnote{The technology and infrastructure to measure water supply was gradually introduced across different areas during the sample period creating an unbalanced panel of supply measurements.
+Water supply is also measured per household by dividing total water supply by the total number of water connections in each area multiplied by the average number of households per connection in each area.}  The relatively small sample prevents estimation of zone-specific leakage rates.
+Therefore, the estimation assumes that all zones experience the same average reduction in leakage as a result of pipe replacements.
+Table~\ref{table:counterleaks} reports results on water supply from estimating equation (\ref{eq:counterest}) without heterogeneous effects by zone.
+Pipe replacement projects are associated with a statistically significant drop in water supplied of around 38 m3 per household.
+Given that the average household uses around 20 m3, this effect suggests that before pipe replacements, the utility loses at least two units of water for every one unit that reaches households.
+The water company approximates that the marginal cost of supplying water is around 5 PhP/m3.
+This approximation suggests substantial leakage savings equal to 188 PhP per household/month as reported in Column (4) of Table~\ref{table:geoinputs}.
+
+\begin{table}[h!] 
+\centering
+\caption{Effects of Pipe Replacements on Leakage}\label{table:counterleaks}
+\vspace{-2mm} 
+\begin{threeparttable} 
+\begin{tabular}{@{}l*{1}{C}@{}}
+\toprule
+	& (1)  \\
+  & Water Supply \\
+\midrule
+\input{tables/nrw_simple}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\subsubsection{Water Pressure}\label{section:counterpress}
+
+Water pressure with respect to pipe age, $P(k_{t})$ depends on the extent to which pipe replacements affect reported water flow.
+Water pressure is measured according to the connection survey, which asks if households do not have water pressure between 6 pm and midnight (when not using a booster pump).
+Column (5) of Table~\ref{table:counterinputs} reports effects on this indicator variable for each zone.
+Pipe replacements reduce the share of households reporting no water pressure across all zones with effects ranging widely from a 56 percentage points in zone 8 to less than 1 percentage point in zone 9.
+Heterogeneous effects may be driven by different rates of infrastructure degradation due to geology, road maintenance, or recent construction.
+Different effects may also be driven by proximity to nearby pumping stations which determine water continuity.
+Effects on water pressure appear roughly correlated with effects on outcomes in the first four columns of Table~\ref{table:counterinputs}.
+
+\subsubsection{Replacement Costs}\label{section:counterrep}
+
+For each hydrological area, pipe replacement project records include the total project costs and total kilometers of replaced pipes.
+Project costs per household in each zone are calculated by multiplying the average cost per kilometer of piping by the kilometers of pipe replaced per household.
+Column (5) of Table~\ref{table:geoinputs} presents project costs in terms of PhP per household.
+Costs range from 6,112 for zone 10 to 11,685 for zone 9.
+Differences in costs across zones likely stem from variations in the material and diameter of pipes needed for different areas as well as local housing densities.
+Costs appear only loosely correlated with consumer surplus and total revenue changes, which suggests that strictly minimizing replacement costs may not maximize total welfare.
+The counterfactuals assume an annual interest rate of $r=5\%$, which is the rate for many of the water company's current loans.
+Given the interest rate, loan payments, $L(k_t)$, necessary to fund the project costs are calculated for each zone.
+
+% The counterfactuals assume an annual discount rate of 5\% (or $\delta=0.0042$ in monthly terms).
+Also, the minimum loan term is assumed to be 5 years.
+Therefore, the counterfactuals do not allow for replacing pipes at intervals shorter than 5 years.
+
+\subsection{Counterfactual Results}\label{section:counterresults}
+
+DO MORE TO PUT THE SIZES IN CONTEXT!! [average bill, etc.!]
+
+For each counterfactual, the simulations compute the optimal frequency of pipe replacements (in years) as well as the welfare deviations from the optimal, full-information benchmark.
+Table~\ref{table:georesults} presents average results across all zones while Table~\ref{table:georesultsbyzone} includes counterfactual results for each zone separately.
+According to column (1), the optimal frequency of pipe replacements for the full information benchmark is 9 years on average (Table~\ref{table:georesults}) and ranges between 7 and 11 years for particular zones (Table~\ref{table:georesultsbyzone}).
+
+Column (2) includes results for the strategy of replacing all pipes every 25 years.
+This strategy roughly approximates the context in Manila where the regulated company replaced most of the pipes had been installed by the public utility 25 years ago.
+This strategy results in replacing pipes around 2.5 less frequent that the full-information benchmark.
+Row ``$\Delta$ Total Surplus'' measures the change in total surplus relative to the full-information benchmark in column (1) where surplus is measured in terms of PhP per household/month.
+Across all zones on average, replacements every 25 years lower welfare by 97 PhP per household/month relative to the full-information benchmark.
+
+Row ``$\Delta$ Cons.
+Surplus'' measures the change in surplus attributable to consumer utility from water use and booster pump expenditures (as described by equation (\ref{eq:dvdr})).
+The average decline in consumer surplus is almost as large as the total decline in welfare which suggests that most of the costs of infrequent pipe replacements are borne directly by consumers in the form of poor quality water consumption and increased booster pump expenditure.
+Under the assumption that the regulator is able to pass on any cost savings/overruns onto consumers, consumer welfare is equal to total surplus.
+This assumption is likely to hold for counterfactuals in columns (1) to (5).
+
+\begin{table}[h!] 
+\centering
+\caption{Counterfactual Results}\label{table:georesults}
+\vspace{-2mm} 
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{FFFFFF}@{}}
+\toprule
+	  & (1) & (2) & (3) & (4) & (5) & (6) \\
+  & Full info & Every 25 yrs & Pressure $<$90\% & Pressure $<$80\% & Cost min & Profit max \\
+\midrule
+Full Sample \\[.2em]
+\hspace{1em}Freq. (yrs) \input{tables/cr_y} \\[.3em]
+\hspace{1em}$\Delta$ Total Surplus \input{tables/cr_t} \\[.3em]
+\hspace{1em}$\Delta$ Cons. Surplus \input{tables/cr_c} \\[.5em]
+Without Zone 9 \\[.2em]
+\hspace{1em}Freq. (yrs) \input{tables/cr_y9} \\[.3em]
+\hspace{1em}$\Delta$ Total Surplus \input{tables/cr_t9} \\[.3em]
+\hspace{1em}$\Delta$ Cons. Surplus \input{tables/cr_c9} \\
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+\begin{table}[h!] 
+\centering
+\caption{Counterfactual Results by Zone}\label{table:georesultsbyzone}
+\vspace{-2mm} 
+\begin{threeparttable}
+\begin{tabular}{@{}l*{1}{DDDDDD}@{}}
+\toprule
+	  & (1) & (2) & (3) & (4) & (5) & (6) \\
+ Zone & Full info & Every 25 yrs & Pressure $<$10\% & Pressure $<$20\% & Cost min & Profit max \\
+\midrule
+\input{tables/counter_results}
+\bottomrule
+\end{tabular}
+\begin{tablenotes}
+\footnotesize
+\item Weighting, discussion of different samples, clustering, controls (especially rate classes).
+This table predicts usage per household with pipe replacement and price with different fixed effects.
+\end{tablenotes}
+\end{threeparttable}
+\end{table}
+
+Table~\ref{table:georesultsbyzone} indicates large heterogeneity in welfare impacts across zones.
+Table~\ref{table:georesultsbyzone} lists the ``$\Delta$ Total Surplus'' and ``$\Delta$ Cons.
+Surplus'' respectively in parentheses below the replacement years.
+While 25 year replacements reduce welfare by under 65 PhP per household/month in zones 2 and 5, the same policy lowers welfare by at least 130 PhP in zones 5 and 11.
+Columns (3) and (4) present counterfactuals where pipes are replaced when the share of households reporting at least some water pressure falls below 90\% and 80\% respectively.
+Zone 9 never reaches these thresholds within 50 years because pipe replacements are estimated to have zero effect on reported water pressure in this zone (Table~\ref{table:counterinputs}).
+Therefore, the counterfactuals assume that pipes in Zone 9 are replaced every 50 years.
+To account for Zone 9 being an outlier, Table~\ref{table:georesults} provides results for the full set of zones and for all zones except Zone 9.
+
+Column (3) finds that the strict 90\% threshold results in an average replacement frequency of 13 years and a drop in total surplus of only 42 PhP per household/month, which is less than half of the surplus change in Column (2).
+Table~\ref{table:georesultsbyzone} reveals substantial heterogeneity in replacement frequencies: four of the zones are constrained by the minimum 5-year rate while three of the zones exceed 15-year rates.
+These replacement frequencies appear at least somewhat correlated with the frequencies in the full-information benchmark, which suggests that quality standards may provide a useful signal of welfare.
+
+Column (4) tests a looser threshold of 80\%, which almost doubles the average welfare loss of the strict threshold in column (3).
+Moving from the strict to loose threshold increases the average replacement frequency from 13 years to 21 years.
+These findings indicate that welfare effects are very sensitive to the quality standards chosen by the regulator.
+
+% For both thresholds, consumer surplus improves relative to the full info optimum.  
+Excluding Zone 9 from average results in the second panel of Table~\ref{table:georesults} improves total welfare by around 20 PhP per household/month relative to the first panel for both columns (3) and (4).
+These results suggest that policies based on quality standards may be sensitive to outliers and/or the precision of pressure measurements.
+% The strict standard for actually results in higher quality.
+
+Column (5) presents the cost-minimization counterfactual where the replacement frequency is chosen to minimize pipe replacement costs and water leakage costs.
+The cost-minimization counterfactual results in an average replacement frequency of 15 years.
+Although this replacement frequency is roughly double the benchmark freqency, welfare is only 31 PhP lower than the benchmark.
+Table~\ref{table:georesultsbyzone} finds that the relative replacement frequencies across zones are similar between the cost-minimization counterfactual and the benchmark.
+% Since replacement costs account for all of the cost differences between zones, these results indicate that replacement costs provide a useful ::: DON'T REALLY WANT TO OVER_INTERPRET HERE....
+These results likely underestimate  % Cost min does not include NRW variation!
+
+Column (6) provides results for the profit maximization counterfactual where the replacement frequency is chosen to maximize revenue net of costs.
+Profit maximization results in an average replacement frequency of 12 years.
+Total surplus is only 12 PhP per household/month lower than the optimal benchmark, which is the smallest average gap across counterfactuals.
+In practice, the regulator is likely to allow the water company to enjoy profits from these investments as a condition of implementing a profit maximization regime.\footnote{For example, the regulator may set a maximum price that takes into account other observable operating/fixed costs, and then allow the company to invest in its own pipe replacements while also capturing the profits.}  Therefore in this counterfactual, consumer welfare equals consumer surplus.
+The relative reduction in consumer surplus is still smaller than the relative reduction in total surplus across the other counterfactuals, which suggests that the profit maximization counterfactual is the optimal second-best policy.
+
+\section{Conclusion}\label{section:conclusion}
+
+% Households are assumed to have common $\alpha$
+
+% % The framework requires specifying three quantities: (1) consumer surplus, $CS(k_t)$, (2) revenue, $W(k_{t})$, and (3) leakage costs, $E(k_{t})$.  Each quantity is assumed to
+
+% at a linear rate proportional to the decline in water usage in the years following the pipe replacement.
+
+% Specify, exactly what is allowed to vary across places and what isn't!
 
 % and the regulator allows the firm to maximize producer surplus, $PS(k) - L(k_{t})$.
-
 % Total welfare versus producer/consumer divide?
@@
 
-Consumer surplus and producer surplus are assumed to linearly decline in pipe age, $k_t$.
+% Consumer surplus and producer surplus are assumed to linearly decline in pipe age, $k_t$.
 This assumption is consistent with civil engineering research documenting a roughly linear relationship between pipe failure and age.\footnote{See \cite{ward2017deterioration}, \cite{kleiner2001comprehensive}, and \cite{aydogdu2015estimation}.}
-
-Since the majority of pipes are replaced
-
-Appendix on decom.
-
-Results are discussed below in Table [x].
-
- then the regulator maximization problem has an interior solution where the regulator choses whether to .  In practice, simulations solve the maximization problem recursively using
 
@@
 
-The fourth counterfactual imagines an uninformed regulator and a fully informed firm where the firm decides when to replace pipes.
+% The fourth counterfactual imagines an uninformed regulator and a fully informed firm where the firm decides when to replace pipes.
 The regulator does not adjust prices to compensate the firm for pipe replacements, which leaves the firm to maximize its own surplus from replacing pipes.\footnote{Strong incentive to reduce costs: This may occur when the regulator can't credibly commit to price increases or when the firm has a strong incentive to inflate costs which the regulator cannot verify.}
 
-according to advice from water engineers who measure costs of replacements as well as pumping cost savings.
+% according to advice from water engineers who measure costs of replacements as well as pumping cost savings.
 The regulator then replaces pipes to optimize upfront replacement costs against marginal savings in pumping costs.
 
-without knowing the replacement costs or how replacements would affect water demand.
+% without knowing the replacement costs or how replacements would affect water demand.
 However, the regulator is able to measure water pressure either through consumer surveys, consumer complaints, or pressure gauges.
@@
 
-Section Welfare:
-	- Welfare benefits with 10 yr 5\% loans (assume discount rates) or 50 yr 5\% loan?
-	- Welfare benefits with cash
-	- Are households willing to pay for pipe improvements?
-
-	- How do welfare estimates compare to traditional estimates from health measures?
-
-Robustness:
-	- Use nearest pipe replacement definition (selection into meter identification)
+	% - How do welfare estimates compare to traditional estimates from health measures?
+% Robustness:
+	% - Use nearest pipe replacement definition (selection into meter identification)
 
@@
 \section{Appendix}
+
+% \subsection{Leakage Measurement}\label{appendix:leakage}
+
+% Water supply is measured at the monthly level for 1,242 hydrological areas for a total of 64,844 area-month observations.  In order to measure water supply,
 
@@
 \centering
-\caption{Water and Booster Pump Use per Household Estimates}\label{table:mainregshet}
+\caption{First Stage and Reduced Form Estimates}\label{table:regstages}
 \vspace{-2mm} 
@@
 \toprule
-  & (1)       & (2)  & (3) & (4)            \\
-  & Water Use & Water Use  & Booster Pump Use & Booster Pump Use \\
+  & \multicolumn{2}{c}{Water Use} &    \multicolumn{2}{c}{Booster Pump Use}        \\
+  & First Stage & Reduced Form   & First Stage & Reduced Form  \\
 \midrule
-\input{tables/reghet}
+\input{tables/reg_stages}
 \bottomrule
@@
 \setcitestyle{authoryear,open={((},close={))}}
-\bibliography{library}
+\bibliography{library_booster}
 }

### 2021-02-09 phil_subcode/reps_pa_6.m

@@ -26,7 +26,7 @@ PSt=PSc+PSt;
 %%% simulate every 30!
 
 
-beta_up = .04/12;
+beta_up = .03/12;
 beta = 1/( 1 + beta_up );
 
 N = 500;
@@ -60,25 +60,18 @@ v(1,1)/1000
 v_PS(1,1)/1000
 v_CS(1,1)/1000
 
-% [h_ni,v_ni,v_PS_ni,v_CS_ni] = sim_reps_pa_noint(welfare,Q0_PS,Q0_CS,pipe_age,total_loan,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t, NRW(1) );
-% [v_ni(1) v_PS(1)]
-
-
 %%%% FULL WELFARE %%%%
 
 welfare=1;
 
 results = zeros(size(CSt,1),4);
 results_alt = zeros(size(CSt,1),4);
-results_noint = zeros(size(CSt,1),4);
 
 for i=1:size(CSt,1)
     [ht,vt,v_PSt,v_CSt]=sim_reps_pa(welfare,  PSt(i)  ,  CSt(i)  ,  pipe_age,  TLt(i)  ,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t, NRW(i) );
     results(i,:) = [ht vt(1) v_PSt(1) v_CSt(1) ];
     results_alt(i,:) = [ht vt(alt) v_PSt(alt) v_CSt(alt) ];
     
-    [ht_ni,vt_ni,v_PSt_ni,v_CSt_ni]=sim_reps_pa_noint(welfare,  PSt(i)  ,  CSt(i)  ,  pipe_age,  TLt(i)  ,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t, NRW(i) );
-    results_noint(i,:) = [ht_ni vt_ni(1) v_PSt_ni(1) v_CSt_ni(1) ];
 end
 
 [results(:,1)  results(:,2:4)/1000]
@@ -99,7 +92,6 @@ we=-.17;
 
 results_qual = zeros(size(CSt,1),4);
 results_qual_alt = zeros(size(CSt,1),4);
-results_qual_noint = zeros(size(CSt,1),4);
 
 for i=1:size(CSt,1)
     
@@ -107,22 +99,11 @@ for i=1:size(CSt,1)
     results_qual(i,:) = [ht vt(1) v_PSt(1) v_CSt(1) ];
[…]

### 2021-02-09 phil_subcode/reps_pv_1.m

@@ -1,0 +1,422 @@
+
+
+loc = '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_temp/';
+cd_out = '/Users/williamviolette/Documents/Philippines/phil_analysis/phil_codes/phil_paper/tables/';
+
+ 
+
+M   = csvread(strcat(loc,'mat_counter.csv'),1);
+% NRW = csvread(strcat(loc,'mat_counter_nrw.csv'),1);
+NRW = 188.*ones(size(M,1),1);
+CSt = M(:,1) + M(:,2);
+PSt = M(:,3) + NRW;
+TLt = M(:,4);
+Wm  = M(:,5);
+We  = M(:,6);
+ee  = M(:,7);
+Wbar=.2;
+
+MC = csvread(strcat(loc,'mat_counter_comm.csv'),1);
+PSc = MC(:,1).*MC(:,2);
+
+PSt=PSc+PSt;
+
+
+% CSe BSe Ae CPe 
+
+%%% simulate every 30!
+
+
+beta_up = .05/12;
+beta = 1/( 1 + beta_up );
+
+N = 500;
+
+A = repmat((0:N)',1,N+1)';
+Aprime = A';
+nA = size(A,1);
+
+pipe_age  =  25*12;
+% 28
+
+loan_term = 5;
+r = .05/12;
+
+Q0_CS = 161 ;
+Q0_PS = 131 ;
+total_loan = 17021;
+
+wbar=0;
+t=0;
+wm=0;
+we=0;
+
+alt = 10*12;
+
+%%% TEST FULL WELFARE
+welfare=1;
+
+[h,v,v_PS,v_CS] = sim_reps_va(welfare,Q0_PS,Q0_CS,pipe_age,total_loan,r,loan_term,nA,Aprime,A,beta,wm,we,wbar,t, NRW(1) )
+h
+v(1,1)/1000
+v_PS(1,1)/1000
+v_CS(1,1)/1000
+
+%%%% FULL WELFARE %%%%
+
+welfare=1;
+
+results = zeros(size(CSt,1),6);
+results_alt = zeros(size(CSt,1),4);
+
+for i=1:size(CSt,1)
[…]
